### 2022-07-08 Scripts/ASR_stocks.Rmd
remove columns from ages and nat.mort that are NA in mx

---
title: "ICM testing"
output: html_document
---

```{r, echo=F, message=F, warning=F}
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)

# OK, lets give this a spin...
funs <- c("https://raw.githubusercontent.com/Dave-Keith/ICM/main/Scripts/functions/backwards_sim.r")
# Now run through a quick loop to load each one, just be sure that your working directory is read/write!
for(fun in funs) 
{
  download.file(fun,destfile = basename(fun))
  source(paste0(getwd(),"/",basename(fun)))
  file.remove(paste0(getwd(),"/",basename(fun)))
}

# Choose 5 ICES stocks that we have the necessary data for
ASR <- read_xlsx("../Data/ASR_2018.xlsx", sheet = "ICES")
datatypes <- unique(gsub(x = names(ASR), pattern = "[^a-zA-Z]", replacement=""))
# we want:
# Year, Num, WA, Catch, AM, NM, StockID, Management, Area, Order, Family, Genus, Species
ASRdat <- ASR[,c(grep(x=names(ASR), "Num"),
                 grep(x=names(ASR), "WA"),
                 grep(x=names(ASR), "Catch"),
                 grep(x=names(ASR), "AM"),
                 grep(x=names(ASR), "NM"))]
ASRdat <- apply(X = ASRdat, 2, as.numeric)
ASRsp <- ASR[, which(!1:length(names(ASR)) %in% grep(x=names(ASR), ".", fixed=T))]
ASR_trim <- cbind(ASRsp, ASRdat)

# need a unique ID for stock
#table(ASR_trim$Management, ASR_trim$Species)
ASR_trim$Stock <- paste0(ASR_trim$Management, "_", ASR_trim$Area, "_", ASR_trim$Genus, "_", ASR_trim$Species)

ASR_long <- ASR_trim %>%
  pivot_longer(!c("Management", "Area", "Order", "Family", "Genus", "Species", "Stock", "Year")) %>%
  separate(col=name, into=c("type", "age"), sep = "\\.")

Stocks <- ASR_long %>%
  filter(!is.na(value)) %>%
  group_by(Stock, type) %>%
  summarize(count=length(unique(value))) %>%
  group_by(Stock) %>%
  summarize(types=length(unique(type))) %>%
  filter(types==5) %>%
  select(Stock)

ASR_stocks <- ASR_long %>%
  filter(Stock %in% Stocks$Stock) %>%
  filter(!is.na(value)) %>%
  arrange(Stock, Year, type, as.numeric(age))

Stocks <- ASR_stocks %>%
  group_by(Stock, Species, type) %>%
  summarize(ages=length(unique(age)),
            years=length(unique(Year))) %>%
  arrange(-years, -ages) %>%
  filter(!Species=="morhua") %>%
  distinct(Stock) %>%
  pull(Stock)

print(Stocks)

# Bring in the data
# Handy import function from the rio package... tricky part was getting the right filename here...
for(i in Stocks){
  print(i)
  ASR_sub <- ASR_long %>%
    select(Year, Stock, type, age, value) %>%
    filter(Stock==i)

  age.mat <- ASR_sub %>% filter(type=="AM") %>% rename(AM=value) %>% select(-type)
  nat.mort <-  ASR_sub %>% filter(type=="NM") %>% rename(NM=value) %>% select(-type)
  abund <- ASR_sub %>% filter(type=="Num") %>% rename(Num=value) %>% select(-type)
  weight.age <- ASR_sub %>% filter(type=="WA") %>% rename(WA=value) %>% select(-type)
  removals <- ASR_sub %>% filter(type=="Catch") %>% rename(Catch=value) %>% select(-type)

  data <- age.mat %>%
    full_join(nat.mort) %>%
    full_join(abund) %>%
    full_join(weight.age) %>%
    full_join(removals)

  data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
  data <- data[data$available==T,]

  # Tidy up the data for input...
  data$prop.nat.mort <- 1-exp(-data$NM)
  #prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))] <- 1-exp(-prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))])

  rem <- data %>% group_by(Year) %>% summarize(rem=sum(Catch,na.rm=T)) %>% pull(rem)
  #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
  years <- data %>% pull(Year) %>% unique() %>% sort()
  N.end <- sum(data[data$Year==max(years),]$Num)
  #N.end <- rowSums(abund[nrow(abund),-which(names(abund) %in% c("Year", "Stock", "type"))], na.rm=T)
  #vpa.abund <- rowSums(abund[,-which(names(abund) %in% c("Year", "Stock", "type"))], na.rm=T)
  vpa.abund <- data %>% group_by(Year) %>% summarize(vpa=sum(Num)) %>% pull(vpa)

  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
  #minage
  minage <- as.numeric(min(data$age))
  #maxage
  maxage <- as.numeric(max(data$age))
  #recruits
  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
  #ssn
  data$ssn <- data$Num * data$AM
  #ssb
  data$ssb <- data$ssn * data$WA
  #tot.ssb
  annual <- data %>% group_by(Year) %>% summarize(tot.ssb = sum(ssb)) %>% left_join(annual)
  #r.p.ssb
  annual$r.p.ssb <- annual$recruits/annual$tot.ssb
  # recs.per.age
  data <- left_join(data, annual)
  data$recs.per.age <- data$ssb*data$r.p.ssb
  # mx
  data$mx <- data$recs.per.age/data$ssn/2 # Moms only! Dividing by around 8 really nails it for NS cod for whatever reason :-)
  # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...

  age.mat <- data %>% select("Year", "age", "AM") %>% pivot_wider(names_from=age, values_from = AM) %>% select(-Year)
  prop.nat.mort <- data %>% select("Year", "age", "prop.nat.mort") %>% pivot_wider(names_from=age, values_from = prop.nat.mort) %>% select(-Year)
  weight.age <- data %>% select("Year", "age", "WA") %>% pivot_wider(names_from=age, values_from = WA) %>% select(-Year)
  mx <- data %>% select("Year", "age", "mx") %>% pivot_wider(names_from=age, values_from = mx) %>% select(-Year) %>% as.data.frame()

  tst <- icm.sim(years = years,
                 mat.age = age.mat,
                 nm = prop.nat.mort,
                 w.age = weight.age,
                 ages = minage:maxage,
                 rems = rem,
                 fecund = mx,
                 N.end = N.end,
                 pop.model = 'exponential',
                 n.sims = 5,
                 sd.mat = 0.5,
                 sd.nm = 0.5,
                 sd.wt = 0.5,
                 sd.fecund = 0.5)

  #Combine the data
  did.it.work <- data.frame(abund = c(vpa.abund,tst$Pop$abund),years = c(years,tst$Pop$years),sim = c(rep('VPA',length(years)),tst$Pop$sim))
  # Here get the Upper and lower 50% quantiles to make a functional boxplot
  quants <- did.it.work %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
                                                                        med = median(abund),
                                                                        U.50 = quantile(abund,probs=c(0.75)))

  # All the results in a plot
  print(ggplot() +
          geom_line(data=did.it.work, aes(x=years,y=abund,color=sim)) +
          xlab("") +
          ylab("Abundance (1000s)") +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + scale_color_viridis_d(end = 0.75) +
          ggtitle(i))
  # Same thing but functional boxplots
  print(ggplot() +
          geom_line(data=quants, aes(x=years,y= med)) +
          geom_ribbon(data=quants, aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue') +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          xlab("") + ylab("Abundance (1000s)") +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          ggtitle(i))
  # Plotting how the estimate of r changes over time (which you can do when we have time varying inputs (e.g. Wgt, M, or maturity at age)
  print(ggplot(tst$r) +
          geom_line(aes(x=years,y=r,group=n.sims,color=n.sims)) +
          xlab("") +
          ylab("Estimated growth rate (r)") +
          #scale_y_continuous(breaks = seq(0,1.5,by=0.1)) +
          #scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          scale_color_viridis_c(end = 0.75) +
          ggtitle(i))
}
```

### 2022-07-08 Scripts/ASR_stocks.r

@@ -1,0 +1,176 @@
+# OK, so using the ICES assessments here's what we get for North Sea cod.
+library(readxl)
+library(tidyverse)
+library(rio)
+library(ggthemes)
+
+# OK, lets give this a spin...
+funs <- c("https://raw.githubusercontent.com/Dave-Keith/ICM/main/Scripts/functions/backwards_sim.r")
+# Now run through a quick loop to load each one, just be sure that your working directory is read/write!
+for(fun in funs) 
+{
+  download.file(fun,destfile = basename(fun))
+  source(paste0(getwd(),"/",basename(fun)))
+  file.remove(paste0(getwd(),"/",basename(fun)))
+}
+
+# Choose 5 ICES stocks that we have the necessary data for
+ASR <- read_xlsx("./Data/ASR_2018.xlsx", sheet = "ICES")
+datatypes <- unique(gsub(x = names(ASR), pattern = "[^a-zA-Z]", replacement=""))
+# we want:
+# Year, Num, WA, Catch, AM, NM, StockID, Management, Area, Order, Family, Genus, Species
+ASRdat <- ASR[,c(grep(x=names(ASR), "Num"), 
+                 grep(x=names(ASR), "WA"), 
+                 grep(x=names(ASR), "Catch"),
+                 grep(x=names(ASR), "AM"),
+                 grep(x=names(ASR), "NM"))]
+ASRdat <- apply(X = ASRdat, 2, as.numeric)
+ASRsp <- ASR[, which(!1:length(names(ASR)) %in% grep(x=names(ASR), ".", fixed=T))]
+ASR_trim <- cbind(ASRsp, ASRdat)
+
+# need a unique ID for stock
+table(ASR_trim$Management, ASR_trim$Species)
+ASR_trim$Stock <- paste0(ASR_trim$Management, "_", ASR_trim$Area, "_", ASR_trim$Genus, "_", ASR_trim$Species)
+
+ASR_long <- ASR_trim %>%
+  pivot_longer(!c("Management", "Area", "Order", "Family", "Genus", "Species", "Stock", "Year")) %>% 
+  separate(col=name, into=c("type", "age"), sep = "\\.")
+
+Stocks <- ASR_long %>%
+  filter(!is.na(value)) %>%
+  group_by(Stock, type) %>%
+  summarize(count=length(unique(value))) %>%
+  group_by(Stock) %>%
+  summarize(types=length(unique(type))) %>%
[…]

### 2022-07-08 Scripts/functions/Lotka_r.r

@@ -19,9 +19,8 @@ lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL
                   #                         2) Using the "Then_pauly" nat mort (L.inf and K only) 
                   #                         3) using the "Jensen K" nat mort(K only needed)
                   #                         4) if using the 'eggs' method to estimate fecundity. (L.inf,K, t0, a.fec.len,b.fec.len)
-                  ) 
+) 
 {
-  
   
   # Some warning messages if you didn't include something you needed...
   #if(nat.mort == "Jensen Maturity")  stop("maybe)
@@ -48,7 +47,7 @@ lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL
   
   # Set up a dataframe
   res <- data.frame(yrs = NA, r = NA)
-  if(yrs > 1) n.yrs <- length(yrs) else n.yrs <- 2 # Needs to be 2 if just doing it for one year to work how I have loop set up
+  if(length(yrs) > 1) n.yrs <- length(yrs) else n.yrs <- 2 # Needs to be 2 if just doing it for one year to work how I have loop set up
   # Get the maximum age
   max.age <- max(ages)
   # If you are using the fecund = ages, then we need to start from age 0
@@ -97,7 +96,7 @@ lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL
     if(is.vector(wt.at.age)) W.age <- rlnorm(length(wt.at.age),wt.at.age,sd.nm)
     if(!is.vector(wt.at.age)) for(i in 1:nrow(wt.at.age)) W.age[i,] <- rlnorm(length(wt.at.age[i,]),as.numeric(log(wt.at.age[i,])),sd.wt)
   }
-  #browser()
+  
   if(is.null(wt.at.age) | fecund =='eggs')
   {
     L.age <- L.inf*(1-exp(-K*(ages-t0))) # Need this for both eggs case and missing weight case.
@@ -134,7 +133,7 @@ lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL
     if(is.vector(nat.mort)) nat.mort <- rlnorm(length(nat.mort),nat.mort,sd.nm)
   }
   
-
+  
   
   # Now get the mx vector, 
   if(is.character(fecund))  
[…]

### 2022-07-08 Scripts/functions/backwards_sim.r

@@ -49,7 +49,6 @@ icm.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
                   L.inf = NULL,K = NULL,t0 = NULL, a.len.wgt = NULL, b.len.wgt = NULL, a.fec.len = NULL, b.fec.len = NULL,
                   sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0)
 {
-  
   # Download the function to go from inla to sf
   funs <- c("https://raw.githubusercontent.com/Dave-Keith/ICM/main/Scripts/functions/Lotka_r.r",
             "https://raw.githubusercontent.com/Dave-Keith/ICM/main/Scripts/functions/backwards_project.r"
@@ -81,7 +80,9 @@ icm.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
     if(i == 1)
     {
       junk<-lotka.r(yrs = years,age.mat = mat.age,nat.mort = nm,ages=ages,wt.at.age=w.age,fecund=fecund,
-                    L.inf = L.inf,K = K,t0 = t0, a.len.wgt = a.len.wgt, b.len.wgt = b.len.wgt, a.fec.len = a.fec.len, b.fec.len = b.fec.len,
+                    L.inf = L.inf,K = K,t0 = t0, 
+                    a.len.wgt = a.len.wgt, b.len.wgt = b.len.wgt, 
+                    a.fec.len = a.fec.len, b.fec.len = b.fec.len,
                     sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0)
     } # end if(i == 1)
       
@@ -143,7 +144,7 @@ icm.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
       Pop.vec[y-1] <- pop.next
 
     } #Loop through all the years.
-    #browser()
+    
     Pop$abund[Pop$sim == i]<-Pop.vec
     
     ### calc removals (increase due to r plus amount population declined by):   

### 2022-07-08 Scripts/functions/backwards_sim.r
Update backwards_sim.r

@@ -50,8 +50,8 @@ icm.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
                   sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0)
 {
   # Download the function to go from inla to sf
-  funs <- c("https://raw.githubusercontent.com/Dave-Keith/ICM/main/Scripts/functions/Lotka_r.r",
-            "https://raw.githubusercontent.com/Dave-Keith/ICM/main/Scripts/functions/backwards_project.r"
+  funs <- c("https://raw.githubusercontent.com/freyakeyser/ICM/main/Scripts/functions/Lotka_r.r",
+            "https://raw.githubusercontent.com/freyakeyser/ICM/main/Scripts/functions/backwards_project.r"
   )
   # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
   for(fun in funs) 

### 2022-07-11 Scripts/ASR_stocks.Rmd
Update ASR_stocks.Rmd

@@
 title: "ICM testing"
-output: html_document
+output:
+  word_document: default
+  html_document: default
+  pdf_document: default
+editor_options:
+  chunk_output_type: console
 ---
+
+The stocks chosen for testing were those with the most complete data.
+
+Some catch information was missing for certain years. These years are marked with "?" in the plots that follow. The median annual catch was assumed for missing years.
+
+Catch data for _Sprattus sprattus_ (European sprat) was manually converted to be on the 1000s scale, in order to align with abundance data.
 
@@
 
-# OK, lets give this a spin...
-funs <- c("https://raw.githubusercontent.com/Dave-Keith/ICM/main/Scripts/functions/backwards_sim.r")
-# Now run through a quick loop to load each one, just be sure that your working directory is read/write!
-for(fun in funs) 
-{
-  download.file(fun,destfile = basename(fun))
-  source(paste0(getwd(),"/",basename(fun)))
-  file.remove(paste0(getwd(),"/",basename(fun)))
-}
+# # OK, lets give this a spin...
+# funs <- c("https://raw.githubusercontent.com/Dave-Keith/ICM/main/Scripts/functions/backwards_sim.r")
+# # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
+# for(fun in funs) 
+# {
+#   download.file(fun,destfile = basename(fun))
+#   source(paste0(getwd(),"/",basename(fun)))
+#   file.remove(paste0(getwd(),"/",basename(fun)))
+# }
+
+source("./functions/backwards_sim.R")
 
@@
 
+  if(i=="ICES-WGBFAS_BS 22-32_Sprattus_sprattus") removals$Catch <- removals$Catch/1000
+
   data <- age.mat %>%
@@
 
-  rem <- data %>% group_by(Year) %>% summarize(rem=sum(Catch,na.rm=T)) %>% pull(rem)
+  rem <- data %>% group_by(Year) %>% summarize(rem=sum(Catch)) %>% pull(rem)
+
+  missing_rem<- NULL
+  if(any(is.na(rem))) {
+    missing_rem <- unique(data$Year)[which(is.na(rem))]
+    rem[is.na(rem)] <- median(rem, na.rm=T)
+  }
+
   #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
@@
   #minage
-  minage <- as.numeric(min(data$age))
+  minage <- min(as.numeric(data$age))
   #maxage
-  maxage <- as.numeric(max(data$age))
+  maxage <- max(as.numeric(data$age))
   #recruits
@@
 
+  did.it.work$missing[did.it.work$years %in% missing_rem] <- "missing"
+
   # All the results in a plot
@@
           theme_few() + theme(legend.position = 'none') + scale_color_viridis_d(end = 0.75) +
-          ggtitle(i))
+          ggtitle(i) +
+          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?")))
   # Same thing but functional boxplots
@@
           theme_few() + theme(legend.position = 'none') +
-          ggtitle(i))
+          ggtitle(i)+
+          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?")))
   # Plotting how the estimate of r changes over time (which you can do when we have time varying inputs (e.g. Wgt, M, or maturity at age)

### 2022-08-11 Scripts/ASR_stocks.Rmd

@@
 output:
-  word_document: default
+  word_document: 
+    reference_docx: template.docx
   html_document: default
@@
 
-```{r, echo=F, message=F, warning=F}
+```{r, echo=F, message=F, warning=F, fig.width=6, fig.height=4}
 # OK, so using the ICES assessments here's what we get for North Sea cod.
@@
 
+# summary plots for ALL stocks
+for (i in unique(ASR_long$Stock)) {
+  ASR_sub <- ASR_long %>%
+    select(Year, Stock, type, age, value) %>%
+    filter(Stock==i)
+  maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]))
+  maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)])
+  minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)])
+  forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
+  p1 <- ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
+        geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
+        theme_bw() + 
+        ggtitle(i) +
+    guides(x =  guide_axis(angle = 90)) 
+  print(p1)
+
+  if(!dir.exists(paste0("../Figures/", i))) dir.create(paste0("../Figures/", i))
+
+  png(filename=paste0("../Figures/", i, "/data_summary_", i, ".png"), height=4, width=12, res=400, units="in")
+  print(p1)
+  dev.off()
+}
+
 Stocks <- ASR_long %>%
@@
     filter(Stock==i)
+
+  # maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]))
+  # maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)])
+  # minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)])
+  # forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
+  # 
+  # # summary plots
+  # print(ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
+  #         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
+  #         theme_bw() + 
+  #         ggtitle(i)
+  # )
 
@@
   # All the results in a plot
-  print(ggplot() +
+  p2 <- ggplot() +
           geom_line(data=did.it.work, aes(x=years,y=abund,color=sim)) +
@@
           ggtitle(i) +
-          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?")))
+          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
   # Same thing but functional boxplots
-  print(ggplot() +
+  p3 <- ggplot() +
           geom_line(data=quants, aes(x=years,y= med)) +
@@
           ggtitle(i)+
-          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?")))
+          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
   # Plotting how the estimate of r changes over time (which you can do when we have time varying inputs (e.g. Wgt, M, or maturity at age)
-  print(ggplot(tst$r) +
+  p4 <- ggplot(tst$r) +
           geom_line(aes(x=years,y=r,group=n.sims,color=n.sims)) +
@@
           scale_color_viridis_c(end = 0.75) +
-          ggtitle(i))
+          ggtitle(i)
+
+  print(p2)
+  print(p3)
+  print(p4)
+
+  png(filename=paste0("../Figures/", i, "/runs_vs_vpa_", i, ".png"), height=4, width=6, res=400, units="in")
+  print(p2)
+  dev.off()
+  png(filename=paste0("../Figures/", i, "/runs_vs_vpa_ribbon_", i, ".png"), height=4, width=6, res=400, units="in")
+  print(p3)
+  dev.off()
+  png(filename=paste0("../Figures/", i, "/growth_", i, ".png"), height=4, width=6, res=400, units="in")
+  print(p4)
+  dev.off()
 }

### 2022-08-30 Scripts/Calcs_to_get_AM__WA_or_N_used in models.R
All NW data are entered
Need to do a check on the catch data to ensure it is in correct units and accounts for all removals.

@@ -2,8 +2,7 @@
 # Pacific Cod in Bering Sea from Stark 2007.
 logis.mod <- function(alpha,beta,x){1/(1+exp((alpha + beta*x)))}
 
-x <- 0:10
-alpha = 4.7143
+1482/3alpha = 4.7143
 beta = -0.9654
 
 res <- logis.mod(alpha,beta,x)
@@ -26,3 +25,13 @@ beta3 = -0.965
 
 res3 <- logis.mod(alpha3,beta3,x3)
 res3
+
+# NEFSC Altantic Mackerel
+logis.mod2 <- function(alpha,beta,x){1/(1+exp(-beta*(x - alpha)))}
+
+x4 <- 1:15
+alpha4 <- 1.71
+beta4 <- 2.94
+
+res4 <- logis.mod2(alpha4,beta4,x4)
+res4

### 2022-09-02 Scripts/ASR_stocks.Rmd
ICES stocks completed
I have run the analysis on the ICES stocks with 250 replicates per run, took about 6 hours to run for 46 stocks.

@@
 
-The stocks chosen for testing were those with the most complete data.
-
-Some catch information was missing for certain years. These years are marked with "?" in the plots that follow. The median annual catch was assumed for missing years.
-
-Catch data for _Sprattus sprattus_ (European sprat) was manually converted to be on the 1000s scale, in order to align with abundance data.
+The data is now avilable to test this on at least 81 stocks.
+All of the NE Atlantic stocks (ICES) have been through the QA/QC process and we are happy with those data (Sept 1, 2022).
+Let's see if we can get this to work on all the stocks with sufficient data...
 
@@
 
-source("./functions/backwards_sim.R")
+source("D:/Github/ICM/Scripts/functions/backwards_sim.R")
 
 # Choose 5 ICES stocks that we have the necessary data for
-ASR <- read_xlsx("../Data/ASR_2018.xlsx", sheet = "ICES")
+#ASR <- read_xlsx("../Data/ASR_2018.xlsx", sheet = "ICES")
+ASR <- read.csv("D:/Github/ICM/Data/ICM_data_NE_atlantic_stocks.csv")
 datatypes <- unique(gsub(x = names(ASR), pattern = "[^a-zA-Z]", replacement=""))
+
+# Replace 0's in Num.tot with NA so the rest of this works as Freya designed it to...
+ASR$Num.tot[ASR$Num.tot == 0] <- NA
 # we want:
@@
                  grep(x=names(ASR), "NM"))]
+# Making all the data numberic that should be numeric
 ASRdat <- apply(X = ASRdat, 2, as.numeric)
+# Getting the species info back
 ASRsp <- ASR[, which(!1:length(names(ASR)) %in% grep(x=names(ASR), ".", fixed=T))]
+# And binding it all back together
 ASR_trim <- cbind(ASRsp, ASRdat)
@@
 ASR_long <- ASR_trim %>%
-  pivot_longer(!c("Management", "Area", "Order", "Family", "Genus", "Species", "Stock", "Year")) %>%
+  pivot_longer(!c("Management", "Area", "Order", "Family", "Genus", "Species", "Stock", "Year","Model","Case","Notes")) %>%
   separate(col=name, into=c("type", "age"), sep = "\\.")
@@
   ASR_sub <- ASR_long %>%
-    select(Year, Stock, type, age, value) %>%
-    filter(Stock==i)
+    dplyr::select(Year, Stock, type, age, value) %>%
+    dplyr::filter(Stock==i)
   maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]))
@@
 
-  if(!dir.exists(paste0("../Figures/", i))) dir.create(paste0("../Figures/", i))
+  if(!dir.exists(paste0("D:/Github/ICM/Figures/", i))) dir.create(paste0("D:/Github/ICM/Figures/", i))
 
-  png(filename=paste0("../Figures/", i, "/data_summary_", i, ".png"), height=4, width=12, res=400, units="in")
+  png(filename=paste0("D:/Github/ICM/Figures/", i, "/data_summary_", i, ".png"), height=4, width=12, res=400, units="in")
   print(p1)
@@
 Stocks <- ASR_long %>%
-  filter(!is.na(value)) %>%
-  group_by(Stock, type) %>%
-  summarize(count=length(unique(value))) %>%
-  group_by(Stock) %>%
-  summarize(types=length(unique(type))) %>%
-  filter(types==5) %>%
-  select(Stock)
+                    dplyr::filter(!is.na(value)) %>%
+                    dplyr::group_by(Stock, type) %>%
+                    dplyr::summarize(count=length(unique(value))) %>%
+                    dplyr::group_by(Stock) %>%
+                    dplyr::summarize(types=length(unique(type))) %>%
+                    dplyr::filter(types==5) %>%
+                    dplyr::select(Stock)
 
 ASR_stocks <- ASR_long %>%
-  filter(Stock %in% Stocks$Stock) %>%
-  filter(!is.na(value)) %>%
-  arrange(Stock, Year, type, as.numeric(age))
+                        dplyr::filter(Stock %in% Stocks$Stock) %>%
+                        dplyr::filter(!is.na(value)) %>%
+                        dplyr::arrange(Stock, Year, type, as.numeric(age))
 
-Stocks <- ASR_stocks %>%
-  group_by(Stock, Species, type) %>%
-  summarize(ages=length(unique(age)),
-            years=length(unique(Year))) %>%
-  arrange(-years, -ages) %>%
-  filter(!Species=="morhua") %>%
-  distinct(Stock) %>%
-  pull(Stock)
-
-print(Stocks)
-
+# Stocks <- ASR_stocks %>%
+#                       dplyr::group_by(Stock, Species, type) %>%
+#                       dplyr::summarize(ages=length(unique(age)),
+#                                 years=length(unique(Year))) %>%
+#                       dplyr::arrange(-years, -ages) %>%
+#                       dplyr::filter(!Species=="morhua") %>%
+#                       dplyr::distinct(Stock) %>%
+#                       dplyr::pull(Stock)
+# 
+# print(Stocks)
+Stocks <- Stocks$Stock
+# Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
+Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
+# Esmarki doesn't work great as it is assessed using a quarterly modle.
+Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
 # Bring in the data
@@
   ASR_sub <- ASR_long %>%
-    select(Year, Stock, type, age, value) %>%
-    filter(Stock==i)
+    dplyr::select(Year, Stock, type, age, value) %>%
+    dplyr::filter(Stock==i)
 
@@
 
-  age.mat <- ASR_sub %>% filter(type=="AM") %>% rename(AM=value) %>% select(-type)
-  nat.mort <-  ASR_sub %>% filter(type=="NM") %>% rename(NM=value) %>% select(-type)
-  abund <- ASR_sub %>% filter(type=="Num") %>% rename(Num=value) %>% select(-type)
-  weight.age <- ASR_sub %>% filter(type=="WA") %>% rename(WA=value) %>% select(-type)
-  removals <- ASR_sub %>% filter(type=="Catch") %>% rename(Catch=value) %>% select(-type)
+  age.mat <- ASR_sub %>% dplyr::filter(type=="AM") %>% dplyr::rename(AM=value) %>% dplyr::select(-type)
+  nat.mort <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
+  abund <- ASR_sub %>% dplyr::filter(type=="Num") %>% dplyr::rename(Num=value) %>% dplyr::select(-type)
+  weight.age <- ASR_sub %>% dplyr::filter(type=="WA") %>% dplyr::rename(WA=value) %>% dplyr::select(-type)
+  removals <- ASR_sub %>% dplyr::filter(type=="Catch") %>% dplyr::rename(Catch=value) %>% dplyr::select(-type)
 
-  if(i=="ICES-WGBFAS_BS 22-32_Sprattus_sprattus") removals$Catch <- removals$Catch/1000
+ # if(i=="ICES-WGBFAS_BS 22-32_Sprattus_sprattus") removals$Catch <- removals$Catch/1000
 
@@
 
-  rem <- data %>% group_by(Year) %>% summarize(rem=sum(Catch)) %>% pull(rem)
+  rem <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(rem=sum(Catch,na.rm=T)) %>% dplyr::pull(rem)
 
@@
   #vpa.abund <- rowSums(abund[,-which(names(abund) %in% c("Year", "Stock", "type"))], na.rm=T)
-  vpa.abund <- data %>% group_by(Year) %>% summarize(vpa=sum(Num)) %>% pull(vpa)
+  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num)) %>% pull(vpa)
 
@@
   data$mx <- data$recs.per.age/data$ssn/2 # Moms only! Dividing by around 8 really nails it for NS cod for whatever reason :-)
+  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
   # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...
 
-  age.mat <- data %>% select("Year", "age", "AM") %>% pivot_wider(names_from=age, values_from = AM) %>% select(-Year)
-  prop.nat.mort <- data %>% select("Year", "age", "prop.nat.mort") %>% pivot_wider(names_from=age, values_from = prop.nat.mort) %>% select(-Year)
-  weight.age <- data %>% select("Year", "age", "WA") %>% pivot_wider(names_from=age, values_from = WA) %>% select(-Year)
-  mx <- data %>% select("Year", "age", "mx") %>% pivot_wider(names_from=age, values_from = mx) %>% select(-Year) %>% as.data.frame()
+  age.mat <- data %>% dplyr::select("Year", "age", "AM") %>% pivot_wider(names_from=age, values_from = AM) %>% dplyr::select(-Year)
+  prop.nat.mort <- data %>% dplyr::select("Year", "age", "prop.nat.mort") %>% pivot_wider(names_from=age, values_from = prop.nat.mort) %>% dplyr::select(-Year)
+  weight.age <- data %>% dplyr::select("Year", "age", "WA") %>% pivot_wider(names_from=age, values_from = WA) %>% dplyr::select(-Year)
+  mx <- data %>% dplyr::select("Year", "age", "mx") %>% pivot_wider(names_from=age, values_from = mx) %>% dplyr::select(-Year) %>% as.data.frame()
 
@@
                  pop.model = 'exponential',
-                 n.sims = 5,
+                 n.sims = 1000,
                  sd.mat = 0.5,
@@
 
-  png(filename=paste0("../Figures/", i, "/runs_vs_vpa_", i, ".png"), height=4, width=6, res=400, units="in")
+  png(filename=paste0("D:/Github/ICM/Figures/", i, "/runs_vs_vpa_", i, ".png"), height=4, width=6, res=400, units="in")
   print(p2)
   dev.off()
-  png(filename=paste0("../Figures/", i, "/runs_vs_vpa_ribbon_", i, ".png"), height=4, width=6, res=400, units="in")
+  png(filename=paste0("D:/Github/ICM/Figures/", i, "/runs_vs_vpa_ribbon_", i, ".png"), height=4, width=6, res=400, units="in")
   print(p3)
   dev.off()
-  png(filename=paste0("../Figures/", i, "/growth_", i, ".png"), height=4, width=6, res=400, units="in")
+  png(filename=paste0("D:/Github/ICM/Figures/", i, "/growth_", i, ".png"), height=4, width=6, res=400, units="in")
   print(p4)

### 2022-09-05 Scripts/ASR_stocks.Rmd
All stocks now run
Results are summarized in the pdf in the scripts folder. Results from naive run for all the stocks.

@@
 output:
+  pdf_document: default
+  html_document: default
   word_document: 
-    reference_docx: template.docx
-  html_document: default
-  pdf_document: default
+    #reference_docx: template.docx
 editor_options:
@@
 #ASR <- read_xlsx("../Data/ASR_2018.xlsx", sheet = "ICES")
-ASR <- read.csv("D:/Github/ICM/Data/ICM_data_NE_atlantic_stocks.csv")
+ASR1 <- read.csv("D:/Github/ICM/Data/ICM_data_NE_atlantic_stocks.csv")
+ASR <- read.csv("D:/Github/ICM/Data/ICM_data_NW_atlantic_stocks.csv")
+ASR <- rbind(ASR1,ASR)
 datatypes <- unique(gsub(x = names(ASR), pattern = "[^a-zA-Z]", replacement=""))
@@
 ASR_long <- ASR_trim %>%
-  pivot_longer(!c("Management", "Area", "Order", "Family", "Genus", "Species", "Stock", "Year","Model","Case","Notes")) %>%
+  pivot_longer(!c("Management", "Area", "Order", "Family", "Genus", "Species", "Stock", "Year","Meeting_or_reference","Model","Case","Notes")) %>%
   separate(col=name, into=c("type", "age"), sep = "\\.")
@@
 # Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
-Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
+#Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
 # Esmarki doesn't work great as it is assessed using a quarterly modle.
-Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
+#Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
 # Bring in the data
@@
                  pop.model = 'exponential',
-                 n.sims = 1000,
+                 n.sims = 500,
                  sd.mat = 0.5,

### 2023-03-15 Scripts/ASR_stocks.Rmd
Fixed fecundity offset
Had to wrap my head around making sure the mx vector was in the correct year... had to account for offset of recruits showing up in the data.  Was painful... think I got it now.

@@
 
-The data is now avilable to test this on at least 81 stocks.
+The data is now available to test this on at least 81 stocks.
 All of the NE Atlantic stocks (ICES) have been through the QA/QC process and we are happy with those data (Sept 1, 2022).
@@
                  grep(x=names(ASR), "NM"))]
-# Making all the data numberic that should be numeric
+# Making all the data numeric that should be numeric
 ASRdat <- apply(X = ASRdat, 2, as.numeric)
@@
     dplyr::filter(Stock==i)
-  maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]))
-  maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)])
-  minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)])
+  maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]),na.rm=T)
+  maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
+  minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
   forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
+  forplot <- forplot[!is.na(forplot$value),] # remove the NAs, hopefully this works for all the stocks...
   p1 <- ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
@@
 
-  rem <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(rem=sum(Catch,na.rm=T)) %>% dplyr::pull(rem)
+  rem <- data %>% dplyr::group_by(Year,.drop=F) %>% dplyr::summarize(rem=sum(Catch,na.rm=T)) #%>% dplyr::pull(rem)
 
   missing_rem<- NULL
-  if(any(is.na(rem))) {
-    missing_rem <- unique(data$Year)[which(is.na(rem))]
-    rem[is.na(rem)] <- median(rem, na.rm=T)
+  if(any(is.na(rem$rem))) 
+  {
+    missing_rem <- unique(data$Year)[which(is.na(rem$rem))]
+    rem$rem[is.na(rem$rem)] <- median(rem$rem, na.rm=T)
   }
@@
   #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
-  years <- data %>% pull(Year) %>% unique() %>% sort()
+  years <- data %>% dplyr::pull(Year) %>% unique() %>% sort()
   N.end <- sum(data[data$Year==max(years),]$Num)
@@
   #ssb
-  data$ssb <- data$ssn * data$WA
+  data$ssb <- data$ssn * data$WA #I need to figure out how to line this up with the number of recruits for the right years in the data object.... got it right for the overall r.p.ssb below.
   #tot.ssb
   annual <- data %>% group_by(Year) %>% summarize(tot.ssb = sum(ssb)) %>% left_join(annual)
-  #r.p.ssb
-  annual$r.p.ssb <- annual$recruits/annual$tot.ssb
+  #r.p.ssb This needs to be offset by the age of recruits
+  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+1):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage)])
   # recs.per.age
   data <- left_join(data, annual)
-  data$recs.per.age <- data$ssb*data$r.p.ssb
+  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
+  tmp <- NULL
+  for(j in 1:length(years))
+  {
+    tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
+    tst$Year <- tst$Year + minage
+    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
+    tmp[[j]] <- tst
+  }
+  # Unpack the list
+  ssb.off <- do.call('rbind',tmp)
+  # And merge it with the data object
+  data <- left_join(data,ssb.off,by=c("Year","age"))
+  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
   # mx
-  data$mx <- data$recs.per.age/data$ssn/2 # Moms only! Dividing by around 8 really nails it for NS cod for whatever reason :-)
+  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
+  # This works because 'males' is also in 'females'
+  if(grepl("males",i)) data$mx <- data$recs.per.age/data$ssn.offset 
+  if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
   data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
+  # Easier to remove the years where we don't have recs.per.age...
+  #data <- data %>% dplyr::filter(Year %in% years[(minage+1):length(years)])
   # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...
@@
   age.mat <- data %>% dplyr::select("Year", "age", "AM") %>% pivot_wider(names_from=age, values_from = AM) %>% dplyr::select(-Year)
-  prop.nat.mort <- data %>% dplyr::select("Year", "age", "prop.nat.mort") %>% pivot_wider(names_from=age, values_from = prop.nat.mort) %>% dplyr::select(-Year)
+  prop.nat.mort <- data %>% dplyr::select("Year", "age", "prop.nat.mort") %>% pivot_wider(names_from=age, values_from = prop.nat.mort) %>% dplyr::select(-Year) %>% as.data.frame
   weight.age <- data %>% dplyr::select("Year", "age", "WA") %>% pivot_wider(names_from=age, values_from = WA) %>% dplyr::select(-Year)
   mx <- data %>% dplyr::select("Year", "age", "mx") %>% pivot_wider(names_from=age, values_from = mx) %>% dplyr::select(-Year) %>% as.data.frame()
+  # For the years of mx without SSB info to inform them
+  if(minage >0 ) 
+  {
+    mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
+    names(mx) <- names(mx.fill)
+   # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
+    mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
+  }
+  source("D:/Github/ICM/Scripts/functions/backwards_sim.R")
 
-  tst <- icm.sim(years = years,
+  tst <- icm.sim(years,
                  mat.age = age.mat,
@@
                  ages = minage:maxage,
-                 rems = rem,
+                 rems = rem$rem,
                  fecund = mx,
@@
                  pop.model = 'exponential',
-                 n.sims = 500,
+                 n.sims = 5,
                  sd.mat = 0.5,
@@
   # Here get the Upper and lower 50% quantiles to make a functional boxplot
-  quants <- did.it.work %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
+  quants <- did.it.work %>% dplyr::filter(sim != "VPA") %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
                                                                         med = median(abund),
@@
           #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') +
+          theme_few() + theme(legend.position = 'none') + #geom_vline()
           ggtitle(i)+
@@
           xlab("") +
-          ylab("Estimated growth rate (r)") +
+          ylab("Lotka r") +
           #scale_y_continuous(breaks = seq(0,1.5,by=0.1)) +
@@
 
-  print(p2)
-  print(p3)
-  print(p4)
+  #print(p2)
+  #print(p3)
+  #print(p4)
 

### 2023-03-15 Scripts/functions/backwards_sim.r

@@ -61,6 +61,9 @@ icm.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
     file.remove(paste0(getwd(),"/",basename(fun)))
   }
   
+  source("D:/Github/ICM/Scripts/functions/Lotka_r.r")
+  
+  
   require(optimx)  || stop("Please load the 'optimx' package which you'll need for the optimations to run")
   
   #Initialize a bunch of objects
@@ -93,10 +96,10 @@ icm.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
                     sd.mat = sd.mat,sd.nm = sd.nm,sd.wt = sd.wt,sd.fecund = sd.fecund)   
       #browser()
     }
-    
+    #browser()
     tmp <-junk$res[,2] 
     if(length(tmp) == 1) tmp <- rep(tmp,n.years)
-    r.vec[[i]] <- data.frame(r = tmp,years = years[-1],n.sims=i)
+    r.vec[[i]] <- data.frame(r = tmp,years = years[],n.sims=i)
 
   }
   #unwrap your r vector
@@ -117,11 +120,12 @@ icm.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
     # if you use the logistic growth model the K estimated for the population.
     for(y in n.years:2)
     {
-      
+      #browser()
       # DK Note: So for our removals time series, we put the removals between t+1 and t 
       # down as year t+1.  We can change this, but that's how this is set up at the moment.
       removals.next <- rems[y-1]
-      r.up <- r.tmp$r[y-1] # This is only a vector of 58 so gotta reduce index by 1.
+      #browser()
+      r.up <- r.tmp$r[y] # This vector is one less than the data
       # The exponential model
       if(pop.model == 'exponential') 
       {

### 2023-03-17 Scripts/ASR_stocks.Rmd
Mostly a tuning script update
Have the 'tuning' simulations working, this backup will include some initial testing of that.

@@
 
-```{r, echo=F, message=F, warning=F, fig.width=6, fig.height=4}
+```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
 # OK, so using the ICES assessments here's what we get for North Sea cod.
@@
 library(ggthemes)
+library(cowplot)
 
@@
 
-# summary plots for ALL stocks
-for (i in unique(ASR_long$Stock)) {
-  ASR_sub <- ASR_long %>%
-    dplyr::select(Year, Stock, type, age, value) %>%
-    dplyr::filter(Stock==i)
-  maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]),na.rm=T)
-  maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
-  minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
-  forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
-  forplot <- forplot[!is.na(forplot$value),] # remove the NAs, hopefully this works for all the stocks...
-  p1 <- ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
-        geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
-        theme_bw() + 
-        ggtitle(i) +
-    guides(x =  guide_axis(angle = 90)) 
-  print(p1)
-
-  if(!dir.exists(paste0("D:/Github/ICM/Figures/", i))) dir.create(paste0("D:/Github/ICM/Figures/", i))
-
-  png(filename=paste0("D:/Github/ICM/Figures/", i, "/data_summary_", i, ".png"), height=4, width=12, res=400, units="in")
-  print(p1)
-  dev.off()
-}
+# summary plots for ALL stocks, this is already run, so lets not keep running it
+# for (i in unique(ASR_long$Stock)) {
+#   ASR_sub <- ASR_long %>%
+#     dplyr::select(Year, Stock, type, age, value) %>%
+#     dplyr::filter(Stock==i)
+#   maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]),na.rm=T)
+#   maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
+#   minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
+#   forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
+#   forplot <- forplot[!is.na(forplot$value),] # remove the NAs, hopefully this works for all the stocks...
+#   p1 <- ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
+#         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
+#         theme_bw() + 
+#         ggtitle(i) +
+#     guides(x =  guide_axis(angle = 90)) 
+#   print(p1)
+#   
+#   if(!dir.exists(paste0("D:/Github/ICM/Figures/", i))) dir.create(paste0("D:/Github/ICM/Figures/", i))
+#   
+#   png(filename=paste0("D:/Github/ICM/Figures/", i, "/data_summary_", i, ".png"), height=4, width=12, res=400, units="in")
+#   print(p1)
+#   dev.off()
+# }
 
@@
 #Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
-# Bring in the data
-# Handy import function from the rio package... tricky part was getting the right filename here...
-for(i in Stocks){
+
+back.res <- NULL
+back.ts <- NULL
+back.ts.quants <- NULL
+tuned.res <- NULL
+for(i in Stocks)
+{
   print(i)
@@
   years <- data %>% dplyr::pull(Year) %>% unique() %>% sort()
+
   N.end <- sum(data[data$Year==max(years),]$Num)
@@
   mx <- data %>% dplyr::select("Year", "age", "mx") %>% pivot_wider(names_from=age, values_from = mx) %>% dplyr::select(-Year) %>% as.data.frame()
+
+  # Dealing with some annoying NAs...
+  if(i == "AFSC_BSAI-Males_Pleuronectes_quadrituberculatus")
+  {
+    age.mat[length(years),] <- age.mat[length(years)-1,]
+    prop.nat.mort[length(years),] <- prop.nat.mort[length(years)-1,]
+    weight.age[length(years),] <- weight.age[length(years)-1,]
+    mx[length(years),13:23] <- mx[length(years),12]
+  }
+
+  if(i == "DFO_2J3KL_Gadus_morhua")
+  {
+    age.mat[,8:10] <- 1
+    prop.nat.mort[,8:10] <- prop.nat.mort[,7]
+    weight.age[12:14,9:10] <- weight.age[12:14,8]
+    weight.age[15,10] <- weight.age[15,9]
+    mx[12:16,9:10] <- mx[12:16,8]
+    mx[17,10] <- mx[17,9]
+  }
+
+  if(i == "DFO_4T-Spring_Clupea_harengus")
+  {
+    age.mat[6:7,10] <- 1
+    prop.nat.mort[6:7,10] <- prop.nat.mort[6:7,9]
+    weight.age[6:7,10] <- weight.age[6:7,9]
+    mx[6:9,10] <- mx[6:9,9]
+  }
+
+  if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
+  {
+    age.mat[30,8] <- 1
+    prop.nat.mort[30,8] <- prop.nat.mort[30,7]
+    weight.age[30,8] <- weight.age[29,8]
+    mx[30:31,8] <- mx[30:31,9]
+  }
+
+  if(i == "ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax")
+  {
+    age.mat[c(14,27,40),5] <- age.mat[1,5]
+    prop.nat.mort[c(14,27,40),5] <- prop.nat.mort[1,5]
+    weight.age[c(14,27,40),5] <- weight.age[c(13,26,39),5]
+    mx[c(14,16,27,29,40,42),5] <- mx[c(14,16,27,29,40,42),6]
+  }
+
   # For the years of mx without SSB info to inform them
@@
   }
+
   source("D:/Github/ICM/Scripts/functions/backwards_sim.R")
@@
                  pop.model = 'exponential',
-                 n.sims = 5,
+                 n.sims = 500,
                  sd.mat = 0.5,
@@
                                                                         U.50 = quantile(abund,probs=c(0.75)))
+
+  back.res[[i]] <- tst
+  back.ts[[i]] <- did.it.work
+  back.ts.quants[[i]] <- quants
 
@@
           geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
+  save_plot(plot = p2, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/runs_vs_vpa_", i, ".png"), base_width = 6,base_height = 4)
   # Same thing but functional boxplots
@@
           geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
+  save_plot(plot = p3, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/runs_vs_vpa_ribbon_", i, ".png"), base_width = 6,base_height = 4)
+
   # Plotting how the estimate of r changes over time (which you can do when we have time varying inputs (e.g. Wgt, M, or maturity at age)
@@
           ggtitle(i)
+  save_plot(plot = p4, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/lokta_r_", i, ".png"), base_width = 6,base_height = 4)
 
-  #print(p2)
-  #print(p3)
-  #print(p4)
+# Now run the tuning sims
 
-  png(filename=paste0("D:/Github/ICM/Figures/", i, "/runs_vs_vpa_", i, ".png"), height=4, width=6, res=400, units="in")
-  print(p2)
-  dev.off()
-  png(filename=paste0("D:/Github/ICM/Figures/", i, "/runs_vs_vpa_ribbon_", i, ".png"), height=4, width=6, res=400, units="in")
-  print(p3)
-  dev.off()
-  png(filename=paste0("D:/Github/ICM/Figures/", i, "/growth_", i, ".png"), height=4, width=6, res=400, units="in")
-  print(p4)
-  dev.off()
+  nm = prop.nat.mort
+
+  source("D:/Github/ICM/Scripts/functions/tuning_sim.R")
+  N.end <- vpa.abund[length(vpa.abund)]
+  tunes <- tune.sim(years,
+                    n.steps = 100,
+                    abund.ts = vpa.abund,
+                    mat.age = age.mat,
+                    nm = prop.nat.mort,
+                    w.age = weight.age,
+                    ages = minage:maxage,
+                    rems = rem$rem,
+                    fecund = mx,
+                    N.end = N.end,
+                    pop.model = 'exponential')
+
+  tuned.res[[i]] <- tunes
+
+  # Comparing our new time series with the old
+  p2 <- ggplot() +
+          geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
+          geom_line(data=tunes$res, aes(x=year,y=vpa.n),color='black') +
+          xlab("") +
+          ylab("Abundance (1000s)") +
+          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
+          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
+          theme_few() + theme(legend.position = 'none') +
+          ggtitle(i) #+
+          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
+  save_plot(plot = p2, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/tunded_vs_vpa_", i, ".png"), base_width = 6,base_height = 4)
+
+  # Comparing the absolute miss from the tuned time series
+   p3 <- ggplot() +
+          #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
+          geom_line(data=tunes$res[-1,], aes(x=year,y=diff.n),color='red') +
+          xlab("") +
+          ylab("Difference in abundance (1000s)") +
+          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
+          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
+          theme_few() + theme(legend.position = 'none') + 
+          ggtitle(i) 
+          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
+  save_plot(plot = p3, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/diff_N_", i, ".png"), base_width = 6,base_height = 4)
+
+  # What percentage (mean) difference
+   p4 <- ggplot() +
+          #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
+          geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.n),color='red') +
+          xlab("") +
+          ylab("Difference in abundance (%)") +
+          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
+          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
+          theme_few() + theme(legend.position = 'none') + 
+          ggtitle(i) #+ ylim(c(-100,100))
+          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
+  save_plot(plot = p4, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/per_diff_N_", i, ".png"), base_width = 6,base_height = 4)
+
+     # Difference in m's
+   p5 <- ggplot() +
+          geom_line(data=tunes$res[-1,], aes(x=year,y=diff.m),color='red') +
+          xlab("") +
+          ylab("Difference in natural mortality (Proportional)") +
+          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
+          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
+          theme_few() + theme(legend.position = 'none') + 
+          ggtitle(i) #+ ylim(c(-100,100))
+          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
+  save_plot(plot = p5, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/diff_m_", i, ".png"), base_width = 6,base_height = 4)
+     # % Difference in m's
+   p6 <- ggplot() +
+          geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.m),color='red') +
+          xlab("") +
+          ylab("Difference in natural mortality (%)") +
+          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
+          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
+          theme_few() + theme(legend.position = 'none') + 
+          ggtitle(i) #+ ylim(c(-100,100))
+          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
+  save_plot(plot = p6, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/per_diff_m_", i, ".png"), base_width = 6,base_height = 4)
+
+   p7 <- ggplot() +
+          geom_line(data=tunes$res[-1,], aes(x=year,y=mn.m),color='blue') +
+          geom_line(data=tunes$res[-1,], aes(x=year,y=vpa.m),color='black') +
+          xlab("") +
+          ylab("Natural mortality (Proportional)") +
+          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
+          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
+          theme_few() + theme(legend.position = 'none') +
+          ggtitle(i) #+
+          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
+  save_plot(plot = p7, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/Nat_M_", i, ".png"), base_width = 6,base_height = 4)
+
+     p8 <- ggplot() +
+          geom_line(data=tunes$res[-1,], aes(x=year,y=r),color='blue') +
+          xlab("") +
+          ylab("Lotka r") +
+          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
+          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
+          theme_few() + theme(legend.position = 'none') +
+          ggtitle(i) #+
+          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
+  save_plot(plot = p8, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/Lotka_r_", i, ".png"), base_width = 6,base_height = 4)
+
 }
+saveRDS(object = tuned.res,file = "D:/Github/ICM/Results/tuned_fits.Rds")
+saveRDS(object = back.res,file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
+saveRDS(object = back.ts,file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
+saveRDS(object = back.ts.quants,file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
 ```
+
+```{r, forward-sims-n-figs,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
+```

### 2023-03-17 Scripts/functions/backwards_sim.r

@@ -3,8 +3,6 @@
 # All the data you need to make it dance...
 # years:          The years you are running the backwards calculation for
 # n.sims:         The number of simulations you are running
-# fwd.n.years:    Number of years forward you want to run the simulation
-
 # mat.age         Age at maturity if one value it is the age at 50% maturity, if a vector it is the age at maturities for each age(or age/year), if a matrix we want this to be unique for each simulation
 #                 we could also let this vary by year, but we'll need to go 3-D array or something for that# ages:           What are the ages you are using this is used to calculate max age, which may not be ideal with plus group stocks.
 
@@ -125,7 +123,7 @@ icm.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
       # down as year t+1.  We can change this, but that's how this is set up at the moment.
       removals.next <- rems[y-1]
       #browser()
-      r.up <- r.tmp$r[y] # This vector is one less than the data
+      r.up <- r.tmp$r[y] # 
       # The exponential model
       if(pop.model == 'exponential') 
       {

### 2023-03-17 Scripts/functions/tuning_sim.r

@@ -1,0 +1,223 @@
+# Here we take the ideas from the backwards projections but 'tune' them to the 'known' biomass by adjusting either the fecundity or survivorship variables iteratively until
+# the biomass in the current year is withing X% of the actual biomass.
+
+# All the data you need to make it dance...
+# years:          The years you are running the backwards calculation for
+# abund.ts:       The abundance time series from the assessment
+# tune.par:       How close to the assessment biomass do we want to get.  default is 0.01 (1%)
+# tuner:          What are we tuning, the fecundity "f", or natural mortality 'm', or both 'b'
+# rems            Removals from the fishery in a given year.
+# n.steps         The number of different m or f options to explore.  Make sure this is an even number!
+
+# mat.age         Age at maturity if one value it is the age at 50% maturity, if a vector it is the age at maturities for each age(or age/year), if a matrix we want this to be unique for each simulation
+#                 we could also let this vary by year, but we'll need to go 3-D array or something for that# ages:           What are the ages you are using this is used to calculate max age, which may not be ideal with plus group stocks.
+
+# nm:             Natural mortality, this wants the instantaneous natural mortality, not the proportional. There are several options here....
+#                 You can enter a vector of instantaneous natural moralities, just put a single number of all ages, or put in a character
+#                 string that will tell the function to calculate the natural mortality based on life history data. If a matrix the rows are different simulations
+#                 we could also let this vary by year, but we'll need to go 3-D array or something for that
+
+# sel             The selectivity of the stock.  Currently this is set up as a single number and it is tweaked in the code, we'll need to make this more complex.
+
+
+# N               Population size in a given year
+
+# u:              Exploitation rate (annual not instantaneous), currently set up to be 1 value.
+
[…]

### 2023-04-05 Drafts/Presentations/test.Rmd

---
title: "Untitled"
author: "David Keith"
date: '2022-09-06'
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

### 2023-04-05 Scripts/ASR_stocks.Rmd

@@
 
-```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
+```{r, load-stuff,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
 # OK, so using the ICES assessments here's what we get for North Sea cod.
@@
 
-# # OK, lets give this a spin...
-# funs <- c("https://raw.githubusercontent.com/Dave-Keith/ICM/main/Scripts/functions/backwards_sim.r")
-# # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
-# for(fun in funs) 
-# {
-#   download.file(fun,destfile = basename(fun))
-#   source(paste0(getwd(),"/",basename(fun)))
-#   file.remove(paste0(getwd(),"/",basename(fun)))
-# }
-
 source("D:/Github/ICM/Scripts/functions/backwards_sim.R")
+source("D:/Github/ICM/Scripts/functions/tuning_sim.R")
 
@@
 ASR <- read.csv("D:/Github/ICM/Data/ICM_data_NW_atlantic_stocks.csv")
+
 ASR <- rbind(ASR1,ASR)
@@
 ASR_trim <- cbind(ASRsp, ASRdat)
-
 # need a unique ID for stock
@@
 
-# summary plots for ALL stocks, this is already run, so lets not keep running it
-# for (i in unique(ASR_long$Stock)) {
-#   ASR_sub <- ASR_long %>%
-#     dplyr::select(Year, Stock, type, age, value) %>%
-#     dplyr::filter(Stock==i)
-#   maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]),na.rm=T)
-#   maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
-#   minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
-#   forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
-#   forplot <- forplot[!is.na(forplot$value),] # remove the NAs, hopefully this works for all the stocks...
-#   p1 <- ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
-#         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
-#         theme_bw() + 
-#         ggtitle(i) +
-#     guides(x =  guide_axis(angle = 90)) 
-#   print(p1)
-#   
-#   if(!dir.exists(paste0("D:/Github/ICM/Figures/", i))) dir.create(paste0("D:/Github/ICM/Figures/", i))
-#   
-#   png(filename=paste0("D:/Github/ICM/Figures/", i, "/data_summary_", i, ".png"), height=4, width=12, res=400, units="in")
-#   print(p1)
-#   dev.off()
-# }
+```
+
+```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
 
@@
 Stocks <- Stocks$Stock
+
 # Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
@@
 
-back.res <- NULL
-back.ts <- NULL
-back.ts.quants <- NULL
-tuned.res <- NULL
+years.tmp <- NULL
+pnm.tmp <- NULL
+waa.tmp <- NULL
+ages.tmp <- NULL
+rem.tmp <- NULL
+mx.tmp <- NULL
+NE.tmp <- NULL
+vpa.tmp <- NULL
+am.tmp <- NULL
+mr.tmp <- NULL
 for(i in Stocks)
@@
   }
+  years.tmp[[i]] <- years
+  pnm.tmp[[i]] <- prop.nat.mort
+  waa.tmp[[i]] <- weight.age
+  ages.tmp[[i]] <- minage:maxage
+  rem.tmp[[i]] <- rem
+  mx.tmp[[i]] <- mx
+  NE.tmp[[i]] <- N.end
+  vpa.tmp[[i]] <- vpa.abund
+  am.tmp[[i]] <- age.mat
+  mr.tmp[[i]] <- missing_rem
+} #end input data loop
 
-  source("D:/Github/ICM/Scripts/functions/backwards_sim.R")
+save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,am.tmp,Stocks,ASR_stocks,ASR_long,file = "D:/Github/ICM/Results/model_inputs.Rdata")
+
+```
+
+```{r, run-mods,echo=F, message=F, warning=F}
+
+load(file = "D:/Github/ICM/Results/model_inputs.Rdata")
+
+back.res <- NULL
+back.ts <- NULL
+back.ts.quants <- NULL
+tuned.res <- NULL
+for(i in Stocks)
+{
+  years <- years.tmp[[i]]
+  prop.nat.mort <- pnm.tmp[[i]] 
+  weight.age <- waa.tmp[[i]] 
+  ages <- ages.tmp[[i]] 
+  rem <- rem.tmp[[i]] 
+  mx <- mx.tmp[[i]] 
+  N.end <- NE.tmp[[i]] 
+  vpa.abund <- vpa.tmp[[i]] 
+  age.mat <- am.tmp[[i]]
 
@@
                  w.age = weight.age,
-                 ages = minage:maxage,
+                 ages = ages,
                  rems = rem$rem,
@@
   back.ts.quants[[i]] <- quants
+
+# Now run the tuning sims
+
+  N.end <- vpa.abund[length(vpa.abund)]
+  tunes <- tune.sim(years,
+                    n.steps = 100,
+                    abund.ts = vpa.abund,
+                    mat.age = age.mat,
+                    nm = prop.nat.mort,
+                    w.age = weight.age,
+                    ages = ages,
+                    rems = rem$rem,
+                    fecund = mx,
+                    N.end = N.end,
+                    pop.model = 'exponential')
+
+  tuned.res[[i]] <- tunes
+} # end i in Stocks look
+# Save all these
+saveRDS(object = tuned.res,file = "D:/Github/ICM/Results/tuned_fits.Rds")
+saveRDS(object = back.res,file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
+saveRDS(object = back.ts,file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
+saveRDS(object = back.ts.quants,file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
+```
+
+```{r, make-figs,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
+
+# Now we can run the figures separately.
+tuned.res <- readRDS(file = "D:/Github/ICM/Results/tuned_fits.Rds")
+back.ts <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
+back.ts.quants <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
+back.res <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
+load(file = "D:/Github/ICM/Results/model_inputs.Rdata")
+
+for(i in Stocks)
+{
+  # Unpack the lists
+  tunes <- tuned.res[[i]] 
+  did.it.work <- back.ts[[i]] 
+  quants <- back.ts.quants[[i]] 
+  missing_rem <- mr.tmp[[i]] 
+  tst <- back.res[[i]]
 
@@
   save_plot(plot = p4, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/lokta_r_", i, ".png"), base_width = 6,base_height = 4)
-
-# Now run the tuning sims
-
-  nm = prop.nat.mort
-
-  source("D:/Github/ICM/Scripts/functions/tuning_sim.R")
-  N.end <- vpa.abund[length(vpa.abund)]
-  tunes <- tune.sim(years,
-                    n.steps = 100,
-                    abund.ts = vpa.abund,
-                    mat.age = age.mat,
-                    nm = prop.nat.mort,
-                    w.age = weight.age,
-                    ages = minage:maxage,
-                    rems = rem$rem,
-                    fecund = mx,
-                    N.end = N.end,
-                    pop.model = 'exponential')
-
-  tuned.res[[i]] <- tunes
 
@@
           xlab("") +
-          ylab("Difference in natural mortality (Proportional)") +
+          ylab("Difference in natural mortality (Instantaneous)") +
           #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
@@
           xlab("") +
-          ylab("Natural mortality (Proportional)") +
+          ylab("Natural mortality (Instantaneous)") +
           #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
@@
 }
-saveRDS(object = tuned.res,file = "D:/Github/ICM/Results/tuned_fits.Rds")
-saveRDS(object = back.res,file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
-saveRDS(object = back.ts,file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
-saveRDS(object = back.ts.quants,file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
+
+# summary plots for ALL stocks, this is already run, so lets not keep running it
+# for (i in unique(ASR_long$Stock)) {
+#   ASR_sub <- ASR_long %>%
+#     dplyr::select(Year, Stock, type, age, value) %>%
+#     dplyr::filter(Stock==i)
+#   maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]),na.rm=T)
+#   maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
+#   minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
+#   forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
+#   forplot <- forplot[!is.na(forplot$value),] # remove the NAs, hopefully this works for all the stocks...
+#   p1 <- ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
+#         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
+#         theme_bw() + 
+#         ggtitle(i) +
+#     guides(x =  guide_axis(angle = 90)) 
+#   print(p1)
+#   
+#   if(!dir.exists(paste0("D:/Github/ICM/Figures/", i))) dir.create(paste0("D:/Github/ICM/Figures/", i))
+#   
+#   png(filename=paste0("D:/Github/ICM/Figures/", i, "/data_summary_", i, ".png"), height=4, width=12, res=400, units="in")
+#   print(p1)
+#   dev.off()
+# }
+
 ```

### 2023-04-21 Scripts/ASR_stocks.Rmd
Got forward working
Now moving to multi-species model

@@
 back.ts.quants <- NULL
+for.res <- NULL
+for.ts <- NULL
+for.ts.quants <- NULL
 tuned.res <- NULL
@@
 
-  tst <- icm.sim(years,
+  tst <- back.sim(years,
                  mat.age = age.mat,
@@
                  pop.model = 'exponential',
-                 n.sims = 500,
+                 n.sims = 2,
                  sd.mat = 0.5,
@@
 
-# Now run the tuning sims
+################# Now run as a forward simulation
+  N.start <- vpa.abund[1]
+
+  tst <- for.sim(years,
+                 mat.age = age.mat,
+                 nm = prop.nat.mort,
+                 w.age = weight.age,
+                 ages = ages,
+                 rems = rem$rem, # rep(0,nrow(rem)),
+                 fecund = mx,
+                 N.start = N.start,
+                 pop.model = 'exponential', K = 2e6,
+                 n.sims = 2,
+                 sd.mat = 0.5,
+                 sd.nm = 0.5,
+                 sd.wt = 0.5,
+                 sd.fecund = 0.5)
+
+  #Combine the data
+  did.it.work <- data.frame(abund = c(vpa.abund,tst$Pop$abund),years = c(years,tst$Pop$years),sim = c(rep('VPA',length(years)),tst$Pop$sim))
+  # Here get the Upper and lower 50% quantiles to make a functional boxplot
+  quants <- did.it.work %>% dplyr::filter(sim != "VPA") %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
+                                                                        med = median(abund),
+                                                                        U.50 = quantile(abund,probs=c(0.75)))
+
+  for.res[[i]] <- tst
+  for.ts[[i]] <- did.it.work
+  for.ts.quants[[i]] <- quants
+
+ggplot(quants) + geom_line(aes(x=years,y=med))
+
+########################## Now run the tuning sims
 
@@
 } # end i in Stocks look
+
 # Save all these
-saveRDS(object = tuned.res,file = "D:/Github/ICM/Results/tuned_fits.Rds")
-saveRDS(object = back.res,file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
-saveRDS(object = back.ts,file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
-saveRDS(object = back.ts.quants,file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
+# saveRDS(object = tuned.res,file = "D:/Github/ICM/Results/tuned_fits.Rds")
+# saveRDS(object = back.res,file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
+# saveRDS(object = back.ts,file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
+# saveRDS(object = back.ts.quants,file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
 ```
@@
 ```{r, forward-sims-n-figs,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
+# Now we have to forward project the stocks, I think it makes the most sense to do this using the tuned data at the moment
+# So we assume the fecundity data and the tuned natural mortality data for the stocks is a reasonable representation of the future
+load(file = "D:/Github/ICM/Results/model_inputs.Rdata")
+
+back.res <- NULL
+back.ts <- NULL
+back.ts.quants <- NULL
+for.res <- NULL
+for.ts <- NULL
+for.ts.quants <- NULL
+tuned.res <- NULL
+for(i in Stocks)
+{
+  years <- years.tmp[[i]]
+  prop.nat.mort <- pnm.tmp[[i]] 
+  weight.age <- waa.tmp[[i]] 
+  ages <- ages.tmp[[i]] 
+  rem <- rem.tmp[[i]] 
+  mx <- mx.tmp[[i]] 
+  N.end <- NE.tmp[[i]] 
+  vpa.abund <- vpa.tmp[[i]] 
+  age.mat <- am.tmp[[i]]
+
+################# Now run as a forward simulation
+  N.start <- vpa.abund[length(vpa.abund)] 
+  years <- 2025:2075
+  # For the forward simulations I'm setting it up so we feed in the mean vector or a character, we'll then create a vector of mx's with variablitity
+  st.time <- Sys.time()
+  tst <- for.sim(years,
+                 mat.age = age.mat,
+                 nm = prop.nat.mort,
+                 w.age = weight.age,
+                 ages = ages,
+                 rems = c(0.1,0.2), # This is set up as a fishing mortality that averages 0.1 with an sd of 0.2)
+                 fecund = mx,
+                 N.start = N.start,
+                 pop.model = 'exponential', sim = 'project', proj.sim = 'sample',
+                 n.sims = 30,
+                 sd.mat = 0.1,
+                 sd.nm = 0.1,
+                 sd.wt = 0.1,
+                 sd.fecund = 0.1)
+  Sys.time() - st.time
+  #Combine the data
+  did.it.work <- data.frame(abund = tst$Pop$abund,years = c(tst$Pop$years),sim = tst$Pop$sim)
+  # Here get the Upper and lower 50% quantiles to make a functional boxplot
+  quants <- tst$Pop %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
+                                                                   med = median(abund),
+                                                                   U.50 = quantile(abund,probs=c(0.75)))
+
+  for.res[[i]] <- tst
+  for.ts[[i]] <- tst$Pop
+  for.ts.quants[[i]] <- quants
+
+ggplot(quants) + geom_line(aes(x=years,y=med))  + geom_ribbon(aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue')
+
 ```

### 2023-04-21 Scripts/functions/Lotka_r.r

@@ -8,11 +8,14 @@
 #              string that will tell the function to calculate the natural mortality based on life history data.
 # ages:        What are the ages you are using 
 # fecund:      How are you estimating 
-# wt.at.age:  The weight of individuals for each age
-#mat.ogive.K  Only used if you provide just the age at 50% maturity.  Default is -50 which is effectively a knife edge maturation, as you approach 0 this becomes more smooth.
+# wt.at.age:   The weight of individuals for each age
+#mat.ogive.K   Only used if you provide just the age at 50% maturity.  Default is -50 which is effectively a knife edge maturation, as you approach 0 this becomes more smooth.
+# sim          Are we doing a retrospective analysis or a forward projection.  default = 'retro', set sim = 'project' for forward projections
+# proj.sim     How do you want to get your samples if you are doing the forward projection. You can 'sample' from the past directly 
+#              or use past data and add uncertainty through a lognormal distribution based on the historic data using proj.sim = 'dist'
 
 lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL,fecund = NULL,
-                  mat.ogive.K = -50,
+                  mat.ogive.K = -50, sim = 'project',proj.sim = 'dist',
                   L.inf = NULL,K = NULL,t0 = NULL, a.len.wgt = NULL, b.len.wgt = NULL, a.fec.len = NULL, b.fec.len = NULL,
                   sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0
                   # The above are needed if 1) no weight at age data (L.inf,K, t0, a.len.wgt, b.len.wgt) 
@@ -45,10 +48,14 @@ lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL
   
   # The Euler-Lotka Function to optimize on to find the intrinsic rate of growth for your population
   eulerlotka <- function(r) (sum(lx * mx * exp(-r * ages)) - 1)^2
-  
   # Set up a dataframe
   res <- data.frame(yrs = NA, r = NA)
   if(length(yrs) > 1) n.yrs <- length(yrs) else n.yrs <- 2 # Needs to be 2 if just doing it for one year to work how I have loop set up
+  
+  
+  if(sim == 'retro')
+  {
+  
   # Get the maximum age
[…]

### 2023-04-21 Scripts/functions/backwards_project.r

@@ -21,10 +21,12 @@ back.proj <- function(option = "exponential",pop.next,r,removals.next,K,fishery.
   {
     if(fishery.timing == 'beginning')
     {
-    Pop.current <- (pop.next)/(exp(r))
+    # Going to 1+r model since we are discrete time...
+    #Pop.current <- (pop.next)/(exp(r))
+    Pop.current <- (pop.next)/(1+r)
     Pop.current<- Pop.current+removals.next 
     }
-    if(fishery.timing =='end') Pop.current <- (pop.next+removals.next)/(exp(r))
+    if(fishery.timing =='end') Pop.current <- (pop.next+removals.next)/((1+r)) #  (pop.next+removals.next)/(exp(r))
   }
   # Logistic growth model, 
   # The maths be.... N(t+1) = N(t) + rN(t)(1-N(t)/K).... now we are solving for N(t) not N(t+1), so we rearrange terms
@@ -39,7 +41,11 @@ back.proj <- function(option = "exponential",pop.next,r,removals.next,K,fishery.
     if(fishery.timing == 'beginning') par <- pop.next
     if(fishery.timing == 'end') par <- pop.next <- pop.next + removals.next
     # Ha, we can use this to solve for N in the previous year
-    logistic.n.last <- function(N.last) sum((exp(r)* ((N.last)/(1-(N.last/K))) / (1 + ( ((N.last)/(1-(N.last/K)))*exp(r))/K) - pop.next))^2
+    #I'm hung up on which of these to use, they give almost the same answer, but not quite, but going with the 1+r version since
+    # we are in discrete time here.
+    #logistic.n.last <- function(N.last) sum((exp(r)* ((N.last)/(1-(N.last/K))) / (1 + ( ((N.last)/(1-(N.last/K)))*exp(r))/K) - pop.next))^2
+    logistic.n.last <- function(N.last) sum(((1+r)* ((N.last)/(1-(N.last/K))) / (1 + ( ((N.last)/(1-(N.last/K)))*(1+r))/K) - pop.next))^2
+    
     # Solve the above function
     Pop.current <- optimx(par, logistic.n.last, method = "BFGS")$p1
     # If the fishery removes individuals at the start of the time series add them in here.

### 2023-04-21 Scripts/functions/forward_project.r

@@ -1,0 +1,45 @@
+# The analogue of the backword projection function.... but to forward project
+
+# Arguments
+#option:         So far we can do exponential or logistic growth, other options are on the table if someone has a good one
+#pop.last:       The population size in year t-1, which is used to estimate the size of the population in year t
+#r:              The intrinsic rate of growth for the population
+#removals:       The removals between t+1 and t
+#K:              The carrying capacity, only necessary for logistic model
+#fishery.timing: When do you want the removals by the fishery to occur, at the 'beginning' of the year, or at the end of the year.  
+#                   At the 'beginning' excludes them from the population dynamics, at the 'end' includes them in the population dynamics (because we are going backwards).
+ 
+for.proj <- function(option = "exponential",pop.last,r,removals.next,K,fishery.timing = 'beginning')
+{
+
+  
+  ### So rolling with the easy peasy continuous time exponential
+  ### simple exponential population growth, in this formulation with the removals I think I'm saying the removals happen right at the outset
+  if(option == 'exponential') 
+  {
+    if(fishery.timing == 'end')
+    {
+    Pop.current <- (pop.last)*((1+r))
+    Pop.current<- Pop.current-removals.next 
+    }
+    if(fishery.timing =='beginning') Pop.current <- (pop.last-removals.next)*((1+r))
+  }
+  # Logistic growth model, 
+  # The maths be.... N(t+1) = N(t) + rN(t)(1-N(t)/K).... now we are solving for N(t) not N(t+1), so we rearrange terms
+  # to get it in the quadratic formula....  (r/K)N^2 -(1+r)N  + N(t+1) = 0... we have r, K, and N(t+1) so we can solve for N(t)
+  # But #1, this is the discrete time version, and that's not useful
+  # But thanks to my longtime biological math hero Sarah Otto and her book on Mathematical modelling
+  # This will solve the backwards logistic and is easy peasy to use for forwards logistic
+  # Hurray for math!
+  if(option == "logistic")
+  {
+    # Get our parameter for the logistic model
+    if(fishery.timing == 'end') par <- pop.last
+    if(fishery.timing == 'beginning') par <- pop.last <- pop.last - removals.next
+    # Get the current population size using logistic model
+    Pop.current <-  pop.last + (r* pop.last)*(1-(pop.last/K)) 
+    # If the fishery removes individuals at the start of the time series add them in here.
+    if(fishery.timing == 'end') Pop.current <- Pop.current - removals.next
+  }
+  return(list(Pop.current = Pop.current))
+}

### 2023-04-21 Scripts/functions/forward_sim.r

@@ -1,4 +1,4 @@
-# The backwards simulation part of the ICM.sim function which we need for the first part of this work to see how well the model does at backwards projections of the stock
+# here we project forward, should be fairly straightforward tweak of the backward simulation function
 
 # All the data you need to make it dance...
 # years:          The years you are running the backwards calculation for
@@ -13,14 +13,14 @@
 
 # sel             The selectivity of the stock.  Currently this is set up as a single number and it is tweaked in the code, we'll need to make this more complex.
 
-# rems        Removals from the fishery in a given year.
+# rems            Projected removals.  Currently this is set up so that you provide the mean and sd of fishing mortality for the forward projections.  Will need to generalize this.
 
 # N               Population size in a given year
 
 # u:              Exploitation rate (annual not instantaneous), currently set up to be 1 value.
 
 # pop.model:      What method you going to use to get the population growth modeled for the backwards model.  You can use exponential model, logistic model, 
-                  #or a dec.rate (decline rate) model.
+#or a dec.rate (decline rate) model.
 
 # What we need for the Lotka.r function...
 # fecund:      How are you estimating fecundity. If a vector it is the number of recruits produced by the average individual in the age classes. 
@@ -39,10 +39,11 @@
 #                 we could also let this vary by year, but we'll need to go 3-D array or something for that
 # K
 # dec.rate
+# sim
+# proj.sim
 
-
-back.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,fecund = NULL,N.end = NULL,
-                  sel,rems,N,u,pop.model = "exp", direction = 'back',
+for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,fecund = NULL,N.start = NULL,
+                  sel,rems = c(0.1,0.2),N,u,pop.model = "exponential", sim = 'retro', proj.sim='dist',
                   dec.rate = NULL,
[…]

### 2023-04-21 Scripts/functions/north_sea_multi_stock_model.r

@@ -1,0 +1,3 @@
+# OK, here's I'm going to try and develop a multi=species projection model for the North Sea, we have 10 stocks with good data, the retro fits aren't perfect
+# But they mostly aren't a disaster either.  All have a reasonable length of time series as well.
+

### 2023-04-21 Scripts/functions/tuning_sim.r

@@ -86,7 +86,7 @@ tune.sim<-function(years,tune.par=0.01,tuner="m", n.steps = 30,
     nm.lst <- NULL
     for(y in 1:n.years)
     {
-      # let's just make 15 steps around the mean either way, changing m by 5% every time....
+      # let's just make X steps around the mean either way, changing m by 5% every time....
       nm.vary <- NULL
       count <- 0
       for(s in (n.steps/2):1) 
@@ -181,7 +181,6 @@ tune.sim<-function(years,tune.par=0.01,tuner="m", n.steps = 30,
         r.vec$lotka.n[r.vec$s == ss & r.vec$year == years[y]] <- pop.next[ss]
         r.vec$diff.n[r.vec$s == ss & r.vec$year == years[y]] <- pop.next[ss] - abund.ts[y-1]
         r.vec$per.diff.n[r.vec$s == ss & r.vec$year == years[y]] <- 100*((pop.next[ss] - abund.ts[y-1])/abund.ts[y-1])
-        
         # Then we find the minimum and that becomes or model of choice and we've retained the summary of the natural mortality from that simulation
         
       }
@@ -198,24 +197,7 @@ tune.sim<-function(years,tune.par=0.01,tuner="m", n.steps = 30,
     res.final <- do.call('rbind',res)
     res.final$diff.m <- res.final$mn.m - res.final$vpa.m
     res.final$per.diff.m <- 100*((res.final$mn.m - res.final$vpa.m)/res.final$vpa.m)
-    #browser()
-    #Pop$abund[Pop$sim == i]<-Pop.vec
-    
-    ### calc removals (increase due to r plus amount population declined by):   
-    # removals[i,]<-Pop.vec-(Pop.vec/exp(r.vec[i]))+(Pop.vec*(decl.rate[i])) WRONG
-    
-    ## removals in final year of population decline to calculate forward exploitation rate   
-    #rem<- removals[n.years]
-    
-    #print(Pop.vec)
-    #B1.vec[i]<-lm(log(Pop.vec)~years)$coef[2]  ## logic check
-    
-    
-    #calculate exploitation
-    #junk<-c()
-    #for(y in 1:n.years) junk[y]<-u.calc(nat.mort.vec[i],juv.mult.vec[i],max.age.vec[i],age.mat.vec[i],sel,rem*0.7,Pop.vec[y])
-    #mean.u.vec[i]<-mean(junk) 
-  #} #end backwards projection
+
 
     return(list(res=res.final))
 }

### 2023-04-27 Scripts/ASR_stocks.Rmd
Building the north sea multi-species model
And other updates.

@@
                  pop.model = 'exponential',
-                 n.sims = 2,
+                 n.sims = 500,
                  sd.mat = 0.5,
@@
 
-################# Now run as a forward simulation
-  N.start <- vpa.abund[1]
+# ################# Now run as a forward simulation
+#   N.start <- vpa.abund[1] 
+# 
+#   tst <- for.sim(years,
+#                  mat.age = age.mat,
+#                  nm = prop.nat.mort,
+#                  w.age = weight.age,
+#                  ages = ages,
+#                  rems = rem$rem, # rep(0,nrow(rem)),
+#                  fecund = mx,
+#                  N.start = N.start,
+#                  pop.model = 'exponential', K = 2e6,
+#                  n.sims = 2,
+#                  sd.mat = 0.5,
+#                  sd.nm = 0.5,
+#                  sd.wt = 0.5,
+#                  sd.fecund = 0.5)
+# 
+#   #Combine the data
+#   did.it.work <- data.frame(abund = c(vpa.abund,tst$Pop$abund),years = c(years,tst$Pop$years),sim = c(rep('VPA',length(years)),tst$Pop$sim))
+#   # Here get the Upper and lower 50% quantiles to make a functional boxplot
+#   quants <- did.it.work %>% dplyr::filter(sim != "VPA") %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
+#                                                                         med = median(abund),
+#                                                                         U.50 = quantile(abund,probs=c(0.75)))
+# 
+#   for.res[[i]] <- tst
+#   for.ts[[i]] <- did.it.work
+#   for.ts.quants[[i]] <- quants
 
-  tst <- for.sim(years,
-                 mat.age = age.mat,
-                 nm = prop.nat.mort,
-                 w.age = weight.age,
-                 ages = ages,
-                 rems = rem$rem, # rep(0,nrow(rem)),
-                 fecund = mx,
-                 N.start = N.start,
-                 pop.model = 'exponential', K = 2e6,
-                 n.sims = 2,
-                 sd.mat = 0.5,
-                 sd.nm = 0.5,
-                 sd.wt = 0.5,
-                 sd.fecund = 0.5)
-
-  #Combine the data
-  did.it.work <- data.frame(abund = c(vpa.abund,tst$Pop$abund),years = c(years,tst$Pop$years),sim = c(rep('VPA',length(years)),tst$Pop$sim))
-  # Here get the Upper and lower 50% quantiles to make a functional boxplot
-  quants <- did.it.work %>% dplyr::filter(sim != "VPA") %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
-                                                                        med = median(abund),
-                                                                        U.50 = quantile(abund,probs=c(0.75)))
-
-  for.res[[i]] <- tst
-  for.ts[[i]] <- did.it.work
-  for.ts.quants[[i]] <- quants
-
-ggplot(quants) + geom_line(aes(x=years,y=med))
-
-########################## Now run the tuning sims
-
-  N.end <- vpa.abund[length(vpa.abund)]
-  tunes <- tune.sim(years,
-                    n.steps = 100,
-                    abund.ts = vpa.abund,
-                    mat.age = age.mat,
-                    nm = prop.nat.mort,
-                    w.age = weight.age,
-                    ages = ages,
-                    rems = rem$rem,
-                    fecund = mx,
-                    N.end = N.end,
-                    pop.model = 'exponential')
-
-  tuned.res[[i]] <- tunes
+# ########################## Now run the tuning sims
+# 
+#   N.end <- vpa.abund[length(vpa.abund)]
+#   tunes <- tune.sim(years,
+#                     n.steps = 100,
+#                     abund.ts = vpa.abund,
+#                     mat.age = age.mat,
+#                     nm = prop.nat.mort,
+#                     w.age = weight.age,
+#                     ages = ages,
+#                     rems = rem$rem,
+#                     fecund = mx,
+#                     N.end = N.end,
+#                     pop.model = 'exponential')
+# 
+#   tuned.res[[i]] <- tunes
 } # end i in Stocks look
+#
 

### 2023-04-27 Scripts/functions/backwards_sim.r

@@ -85,6 +85,7 @@ back.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL
                     a.len.wgt = a.len.wgt, b.len.wgt = b.len.wgt, 
                     a.fec.len = a.fec.len, b.fec.len = b.fec.len,
                     sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0)
+      browser()
     } # end if(i == 1)
       
     if(i > 1)

### 2023-04-27 Scripts/functions/forward_project.r

@@ -11,8 +11,6 @@
  
 for.proj <- function(option = "exponential",pop.last,r,removals.next,K,fishery.timing = 'beginning')
 {
-
-  
   ### So rolling with the easy peasy continuous time exponential
   ### simple exponential population growth, in this formulation with the removals I think I'm saying the removals happen right at the outset
   if(option == 'exponential') 

### 2023-04-27 Scripts/functions/forward_sim.r

@@ -48,22 +48,8 @@ for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
                   L.inf = NULL,K = NULL,t0 = NULL, a.len.wgt = NULL, b.len.wgt = NULL, a.fec.len = NULL, b.fec.len = NULL,
                   sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0)
 {
-  # Download the function to go from inla to sf
-  funs <- c("https://raw.githubusercontent.com/freyakeyser/ICM/main/Scripts/functions/Lotka_r.r",
-            "https://raw.githubusercontent.com/freyakeyser/ICM/main/Scripts/functions/backwards_project.r"
-  )
-  # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
-  for(fun in funs) 
-  {
-    download.file(fun,destfile = basename(fun))
-    source(paste0(getwd(),"/",basename(fun)))
-    file.remove(paste0(getwd(),"/",basename(fun)))
-  }
-  
-  source("D:/Github/ICM/Scripts/functions/Lotka_r.r") # For testing purposes, delete when done
-  
-  st.time <- Sys.time()
-  require(optimx)  || stop("Please load the 'optimx' package which you'll need for the optimations to run")
+
+  #st.time <- Sys.time()
   
   #Initialize a bunch of objects
   n.years<-length(years)
@@ -77,6 +63,7 @@ for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
   #Calculate r for your example
   for(i in 1:n.sims)
   {
+    #browser()
     # For the first run we use the mean estimate, for runs after that we add in all the uncertainty specified
     # For now I've only tested this using the stock assessment data, needs cleaned up for other options.
       junk<-lotka.r(yrs = years,age.mat = mat.age,nat.mort = nm,ages=ages,wt.at.age=w.age,fecund=fecund,sim =sim,proj.sim = proj.sim,
@@ -85,10 +72,9 @@ for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
     #browser()
     tmp <-junk$res[,2] 
     if(length(tmp) == 1) tmp <- rep(tmp,n.years)
-    r.vec[[i]] <- data.frame(r = tmp,years = years[],n.sims=i)
-
[…]

### 2023-04-27 Scripts/functions/north_sea_multi_stock_model.r

@@ -1,3 +1,312 @@
 # OK, here's I'm going to try and develop a multi=species projection model for the North Sea, we have 10 stocks with good data, the retro fits aren't perfect
 # But they mostly aren't a disaster either.  All have a reasonable length of time series as well.
+library(tidyverse)
+library(GGally)
+library(cowplot)
+
+# Download the function to go from inla to sf
+funs <- c("https://raw.githubusercontent.com/freyakeyser/ICM/main/Scripts/functions/Lotka_r.r",
+          "https://raw.githubusercontent.com/freyakeyser/ICM/main/Scripts/functions/forwrd_sim.r",
+          "https://raw.githubusercontent.com/freyakeyser/ICM/main/Scripts/functions/forwrd_project.r"
+)
+# Now run through a quick loop to load each one, just be sure that your working directory is read/write!
+for(fun in funs) 
+{
+  download.file(fun,destfile = basename(fun))
+  source(paste0(getwd(),"/",basename(fun)))
+  file.remove(paste0(getwd(),"/",basename(fun)))
+}
+
+#source("D:/Github/ICM/Scripts/functions/Lotka_r.r") # For testing purposes, delete when done
+
+
+
+
+
+load(file = "D:/Github/ICM/Results/model_inputs.Rdata")
+
+# Subset to the north sea stocks.  I need years, end abundance, natural mortality, and mx
+
+Stocks <- names(years.tmp)[grep("WGNSSK",names(years.tmp))]
+# I'm going to reorder the stocks here so the correlation bit below flows better. Kinda a-posteriorying this :-P 
+Stocks <- c("ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus", "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
+            "ICES-WGNSSK_NS 4-6- 3a_Pollachius_virens", "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua", "ICES-WGNSSK_NS4 _Scopthalmus_maximus",
+            "ICES-WGNSSK_NS 7d_Pleuronectes_platessa", "ICES-WGNSSK_NS 4,20_Pleuronectes_platessa","ICES-WGNSSK_NS 7d._Solea_solea","ICES-WGNSSK_NS4 _Solea_solea",
+            "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus")
[…]

### 2023-06-02 Scripts/ASR_stocks.Rmd
Many many updates, multi-species NS model has been developed
The NS multi-species model is in its infancy, but if we can land a student it can certainly be generalized nicely.

--- 2023-04-05 Scripts/ASR_stocks.Rmd
@@
   N.end <- sum(data[data$Year==max(years),]$Num)
-  #N.end <- rowSums(abund[nrow(abund),-which(names(abund) %in% c("Year", "Stock", "type"))], na.rm=T)
-  #vpa.abund <- rowSums(abund[,-which(names(abund) %in% c("Year", "Stock", "type"))], na.rm=T)
-  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num)) %>% pull(vpa)
+  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
 
@@
   annual <- data %>% group_by(Year) %>% summarize(tot.ssb = sum(ssb)) %>% left_join(annual)
+
+  #tst <- data %>% group_by(Year) %>% summarize(tot.ssn = sum(ssn)) %>% left_join(annual)
+
   #r.p.ssb This needs to be offset by the age of recruits
@@
 
-  tst <- icm.sim(years,
+  tst <- back.sim(years,
                  mat.age = age.mat,
-                 nm = prop.nat.mort,
+                 nm = -(log(1-prop.nat.mort)),
                  w.age = weight.age,
@@
 
-# Now run the tuning sims
+# ################# Now run as a forward simulation
+#   N.start <- vpa.abund[1] 
+# 
+#   tst <- for.sim(years,
+#                  mat.age = age.mat,
+#                  nm = -(log(1-prop.nat.mort)),
+#                  w.age = weight.age,
+#                  ages = ages,
+#                  rems = rem$rem, # rep(0,nrow(rem)),
+#                  fecund = mx,
+#                  N.start = N.start,
+#                  pop.model = 'exponential', K = 2e6,
+#                  n.sims = 2,
+#                  sd.mat = 0.5,
+#                  sd.nm = 0.5,
+#                  sd.wt = 0.5,
+#                  sd.fecund = 0.5)
+# 
+#   #Combine the data
+#   did.it.work <- data.frame(abund = c(vpa.abund,tst$Pop$abund),years = c(years,tst$Pop$years),sim = c(rep('VPA',length(years)),tst$Pop$sim))
+#   # Here get the Upper and lower 50% quantiles to make a functional boxplot
+#   quants <- did.it.work %>% dplyr::filter(sim != "VPA") %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
+#                                                                         med = median(abund),
+#                                                                         U.50 = quantile(abund,probs=c(0.75)))
+# 
+#   for.res[[i]] <- tst
+#   for.ts[[i]] <- did.it.work
+#   for.ts.quants[[i]] <- quants
 
+# ########################## Now run the tuning sims
+#
    N.end <- vpa.abund[length(vpa.abund)]
@@
                      mat.age = age.mat,
-                    nm = prop.nat.mort,
+                     nm = -(log(1-prop.nat.mort)),
                      w.age = weight.age,
@@
 } # end i in Stocks look
+
 # Save all these
@@
 ```{r, forward-sims-n-figs,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
+# Now we have to forward project the stocks, I think it makes the most sense to do this using the tuned data at the moment
+# So we assume the fecundity data and the tuned natural mortality data for the stocks is a reasonable representation of the future
+load(file = "D:/Github/ICM/Results/model_inputs.Rdata")
+
+back.res <- NULL
+back.ts <- NULL
+back.ts.quants <- NULL
+for.res <- NULL
+for.ts <- NULL
+for.ts.quants <- NULL
+tuned.res <- NULL
+for(i in Stocks)
+{
+  years <- years.tmp[[i]]
+  prop.nat.mort <- pnm.tmp[[i]] 
+  weight.age <- waa.tmp[[i]] 
+  ages <- ages.tmp[[i]] 
+  rem <- rem.tmp[[i]] 
+  mx <- mx.tmp[[i]] 
+  N.end <- NE.tmp[[i]] 
+  vpa.abund <- vpa.tmp[[i]] 
+  age.mat <- am.tmp[[i]]
+
+################# Now run as a forward simulation
+  N.start <- vpa.abund[length(vpa.abund)] 
+  years <- 2025:2075
+  # For the forward simulations I'm setting it up so we feed in the mean vector or a character, we'll then create a vector of mx's with variablitity
+  st.time <- Sys.time()
+  tst <- for.sim(years,
+                 mat.age = age.mat,
+                 nm = -(log(1-prop.nat.mort)),
+                 w.age = weight.age,
+                 ages = ages,
+                 rems = c(0.1,0.2), # This is set up as a fishing mortality that averages 0.1 with an sd of 0.2)
+                 fecund = mx,
+                 N.start = N.start,
+                 pop.model = 'exponential', sim = 'project', proj.sim = 'sample',
+                 n.sims = 30,
+                 sd.mat = 0.1,
+                 sd.nm = 0.1,
+                 sd.wt = 0.1,
+                 sd.fecund = 0.1)
+  Sys.time() - st.time
+  #Combine the data
+  did.it.work <- data.frame(abund = tst$Pop$abund,years = c(tst$Pop$years),sim = tst$Pop$sim)
+  # Here get the Upper and lower 50% quantiles to make a functional boxplot
+  quants <- tst$Pop %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
+                                                                   med = median(abund),
+                                                                   U.50 = quantile(abund,probs=c(0.75)))
+
+  for.res[[i]] <- tst
+  for.ts[[i]] <- tst$Pop
+  for.ts.quants[[i]] <- quants  
+}  
+ggplot(quants) + geom_line(aes(x=years,y=med))  + geom_ribbon(aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue')
+
 ```

### 2023-06-02 Scripts/functions/Lotka_r.r

@@ -228,7 +228,7 @@ lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL
         nat.mort[y,] <- nat.mort[y,]*nm.deva  
       } # end for(y in 1:n.yrs) loop
      } # end if(proj.sim == 'dist')
-      
+
   }
   
   ################################### END PROJECTION SECTION ################################### END PROJECTION SECTION################################### END PROJECTION SECTION
@@ -246,7 +246,7 @@ lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL
     # Just use the first year if we don't have same length nat.mort as years
     if(!is.null(nrow(nat.mort))) lx <- 1-exp(-nat.mort[j,]) else lx <- 1-exp(-nat.mort)
     # Convert to survivorship vector
-    si <- 1-lx
+    si <- 1-lx 
     # Set the first age class to be 1
     lx<-1
     # And get cumulative survivorship for the stock
@@ -258,6 +258,7 @@ lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL
     res[j,] <- c(yrs[j],junk$par)
     mx.tmp[[j]] <- mx
     lx.tmp[[j]] <- lx
+    #browser()
   } # end for(j in 1:(n.yrs-1))
   
   mx.mat <- do.call("rbind",mx.tmp)

### 2023-06-02 Scripts/functions/backwards_project.r

@@ -40,7 +40,7 @@ back.proj <- function(option = "exponential",pop.next,r,removals.next,K,fishery.
     # Get our parameter for the logistic model
     if(fishery.timing == 'beginning') par <- pop.next
     if(fishery.timing == 'end') par <- pop.next <- pop.next + removals.next
-    # Ha, we can use this to solve for N in the previous year
+    # Ha, we can use this to solve for N in the previous year 
     #I'm hung up on which of these to use, they give almost the same answer, but not quite, but going with the 1+r version since
     # we are in discrete time here.
     #logistic.n.last <- function(N.last) sum((exp(r)* ((N.last)/(1-(N.last/K))) / (1 + ( ((N.last)/(1-(N.last/K)))*exp(r))/K) - pop.next))^2

### 2023-06-02 Scripts/functions/backwards_sim.r

@@ -80,12 +80,13 @@ back.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL
     # For now I've only tested this using the stock assessment data, needs cleaned up for other options.
     if(i == 1)
     {
+      
       junk<-lotka.r(yrs = years,age.mat = mat.age,nat.mort = nm,ages=ages,wt.at.age=w.age,fecund=fecund,
-                    L.inf = L.inf,K = K,t0 = t0, 
+                    L.inf = L.inf,K = K,t0 = t0,  
                     a.len.wgt = a.len.wgt, b.len.wgt = b.len.wgt, 
                     a.fec.len = a.fec.len, b.fec.len = b.fec.len,
                     sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0)
-      browser()
+      #browser()
     } # end if(i == 1)
       
     if(i > 1)

### 2023-06-02 Scripts/functions/forward_sim.r

@@ -72,12 +72,15 @@ for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
     #browser()
     tmp <-junk$res[,2] 
     if(length(tmp) == 1) tmp <- rep(tmp,n.years)
+    
     r.vec[[i]] <- data.frame(r = c(tmp[-length(tmp)],NA),years = years[],n.sims=i)# How I have it set up the last entry should be an NA  as we don't use that
+    browser()
   }
-  
-  st.time2 <- Sys.time()
+  #browser() 
+  #print(st.time2 <- Sys.time())
   #unwrap your r vector
   r.vec <- do.call('rbind',r.vec)
+  
   #temp.r.vec<-r.vec[r.vec>0 & r.vec<r.cutoff]
   #r.vec<-temp.r.vec[1:n.sims]
   ############################################################
@@ -106,6 +109,7 @@ for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
       # Going to rescale r to be instantaneous, won't have much different for most stocks
       # but will help keep F reasonable for the highly productive stocks
       # Note that I'm using this as proportional removals hereafter (rescaling back properly would lead to fm values > 1 for some stocks)
+     
       r.insta <- 1-exp(median(-r.tmp$r,na.rm=T))
       if(r.insta < 0) r.insta <- 0.02 # If this negative, make mortality like 2% for this scenario.
       mn.fm <- rems[[2]]*r.insta
@@ -119,14 +123,14 @@ for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
       if(sim == 'retro') removals.next <- rems[y]
       if(sim == 'project') 
       {
-        
-        
+
         # Adding in harvest controls, basically if population is < 20% of K (B0), then harvesting rate declines by 90%
         # This is all stuff we can tweak.
         if(pop.last < 0.2*K) removals.next <- 0.1*fm[y]*pop.last
         if(pop.last >= 0.2*K) removals.next <- fm[y]*pop.last
         
       } 
+     
       r.up <- r.tmp$r[y-1] # So we grab the r associated with the lead in year so r aligns with the initial population numbers
       # The exponential model
       if(pop.model == 'exponential') 
[…]

### 2023-06-02 Scripts/functions/north_sea_multi_stock_model.r

@@ -61,8 +61,8 @@ sd.mx <- 0.1
 # or natural mortality terms by 1% or 0.5% a decade, based on how I code things below.  Lots of scope to
 # do whatever the heck we wanted here.
 c.effect <- round(0.25*n.yrs.proj) # The year in which the climate effect starts, 
-climate.mx.effect <- 0.01
-climate.nm.effect <- 0.01
+climate.mx.effect <- 0
+climate.nm.effect <- 0
 
 
 
@@ -296,10 +296,10 @@ for(s in Stocks)
   
   tst <- for.sim(years,
                  mat.age = age.mat,
-                 nm = prop.nat.mort,
+                 nm = -(log(1-prop.nat.mort)),
                  w.age = weight.age,
                  ages = ages,
-                 rems =  list("R_based",1), #fm,
+                 rems =  list("R_based",0.5), #fm,
                  fecund = mx,
                  N.start = N.start,
                  pop.model = 'bounded_exp', K = K,

### 2023-06-03 Scripts/functions/backwards_sim.r
Quick update

@@ -59,7 +59,7 @@ back.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL
     file.remove(paste0(getwd(),"/",basename(fun)))
   }
   
-  source("D:/Github/ICM/Scripts/functions/Lotka_r.r")
+  #source("D:/Github/ICM/Scripts/functions/Lotka_r.r")
   
   
   require(optimx)  || stop("Please load the 'optimx' package which you'll need for the optimations to run")

### 2023-06-03 Scripts/functions/forward_sim.r
quicky

@@ -74,7 +74,7 @@ for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
     if(length(tmp) == 1) tmp <- rep(tmp,n.years)
     
     r.vec[[i]] <- data.frame(r = c(tmp[-length(tmp)],NA),years = years[],n.sims=i)# How I have it set up the last entry should be an NA  as we don't use that
-    browser()
+    #browser()
   }
   #browser() 
   #print(st.time2 <- Sys.time())

### 2023-06-09 Scripts/NS_tuning_models.Rmd
MAESTRO update
Still working through shit though.

---
title: "ICM testing"
output:
  pdf_document: default
  html_document: default
  word_document: 
    #reference_docx: template.docx
editor_options:
  chunk_output_type: console
---

The data is now available to test this on at least 81 stocks.  All of the NE Atlantic stocks (ICES) have been through the QA/QC process and we are happy with those data (Sept 1, 2022).  Let's see if we can get this to work on all the stocks with sufficient data...

```{r, load-stuff,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)
library(cowplot)

loc <- 'C:/Users/Owner/Documents/GitHub/ICM'
source(paste0(loc,"/Scripts/functions/backwards_sim.R"))
source(paste0(loc,"/Scripts/functions/tuning_sim_version_2.R"))
load(file = paste0(loc,"/Results/model_inputs.Rdata"))

Stocks <- Stocks[grep("WGNSSK",Stocks)]
# Haddock in NS is busted before 1972, not sure why, but I'm chucking all that data here in a very sloppy way
  ns.had <- "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus"
  years.tmp[[ns.had]] <- years.tmp[[ns.had]][-1:-7]
  pnm.tmp[[ns.had]] <- pnm.tmp[[ns.had]][-1:-7,]
  waa.tmp[[ns.had]] <- waa.tmp[[ns.had]][-1:-7,]
  #ages.tmp[[ns.had]] <- ages.tmp[[ns.had]][-1:-7]
  rem.tmp[[ns.had]] <- rem.tmp[[ns.had]][-1:-7,]
  mx.tmp[[ns.had]] <- mx.tmp[[ns.had]][-1:-7,]
  #N.end[[ns.had]] <- NE.tmp[[ns.had]][-1:-7]
  vpa.tmp[[ns.had]] <- vpa.tmp[[ns.had]][-1:-7]
  am.tmp[[ns.had]] <- am.tmp[[ns.had]][-1:-7,]

  ns.had <- "ICES-WGNSSK_NS4 _Solea_solea"
  years.tmp[[ns.had]] <- years.tmp[[ns.had]][-1:-7]
  pnm.tmp[[ns.had]] <- pnm.tmp[[ns.had]][-1:-7,]
  waa.tmp[[ns.had]] <- waa.tmp[[ns.had]][-1:-7,]
  #ages.tmp[[ns.had]] <- ages.tmp[[ns.had]][-1:-7]
  rem.tmp[[ns.had]] <- rem.tmp[[ns.had]][-1:-7,]
  mx.tmp[[ns.had]] <- mx.tmp[[ns.had]][-1:-7,]
  #N.end[[ns.had]] <- NE.tmp[[ns.had]][-1:-7]
  vpa.tmp[[ns.had]] <- vpa.tmp[[ns.had]][-1:-7]
  am.tmp[[ns.had]] <- am.tmp[[ns.had]][-1:-7,]

```

```{r, run-mods,echo=F, message=F, warning=F}

back.res <- NULL
back.ts <- NULL
back.ts.quants <- NULL
for.res <- NULL
for.ts <- NULL
for.ts.quants <- NULL
tuned.res <- NULL
for(i in Stocks)
{
  years <- years.tmp[[i]]
  prop.nat.mort <- pnm.tmp[[i]] 
  weight.age <- waa.tmp[[i]] 
  ages <- ages.tmp[[i]] 
  rem <- rem.tmp[[i]] 
  mx <- mx.tmp[[i]] 
  N.end <- NE.tmp[[i]] 
  vpa.abund <- vpa.tmp[[i]] 
  age.mat <- am.tmp[[i]]

#
  # N.end <- vpa.abund[length(vpa.abund)]
   tunes <- tune.sim(years,
                     n.steps = 10,
                     tune.par=0.1,
                     abund.ts = vpa.abund,
                     mat.age = age.mat,
                     nm = -(log(1-prop.nat.mort)),
                     w.age = weight.age,
                     ages = ages,
                     rems = rem$rem,
                     fecund = mx,
                     N.end = N.end,
                     pop.model = 'exponential',
                     tuner = "nm")

   tuned.res[[i]] <- tunes
} # end i in Stocks look

# Save all these
 save.image(file = paste0(loc,"/Results/NS_tuned_sim_results.RData"))

```

```{r, make-figs,echo=F, message=F, warning=F, fig.width=6, fig.height=4}

# Now we can run the figures separately.
#tuned.res <- readRDS(file = "D:/Github/ICM/Results/tuned_fits.Rds")
#load(file = "D:/Github/ICM/Results/model_inputs.Rdata")
load(file = paste0(loc,"/Results/NS_tuned_sim_results.RData"))

for(i in Stocks)
{
  # Unpack the lists
  tunes <- tuned.res[[i]] 
  missing_rem <- mr.tmp[[i]]

  # Comparing our new time series with the old
  p2 <- ggplot() +
          geom_line(data=tunes$res, aes(x=years,y=abund),color='blue') +
          geom_line(data=tunes$res, aes(x=years,y=vpa.abund),color='black') +
          xlab("") +
          ylab("Abundance (1000s)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          ggtitle(i) #+
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p2, filename = paste0(loc,"/Figures/NS_sims/tunes/", i, "/tunded_vs_vpa_", i, ".png"), 
            base_width = 6,base_height = 4)

  # # Comparing the absolute miss from the tuned time series
  #  p3 <- ggplot() +
  #         #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
  #         geom_line(data=tunes$res[-1,], aes(x=year,y=diff.n),color='red') +
  #         xlab("") +
  #         ylab("Difference in abundance (1000s)") +
  #         #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
  #         theme_few() + theme(legend.position = 'none') + 
  #         ggtitle(i) 
  #         #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  # save_plot(plot = p3, filename = paste0(loc,"/Figures/NS_sims/tunes/", i, "/diff_N_", i, ".png"), 
  #           base_width = 6,base_height = 4)
  # 
  # # What percentage (mean) difference
  #  p4 <- ggplot() +
  #         #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
  #         geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.n),color='red') +
  #         xlab("") +
  #         ylab("Difference in abundance (%)") +
  #         #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
  #         theme_few() + theme(legend.position = 'none') + 
  #         ggtitle(i) #+ ylim(c(-100,100))
  #         #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  # save_plot(plot = p4, filename = paste0(loc,"/Figures/NS_sims/tunes/", i, "/per_diff_N_", i, ".png"), 
  #           base_width = 6,base_height = 4)
  # 
  # 
  #     p8 <- ggplot() +
  #         geom_line(data=tunes$res[-1,], aes(x=year,y=r),color='blue') +
  #         xlab("") +
  #         ylab("Lotka r") +
  #         #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
  #         theme_few() + theme(legend.position = 'none') +
  #         ggtitle(i) #+
  #         #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  # save_plot(plot = p8, filename = paste0(loc,"/Figures/NS_sims/tunes/", i, "/Lotka_r_", i, ".png"), 
  #           base_width = 6,base_height = 4)
  #    
  #    # Difference in m's
  #  p5 <- ggplot() +
  #         geom_line(data=tunes$res[-1,], aes(x=year,y=diff.m),color='red') +
  #         xlab("") +
  #         ylab("Difference in natural mortality (Instantaneous)") +
  #         #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
  #         theme_few() + theme(legend.position = 'none') + 
  #         ggtitle(i) #+ ylim(c(-100,100))
  #         #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  # save_plot(plot = p5, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/diff_m_", i, ".png"), base_width = 6,base_height = 4)
  #    # % Difference in m's
  #  p6 <- ggplot() +
  #         geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.m),color='red') +
  #         xlab("") +
  #         ylab("Difference in natural mortality (%)") +
  #         #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
  #         theme_few() + theme(legend.position = 'none') + 
  #         ggtitle(i) #+ ylim(c(-100,100))
  #         #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  # save_plot(plot = p6, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/per_diff_m_", i, ".png"), base_width = 6,base_height = 4)
  # 
  #  p7 <- ggplot() +
  #         geom_line(data=tunes$res[-1,], aes(x=year,y=mn.m),color='blue') +
  #         geom_line(data=tunes$res[-1,], aes(x=year,y=vpa.m),color='black') +
  #         xlab("") +
  #         ylab("Natural mortality (Instantaneous)") +
  #         #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
  #         theme_few() + theme(legend.position = 'none') +
  #         ggtitle(i) #+
  #         #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  # save_plot(plot = p7, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/Nat_M_", i, ".png"), base_width = 6,base_height = 4)
  #

}

```

### 2023-06-09 Scripts/functions/forward_sim.r

@@ -37,7 +37,8 @@
 
 # w.age           The weight of individuals for each age, if a matrix the rows are different simulations
 #                 we could also let this vary by year, but we'll need to go 3-D array or something for that
-# K
+# CC
+# B0
 # dec.rate
 # sim
 # proj.sim
@@ -46,7 +47,8 @@ for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
                   sel,rems = c(0.1,0.2),N,u,pop.model = "exponential", sim = 'retro', proj.sim='dist',
                   dec.rate = NULL,
                   L.inf = NULL,K = NULL,t0 = NULL, a.len.wgt = NULL, b.len.wgt = NULL, a.fec.len = NULL, b.fec.len = NULL,
-                  sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0)
+                  sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0,
+                  CC = 1e6,B0 = 1e6)
 {
 
   #st.time <- Sys.time()
@@ -58,6 +60,7 @@ for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
   rem<-rep(NA,n.years)
   r.vec<-NULL
   B1.vec<-rep(0,n.sims) ### backwards projections 
+  if(length(CC) == 1) CC <- rep(CC,n.years)
   #rems<-matrix(rep(0,n.years*n.sims),n.sims,n.years)
 
   #Calculate r for your example
@@ -93,15 +96,16 @@ for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
     # Get the final year estimate of your population
     Pop.vec[1] <- pop.last <- N.start  # Assuming this is our known starting point, could add uncertainty to this as well if we want to.
     removals <- NA
-    r.tmp <- r.vec[r.vec$n.sims == i,]
+    r.tmp <- r.vec[r.vec$n.sims == i,] 
     #browser()
     #r.store <- r.vec[r.vec$n.sims == i,-1] # We don't use the first r value 
     #Now run your model backwards with the r from the Lotka function and
     # if you use the logistic growth model the K estimated for the population.
     
     # Now we can calculate removals.
+
[…]

### 2023-06-09 Scripts/functions/north_sea_multi_stock_model.r

@@ -23,25 +23,11 @@ for(fun in funs)
 }
 
 #source("D:/Github/ICM/Scripts/functions/Lotka_r.r") # For testing purposes, delete when done
-load(file = "D:/Github/ICM/Results/model_inputs.Rdata")
+#load(file = "C:/Users/Owner/Documents/Github/ICM/Results/model_inputs.Rdata")
+#load(file = "D:/Github/ICM/Results/model_inputs.Rdata")
+loc <- 'C:/Users/Owner/Documents/GitHub/ICM'
 
-
-
-# Subset to the north sea stocks.  I need years, end abundance, natural mortality, and mx
-Stocks <- names(years.tmp)[grep("WGNSSK",names(years.tmp))]
-# I'm going to reorder the stocks here so the correlation bit below flows better. Kinda a-posteriorying this :-P 
-Stocks <- c("ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus", "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
-            "ICES-WGNSSK_NS 4-6- 3a_Pollachius_virens", "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua", "ICES-WGNSSK_NS4 _Scopthalmus_maximus",
-            "ICES-WGNSSK_NS 7d_Pleuronectes_platessa", "ICES-WGNSSK_NS 4,20_Pleuronectes_platessa","ICES-WGNSSK_NS 7d._Solea_solea","ICES-WGNSSK_NS4 _Solea_solea",
-            "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus")
-yrs.ns <- years.tmp[Stocks]
-nm.ns <- pnm.tmp[Stocks] # Proportional natural mortality here.
-mx.ns <- mx.tmp[Stocks]
-vpa.ns <- vpa.tmp[Stocks]
-ages.ns <- ages.tmp[Stocks]
-waa.ns <- waa.tmp[Stocks]
-mat.ns <- am.tmp[Stocks]
-rem.ns <- rem.tmp[Stocks]
+load(file = paste0(loc,"/Results/NS_tuned_sim_results.RData"))
 
 ########################### End Section 1 Loading  ###################################### End Section 1 Loading ###############################################
 
@@ -53,8 +39,8 @@ rem.ns <- rem.tmp[Stocks]
[…]

### 2023-06-09 Scripts/functions/north_sea_multi_stock_model_K_version.r

@@ -1,0 +1,315 @@
+# OK, here's I'm going to try and develop a multi=species projection model for the North Sea, we have 10 stocks with good data, the retro fits aren't perfect
+# But they mostly aren't a disaster either.  All have a reasonable length of time series as well.
+
+#################  Section 1 Loading #################  Section 1 Loading #################  Section 1 Loading  ###############################################
+library(tidyverse)
+library(GGally)
+library(cowplot)
+library(ggthemes)
+# Set the base plot theme
+theme_set(theme_few(base_size = 14))
+
+# Download the function to go from inla to sf
+funs <- c("https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/Lotka_r.r",
+          "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/forward_sim.r",
+          "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/forward_project.r"
+)
+# Now run through a quick loop to load each one, just be sure that your working directory is read/write!
+for(fun in funs) 
+{
+  download.file(fun,destfile = basename(fun))
+  source(paste0(getwd(),"/",basename(fun)))
+  file.remove(paste0(getwd(),"/",basename(fun)))
+}
+
+#source("D:/Github/ICM/Scripts/functions/Lotka_r.r") # For testing purposes, delete when done
+load(file = "C:/Users/Owner/Documents/Github/ICM/Results/model_inputs.Rdata")
+#load(file = "D:/Github/ICM/Results/model_inputs.Rdata")
+loc <- 'C:/Users/Owner/Documents/GitHub/ICM'
+
+load(file = paste0(loc,"/Results/NS_tuned_sim_results.RData"))
+
+########################### End Section 1 Loading  ###################################### End Section 1 Loading ###############################################
+
+
+
+
+
+
+########################## Section 2 Parameters ########################## Section 2 Parameters ########################## Section 2 Parameters
+
[…]

### 2023-06-09 Scripts/functions/tuning_sim_version_2.r

@@ -46,7 +46,7 @@
 # dec.rate
 
 
-tune.sim<-function(years,tune.par=0.01,tuner="m", n.steps = 30,
+tune.sim<-function(years,tune.par=0.01,tuner="fec", n.steps = 30,
                    mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,fecund = NULL,N.end = NULL,abund.ts = NULL,
                    sel,rems,N,u,pop.model = "exp",
                    dec.rate = NULL,
@@ -54,8 +54,8 @@ tune.sim<-function(years,tune.par=0.01,tuner="m", n.steps = 30,
                    sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0)
 {
   # Download the function to go from inla to sf
-  funs <- c("https://raw.githubusercontent.com/freyakeyser/ICM/main/Scripts/functions/Lotka_r.r",
-            "https://raw.githubusercontent.com/freyakeyser/ICM/main/Scripts/functions/backwards_project.r"
+  funs <- c("https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/Lotka_r.r",
+            "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/backwards_project.r"
   )
   # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
   for(fun in funs) 
@@ -64,9 +64,6 @@ tune.sim<-function(years,tune.par=0.01,tuner="m", n.steps = 30,
     source(paste0(getwd(),"/",basename(fun)))
     file.remove(paste0(getwd(),"/",basename(fun)))
   }
-  
-  source("D:/Github/ICM/Scripts/functions/Lotka_r.r")
-  
   
   require(optimx)  || stop("Please load the 'optimx' package which you'll need for the optimations to run")
   
@@ -79,128 +76,157 @@ tune.sim<-function(years,tune.par=0.01,tuner="m", n.steps = 30,
   #B1.vec<-rep(0,n.sims) ### backwards projections 
   #rems<-matrix(rep(0,n.years*n.sims),n.sims,n.years)
 
+  
+  
   # So I think what I want to create here is a big list of natural mortality and fecundity 'scenarios' that we select from until we find one that 'works'
   
-  if(tuner == 'm')
+  if(tuner == 'nm')
   {
-    nm.lst <- NULL
-    for(y in 1:n.years)
+    #nm.lst <- NULL
+    #fecund.lst <- NULL
[…]

### 2023-06-09 Scripts/north_sea_cod_test.r

@@ -79,7 +79,7 @@ mx <- recs.per.age/ssn/2 # Moms only! Dividing by around 8 really nails it for N
 # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...
 
 
-tst <- icm.sim(years = years,mat.age = age.mat[,c(-1,-ncol(age.mat))],nm = prop.nat.mort[,c(-1,-ncol(prop.nat.mort))],
+tst <- back.sim(years = years,mat.age = age.mat[,c(-1,-ncol(age.mat))],nm = prop.nat.mort[,c(-1,-ncol(prop.nat.mort))],
                w.age = weight.age[,c(-1,-ncol(weight.age))],ages = 0:6,rems = rem,
                fecund = mx,N.end =N.end,pop.model = 'exponential',
                n.sims = 5,sd.mat = 0.5,sd.nm = 0.5,sd.wt = 0.5,sd.fecund = 0.5)

### 2023-06-22 Scripts/ASR_stocks.Rmd
End of MAESTRO update
Still trying to sort out Esmarkii and Cod tuning shit.  Also still thinking about the correct ages to use for the VPA time sereis.  I think it is right now, but still needs more thought.  Gettnig close, but not quite there for the tuning stuff

@@
 library(cowplot)
+loc <- 'C:/Users/Owner/Documents/GitHub/ICM'
 
-source("D:/Github/ICM/Scripts/functions/backwards_sim.R")
-source("D:/Github/ICM/Scripts/functions/tuning_sim.R")
+source(paste0(loc,"/Scripts/functions/backwards_sim.R"))
+source(paste0(loc,"/Scripts/functions/tuning_sim.R"))
 
 # Choose 5 ICES stocks that we have the necessary data for
-#ASR <- read_xlsx("../Data/ASR_2018.xlsx", sheet = "ICES")
-ASR1 <- read.csv("D:/Github/ICM/Data/ICM_data_NE_atlantic_stocks.csv")
-ASR <- read.csv("D:/Github/ICM/Data/ICM_data_NW_atlantic_stocks.csv")
+#ASR <- read_xlsx("../Data/ASR_2018.xlsx" sheet = "ICES")
+ASR1 <- read.csv(paste0(loc,"/Data/ICM_data_NE_atlantic_stocks.csv"))
+ASR <- read.csv(paste0(loc,"/Data/ICM_data_NW_atlantic_stocks.csv"))
 
@@
   age.mat <- ASR_sub %>% dplyr::filter(type=="AM") %>% dplyr::rename(AM=value) %>% dplyr::select(-type)
+  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
+  # in case that changes later...
+  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
+  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
+  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
+  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
+  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
+  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0
+
+  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
   nat.mort <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
@@
 
+  # Aahh??  Is this NA dropping useful data, needed to quick fix the age at maturity data...
   data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
@@
 
-save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,am.tmp,Stocks,ASR_stocks,ASR_long,file = "D:/Github/ICM/Results/model_inputs.Rdata")
+save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,am.tmp,Stocks,ASR_stocks,ASR_long,file =  paste0(loc,"/Results/model_inputs.Rdata"))
 
@@
 
-load(file = "D:/Github/ICM/Results/model_inputs.Rdata")
+load(file = paste0(loc,"/Results/model_inputs.Rdata"))
 
@@
                  pop.model = 'exponential',
-                 n.sims = 500,
+                 n.sims = 50,
                  sd.mat = 0.5,
@@
 # ########################## Now run the tuning sims
+# #
+#    N.end <- vpa.abund[length(vpa.abund)]
+#    tunes <- tune.sim(years,
+#                      n.steps = 100,
+#                      abund.ts = vpa.abund,
+#                      mat.age = age.mat,
+#                      nm = -(log(1-prop.nat.mort)),
+#                      w.age = weight.age,
+#                      ages = ages,
+#                      rems = rem$rem,
+#                      fecund = mx,
+#                      N.end = N.end,
+#                      pop.model = 'exponential')
 # 
-   N.end <- vpa.abund[length(vpa.abund)]
-   tunes <- tune.sim(years,
-                     n.steps = 100,
-                     abund.ts = vpa.abund,
-                     mat.age = age.mat,
-                     nm = -(log(1-prop.nat.mort)),
-                     w.age = weight.age,
-                     ages = ages,
-                     rems = rem$rem,
-                     fecund = mx,
-                     N.end = N.end,
-                     pop.model = 'exponential')
-
-   tuned.res[[i]] <- tunes
+#    tuned.res[[i]] <- tunes
 } # end i in Stocks look
@@
 # Save all these
- saveRDS(object = tuned.res,file = "D:/Github/ICM/Results/tuned_fits.Rds")
- saveRDS(object = back.res,file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
- saveRDS(object = back.ts,file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
- saveRDS(object = back.ts.quants,file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
+# saveRDS(object = tuned.res,file = "D:/Github/ICM/Results/tuned_fits.Rds")
+ saveRDS(object = back.res,file = paste0(loc,"/Results/backwards_sim_results.Rds"))
+ saveRDS(object = back.ts,file = paste0(loc,"/Results/backwards_sim_ts_summaries.Rds"))
+ saveRDS(object = back.ts.quants,file = paste0(loc,"/Results/backwards_sim_ts_quantiles_summaries.Rds"))
 ```

### 2023-06-22 Scripts/functions/forward_sim.r

@@ -37,8 +37,7 @@
 
 # w.age           The weight of individuals for each age, if a matrix the rows are different simulations
 #                 we could also let this vary by year, but we'll need to go 3-D array or something for that
-# CC
-# B0
+# K
 # dec.rate
 # sim
 # proj.sim
@@ -47,8 +46,7 @@ for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
                   sel,rems = c(0.1,0.2),N,u,pop.model = "exponential", sim = 'retro', proj.sim='dist',
                   dec.rate = NULL,
                   L.inf = NULL,K = NULL,t0 = NULL, a.len.wgt = NULL, b.len.wgt = NULL, a.fec.len = NULL, b.fec.len = NULL,
-                  sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0,
-                  CC = 1e6,B0 = 1e6)
+                  sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0)
 {
 
   #st.time <- Sys.time()
@@ -60,7 +58,6 @@ for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
   rem<-rep(NA,n.years)
   r.vec<-NULL
   B1.vec<-rep(0,n.sims) ### backwards projections 
-  if(length(CC) == 1) CC <- rep(CC,n.years)
   #rems<-matrix(rep(0,n.years*n.sims),n.sims,n.years)
 
   #Calculate r for your example
@@ -96,16 +93,15 @@ for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
     # Get the final year estimate of your population
     Pop.vec[1] <- pop.last <- N.start  # Assuming this is our known starting point, could add uncertainty to this as well if we want to.
     removals <- NA
-    r.tmp <- r.vec[r.vec$n.sims == i,] 
+    r.tmp <- r.vec[r.vec$n.sims == i,]
     #browser()
     #r.store <- r.vec[r.vec$n.sims == i,-1] # We don't use the first r value 
     #Now run your model backwards with the r from the Lotka function and
     # if you use the logistic growth model the K estimated for the population.
     
     # Now we can calculate removals.
-
[…]

### 2023-06-22 Scripts/functions/tuning_sim_version_2.r

@@ -43,7 +43,7 @@
 # w.age           The weight of individuals for each age, if a matrix the rows are different simulations
 #                 we could also let this vary by year, but we'll need to go 3-D array or something for that
 # K
-# dec.rate
+# dec.rate  
 
 
 tune.sim<-function(years,tune.par=0.01,tuner="fec", n.steps = 30,
@@ -51,7 +51,7 @@ tune.sim<-function(years,tune.par=0.01,tuner="fec", n.steps = 30,
                    sel,rems,N,u,pop.model = "exp",
                    dec.rate = NULL,
                    L.inf = NULL,K = NULL,t0 = NULL, a.len.wgt = NULL, b.len.wgt = NULL, a.fec.len = NULL, b.fec.len = NULL,
-                   sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0)
+                   sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0,CC =1e20)
 {
   # Download the function to go from inla to sf
   funs <- c("https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/Lotka_r.r",
@@ -181,19 +181,34 @@ tune.sim<-function(years,tune.par=0.01,tuner="fec", n.steps = 30,
   
         # Need to think here
         r.up <- r.tmp %>% dplyr::filter(year == years[y]) %>% dplyr::pull(r) # Grab the correct value of r
-    
+        # So this one is the exponential, but when above whatever bound you have set the population growth rate averages 0 with a little uncertainty
+        if(pop.model == 'bounded_exp') 
+        {
+          #browser()
+          if(pop.next[y] > CC & r.up > 0) 
+          {
+            r.up <- rlnorm(1,0,0.02)-1
+          }
+          exp.res <- back.proj(option = "exponential",pop.last = pop.next[y] ,r=r.up,removals = removals.next,direction,fishery.timing = 'beginning')
+          #browser()
+          if(exp.res$Pop.current < 0) exp.res$Pop.current =0 # don't let it drop below 0
+          pop.next[y-1]  <- exp.res$Pop.current
+        } 
         # The exponential model
         if(pop.model == 'exponential') 
         {
           exp.res <- back.proj(option = "exponential",pop.next = pop.next[y],r=r.up,removals = removals.next)
+          if(exp.res$Pop.current < 0) exp.res$Pop.current =0 # don't let it drop below 0
           pop.next[y-1] <- exp.res$Pop.current
[…]

### 2023-06-22 Scripts/functions/tuning_sim.r
oopsy
forget to save

@@ -102,7 +102,6 @@ tune.sim<-function(years,tune.par=0.01,tuner="m", n.steps = 30,
       nm.lst[[as.character(years[y])]] <- nm.vary
     }
   }
-  browser()
   
   #Calculate r for your examples... going to be a lot of lotka.r's all of a sudden isn't there...
   tmp.y <- NULL

### 2023-10-03 Scripts/Paper_1.Rmd
Forward and backward tuning with fecundity working

--- 2023-06-22 Scripts/ASR_stocks.Rmd
@@
 library(cowplot)
-loc <- 'C:/Users/Owner/Documents/GitHub/ICM'
+loc <- 'D:/GitHub/ICM'
 
@@
   age.mat <- am.tmp[[i]]
-
+  # 
+  # # The first run gives us the mean estimate, I think that's all we need for our first paper
   tst <- back.sim(years,
@@
                  pop.model = 'exponential',
-                 n.sims = 50,
-                 sd.mat = 0.5,
-                 sd.nm = 0.5,
-                 sd.wt = 0.5,
-                 sd.fecund = 0.5)
+                 n.sims = 1)
 
@@
 # ################# Now run as a forward simulation
-#   N.start <- vpa.abund[1] 
-# 
-#   tst <- for.sim(years,
-#                  mat.age = age.mat,
-#                  nm = -(log(1-prop.nat.mort)),
-#                  w.age = weight.age,
-#                  ages = ages,
-#                  rems = rem$rem, # rep(0,nrow(rem)),
-#                  fecund = mx,
-#                  N.start = N.start,
-#                  pop.model = 'exponential', K = 2e6,
-#                  n.sims = 2,
-#                  sd.mat = 0.5,
-#                  sd.nm = 0.5,
-#                  sd.wt = 0.5,
-#                  sd.fecund = 0.5)
-# 
-#   #Combine the data
-#   did.it.work <- data.frame(abund = c(vpa.abund,tst$Pop$abund),years = c(years,tst$Pop$years),sim = c(rep('VPA',length(years)),tst$Pop$sim))
-#   # Here get the Upper and lower 50% quantiles to make a functional boxplot
-#   quants <- did.it.work %>% dplyr::filter(sim != "VPA") %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
-#                                                                         med = median(abund),
-#                                                                         U.50 = quantile(abund,probs=c(0.75)))
-# 
-#   for.res[[i]] <- tst
-#   for.ts[[i]] <- did.it.work
-#   for.ts.quants[[i]] <- quants
+N.start <- vpa.abund[1]
 
-# ########################## Now run the tuning sims
-# #
-#    N.end <- vpa.abund[length(vpa.abund)]
-#    tunes <- tune.sim(years,
-#                      n.steps = 100,
-#                      abund.ts = vpa.abund,
-#                      mat.age = age.mat,
-#                      nm = -(log(1-prop.nat.mort)),
-#                      w.age = weight.age,
-#                      ages = ages,
-#                      rems = rem$rem,
-#                      fecund = mx,
-#                      N.end = N.end,
-#                      pop.model = 'exponential')
-# 
-#    tuned.res[[i]] <- tunes
+tst <- for.sim(years,
+               mat.age = age.mat,
+               nm = -(log(1-prop.nat.mort)),
+               w.age = weight.age,
+               ages = ages,
+               rems = rem$rem, # rep(0,nrow(rem)),
+               fecund = mx,
+               N.start = N.start,
+               pop.model = 'exponential',
+               n.sims = 1,
+               sd.mat = 0,
+               sd.nm = 0,
+               sd.wt = 0,
+               sd.fecund = 0)
+
+  #Combine the data
+  did.it.work <- data.frame(abund = c(vpa.abund,tst$Pop$abund),years = c(years,tst$Pop$years),sim = c(rep('VPA',length(years)),tst$Pop$sim))
+  # Here get the Upper and lower 50% quantiles to make a functional boxplot
+  quants <- did.it.work %>% dplyr::filter(sim != "VPA") %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
+                                                                        med = median(abund),
+                                                                        U.50 = quantile(abund,probs=c(0.75)))
+
+  for.res[[i]] <- tst
+  for.ts[[i]] <- did.it.work
+  for.ts.quants[[i]] <- quants
+
 } # end i in Stocks look
@@
 # Save all these
-# saveRDS(object = tuned.res,file = "D:/Github/ICM/Results/tuned_fits.Rds")
- saveRDS(object = back.res,file = paste0(loc,"/Results/backwards_sim_results.Rds"))
- saveRDS(object = back.ts,file = paste0(loc,"/Results/backwards_sim_ts_summaries.Rds"))
- saveRDS(object = back.ts.quants,file = paste0(loc,"/Results/backwards_sim_ts_quantiles_summaries.Rds"))
-```
-
-```{r, make-figs,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
-
-# Now we can run the figures separately.
-tuned.res <- readRDS(file = "D:/Github/ICM/Results/tuned_fits.Rds")
-back.ts <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
-back.ts.quants <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
-back.res <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
-load(file = "D:/Github/ICM/Results/model_inputs.Rdata")
-
-for(i in Stocks)
-{
-  # Unpack the lists
-  tunes <- tuned.res[[i]] 
-  did.it.work <- back.ts[[i]] 
-  quants <- back.ts.quants[[i]] 
-  missing_rem <- mr.tmp[[i]] 
-  tst <- back.res[[i]]
-
-  did.it.work$missing[did.it.work$years %in% missing_rem] <- "missing"
-
-    # All the results in a plot
-  p2 <- ggplot() +
-          geom_line(data=did.it.work, aes(x=years,y=abund,color=sim)) +
-          xlab("") +
-          ylab("Abundance (1000s)") +
-          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
-          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') + scale_color_viridis_d(end = 0.75) +
-          ggtitle(i) +
-          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p2, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/runs_vs_vpa_", i, ".png"), base_width = 6,base_height = 4)
-  # Same thing but functional boxplots
-  p3 <- ggplot() +
-          geom_line(data=quants, aes(x=years,y= med)) +
-          geom_ribbon(data=quants, aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue') +
-          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
-          xlab("") + ylab("Abundance (1000s)") +
-          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') + #geom_vline()
-          ggtitle(i)+
-          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p3, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/runs_vs_vpa_ribbon_", i, ".png"), base_width = 6,base_height = 4)
-
-  # Plotting how the estimate of r changes over time (which you can do when we have time varying inputs (e.g. Wgt, M, or maturity at age)
-  p4 <- ggplot(tst$r) +
-          geom_line(aes(x=years,y=r,group=n.sims,color=n.sims)) +
-          xlab("") +
-          ylab("Lotka r") +
-          #scale_y_continuous(breaks = seq(0,1.5,by=0.1)) +
-          #scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') +
-          scale_color_viridis_c(end = 0.75) +
-          ggtitle(i)
-  save_plot(plot = p4, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/lokta_r_", i, ".png"), base_width = 6,base_height = 4)
-
-  # Comparing our new time series with the old
-  p2 <- ggplot() +
-          geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
-          geom_line(data=tunes$res, aes(x=year,y=vpa.n),color='black') +
-          xlab("") +
-          ylab("Abundance (1000s)") +
-          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
-          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') +
-          ggtitle(i) #+
-          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p2, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/tunded_vs_vpa_", i, ".png"), base_width = 6,base_height = 4)
-
-  # Comparing the absolute miss from the tuned time series
-   p3 <- ggplot() +
-          #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
-          geom_line(data=tunes$res[-1,], aes(x=year,y=diff.n),color='red') +
-          xlab("") +
-          ylab("Difference in abundance (1000s)") +
-          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
-          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') + 
-          ggtitle(i) 
-          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p3, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/diff_N_", i, ".png"), base_width = 6,base_height = 4)
-
-  # What percentage (mean) difference
-   p4 <- ggplot() +
-          #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
-          geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.n),color='red') +
-          xlab("") +
-          ylab("Difference in abundance (%)") +
-          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
-          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') + 
-          ggtitle(i) #+ ylim(c(-100,100))
-          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p4, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/per_diff_N_", i, ".png"), base_width = 6,base_height = 4)
-
-     # Difference in m's
-   p5 <- ggplot() +
-          geom_line(data=tunes$res[-1,], aes(x=year,y=diff.m),color='red') +
-          xlab("") +
-          ylab("Difference in natural mortality (Instantaneous)") +
-          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
-          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') + 
-          ggtitle(i) #+ ylim(c(-100,100))
-          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p5, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/diff_m_", i, ".png"), base_width = 6,base_height = 4)
-     # % Difference in m's
-   p6 <- ggplot() +
-          geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.m),color='red') +
-          xlab("") +
-          ylab("Difference in natural mortality (%)") +
-          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
-          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') + 
-          ggtitle(i) #+ ylim(c(-100,100))
-          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p6, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/per_diff_m_", i, ".png"), base_width = 6,base_height = 4)
-
-   p7 <- ggplot() +
-          geom_line(data=tunes$res[-1,], aes(x=year,y=mn.m),color='blue') +
-          geom_line(data=tunes$res[-1,], aes(x=year,y=vpa.m),color='black') +
-          xlab("") +
-          ylab("Natural mortality (Instantaneous)") +
-          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
-          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') +
-          ggtitle(i) #+
-          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p7, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/Nat_M_", i, ".png"), base_width = 6,base_height = 4)
-
-     p8 <- ggplot() +
-          geom_line(data=tunes$res[-1,], aes(x=year,y=r),color='blue') +
-          xlab("") +
-          ylab("Lotka r") +
-          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
-          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') +
-          ggtitle(i) #+
-          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p8, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/Lotka_r_", i, ".png"), base_width = 6,base_height = 4)
-
-}
-
-# summary plots for ALL stocks, this is already run, so lets not keep running it
-# for (i in unique(ASR_long$Stock)) {
-#   ASR_sub <- ASR_long %>%
-#     dplyr::select(Year, Stock, type, age, value) %>%
-#     dplyr::filter(Stock==i)
-#   maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]),na.rm=T)
-#   maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
-#   minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
-#   forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
-#   forplot <- forplot[!is.na(forplot$value),] # remove the NAs, hopefully this works for all the stocks...
-#   p1 <- ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
-#         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
-#         theme_bw() + 
-#         ggtitle(i) +
-#     guides(x =  guide_axis(angle = 90)) 
-#   print(p1)
-#   
-#   if(!dir.exists(paste0("D:/Github/ICM/Figures/", i))) dir.create(paste0("D:/Github/ICM/Figures/", i))
-#   
-#   png(filename=paste0("D:/Github/ICM/Figures/", i, "/data_summary_", i, ".png"), height=4, width=12, res=400, units="in")
-#   print(p1)
-#   dev.off()
-# }
+saveRDS(object = back.res,file = paste0(loc,"/Results/backwards_sim_results_no_error.Rds"))
+saveRDS(object = back.ts,file = paste0(loc,"/Results/backwards_sim_ts_summaries_no_error.Rds"))
+saveRDS(object = back.ts.quants,file = paste0(loc,"/Results/backwards_sim_ts_quantiles_summaries_no_error.Rds"))
+# Forward simulations, just using the 'realization'
+saveRDS(object = for.res,file = paste0(loc,"/Results/forwards_sim_results_no_error.Rds"))
+saveRDS(object = for.ts,file = paste0(loc,"/Results/forwards_sim_ts_summaries_no_error.Rds"))
+saveRDS(object = for.ts.quants,file = paste0(loc,"/Results/forwards_sim_ts_quantiles_summaries_no_error.Rds"))
 
@@
 
-```{r, forward-sims-n-figs,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
-# Now we have to forward project the stocks, I think it makes the most sense to do this using the tuned data at the moment
-# So we assume the fecundity data and the tuned natural mortality data for the stocks is a reasonable representation of the future
-load(file = "D:/Github/ICM/Results/model_inputs.Rdata")
+```{r}
+
+# Upack the back.res object...
+
+tst.for <- NULL
+tst.back <- NULL
+count = 0
+for(i in Stocks)
+{
+  count=count+1
+  tmp.for <- for.res[[i]]$r %>% dplyr::filter(n.sims==1)
+  tmp.for <- data.frame(tmp.for,stock = i,direction = 'forward simulations',id = count)
+  tmp.pop.for <- for.res[[i]]$Pop %>% dplyr::filter(sim==1)
+  tst.for[[i]] <- left_join(tmp.pop.for,tmp.for,by=c('years'))
+  # backwards
+  tmp.back <- back.res[[i]]$r %>% dplyr::filter(n.sims==1)
+  tmp.back <- data.frame(tmp.back,stock = i,direction = 'backwards simulations',id = count)
+  tmp.pop.back <- back.res[[i]]$Pop %>% dplyr::filter(sim==1)
+  tst.back[[i]] <- left_join(tmp.pop.back,tmp.back,by=c('years'))
+}
+
+fors <- do.call('rbind',tst.for)
+fors <- fors[,-4]
+backs <- do.call('rbind',tst.back)
+
+exploring <- rbind(fors,backs)
+mn.r <- exploring %>% dplyr::group_by(stock,direction,id) %>% dplyr::summarise(r = median(r,na.rm=T),
+                                                                  pop.ratio = dplyr::last(abund)/dplyr::first(abund))
+windows(11,11)
+ggplot(mn.r) + geom_text(aes(r,pop.ratio,label=id)) + scale_y_log10() + facet_wrap(~direction) + xlab("mean instrinc rate of growth (r)") + ylab("N (Final) / N (Initial)")
+
+quantile(mn.r$r,probs = seq(0.01,1,by=0.01),na.rm=T)
+
+```
+
+So now I can try to do some tuning, both forwards and backwards, lets see what we get from that...
+
+```{r tunes}
+
+########################## Now run the tuning sims
+#
+
+load(file = paste0(loc,"/Results/model_inputs.Rdata"))
 
@@
   age.mat <- am.tmp[[i]]
+  N.end <- vpa.abund[length(vpa.abund)]
 
-################# Now run as a forward simulation
-  N.start <- vpa.abund[length(vpa.abund)] 
-  years <- 2025:2075
-  # For the forward simulations I'm setting it up so we feed in the mean vector or a character, we'll then create a vector of mx's with variablitity
-  st.time <- Sys.time()
-  tst <- for.sim(years,
+   back.tunes <- tune.sim(years,
+                          tuner = 'f',
+                           n.steps = 100, step.size = 0.2,
+                           abund.ts = vpa.abund,
                            mat.age = age.mat,
@@
                            ages = ages,
-                 rems = c(0.1,0.2), # This is set up as a fishing mortality that averages 0.1 with an sd of 0.2)
+                           rems = rem$rem,
                            fecund = mx,
-                 N.start = N.start,
-                 pop.model = 'exponential', sim = 'project', proj.sim = 'sample',
-                 n.sims = 30,
-                 sd.mat = 0.1,
-                 sd.nm = 0.1,
-                 sd.wt = 0.1,
-                 sd.fecund = 0.1)
-  Sys.time() - st.time
-  #Combine the data
-  did.it.work <- data.frame(abund = tst$Pop$abund,years = c(tst$Pop$years),sim = tst$Pop$sim)
-  # Here get the Upper and lower 50% quantiles to make a functional boxplot
-  quants <- tst$Pop %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
-                                                                   med = median(abund),
-                                                                   U.50 = quantile(abund,probs=c(0.75)))
+                           N.init = N.end,
+                           pop.model = 'exponential',
+                           direction='backwards')
 
-  for.res[[i]] <- tst
-  for.ts[[i]] <- tst$Pop
-  for.ts.quants[[i]] <- quants  
+   back.tuned.res[[i]] <- back.tunes
+
+   N.start <- vpa.abund[1]
+
+   for.tunes   <- tune.sim(years,
+                           tuner='f',
+                           n.steps =100, step.size =0.2,
+                           abund.ts = vpa.abund,
+                           mat.age = age.mat,
+                           nm = -(log(1-prop.nat.mort)),
+                           w.age = weight.age,
+                           ages = ages,
+                           rems = rem$rem,
+                           fecund = mx,
+                           N.init = N.start,
+                           pop.model = 'exponential',
+                           direction= 'forwards')
+
+   for.tuned.res[[i]] <- for.tunes
+
 }
-ggplot(quants) + geom_line(aes(x=years,y=med))  + geom_ribbon(aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue')
 

### 2023-10-03 Scripts/functions/Lotka_r.r

@@ -76,11 +76,11 @@ lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL
   # If you have given me the maturity ogive than rename it
   if(length(age.mat) > 1) 
   {
-    if(is.vector(age.mat)) mat.ogive <- rlnorm(length(age.mat),age.mat,sd.nm)
+    if(is.vector(age.mat)) mat.ogive <- rlnorm(length(age.mat),age.mat,sd.mat)
     if(!is.vector(age.mat)) 
     {
       mat.ogive <- as.data.frame(age.mat) # Get it set up, then overwrite it with the uncertainty
-      for(i in 1:nrow(age.mat)) mat.ogive[i,] <- rlnorm(length(age.mat[i,]),as.numeric(log(age.mat[i,])),sd.nm)
+      for(i in 1:nrow(age.mat)) mat.ogive[i,] <- rlnorm(length(age.mat[i,]),as.numeric(log(age.mat[i,])),sd.mat)
     }
     
     
@@ -100,7 +100,7 @@ lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL
   {  
     W.age <- as.data.frame(wt.at.age)
     # Add in uncertainty
-    if(is.vector(wt.at.age)) W.age <- rlnorm(length(wt.at.age),wt.at.age,sd.nm)
+    if(is.vector(wt.at.age)) W.age <- rlnorm(length(wt.at.age),wt.at.age,sd.wt)
     if(!is.vector(wt.at.age)) for(i in 1:nrow(wt.at.age)) W.age[i,] <- rlnorm(length(wt.at.age[i,]),as.numeric(log(wt.at.age[i,])),sd.wt)
   }
   

### 2023-10-03 Scripts/functions/backwards_sim.r

@@ -42,14 +42,14 @@
 
 
 back.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,fecund = NULL,N.end = NULL,
-                  sel,rems,N,u,pop.model = "exp", direction = 'back',
+                  sel,rems,N,u,pop.model = "exponential", 
                   dec.rate = NULL,
                   L.inf = NULL,K = NULL,t0 = NULL, a.len.wgt = NULL, b.len.wgt = NULL, a.fec.len = NULL, b.fec.len = NULL,
                   sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0)
 {
   # Download the function to go from inla to sf
-  funs <- c("https://raw.githubusercontent.com/freyakeyser/ICM/main/Scripts/functions/Lotka_r.r",
-            "https://raw.githubusercontent.com/freyakeyser/ICM/main/Scripts/functions/backwards_project.r"
+  funs <- c("https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/Lotka_r.r",
+            "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/backwards_project.r"
   )
   # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
   for(fun in funs) 
@@ -63,6 +63,10 @@ back.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL
   
   
   require(optimx)  || stop("Please load the 'optimx' package which you'll need for the optimations to run")
+  
+  # In case I try to be lazy and shorten names...
+  if(pop.model == 'exp') pop.model <- 'exponential'
+  if(pop.model == 'log') pop.model <- 'logistic'
   
   #Initialize a bunch of objects
   n.years<-length(years)
@@ -123,9 +127,12 @@ back.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL
       #browser()
       # DK Note: So for our removals time series, we put the removals between t+1 and t 
       # down as year t+1.  We can change this, but that's how this is set up at the moment.
-      removals.next <- rems[y-1]
+      # DK changed this to be rems[y] not rems[y-1] in Oct 2023, as I think that makes more sense to me at the moment.
+      removals.next <- rems[y]
       #browser()
-      r.up <- r.tmp$r[y] # 
[…]

### 2023-10-03 Scripts/functions/forward_sim.r

@@ -43,14 +43,31 @@
 # proj.sim
 
 for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,fecund = NULL,N.start = NULL,
-                  sel,rems = c(0.1,0.2),N,u,pop.model = "exponential", sim = 'retro', proj.sim='dist',
+                  sel,rems,N,u,pop.model = "exponential", sim = 'retro', proj.sim='dist',
                   dec.rate = NULL,
                   L.inf = NULL,K = NULL,t0 = NULL, a.len.wgt = NULL, b.len.wgt = NULL, a.fec.len = NULL, b.fec.len = NULL,
                   sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0)
 {
 
-  #st.time <- Sys.time()
+  # Download the function to go from inla to sf
+  funs <- c("https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/Lotka_r.r",
+            "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/forward_project.r"
+  )
+  # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
+  for(fun in funs) 
+  {
+    download.file(fun,destfile = basename(fun))
+    source(paste0(getwd(),"/",basename(fun)))
+    file.remove(paste0(getwd(),"/",basename(fun)))
+  }
   
+  source("D:/Github/ICM/Scripts/functions/Lotka_r.r")
+  source("D:/Github/ICM/Scripts/functions/forward_project.r")
+  
+  #st.time <- Sys.time()
+  # In case I try to be lazy and shorten names...
+  if(pop.model == 'exp') pop.model <- 'exponential'
+  if(pop.model == 'log') pop.model <- 'logistic'
   #Initialize a bunch of objects
   n.years<-length(years)
   Pop<-data.frame(abund = rep(NA,n.years*n.sims),sim = rep(1:n.sims,n.years),years = sort(rep(years,n.sims)))    #matrix(data=NA, nrow=<<see below>>, ncol=<<see below>>,byrow=F, dimnames=NULL) 
@@ -63,19 +80,36 @@ for.sim<-function(years,n.sims=1,mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,
   #Calculate r for your example
   for(i in 1:n.sims)
   {
+    # For the first run we use the mean estimate, for runs after that we add in all the uncertainty specified
[…]

### 2023-10-03 Scripts/functions/tuning_sim.r

@@ -4,11 +4,11 @@
 # All the data you need to make it dance...
 # years:          The years you are running the backwards calculation for
 # abund.ts:       The abundance time series from the assessment
-# tune.par:       How close to the assessment biomass do we want to get.  default is 0.01 (1%)
+
 # tuner:          What are we tuning, the fecundity "f", or natural mortality 'm', or both 'b'
 # rems            Removals from the fishery in a given year.
 # n.steps         The number of different m or f options to explore.  Make sure this is an even number!
-
+# step.size:      How big is the difference (proportional) in the simulation step.  Default = 0.05 which is about a 5% change for each step
 # mat.age         Age at maturity if one value it is the age at 50% maturity, if a vector it is the age at maturities for each age(or age/year), if a matrix we want this to be unique for each simulation
 #                 we could also let this vary by year, but we'll need to go 3-D array or something for that# ages:           What are the ages you are using this is used to calculate max age, which may not be ideal with plus group stocks.
 
@@ -44,10 +44,10 @@
 #                 we could also let this vary by year, but we'll need to go 3-D array or something for that
 # K
 # dec.rate
+# direction       Allow for forwards and backwards simulations
 
-
-tune.sim<-function(years,tune.par=0.01,tuner="m", n.steps = 30,
-                   mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,fecund = NULL,N.end = NULL,abund.ts = NULL,
+tune.sim<-function(years,step.size=0.05,tuner="m", n.steps = 30, direction = 'backwards',
+                   mat.age = NULL,nm=NULL,w.age = NULL,ages =NULL,fecund = NULL,N.init = NULL,abund.ts = NULL,
                    sel,rems,N,u,pop.model = "exp",
                    dec.rate = NULL,
                    L.inf = NULL,K = NULL,t0 = NULL, a.len.wgt = NULL, b.len.wgt = NULL, a.fec.len = NULL, b.fec.len = NULL,
@@ -93,35 +93,79 @@ tune.sim<-function(years,tune.par=0.01,tuner="m", n.steps = 30,
       {
        count <- count + 1
        if(s == n.steps/2) nm.vary[[s]] <- nm[y,]
[…]

### 2023-10-04 Scripts/Paper_1.Rmd
Including Lotka output in tunning
This includes the mx/lx nat mort, and fecundity vectors used to get the r value, so this can be used to get at other metrics we might want.

@@
                           tuner = 'f',
-                           n.steps = 100, step.size = 0.2,
+                           n.steps = 250, step.size = 0.2,
                            abund.ts = vpa.abund,
@@
                            tuner='f',
-                           n.steps =100, step.size =0.2,
+                           n.steps =250, step.size =0.2,
                            abund.ts = vpa.abund,

### 2023-10-04 Scripts/functions/tuning_sim.r

@@ -54,8 +54,10 @@ tune.sim<-function(years,step.size=0.05,tuner="m", n.steps = 30, direction = 'ba
                    sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0)
 {
   # Download the function to go from inla to sf
-  funs <- c("https://raw.githubusercontent.com/freyakeyser/ICM/main/Scripts/functions/Lotka_r.r",
-            "https://raw.githubusercontent.com/freyakeyser/ICM/main/Scripts/functions/backwards_project.r"
+  funs <- c("https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/Lotka_r.r",
+            "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/backwards_project.r",
+            "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/forward_project.r"
+            
   )
   # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
   for(fun in funs) 
@@ -129,6 +131,7 @@ tune.sim<-function(years,step.size=0.05,tuner="m", n.steps = 30, direction = 'ba
   
   #Calculate r for your examples... going to be a lot of lotka.r's all of a sudden isn't there...
   tmp.y <- NULL
+  lotka.res <- NULL
   for(y in 1:n.years)
   {
     if(tuner == 'm') nm.tmp <- nm.lst[[as.character(years[y])]] 
@@ -138,8 +141,10 @@ tune.sim<-function(years,step.size=0.05,tuner="m", n.steps = 30, direction = 'ba
     waa.tmp <- w.age[y,]
     if(tuner == 'f') fecund.tmp <- fec.lst[[as.character(years[y])]] 
     if(tuner != 'f') fecund.tmp <- fecund[y,]
-    tmp.s <- NULL
     
+    tmp.s <- NULL
+    tmp.l <- NULL
+
     #browser()
     
     for(ss in 1:n.steps)
@@ -152,6 +157,7 @@ tune.sim<-function(years,step.size=0.05,tuner="m", n.steps = 30, direction = 'ba
                     a.fec.len = a.fec.len, b.fec.len = b.fec.len,
                     sd.mat = 0,sd.nm = 0,sd.wt = 0,sd.fecund = 0)
[…]

### 2023-10-16 Scripts/Paper_1.Rmd
Tuning completed
Backwards and forwards are working nicely now.  Next up getting other metrics.

@@
 
-source(paste0(loc,"/Scripts/functions/backwards_sim.R"))
-source(paste0(loc,"/Scripts/functions/tuning_sim.R"))
+source(paste0(loc,"/Scripts/functions/tuning_sim_fast.R"))
 
@@
 #Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
-# Esmarki doesn't work great as it is assessed using a quarterly modle.
+# Esmarki doesn't work great as it is assessed using a quarterly model.
 #Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
@@
 mr.tmp <- NULL
+all.abund.tmp <- NULL
+full.abund.tmp <- NULL
 for(i in Stocks)
@@
     dplyr::filter(Stock==i)
+
+  # Drop the NA years....
+  if(i == "ICES-NWWG_ICE-Summer_Clupea_harengus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1986)
+  # There's some funkiness going on in the first 7 years of these data, so staring in year 8
+  if( i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1971)
+  if(i == "ICES-NWWG_FA5b_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)
+  if(i == "ICES-NWWG_FA5a_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1984)
+  if(i == "ICES-AFWG_NEA1-2_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1969)
+  if(i == "ICES-WGCSE_CS27.6a_Merlangius_merlangus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1980)
+  if(i == "ICES-WGCSE_NS6a_Gadus_morhua") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1980)
+  if(i == "ICES-AFWG_COASTNOR 1-2_Gadus_morhua") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 2006)
+  if(i == "NEFSC_5Z_Pseudopleuronectes_americanus")ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)
 
@@
   am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
+  am.3s <- length(which((!is.na(age.mat$AM[age.mat$age ==3]))))
   if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
@@
   if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0
+  if(am.3s == 0) age.mat$AM[age.mat$age ==3] <- 0
+
+   # Now we can get the abundance from the VPA models
+  abund <- ASR_sub %>% dplyr::filter(type=="Num") %>% dplyr::rename(Num=value) %>% dplyr::select(-type)
 
   #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
-  nat.mort <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
-  abund <- ASR_sub %>% dplyr::filter(type=="Num") %>% dplyr::rename(Num=value) %>% dplyr::select(-type)
+  # Now do something similar for the Natural moralities, but in this case
+  # we take the NM of the youngest age class we have information for and back that number up to year 0.
+  # DK NOTE:  THIS IS A BIG CHANGE IN DIRECTION FOR THE LOTKA CALCS SO NEED TO NOTE THIS ONE!!
+
+  nm.tmp <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
+  #minage
+  minage <- min(as.numeric(nm.tmp$age[!is.na(nm.tmp$NM)]))
+  if(minage == 0)  nat.mort <- nm.tmp
+  # Some specials...
+  if(i %in% c("ICES-WGCSE_CS7e-k_Gadus_morhua","ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus",
+              "ICES-WGHANSA_SP8abd_Sardina _pilchardus","ICES-WGWIDE_NEA 1-9,12,14_Micromesistius_poutassou")) minage <- 1
+  if(i == "ICES-WGWIDE_NEA 1,2,5,4a,14a_clupea_ harengus") minage <- 2
+  #maxage
+  maxage <- max(as.numeric(nm.tmp$age[!is.na(nm.tmp$NM)]))
+  # Set up the full abundance matrix 
+  full.abund <- abund
+  # If we need to imput some data run this loop for natural mortality
+  if(minage == 0) full.abund <- abund
+
+  if(minage > 0)
+  {
+    yrs <- sort(unique((nm.tmp$Year)))
+    nm.res <- NULL
+    if(!i %in% c("ICES-WGCSE_CS7e-k_Gadus_morhua","ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus",
+                 "ICES-WGHANSA_SP8abd_Sardina _pilchardus","ICES-WGWIDE_NEA 1,2,5,4a,14a_clupea_ harengus",
+                 "ICES-WGWIDE_NEA 1-9,12,14_Micromesistius_poutassou"))
+    {
+      for(y in 1:(length(yrs)))
+      {
+        tmp <- nm.tmp %>% dplyr::filter(Year == yrs[y])
+        tmp.abund <- abund %>% dplyr::filter(Year == yrs[y])
+        min.nm <- tmp$NM[tmp$age == minage]
+        tmp$NM[as.numeric(tmp$age) < minage] <- min.nm
+        # Now save these mudders...
+        nm.res[[y]] <- tmp
+      } # end years loop
+      nat.mort <- do.call('rbind',nm.res)
+    }
+  # Now do the same loopiness for abundance
+    for(y in length(yrs):2)
+    {
+      # The minage of the natural mortality is different from minage of the abundance, annoyingly for this stock...
+      if(i == "ICES-AFWG_NEA1-2_Gadus_morhua") minage <- 3
+      if(i == "ICES-NWWG_ICE-Summer_Clupea_harengus") minage <- 3
+
+      # for(a in (minage-1):0)
+      # {
+      #   start.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == a+1) %>% dplyr::pull(Num)
+      #   nm.calc <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][a+1,]$NM) 
+      #   full.abund[full.abund$Year ==yrs[y]-1,][a+1,]$Num <- start.abund/(1-nm.calc)
+      # }
+
+        #if(minage >1 & y == 1)
+        #{
+           # The lowest minage =4, This goes first since we go backwards, this gets us age 3 in year 3
+           if(minage ==4) 
+           {
+               four.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 4) %>% dplyr::pull(Num)
+               nm.four <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][4,]$NM) 
+               full.abund[full.abund$Year ==yrs[y]-1,][4,]$Num <- four.abund/(1-nm.four)
+             #}# end my 2:0
+           } # end if minage ==4
+
+            # The minage =3 scenario, goes after 4...
+           if(minage >=3)
+           {
+             # for(my in 0:1)
+             # {
+               three.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 3) %>% dplyr::pull(Num)
+               nm.three <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][3,]$NM) 
+               full.abund[full.abund$Year ==yrs[y]-1,][3,]$Num <- three.abund/(1-nm.three)
+             #} # end my 1:0
+           } # end if(minage ==2)
+
+           # The minage =2 scenario, this goes last
+           if(minage >=2)
+           {
+             two.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 2) %>% dplyr::pull(Num)
+             nm.two <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][2,]$NM) 
+             full.abund[full.abund$Year ==yrs[y]-1,][2,]$Num <- two.abund/(1-nm.two)
+           } # end if(minage ==2)
+
+           if(minage >=1)
+           {
+             one.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 1) %>% dplyr::pull(Num)
+             nm.one <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][1,]$NM) 
+             full.abund[full.abund$Year ==yrs[y]-1,][1,]$Num <- one.abund/(1-nm.one)
+           } # end if(minage ==2)
+
+         } # The annoying if to fill in rest of the first few years.
+  } # end if minage > 0
+
+  # We won't have a weight at age for the young ages, which is fine since we only need that for SSB
   weight.age <- ASR_sub %>% dplyr::filter(type=="WA") %>% dplyr::rename(WA=value) %>% dplyr::select(-type)
   removals <- ASR_sub %>% dplyr::filter(type=="Catch") %>% dplyr::rename(Catch=value) %>% dplyr::select(-type)
-
+  # Fill the leading NAs with 0s now...
+  if(minage > 0) 
+  {
+    weight.age$WA[weight.age$age %in% 0:(minage-1)] <- 0
+    removals$Catch[removals$age %in% 0:(minage-1)] <- 0
+  }
  # if(i=="ICES-WGBFAS_BS 22-32_Sprattus_sprattus") removals$Catch <- removals$Catch/1000
@@
     full_join(nat.mort) %>%
-    full_join(abund) %>%
+    #full_join(abund) %>%
+    full_join(full.abund) %>%
     full_join(weight.age) %>%
@@
 
-  # Aahh??  Is this NA dropping useful data, needed to quick fix the age at maturity data...
+  # Nice way to toss NAs!
   data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
   data <- data[data$available==T,]
+  # And then toss the years we don't have 0 data for Numbers in the 0 age class
+  toss.years <- data %>% dplyr::group_by(Year) %>% dplyr::reframe(bad.years = which(min(age)>0))
+  data <- data[!data$Year %in% toss.years$Year,]
 
@@
   N.end <- sum(data[data$Year==max(years),]$Num)
-  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
+  all.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
+  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::filter(age >= minage) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
+  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
 
-  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
-  #minage
-  minage <- min(as.numeric(data$age))
-  #maxage
-  maxage <- max(as.numeric(data$age))
   #recruits
-  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
+  annual <- data.frame(Year=data$Year[data$age==0], recruits=data$Num[data$age==0])
   #ssn
@@
 
-  #r.p.ssb This needs to be offset by the age of recruits
-  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+1):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage)])
+  #r.p.ssb This no longer needs any offset...
+  annual$r.p.ssb <- annual$recruits/annual$tot.ssb
   # recs.per.age
@@
   # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
-  tmp <- NULL
-  for(j in 1:length(years))
-  {
-    tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
-    tst$Year <- tst$Year + minage
-    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
-    tmp[[j]] <- tst
-  }
+  # tmp <- NULL
+  # for(j in 1:length(years))
+  # {
+  #   tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
+  #   tst$Year <- tst$Year + minage
+  #   names(tst) <- c("ssb.offset","ssn.offset","Year","age")
+  #   tmp[[j]] <- tst
+  # }
   # Unpack the list
-  ssb.off <- do.call('rbind',tmp)
+  #@ssb.off <- do.call('rbind',tmp)
   # And merge it with the data object
-  data <- left_join(data,ssb.off,by=c("Year","age"))
-  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
+  #data <- left_join(data,ssb.off,by=c("Year","age"))
+  data$recs.per.age <- data$ssb*data$r.p.ssb
   # mx
@@
   # This works because 'males' is also in 'females'
-  if(grepl("males",i)) data$mx <- data$recs.per.age/data$ssn.offset 
-  if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
+  if(grepl("males",i)) data$mx <- data$recs.per.age/data$ssn 
+  if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn/2 # Moms only! 
   data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
@@
   # Dealing with some annoying NAs...
-  if(i == "AFSC_BSAI-Males_Pleuronectes_quadrituberculatus")
-  {
-    age.mat[length(years),] <- age.mat[length(years)-1,]
-    prop.nat.mort[length(years),] <- prop.nat.mort[length(years)-1,]
-    weight.age[length(years),] <- weight.age[length(years)-1,]
-    mx[length(years),13:23] <- mx[length(years),12]
-  }
-
+  # if(i == "AFSC_BSAI-Males_Pleuronectes_quadrituberculatus")
+  # {
+  #   age.mat[length(years),] <- age.mat[length(years)-1,]
+  #   prop.nat.mort[length(years),] <- prop.nat.mort[length(years)-1,]
+  #   weight.age[length(years),] <- weight.age[length(years)-1,]
+  #   mx[length(years),13:23] <- mx[length(years),12]
+  # }
+  # 
   if(i == "DFO_2J3KL_Gadus_morhua")
   {
-    age.mat[,8:10] <- 1
-    prop.nat.mort[,8:10] <- prop.nat.mort[,7]
-    weight.age[12:14,9:10] <- weight.age[12:14,8]
-    weight.age[15,10] <- weight.age[15,9]
-    mx[12:16,9:10] <- mx[12:16,8]
-    mx[17,10] <- mx[17,9]
+    age.mat[,10:12] <- 1
+    prop.nat.mort[,10:12] <- prop.nat.mort[,9]
+    weight.age[12:14,11:12] <- weight.age[12:14,10]
+    weight.age[15,12] <- weight.age[15,11]
+    mx[12:14,11:12] <- mx[12:14,10]
+    mx[15,12] <- mx[15,11]
   }
@@
   {
-    age.mat[6:7,10] <- 1
-    prop.nat.mort[6:7,10] <- prop.nat.mort[6:7,9]
-    weight.age[6:7,10] <- weight.age[6:7,9]
-    mx[6:9,10] <- mx[6:9,9]
+    age.mat[6:7,12] <- 1
+    prop.nat.mort[6:7,12] <- prop.nat.mort[6:7,11]
+    weight.age[6:7,12] <- weight.age[6:7,11]
+    mx[6:7,12] <- mx[6:7,11]
   }
@@
   {
-    age.mat[30,8] <- 1
-    prop.nat.mort[30,8] <- prop.nat.mort[30,7]
-    weight.age[30,8] <- weight.age[29,8]
-    mx[30:31,8] <- mx[30:31,9]
+    age.mat[30,9] <- 1
+    prop.nat.mort[30,9] <- prop.nat.mort[30,8]
+    weight.age[30,9] <- weight.age[29,9]
+    mx[30,9] <- mx[30,8]
   }
@@
   {
-    age.mat[c(14,27,40),5] <- age.mat[1,5]
-    prop.nat.mort[c(14,27,40),5] <- prop.nat.mort[1,5]
-    weight.age[c(14,27,40),5] <- weight.age[c(13,26,39),5]
-    mx[c(14,16,27,29,40,42),5] <- mx[c(14,16,27,29,40,42),6]
+    age.mat[c(14,27,40),7] <- age.mat[1,7]
+    prop.nat.mort[c(14,27,40),7] <- prop.nat.mort[1,7]
+    weight.age[c(14,27,40),7] <- weight.age[c(13,26,39),7]
+    mx[c(14,27,40),7] <- mx[c(14,27,40),6]
   }
-
+  # Clear out some 0's...
+  if( i == "AFSC_EEBSAI_Limanda_aspera")
+  {
+    mx[4,19] <- mean(unlist(mx[4,c(18,20)]))
+    mx[c(5,7),20] <- mx[c(5,7),19]
+    mx[1:6,21] <- mx[1:6,20] 
+  }
   # For the years of mx without SSB info to inform them
-  if(minage >0 ) 
-  {
-    mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
-    names(mx) <- names(mx.fill)
-   # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
-    mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
-  }
+  # if(minage >0 ) 
+  # {
+  #   mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
+  #   names(mx) <- names(mx.fill)
+  #  # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
+  #   mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
+  # }
   years.tmp[[i]] <- years
@@
   vpa.tmp[[i]] <- vpa.abund
+  all.abund.tmp[[i]] <- all.abund
+  full.abund.tmp[[i]] <- full.abund
   am.tmp[[i]] <- age.mat
@@
 
-save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,am.tmp,Stocks,ASR_stocks,ASR_long,file =  paste0(loc,"/Results/model_inputs.Rdata"))
-
-```
-
-```{r, run-mods,echo=F, message=F, warning=F}
-
-load(file = paste0(loc,"/Results/model_inputs.Rdata"))
-
-back.res <- NULL
-back.ts <- NULL
-back.ts.quants <- NULL
-for.res <- NULL
-for.ts <- NULL
-for.ts.quants <- NULL
-tuned.res <- NULL
-for(i in Stocks)
-{
-  years <- years.tmp[[i]]
-  prop.nat.mort <- pnm.tmp[[i]] 
-  weight.age <- waa.tmp[[i]] 
-  ages <- ages.tmp[[i]] 
-  rem <- rem.tmp[[i]] 
-  mx <- mx.tmp[[i]] 
-  N.end <- NE.tmp[[i]] 
-  vpa.abund <- vpa.tmp[[i]] 
-  age.mat <- am.tmp[[i]]
-  # 
-  # # The first run gives us the mean estimate, I think that's all we need for our first paper
-  tst <- back.sim(years,
-                 mat.age = age.mat,
-                 nm = -(log(1-prop.nat.mort)),
-                 w.age = weight.age,
-                 ages = ages,
-                 rems = rem$rem,
-                 fecund = mx,
-                 N.end = N.end,
-                 pop.model = 'exponential',
-                 n.sims = 1)
-
-  #Combine the data
-  did.it.work <- data.frame(abund = c(vpa.abund,tst$Pop$abund),years = c(years,tst$Pop$years),sim = c(rep('VPA',length(years)),tst$Pop$sim))
-  # Here get the Upper and lower 50% quantiles to make a functional boxplot
-  quants <- did.it.work %>% dplyr::filter(sim != "VPA") %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
-                                                                        med = median(abund),
-                                                                        U.50 = quantile(abund,probs=c(0.75)))
-
-  back.res[[i]] <- tst
-  back.ts[[i]] <- did.it.work
-  back.ts.quants[[i]] <- quants
-
-# ################# Now run as a forward simulation
-N.start <- vpa.abund[1]
-
-tst <- for.sim(years,
-               mat.age = age.mat,
-               nm = -(log(1-prop.nat.mort)),
-               w.age = weight.age,
-               ages = ages,
-               rems = rem$rem, # rep(0,nrow(rem)),
-               fecund = mx,
-               N.start = N.start,
-               pop.model = 'exponential',
-               n.sims = 1,
-               sd.mat = 0,
-               sd.nm = 0,
-               sd.wt = 0,
-               sd.fecund = 0)
-
-  #Combine the data
-  did.it.work <- data.frame(abund = c(vpa.abund,tst$Pop$abund),years = c(years,tst$Pop$years),sim = c(rep('VPA',length(years)),tst$Pop$sim))
-  # Here get the Upper and lower 50% quantiles to make a functional boxplot
-  quants <- did.it.work %>% dplyr::filter(sim != "VPA") %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
-                                                                        med = median(abund),
-                                                                        U.50 = quantile(abund,probs=c(0.75)))
-
-  for.res[[i]] <- tst
-  for.ts[[i]] <- did.it.work
-  for.ts.quants[[i]] <- quants
-
-} # end i in Stocks look
-
-# Save all these
-saveRDS(object = back.res,file = paste0(loc,"/Results/backwards_sim_results_no_error.Rds"))
-saveRDS(object = back.ts,file = paste0(loc,"/Results/backwards_sim_ts_summaries_no_error.Rds"))
-saveRDS(object = back.ts.quants,file = paste0(loc,"/Results/backwards_sim_ts_quantiles_summaries_no_error.Rds"))
-# Forward simulations, just using the 'realization'
-saveRDS(object = for.res,file = paste0(loc,"/Results/forwards_sim_results_no_error.Rds"))
-saveRDS(object = for.ts,file = paste0(loc,"/Results/forwards_sim_ts_summaries_no_error.Rds"))
-saveRDS(object = for.ts.quants,file = paste0(loc,"/Results/forwards_sim_ts_quantiles_summaries_no_error.Rds"))
-
-```
-
-```{r}
-
-# Upack the back.res object...
-
-tst.for <- NULL
-tst.back <- NULL
-count = 0
-for(i in Stocks)
-{
-  count=count+1
-  tmp.for <- for.res[[i]]$r %>% dplyr::filter(n.sims==1)
-  tmp.for <- data.frame(tmp.for,stock = i,direction = 'forward simulations',id = count)
-  tmp.pop.for <- for.res[[i]]$Pop %>% dplyr::filter(sim==1)
-  tst.for[[i]] <- left_join(tmp.pop.for,tmp.for,by=c('years'))
-  # backwards
-  tmp.back <- back.res[[i]]$r %>% dplyr::filter(n.sims==1)
-  tmp.back <- data.frame(tmp.back,stock = i,direction = 'backwards simulations',id = count)
-  tmp.pop.back <- back.res[[i]]$Pop %>% dplyr::filter(sim==1)
-  tst.back[[i]] <- left_join(tmp.pop.back,tmp.back,by=c('years'))
-}
-
-fors <- do.call('rbind',tst.for)
-fors <- fors[,-4]
-backs <- do.call('rbind',tst.back)
-
-exploring <- rbind(fors,backs)
-mn.r <- exploring %>% dplyr::group_by(stock,direction,id) %>% dplyr::summarise(r = median(r,na.rm=T),
-                                                                  pop.ratio = dplyr::last(abund)/dplyr::first(abund))
-windows(11,11)
-ggplot(mn.r) + geom_text(aes(r,pop.ratio,label=id)) + scale_y_log10() + facet_wrap(~direction) + xlab("mean instrinc rate of growth (r)") + ylab("N (Final) / N (Initial)")
-
-quantile(mn.r$r,probs = seq(0.01,1,by=0.01),na.rm=T)
+save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,am.tmp,Stocks,ASR_stocks,ASR_long,all.abund.tmp,full.abund.tmp,file =  paste0(loc,"/Results/model_inputs_all_ages.Rdata"))
 
@@
 
-load(file = paste0(loc,"/Results/model_inputs.Rdata"))
+load(file = paste0(loc,"/Results/model_inputs_all_ages.Rdata"))
 
-back.res <- NULL
-back.ts <- NULL
-back.ts.quants <- NULL
-for.res <- NULL
-for.ts <- NULL
-for.ts.quants <- NULL
-tuned.res <- NULL
+back.tune.all.res <- NULL
+back.tune.summary <- NULL
+for.tune.all.res <- NULL
+for.tune.summary <- NULL
 for(i in Stocks)
@@
   prop.nat.mort <- pnm.tmp[[i]] 
-  weight.age <- waa.tmp[[i]] 
-  ages <- ages.tmp[[i]] 
   rem <- rem.tmp[[i]] 
@@
   N.end <- NE.tmp[[i]] 
+  ages <- ages.tmp[[i]]
   vpa.abund <- vpa.tmp[[i]] 
-  age.mat <- am.tmp[[i]]
-  N.end <- vpa.abund[length(vpa.abund)]
+  all.abund <- all.abund.tmp[[i]]
+  #N.end <- vpa.abund[length(vpa.abund)]
 
-   back.tunes <- tune.sim(years,
-                          tuner = 'f',
-                           n.steps = 250, step.size = 0.2,
-                           abund.ts = vpa.abund,
-                           mat.age = age.mat,
+   N.start <- all.abund[1]
+   print(i)
+   # The fecundities are 
+   fast.for.tune <- fast.tunes(years,
+                           tuner='f',
+                           step.size = 0.025, # Make sure n.steps is even please!!
+                           abund.ts = all.abund,
+                           ages=ages,
                            nm = -(log(1-prop.nat.mort)),
-                           w.age = weight.age,
+                           rems = rem$rem,
+                           fecund = mx,
+                           N.init = N.start,
+                           direction= 'forwards'
+                           )
+
+   for.tune.all.res[[i]] <- fast.for.tune
+   for.tune.tmp <- data.frame(fast.for.tune$res,Stock = i)
+   for.tune.summary[[i]] <- for.tune.tmp
+
+   N.end <- all.abund[length(all.abund)]
+
+   fast.back.tune <- fast.tunes(years,
+                           tuner='f',
+                           step.size = 0.025, # Make sure n.steps is even please!!
+                           abund.ts = all.abund,
                            ages = ages,
+                           nm = -(log(1-prop.nat.mort)),
                            rems = rem$rem,
@@
                            N.init = N.end,
-                           pop.model = 'exponential',
-                           direction='backwards')
+                           direction= 'backwards'
+                           )
 
-   back.tuned.res[[i]] <- back.tunes
-
-   N.start <- vpa.abund[1]
-
-   for.tunes   <- tune.sim(years,
-                           tuner='f',
-                           n.steps =250, step.size =0.2,
-                           abund.ts = vpa.abund,
-                           mat.age = age.mat,
-                           nm = -(log(1-prop.nat.mort)),
-                           w.age = weight.age,
-                           ages = ages,
-                           rems = rem$rem,
-                           fecund = mx,
-                           N.init = N.start,
-                           pop.model = 'exponential',
-                           direction= 'forwards')
-
-   for.tuned.res[[i]] <- for.tunes
+   back.tune.all.res[[i]] <- fast.back.tune
+   back.tune.tmp <- data.frame(fast.back.tune$res,Stock = i)
+   back.tune.summary[[i]] <- back.tune.tmp
 
@@
 
+tst <- do.call('rbind',for.tune.summary)
+quantile(tst$per.diff,probs=seq(0.001,1,0.001),na.rm=T)
+# summary(tst$per.diff)
+# summary(tst$r)
+# tst <- tst[abs(tst$per.diff) > 5,]
+# 
+# range(tst$per.diff,na.rm=T)
+# It completed 33 stocks, was on stock 34
+saveRDS(back.tune.summary,"D:/Github/ICM/Results/backwards_fully_tuned_summary.Rds")
+saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary.Rds")
+saveRDS(back.tune.all.res,"D:/Github/ICM/Results/backwards_fully_tuned_all_res.Rds")
+saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res.Rds")
+
 ```

### 2023-10-16 Scripts/functions/Lotka_r.r

@@ -24,6 +24,7 @@ lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL
                   #                         4) if using the 'eggs' method to estimate fecundity. (L.inf,K, t0, a.fec.len,b.fec.len)
 ) 
 {
+  
   if(is.character(nat.mort)[1]) nm.c <- nat.mort else nm.c <- "Using data"
   if(is.character(fecund)[1]) fecund.c <- fecund else fecund.c <- "Using data"
   # Some warning messages if you didn't include something you needed...
@@ -52,7 +53,7 @@ lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL
   res <- data.frame(yrs = NA, r = NA)
   if(length(yrs) > 1) n.yrs <- length(yrs) else n.yrs <- 2 # Needs to be 2 if just doing it for one year to work how I have loop set up
   
-  
+ 
   if(sim == 'retro')
   {
   
@@ -72,7 +73,7 @@ lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL
     mat.ogive <- 1/(1+exp(-(mat.K)*(age.at.50.mat-ages)))
     
   } # end if(length(age.mat) == 1) 
-  
+ 
   # If you have given me the maturity ogive than rename it
   if(length(age.mat) > 1) 
   {
@@ -174,12 +175,13 @@ lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL
   # Or if we directly had an estimate of fecundity (number of recruits per individual)
   if(!is.character(fecund)) 
   { 
-
+   
     mx.t <- fecund
     spr <- NULL
     if(is.null(nrow(fecund))) mx.t <- rlnorm(length(mx.t),mx.t,sd.fecund)
     if(nrow(mx.t) > 1) for(m in 1:nrow(mx.t)) mx.t[m,] <- rlnorm(length(mx.t[m,]),as.numeric(log(mx.t[m,])),sd.fecund)
   }
+  #browser() 
   # remove columns associated with NAs in mx, and remove NAs from mx
   if(any(is.na(colSums(mx)))) {
     ages <- ages[-which(is.na(colSums(mx)))]
@@ -191,7 +193,7 @@ lotka.r<-function(yrs = 1,age.mat=4,nat.mort = NULL,ages = ages,wt.at.age = NULL
[…]

### 2023-10-16 Scripts/functions/simple_Lotka_r.r

@@ -1,0 +1,39 @@
+# Function to calculate Lotka R, DK revised this with several options of how we want to calculate
+
+# Function Arguments
+# nat.mort:    Natural mortality, 
+# fecund:      Fecundity
+# ages:
+
+simple.lotka.r<-function(nat.mort = NULL,fecund = NULL,ages = NULL) 
+{
+  
+  # The Euler-Lotka Function to optimize on to find the intrinsic rate of growth for your population
+  eulerlotka <- function(r) (sum(lx * mx * exp(-r * ages)) - 1)^2
+  # Set up a dataframe
+  res <- data.frame(r = NA)
+  
+  
+  
+  #################################### Calculate Lotka SECTION #################################### Calculate Lotka SECTION #################################### Calculate Lotka SECTION
+  mx.tmp <- NULL
+  lx.tmp <- NULL
+  
+  # Now run this through all the yrs 
+
+    # Get the r estimate for each year if we are running through a bunch of years
+    # Just use the first year if we don't have same length nat.mort as years
+    if(!is.null(nrow(nat.mort))) lx <- 1-exp(-nat.mort) else lx <- 1-exp(-nat.mort)
+    # Convert to survivorship vector
+    si <- 1-lx 
+    # Set the first age class to be 1
+    lx<-1
+    # And get cumulative survivorship for the stock
+    for(s in 2:(length(si))) lx[s]<-lx[s-1]*si[s-1]
+    mx <- fecund
+    # Now we are cooking!
+    junk<-optimize(lower=-0.999999,upper=15,f = eulerlotka)
+    res <- c(junk$minimum)
+
+  return(list(res=res,mx=mx,lx=lx,nat.mort = nat.mort,ages=ages))
+}

### 2023-10-16 Scripts/functions/tuning_sim.r

@@ -143,9 +143,9 @@ tune.sim<-function(years,step.size=0.05,tuner="m", n.steps = 30, direction = 'ba
     if(tuner != 'f') fecund.tmp <- fecund[y,]
     
     tmp.s <- NULL
-    tmp.l <- NULL
+    tmp.l <- NULL 
 
-    #browser()
+    
     
     for(ss in 1:n.steps)
     { 
@@ -173,6 +173,8 @@ tune.sim<-function(years,step.size=0.05,tuner="m", n.steps = 30, direction = 'ba
       
     
     } # end for(s in 1:ns.steps)
+    #browser() 
+    
     lotka.res[[as.character(years[y])]] <- tmp.l
     tmp.y[[as.character(years[y])]] <- do.call('rbind',tmp.s)
     print(paste0("Running lotka simulation " ,ss, ' for year ',years[y]))
@@ -202,11 +204,11 @@ tune.sim<-function(years,step.size=0.05,tuner="m", n.steps = 30, direction = 'ba
   lotka.final <- NULL
   # Setting up the output vector, more mind games here with the forwards and backwards methods.
   # want to make sure that the r value lines up with the population estimate that is relevant to it..
-  # i.e. when going forwards the 2020 r value is used to get the 2021 population estimate, so we line up the r in 2020 with the 2021 results, so here we give it a +1
+  # i.e. when going forwards the 2021 r value is used to get the 2021 population estimate, so we line up the r in 2021 with the 2021 results, 
   # i.e. when going backwards the 2020 populations r value is used to get us from the 2021 population to the 2020 population, so we line it up with 2020 since 2020 is the result
   # 
   r.out <- r.vec
-  if(direction == 'forwards') r.out$year <- r.out$year+1
+  #if(direction == 'forwards') r.out$year <- r.out$year+1
   
   for(y in y.index)
   {
@@ -221,12 +223,12 @@ tune.sim<-function(years,step.size=0.05,tuner="m", n.steps = 30, direction = 'ba
       
       for(ss in 1:n.steps)
       {
-        
-        # DK changed this to be y-1 in Oct 2023, because the population got to where it is from the year before r.  This might be why 
+        # DK has been waffling on this in Oct 2023, moved back to using y
[…]

### 2023-10-16 Scripts/functions/tuning_sim_fast.r

@@ -1,0 +1,328 @@
+# Here we take the ideas from the backwards projections but 'tune' them to the 'known' biomass by adjusting either the fecundity or survivorship variables iteratively until
+# the biomass in the current year is withing X% of the actual biomass.
+
+# All the data you need to make it dance...
+# years:          The years you are running the backwards calculation for
+# abund.ts:       The abundance time series from the assessment
+
+# tuner:          What are we tuning, the fecundity "f", or natural mortality 'm', or both 'b'
+# rems            Removals from the fishery in a given year.
+# step.size:      How big is the difference (proportional) in the simulation step.  Default = 0.05 which is about a 5% change for each step
+
+# direction       Allow for forwards and backwards simulations
+# What we need for the Lotka.r function...
+# fecund:      How are you estimating fecundity. If a vector it is the number of recruits produced by the average individual in the age classes. 
+#              If a matrix the rows are different simulations. Also have options to set fecund = 'eggs' which we can use if we can get an estimate of egg mortality
+#              fecund = 'SPR' uses the spawner per recruit metric, to get this to work we need to know how many recruits there are in a given year
+#              We could also let this vary by year, but we'll need to go 3-D array or something for that
+# nm:             Natural mortality, this wants the instantaneous natural mortality, not the proportional. There are several options here....
+#                 You can enter a vector of instantaneous natural moralities, just put a single number of all ages, or put in a character
+#                 string that will tell the function to calculate the natural mortality based on life history data. If a matrix the rows are different simulations
+#                 we could also let this vary by year, but we'll need to go 3-D array or something for that
+# ages:       Ages...
+
+
+fast.tunes<-function(years,step.size=0.05,tuner="m",  direction = 'backwards',ages = NULL,
+                   nm=NULL,fecund = NULL,N.init = NULL,abund.ts = NULL, rems)
+{
+  # Download the function to go from inla to sf
[…]

### 2023-10-24 Scripts/ASR_stocks.Rmd
Tuning fixes completed
Everything appears to be working A-OK now, last big fix was fixing the r value coming from the Euler-Lotka model, it needs to be exp(r) to make it = lambda, then simply used lambda in the models

@@
 library(cowplot)
-loc <- 'C:/Users/Owner/Documents/GitHub/ICM'
+loc <- 'D:/GitHub/ICM'
 
 source(paste0(loc,"/Scripts/functions/backwards_sim.R"))
+source(paste0(loc,"/Scripts/functions/forward_sim.R"))
 source(paste0(loc,"/Scripts/functions/tuning_sim.R"))
@@
   # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
-  # This works because 'males' is also in 'females'
-  if(grepl("males",i)) data$mx <- data$recs.per.age/data$ssn.offset 
-  if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
+  # No longer dividing by 2 because we should really divide recruits and ssn by 2 to be female only, but that's pointless so we roll along with this.
+  data$mx <- data$recs.per.age/data$ssn.offset # if(grepl("males",i)) 
+  #if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
   data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
@@
 
+  # The first run gives us the mean estimate, I think that's all we need for our first paper
   tst <- back.sim(years,
@@
                  pop.model = 'exponential',
-                 n.sims = 50,
+                 n.sims = 100,
                  sd.mat = 0.5,
@@
 # ################# Now run as a forward simulation
-#   N.start <- vpa.abund[1] 
-# 
-#   tst <- for.sim(years,
-#                  mat.age = age.mat,
-#                  nm = -(log(1-prop.nat.mort)),
-#                  w.age = weight.age,
-#                  ages = ages,
-#                  rems = rem$rem, # rep(0,nrow(rem)),
-#                  fecund = mx,
-#                  N.start = N.start,
-#                  pop.model = 'exponential', K = 2e6,
-#                  n.sims = 2,
-#                  sd.mat = 0.5,
-#                  sd.nm = 0.5,
-#                  sd.wt = 0.5,
-#                  sd.fecund = 0.5)
-# 
-#   #Combine the data
-#   did.it.work <- data.frame(abund = c(vpa.abund,tst$Pop$abund),years = c(years,tst$Pop$years),sim = c(rep('VPA',length(years)),tst$Pop$sim))
-#   # Here get the Upper and lower 50% quantiles to make a functional boxplot
-#   quants <- did.it.work %>% dplyr::filter(sim != "VPA") %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
-#                                                                         med = median(abund),
-#                                                                         U.50 = quantile(abund,probs=c(0.75)))
-# 
-#   for.res[[i]] <- tst
-#   for.ts[[i]] <- did.it.work
-#   for.ts.quants[[i]] <- quants
+N.start <- vpa.abund[1]
 
-# ########################## Now run the tuning sims
-# #
-#    N.end <- vpa.abund[length(vpa.abund)]
-#    tunes <- tune.sim(years,
-#                      n.steps = 100,
-#                      abund.ts = vpa.abund,
-#                      mat.age = age.mat,
-#                      nm = -(log(1-prop.nat.mort)),
-#                      w.age = weight.age,
-#                      ages = ages,
-#                      rems = rem$rem,
-#                      fecund = mx,
-#                      N.end = N.end,
-#                      pop.model = 'exponential')
-# 
-#    tuned.res[[i]] <- tunes
-} # end i in Stocks look
+tst <- for.sim(years,
+               mat.age = age.mat,
+               nm = -(log(1-prop.nat.mort)),
+               w.age = weight.age,
+               ages = ages,
+               rems = rem$rem, # rep(0,nrow(rem)),
+               fecund = mx,
+               N.start = N.start,
+               pop.model = 'exponential',
+               n.sims = 100,
+               sd.mat = 0.5,
+               sd.nm = 0.5,
+               sd.wt = 0.5,
+               sd.fecund = 0.5)
+
+  #Combine the data
+  did.it.work <- data.frame(abund = c(vpa.abund,tst$Pop$abund),years = c(years,tst$Pop$years),sim = c(rep('VPA',length(years)),tst$Pop$sim))
+  # Here get the Upper and lower 50% quantiles to make a functional boxplot
+  quants <- did.it.work %>% dplyr::filter(sim != "VPA") %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
+                                                                        med = median(abund),
+                                                                        U.50 = quantile(abund,probs=c(0.75)))
+
+  for.res[[i]] <- tst
+  for.ts[[i]] <- did.it.work
+  for.ts.quants[[i]] <- quants
+
+}
 
@@
 saveRDS(object = back.ts.quants,file = paste0(loc,"/Results/backwards_sim_ts_quantiles_summaries.Rds"))
+saveRDS(object = for.res,file = paste0(loc,"/Results/forwards_sim_results.Rds"))
+saveRDS(object = for.ts,file = paste0(loc,"/Results/forwards_sim_ts_summaries.Rds"))
+saveRDS(object = for.ts.quants,file = paste0(loc,"/Results/forwards_sim_ts_quantiles_summaries.Rds"))
+
 ```
@@
 # Now we can run the figures separately.
-tuned.res <- readRDS(file = "D:/Github/ICM/Results/tuned_fits.Rds")
+# tuned.res <- readRDS(file = "D:/Github/ICM/Results/tuned_fits.Rds")
 back.ts <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")

### 2023-10-24 Scripts/Paper_1.Rmd
Tuning fixes completed
Everything appears to be working A-OK now, last big fix was fixing the r value coming from the Euler-Lotka model, it needs to be exp(r) to make it = lambda, then simply used lambda in the models

@@
 #Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
-
+#i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
 years.tmp <- NULL
@@
   if(i == "ICES-AFWG_COASTNOR 1-2_Gadus_morhua") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 2006)
-  if(i == "NEFSC_5Z_Pseudopleuronectes_americanus")ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)
+  if(i == "NEFSC_5Z_Pseudopleuronectes_americanus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)
+  if(i == "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1989)
 
@@
   nm.tmp <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
+
   #minage
@@
   maxage <- max(as.numeric(nm.tmp$age[!is.na(nm.tmp$NM)]))
+
+  # Now get the number of individuals in the youngest age category
+  num.age.min <- ASR_sub %>% dplyr::filter(age==minage,type=="Num")
+  # So any Recruitment even that is > 3 SE's away from the median I'm calling 
+  # an 'extreme' recruitment event and it is going to get a lower/higher natural mortality term.
+  med.mun.age.min <- mean(num.age.min$value,na.rm=T)
+  sd.mun.age.min <- sd(num.age.min$value,na.rm=T)#/sqrt(length(na.omit(num.age.min$value)))
+  low.rec <- med.mun.age.min - 2*sd.mun.age.min
+  high.rec <- med.mun.age.min + 2*sd.mun.age.min
+  high.rec.years <- as.vector(na.omit(num.age.min$Year[num.age.min$value > high.rec]))
+  low.rec.years <- as.vector(na.omit(num.age.min$Year[num.age.min$value < low.rec]))
   # Set up the full abundance matrix 
   full.abund <- abund
+  print(paste0("Stock ", i , ' high recruit years include ', length(c(low.rec.years,high.rec.years)), ' years'))
   # If we need to imput some data run this loop for natural mortality
@@
     nm.res <- NULL
+    # These already have NM estimates at 0 so don't need to do them...
     if(!i %in% c("ICES-WGCSE_CS7e-k_Gadus_morhua","ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus",
@@
     {
-      for(y in 1:(length(yrs)))
-      {
-        tmp <- nm.tmp %>% dplyr::filter(Year == yrs[y])
-        tmp.abund <- abund %>% dplyr::filter(Year == yrs[y])
-        min.nm <- tmp$NM[tmp$age == minage]
-        tmp$NM[as.numeric(tmp$age) < minage] <- min.nm
-        # Now save these mudders...
-        nm.res[[y]] <- tmp
-      } # end years loop
-      nat.mort <- do.call('rbind',nm.res)
-    }
+      # Just use the mean mortality of the youngest age class we have information for
+      nm.use <- mean(nm.tmp$NM[nm.tmp$age==minage],na.rm=T)
+      # Take the average natural mortality of the youngest age class with an m and use that
+      # This avoids really blowing up the abundance in the younger age classes which can get a bit squirrly
+      # nm.high.rec <- 0.5*(min(nm.tmp$NM[nm.tmp$age==minage],na.rm=T))
+      # nm.low.rec <-  1.5*(max(nm.tmp$NM[nm.tmp$age==minage],na.rm=T))
+      # Start by filling in everything...
+      nm.tmp$NM[is.na(nm.tmp$NM)] <- nm.use
+      nm.tmp <- nm.tmp[nm.tmp$age %in% 0:maxage,]
+      # Now we need to fill in the 'special' cohorts that were really big (low m) or really small (high m)
+      # for(y in length(yrs):1)
+      # {
+      #   if(yrs[y] %in% c(high.rec.years,low.rec.years))
+      #   {
+      #     if(yrs[y] %in% high.rec.years) nm.pick <- nm.high.rec
+      #     if(yrs[y] %in% low.rec.years) nm.pick <- nm.low.rec
+      #     for(a in minage:1) nm.tmp$NM[nm.tmp$Year == (yrs[y]-a) & nm.tmp$age == minage-a] <- nm.pick
+      # }} #Close the if and for loops
+      # Pointless rename...
+    } #end the skip the stocks with nm at 0 if
+      nat.mort <- nm.tmp
+
   # Now do the same loopiness for abundance
@@
 
-      # for(a in (minage-1):0)
-      # {
-      #   start.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == a+1) %>% dplyr::pull(Num)
-      #   nm.calc <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][a+1,]$NM) 
-      #   full.abund[full.abund$Year ==yrs[y]-1,][a+1,]$Num <- start.abund/(1-nm.calc)
-      # }
-
-        #if(minage >1 & y == 1)
-        #{
            # The lowest minage =4, This goes first since we go backwards, this gets us age 3 in year 3
@@
   all.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
-  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::filter(age >= minage) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
+  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::filter(age %in% minage:maxage) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
   # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
@@
 
-  #r.p.ssb This no longer needs any offset...
+  #r.p.ssb So we are assuming the SSB in year X produces the observed recruits in year X
   annual$r.p.ssb <- annual$recruits/annual$tot.ssb
@@
   # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
-  # This works because 'males' is also in 'females'
-  if(grepl("males",i)) data$mx <- data$recs.per.age/data$ssn 
-  if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn/2 # Moms only! 
+  # The demographic models are 'female' only, so we'd want to divide the number of recruits by 2 and the SSN by 2, but that just cancels out
+  # so there is no need to make the mom adjustment.
+  data$mx <- data$recs.per.age/data$ssn # if(grepl("males",i))
+  # if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn/2 # Moms only! 
   data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
-  # Easier to remove the years where we don't have recs.per.age...
-  #data <- data %>% dplyr::filter(Year %in% years[(minage+1):length(years)])
-  # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...
+  # Now for the very high recruitment years allow for a small amount of recruitment (20% of the lowest age) in the age classes after year 0....
+
+  # if(length(high.rec.years) > 0)
+  # {
+  #   for(y in high.rec.years)
+  #   {
+  #     tmp <- data$AM[data$Year == y]
+  #     am.fill <- which(tmp ==0) 
+  #     if(length(am.fill) > 1) data$mx[data$Year == y-1][am.fill[-1]] <- 0.2*min(data$mx[data$Year == y & data$mx > 0],na.rm=T)
+  #   }
+  # }
 
@@
 
+#DK PICK IT UP HERE#
+# OK So the problem isn't so much "high" recruitment events, it's years in which the population abundance jumps like crash, Stock 57 (ICES Haddock NS)
+# Is the best example, look at year 2005, it isn't a outlier in terms of numbers of recruits, but the population jump from 2004 to 2005 is huge and
+# thus it's those years that get us the crazy fecundity numbers, which can easily be ameliorated by having a small fecundity in the age classes
+# that aren't supposed to be mature yet.  Of course, is that BS, maybe!!  Ended the night running all the stocks trying to see what the changes so far brought about.
+
 back.tune.all.res <- NULL
@@
 
-tst <- do.call('rbind',for.tune.summary)
-quantile(tst$per.diff,probs=seq(0.001,1,0.001),na.rm=T)
+#tst <- do.call('rbind',for.tune.summary)
+#quantile(tst$per.diff,probs=seq(0.001,1,0.001),na.rm=T)
 # summary(tst$per.diff)
@@
 ```
+
+```{r paper-other-metrics}
+
+# So we agreed we wanted to look at cod, haddock, herring, and sole using the forward tuning sceanrios...
+
+for.tune.summary <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_summary.Rds")
+for.tune.all <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_all_res.Rds")
+
+cod <- grep("morhua",names(for.tune.summary))
+haddock <- grep('aeglefinus',names(for.tune.summary))
+herring <- grep("harengus",names(for.tune.summary))
+pollock <- grep("virens",names(for.tune.summary)) 
+sole <- grep("solea",names(for.tune.summary))
+euro.plaice <- grep("platessa",names(for.tune.summary))
+am.plaice <- grep("platessoides",names(for.tune.summary))
+
+p1.stocks <- sort(c(cod,haddock,herring,pollock,sole,euro.plaice,am.plaice))
+
+Stocks <- names(for.tune.summary)
+n.stocks <- length(Stocks)
+
+for.tune.stocks <- NULL
+for(i in p1.stocks) 
+{
+  nam <- Stocks[i]
+  #  A quick way to get the other potentially interesting info for the stock...
+  meta <- ASR_long[ASR_long$Stock == nam,][1,]
+  tmp <- for.tune.summary[[nam]]
+  tmp$Management   <- meta$Management  
+  tmp$Area <- meta$Area
+  tmp$Order <- meta$Order
+  tmp$Family   <- meta$Family  
+  tmp$Genus  <- meta$Genus 
+  tmp$Species <- meta$Species
+  tmp$Model <- meta$Model
+  tmp$Meeting_or_reference <- meta$Meeting_or_reference
+  tmp$Notes <- meta$Notes
+  for.tune.stocks[[nam]] <- tmp
+}
+
+# Now unpack them...
+for.tunes <- do.call("rbind",for.tune.stocks)
+# Typo clean up...
+for.tunes$Species[for.tunes$Species==" harengus"] <- "harengus"
+# Now what does this look like...
+paper.stocks <- unique(for.tunes$Stock)
+
+# Now the doubling time simulations for each stock
+
+dt.res <- NULL
+for(i in paper.stocks)
+{
+  try <- for.tunes %>% dplyr::filter(Stock == i)
+  double.time <- NA
+  pop <- 1000
+
+for(s in 1:100)
+{
+for(y in 2:100)
+{
+  r <- sample(na.omit(try$r),size=1)
+  pop[y] <- (1+r)*pop[y-1]
+} # end the years loop
+tmp <- which(pop >= 2*pop[1])[1]
+
+if(is.na(tmp)) double.time[s] <- 0
+if(!is.na(tmp))double.time[s] <- tmp
+} # end sim loop
+
+dt.res[[i]] <- data.frame(dt = double.time,Stock = i,Species = try$Species[1])
+
+} # end Stocks loop
+
+dub.time <- do.call("rbind",dt.res)
+
+# Now to get generation lengths + reproductive rates....
+# First I need to get the fecundity and natural mortalities by cohort instead of year.
+
+res.fin <- NULL
+res.year.fin <- NULL
+for(i in paper.stocks)
+{
+tst <- for.tune.all[[i]]
+f.tmp <- tst$fecund.opt
+m.tmp <- exp(-tst$nm.opt)
+f.org.tmp <- tst$fecund.org
+m.org.tmp <- exp(-tst$nm.org)
+
+ages <- 0:(ncol(f.tmp)-1)
+n.ages <- length(ages)
+years <- tst$res$year
+n.years <- length(years)
+# Now I need to grab the fecundities and nat morts by cohort
+if(n.years > n.ages)
+{
+res.cohort <- NULL
+res.year <- NULL
+for(y in 1:(n.years-n.ages+1))
+{
+  count = 0
+  fs <- NA
+  lx <- 1
+  fs.org <- NA
+  lx.org <- 1
+  lx.year <- 1
+  for(a in 1:n.ages)
+  {
+  fs[a] <- f.tmp[y+count,a]  
+  fs.org[a] <- f.org.tmp[y+count,a]  
+  if(a > 1) 
+  {
+    lx[a] <- lx[a-1] * m.tmp[y+count,a]  
+    lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
+    lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
+  }  # end the a > 1 if
+  count <- count + 1
+  }# end the ages loop
+  res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,lx.org = lx.org,age = ages,
+                         mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
+                         x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
+                         cohort=years[y],Stock = i)
+
+  res.year[[y]] <- data.frame(mx.opt = unlist(f.tmp[y,]),lx.opt = lx.year,age = ages,
+                         mx.lx.opt = unlist(f.tmp[y,])*lx.year,
+                         x.mx.lx.opt = unlist(f.tmp[y,])*lx.year*ages,
+                         year=years[y],Stock = i)
+
+} # end the years loop
+
+# unpack it...
+res.fin[[i]] <- do.call('rbind',res.cohort)
+res.year.fin[[i]] <- do.call('rbind',res.year)
+}  # end if to make sure we have enough data to get the cohort estimates.
+
+}# end the stock loop
+res.cohort.final <- do.call('rbind',res.fin)
+res.year.final <- do.call('rbind',res.year.fin)
+
+pop.dam <- res.cohort.final %>% dplyr::group_by(cohort,Stock) %>% dplyr::summarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
+                                                                gen.len.org = sum(x.mx.lx.org)/sum(mx.lx.org),
+                                                                R0.opt = sum(mx.lx.opt),R0.org = sum(mx.lx.org))
+pop.dam <- data.frame(pop.dam,Management=NA,Area = NA,Order=NA,
+                      Family=NA,Genus=NA,Species=NA,Model=NA,Meeting_or_reference = NA,Notes = NA)
+
+for(i in p1.stocks) 
+{
+  nam <- Stocks[i]
+  #  A quick way to get the other potentially interesting info for the stock...
+  meta <- ASR_long[ASR_long$Stock == nam,][1,]
+
+  pop.dam$Management[pop.dam$Stock == nam]   <- meta$Management  
+  pop.dam$Area[pop.dam$Stock == nam] <- meta$Area
+  pop.dam$Order[pop.dam$Stock == nam] <- meta$Order
+  pop.dam$Family[pop.dam$Stock == nam]   <- meta$Family  
+  pop.dam$Genus[pop.dam$Stock == nam]  <- meta$Genus 
+  pop.dam$Species[pop.dam$Stock == nam] <- meta$Species
+  pop.dam$Model[pop.dam$Stock == nam] <- meta$Model
+  pop.dam$Meeting_or_reference[pop.dam$Stock == nam] <- meta$Meeting_or_reference
+  pop.dam$Notes[pop.dam$Stock == nam] <- meta$Notes
+
+}
+
+pop.dam$Species[pop.dam$Species==" harengus"] <- "harengus"
+
+hmm <- pop.dam %>% dplyr::filter(R0.opt > 500)
+
+hmm
+
+hmm[hmm$Stock == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",]
+for.tune.all$`ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus`$res
+
+unique(hmm$Stock)
+# There are 7 stocks with some bat shit happening...
+# Fixed... "ICES-WGNSSK_NS4 _Solea_solea"
+
+# These are all problems because the abundance increases like nuts in a few years....
+"ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus"
+"ICES-WGCSE_CS7e-k_Gadus_morhua"                  
+"ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus" # Something special weird going on with this stock
+"ICES-WGBFAS_WBS-25-32_Gadus_morhua"
+
+# Figure out how to get an r of 10 and what the mx vector needs to look like for
+#"ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus"
+
+ages <- 0:12 # ages
+mx <- c(0.9,500,500,rep(5000,10)) # fecundity
+nat.mort <- rep(0.2,13) # natural mortality
+si <- 1- nat.mort # survivial
+
+lx <- 1
+for(s in 2:(length(si))) lx[s]<-lx[s-1]*si[s-1]
+
+eulerlotka <- function(r) (sum(lx * mx * exp(-r * ages)) - 1)^2
+
+junk<-optimize(lower=-0.999999,upper=55,f = eulerlotka)
+res <- c(junk$minimum)
+res
+
+p.start <- 10
+
+p.end <- (1+res)*p.start
+p.end
+
+R0 <- sum(lx*mx)
+R0
+
+tmp <- for.tune.all[["ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus"]]
+tmp$nm.org
+tmp$fecund.opt
+t1 <- vpa.tmp$`ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus`
+range(t1[2:length(t1)]/t1[1:(length(t1)-1)])
+# So using all the age classes actually reduces the ratios from year to year requiring less insanity...
+t2 <- all.abund.tmp$`ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus`
+range(t2[2:length(t2)]/t2[1:(length(t2)-1)])
+
+data.frame(tmp$res$year,tmp$res$vpa.abund,t1,t2)
+
+mx <- c(0,0,0,rep(30,11))
+nm <- rep(0.2,14)
+
+```
+
+```{r simp-figs}
+
+ggplot(for.tunes) + geom_jitter(aes(y=r,x=Species)) + scale_y_continuous(name = 'rate of growth (r)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))
+
+ggplot(for.tunes) + geom_jitter(aes(y=r.vpa.init,x=Species)) + scale_y_continuous(name = 'rate of growth (r)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))
+
+unique(for.tunes$Species)
+windows(11,11)
+ggplot(dub.time) + geom_jitter(aes(y=dt,x=Species),alpha=0.05,fill="black",color="black",shape=22) + 
+                   scale_y_continuous(name = 'Doubling time (years)',breaks = seq(0,100,by=5))
+
+ggplot(for.tunes) + geom_density(aes(r,group=Species,color=Species,fill=Species),alpha = 0.2)
+
+windows(11,11)
+ggplot(pop.dam) + geom_boxplot(aes(y=gen.len.opt,x=Species)) + ylab("Generation Length (years)")
+
+options(scipen=999)
+ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Species))  + scale_y_log10(name = "Lifetime Reproductive Output",
+                                                                         breaks = c(0.001,0.01,0.1,1,5,10,50,100,500,1000,5000,1e4,1e5,1e6),
+                                                                         minor_breaks = NULL)
+
+```

### 2023-10-24 Scripts/Leslie_vs_lotka.R

@@ -1,0 +1,54 @@
+# Two functions to start the festivities...
+# The eulerlotka function
+eulerlotka <- function(r) (sum(lx * mx * exp(-r * ages)) - 1)^2
+# And it's friend to get the eigen values from a Leslie Matrix
+
+eigenfun<- function(A)
+{
+  # Get the eigen values
+  lambdas <- eigen(A)
+  lmax <- which(Re(lambdas$values) == max(Re(lambdas$values)))
+  lmax <- lmax[1]
+  # Grab the largest eigenvalue
+  lambda1 <- Re(lambdas$values[lmax])
+  return(list(lambda1=lambda1,lambdas = lambdas)) # this output the variables of interest for future fun
+}
+
+ages <- 1:10 # ages
+mx <- c(0,0,rep(0.25,8)) # fecundity
+nat.mort <- rep(0.89,10) # natural mortality
+
+si <- 1-nat.mort # Survivorship
+# Turn this into a Leslie matrix...
+Leslie <- matrix(data = 0,nrow=10,ncol=10)
+Leslie[1,] <- mx
+for(i in 1:9) Leslie[i+1,i] <- si[i]
+#Leslie[10,10] <- si[10] 
+# If you set it to 0 then everyone dies at age 10, which is fine too, doesn't make much difference here.
+Leslie[10,10] <- 0
+# Get the lx matrix for Euler-Lotka
+lx <- 1
+for(s in 2:(length(si))) lx[s]<-lx[s-1]*si[s-1]
+
+# Now solve the Euler-lotka add 1 to make it lambda
+junk<-optimize(lower=-15,upper=15,f = eulerlotka)
+res <- c(junk$minimum)
+lambda.euler <- exp(res) # exp you fool!!
+lambda.euler
+
+# Now solve your Leslie matrix
+res.leslie <- eigenfun(Leslie)
+lambda.leslie <- res.leslie$lambda1
+lambda.leslie
+
+ages <- 0:8
+nat.mort <- c(2.4,2.4,2.4,1.4,0.85,0.75,0.51,0.43,0.39)
+mx <- c(0,0,0,9,14,23,22,23,37)
+si <- exp(-nat.mort) # Survivorship
+lx <- 1
+for(s in 2:(length(si))) lx[s]<-lx[s-1]*si[s-1]
+
+# Now solve the Euler-lotka add 1 to make it lambda
+junk<-optimize(lower=-15,upper=15,f = eulerlotka)
+res <- c(junk$minimum)
+res

### 2023-10-24 Scripts/functions/backwards_project.r

@@ -23,10 +23,10 @@ back.proj <- function(option = "exponential",pop.next,r,removals.next,K,fishery.
     {
     # Going to 1+r model since we are discrete time...
     #Pop.current <- (pop.next)/(exp(r))
-    Pop.current <- (pop.next)/(1+r)
+    Pop.current <- (pop.next)/(exp(r))
     Pop.current<- Pop.current+removals.next 
     }
-    if(fishery.timing =='end') Pop.current <- (pop.next+removals.next)/((1+r)) #  (pop.next+removals.next)/(exp(r))
+    if(fishery.timing =='end') Pop.current <- (pop.next+removals.next)/((exp(r))) # (pop.next+removals.next)/(exp(r))
   }
   # Logistic growth model, 
   # The maths be.... N(t+1) = N(t) + rN(t)(1-N(t)/K).... now we are solving for N(t) not N(t+1), so we rearrange terms
@@ -43,8 +43,8 @@ back.proj <- function(option = "exponential",pop.next,r,removals.next,K,fishery.
     # Ha, we can use this to solve for N in the previous year 
     #I'm hung up on which of these to use, they give almost the same answer, but not quite, but going with the 1+r version since
     # we are in discrete time here.
-    #logistic.n.last <- function(N.last) sum((exp(r)* ((N.last)/(1-(N.last/K))) / (1 + ( ((N.last)/(1-(N.last/K)))*exp(r))/K) - pop.next))^2
-    logistic.n.last <- function(N.last) sum(((1+r)* ((N.last)/(1-(N.last/K))) / (1 + ( ((N.last)/(1-(N.last/K)))*(1+r))/K) - pop.next))^2
+    logistic.n.last <- function(N.last) sum((exp(r)* ((N.last)/(1-(N.last/K))) / (1 + ( ((N.last)/(1-(N.last/K)))*exp(r))/K) - pop.next))^2
+    #logistic.n.last <- function(N.last) sum(((1+r)* ((N.last)/(1-(N.last/K))) / (1 + ( ((N.last)/(1-(N.last/K)))*(1+r))/K) - pop.next))^2
     
     # Solve the above function
     Pop.current <- optimx(par, logistic.n.last, method = "BFGS")$p1

### 2023-10-24 Scripts/functions/forward_project.r

@@ -17,10 +17,10 @@ for.proj <- function(option = "exponential",pop.last,r,removals.next,K,fishery.t
   {
     if(fishery.timing == 'end')
     {
-    Pop.current <- (pop.last)*((1+r))
+    Pop.current <- (pop.last)*((exp(r)))
     Pop.current<- Pop.current-removals.next  
     }
-    if(fishery.timing =='beginning') Pop.current <- (pop.last-removals.next)*((1+r))
+    if(fishery.timing =='beginning') Pop.current <- (pop.last-removals.next)*((exp(r)))
   }
   # Logistic growth model, 
   # The maths be.... N(t+1) = N(t) + rN(t)(1-N(t)/K).... now we are solving for N(t) not N(t+1), so we rearrange terms
@@ -35,7 +35,7 @@ for.proj <- function(option = "exponential",pop.last,r,removals.next,K,fishery.t
     if(fishery.timing == 'end') par <- pop.last
     if(fishery.timing == 'beginning') par <- pop.last <- pop.last - removals.next
     # Get the current population size using logistic model
-    Pop.current <-  pop.last + (r* pop.last)*(1-(pop.last/K)) 
+    Pop.current <-  (exp(r)* pop.last)*(1-(pop.last/K)) 
     # If the fishery removes individuals at the start of the time series add them in here.
     if(fishery.timing == 'end') Pop.current <- Pop.current - removals.next
   }

### 2023-10-24 Scripts/functions/simple_Lotka_r.r

@@ -32,7 +32,8 @@ simple.lotka.r<-function(nat.mort = NULL,fecund = NULL,ages = NULL)
     for(s in 2:(length(si))) lx[s]<-lx[s-1]*si[s-1]
     mx <- fecund
     # Now we are cooking!
-    junk<-optimize(lower=-0.999999,upper=15,f = eulerlotka)
+    #browser()
+    junk<-optimize(lower=-15,upper=15,f = eulerlotka)
     res <- c(junk$minimum)
 
   return(list(res=res,mx=mx,lx=lx,nat.mort = nat.mort,ages=ages))

### 2023-10-24 Scripts/functions/tuning_sim_fast.r

@@ -40,14 +40,15 @@ fast.tunes<-function(years,step.size=0.05,tuner="m",  direction = 'backwards',ag
   }
   
   source("D:/Github/ICM/Scripts/functions/simple_Lotka_r.r")
-  
+  source("D:/Github/ICM/Scripts/functions/forward_project.r")
+  source("D:/Github/ICM/Scripts/functions/backwards_project.r")
   
   require(optimx)  || stop("Please load the 'optimx' package which you'll need for the optimations to run")
   
  
   #Initialize a bunch of objects
   n.years<-length(years)
-  res <- data.frame(year = years,vpa.abund = N.init, est.abund = NA, diff= NA,per.diff = NA,r=NA,r.vpa.init = NA,
+  res <- data.frame(year = years,vpa.abund = N.init, est.abund = NA, diff= NA,per.diff = NA,lambda=NA,lambda.vpa.init = NA,
                     removals = NA,mean.fec=NA,mean.vpa.fec = NA,mean.nm = NA,mean.vpa.nm = NA)
   fecund.ts <- data.frame(fecund)
   nm.ts <- data.frame(nm)
@@ -85,11 +86,11 @@ fast.tunes<-function(years,step.size=0.05,tuner="m",  direction = 'backwards',ag
     r.est = lotka.est$res
     
     # For extremes, get away from that bad estimate area fast as it is numerical instability territory!
-    if(r.est < -0.995) 
-    {
-      fecund.tmp <- 1.5*fecund.tmp
-      nm.tmp <- nm.tmp/1.5
-    }
+    # if(r.est < -0.995) 
+    # {
+    #   fecund.tmp <- 1.5*fecund.tmp
+    #   nm.tmp <- nm.tmp/1.5
+    # }
     # Then we run the model 1 year (either backwards or forwards) and see how well it fits.
     
     if(direction == 'backwards')
@@ -165,7 +166,7 @@ fast.tunes<-function(years,step.size=0.05,tuner="m",  direction = 'backwards',ag
         } # end if(direction == 'forwards')
         
        
-        
+        #browser()
         if(abs(per.diff.inc) < abs(per.diff.dec))
         {
           going <- 'up'
@@ -215,7 +216,7 @@ fast.tunes<-function(years,step.size=0.05,tuner="m",  direction = 'backwards',ag
             }
           }
           
-          
+          #browser()
[…]

### 2023-11-20 Scripts/Paper_1.Rmd
Built in a Fecundity-mortality simulation
Now have simulations running.  This is absolutely for sure the final version of the tuning simulations we'll need, until tomorrow.

@@
 
+# Something is weird with the mentella stock, I'm going to drop it...
+ASR_long <- ASR_long %>% dplyr::filter(Stock != "ICES-AFWG_DEEP1-2_Sebastes_mentella")
+
 ```
@@
 full.abund.tmp <- NULL
+full.rem.tmp <- NULL
+fs.tmp <- NULL
 for(i in Stocks)
@@
   mx <- data %>% dplyr::select("Year", "age", "mx") %>% pivot_wider(names_from=age, values_from = mx) %>% dplyr::select(-Year) %>% as.data.frame()
+  abund.age <- data %>% dplyr::select("Year", "age", "Num") %>% pivot_wider(names_from=age, values_from = Num) %>% dplyr::select(-Year) %>% as.data.frame()
+  # Now we can save out the catch and get an instantaneous F
+  data$Catch[is.na(data$Catch)] <- 0
+  data$Exp <- data$Catch/data$Num
+  # If it is exactly 1 that leads to an Inf, which is annoying, so make it 1.1 and fix it with the rest below
+  data$Exp[data$Exp == 1] <- 1.1
+  # And make this an F
+  data$Fs <- -log(1-data$Exp)
+  if(any(is.na(data$Fs)))
+  {
+    fixers <- which(is.na(data$Fs))
+    print(paste0("Had to replace ",length(fixers), ' exploitation rates for stock ',i))
+    for(f in fixers)
+    {
+      yr <- data$Year[f]
+      fs <- max(data$Fs[data$Year == yr],na.rm=T)
+      data$Fs[f] <- fs
+      data$Exp[f] <- 1-exp(-fs)
+    }
+  }
 
-  # Dealing with some annoying NAs...
-  # if(i == "AFSC_BSAI-Males_Pleuronectes_quadrituberculatus")
-  # {
-  #   age.mat[length(years),] <- age.mat[length(years)-1,]
-  #   prop.nat.mort[length(years),] <- prop.nat.mort[length(years)-1,]
-  #   weight.age[length(years),] <- weight.age[length(years)-1,]
-  #   mx[length(years),13:23] <- mx[length(years),12]
-  # }
-  # 
+  full.rems <- data %>% dplyr::select("Year", "age", "Catch") %>% pivot_wider(names_from=age, values_from = Catch) %>% dplyr::select(-Year)
+  full.Fs <-  data %>% dplyr::select("Year", "age", "Fs") %>% pivot_wider(names_from=age, values_from = Fs) %>% dplyr::select(-Year)
+
   if(i == "DFO_2J3KL_Gadus_morhua")
@@
     mx[15,12] <- mx[15,11]
+    full.Fs[12:14,11:12] <- full.Fs[12:14,10]
+    full.Fs[15,12] <- full.Fs[15,11]
+    abund.age[12:14,11:12] <- abund.age[12:14,10]
+    abund.age[15,12] <- abund.age[15,11]
+    # I could calculate, but this will get us to the same place...
+    full.rems[12:14,11:12] <- full.rems[12:14,10]
+    full.rems[15,12] <- full.rems[15,11]
   }
@@
     mx[6:7,12] <- mx[6:7,11]
+    full.Fs[6:7,12] <- full.Fs[6:7,11]
+    abund.age[6:7,12] <- abund.age[6:7,11]
+    full.rems[6:7,12] <- full.rems[6:7,11]
   }
@@
     mx[30,9] <- mx[30,8]
+    full.Fs[30,9] <- full.Fs[30,8]
+    abund.age[30,9] <- abund.age[30,8]
+    full.rems[30,9] <- full.rems[30,8]
   }
@@
     mx[c(14,27,40),7] <- mx[c(14,27,40),6]
+    full.Fs[c(14,27,40),7] <- full.Fs[c(14,27,40),6]
+    abund.age[c(14,27,40),7] <- abund.age[c(14,27,40),6]
+    full.rems[c(14,27,40),7] <- full.rems[c(14,27,40),6]
   }
@@
   all.abund.tmp[[i]] <- all.abund
-  full.abund.tmp[[i]] <- full.abund
+  full.abund.tmp[[i]] <- abund.age
   am.tmp[[i]] <- age.mat
   mr.tmp[[i]] <- missing_rem
+  fs.tmp[[i]] <- full.Fs
+  full.rem.tmp[[i]] <- full.rems
 } #end input data loop
 
-save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,am.tmp,Stocks,ASR_stocks,ASR_long,all.abund.tmp,full.abund.tmp,file =  paste0(loc,"/Results/model_inputs_all_ages.Rdata"))
+save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,am.tmp,Stocks,ASR_stocks,ASR_long,all.abund.tmp,full.abund.tmp,fs.tmp,full.rem.tmp,file =  paste0(loc,"/Results/model_inputs_all_ages.Rdata"))
 
@@
   prop.nat.mort <- pnm.tmp[[i]] 
-  rem <- rem.tmp[[i]] 
+  #rem <- rem.tmp[[i]] 
   mx <- mx.tmp[[i]] 
@@
   all.abund <- all.abund.tmp[[i]]
+  fs <-fs.tmp[[i]]
+  full.rem <- full.rem.tmp[[i]]
+  full.abund <- full.abund.tmp[[i]]
+  #all.abund <- full.abund.tmp[[i]]
   #N.end <- vpa.abund[length(vpa.abund)]
+  #Pick your step size
+  ss.size <- 0.01
+  sensistive.stocks <- c("ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
+                          "ICES-HAWG_NS_Ammodytes_dubius",
+                          "DFO_2J3KL_Gadus_morhua",
+                          "DFO_3Pn-4RS_Gadus_morhua",
+                          "DFO_4T-4VN_Gadus_morhua",
+                          "ICES-WGCSE_IS7a_Gadus_morhua",
+                          "ICES-WGCSE_CS7a_Merlangius_merlangus",
+                          "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua",
+                          "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",
+                          "ICES-WGHANSA_SP8abd_Sardina _pilchardus",
+                          "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus",
+                          "NEFSC-GARMIII_SNE- MA_Limanda_ferruginea",
+                          "NEFSC-GARMIII_MA_Paralichthys_dentatus",
+                          "ICES-WGCSE_CS7e-k_Gadus_morhua",
+                          "DFO_4T_Scomber_scombrus",
+                          "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
+                          "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
+                           "AFSC_GOA_Theragra_chalcogramma")
+
+  if(i %in% sensistive.stocks) ss.size = ss.size/10
 
@@
    fast.for.tune <- fast.tunes(years,
-                           tuner='f',
-                           step.size = 0.025, # Make sure n.steps is even please!!
+                           tuner='fec_nm',
+                           step.size = ss.size, 
                            abund.ts = all.abund,
@@
                            nm = -(log(1-prop.nat.mort)),
-                           rems = rem$rem,
                            fecund = mx,
+                           fm = fs,
+                           abund.age = full.abund, 
+                           catch.age = full.rem, 
                            N.init = N.start,
@@
 
-   fast.back.tune <- fast.tunes(years,
-                           tuner='f',
-                           step.size = 0.025, # Make sure n.steps is even please!!
-                           abund.ts = all.abund,
-                           ages = ages,
-                           nm = -(log(1-prop.nat.mort)),
-                           rems = rem$rem,
-                           fecund = mx,
-                           N.init = N.end,
-                           direction= 'backwards'
-                           )
-
-   back.tune.all.res[[i]] <- fast.back.tune
-   back.tune.tmp <- data.frame(fast.back.tune$res,Stock = i)
-   back.tune.summary[[i]] <- back.tune.tmp
+   # fast.back.tune <- fast.tunes(years,
+   #                         tuner='fm',
+   #                         step.size = 0.01, # Make sure n.steps is even please!!
+   #                         abund.ts = all.abund,
+   #                         ages=ages,
+   #                         nm = -(log(1-prop.nat.mort)),
+   #                         fecund = mx,
+   #                         fm = fs,
+   #                         abund.age = full.abund, 
+   #                         catch.age = full.rem, 
+   #                         N.init = N.end,
+   #                         direction= 'backwards'
+   #                         )
+   # 
+   # back.tune.all.res[[i]] <- fast.back.tune
+   # back.tune.tmp <- data.frame(fast.back.tune$res,Stock = i)
+   # back.tune.summary[[i]] <- back.tune.tmp
 
@@
 
-#tst <- do.call('rbind',for.tune.summary)
-#quantile(tst$per.diff,probs=seq(0.001,1,0.001),na.rm=T)
-# summary(tst$per.diff)
-# summary(tst$r)
-# tst <- tst[abs(tst$per.diff) > 5,]
+#DFO_2J3KL_Gadus_morhua -27.7984654 2.815738e+08
+#ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax -21.6050608
+# ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax Lotka error
+# ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus # lotka error
+
+# Fixed...
+#ICES-HAWG_NS_Ammodytes_dubius Overshoot
+# ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii  Overshoot
+#ICES-WGNSSK_NS 4-7d,20_Gadus_morhua Overshoot
+# ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus Overshoot
+# ICES-WGCSE_ISbc-ek_Melanogrammus_aeglefinus  Overshoot
+
+#saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_z.Rds")
+#saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_z.Rds")
+# saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_nm.Rds")
+# saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_nm.Rds")
+#saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_fm.Rds")
+#saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_fm.Rds")
+saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_fec_nm.Rds")
+saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_fec_nm.Rds")
 #
-# range(tst$per.diff,na.rm=T)
-# It completed 33 stocks, was on stock 34
-saveRDS(back.tune.summary,"D:/Github/ICM/Results/backwards_fully_tuned_summary.Rds")
-saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary.Rds")
-saveRDS(back.tune.all.res,"D:/Github/ICM/Results/backwards_fully_tuned_all_res.Rds")
-saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res.Rds")
 
@@
 
-# So we agreed we wanted to look at cod, haddock, herring, and sole using the forward tuning sceanrios...
+# We are now looking at everything, lifetime reproductive success
 
-for.tune.summary <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_summary.Rds")
-for.tune.all <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_all_res.Rds")
+for.tune.summary <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_summary_fec_nm.Rds")
+for.tune.all <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_all_res_fec_nm.Rds")
 
-cod <- grep("morhua",names(for.tune.summary))
-haddock <- grep('aeglefinus',names(for.tune.summary))
-herring <- grep("harengus",names(for.tune.summary))
-pollock <- grep("virens",names(for.tune.summary)) 
-sole <- grep("solea",names(for.tune.summary))
-euro.plaice <- grep("platessa",names(for.tune.summary))
-am.plaice <- grep("platessoides",names(for.tune.summary))
+load(file =  paste0(loc,"/Results/model_inputs_all_ages.Rdata"))
 
-p1.stocks <- sort(c(cod,haddock,herring,pollock,sole,euro.plaice,am.plaice))
+# 
+# cod <- grep("morhua",names(for.tune.summary))
+# haddock <- grep('aeglefinus',names(for.tune.summary))
+# herring <- grep("harengus",names(for.tune.summary))
+# pollock <- grep("virens",names(for.tune.summary)) 
+# sole <- grep("solea",names(for.tune.summary))
+# euro.plaice <- grep("platessa",names(for.tune.summary))
+# am.plaice <- grep("platessoides",names(for.tune.summary))
+# 
+# p1.stocks <- sort(c(cod,haddock,herring,pollock,sole,euro.plaice,am.plaice))
 
@@
 for.tune.stocks <- NULL
-for(i in p1.stocks) 
+for(i in 1:n.stocks) 
 {
@@
   tmp$Area <- meta$Area
+  if(nam == "NEFSC-GARMIII_GB_Gadus_morhua") tmp$Area <- "GB (West)"
   tmp$Order <- meta$Order
@@
   tmp$Notes <- meta$Notes
+  #tmp$removals.init <- rem.tmp[[nam]]$rem
   for.tune.stocks[[nam]] <- tmp
@@
 for.tunes$Species[for.tunes$Species==" harengus"] <- "harengus"
-# Now what does this look like...
-paper.stocks <- unique(for.tunes$Stock)
+for.tunes$Species[for.tunes$Species=="Aeglefinus"] <- "aeglefinus"
+for.tunes$Species[for.tunes$Species=="Solea"] <- "solea"
 
-# Now the doubling time simulations for each stock
+# What Stocks suck
+# sucker.check <- for.tunes %>% dplyr::group_by(Stock) %>% dplyr::summarise(min = min(per.diff,na.rm=T),
+#                                                                           max = max(per.diff,na.rm=T))
+# View(sucker.check)
+# 
+# # FM issues are all really related to having very low fishing mortality years...
+# # Not really sure how to handle that... maybe an if in the code to make a big jump if model is nowhere on convergence
+# # and fishing is < 10% of mean F for the population, that would cover all the problems I'm seeing here.
+# # Has years with 0 fishing, need to put in something
+# "ICES-WGNSSK_NS4 _Scopthalmus_maximus"
+# "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"
+# # Removals so low the step size isn't enough...
+# "DFO_3Pn-4RS_Gadus_morhua" # Worked great until the second last year then it did nothing, I think the step size was too small
+# "DFO_4T-4VN_Gadus_morhua" # In 1995 it just does nothing, I think because the step size is too small due to super low F.
+# "DFO_4T_Hippoglossoides _platessoides"
+# "NEFSC-GARMIII_GOM-CHATT_Morone_saxatilis"
+# tst <- for.tunes %>% dplyr::filter(Stock == "ICES-HAWG_NS_Ammodytes_dubius")
+# 
+# # Now what does this look like...
+# paper.stocks <- unique(for.tunes$Stock)
+# 
+# tst <- for.tunes %>% dplyr::group_by(Stock) %>% dplyr::summarise(min = min(per.diff,na.rm=T),
+#                                                                  max = max(per.diff, na.rm=T))
+# # Now the doubling time simulations for each stock
 
@@
 {
-  r <- sample(na.omit(try$r),size=1)
-  pop[y] <- (1+r)*pop[y-1]
+  lambda <- sample(na.omit(try$lambda),size=1)
+  pop[y] <- lambda*pop[y-1]
 } # end the years loop
@@
   tst <- for.tune.all[[i]]
-f.tmp <- tst$fecund.opt
+  # Fishing mortality
+  fm.org.tmp <- fs.tmp[[i]]
+  fm.tmp <- tst$fm.opt
+  # fecundity
+  fec.tmp <- tst$fecund.opt
+  fec.org.tmp <- tst$fecund.org
+  # Natural mortality
+  m.org.tmp <- exp(-tst$nm.org)
   m.tmp <- exp(-tst$nm.opt)
-f.org.tmp <- tst$fecund.org
-m.org.tmp <- exp(-tst$nm.org)
+  # Total mortality
+  z.tmp <- exp(-tst$z.opt)
+  z.org.tmp <- exp(-tst$nm.org -fm.org.tmp)
 
-ages <- 0:(ncol(f.tmp)-1)
+  ages <- 0:(ncol(fec.tmp)-1)
   n.ages <- length(ages)
@@
     {
-  fs[a] <- f.tmp[y+count,a]  
-  fs.org[a] <- f.org.tmp[y+count,a]  
+    fs[a] <- fec.tmp[y+count,a]  
+    fs.org[a] <- fec.org.tmp[y+count,a]  
     if(a > 1) 
@@
 
-  res.year[[y]] <- data.frame(mx.opt = unlist(f.tmp[y,]),lx.opt = lx.year,age = ages,
-                         mx.lx.opt = unlist(f.tmp[y,])*lx.year,
-                         x.mx.lx.opt = unlist(f.tmp[y,])*lx.year*ages,
+    res.year[[y]] <- data.frame(mx.opt = unlist(fec.tmp[y,]),lx.opt = lx.year,age = ages,
+                           mx.lx.opt = unlist(fec.tmp[y,])*lx.year,
+                           x.mx.lx.opt = unlist(fec.tmp[y,])*lx.year*ages,
                            year=years[y],Stock = i)
@@
 
-for(i in p1.stocks) 
+for(i in 1:n.stocks) 
 {
@@
   pop.dam$Area[pop.dam$Stock == nam] <- meta$Area
+  if(nam == "NEFSC-GARMIII_GB_Gadus_morhua") pop.dam$Area[pop.dam$Stock == nam] <- "GB (West)"
   pop.dam$Order[pop.dam$Stock == nam] <- meta$Order
@@
 pop.dam$Species[pop.dam$Species==" harengus"] <- "harengus"
-
-hmm <- pop.dam %>% dplyr::filter(R0.opt > 500)
-
-hmm
-
-hmm[hmm$Stock == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",]
-for.tune.all$`ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus`$res
-
-unique(hmm$Stock)
-# There are 7 stocks with some bat shit happening...
-# Fixed... "ICES-WGNSSK_NS4 _Solea_solea"
-
-# These are all problems because the abundance increases like nuts in a few years....
-"ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus"
-"ICES-WGCSE_CS7e-k_Gadus_morhua"                  
-"ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus" # Something special weird going on with this stock
-"ICES-WGBFAS_WBS-25-32_Gadus_morhua"
-
-# Figure out how to get an r of 10 and what the mx vector needs to look like for
-#"ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus"
-
-ages <- 0:12 # ages
-mx <- c(0.9,500,500,rep(5000,10)) # fecundity
-nat.mort <- rep(0.2,13) # natural mortality
-si <- 1- nat.mort # survivial
-
-lx <- 1
-for(s in 2:(length(si))) lx[s]<-lx[s-1]*si[s-1]
-
-eulerlotka <- function(r) (sum(lx * mx * exp(-r * ages)) - 1)^2
-
-junk<-optimize(lower=-0.999999,upper=55,f = eulerlotka)
-res <- c(junk$minimum)
-res
-
-p.start <- 10
-
-p.end <- (1+res)*p.start
-p.end
-
-R0 <- sum(lx*mx)
-R0
-
-tmp <- for.tune.all[["ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus"]]
-tmp$nm.org
-tmp$fecund.opt
-t1 <- vpa.tmp$`ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus`
-range(t1[2:length(t1)]/t1[1:(length(t1)-1)])
-# So using all the age classes actually reduces the ratios from year to year requiring less insanity...
-t2 <- all.abund.tmp$`ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus`
-range(t2[2:length(t2)]/t2[1:(length(t2)-1)])
-
-data.frame(tmp$res$year,tmp$res$vpa.abund,t1,t2)
-
-mx <- c(0,0,0,rep(30,11))
-nm <- rep(0.2,14)
+pop.dam$Species[pop.dam$Species=="Aeglefinus"] <- "aeglefinus"
+pop.dam$Species[pop.dam$Species=="Solea"] <- "solea"
 
@@
 
-ggplot(for.tunes) + geom_jitter(aes(y=r,x=Species)) + scale_y_continuous(name = 'rate of growth (r)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))
+ggplot(for.tunes) + geom_jitter(aes(y=lambda,x=Species,group=Stock,color=Stock)) + scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10))
 
-ggplot(for.tunes) + geom_jitter(aes(y=r.vpa.init,x=Species)) + scale_y_continuous(name = 'rate of growth (r)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))
+ggplot(for.tunes) + geom_jitter(aes(y=lambda.vpa.init,x=Species)) + scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))
 
@@
 
-ggplot(for.tunes) + geom_density(aes(r,group=Species,color=Species,fill=Species),alpha = 0.2)
+ggplot(for.tunes) + geom_density(aes(lambda,group=Species,color=Species,fill=Species),alpha = 0.2) + scale_x_continuous(breaks = c(0,0.5,1,2,5,10))
 
@@
 
-options(scipen=999)
-ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Species))  + scale_y_log10(name = "Lifetime Reproductive Output",
-                                                                         breaks = c(0.001,0.01,0.1,1,5,10,50,100,500,1000,5000,1e4,1e5,1e6),
-                                                                         minor_breaks = NULL)
+#options(scipen=999)
+r0.plt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
+                            scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.05,0.1,0.5,1,5,10,50,100),minor_breaks = NULL) + 
+                            facet_wrap(~Species,scales = 'free')+
+                            theme(axis.text.x = element_text(angle =45,hjust=1))
+save_plot("D:/Github/ICM/Figures/tuned/R0_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
+
+windows(11,11)
+r0.ts.plt <- ggplot(pop.dam) + geom_line(aes(y=R0.opt,x=cohort,group=Area,color=Area))  + 
+                            scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
+                            facet_wrap(~Species,scales = 'free')+
+                            theme(axis.text.x = element_text(angle =45,hjust=1))
+r0.ts.plt
+save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
+
+vickis.cols <- sort(rep(c( "#172582",  "#F8DC91", "#FBB891", "#FB6A01", "#B80000"),3))
+linetypes <- rep(c(1,2,4),5)
+
+windows(11,11)
+cod.r0.ts.plt <- ggplot(pop.dam %>% dplyr::filter(Species == 'morhua')) + geom_line(aes(y=R0.opt,x=cohort,group=Area,color=Area,linetype=Area),size=1.5)  + 
+                            scale_y_log10(name = "Lifetime Reproductive Output", breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
+                            scale_color_manual(values = vickis.cols) +
+                            scale_linetype_manual(values = linetypes) +
+                            theme(legend.key.width  = unit(2, "cm"))
+cod.r0.ts.plt
+#save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
+
+windows(11,11)
+ggplot(pop.dam %>% dplyr::filter(Species =="morhua")) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
+                                                        scale_y_log10(name = "Lifetime Reproductive Output",breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) +
+                                                        theme(axis.text.x = element_text(angle =45,hjust=1))
+
+# Missing catch questions
+# first did we do much to the Fecundity term to get here
+quantile(for.tunes$mean.fec/for.tunes$mean.vpa.fec,probs=seq(0.01,1,0.01),na.rm=T)
+
+quantile((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init,probs=seq(0.01,1,0.01),na.rm=T)
+quantile((for.tunes$mean.nm-for.tunes$mean.vpa.nm)/for.tunes$mean.vpa.nm,probs=seq(0.01,1,0.01),na.rm=T)
+
+for.tunes$excess.catch <- for.tunes$removals-for.tunes$removals.init
+for.tunes$per.excess.catch <- 100*((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init)
+
+windows(11,11)
+bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Species)) + 
+                                   ylab("Adjustment to catch (%)") +
+                                   theme(axis.text.x = element_text(angle=45,hjust = 1))
+
+save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_species.png",bycatch.plt,base_width = 8,base_height = 8)
+
+bycatch.plt.cod <- ggplot(for.tunes %>% dplyr::filter(Species == 'morhua')) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + 
+                                                                              ylab("Adjustment to catch (%)") +
+                                                                              theme(axis.text.x = element_text(angle=45,hjust = 1))
+
+save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_cod_stock.png",bycatch.plt.cod,base_width = 8,base_height = 8)
+
+bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + facet_wrap(~Species,scales = 'free_x')
+                                   ylab("Adjustment to catch (%)") +
+                                   theme(axis.text.x = element_text(angle=45,hjust = 1))
 

### 2023-11-20 Scripts/functions/backwards_project.r

@@ -6,28 +6,17 @@
 #option:         So far we can do exponential or logistic growth, other options are on the table if someone has a good one
 #pop.next:       The population size in year t+1, which is used to estimate the size of the population in year t
 #r:              The intrinsic rate of growth for the population
-#removals:       The removals between t+1 and t
 #K:              The carrying capacity, only necessary for logistic model
-#fishery.timing: When do you want the removals by the fishery to occur, at the 'beginning' of the year, or at the end of the year.  
-#                   At the 'beginning' excludes them from the population dynamics, at the 'end' includes them in the population dynamics (because we are going backwards).
 
-back.proj <- function(option = "exponential",pop.next,r,removals.next,K,fishery.timing = 'beginning')
+back.proj <- function(option = "exponential",pop.next,r,K)
 {
 
   
   ### So rolling with the easy peasy continuous time exponential
   ### simple exponential population growth, in this formulation with the removals I think I'm saying the removals happen right at the outset
-  if(option == 'exponential') 
-  {
-    if(fishery.timing == 'beginning')
-    {
-    # Going to 1+r model since we are discrete time...
-    #Pop.current <- (pop.next)/(exp(r))
-    Pop.current <- (pop.next)/(exp(r))
-    Pop.current<- Pop.current+removals.next 
-    }
-    if(fishery.timing =='end') Pop.current <- (pop.next+removals.next)/((exp(r))) # (pop.next+removals.next)/(exp(r))
-  }
+  if(option == 'exponential') Pop.current <- (pop.next)/(exp(r))
+  
+  
   # Logistic growth model, 
   # The maths be.... N(t+1) = N(t) + rN(t)(1-N(t)/K).... now we are solving for N(t) not N(t+1), so we rearrange terms
   # to get it in the quadratic formula....  (r/K)N^2 -(1+r)N  + N(t+1) = 0... we have r, K, and N(t+1) so we can solve for N(t)
@@ -38,18 +27,12 @@ back.proj <- function(option = "exponential",pop.next,r,removals.next,K,fishery.
   if(option == "logistic")
   {
     # Get our parameter for the logistic model
-    if(fishery.timing == 'beginning') par <- pop.next
-    if(fishery.timing == 'end') par <- pop.next <- pop.next + removals.next
+    par <- pop.next
     # Ha, we can use this to solve for N in the previous year 
[…]

### 2023-11-20 Scripts/functions/forward_project.r

@@ -4,24 +4,15 @@
 #option:         So far we can do exponential or logistic growth, other options are on the table if someone has a good one
 #pop.last:       The population size in year t-1, which is used to estimate the size of the population in year t
 #r:              The intrinsic rate of growth for the population
-#removals:       The removals between t+1 and t
 #K:              The carrying capacity, only necessary for logistic model
-#fishery.timing: When do you want the removals by the fishery to occur, at the 'beginning' of the year, or at the end of the year.  
-#                   At the 'beginning' excludes them from the population dynamics, at the 'end' includes them in the population dynamics (because we are going backwards).
+                 
  
-for.proj <- function(option = "exponential",pop.last,r,removals.next,K,fishery.timing = 'beginning')
+for.proj <- function(option = "exponential",pop.last,r,K)
 {
   ### So rolling with the easy peasy continuous time exponential
   ### simple exponential population growth, in this formulation with the removals I think I'm saying the removals happen right at the outset
-  if(option == 'exponential') 
-  {
-    if(fishery.timing == 'end')
-    {
-    Pop.current <- (pop.last)*((exp(r)))
-    Pop.current<- Pop.current-removals.next  
-    }
-    if(fishery.timing =='beginning') Pop.current <- (pop.last-removals.next)*((exp(r)))
-  }
+  if(option == 'exponential') Pop.current <- (pop.last)*((exp(r)))
+
   # Logistic growth model, 
   # The maths be.... N(t+1) = N(t) + rN(t)(1-N(t)/K).... now we are solving for N(t) not N(t+1), so we rearrange terms
   # to get it in the quadratic formula....  (r/K)N^2 -(1+r)N  + N(t+1) = 0... we have r, K, and N(t+1) so we can solve for N(t)
@@ -29,15 +20,7 @@ for.proj <- function(option = "exponential",pop.last,r,removals.next,K,fishery.t
   # But thanks to my longtime biological math hero Sarah Otto and her book on Mathematical modelling
   # This will solve the backwards logistic and is easy peasy to use for forwards logistic
   # Hurray for math!
-  if(option == "logistic")
-  {
-    # Get our parameter for the logistic model
-    if(fishery.timing == 'end') par <- pop.last
-    if(fishery.timing == 'beginning') par <- pop.last <- pop.last - removals.next
-    # Get the current population size using logistic model
[…]

### 2023-11-20 Scripts/functions/simple_Lotka_r.r

@@ -1,12 +1,12 @@
 # Function to calculate Lotka R, DK revised this with several options of how we want to calculate
 
 # Function Arguments
-# nat.mort:    Natural mortality, 
+# Z:    Total mortality, 
 # fecund:      Fecundity
 # ages:
 
-simple.lotka.r<-function(nat.mort = NULL,fecund = NULL,ages = NULL) 
-{
+simple.lotka.r<-function(Z = NULL,fecund = NULL,ages = NULL) 
+{  
   
   # The Euler-Lotka Function to optimize on to find the intrinsic rate of growth for your population
   eulerlotka <- function(r) (sum(lx * mx * exp(-r * ages)) - 1)^2
@@ -16,14 +16,11 @@ simple.lotka.r<-function(nat.mort = NULL,fecund = NULL,ages = NULL)
   
   
   #################################### Calculate Lotka SECTION #################################### Calculate Lotka SECTION #################################### Calculate Lotka SECTION
-  mx.tmp <- NULL
-  lx.tmp <- NULL
-  
   # Now run this through all the yrs 
 
     # Get the r estimate for each year if we are running through a bunch of years
-    # Just use the first year if we don't have same length nat.mort as years
-    if(!is.null(nrow(nat.mort))) lx <- 1-exp(-nat.mort) else lx <- 1-exp(-nat.mort)
+    # Just use the first year if we don't have same length Z as years
+    if(!is.null(nrow(Z))) lx <- 1-exp(-Z) else lx <- 1-exp(-Z)
     # Convert to survivorship vector
     si <- 1-lx 
     # Set the first age class to be 1
@@ -33,8 +30,8 @@ simple.lotka.r<-function(nat.mort = NULL,fecund = NULL,ages = NULL)
     mx <- fecund
     # Now we are cooking!
     #browser()
-    junk<-optimize(lower=-15,upper=15,f = eulerlotka)
+    junk<-optimize(lower=-5,upper=5,f = eulerlotka)
     res <- c(junk$minimum)
 
-  return(list(res=res,mx=mx,lx=lx,nat.mort = nat.mort,ages=ages))
+  return(list(res=res,mx=mx,lx=lx,Z = Z,ages=ages))
 }

### 2023-11-20 Scripts/functions/tuning_sim_fast.r

@@ -3,7 +3,7 @@
 
 # All the data you need to make it dance...
 # years:          The years you are running the backwards calculation for
-# abund.ts:       The abundance time series from the assessment
+# abund.ts:        The abundance time series from the assessment
 
 # tuner:          What are we tuning, the fecundity "f", or natural mortality 'm', or both 'b'
 # rems            Removals from the fishery in a given year.
@@ -23,7 +23,7 @@
 
 
 fast.tunes<-function(years,step.size=0.05,tuner="m",  direction = 'backwards',ages = NULL,
-                   nm=NULL,fecund = NULL,N.init = NULL,abund.ts = NULL, rems)
+                   nm=NULL,fecund = NULL,fm = NULL,N.init = NULL,abund.ts = NULL,abund.age = NULL,catch.age = NULL)
 {
   # Download the function to go from inla to sf
   funs <- c(#"https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/simple.lotka.r",
@@ -48,11 +48,23 @@ fast.tunes<-function(years,step.size=0.05,tuner="m",  direction = 'backwards',ag
  
   #Initialize a bunch of objects
   n.years<-length(years)
+  # Not using this, but I might someday, this is the minimum age in the VPA, we've filled in the rest of the 0s...
+  min.age <- min(ages)
+  # Now these all run from age 0 not
+  ages <- 0:max(ages)
   res <- data.frame(year = years,vpa.abund = N.init, est.abund = NA, diff= NA,per.diff = NA,lambda=NA,lambda.vpa.init = NA,
-                    removals = NA,mean.fec=NA,mean.vpa.fec = NA,mean.nm = NA,mean.vpa.nm = NA)
+                    removals = NA,removals.init = NA,mean.fec=NA,mean.vpa.fec = NA,mean.nm = NA,mean.vpa.nm = NA)
   fecund.ts <- data.frame(fecund)
   nm.ts <- data.frame(nm)
+  fm.ts <- data.frame(fm)
+  z.ts <- data.frame(fm.ts + nm.ts)
+  catch.age.ts <- data.frame(catch.age)
+  abund.age.ts <- data.frame(abund.age)
   
+  # Get the average removals so we can identify really low years
+  tot.catch <- rowSums(catch.age.ts,na.rm=T)
+  mn.fm.age <- colMeans(fm.ts,na.rm=T)
+  mn.catch <- mean(tot.catch,na.rm=T)
   # Here I try to make a fast fitting version of the previous model...
   
[…]

### 2023-11-29 Scripts/Paper_1.Rmd
Mostly new figures
Mostly focused on building better figures for the paper, some other general tweaks.

@@
 
-```{r paper-other-metrics}
+```{r paper-other-metrics-and-metadata}
 
 # We are now looking at everything, lifetime reproductive success
-
-for.tune.summary <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_summary_fec_nm.Rds")
-for.tune.all <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_all_res_fec_nm.Rds")
+model <- "fec_nm"
+for.tune.summary <- readRDS(paste0("D:/Github/ICM/Results/forwards_fully_tuned_summary_",model,".Rds"))
+for.tune.all <- readRDS(paste0("D:/Github/ICM/Results/forwards_fully_tuned_all_res_",model,".Rds"))
 
 load(file =  paste0(loc,"/Results/model_inputs_all_ages.Rdata"))
-
-# 
-# cod <- grep("morhua",names(for.tune.summary))
-# haddock <- grep('aeglefinus',names(for.tune.summary))
-# herring <- grep("harengus",names(for.tune.summary))
-# pollock <- grep("virens",names(for.tune.summary)) 
-# sole <- grep("solea",names(for.tune.summary))
-# euro.plaice <- grep("platessa",names(for.tune.summary))
-# am.plaice <- grep("platessoides",names(for.tune.summary))
-# 
-# p1.stocks <- sort(c(cod,haddock,herring,pollock,sole,euro.plaice,am.plaice))
-
+# Get the stocks...
 Stocks <- names(for.tune.summary)
@@
 
+############ Meta data and clean up, could be it's own chunk really, but it's really fast, so meh...
+
+#  A quick way to get the other potentially interesting info for the stock...
+drop <- which(names(ASR_long) %in% c("Year","type","age","value"))
+meta <- NULL
+for(i in Stocks) meta[[i]] <- ASR_long[ASR_long$Stock == i,-drop][1,]
+meta <- do.call('rbind',meta)
+
+# First making a meta data object and adding a bunch of columns to it... very messy!!
+meta$Species[meta$Species == ' harengus']  <- "harengus"
+meta$Species[meta$Species == "Aeglefinus"] <- "aeglefinus"
+meta$Species[meta$Species == "Solea"] <- "solea"
+meta$Genus[meta$Genus == " Hippoglossoides"] <- "Hippoglossoides"
+meta$G.short <- toupper(paste0(substr(meta$Genus,1,1),"."))
+meta$G.Species <- paste0(meta$G.short," ",meta$Species)
+# Simplified Management
+meta$Manage.short <- meta$Management
+meta$Manage.short[grep("TRAC",meta$Management)] <- "DFO-TRAC"
+meta$Manage.short[grep("DFO",meta$Management)] <- "DFO-TRAC"
+meta$Manage.short[grep("NEFSC",meta$Management)] <- "NEFSC"
+meta$Manage.short[grep("ICES",meta$Management)] <- "ICES"
+
+# The 3 pieces of the ocean
+meta$LME <- "NW Atlantic"
+meta$LME[meta$Management == "AFSC"] <- "Pacific (Alaska)"
+meta$LME[grepl("ICES",meta$Management)] <- "NE Atlantic"
+# Some other Area summaries
+meta$Area.broad <- meta$Area
+meta$Area.long <- meta$Area
+meta$Area.narrow <- "" # Leave this blank if not needed
+
+meta$Area.broad[grep("NS",meta$Area)] <- "NS"
+meta$Area.long[grep("NS",meta$Area)] <- "North Sea"
+meta$Area.broad[grep("CS",meta$Area)] <- "CS"
+meta$Area.long[grep("CS",meta$Area)] <- "Celtic Sea"
+meta$Area.broad[grep("ROCK6b",meta$Area)] <- "CS"
+meta$Area.long[grep("ROCK6b",meta$Area)] <- "Celtic Sea Rockall"
+meta$Area.broad[grep("IS",meta$Area)] <- "IS"
+meta$Area.long[grep("IS",meta$Area)] <- "Irish Sea"
+meta$Area.broad[grep("BS",meta$Area)] <- "BS"
+meta$Area.long[grep("BS",meta$Area)] <- "Baltic Sea"
+meta$Area.broad[grep("NEA",meta$Area)] <- "NEA"
+meta$Area.long[grep("NEA",meta$Area)] <- "NE Arctic"
+meta$Area.broad[grep("B28.1",meta$Area)] <- "BS"
+meta$Area.long[grep("B28.1",meta$Area)] <- "Baltic Sea"
+meta$Area.broad[grep("SP8abd",meta$Area)] <- "BoB"
+meta$Area.long[grep("SP8abd",meta$Area)] <- "Bay of Biscay"
+meta$Area.broad[grep("FA",meta$Area)] <- "I-F"
+meta$Area.broad[grep("ICE",meta$Area)] <- "I-F"
+meta$Area.long[grep("FA",meta$Area)] <- "Faroes"
+meta$Area.long[grep("ICE",meta$Area)] <- "Iceland"
+
+meta$Area.broad[grep("GOM",meta$Area)] <- "GOM-GB"
+meta$Area.long[grep("GOM",meta$Area)] <- "Gulf of Maine"
+meta$Area.broad[grep("GB",meta$Area)] <- "GOM-GB"
+meta$Area.long[grep("GB",meta$Area)] <- "Georges Bank"
+meta$Area.broad[grep("5Y",meta$Area)] <- "GOM-GB"
+meta$Area.long[grep("5Y",meta$Area)] <- "NAFO 5Y"
+meta$Area.broad[grep("5Z",meta$Area)] <- "GOM-GB"
+meta$Area.long[grep("5Z",meta$Area)] <- "NAFO 5Z"
+meta$Area.broad[grep("USATL",meta$Area)] <- "GOM-GB" # The fishery is broader than just GOM, but it does also include it.
+meta$Area.long[grep("USATL",meta$Area)] <- "US Atlantic" # The fishery is broader than just GOM, but it does also include it.
+meta$Area.broad[grep("NWA",meta$Area)] <- "GOM-GB" # Mackerel... so that definition is a bit narrow....
+meta$Area.long[grep("NWA",meta$Area)] <- "US Atlantic" # Mackerel... so that definition is a bit narrow....
+#meta$Area1[grep("SNE- MA",meta$Area)] <- "GOM-GB" # YT in US, so no GB so that definition is a bit narrow....
+meta$Area.broad[grep("MA",meta$Area)] <- "GOM-GB" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
+meta$Area.long[grep("MA",meta$Area)] <- "Gulf of Maine" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
+meta$Area.broad[grep("BSAI",meta$Area)] <- "BSAI"
+meta$Area.broad[grep("4T",meta$Area)] <- "GSL"
+meta$Area.long[grep("4T",meta$Area)] <- "NAFO 4T"
+meta$Area.broad[grep("2J3",meta$Area)] <- "NFLD"
+meta$Area.long[grep("2J3",meta$Area)] <- "NFLD"
+meta$Area.broad[grep("3Pn-4RS",meta$Area)] <- "NFLD"
+meta$Area.long[grep("3Pn-4RS",meta$Area)] <- "NFLD"
+meta$Area.long[grep("GOA",meta$Area)] <- "Gulf of Alaska"
+meta$Area.long[grep("AI",meta$Area)] <- "Aleutian Islands"
+meta$Area.long[grep("ESB",meta$Area)] <- "Bering Sea"
+meta$Area.long[grep("BSAI",meta$Area)] <- "Bering Sea & AI"
+meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI-Females"
+meta$Area.long[grep("BSAI-Females",meta$Area)] <- "Bering Sea & AI"
+meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Pollachius_virens"] <- "5b"
+meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5a_Pollachius_virens"] <- "5a"
+meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS4 _Solea_solea"] <- "4"
+meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d._Solea_solea"] <- "7d"
+meta$Area.narrow[meta$Stock == "ICES-WGBFAS_NS IIIa 22-24_Solea_Solea"] <- "22-24"
+meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d_Pleuronectes_platessa"] <- "7d"
+meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4,20_Pleuronectes_platessa"] <- "4 20"
+meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS7e_Pleuronectes_platessa"] <- "7e"
+meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS27.7a_Pleuronectes_platessa"] <- "7a"
+meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Melanogrammus_aeglefinus"] <- "5b"
+meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Melanogrammus_aeglefinus"] <- "5a"
+meta$Area.narrow[meta$Stock == "ICES-WGBFAS_B28.1_Clupea_harengus"] <- "28"
+meta$Area.narrow[meta$Stock == "ICES-WGBFAS_BS 25-29-32_Clupea_harengus" ] <- "25-32"
+meta$Area.narrow[meta$Stock == "ICES-HAWG_WBS 22-24_Clupea_harengus"] <- "22-24"
+meta$Area.narrow[meta$Stock == "DFO_4T-Fall_Clupea_harengus"] <- "Fall"
+meta$Area.narrow[meta$Stock == "DFO_4T-Spring_Clupea_harengus"] <- "Spring"
+meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS27.6a_Merlangius_merlangus"] <- "27.6a"
+meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS7a_Merlangius_merlangus"] <- "7a"
+meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Gadus_morhua"] <- "5a"
+meta$Area.narrow[meta$Stock == "ICES-NWWG_FAPL5b1_Gadus_morhua" ] <- "5b"
+meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua"] <- "4-7 20"
+meta$Area.narrow[meta$Stock == "ICES-WGCSE_NS6a_Gadus_morhua"] <- "6a"
+meta$Area.narrow[meta$Stock == "DFO_2J3KL_Gadus_morhua"] <- "2J 3KL"
+meta$Area.narrow[meta$Stock == "DFO_3Pn-4RS_Gadus_morhua"] <- "3Pn 4RS"
+meta$Area.narrow[meta$Stock == "NEFSC-CERT-TRAC_GB _Gadus_morhua"] <- "East"
+
+meta$Stock.short <- paste0(meta$Area.long," ",meta$Area.narrow," ",meta$G.short," ",meta$Species)
+meta$Stock.no.species <- paste0(meta$Area.long," ",meta$Area.narrow)
+
 for.tune.stocks <- NULL
-for(i in 1:n.stocks) 
-{
-  nam <- Stocks[i]
-  #  A quick way to get the other potentially interesting info for the stock...
-  meta <- ASR_long[ASR_long$Stock == nam,][1,]
-  tmp <- for.tune.summary[[nam]]
-  tmp$Management   <- meta$Management  
-  tmp$Area <- meta$Area
-  if(nam == "NEFSC-GARMIII_GB_Gadus_morhua") tmp$Area <- "GB (West)"
-  tmp$Order <- meta$Order
-  tmp$Family   <- meta$Family  
-  tmp$Genus  <- meta$Genus 
-  tmp$Species <- meta$Species
-  tmp$Model <- meta$Model
-  tmp$Meeting_or_reference <- meta$Meeting_or_reference
-  tmp$Notes <- meta$Notes
-  #tmp$removals.init <- rem.tmp[[nam]]$rem
-  for.tune.stocks[[nam]] <- tmp
+fta <- NULL
+
+# Going to rename these female stocks.
+fem.names <- c("AFSC_BASI-Females_Pleuronectes_quadrituberculatus",
+                  "AFSC_EEBSAI-Females_Lepidopsetta_polyxystra",
+                  "AFSC_BSAI-females_Atheresthes_stomais")
+fem.rename <- c("AFSC_BSAI_Pleuronectes_quadrituberculatus",
+                  "AFSC_EEBSAI_Lepidopsetta_polyxystra",
+                  "AFSC_BSAI_Atheresthes_stomais")
+# Going to drop these stocks
+dont <- paste(c("Mles","Males","COASTNOR"),collapse = "|")
+
+meta.sub <- NULL
+for(i in Stocks) 
+{
+  org.nam <- i
+  tmp <- for.tune.summary[[org.nam]]
+  new.stock.nam <- org.nam
+  # Don't bother for these stocks...
+  if(!grepl(dont,tmp$Stock[1]))
+  {
+    # Grab the metadata and add in some new useful things...
+    meta.sub[[i]] <- meta[meta$Stock == org.nam,]
+
+    # Rename the ladies
+    if(tmp$Stock[1] == fem.names[1]) new.stock.nam <- tmp$Stock <- fem.rename[1]
+    if(tmp$Stock[1] == fem.names[2]) new.stock.nam <- tmp$Stock <- fem.rename[2]
+    if(tmp$Stock[1] == fem.names[3]) new.stock.nam <- tmp$Stock <- fem.rename[3]
+
+    meta.sub[[i]]$Stock <- new.stock.nam
+    tmp <- data.frame(tmp,meta.sub[[i]])
+    # For tunes all
+    fta[[new.stock.nam]] <- for.tune.all[[org.nam]]
+    fta[[new.stock.nam]]$meta <- meta.sub[[i]]
+    for.tune.stocks[[new.stock.nam]] <- tmp
+  }# End skip stocks...
 }
-
 # Now unpack them...
 for.tunes <- do.call("rbind",for.tune.stocks)
-# Typo clean up...
-for.tunes$Species[for.tunes$Species==" harengus"] <- "harengus"
-for.tunes$Species[for.tunes$Species=="Aeglefinus"] <- "aeglefinus"
-for.tunes$Species[for.tunes$Species=="Solea"] <- "solea"
-
-# What Stocks suck
-# sucker.check <- for.tunes %>% dplyr::group_by(Stock) %>% dplyr::summarise(min = min(per.diff,na.rm=T),
-#                                                                           max = max(per.diff,na.rm=T))
-# View(sucker.check)
-# 
-# # FM issues are all really related to having very low fishing mortality years...
-# # Not really sure how to handle that... maybe an if in the code to make a big jump if model is nowhere on convergence
-# # and fishing is < 10% of mean F for the population, that would cover all the problems I'm seeing here.
-# # Has years with 0 fishing, need to put in something
-# "ICES-WGNSSK_NS4 _Scopthalmus_maximus"
-# "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"
-# # Removals so low the step size isn't enough...
-# "DFO_3Pn-4RS_Gadus_morhua" # Worked great until the second last year then it did nothing, I think the step size was too small
-# "DFO_4T-4VN_Gadus_morhua" # In 1995 it just does nothing, I think because the step size is too small due to super low F.
-# "DFO_4T_Hippoglossoides _platessoides"
-# "NEFSC-GARMIII_GOM-CHATT_Morone_saxatilis"
-# tst <- for.tunes %>% dplyr::filter(Stock == "ICES-HAWG_NS_Ammodytes_dubius")
-# 
-# # Now what does this look like...
-# paper.stocks <- unique(for.tunes$Stock)
-# 
-# tst <- for.tunes %>% dplyr::group_by(Stock) %>% dplyr::summarise(min = min(per.diff,na.rm=T),
-#                                                                  max = max(per.diff, na.rm=T))
-# # Now the doubling time simulations for each stock
-
+for.tune.all <- fta
+meta.sub <- do.call("rbind",meta.sub)
+
+######################### End Meta data and clean up #####################
+
+# Now some summaries...
+
+# Reset on the stocks...
+Stocks <- sort(names(for.tune.all))
+n.stocks <- length(Stocks)
+
+# Doubling time, no fishing
 dt.res <- NULL
-for(i in paper.stocks)
+n.dt.sims <- 20 # Number of simultions...
+n.years <- 100
+for(i in Stocks)
 {
   try <- for.tunes %>% dplyr::filter(Stock == i)
+  meta.tmp <- meta.sub %>% dplyr::filter(Stock == i)
   double.time <- NA
   pop <- 1000
-
-for(s in 1:100)
-{
-for(y in 2:100)
+  tmp.res <- NULL
+for(s in 1:n.dt.sims)
+{
+  tmp <- rep(0,n.years)
+
+  for(y in 2:n.years)
   {
@@
     pop[y] <- lambda*pop[y-1]
+    if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.years] <- 1
   } # end the years loop
-tmp <- which(pop >= 2*pop[1])[1]
-
-if(is.na(tmp)) double.time[s] <- 0
-if(!is.na(tmp))double.time[s] <- tmp
+  tmp.res[[s]] <- data.frame(year =1:100,doubled = tmp,sim=s)
   } # end sim loop
-
-dt.res[[i]] <- data.frame(dt = double.time,Stock = i,Species = try$Species[1])
+  res.tmp <- do.call("rbind",tmp.res)
+
+dt.res[[i]] <- data.frame(res.tmp,meta.tmp)
 
@@
 dub.time <- do.call("rbind",dt.res)
+
+dub.time.summary <- dub.time %>% dplyr::group_by(Stock,year)  %>% dplyr::summarise(prop = sum(doubled)/n.dt.sims)
+dub.time.summary <- left_join(dub.time.summary,meta.sub,by="Stock")
 
@@
 # First I need to get the fecundity and natural mortalities by cohort instead of year.
-
 res.fin <- NULL
 res.year.fin <- NULL
-for(i in paper.stocks)
+res.lambda.fin <- NULL
+for(i in Stocks)
 {
   tst <- for.tune.all[[i]]
+  meta.tmp <- tst$meta
   # Fishing mortality
-  fm.org.tmp <- fs.tmp[[i]]
+  fm.org.tmp <- tst$fm.org
   fm.tmp <- tst$fm.opt
@@
   # Natural mortality
-  m.org.tmp <- exp(-tst$nm.org)
-  m.tmp <- exp(-tst$nm.opt)
+  m.org.tmp <- exp(-tst$nm.org) # This is survivorship
+  m.tmp <- exp(-tst$nm.opt) # This is survivorship
   # Total mortality
-  z.tmp <- exp(-tst$z.opt)
-  z.org.tmp <- exp(-tst$nm.org -fm.org.tmp)
+  z.tmp <- exp(-tst$z.opt) # This is survivorship
+  z.org.tmp <- exp(-tst$nm.org -fm.org.tmp) # This is survivorship
 
@@
   res.year <- NULL
+  res.lambda <- NULL
   for(y in 1:(n.years-n.ages+1))
@@
                                x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
-                           cohort=years[y],Stock = i)
+                               cohort=years[y],meta.tmp)
 
@@
                                x.mx.lx.opt = unlist(fec.tmp[y,])*lx.year*ages,
-                           year=years[y],Stock = i)
+                               year=years[y],meta.tmp)
 
@@
 
+# Do a years loop to get lambda with no fishing for each year, rather than by cohort...
+  for(yy in 1:n.years)
+  {
+    nm <- as.numeric(tst$nm.opt[yy,])
+    z <- as.numeric(tst$z.opt[yy,])
+    fec <- as.numeric(tst$fecund.opt[yy,])
+    nm.init <- as.numeric(tst$nm.org[yy,])
+    fec.init <- as.numeric(tst$fecund.org[yy,])
+    z.init <- as.numeric(tst$z.org[yy,])
+    lam.no.fish <- exp(simple.lotka.r(Z = nm,fecund = fec,ages=ages)$res)
+    lam.fish <- exp(simple.lotka.r(Z = z,fecund = fec,ages=ages)$res)
+    lam.org.no.fish <- exp(simple.lotka.r(Z = nm.init,fecund = fec.init,ages=ages)$res)
+    lam.org.fish <- exp(simple.lotka.r(Z =  z.init,fecund = fec.init,ages=ages)$res)
+
+    # Now summarize these
+    res.lambda[[yy]] <-  data.frame(lam.no.fish = lam.no.fish,lam.fish = lam.fish,
+                                    lam.org.no.fish = lam.org.no.fish,
+                                    lam.org.fish = lam.org.fish,
+                                    year=years[yy],meta.tmp)
+  } # End the yy loop to get the lambdas...
 # unpack it...
@@
 res.year.fin[[i]] <- do.call('rbind',res.year)
+res.lambda.fin[[i]] <-  do.call('rbind',res.lambda)
 }  # end if to make sure we have enough data to get the cohort estimates.
@@
 }# end the stock loop
+
 res.cohort.final <- do.call('rbind',res.fin)
 res.year.final <- do.call('rbind',res.year.fin)
+res.lambda.final <- do.call('rbind',res.lambda.fin)
 
@@
                                                                 R0.opt = sum(mx.lx.opt),R0.org = sum(mx.lx.org))
-pop.dam <- data.frame(pop.dam,Management=NA,Area = NA,Order=NA,
-                      Family=NA,Genus=NA,Species=NA,Model=NA,Meeting_or_reference = NA,Notes = NA)
-
-for(i in 1:n.stocks) 
-{
-  nam <- Stocks[i]
-  #  A quick way to get the other potentially interesting info for the stock...
-  meta <- ASR_long[ASR_long$Stock == nam,][1,]
-
-  pop.dam$Management[pop.dam$Stock == nam]   <- meta$Management  
-  pop.dam$Area[pop.dam$Stock == nam] <- meta$Area
-  if(nam == "NEFSC-GARMIII_GB_Gadus_morhua") pop.dam$Area[pop.dam$Stock == nam] <- "GB (West)"
-  pop.dam$Order[pop.dam$Stock == nam] <- meta$Order
-  pop.dam$Family[pop.dam$Stock == nam]   <- meta$Family  
-  pop.dam$Genus[pop.dam$Stock == nam]  <- meta$Genus 
-  pop.dam$Species[pop.dam$Stock == nam] <- meta$Species
-  pop.dam$Model[pop.dam$Stock == nam] <- meta$Model
-  pop.dam$Meeting_or_reference[pop.dam$Stock == nam] <- meta$Meeting_or_reference
-  pop.dam$Notes[pop.dam$Stock == nam] <- meta$Notes
-
-}
-
-pop.dam$Species[pop.dam$Species==" harengus"] <- "harengus"
-pop.dam$Species[pop.dam$Species=="Aeglefinus"] <- "aeglefinus"
-pop.dam$Species[pop.dam$Species=="Solea"] <- "solea"
+pop.dam <- left_join(pop.dam,meta.sub,by="Stock")
+
+dub.time.summary <- data.frame(dub.time.summary)
+pop.dam <- data.frame(pop.dam)
+# saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",model,".Rds"))
+# saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",model,".Rds"))
+# saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",model,".Rds"))
+save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
+     file=paste0("D:/Github/ICM/Results/all_cleaned_forward_tune_summaries_",model,".Rdata"))
+
+write.csv(meta.sub, "D:/Github/ICM/Data/metadata.csv")
 
@@
 ```{r simp-figs}
-
-ggplot(for.tunes) + geom_jitter(aes(y=lambda,x=Species,group=Stock,color=Stock)) + scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10))
-
-ggplot(for.tunes) + geom_jitter(aes(y=lambda.vpa.init,x=Species)) + scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))
-
-unique(for.tunes$Species)
-windows(11,11)
-ggplot(dub.time) + geom_jitter(aes(y=dt,x=Species),alpha=0.05,fill="black",color="black",shape=22) + 
-                   scale_y_continuous(name = 'Doubling time (years)',breaks = seq(0,100,by=5))
-
-ggplot(for.tunes) + geom_density(aes(lambda,group=Species,color=Species,fill=Species),alpha = 0.2) + scale_x_continuous(breaks = c(0,0.5,1,2,5,10))
-
-windows(11,11)
-ggplot(pop.dam) + geom_boxplot(aes(y=gen.len.opt,x=Species)) + ylab("Generation Length (years)")
-
-#options(scipen=999)
-r0.plt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
-                            scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.05,0.1,0.5,1,5,10,50,100),minor_breaks = NULL) + 
-                            facet_wrap(~Species,scales = 'free')+
-                            theme(axis.text.x = element_text(angle =45,hjust=1))
-save_plot("D:/Github/ICM/Figures/tuned/R0_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
-
-windows(11,11)
-r0.ts.plt <- ggplot(pop.dam) + geom_line(aes(y=R0.opt,x=cohort,group=Area,color=Area))  + 
-                            scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
-                            facet_wrap(~Species,scales = 'free')+
-                            theme(axis.text.x = element_text(angle =45,hjust=1))
-r0.ts.plt
-save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
-
-vickis.cols <- sort(rep(c( "#172582",  "#F8DC91", "#FBB891", "#FB6A01", "#B80000"),3))
-linetypes <- rep(c(1,2,4),5)
-
-windows(11,11)
-cod.r0.ts.plt <- ggplot(pop.dam %>% dplyr::filter(Species == 'morhua')) + geom_line(aes(y=R0.opt,x=cohort,group=Area,color=Area,linetype=Area),size=1.5)  + 
-                            scale_y_log10(name = "Lifetime Reproductive Output", breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
-                            scale_color_manual(values = vickis.cols) +
-                            scale_linetype_manual(values = linetypes) +
-                            theme(legend.key.width  = unit(2, "cm"))
-cod.r0.ts.plt
-#save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
-
-windows(11,11)
-ggplot(pop.dam %>% dplyr::filter(Species =="morhua")) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
-                                                        scale_y_log10(name = "Lifetime Reproductive Output",breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) +
-                                                        theme(axis.text.x = element_text(angle =45,hjust=1))
-
-# Missing catch questions
-# first did we do much to the Fecundity term to get here
-quantile(for.tunes$mean.fec/for.tunes$mean.vpa.fec,probs=seq(0.01,1,0.01),na.rm=T)
-
-quantile((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init,probs=seq(0.01,1,0.01),na.rm=T)
-quantile((for.tunes$mean.nm-for.tunes$mean.vpa.nm)/for.tunes$mean.vpa.nm,probs=seq(0.01,1,0.01),na.rm=T)
-
-for.tunes$excess.catch <- for.tunes$removals-for.tunes$removals.init
-for.tunes$per.excess.catch <- 100*((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init)
-
-windows(11,11)
-bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Species)) + 
-                                   ylab("Adjustment to catch (%)") +
-                                   theme(axis.text.x = element_text(angle=45,hjust = 1))
-
-save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_species.png",bycatch.plt,base_width = 8,base_height = 8)
-
-bycatch.plt.cod <- ggplot(for.tunes %>% dplyr::filter(Species == 'morhua')) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + 
-                                                                              ylab("Adjustment to catch (%)") +
-                                                                              theme(axis.text.x = element_text(angle=45,hjust = 1))
-
-save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_cod_stock.png",bycatch.plt.cod,base_width = 8,base_height = 8)
-
-bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + facet_wrap(~Species,scales = 'free_x')
-                                   ylab("Adjustment to catch (%)") +
-                                   theme(axis.text.x = element_text(angle=45,hjust = 1))
-
-```
+theme_set(theme_few(base_size = 14))
+model <- 'fec_nm'
+load(file=paste0("D:/Github/ICM/Results/all_cleaned_forward_tune_summaries_",model,".Rdata"))
+
+pop.dam.6 <- pop.dam %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
+for.tunes.6 <- for.tunes %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
+res.lambda.final.6 <- res.lambda.final %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
+dub.time.6 <- dub.time.summary %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
+# Lambda plot
+
+res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(LME,Area.broad) %>%
+                                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+
+res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(Species,Area.broad) %>%
+                                             dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
+
+res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::group_by(Stock) %>% 
+                                            dplyr::mutate(lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
+                                                          lam.fish.mn = mean(lam.fish,na.rm=T),
+                                                          lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
+                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T))
+
+#hmm <- merge(tst,res.lambda.final.6,by="Stock")
+
+# So this is lambda with fishing included
+lambda.plt <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.no.fish,x=Stock.no.species))  + 
+                                           geom_point(aes(y=lam.no.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
+                                           xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10)) + 
+                                           geom_hline(yintercept = 1,linetype='dashed') +
+                                           facet_wrap(~G.Species,scales='free')+
+                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
+                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+
+save_plot("D:/Github/ICM/Figures/tuned/lambda_no_fishing_6.png",lambda.plt,base_width = 12,base_height = 10)
+
+# With fishing
+lambda.plt.fish <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.fish,x=Stock.no.species))  + 
+                                           geom_point(aes(y=lam.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
+                                           xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10)) + 
+                                           geom_hline(yintercept = 1,linetype='dashed') +
+                                           facet_wrap(~G.Species,scales='free')+
+                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
+                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+
+save_plot("D:/Github/ICM/Figures/tuned/lambda_with_fishing_6.png",lambda.plt.fish,base_width = 12,base_height = 10)
+
+# Time series of lambdas....
+col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
+#col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
+pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
+#pty <- rep(rep(c(21:23),5),20)
+
+lambda.ts.plt <- ggplot(res.lambda.final.6,aes(y=lam.fish,x=year,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
+                            geom_point(size=4) +
+                            geom_smooth(method='gam',formula = y ~ s(x, bs = "cs", fx = TRUE, k = 5),se=F) + 
+                            #scale_y_log10(name = "lambda") +
+                            facet_wrap(~G.Species,scales='free_y') +
+                            scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
+                            scale_fill_manual(name = "Stock",values = col.try)+
+                            guides(colour = guide_legend(ncol = 1))+
+                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm'))
+#lambda.ts.plt
+save_plot("D:/Github/ICM/Figures/tuned/lambda_timeseries_6.png",lambda.ts.plt,base_width = 12,base_height = 10)
+
+res.lambda.final.6$decade <- floor(res.lambda.final.6$year/10)*10
+
+tst <- res.lambda.final.6 %>% dplyr::group_by(Stock,decade) %>% dplyr::summarise(mn.lam = mean(lam.fish,na.rm=T),
+                                                                                 med.lam = median(lam.fish,na.rm=T),
+                                                                                 sd.lam = sd(lam.fish,na.rm=T))
+tst <- merge(tst,meta.sub,by="Stock")
+
+tst <- tst %>% dplyr::arrange(Species,Area.broad) %>%
+                                             dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
+
+lambda.dec.mn.plt <- ggplot(tst,aes(y=mn.lam,x=decade,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
+                            geom_jitter(size=4,width = 1) +
+                            scale_x_continuous(breaks=seq(1940,2020,by=10))+
+                            geom_hline(yintercept = 1,linetype='dashed') +
+                            facet_wrap(~G.Species,scales='free_y') +
+                            scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
+                            scale_fill_manual(name = "Stock",values = col.try)+
+                            guides(colour = guide_legend(ncol = 1))+
+                            theme(legend.key.width = unit(5,'cm'))
+save_plot("D:/Github/ICM/Figures/tuned/lambda_decades_mean.png",lambda.dec.mn.plt,base_width = 30,base_height = 12)
+
+lambda.dec.med.plt <- ggplot(tst,aes(y=med.lam,x=decade,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
+                            geom_jitter(size=4,width = 1) +
+                            scale_x_continuous(breaks=seq(1940,2020,by=10))+
+                            geom_hline(yintercept = 1,linetype='dashed') +
+                            facet_wrap(~G.Species,scales='free_y') +
+                            scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
+                            scale_fill_manual(name = "Stock",values = col.try)+
+                            guides(colour = guide_legend(ncol = 1))+
+                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm'))
+save_plot("D:/Github/ICM/Figures/tuned/lambda_decades_median.png",lambda.dec.med.plt,base_width = 30,base_height = 12)
+
+# Doubling Times
+# Reorder the doubling time, either by Species and LME, or the other way around
+dub.time.summary <- dub.time.summary %>%
+                            dplyr::arrange(Species,LME) %>%
+                            dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
+
+dub.heatmap.ne <- ggplot(dub.time.summary %>% dplyr::filter(LME == "NE Atlantic"), aes(x=year, y=Stock.short, fill= prop)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") +
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
+
+dub.heatmap.nw <- ggplot(dub.time.summary %>% dplyr::filter(LME == "NW Atlantic"), aes(x=year, y=Stock.short, fill= prop)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
+
+dub.heatmap.pac <- ggplot(dub.time.summary %>% dplyr::filter(LME == "Pacific (Alaska)"), aes(x=year, y=Stock.short, fill= prop)) + xlab("") + ylab("")+
+                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
+                                  legend.key.width = unit(3,'cm'))
+
+dub.heatmap <- cowplot::plot_grid(dub.heatmap.pac,dub.heatmap.nw,dub.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
+dub.heatmap
+
+save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap.png",dub.heatmap,base_width = 20,base_height = 17)
+
+dub.time.6 <- dub.time.6 %>%
+                            dplyr::arrange(LME) %>%
+                            dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+
+dub.heatmap.cod <- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "G.
+morhua"), aes(x=year, y=Stock.no.species, fill= prop)) + xlab("") + ylab("")+                                     facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") +
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + scale_x_continuous(labels=NULL) +
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"))
+
+dub.heatmap.herring<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "C. harengus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+                              xlab("") + ylab("")+                                    
+                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
+
+dub.heatmap.haddock<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "M. aeglefinus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+                              xlab("") + ylab("")+                                    
+                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.125, "cm"))
+
+dub.heatmap.virens<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "P. virens"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+                              xlab("") + ylab("")+                                    
+                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.4, "cm"))
+
+dub.heatmap.solea<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "S. solea"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+                              xlab("") + ylab("")+                                    
+                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
+
+dub.heatmap.platessa<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "P. platessa"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+                              xlab("") + ylab("")+                                    
+                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous() +
+                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
+
+dub.heatmap.sp6 <- cowplot::plot_grid(dub.heatmap.cod,dub.heatmap.herring,dub.heatmap.haddock,
+                                 dub.heatmap.virens, dub.heatmap.solea,dub.heatmap.platessa,nrow = 6,rel_heights = c(14,9,8,5,5,4))
+dub.heatmap.sp6
+
+save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap_by_sp6.png",dub.heatmap.sp6,base_width = 20,base_height = 17)
+
+# Generation length
+pop.dam <- pop.dam %>% dplyr::arrange(Species,LME) %>%
+                       dplyr::mutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
+
+pop.dam.6 <- pop.dam.6 %>% dplyr::arrange(LME,Area.broad) %>%
+                       dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+
+gen.boxplt <- ggplot(pop.dam.6) +
+                            geom_boxplot(aes(y=gen.len.opt,x=Stock.no.species))  + 
+                            xlab("") + scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
+                            facet_wrap(~G.Species,scales='free_x')+
+                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',plot.margin = margin(0,0.5,0,0.5, "cm"),
+                                  axis.title.y = element_text(margin = margin(r = 30)))
+
+save_plot("D:/Github/ICM/Figures/tuned/GL_boxplot_no_fish_6_species.png",gen.boxplt,base_width = 12,base_height = 10)
+
+gen.heatmap.ne <- ggplot(pop.dam %>% dplyr::filter(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
+                                              xlab("") + ylab("")+  
+                                              facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
+                                              geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
+                                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
+
+gen.heatmap.nw <- ggplot(pop.dam %>% dplyr::filter(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
+
+gen.heatmap.pac <- ggplot(pop.dam %>% dplyr::filter(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
+                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
+                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
+                                  legend.key.width = unit(3,'cm'))
+
+gen.heatmap <- cowplot::plot_grid(gen.heatmap.pac,gen.heatmap.nw,gen.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
+gen.heatmap
+
+save_plot("D:/Github/ICM/Figures/tuned/gen_heatmap.png",gen.heatmap,base_width = 20,base_height = 17)
+
+# Lifetime reproductive success (no fishing)
+r0.heatmap.ne <- ggplot(pop.dam %>% dplyr::filter(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
+                                    xlab("") + ylab("")+
+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
+                                    geom_tile() + 
+                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
+                                                        discrete=FALSE,trans='log') + 
+                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
+
+r0.heatmap.nw <- ggplot(pop.dam %>% dplyr::filter(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
+                                    xlab("") + ylab("")+
+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                                    geom_tile() + 
+                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
+                                                        discrete=FALSE,trans='log') + 
+                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
+
+r0.heatmap.pac <- ggplot(pop.dam %>% dplyr::filter(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
+                                     xlab("") + ylab("")+
+                                     facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                                     geom_tile() + 
+                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
+                                                        discrete=FALSE,trans='log') + 
+                                     theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
+                                           legend.key.width = unit(3,'cm'))
+
+r0.heatmap <- cowplot::plot_grid(r0.heatmap.pac,r0.heatmap.nw,r0.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
+r0.heatmap
+
+save_plot("D:/Github/ICM/Figures/tuned/r0_heatmap.png",r0.heatmap,base_width = 20,base_height = 17)
+
+r0.boxplt <- ggplot(pop.dam.6) +
+                            geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
+                            xlab("") + scale_y_log10(name = "Lifetime Reproductive Output")+
+                            facet_wrap(~G.Species,scales = 'free')+
+                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',plot.margin = margin(0,0.5,0,0.5, "cm"),
+                                  axis.title.y = element_text(margin = margin(r = 30)))
+
+save_plot("D:/Github/ICM/Figures/tuned/R0_boxplot_no_fish_6_species.png",r0.boxplt,base_width = 12,base_height = 10)
+
+# Other figures....
+
+# windows(11,11)
+# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
+# pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
+
+# 
+# r0.ts.plt <- ggplot(pop.dam.6,aes(y=R0.opt,x=cohort,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) + 
+#                             geom_line(size=2)  + geom_point(size=4) +
+#                             scale_y_log10(name = "Lifetime Reproductive Output") +
+#                             facet_wrap(~G.Species) +
+#                             scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
+#                             scale_fill_manual(name = "Stock",values = col.try)+
+#                             guides(colour = guide_legend(ncol = 1))+
+#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
+# r0.ts.plt
+# 
+# save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_6.png",r0.ts.plt,base_width = 30,base_height = 12)
+# 
+# r0.boxplt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
+#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
+#                             facet_wrap(~G.Species,scales = 'free')+
+#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none')
+# r0.boxplt
+
+# 
+# windows(11,11)
+# ggplot(pop.dam) + geom_boxplot(aes(y=gen.len.opt,x=Species)) + facet_wrap(~LME,scales='free_x') +
+#                   ylab("Generation Length (years)") + theme(axis.text.x = element_text(angle =45,hjust=1))
+# 
+# windows(11,11)
+# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
+# lty <- rep(c(rep(1,5),rep(2,5),rep(4,5)),20)
+# 
+# gen.ts.plt <- ggplot(pop.dam.6,aes(y=gen.len.opt,x=cohort,group=Stock.short,color=Stock.short,linetype = Stock.short)) + 
+#                             geom_line(size=2)  + 
+#                             scale_y_log10(name = "Generation Length") +
+#                             facet_wrap(~G.Species) +
+#                             scale_color_manual(name = "Stock",values = col.try) + scale_linetype_manual(name = "Stock",values = lty) +
+#                             guides(colour = guide_legend(ncol = 1))+
+#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
+# gen.ts.plt
+# save_plot("D:/Github/ICM/Figures/tuned/Gen_time_series_6.png",gen.ts.plt,base_width = 20,base_height = 12)
+
+# 
+# ggplot(for.tunes) + geom_jitter(aes(y=lambda,x=Species,group=Stock.short,color=Stock.short)) + 
+#                     scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10)) +
+#                             theme(axis.text.x = element_text(angle =45,hjust=1))
+# 
+# ggplot(for.tunes) + geom_jitter(aes(y=lambda.vpa.init,x=Species)) + scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))
+# 
+# unique(for.tunes$Species)
+# windows(11,11)
+# 
+# ggplot(for.tunes) + geom_density(aes(lambda,group=Species,color=Species,fill=Species),alpha = 0.2) + scale_x_continuous(breaks = c(0,0.5,1,2,5,10))
+# 
+# 
+# #options(scipen=999)
+# r0.plt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
+#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.05,0.1,0.5,1,5,10,50,100),minor_breaks = NULL) + 
+#                             facet_wrap(~Species,scales = 'free')+
+#                             theme(axis.text.x = element_text(angle =45,hjust=1))
+# save_plot("D:/Github/ICM/Figures/tuned/R0_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
+# 
+# 
+# 
+# vickis.cols <- sort(rep(c( "#172582",  "#F8DC91", "#FBB891", "#FB6A01", "#B80000"),3))
+# linetypes <- rep(c(1,2,4),5)
+# 
+# windows(11,11)
+# cod.r0.ts.plt <- ggplot(pop.dam %>% dplyr::filter(Species == 'morhua')) + geom_line(aes(y=R0.opt,x=cohort,group=Area,color=Area,linetype=Area),size=1.5)  + 
+#                             scale_y_log10(name = "Lifetime Reproductive Output", breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
+#                             scale_color_manual(values = vickis.cols) +
+#                             scale_linetype_manual(values = linetypes) +
+#                             theme(legend.key.width  = unit(2, "cm"))
+# cod.r0.ts.plt
+# #save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
+# 
+# 
+# windows(11,11)
+# ggplot(pop.dam %>% dplyr::filter(Species =="morhua")) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
+#                                                         scale_y_log10(name = "Lifetime Reproductive Output",breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) +
+#                                                         theme(axis.text.x = element_text(angle =45,hjust=1))
+# 
+# # Missing catch questions
+# # first did we do much to the Fecundity term to get here
+# quantile(for.tunes$mean.fec/for.tunes$mean.vpa.fec,probs=seq(0.01,1,0.01),na.rm=T)
+# 
+# quantile((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init,probs=seq(0.01,1,0.01),na.rm=T)
+# quantile((for.tunes$mean.nm-for.tunes$mean.vpa.nm)/for.tunes$mean.vpa.nm,probs=seq(0.01,1,0.01),na.rm=T)
+# 
+# for.tunes$excess.catch <- for.tunes$removals-for.tunes$removals.init
+# for.tunes$per.excess.catch <- 100*((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init)
+# 
+# windows(11,11)
+# bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Species)) + 
+#                                    ylab("Adjustment to catch (%)") +
+#                                    theme(axis.text.x = element_text(angle=45,hjust = 1))
+#                                    
+# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_species.png",bycatch.plt,base_width = 8,base_height = 8)
+#                                    
+# bycatch.plt.cod <- ggplot(for.tunes %>% dplyr::filter(Species == 'morhua')) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + 
+#                                                                               ylab("Adjustment to catch (%)") +
+#                                                                               theme(axis.text.x = element_text(angle=45,hjust = 1))
+#                                                                               
+# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_cod_stock.png",bycatch.plt.cod,base_width = 8,base_height = 8)
+# 
+# # bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + facet_wrap(~Species,scales = 'free_x')
+# #                                    ylab("Adjustment to catch (%)") +
+# #                                    theme(axis.text.x = element_text(angle=45,hjust = 1))
+# # bycatch.plt                                   
+#

### 2023-11-29 Scripts/functions/simple_Lotka_r.r

@@ -4,7 +4,7 @@
 # Z:    Total mortality, 
 # fecund:      Fecundity
 # ages:
-
+ 
 simple.lotka.r<-function(Z = NULL,fecund = NULL,ages = NULL) 
 {  
   

### 2023-12-29 Scripts/Paper_1.Rmd
End of year update
Don't even remember what I did

@@
 library(cowplot)
+library(gtable)
+library(viridis)
 loc <- 'D:/GitHub/ICM'
@@
 dt.res <- NULL
-n.dt.sims <- 20 # Number of simultions...
+n.dt.sims <- 2000 # Number of simulations...
 n.years <- 100
@@
     fs <- NA
-    lx <- 1
+    # The lx is no fishing survivorship, zx I'm calling the survivorship including fishing
+    lx <- lx.org <- lx.year <- zx <- zx.org <- zx.year <- 1
     fs.org <- NA
-    lx.org <- 1
-    lx.year <- 1
+
     for(a in 1:n.ages)
@@
     {
+      # No fishing
       lx[a] <- lx[a-1] * m.tmp[y+count,a]  
@@
       lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
+      # Including fishing
+      zx[a] <- zx[a-1] * z.tmp[y+count,a]  
+      zx.org[a] <- zx.org[a-1]* z.org.tmp[y+count,a]  
+      zx.year[a] <- zx.year[a-1] * z.tmp[y,a]
     }  # end the a > 1 if
@@
     }# end the ages loop
-        res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,lx.org = lx.org,age = ages,
+        res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,lx.opt = lx,
                                mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
                                x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
-                               cohort=years[y],meta.tmp)
-
-        res.year[[y]] <- data.frame(mx.opt = unlist(fec.tmp[y,]),lx.opt = lx.year,age = ages,
+                               zx.opt = zx,zx.opt = zx,
+                               mx.zx.opt = fs*zx,mx.zx.org = fs.org*zx.org,
+                               x.mx.zx.opt = fs*zx*ages,x.mx.zx.org = fs.org*zx.org*ages,
+                               cohort=years[y],age = ages,meta.tmp)
+
+        res.year[[y]] <- data.frame(mx.opt = unlist(fec.tmp[y,]),lx.opt = lx.year,
                                mx.lx.opt = unlist(fec.tmp[y,])*lx.year,
                                x.mx.lx.opt = unlist(fec.tmp[y,])*lx.year*ages,
-                               year=years[y],meta.tmp)
+                               zx.opt = zx.year,
+                               mx.zx.opt = unlist(fec.tmp[y,])*lx.year,
+                               x.mx.zx.opt = unlist(fec.tmp[y,])*lx.year*ages,
+                               age = ages,year=years[y],meta.tmp)
 
@@
 load(file=paste0("D:/Github/ICM/Results/all_cleaned_forward_tune_summaries_",model,".Rdata"))
-
-pop.dam.6 <- pop.dam %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
-for.tunes.6 <- for.tunes %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
-res.lambda.final.6 <- res.lambda.final %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
-dub.time.6 <- dub.time.summary %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
-# Lambda plot
-
-res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(LME,Area.broad) %>%
-                                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(Species,Area.broad) %>%
-                                             dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::group_by(Stock) %>% 
+pop.dam <- data.frame(pop.dam)
+six.species <- c('morhua','harengus','aeglefinus','virens','solea','platessa')
+pop.dam.6 <- pop.dam %>% dplyr::filter(Species %in% six.species)
+for.tunes.6 <- for.tunes %>% dplyr::filter(Species %in% six.species)
+dub.time.6 <- dub.time.summary %>% dplyr::filter(Species %in% six.species)
+res.lambda.final$decade <- floor(res.lambda.final$year/10)*10
+res.lambda.final <- res.lambda.final %>% dplyr::group_by(Stock,decade) %>% dplyr::mutate(mn.lam = mean(lam.fish,na.rm=T),
+                                                                                 med.lam = median(lam.fish,na.rm=T),
+                                                                                 sd.lam = sd(lam.fish,na.rm=T))
+res.lambda.final <- res.lambda.final %>% dplyr::group_by(Species,decade) %>% dplyr::mutate(lm.spec.mn = mean(mn.lam,na.rm=T))              
+res.lambda.final <- res.lambda.final %>% dplyr::group_by(Stock) %>% 
                                             dplyr::mutate(lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
@@
                                                           lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T))
+                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T),
+                                                          lam.no.fish.med = median(lam.no.fish,na.rm=T),
+                                                          lam.fish.med = median(lam.fish,na.rm=T),
+                                                          lam.org.no.fish.med = median(lam.org.no.fish,na.rm=T),
+                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T),) %>% data.frame()
+
+res.lambda.final.6 <- res.lambda.final %>% dplyr::filter(Species %in% six.species)
+# Sort the data into a nice order...
+res.lambda.final <- res.lambda.final %>% dplyr::arrange(Species,Area.broad) %>%
+                                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(Species,Area.broad) %>%
+                                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+dub.time <- dub.time %>% dplyr::arrange(LME) %>%
+                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+
+dub.time.summary <- dub.time.summary %>% dplyr::arrange(LME,Order,Species,Area.broad) %>%
+                                         dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
+
+dub.time.6 <- dub.time.6 %>% dplyr::arrange(LME) %>%
+                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+pop.dam <- pop.dam %>% dplyr::arrange(Species,LME) %>%
+                       dplyr::mutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
+pop.dam.6 <- pop.dam.6 %>% dplyr::arrange(LME,Area.broad) %>%
+                       dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+
+# Lambda plots
+
+# res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(LME,Area.broad) %>%
+#                                              dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+
+################### Figures in main text################### Figures in main text################### Figures in main text###################
 
 #hmm <- merge(tst,res.lambda.final.6,by="Stock")
-
+plot(res.lambda.final$lam.fish.med ~ res.lambda.final$lam.fish.mn)
 # So this is lambda with fishing included
@@
 save_plot("D:/Github/ICM/Figures/tuned/lambda_with_fishing_6.png",lambda.plt.fish,base_width = 12,base_height = 10)
+
+# Doubling Times
+
+dub.heatmap.cod <- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "G.
+morhua"), aes(x=year, y=Stock.no.species, fill= prop)) + xlab("") + ylab("")+                                     facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") +
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + scale_x_continuous(labels=NULL) +
+                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
+                                  legend.key.width = unit(3,'cm'))
+
+dub.heatmap.herring<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "C. harengus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+                              xlab("") + ylab("")+                                    
+                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
+
+dub.heatmap.haddock<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "M. aeglefinus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+                              xlab("") + ylab("")+                                    
+                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.125, "cm"))
+
+dub.heatmap.virens<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "P. virens"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+                              xlab("") + ylab("")+                                    
+                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.4, "cm"))
+
+dub.heatmap.solea<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "S. solea"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+                              xlab("") + ylab("")+                                    
+                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
+
+dub.heatmap.platessa<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "P. platessa"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+                              xlab("") + ylab("")+                                    
+                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous() +
+                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
+
+dub.heatmap.sp6 <- cowplot::plot_grid(dub.heatmap.cod,dub.heatmap.herring,dub.heatmap.haddock,
+                                 dub.heatmap.virens, dub.heatmap.solea,dub.heatmap.platessa,nrow = 6,rel_heights = c(14,9,8,5,5,4))
+dub.heatmap.sp6
+
+save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap_by_sp6.png",dub.heatmap.sp6,base_width = 20,base_height = 17)
+
+# Generation length
+
+gen.boxplt <- ggplot(pop.dam.6) +
+                            geom_boxplot(aes(y=gen.len.opt,x=Stock.no.species))  + 
+                            xlab("") + scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
+                            facet_wrap(~G.Species,scales='free_x')+
+                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',plot.margin = margin(0,0.5,0,0.5, "cm"),
+                                  axis.title.y = element_text(margin = margin(r = 30)))
+
+save_plot("D:/Github/ICM/Figures/tuned/GL_boxplot_no_fish_6_species.png",gen.boxplt,base_width = 12,base_height = 10)
+
+# Lifetime reproductive success (no fishing)
+
+r0.boxplt <- ggplot(pop.dam.6) +
+                            geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
+                            xlab("") + scale_y_log10(name = "Lifetime Reproductive Output")+
+                            geom_hline(yintercept = 1,linetype='dashed',color='blue')+
+                            facet_wrap(~G.Species,scales = 'free')+
+                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',plot.margin = margin(0,0.5,0,0.5, "cm"),
+                                  axis.title.y = element_text(margin = margin(r = 30)))
+
+save_plot("D:/Github/ICM/Figures/tuned/R0_boxplot_no_fish_6_species.png",r0.boxplt,base_width = 12,base_height = 10)
+
+################### Supplemental Figures################### Supplemental Figures################### Supplemental Figures################### Supplemental
+
+# Reorder the doubling time, either by Species and LME, or the other way around
+
+dub.time.summary$Order.short <- "Gadi"
+dub.time.summary$Order.short[dub.time.summary$Order == "Pleuronectiformes"] <- "Plero"
+dub.time.summary$Order.short[dub.time.summary$Order == "Clupeiformes"] <- "Clupei"
+dub.time.summary$Order.short[dub.time.summary$Order == "Scorpaeniformes "] <- "Scor"
+dub.time.summary$Order.short[dub.time.summary$Order == "Scombriformes"] <- "Scomb"
+dub.time.summary$Order.short[dub.time.summary$Order == "Perciformes"] <- "Perci"
+
+dub.time.summary <- dub.time.summary %>%
+                            dplyr::arrange(G.Species,LME,Area.broad) %>%
+                            dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
+
+dub.heatmap.gad <- ggplot(dub.time.summary %>% dplyr::filter(Order == "Gadiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
+                            xlab("") + ylab("")+                                    
+                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.45, "cm"),
+                                  legend.key.width = unit(3,'cm'))
+
+dub.heatmap.pl <- ggplot(dub.time.summary %>% dplyr::filter(Order == "Pleuronectiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
+                            xlab("") + ylab("")+                                    
+                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"))
+
+dub.heatmap.cl <- ggplot(dub.time.summary %>% dplyr::filter(Order == "Clupeiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
+                            xlab("") + ylab("")+
+                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.35, "cm"),
+                                  legend.key.width = unit(3,'cm'))
+
+dub.heatmap.per <- ggplot(dub.time.summary %>% dplyr::filter(Order == "Perciformes"), aes(x=year, y=Stock.short, fill= prop)) + 
+                            xlab("") + ylab("")+
+                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2, "cm"),
+                                  legend.key.width = unit(3,'cm'))
+
+dub.heatmap.scom <- ggplot(dub.time.summary %>% dplyr::filter(Order == "Scombriformes"), aes(x=year, y=Stock.short, fill= prop)) + 
+                            xlab("") + ylab("")+
+                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2.1, "cm"),
+                                  legend.key.width = unit(3,'cm'))
+
+dub.heatmap.scorp <- ggplot(dub.time.summary %>% dplyr::filter(Order %in% "Scorpaeniformes "), aes(x=year, y=Stock.short, fill= prop)) + 
+                            xlab("") + ylab("")+
+                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + 
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.5, "cm"),
+                                  legend.key.width = unit(3,'cm'))
+
+dub.heatmap <- cowplot::plot_grid(dub.heatmap.gad,dub.heatmap.pl,dub.heatmap.cl,dub.heatmap.per,dub.heatmap.scom,dub.heatmap.scorp,
+                                  nrow = 6,rel_heights = c(39,20,11,4,3,3))
+dub.heatmap
+
+save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap_by_order.png",dub.heatmap,base_width = 20,base_height = 20)
 
@@
 
-res.lambda.final.6$decade <- floor(res.lambda.final.6$year/10)*10
-
-tst <- res.lambda.final.6 %>% dplyr::group_by(Stock,decade) %>% dplyr::summarise(mn.lam = mean(lam.fish,na.rm=T),
-                                                                                 med.lam = median(lam.fish,na.rm=T),
-                                                                                 sd.lam = sd(lam.fish,na.rm=T))
-tst <- merge(tst,meta.sub,by="Stock")
-
-tst <- tst %>% dplyr::arrange(Species,Area.broad) %>%
-                                             dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-lambda.dec.mn.plt <- ggplot(tst,aes(y=mn.lam,x=decade,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
-                            geom_jitter(size=4,width = 1) +
-                            scale_x_continuous(breaks=seq(1940,2020,by=10))+
+lambda.dec.plt <- ggplot(res.lambda.final.6,aes(y=med.lam,x=as.factor(decade))) +
+                            geom_boxplot() + scale_y_log10()+
+                            xlab("Decade") + ylab("Lambda") + 
+                            geom_point(aes(x=as.factor(decade),y=lm.spec.mn),color='blue',shape=8,fill='blue')+
+                            #scale_x_continuous(breaks=seq(1940,2020,by=10))+
                             geom_hline(yintercept = 1,linetype='dashed') +
-                            facet_wrap(~G.Species,scales='free_y') +
-                            scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-                            scale_fill_manual(name = "Stock",values = col.try)+
-                            guides(colour = guide_legend(ncol = 1))+
-                            theme(legend.key.width = unit(5,'cm'))
-save_plot("D:/Github/ICM/Figures/tuned/lambda_decades_mean.png",lambda.dec.mn.plt,base_width = 30,base_height = 12)
-
-lambda.dec.med.plt <- ggplot(tst,aes(y=med.lam,x=decade,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
-                            geom_jitter(size=4,width = 1) +
-                            scale_x_continuous(breaks=seq(1940,2020,by=10))+
-                            geom_hline(yintercept = 1,linetype='dashed') +
-                            facet_wrap(~G.Species,scales='free_y') +
-                            scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-                            scale_fill_manual(name = "Stock",values = col.try)+
-                            guides(colour = guide_legend(ncol = 1))+
-                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm'))
-save_plot("D:/Github/ICM/Figures/tuned/lambda_decades_median.png",lambda.dec.med.plt,base_width = 30,base_height = 12)
-
-# Doubling Times
-# Reorder the doubling time, either by Species and LME, or the other way around
-dub.time.summary <- dub.time.summary %>%
-                            dplyr::arrange(Species,LME) %>%
-                            dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-dub.heatmap.ne <- ggplot(dub.time.summary %>% dplyr::filter(LME == "NE Atlantic"), aes(x=year, y=Stock.short, fill= prop)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-dub.heatmap.nw <- ggplot(dub.time.summary %>% dplyr::filter(LME == "NW Atlantic"), aes(x=year, y=Stock.short, fill= prop)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-dub.heatmap.pac <- ggplot(dub.time.summary %>% dplyr::filter(LME == "Pacific (Alaska)"), aes(x=year, y=Stock.short, fill= prop)) + xlab("") + ylab("")+
-                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap <- cowplot::plot_grid(dub.heatmap.pac,dub.heatmap.nw,dub.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-dub.heatmap
-
-save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap.png",dub.heatmap,base_width = 20,base_height = 17)
-
-dub.time.6 <- dub.time.6 %>%
-                            dplyr::arrange(LME) %>%
-                            dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-dub.heatmap.cod <- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "G.
-morhua"), aes(x=year, y=Stock.no.species, fill= prop)) + xlab("") + ylab("")+                                     facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + scale_x_continuous(labels=NULL) +
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"))
-
-dub.heatmap.herring<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "C. harengus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-                              xlab("") + ylab("")+                                    
-                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-
-dub.heatmap.haddock<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "M. aeglefinus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-                              xlab("") + ylab("")+                                    
-                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.125, "cm"))
-
-dub.heatmap.virens<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "P. virens"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-                              xlab("") + ylab("")+                                    
-                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.4, "cm"))
-
-dub.heatmap.solea<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "S. solea"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-                              xlab("") + ylab("")+                                    
-                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-
-dub.heatmap.platessa<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "P. platessa"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-                              xlab("") + ylab("")+                                    
-                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous() +
-                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
-
-dub.heatmap.sp6 <- cowplot::plot_grid(dub.heatmap.cod,dub.heatmap.herring,dub.heatmap.haddock,
-                                 dub.heatmap.virens, dub.heatmap.solea,dub.heatmap.platessa,nrow = 6,rel_heights = c(14,9,8,5,5,4))
-dub.heatmap.sp6
-
-save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap_by_sp6.png",dub.heatmap.sp6,base_width = 20,base_height = 17)
-
-# Generation length
-pop.dam <- pop.dam %>% dplyr::arrange(Species,LME) %>%
-                       dplyr::mutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
-
-pop.dam.6 <- pop.dam.6 %>% dplyr::arrange(LME,Area.broad) %>%
-                       dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-gen.boxplt <- ggplot(pop.dam.6) +
-                            geom_boxplot(aes(y=gen.len.opt,x=Stock.no.species))  + 
-                            xlab("") + scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
-                            facet_wrap(~G.Species,scales='free_x')+
-                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',plot.margin = margin(0,0.5,0,0.5, "cm"),
-                                  axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot("D:/Github/ICM/Figures/tuned/GL_boxplot_no_fish_6_species.png",gen.boxplt,base_width = 12,base_height = 10)
+                            facet_wrap(~G.Species,scales='free_y') 
+save_plot("D:/Github/ICM/Figures/tuned/lambda_by_decade_6.png",lambda.dec.plt,base_width = 12,base_height = 12)
 
@@
 
-# Lifetime reproductive success (no fishing)
 r0.heatmap.ne <- ggplot(pop.dam %>% dplyr::filter(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
@@
 save_plot("D:/Github/ICM/Figures/tuned/r0_heatmap.png",r0.heatmap,base_width = 20,base_height = 17)
-
-r0.boxplt <- ggplot(pop.dam.6) +
-                            geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
-                            xlab("") + scale_y_log10(name = "Lifetime Reproductive Output")+
-                            facet_wrap(~G.Species,scales = 'free')+
-                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',plot.margin = margin(0,0.5,0,0.5, "cm"),
-                                  axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot("D:/Github/ICM/Figures/tuned/R0_boxplot_no_fish_6_species.png",r0.boxplt,base_width = 12,base_height = 10)
 
@@
 #
+
+# Doubling time for the rest of the stocks...
+
+# dub.heatmap.no.6 <- ggplot(dub.time.summary %>% dplyr::filter(!Species %in% six.species), aes(x=year, y=Stock.short, fill= prop)) + 
+#                               xlab("") + ylab("")+                                    
+#                               #facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + 
+#                               scale_x_continuous() +
+#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))

### 2024-04-09 Scripts/Paper_1.Rmd
Tidy up
Tweaked a couple of function and began annotating the functions and scripts better

@@
 
-#DK PICK IT UP HERE#
-# OK So the problem isn't so much "high" recruitment events, it's years in which the population abundance jumps like crash, Stock 57 (ICES Haddock NS)
-# Is the best example, look at year 2005, it isn't a outlier in terms of numbers of recruits, but the population jump from 2004 to 2005 is huge and
-# thus it's those years that get us the crazy fecundity numbers, which can easily be ameliorated by having a small fecundity in the age classes
-# that aren't supposed to be mature yet.  Of course, is that BS, maybe!!  Ended the night running all the stocks trying to see what the changes so far brought about.
-
-back.tune.all.res <- NULL
-back.tune.summary <- NULL
 for.tune.all.res <- NULL
@@
 
-   # fast.back.tune <- fast.tunes(years,
-   #                         tuner='fm',
-   #                         step.size = 0.01, # Make sure n.steps is even please!!
-   #                         abund.ts = all.abund,
-   #                         ages=ages,
-   #                         nm = -(log(1-prop.nat.mort)),
-   #                         fecund = mx,
-   #                         fm = fs,
-   #                         abund.age = full.abund, 
-   #                         catch.age = full.rem, 
-   #                         N.init = N.end,
-   #                         direction= 'backwards'
-   #                         )
-   # 
-   # back.tune.all.res[[i]] <- fast.back.tune
-   # back.tune.tmp <- data.frame(fast.back.tune$res,Stock = i)
-   # back.tune.summary[[i]] <- back.tune.tmp
-
 }
@@
 # ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus # lotka error
-
-# Fixed...
-#ICES-HAWG_NS_Ammodytes_dubius Overshoot
-# ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii  Overshoot
-#ICES-WGNSSK_NS 4-7d,20_Gadus_morhua Overshoot
-# ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus Overshoot
-# ICES-WGCSE_ISbc-ek_Melanogrammus_aeglefinus  Overshoot
 

### 2024-04-09 Scripts/archive/NS_tuning_models.Rmd
Tidy up
Tweaked a couple of function and began annotating the functions and scripts better

--- 2023-06-09 Scripts/NS_tuning_models.Rmd
@@
   age.mat <- am.tmp[[i]]
-
+  # Esmarkii recruitment collapses in year 27 and it screws the r in that year... model fits easily with this tweak
+  # Which is still an mx of like 0.25 of mean, so still shit recruitment....
+  if(i == Stocks[2]) mx[27,] <- 4*mx[27,] # mx[27,] <- colMeans(mx)
 #
@@
    tunes <- tune.sim(years,
-                     n.steps = 10,
+                     n.steps = 20,
                      tune.par=0.1,
@@
                      pop.model = 'exponential',
-                     tuner = "nm")
+                     tuner = "fec",
+                     CC = max(vpa.abund))
 

### 2024-04-09 Scripts/functions/forward_project.r

@@ -1,26 +1,17 @@
-# The analogue of the backword projection function.... but to forward project
+# Very simple model that projects the population forward using exponential or logistic models
 
 # Arguments
 #option:         So far we can do exponential or logistic growth, other options are on the table if someone has a good one
 #pop.last:       The population size in year t-1, which is used to estimate the size of the population in year t
-#r:              The intrinsic rate of growth for the population
+#r:              The rate of growth for the population
 #K:              The carrying capacity, only necessary for logistic model
                  
  
 for.proj <- function(option = "exponential",pop.last,r,K)
 {
   ### So rolling with the easy peasy continuous time exponential
-  ### simple exponential population growth, in this formulation with the removals I think I'm saying the removals happen right at the outset
   if(option == 'exponential') Pop.current <- (pop.last)*((exp(r)))
-
   # Logistic growth model, 
-  # The maths be.... N(t+1) = N(t) + rN(t)(1-N(t)/K).... now we are solving for N(t) not N(t+1), so we rearrange terms
-  # to get it in the quadratic formula....  (r/K)N^2 -(1+r)N  + N(t+1) = 0... we have r, K, and N(t+1) so we can solve for N(t)
-  # But #1, this is the discrete time version, and that's not useful
-  # But thanks to my longtime biological math hero Sarah Otto and her book on Mathematical modelling
-  # This will solve the backwards logistic and is easy peasy to use for forwards logistic
-  # Hurray for math!
   if(option == "logistic")   Pop.current <-  (exp(r)* pop.last)*(1-(pop.last/K)) 
-  
   return(list(Pop.current = Pop.current))
 }

### 2024-04-09 Scripts/functions/forward_sim.r

@@ -1,4 +1,4 @@
-# here we project forward, should be fairly straightforward tweak of the backward simulation function
+# Here we project forward, should be fairly straightforward tweak of the backward simulation function
 
 # All the data you need to make it dance...
 # years:          The years you are running the backwards calculation for

### 2024-04-09 Scripts/functions/simple_Lotka_r.r

@@ -1,37 +1,52 @@
-# Function to calculate Lotka R, DK revised this with several options of how we want to calculate
+# Function to calculate Lotka R, this is a simplified version of a more complex function (the more complex function allows for life history estimates of fecund and mort)
+# In this case we are feeding it the mortality and fecundity directly, effectively for this function we know the components of the Leslie matrix and are just
+# doing the optimization.
 
 # Function Arguments
-# Z:    Total mortality, 
-# fecund:      Fecundity
-# ages:
+#
+# mort:     Mortality for each age class, you could use natural mortality (M) or total mortality (Z=F+M).  The function is expecting natural mortality to be instantaneous
+# fecund:   Fecundity by age class, this is the average number of offspring produced by a female in an age class
+# ages:     The ages vector, ideally this goes from 1 (or even 0) to the maximum age, should have same number of age classes as the mortality and fecundity vectors(matrices)
  
-simple.lotka.r<-function(Z = NULL,fecund = NULL,ages = NULL) 
+simple.lotka.r<-function(yrs = 1,mort = NULL,fecund = NULL,ages = NULL) 
 {  
+  
   
   # The Euler-Lotka Function to optimize on to find the intrinsic rate of growth for your population
   eulerlotka <- function(r) (sum(lx * mx * exp(-r * ages)) - 1)^2
   # Set up a dataframe
-  res <- data.frame(r = NA)
+  res <- data.frame(years = NA,r = NA)
   
+  n.yrs <- length(yrs)
+  mx.tmp <- NULL
+  lx.tmp <- NULL
   
-  
-  #################################### Calculate Lotka SECTION #################################### Calculate Lotka SECTION #################################### Calculate Lotka SECTION
   # Now run this through all the yrs 
-
+  for(j in 1:(n.yrs))
+  { 
+    #browser() 
     # Get the r estimate for each year if we are running through a bunch of years
-    # Just use the first year if we don't have same length Z as years
-    if(!is.null(nrow(Z))) lx <- 1-exp(-Z) else lx <- 1-exp(-Z)
+    # Just use the first year if we don't have same length nat.mort as years
[…]

### 2024-04-09 Scripts/functions/simple_forward_sim.r

@@ -1,0 +1,185 @@
+# This function projects the populations 'forward' (a similar function can be used to project 'backwards' from a starting point).
+
+# All the data you need to make it dance...
+# years:      The years you are running the simulation for
+# nm:         Natural mortality, this wants the instantaneous natural mortality, not the proportional. Expects a matrix (dataframe) with 
+#             a column for each age class, and a row for each year.  Should have same number of rows as there are years, 
+#             and same number of columns as in fecund.
+# fecund:     The fecundity, this is the average number of offspring produced by a female in a given year.Expects a matrix (dataframe) with 
+#             a column for each age class, and a row for each year.  Should have same number of rows as there are years, 
+#             and same number of columns as in nm.
+# ages:       The age classes, should be a vector that has the same length as the columns of nm and fecund
+# rems        Removals.  For retro simultions you just have a vector of the 'realized' removals here and that is used. For the projections
+#             this is set up so that you provide the mean and sd of fishing mortality for the forward projections. 
+#             also added an option ("R_based") to make F a function of R from the euler-lotka model, this give general stability in the model.
+
+# K:          If you have a logistic or 'bounded exponential' model then you'll need to give it a K (carrying capacity). Can be a vector the same length
+#             as the number of years in simulation, or can be a single fixed value.
+# N.start:    The abundance in the first year
+# pop.model:  What method you going to use to get the population growth modeled. You can use exponential model, bounded exponential model, or a logistic model
+# n.sims:     The number of simulations you are running
+# sim:        Are you doing a retrospecitive "retro" or a projection 'project' simulations. Main difference is really that you don't know removals in the
+#             project case, but do know projections in the retrospective.
+# repo.loc    Where is your repo.  Deaults to pulling from online Github Repo using 'repo'.  If you put in the directory to point at
[…]

### 2024-04-09 Scripts/functions/tuning_sim_fast.r

@@ -26,7 +26,7 @@ fast.tunes<-function(years,step.size=0.05,tuner="m",  direction = 'backwards',ag
                    nm=NULL,fecund = NULL,fm = NULL,N.init = NULL,abund.ts = NULL,abund.age = NULL,catch.age = NULL)
 {
   # Download the function to go from inla to sf
-  funs <- c(#"https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/simple.lotka.r",
+  funs <- c("https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/simple.lotka.r",
             "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/backwards_project.r",
             "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/forward_project.r"
             
@@ -39,9 +39,9 @@ fast.tunes<-function(years,step.size=0.05,tuner="m",  direction = 'backwards',ag
     file.remove(paste0(getwd(),"/",basename(fun)))
   }
   
-  source("D:/Github/ICM/Scripts/functions/simple_Lotka_r.r")
-  source("D:/Github/ICM/Scripts/functions/forward_project.r")
-  source("D:/Github/ICM/Scripts/functions/backwards_project.r")
+  #source("D:/Github/ICM/Scripts/functions/simple_Lotka_r.r")
+  #source("D:/Github/ICM/Scripts/functions/forward_project.r")
+  #source("D:/Github/ICM/Scripts/functions/backwards_project.r")
   
   require(optimx)  || stop("Please load the 'optimx' package which you'll need for the optimations to run")
   
@@ -104,7 +104,7 @@ fast.tunes<-function(years,step.size=0.05,tuner="m",  direction = 'backwards',ag
     # we want to use the previous years. This is all handled by the y.index happily.
     #removals.next <- rems[y]
     # Going to line up the r with the 'previous' year, so the r in column 2020 is the r used to move between 2020 and 2021 (in either direction)
-    lotka.est <- simple.lotka.r(Z = z.tmp,fecund=fecund.tmp,ages=ages)
+    lotka.est <- simple.lotka.r(mort = z.tmp,fecund=fecund.tmp,ages=ages)
     
     r.est = lotka.est$res
     
[…]

### 2024-04-10 Scripts/functions/simple_forward_sim.r
Minor tweak
Getting years lined up right for the projection sims

@@ -52,6 +52,8 @@ simp.for.sim<-function(years,nm=NULL,fecund = NULL,ages =NULL,rems,K=NULL,N.star
   # In case I try to be lazy and shorten names...
   if(pop.model == 'exp') pop.model <- 'exponential'
   if(pop.model == 'log') pop.model <- 'logistic'
+  # If doing the projections we start from the year before the simulations period, so we add in the N.start year.
+  years <- c(min(years)-1,years)
   #Initialize a bunch of objects
   n.years<-length(years)
   Pop<-data.frame(abund = rep(NA,n.years*n.sims),sim = rep(1:n.sims,n.years),years = sort(rep(years,n.sims)))   
@@ -124,8 +126,8 @@ simp.for.sim<-function(years,nm=NULL,fecund = NULL,ages =NULL,rems,K=NULL,N.star
       {
         # FIX: I've added in harvest controls for the projections, basically if population is < 20% of K (B0), then harvesting rate declines by 90%
         # This is something to discuss and make customizable.
-        if(pop.last < 0.2*K[y-1]) removals.next <- 0.1*fm[y]*pop.last
-        if(pop.last >= 0.2*K[y-1]) removals.next <- fm[y]*pop.last
+        if(pop.last < 0.2*K[y-1]) removals.next <- 0.1*fm[y-1]*pop.last
+        if(pop.last >= 0.2*K[y-1]) removals.next <- fm[y-1]*pop.last
       } 
      
       r.up <- r.tmp$r[y-1] # So we grab the r associated with the lead in year so r aligns with the initial population numbers
@@ -172,6 +174,7 @@ simp.for.sim<-function(years,nm=NULL,fecund = NULL,ages =NULL,rems,K=NULL,N.star
       removals[y-1] <- removals.next 
 
     } #Loop through all the years.
+    #browser()
     # Extract the data
     Pop$abund[Pop$sim == i]<-Pop.vec
     Pop$removals[Pop$sim == i]<- c(removals,NA)

### 2024-04-10 Scripts/functions/tuning_sim_fast.r
Tidy up Part 1/X
Just annotating and bug fixes

@@ -1,32 +1,31 @@
-# Here we take the ideas from the backwards projections but 'tune' them to the 'known' biomass by adjusting either the fecundity or survivorship variables iteratively until
-# the biomass in the current year is withing X% of the actual biomass.
+# This function is the workhorse to make the model 'fit' to the observed time series, to do so we adjust the fecundity or survivorship variables iteratively until
+# the observed population abundance is within X% of the VPA model.
 
 # All the data you need to make it dance...
 # years:          The years you are running the backwards calculation for
-# abund.ts:        The abundance time series from the assessment
-
-# tuner:          What are we tuning, the fecundity "f", or natural mortality 'm', or both 'b'
-# rems            Removals from the fishery in a given year.
 # step.size:      How big is the difference (proportional) in the simulation step.  Default = 0.05 which is about a 5% change for each step
-
+# tuner:          What are we tuning, the fecundity "f", or natural mortality 'm', or both 'b'
 # direction       Allow for forwards and backwards simulations
-# What we need for the Lotka.r function...
-# fecund:      How are you estimating fecundity. If a vector it is the number of recruits produced by the average individual in the age classes. 
-#              If a matrix the rows are different simulations. Also have options to set fecund = 'eggs' which we can use if we can get an estimate of egg mortality
-#              fecund = 'SPR' uses the spawner per recruit metric, to get this to work we need to know how many recruits there are in a given year
-#              We could also let this vary by year, but we'll need to go 3-D array or something for that
-# nm:             Natural mortality, this wants the instantaneous natural mortality, not the proportional. There are several options here....
-#                 You can enter a vector of instantaneous natural moralities, just put a single number of all ages, or put in a character
-#                 string that will tell the function to calculate the natural mortality based on life history data. If a matrix the rows are different simulations
-#                 we could also let this vary by year, but we'll need to go 3-D array or something for that
-# ages:       Ages...
-
+# ages:           The age classes of your population
[…]

### 2024-04-16 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
Update with age and no age correction
Revised to run the model without using the age-correction (i.e., model without going to age 0, which should work fine since fecundity of anything smaller than recruits is effectively 0 for basically all the stocks).  Results very similar to the 'age corrected' analysis.  A few minor bug fixes as well.  Also have part of the methods written.

--- 2024-04-09 Scripts/Paper_1.Rmd
@@
 ---
-title: "ICM testing"
-output:
-  pdf_document: default
-  html_document: default
-  word_document: 
-    #reference_docx: template.docx
+output: word_document
 editor_options: 
@@
 
-The data is now available to test this on at least 81 stocks.
-All of the NE Atlantic stocks (ICES) have been through the QA/QC process and we are happy with those data (Sept 1, 2022).
-Let's see if we can get this to work on all the stocks with sufficient data...
-
-```{r, load-stuff,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
-# OK, so using the ICES assessments here's what we get for North Sea cod.
-library(readxl)
-library(tidyverse)
-library(rio)
-library(ggthemes)
-library(cowplot)
-library(gtable)
-library(viridis)
-loc <- 'D:/GitHub/ICM'
-
-source(paste0(loc,"/Scripts/functions/tuning_sim_fast.R"))
-
-# Choose 5 ICES stocks that we have the necessary data for
-#ASR <- read_xlsx("../Data/ASR_2018.xlsx" sheet = "ICES")
-ASR1 <- read.csv(paste0(loc,"/Data/ICM_data_NE_atlantic_stocks.csv"))
-ASR <- read.csv(paste0(loc,"/Data/ICM_data_NW_atlantic_stocks.csv"))
-
-ASR <- rbind(ASR1,ASR)
-datatypes <- unique(gsub(x = names(ASR), pattern = "[^a-zA-Z]", replacement=""))
-
-# Replace 0's in Num.tot with NA so the rest of this works as Freya designed it to...
-ASR$Num.tot[ASR$Num.tot == 0] <- NA
-# we want:
-# Year, Num, WA, Catch, AM, NM, StockID, Management, Area, Order, Family, Genus, Species
-ASRdat <- ASR[,c(grep(x=names(ASR), "Num"),
-                 grep(x=names(ASR), "WA"),
-                 grep(x=names(ASR), "Catch"),
-                 grep(x=names(ASR), "AM"),
-                 grep(x=names(ASR), "NM"))]
-# Making all the data numeric that should be numeric
-ASRdat <- apply(X = ASRdat, 2, as.numeric)
-# Getting the species info back
-ASRsp <- ASR[, which(!1:length(names(ASR)) %in% grep(x=names(ASR), ".", fixed=T))]
-# And binding it all back together
-ASR_trim <- cbind(ASRsp, ASRdat)
-# need a unique ID for stock
-#table(ASR_trim$Management, ASR_trim$Species)
-ASR_trim$Stock <- paste0(ASR_trim$Management, "_", ASR_trim$Area, "_", ASR_trim$Genus, "_", ASR_trim$Species)
-
-ASR_long <- ASR_trim %>%
-  pivot_longer(!c("Management", "Area", "Order", "Family", "Genus", "Species", "Stock", "Year","Meeting_or_reference","Model","Case","Notes")) %>%
-  separate(col=name, into=c("type", "age"), sep = "\\.")
-
-# Something is weird with the mentella stock, I'm going to drop it...
-ASR_long <- ASR_long %>% dplyr::filter(Stock != "ICES-AFWG_DEEP1-2_Sebastes_mentella")
-
-```
-
-```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
-
+```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4,include=F,message=F}
+
+if(load.results==F)
+{
   Stocks <- ASR_long %>%
@@
 
-# Stocks <- ASR_stocks %>%
-#                       dplyr::group_by(Stock, Species, type) %>%
-#                       dplyr::summarize(ages=length(unique(age)),
-#                                 years=length(unique(Year))) %>%
-#                       dplyr::arrange(-years, -ages) %>%
-#                       dplyr::filter(!Species=="morhua") %>%
-#                       dplyr::distinct(Stock) %>%
-#                       dplyr::pull(Stock)
-# 
   # print(Stocks)
@@
   mr.tmp <- NULL
-all.abund.tmp <- NULL
+  abund.tmp <- NULL
   full.abund.tmp <- NULL
@@
 
-  # Drop the NA years....
-  if(i == "ICES-NWWG_ICE-Summer_Clupea_harengus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1986)
-  # There's some funkiness going on in the first 7 years of these data, so staring in year 8
-  if( i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1971)
-  if(i == "ICES-NWWG_FA5b_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)
-  if(i == "ICES-NWWG_FA5a_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1984)
-  if(i == "ICES-AFWG_NEA1-2_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1969)
-  if(i == "ICES-WGCSE_CS27.6a_Merlangius_merlangus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1980)
-  if(i == "ICES-WGCSE_NS6a_Gadus_morhua") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1980)
-  if(i == "ICES-AFWG_COASTNOR 1-2_Gadus_morhua") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 2006)
-  if(i == "NEFSC_5Z_Pseudopleuronectes_americanus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)
-  if(i == "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1989)
-
+    # Dropping the first 7 years as the 8 year olds are all missing
+  if(i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR_sub <- ASR_sub |> collapse::fsubset(Year >= 1972)
   # maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]))
@@
   am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
-  am.3s <- length(which((!is.na(age.mat$AM[age.mat$age ==3]))))
   if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
@@
   if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0
-  if(am.3s == 0) age.mat$AM[age.mat$age ==3] <- 0
-
-   # Now we can get the abundance from the VPA models
+
+  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
+  nat.mort <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
   abund <- ASR_sub %>% dplyr::filter(type=="Num") %>% dplyr::rename(Num=value) %>% dplyr::select(-type)
-
-  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
-  # Now do something similar for the Natural moralities, but in this case
-  # we take the NM of the youngest age class we have information for and back that number up to year 0.
-  # DK NOTE:  THIS IS A BIG CHANGE IN DIRECTION FOR THE LOTKA CALCS SO NEED TO NOTE THIS ONE!!
-
-  nm.tmp <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
-
-  #minage
-  minage <- min(as.numeric(nm.tmp$age[!is.na(nm.tmp$NM)]))
-  if(minage == 0)  nat.mort <- nm.tmp
-  # Some specials...
-  if(i %in% c("ICES-WGCSE_CS7e-k_Gadus_morhua","ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus",
-              "ICES-WGHANSA_SP8abd_Sardina _pilchardus","ICES-WGWIDE_NEA 1-9,12,14_Micromesistius_poutassou")) minage <- 1
-  if(i == "ICES-WGWIDE_NEA 1,2,5,4a,14a_clupea_ harengus") minage <- 2
-  #maxage
-  maxage <- max(as.numeric(nm.tmp$age[!is.na(nm.tmp$NM)]))
-
-  # Now get the number of individuals in the youngest age category
-  num.age.min <- ASR_sub %>% dplyr::filter(age==minage,type=="Num")
-  # So any Recruitment even that is > 3 SE's away from the median I'm calling 
-  # an 'extreme' recruitment event and it is going to get a lower/higher natural mortality term.
-  med.mun.age.min <- mean(num.age.min$value,na.rm=T)
-  sd.mun.age.min <- sd(num.age.min$value,na.rm=T)#/sqrt(length(na.omit(num.age.min$value)))
-  low.rec <- med.mun.age.min - 2*sd.mun.age.min
-  high.rec <- med.mun.age.min + 2*sd.mun.age.min
-  high.rec.years <- as.vector(na.omit(num.age.min$Year[num.age.min$value > high.rec]))
-  low.rec.years <- as.vector(na.omit(num.age.min$Year[num.age.min$value < low.rec]))
-  # Set up the full abundance matrix 
-  full.abund <- abund
-  print(paste0("Stock ", i , ' high recruit years include ', length(c(low.rec.years,high.rec.years)), ' years'))
-  # If we need to imput some data run this loop for natural mortality
-  if(minage == 0) full.abund <- abund
-
-  if(minage > 0)
-  {
-    yrs <- sort(unique((nm.tmp$Year)))
-    nm.res <- NULL
-    # These already have NM estimates at 0 so don't need to do them...
-    if(!i %in% c("ICES-WGCSE_CS7e-k_Gadus_morhua","ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus",
-                 "ICES-WGHANSA_SP8abd_Sardina _pilchardus","ICES-WGWIDE_NEA 1,2,5,4a,14a_clupea_ harengus",
-                 "ICES-WGWIDE_NEA 1-9,12,14_Micromesistius_poutassou"))
-    {
-      # Just use the mean mortality of the youngest age class we have information for
-      nm.use <- mean(nm.tmp$NM[nm.tmp$age==minage],na.rm=T)
-      # Take the average natural mortality of the youngest age class with an m and use that
-      # This avoids really blowing up the abundance in the younger age classes which can get a bit squirrly
-      # nm.high.rec <- 0.5*(min(nm.tmp$NM[nm.tmp$age==minage],na.rm=T))
-      # nm.low.rec <-  1.5*(max(nm.tmp$NM[nm.tmp$age==minage],na.rm=T))
-      # Start by filling in everything...
-      nm.tmp$NM[is.na(nm.tmp$NM)] <- nm.use
-      nm.tmp <- nm.tmp[nm.tmp$age %in% 0:maxage,]
-      # Now we need to fill in the 'special' cohorts that were really big (low m) or really small (high m)
-      # for(y in length(yrs):1)
-      # {
-      #   if(yrs[y] %in% c(high.rec.years,low.rec.years))
-      #   {
-      #     if(yrs[y] %in% high.rec.years) nm.pick <- nm.high.rec
-      #     if(yrs[y] %in% low.rec.years) nm.pick <- nm.low.rec
-      #     for(a in minage:1) nm.tmp$NM[nm.tmp$Year == (yrs[y]-a) & nm.tmp$age == minage-a] <- nm.pick
-      # }} #Close the if and for loops
-      # Pointless rename...
-    } #end the skip the stocks with nm at 0 if
-      nat.mort <- nm.tmp
-
-  # Now do the same loopiness for abundance
-    for(y in length(yrs):2)
-    {
-      # The minage of the natural mortality is different from minage of the abundance, annoyingly for this stock...
-      if(i == "ICES-AFWG_NEA1-2_Gadus_morhua") minage <- 3
-      if(i == "ICES-NWWG_ICE-Summer_Clupea_harengus") minage <- 3
-
-           # The lowest minage =4, This goes first since we go backwards, this gets us age 3 in year 3
-           if(minage ==4) 
-           {
-               four.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 4) %>% dplyr::pull(Num)
-               nm.four <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][4,]$NM) 
-               full.abund[full.abund$Year ==yrs[y]-1,][4,]$Num <- four.abund/(1-nm.four)
-             #}# end my 2:0
-           } # end if minage ==4
-
-            # The minage =3 scenario, goes after 4...
-           if(minage >=3)
-           {
-             # for(my in 0:1)
-             # {
-               three.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 3) %>% dplyr::pull(Num)
-               nm.three <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][3,]$NM) 
-               full.abund[full.abund$Year ==yrs[y]-1,][3,]$Num <- three.abund/(1-nm.three)
-             #} # end my 1:0
-           } # end if(minage ==2)
-
-           # The minage =2 scenario, this goes last
-           if(minage >=2)
-           {
-             two.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 2) %>% dplyr::pull(Num)
-             nm.two <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][2,]$NM) 
-             full.abund[full.abund$Year ==yrs[y]-1,][2,]$Num <- two.abund/(1-nm.two)
-           } # end if(minage ==2)
-
-           if(minage >=1)
-           {
-             one.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 1) %>% dplyr::pull(Num)
-             nm.one <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][1,]$NM) 
-             full.abund[full.abund$Year ==yrs[y]-1,][1,]$Num <- one.abund/(1-nm.one)
-           } # end if(minage ==2)
-
-         } # The annoying if to fill in rest of the first few years.
-  } # end if minage > 0
-
-  # We won't have a weight at age for the young ages, which is fine since we only need that for SSB
   weight.age <- ASR_sub %>% dplyr::filter(type=="WA") %>% dplyr::rename(WA=value) %>% dplyr::select(-type)
+  if(i == Stocks[30]) weight.age$WA <- weight.age$WA/1000
   removals <- ASR_sub %>% dplyr::filter(type=="Catch") %>% dplyr::rename(Catch=value) %>% dplyr::select(-type)
-  # Fill the leading NAs with 0s now...
-  if(minage > 0) 
-  {
-    weight.age$WA[weight.age$age %in% 0:(minage-1)] <- 0
-    removals$Catch[removals$age %in% 0:(minage-1)] <- 0
-  }
+
  # if(i=="ICES-WGBFAS_BS 22-32_Sprattus_sprattus") removals$Catch <- removals$Catch/1000
@@
     full_join(nat.mort) %>%
-    #full_join(abund) %>%
-    full_join(full.abund) %>%
+    full_join(abund) %>%
     full_join(weight.age) %>%
@@
 
-  # Nice way to toss NAs!
+  # Aahh??  Is this NA dropping useful data, needed to quick fix the age at maturity data...
   data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
   data <- data[data$available==T,]
-  # And then toss the years we don't have 0 data for Numbers in the 0 age class
-  toss.years <- data %>% dplyr::group_by(Year) %>% dplyr::reframe(bad.years = which(min(age)>0))
-  data <- data[!data$Year %in% toss.years$Year,]
 
@@
   N.end <- sum(data[data$Year==max(years),]$Num)
-  all.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
-  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::filter(age %in% minage:maxage) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
+  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
+
   # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
-
+  #minage
+  minage <- min(as.numeric(data$age))
+  #maxage
+  maxage <- max(as.numeric(data$age))
   #recruits
-  annual <- data.frame(Year=data$Year[data$age==0], recruits=data$Num[data$age==0])
+  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
   #ssn
@@
 
-  #r.p.ssb So we are assuming the SSB in year X produces the observed recruits in year X
-  annual$r.p.ssb <- annual$recruits/annual$tot.ssb
+  #r.p.ssb This needs to be offset by the age of recruits
+  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+1):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage)])
   # recs.per.age
@@
   # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
-  # tmp <- NULL
-  # for(j in 1:length(years))
-  # {
-  #   tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
-  #   tst$Year <- tst$Year + minage
-  #   names(tst) <- c("ssb.offset","ssn.offset","Year","age")
-  #   tmp[[j]] <- tst
-  # }
+  tmp <- NULL
+  for(j in 1:length(years))
+  {
+    tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
+    tst$Year <- tst$Year + minage
+    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
+    tmp[[j]] <- tst
+  }
   # Unpack the list
-  #@ssb.off <- do.call('rbind',tmp)
+  ssb.off <- do.call('rbind',tmp)
   # And merge it with the data object
-  #data <- left_join(data,ssb.off,by=c("Year","age"))
-  data$recs.per.age <- data$ssb*data$r.p.ssb
+  data <- left_join(data,ssb.off,by=c("Year","age"))
+  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
   # mx
   # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
-  # The demographic models are 'female' only, so we'd want to divide the number of recruits by 2 and the SSN by 2, but that just cancels out
-  # so there is no need to make the mom adjustment.
-  data$mx <- data$recs.per.age/data$ssn # if(grepl("males",i))
-  # if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn/2 # Moms only! 
+  # No longer dividing by 2 because we should really divide recruits and ssn by 2 to be female only, but that's pointless so we roll along with this.
+  data$mx <- data$recs.per.age/data$ssn.offset # if(grepl("males",i)) 
+  #if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
   data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
-  # Now for the very high recruitment years allow for a small amount of recruitment (20% of the lowest age) in the age classes after year 0....
-
-  # if(length(high.rec.years) > 0)
-  # {
-  #   for(y in high.rec.years)
-  #   {
-  #     tmp <- data$AM[data$Year == y]
-  #     am.fill <- which(tmp ==0) 
-  #     if(length(am.fill) > 1) data$mx[data$Year == y-1][am.fill[-1]] <- 0.2*min(data$mx[data$Year == y & data$mx > 0],na.rm=T)
-  #   }
-  # }
+  # Easier to remove the years where we don't have recs.per.age...
+  #data <- data %>% dplyr::filter(Year %in% years[(minage+1):length(years)])
+  # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...
 
   age.mat <- data %>% dplyr::select("Year", "age", "AM") %>% pivot_wider(names_from=age, values_from = AM) %>% dplyr::select(-Year)
-  prop.nat.mort <- data %>% dplyr::select("Year", "age", "prop.nat.mort") %>% pivot_wider(names_from=age, values_from = prop.nat.mort) %>% dplyr::select(-Year) %>% as.data.frame
+  prop.nat.mort <- data %>% dplyr::select("Year", "age", "prop.nat.mort") %>% 
+                            pivot_wider(names_from=age, values_from = prop.nat.mort) %>% 
+                            dplyr::select(-Year) %>% as.data.frame
+
   weight.age <- data %>% dplyr::select("Year", "age", "WA") %>% pivot_wider(names_from=age, values_from = WA) %>% dplyr::select(-Year)
-  mx <- data %>% dplyr::select("Year", "age", "mx") %>% pivot_wider(names_from=age, values_from = mx) %>% dplyr::select(-Year) %>% as.data.frame()
-  abund.age <- data %>% dplyr::select("Year", "age", "Num") %>% pivot_wider(names_from=age, values_from = Num) %>% dplyr::select(-Year) %>% as.data.frame()
+  mx <- data %>% dplyr::select("Year", "age", "mx") %>% 
+                 pivot_wider(names_from=age, values_from = mx) %>% 
+                 dplyr::select(-Year) %>% as.data.frame()
+  # Get the abundance matrix
+  abund.age <- data %>% dplyr::select("Year", "age", "Num") %>% 
+                        pivot_wider(names_from=age, values_from = Num) %>% 
+                        dplyr::select(-Year) %>% as.data.frame()
+
   # Now we can save out the catch and get an instantaneous F
@@
     {
-    age.mat[,10:12] <- 1
-    prop.nat.mort[,10:12] <- prop.nat.mort[,9]
-    weight.age[12:14,11:12] <- weight.age[12:14,10]
-    weight.age[15,12] <- weight.age[15,11]
-    mx[12:14,11:12] <- mx[12:14,10]
-    mx[15,12] <- mx[15,11]
-    full.Fs[12:14,11:12] <- full.Fs[12:14,10]
-    full.Fs[15,12] <- full.Fs[15,11]
-    abund.age[12:14,11:12] <- abund.age[12:14,10]
-    abund.age[15,12] <- abund.age[15,11]
+      age.mat[,8:10] <- 1
+      prop.nat.mort[,8:10] <- prop.nat.mort[,7]
+      weight.age[12:14,9:10] <- weight.age[12:14,8]
+      weight.age[15,10] <- weight.age[15,9]
+      mx[12:16,9:10] <- mx[12:16,8]
+      mx[17,10] <- mx[17,9]
+      full.Fs[12:14,9:10] <- full.Fs[12:14,8]
+      full.Fs[15,10] <- full.Fs[15,9]
+      abund.age[12:14,9:10] <- abund.age[12:14,8]
+      abund.age[15,10] <- abund.age[15,9]
       # I could calculate, but this will get us to the same place...
-    full.rems[12:14,11:12] <- full.rems[12:14,10]
-    full.rems[15,12] <- full.rems[15,11]
+      full.rems[12:14,9:10] <- full.rems[12:14,8]
+      full.rems[15,10] <- full.rems[15,9]
     }
@@
     {
-    age.mat[6:7,12] <- 1
-    prop.nat.mort[6:7,12] <- prop.nat.mort[6:7,11]
-    weight.age[6:7,12] <- weight.age[6:7,11]
-    mx[6:7,12] <- mx[6:7,11]
-    full.Fs[6:7,12] <- full.Fs[6:7,11]
-    abund.age[6:7,12] <- abund.age[6:7,11]
-    full.rems[6:7,12] <- full.rems[6:7,11]
+      age.mat[6:7,10] <- 1
+      prop.nat.mort[6:7,10] <- prop.nat.mort[6:7,9]
+      weight.age[6:7,10] <- weight.age[6:7,9]
+      mx[6:9,10] <- mx[6:9,9]
+      full.Fs[6:7,10] <- full.Fs[6:7,9]
+      abund.age[6:7,10] <- abund.age[6:7,9]
+      full.rems[6:7,10] <- full.rems[6:7,9]
     }
@@
     {
-    age.mat[30,9] <- 1
-    prop.nat.mort[30,9] <- prop.nat.mort[30,8]
-    weight.age[30,9] <- weight.age[29,9]
-    mx[30,9] <- mx[30,8]
-    full.Fs[30,9] <- full.Fs[30,8]
-    abund.age[30,9] <- abund.age[30,8]
-    full.rems[30,9] <- full.rems[30,8]
+      age.mat[30,8] <- 1
+      prop.nat.mort[30,8] <- prop.nat.mort[30,7]
+      weight.age[30,8] <- weight.age[29,8]
+      mx[30:31,8] <- mx[30:31,9]
+      full.Fs[30,8] <- full.Fs[30,7]
+      abund.age[30,8] <- abund.age[30,7]
+      full.rems[30,8] <- full.rems[30,7]
     }
@@
     {
-    age.mat[c(14,27,40),7] <- age.mat[1,7]
-    prop.nat.mort[c(14,27,40),7] <- prop.nat.mort[1,7]
-    weight.age[c(14,27,40),7] <- weight.age[c(13,26,39),7]
-    mx[c(14,27,40),7] <- mx[c(14,27,40),6]
-    full.Fs[c(14,27,40),7] <- full.Fs[c(14,27,40),6]
-    abund.age[c(14,27,40),7] <- abund.age[c(14,27,40),6]
-    full.rems[c(14,27,40),7] <- full.rems[c(14,27,40),6]
+      age.mat[c(14,27,40),5] <- age.mat[1,5]
+      prop.nat.mort[c(14,27,40),5] <- prop.nat.mort[1,5]
+      weight.age[c(14,27,40),5] <- weight.age[c(13,26,39),5]
+      mx[c(14,16,27,29,40,42),5] <- mx[c(14,16,27,29,40,42),6]
+      full.Fs[c(14,27,40),5] <- full.Fs[c(14,27,40),4]
+      abund.age[c(14,27,40),5] <- abund.age[c(14,27,40),4]
+      full.rems[c(14,27,40),5] <- full.rems[c(14,27,40),4]
     }
@@
     {
-    mx[4,19] <- mean(unlist(mx[4,c(18,20)]))
-    mx[c(5,7),20] <- mx[c(5,7),19]
-    mx[1:6,21] <- mx[1:6,20] 
-  }
+      mx[5,18] <- mean(unlist(mx[5,c(17,19)]))
+      mx[c(6,8),19] <- mx[c(6,8),18]
+      mx[2:7,20] <- mx[2:7,19] 
+    }
+
   # For the years of mx without SSB info to inform them
-  # if(minage >0 ) 
-  # {
-  #   mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
-  #   names(mx) <- names(mx.fill)
-  #  # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
-  #   mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
-  # }
+  if(minage >0 ) 
+  {
+    mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
+    names(mx) <- names(mx.fill)
+   # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
+    mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
+  }
+
     years.tmp[[i]] <- years
@@
     vpa.tmp[[i]] <- vpa.abund
-  all.abund.tmp[[i]] <- all.abund
-  full.abund.tmp[[i]] <- abund.age
     am.tmp[[i]] <- age.mat
     mr.tmp[[i]] <- missing_rem
+    abund.tmp[[i]] <- abund.age
     fs.tmp[[i]] <- full.Fs
@@
 
-save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,am.tmp,Stocks,ASR_stocks,ASR_long,all.abund.tmp,full.abund.tmp,fs.tmp,full.rem.tmp,file =  paste0(loc,"/Results/model_inputs_all_ages.Rdata"))
-
+  save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,
+       am.tmp,Stocks,ASR_stocks,ASR_long,abund.tmp,fs.tmp,full.rem.tmp,
+       file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
+
+  } # end load results
 ```
@@
 
-```{r tunes}
+```{r tunes,include=F,echo=F,warning=F,message=F}
 
@@
 
-load(file = paste0(loc,"/Results/model_inputs_all_ages.Rdata"))
+  if(load.results==F)
+  {
+  load(file = paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
 
@@
     vpa.abund <- vpa.tmp[[i]] 
-  all.abund <- all.abund.tmp[[i]]
+    abund <- abund.tmp[[i]]
     fs <-fs.tmp[[i]]
-  full.rem <- full.rem.tmp[[i]]
-  full.abund <- full.abund.tmp[[i]]
+    full.rem <- rem.tmp[[i]]
+    #full.abund <- full.abund.tmp[[i]]
     #all.abund <- full.abund.tmp[[i]]
@@
     ss.size <- 0.01
-  sensistive.stocks <- c("ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
-                          "ICES-HAWG_NS_Ammodytes_dubius",
+    sensistive.stocks <- c("AFSC_GOA_Theragra_chalcogramma",
                             "DFO_2J3KL_Gadus_morhua",
@@
                             "DFO_4T-4VN_Gadus_morhua",
+                            "DFO_4T_Scomber_scombrus",
+                            "ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus",
+                            "ICES-AFWG_NEA1-2_Gadus_morhua",
+                            "ICES-HAWG_NS_Ammodytes_dubius",
+                            "ICES-NWWG_FA5b_Pollachius_virens",
+                            "ICES-NWWG_FAPL5b1_Gadus_morhua",
+                            "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
                             "ICES-WGCSE_IS7a_Gadus_morhua",
                             "ICES-WGCSE_CS7a_Merlangius_merlangus",
+                            "ICES-WGCSE_CS7e-k_Gadus_morhua",
+                            "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
+                            "ICES-WGHANSA_SP8abd_Sardina _pilchardus", 
                             "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua",
                             "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",
-                          "ICES-WGHANSA_SP8abd_Sardina _pilchardus",
                             "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus",
+                            "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
                             "NEFSC-GARMIII_SNE- MA_Limanda_ferruginea",
                             "NEFSC-GARMIII_MA_Paralichthys_dentatus",
-                          "ICES-WGCSE_CS7e-k_Gadus_morhua",
-                          "DFO_4T_Scomber_scombrus",
-                          "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
-                          "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
-                           "AFSC_GOA_Theragra_chalcogramma")
+                            "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus")
+
+  #NE Arctic aeglefinus (high and lows)  (21) solved
+  #Faroes 5b P. virens (high and lows)  (29) solved
 
@@
 
-   N.start <- all.abund[1]
+     N.start <- vpa.abund[1]
      print(i)
@@
      fast.for.tune <- fast.tunes(years,
-                           tuner='fec_nm',
+                             tuner=what.2.tune,
                              step.size = ss.size, 
-                           abund.ts = all.abund,
+                             abund.ts = vpa.abund,
                              ages=ages,
@@
                              fm = fs,
-                           abund.age = full.abund, 
+                             abund.age = abund, 
                              catch.age = full.rem, 
@@
 
-   N.end <- all.abund[length(all.abund)]
-
-}
-
-#DFO_2J3KL_Gadus_morhua -27.7984654 2.815738e+08
-#ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax -21.6050608
-# ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax Lotka error
-# ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus # lotka error
-
-#saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_z.Rds")
-#saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_z.Rds")
-# saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_nm.Rds")
-# saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_nm.Rds")
-#saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_fm.Rds")
-#saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_fm.Rds")
-saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_fec_nm.Rds")
-saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_fec_nm.Rds")
-#
+  }
+
+  saveRDS(for.tune.summary,paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
+  saveRDS(for.tune.all.res,paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
+  # 
+}# end if load results
 
@@
 
-```{r paper-other-metrics-and-metadata}
-
+```{r paper-other-metrics-and-metadata,echo=F,include=F,warning=F,message=F}
+
+if(load.results==F)
+{
   # We are now looking at everything, lifetime reproductive success
-model <- "fec_nm"
-for.tune.summary <- readRDS(paste0("D:/Github/ICM/Results/forwards_fully_tuned_summary_",model,".Rds"))
-for.tune.all <- readRDS(paste0("D:/Github/ICM/Results/forwards_fully_tuned_all_res_",model,".Rds"))
-
-load(file =  paste0(loc,"/Results/model_inputs_all_ages.Rdata"))
+
+  for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
+  for.tune.all <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
+
+  load(file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
   # Get the stocks...
@@
   meta <- NULL
-for(i in Stocks) meta[[i]] <- ASR_long[ASR_long$Stock == i,-drop][1,]
+  for(i in Stocks) 
+  {
+    meta[[i]] <- ASR_long[ASR_long$Stock == i,-drop][1,]
+    meta[[i]]$age.min <- min(ages.tmp[[i]])
+    meta[[i]]$age.max <- max(ages.tmp[[i]])
+  }
   meta <- do.call('rbind',meta)
@@
   res.lambda.fin <- NULL
-for(i in Stocks)
+  for(i in Stocks) # 
   {
@@
 
-  ages <- 0:(ncol(fec.tmp)-1)
+    ages <- meta.tmp$age.min:meta.tmp$age.max
     n.ages <- length(ages)
@@
       z.init <- as.numeric(tst$z.org[yy,])
-    lam.no.fish <- exp(simple.lotka.r(Z = nm,fecund = fec,ages=ages)$res)
-    lam.fish <- exp(simple.lotka.r(Z = z,fecund = fec,ages=ages)$res)
-    lam.org.no.fish <- exp(simple.lotka.r(Z = nm.init,fecund = fec.init,ages=ages)$res)
-    lam.org.fish <- exp(simple.lotka.r(Z =  z.init,fecund = fec.init,ages=ages)$res)
+      lam.no.fish <- exp(simple.lotka.r(mort = nm,fecund = fec,ages=ages)$res$r)
+      lam.fish <- exp(simple.lotka.r(mort = z,fecund = fec,ages=ages)$res$r)
+      lam.org.no.fish <- exp(simple.lotka.r(mort = nm.init,fecund = fec.init,ages=ages)$res$r)
+      lam.org.fish <- exp(simple.lotka.r(mort =  z.init,fecund = fec.init,ages=ages)$res$r)
 
@@
   pop.dam <- data.frame(pop.dam)
-# saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",model,".Rds"))
-# saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",model,".Rds"))
-# saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",model,".Rds"))
+  # saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",what.2.tune,".Rds"))
+  # saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",what.2.tune,".Rds"))
+  # saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",what.2.tune,".Rds"))
   save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
-     file=paste0("D:/Github/ICM/Results/all_cleaned_forward_tune_summaries_",model,".Rdata"))
-
-write.csv(meta.sub, "D:/Github/ICM/Data/metadata.csv")
-
+       file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
+
+  write.csv(meta.sub, paste0(loc,"/Data/metadata_no_age_corection.csv"))
+} # end if load results
 ```
 
-```{r simp-figs}
-theme_set(theme_few(base_size = 14))
-model <- 'fec_nm'
-load(file=paste0("D:/Github/ICM/Results/all_cleaned_forward_tune_summaries_",model,".Rdata"))
+```{r simp-figs,include=F,echo=F,message=F,warning=F}
+load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
 pop.dam <- data.frame(pop.dam)
@@
 
-# Lambda plots
-
 # res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(LME,Area.broad) %>%
@@
 #hmm <- merge(tst,res.lambda.final.6,by="Stock")
+# Note the LIMITS I PUT ON THESE BECAUSE 4 STOCKS WERE SHITTY
 plot(res.lambda.final$lam.fish.med ~ res.lambda.final$lam.fish.mn)
@@
                                            geom_point(aes(y=lam.no.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-                                           xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10)) + 
+                                           xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10)) + 
                                            geom_hline(yintercept = 1,linetype='dashed') +
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/lambda_no_fishing_6.png",lambda.plt,base_width = 12,base_height = 10)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_no_fishing_6_",what.2.tune,".png"),lambda.plt,base_width = 12,base_height = 10)
 
@@
                                            geom_point(aes(y=lam.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-                                           xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10)) + 
+                                           xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,5)) + 
                                            geom_hline(yintercept = 1,linetype='dashed') +
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/lambda_with_fishing_6.png",lambda.plt.fish,base_width = 12,base_height = 10)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_with_fishing_6_",what.2.tune,".png"),lambda.plt.fish,base_width = 12,base_height = 10)
 
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap_by_sp6.png",dub.heatmap.sp6,base_width = 20,base_height = 17)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_sp6_",what.2.tune,".png"),dub.heatmap.sp6,base_width = 20,base_height = 17)
 
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/GL_boxplot_no_fish_6_species.png",gen.boxplt,base_width = 12,base_height = 10)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_no_fish_6_species_",what.2.tune,".png"),gen.boxplt,base_width = 12,base_height = 10)
 
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/R0_boxplot_no_fish_6_species.png",r0.boxplt,base_width = 12,base_height = 10)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_no_fish_6_species_",what.2.tune,".png"),r0.boxplt,base_width = 12,base_height = 10)
 
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap_by_order.png",dub.heatmap,base_width = 20,base_height = 20)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"),dub.heatmap,base_width = 20,base_height = 20)
 
@@
 #lambda.ts.plt
-save_plot("D:/Github/ICM/Figures/tuned/lambda_timeseries_6.png",lambda.ts.plt,base_width = 12,base_height = 10)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_timeseries_6_",what.2.tune,".png"),lambda.ts.plt,base_width = 12,base_height = 10)
 
@@
                             facet_wrap(~G.Species,scales='free_y') 
-save_plot("D:/Github/ICM/Figures/tuned/lambda_by_decade_6.png",lambda.dec.plt,base_width = 12,base_height = 12)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_by_decade_6_",what.2.tune,".png"),lambda.dec.plt,base_width = 12,base_height = 12)
 
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/gen_heatmap.png",gen.heatmap,base_width = 20,base_height = 17)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/gen_heatmap_",what.2.tune,".png"),gen.heatmap,base_width = 20,base_height = 17)
 
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/r0_heatmap.png",r0.heatmap,base_width = 20,base_height = 17)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_",what.2.tune,".png"),r0.heatmap,base_width = 20,base_height = 17)
 
@@
 #                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
+```

### 2024-04-16 Drafts/Paper_1/03-methods.Rmd
Update with age and no age correction
Revised to run the model without using the age-correction (i.e., model without going to age 0, which should work fine since fecundity of anything smaller than recruits is effectively 0 for basically all the stocks).  Results very similar to the 'age corrected' analysis.  A few minor bug fixes as well.  Also have part of the methods written.

# Methods {#meth}

## Data

Data from Julie's repo, cite Julie. This data repository had sufficient data to run the analysis for 77 stocks from NE Atlantic, NW Atlantic, and the North Pacific, this includes stocks managed by Fisheries and Oceans Canada (DFO), NOAA, and ICES. See Appendix X for details on the stocks included. These stocks all have age-specific estimates of abundance, biomass, removals, natural mortality, and maturity.

## Incidental Catch Model (ICM)
## Reconstrutive Life-Table Analysis (REC)
## Life Table Reconstruction (LITAR)

## Discrete Time Age Structured Life Tables

The discrete time Euler-Lotka was first proposed by Euler in 1760 (subsequently published by @moserGesetzeLebensdauer1839) and is a special case of the continuous time demographic model first proposed by Lotka in 1907 [@lotkaRelationsBirthRates1907; @sharpeProblemAgedistribution1911; @lotkaRelationBirthRate1918]:

$$
1 = \sum_{x=\alpha}^{\omega} \lambda^{-x} s_x f_x dx
$$
Where $x$ is the age, $\alpha$ is the age at first reproduction, $\omega$ is the maximum age, $\lambda$ is the discrete rate of population growth ($\lambda = e^r$), $s_x$ is the survivorship to age $x$, and $f_x$ is the fecundity of individuals of age $x$. The discrete time Euler-Lotka equation can be shown to be the characteristic polynomial of the Leslie Matrix, where $f_0$ is the fecundity of the first age class with mature individuals [@leslieUseMatricesCertain1945,@caswellMatrixPopulationModels2001]:

$$

  \begin{bmatrix}
    f_0  & f_1 & f_2  & f_3    & ...          & f_{\omega-1} \\
    s_0  & 0   & 0    & 0      & ...          & 0 \\
    0    & s_1 & 0    & 0      & ...          & 0 \\
    0    & 0   & s_2  & 0      & ...          & 0 \\
    0    & 0   & 0    & \ddots & ...          & 0 \\
    0    & 0   & 0    & ...    & s_{\omega-2} & 0 \\
  \end{bmatrix}
$$

## Life-Table Reconstruction (LITAR)

The data necessary to obtain age specific estimates of fecundity and mortality are publicly available from the database  @charbonneauAgestructuredmarinefishdatabase2022.

The Euler-lotka equation requires the fecundity given as the number of offspring produced by each female in each age class. This can be estimated from the available recruitment, age at maturity, and biomass information. **Note there is no need to divide by 2 for females because we'd divide the recruits by 2 to get the number of females, and the spawning numbers by 2, which would just cancel out**.

The number of spawners in year $t$ and age class $a$ ($SSN_{t,a}$) is the proportion of mature individuals ($Mat_{t,a}$) multiplied by the Number of individuals

$$
SSN_{t,a} = Mat_{t,a} N_{t,a}
$$

# NEED TO SORT OUT THE "NOMENCLATURE" AROUND LINING THESE UP RIGHT!

The number of recruits produced per spawner $RPS_{t}$ is calculated as

$$
RPS_{t+ra} = R_{t+ra} SSB_{t} 
$$

Where $SSB_{t}$ is the total spawning stock biomass in year $t$ and $R_t$ is the number individuals in the youngest age class (hereafter referred to as recruits).  The spawner abundance ($SSB$) is offset by the age of the recruits ($ra$), for example, if the recruits are two-year olds, we assume that the recruits in 2010 were produced by the spawners in 2008. The number of recruits produced by each age class can then be calculated by multiplying the spawner biomass in each age class $S_{t,a}$ by the number of number of recruits produced per kilogram of SSB

$$
RPA_{(t+ra),a} =  SSB_{t,a} RPS_{(t+ra),a}
$$
This method assumes that there is no effect of age on reproductive success (i.e., each kilogram of spawning biomass contributes the same to the total total reproductive output, irrespective of their age). Finally, the fecundity is calculated as number of offspring produced by each individual in the population

$$
Fec_{t,a} =  RPA_{t,a} / SSN_{t,a}
$$

Due to challenges with separability in typical stock assessment models, natural mortality is often assumed for each age class, in some assessments it varies by age and over time, in other assessments it does not.  Irrespective of this, the stock assessment used in this analysis all provide an estimate of natural mortality by age and year, this value is typically an instantaneous rate and is convert to a proportional natural mortality for the Euler-Lotka model.

The data also contains the number of fish harvested by the fishery each year and for each age. This can be combined with the assessed numbers at age to get an estimate of fishing mortality in each year for each age.

$$
FM_{t,a} =  Catch_{t,a} / N_{t,a}
$$
This is combined with the natural mortality to get a total mortality estimate ($Z_{t,a}$) for each age in each year

$$
Z_{t,a} =  FM_{t,a} + NM_{t,a}
$$

The fecundity, natural mortality, and fishing mortality estimates were then used to obtain an estimate of $\lambda$ for a given year from the Euler-Lotka equation and used to predict the abundance in the following year.

$$
N_{t+1} = \lambda N_{t}
$$
The result of this was compared to the abundance estimate from the stock assessment for the upcoming year ($N_{t+1}$). Where necessary, the fecundity and natural mortality estimates were adjusted until the $\lambda$ estimate from the Euler-Lotka equation resulted in an abundance time-series estimate ($N_{t+1}$) that was less than 5% different from the abundance estimates from the stock assessment (AVERAGE DIFFERNCE WAS 0.XX%). In this way the $\lambda$, fecundity, and natural mortality estimates are obtained for each year in which data are available.

WONDER IF I HAVE THE "AVERAGE" DIFFERENCE of NM and FECUNDITY FROM THE ORIGINAL VALUES FROM THE ABOVE or is that opening up pandora's box.

<!-- For consistency in the Euler-lotka estimates across all the stocks, the first age used in the analysis was 'age 0' (which is simply an estimate of abundance of fish in the year they were born). For some stocks this information is not available (see Table X, **possibly in an Appendix where we have meta-data**). For the stocks in which age 0 information is unavailable, an estimate of the abundance of the younger age classes were back calculated using average natural mortality provided for the youngest age class available. -->

### 2024-04-16 Drafts/Paper_1/07-tables.Rmd
Update with age and no age correction
Revised to run the model without using the age-correction (i.e., model without going to age 0, which should work fine since fecundity of anything smaller than recruits is effectively 0 for basically all the stocks).  Results very similar to the 'age corrected' analysis.  A few minor bug fixes as well.  Also have part of the methods written.

---
output:
  word_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---
\clearpage
\newpage

# Tables {-}

### 2024-04-16 Drafts/Paper_1/08-figures.Rmd
Update with age and no age correction
Revised to run the model without using the age-correction (i.e., model without going to age 0, which should work fine since fecundity of anything smaller than recruits is effectively 0 for basically all the stocks).  Results very similar to the 'age corrected' analysis.  A few minor bug fixes as well.  Also have part of the methods written.

---
output:
  pdf_document:
    fig_caption: yes
    extra_dependencies: float
linkcolor: blue
header-includes: \usepackage{float}
editor_options:
  chunk_output_type: console
---

```{r, include=F, echo=F}
knitr::opts_knit$set(eval.after = "fig.cap")
knitr::opts_chunk$set(fig.pos = 'H')
options(knitr.kable.NA = '')
require(tidyverse)
options(tinytex.verbose = TRUE)

```

### 2024-04-16 Drafts/Paper_1/Paper_1_frist_draft.Rmd
Update with age and no age correction
Revised to run the model without using the age-correction (i.e., model without going to age 0, which should work fine since fecundity of anything smaller than recruits is effectively 0 for basically all the stocks).  Results very similar to the 'age corrected' analysis.  A few minor bug fixes as well.  Also have part of the methods written.

--- 2023-11-29 Scripts/Paper_1.Rmd
@@
 output:
-  pdf_document: default
-  html_document: default
+  #pdf_document: default
+  #html_document: default
   word_document: 
@@
 
-```{r, load-stuff,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
+```{r, load-stuff,echo=F, message=F, warning=F, fig.width=6, fig.height=4,include=F}
 # OK, so using the ICES assessments here's what we get for North Sea cod.
@@
 library(cowplot)
+library(gtable)
+library(viridis)
+theme_set(theme_few(base_size = 14))
+
+# The location of your data
 loc <- 'D:/GitHub/ICM'
 
-source(paste0(loc,"/Scripts/functions/tuning_sim_fast.R"))
+# If we already have the results don't re-run the models or load data we don't need.
+load.results <- T
+# What tunning model are you running or did you run!
+what.2.tune <- 'fec_nm'
 
+#source(paste0(loc,"/Scripts/functions/tuning_sim_fast.R"))
+
+# Download the functions we'll need from github
+funs <- c("https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/simple_Lotka_r.r",
+          "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/backwards_project.r",
+          "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/forward_project.r",
+          "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/tuning_sim_fast.r"
+)
+  # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
+for(fun in funs) 
+{
+  download.file(fun,destfile = basename(fun))
+  source(paste0(getwd(),"/",basename(fun)))
+  file.remove(paste0(getwd(),"/",basename(fun)))
+}
+
+if(load.results==F)
+{
   # Choose 5 ICES stocks that we have the necessary data for
@@
   ASR_long <- ASR_long %>% dplyr::filter(Stock != "ICES-AFWG_DEEP1-2_Sebastes_mentella")
-
+}# end if load results
 ```
-
-```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
-
-Stocks <- ASR_long %>%
-                    dplyr::filter(!is.na(value)) %>%
-                    dplyr::group_by(Stock, type) %>%
-                    dplyr::summarize(count=length(unique(value))) %>%
-                    dplyr::group_by(Stock) %>%
-                    dplyr::summarize(types=length(unique(type))) %>%
-                    dplyr::filter(types==5) %>%
-                    dplyr::select(Stock)
-
-ASR_stocks <- ASR_long %>%
-                        dplyr::filter(Stock %in% Stocks$Stock) %>%
-                        dplyr::filter(!is.na(value)) %>%
-                        dplyr::arrange(Stock, Year, type, as.numeric(age))
-
-# Stocks <- ASR_stocks %>%
-#                       dplyr::group_by(Stock, Species, type) %>%
-#                       dplyr::summarize(ages=length(unique(age)),
-#                                 years=length(unique(Year))) %>%
-#                       dplyr::arrange(-years, -ages) %>%
-#                       dplyr::filter(!Species=="morhua") %>%
-#                       dplyr::distinct(Stock) %>%
-#                       dplyr::pull(Stock)
-# 
-# print(Stocks)
-Stocks <- Stocks$Stock
-
-# Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
-#Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
-# Esmarki doesn't work great as it is assessed using a quarterly model.
-#Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
-#i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
-years.tmp <- NULL
-pnm.tmp <- NULL
-waa.tmp <- NULL
-ages.tmp <- NULL
-rem.tmp <- NULL
-mx.tmp <- NULL
-NE.tmp <- NULL
-vpa.tmp <- NULL
-am.tmp <- NULL
-mr.tmp <- NULL
-all.abund.tmp <- NULL
-full.abund.tmp <- NULL
-full.rem.tmp <- NULL
-fs.tmp <- NULL
-for(i in Stocks)
-{
-  print(i)
-  ASR_sub <- ASR_long %>%
-    dplyr::select(Year, Stock, type, age, value) %>%
-    dplyr::filter(Stock==i)
-
-  # Drop the NA years....
-  if(i == "ICES-NWWG_ICE-Summer_Clupea_harengus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1986)
-  # There's some funkiness going on in the first 7 years of these data, so staring in year 8
-  if( i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1971)
-  if(i == "ICES-NWWG_FA5b_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)
-  if(i == "ICES-NWWG_FA5a_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1984)
-  if(i == "ICES-AFWG_NEA1-2_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1969)
-  if(i == "ICES-WGCSE_CS27.6a_Merlangius_merlangus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1980)
-  if(i == "ICES-WGCSE_NS6a_Gadus_morhua") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1980)
-  if(i == "ICES-AFWG_COASTNOR 1-2_Gadus_morhua") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 2006)
-  if(i == "NEFSC_5Z_Pseudopleuronectes_americanus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)
-  if(i == "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1989)
-
-  # maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]))
-  # maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)])
-  # minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)])
-  # forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
-  # 
-  # # summary plots
-  # print(ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
-  #         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
-  #         theme_bw() + 
-  #         ggtitle(i)
-  # )
-
-  age.mat <- ASR_sub %>% dplyr::filter(type=="AM") %>% dplyr::rename(AM=value) %>% dplyr::select(-type)
-  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
-  # in case that changes later...
-  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
-  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
-  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
-  am.3s <- length(which((!is.na(age.mat$AM[age.mat$age ==3]))))
-  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
-  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
-  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0
-  if(am.3s == 0) age.mat$AM[age.mat$age ==3] <- 0
-
-   # Now we can get the abundance from the VPA models
-  abund <- ASR_sub %>% dplyr::filter(type=="Num") %>% dplyr::rename(Num=value) %>% dplyr::select(-type)
-
-  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
-  # Now do something similar for the Natural moralities, but in this case
-  # we take the NM of the youngest age class we have information for and back that number up to year 0.
-  # DK NOTE:  THIS IS A BIG CHANGE IN DIRECTION FOR THE LOTKA CALCS SO NEED TO NOTE THIS ONE!!
-
-  nm.tmp <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
-
-  #minage
-  minage <- min(as.numeric(nm.tmp$age[!is.na(nm.tmp$NM)]))
-  if(minage == 0)  nat.mort <- nm.tmp
-  # Some specials...
-  if(i %in% c("ICES-WGCSE_CS7e-k_Gadus_morhua","ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus",
-              "ICES-WGHANSA_SP8abd_Sardina _pilchardus","ICES-WGWIDE_NEA 1-9,12,14_Micromesistius_poutassou")) minage <- 1
-  if(i == "ICES-WGWIDE_NEA 1,2,5,4a,14a_clupea_ harengus") minage <- 2
-  #maxage
-  maxage <- max(as.numeric(nm.tmp$age[!is.na(nm.tmp$NM)]))
-
-  # Now get the number of individuals in the youngest age category
-  num.age.min <- ASR_sub %>% dplyr::filter(age==minage,type=="Num")
-  # So any Recruitment even that is > 3 SE's away from the median I'm calling 
-  # an 'extreme' recruitment event and it is going to get a lower/higher natural mortality term.
-  med.mun.age.min <- mean(num.age.min$value,na.rm=T)
-  sd.mun.age.min <- sd(num.age.min$value,na.rm=T)#/sqrt(length(na.omit(num.age.min$value)))
-  low.rec <- med.mun.age.min - 2*sd.mun.age.min
-  high.rec <- med.mun.age.min + 2*sd.mun.age.min
-  high.rec.years <- as.vector(na.omit(num.age.min$Year[num.age.min$value > high.rec]))
-  low.rec.years <- as.vector(na.omit(num.age.min$Year[num.age.min$value < low.rec]))
-  # Set up the full abundance matrix 
-  full.abund <- abund
-  print(paste0("Stock ", i , ' high recruit years include ', length(c(low.rec.years,high.rec.years)), ' years'))
-  # If we need to imput some data run this loop for natural mortality
-  if(minage == 0) full.abund <- abund
-
-  if(minage > 0)
-  {
-    yrs <- sort(unique((nm.tmp$Year)))
-    nm.res <- NULL
-    # These already have NM estimates at 0 so don't need to do them...
-    if(!i %in% c("ICES-WGCSE_CS7e-k_Gadus_morhua","ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus",
-                 "ICES-WGHANSA_SP8abd_Sardina _pilchardus","ICES-WGWIDE_NEA 1,2,5,4a,14a_clupea_ harengus",
-                 "ICES-WGWIDE_NEA 1-9,12,14_Micromesistius_poutassou"))
-    {
-      # Just use the mean mortality of the youngest age class we have information for
-      nm.use <- mean(nm.tmp$NM[nm.tmp$age==minage],na.rm=T)
-      # Take the average natural mortality of the youngest age class with an m and use that
-      # This avoids really blowing up the abundance in the younger age classes which can get a bit squirrly
-      # nm.high.rec <- 0.5*(min(nm.tmp$NM[nm.tmp$age==minage],na.rm=T))
-      # nm.low.rec <-  1.5*(max(nm.tmp$NM[nm.tmp$age==minage],na.rm=T))
-      # Start by filling in everything...
-      nm.tmp$NM[is.na(nm.tmp$NM)] <- nm.use
-      nm.tmp <- nm.tmp[nm.tmp$age %in% 0:maxage,]
-      # Now we need to fill in the 'special' cohorts that were really big (low m) or really small (high m)
-      # for(y in length(yrs):1)
-      # {
-      #   if(yrs[y] %in% c(high.rec.years,low.rec.years))
-      #   {
-      #     if(yrs[y] %in% high.rec.years) nm.pick <- nm.high.rec
-      #     if(yrs[y] %in% low.rec.years) nm.pick <- nm.low.rec
-      #     for(a in minage:1) nm.tmp$NM[nm.tmp$Year == (yrs[y]-a) & nm.tmp$age == minage-a] <- nm.pick
-      # }} #Close the if and for loops
-      # Pointless rename...
-    } #end the skip the stocks with nm at 0 if
-      nat.mort <- nm.tmp
-
-  # Now do the same loopiness for abundance
-    for(y in length(yrs):2)
-    {
-      # The minage of the natural mortality is different from minage of the abundance, annoyingly for this stock...
-      if(i == "ICES-AFWG_NEA1-2_Gadus_morhua") minage <- 3
-      if(i == "ICES-NWWG_ICE-Summer_Clupea_harengus") minage <- 3
-
-           # The lowest minage =4, This goes first since we go backwards, this gets us age 3 in year 3
-           if(minage ==4) 
-           {
-               four.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 4) %>% dplyr::pull(Num)
-               nm.four <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][4,]$NM) 
-               full.abund[full.abund$Year ==yrs[y]-1,][4,]$Num <- four.abund/(1-nm.four)
-             #}# end my 2:0
-           } # end if minage ==4
-
-            # The minage =3 scenario, goes after 4...
-           if(minage >=3)
-           {
-             # for(my in 0:1)
-             # {
-               three.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 3) %>% dplyr::pull(Num)
-               nm.three <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][3,]$NM) 
-               full.abund[full.abund$Year ==yrs[y]-1,][3,]$Num <- three.abund/(1-nm.three)
-             #} # end my 1:0
-           } # end if(minage ==2)
-
-           # The minage =2 scenario, this goes last
-           if(minage >=2)
-           {
-             two.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 2) %>% dplyr::pull(Num)
-             nm.two <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][2,]$NM) 
-             full.abund[full.abund$Year ==yrs[y]-1,][2,]$Num <- two.abund/(1-nm.two)
-           } # end if(minage ==2)
-
-           if(minage >=1)
-           {
-             one.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 1) %>% dplyr::pull(Num)
-             nm.one <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][1,]$NM) 
-             full.abund[full.abund$Year ==yrs[y]-1,][1,]$Num <- one.abund/(1-nm.one)
-           } # end if(minage ==2)
-
-         } # The annoying if to fill in rest of the first few years.
-  } # end if minage > 0
-
-  # We won't have a weight at age for the young ages, which is fine since we only need that for SSB
-  weight.age <- ASR_sub %>% dplyr::filter(type=="WA") %>% dplyr::rename(WA=value) %>% dplyr::select(-type)
-  removals <- ASR_sub %>% dplyr::filter(type=="Catch") %>% dplyr::rename(Catch=value) %>% dplyr::select(-type)
-  # Fill the leading NAs with 0s now...
-  if(minage > 0) 
-  {
-    weight.age$WA[weight.age$age %in% 0:(minage-1)] <- 0
-    removals$Catch[removals$age %in% 0:(minage-1)] <- 0
-  }
- # if(i=="ICES-WGBFAS_BS 22-32_Sprattus_sprattus") removals$Catch <- removals$Catch/1000
-
-  data <- age.mat %>%
-    full_join(nat.mort) %>%
-    #full_join(abund) %>%
-    full_join(full.abund) %>%
-    full_join(weight.age) %>%
-    full_join(removals)
-
-  # Nice way to toss NAs!
-  data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
-  data <- data[data$available==T,]
-  # And then toss the years we don't have 0 data for Numbers in the 0 age class
-  toss.years <- data %>% dplyr::group_by(Year) %>% dplyr::reframe(bad.years = which(min(age)>0))
-  data <- data[!data$Year %in% toss.years$Year,]
-
-  # Tidy up the data for input...
-  data$prop.nat.mort <- 1-exp(-data$NM)
-  #prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))] <- 1-exp(-prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))])
-
-  rem <- data %>% dplyr::group_by(Year,.drop=F) %>% dplyr::summarize(rem=sum(Catch,na.rm=T)) #%>% dplyr::pull(rem)
-
-  missing_rem<- NULL
-  if(any(is.na(rem$rem))) 
-  {
-    missing_rem <- unique(data$Year)[which(is.na(rem$rem))]
-    rem$rem[is.na(rem$rem)] <- median(rem$rem, na.rm=T)
-  }
-
-  #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
-  years <- data %>% dplyr::pull(Year) %>% unique() %>% sort()
-
-  N.end <- sum(data[data$Year==max(years),]$Num)
-  all.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
-  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::filter(age %in% minage:maxage) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
-  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
-
-  #recruits
-  annual <- data.frame(Year=data$Year[data$age==0], recruits=data$Num[data$age==0])
-  #ssn
-  data$ssn <- data$Num * data$AM
-  #ssb
-  data$ssb <- data$ssn * data$WA #I need to figure out how to line this up with the number of recruits for the right years in the data object.... got it right for the overall r.p.ssb below.
-  #tot.ssb
-  annual <- data %>% group_by(Year) %>% summarize(tot.ssb = sum(ssb)) %>% left_join(annual)
-
-  #tst <- data %>% group_by(Year) %>% summarize(tot.ssn = sum(ssn)) %>% left_join(annual)
-
-  #r.p.ssb So we are assuming the SSB in year X produces the observed recruits in year X
-  annual$r.p.ssb <- annual$recruits/annual$tot.ssb
-  # recs.per.age
-  data <- left_join(data, annual)
-  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
-  # tmp <- NULL
-  # for(j in 1:length(years))
-  # {
-  #   tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
-  #   tst$Year <- tst$Year + minage
-  #   names(tst) <- c("ssb.offset","ssn.offset","Year","age")
-  #   tmp[[j]] <- tst
-  # }
-  # Unpack the list
-  #@ssb.off <- do.call('rbind',tmp)
-  # And merge it with the data object
-  #data <- left_join(data,ssb.off,by=c("Year","age"))
-  data$recs.per.age <- data$ssb*data$r.p.ssb
-  # mx
-  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
-  # The demographic models are 'female' only, so we'd want to divide the number of recruits by 2 and the SSN by 2, but that just cancels out
-  # so there is no need to make the mom adjustment.
-  data$mx <- data$recs.per.age/data$ssn # if(grepl("males",i))
-  # if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn/2 # Moms only! 
-  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
-  # Now for the very high recruitment years allow for a small amount of recruitment (20% of the lowest age) in the age classes after year 0....
-
-  # if(length(high.rec.years) > 0)
-  # {
-  #   for(y in high.rec.years)
-  #   {
-  #     tmp <- data$AM[data$Year == y]
-  #     am.fill <- which(tmp ==0) 
-  #     if(length(am.fill) > 1) data$mx[data$Year == y-1][am.fill[-1]] <- 0.2*min(data$mx[data$Year == y & data$mx > 0],na.rm=T)
-  #   }
-  # }
-
-  age.mat <- data %>% dplyr::select("Year", "age", "AM") %>% pivot_wider(names_from=age, values_from = AM) %>% dplyr::select(-Year)
-  prop.nat.mort <- data %>% dplyr::select("Year", "age", "prop.nat.mort") %>% pivot_wider(names_from=age, values_from = prop.nat.mort) %>% dplyr::select(-Year) %>% as.data.frame
-  weight.age <- data %>% dplyr::select("Year", "age", "WA") %>% pivot_wider(names_from=age, values_from = WA) %>% dplyr::select(-Year)
-  mx <- data %>% dplyr::select("Year", "age", "mx") %>% pivot_wider(names_from=age, values_from = mx) %>% dplyr::select(-Year) %>% as.data.frame()
-  abund.age <- data %>% dplyr::select("Year", "age", "Num") %>% pivot_wider(names_from=age, values_from = Num) %>% dplyr::select(-Year) %>% as.data.frame()
-  # Now we can save out the catch and get an instantaneous F
-  data$Catch[is.na(data$Catch)] <- 0
-  data$Exp <- data$Catch/data$Num
-  # If it is exactly 1 that leads to an Inf, which is annoying, so make it 1.1 and fix it with the rest below
-  data$Exp[data$Exp == 1] <- 1.1
-  # And make this an F
-  data$Fs <- -log(1-data$Exp)
-  if(any(is.na(data$Fs)))
-  {
-    fixers <- which(is.na(data$Fs))
-    print(paste0("Had to replace ",length(fixers), ' exploitation rates for stock ',i))
-    for(f in fixers)
-    {
-      yr <- data$Year[f]
-      fs <- max(data$Fs[data$Year == yr],na.rm=T)
-      data$Fs[f] <- fs
-      data$Exp[f] <- 1-exp(-fs)
-    }
-  }
-
-  full.rems <- data %>% dplyr::select("Year", "age", "Catch") %>% pivot_wider(names_from=age, values_from = Catch) %>% dplyr::select(-Year)
-  full.Fs <-  data %>% dplyr::select("Year", "age", "Fs") %>% pivot_wider(names_from=age, values_from = Fs) %>% dplyr::select(-Year)
-
-  if(i == "DFO_2J3KL_Gadus_morhua")
-  {
-    age.mat[,10:12] <- 1
-    prop.nat.mort[,10:12] <- prop.nat.mort[,9]
-    weight.age[12:14,11:12] <- weight.age[12:14,10]
-    weight.age[15,12] <- weight.age[15,11]
-    mx[12:14,11:12] <- mx[12:14,10]
-    mx[15,12] <- mx[15,11]
-    full.Fs[12:14,11:12] <- full.Fs[12:14,10]
-    full.Fs[15,12] <- full.Fs[15,11]
-    abund.age[12:14,11:12] <- abund.age[12:14,10]
-    abund.age[15,12] <- abund.age[15,11]
-    # I could calculate, but this will get us to the same place...
-    full.rems[12:14,11:12] <- full.rems[12:14,10]
-    full.rems[15,12] <- full.rems[15,11]
-  }
-
-  if(i == "DFO_4T-Spring_Clupea_harengus")
-  {
-    age.mat[6:7,12] <- 1
-    prop.nat.mort[6:7,12] <- prop.nat.mort[6:7,11]
-    weight.age[6:7,12] <- weight.age[6:7,11]
-    mx[6:7,12] <- mx[6:7,11]
-    full.Fs[6:7,12] <- full.Fs[6:7,11]
-    abund.age[6:7,12] <- abund.age[6:7,11]
-    full.rems[6:7,12] <- full.rems[6:7,11]
-  }
-
-  if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
-  {
-    age.mat[30,9] <- 1
-    prop.nat.mort[30,9] <- prop.nat.mort[30,8]
-    weight.age[30,9] <- weight.age[29,9]
-    mx[30,9] <- mx[30,8]
-    full.Fs[30,9] <- full.Fs[30,8]
-    abund.age[30,9] <- abund.age[30,8]
-    full.rems[30,9] <- full.rems[30,8]
-  }
-
-  if(i == "ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax")
-  {
-    age.mat[c(14,27,40),7] <- age.mat[1,7]
-    prop.nat.mort[c(14,27,40),7] <- prop.nat.mort[1,7]
-    weight.age[c(14,27,40),7] <- weight.age[c(13,26,39),7]
-    mx[c(14,27,40),7] <- mx[c(14,27,40),6]
-    full.Fs[c(14,27,40),7] <- full.Fs[c(14,27,40),6]
-    abund.age[c(14,27,40),7] <- abund.age[c(14,27,40),6]
-    full.rems[c(14,27,40),7] <- full.rems[c(14,27,40),6]
-  }
-  # Clear out some 0's...
-  if( i == "AFSC_EEBSAI_Limanda_aspera")
-  {
-    mx[4,19] <- mean(unlist(mx[4,c(18,20)]))
-    mx[c(5,7),20] <- mx[c(5,7),19]
-    mx[1:6,21] <- mx[1:6,20] 
-  }
-  # For the years of mx without SSB info to inform them
-  # if(minage >0 ) 
-  # {
-  #   mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
-  #   names(mx) <- names(mx.fill)
-  #  # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
-  #   mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
-  # }
-  years.tmp[[i]] <- years
-  pnm.tmp[[i]] <- prop.nat.mort
-  waa.tmp[[i]] <- weight.age
-  ages.tmp[[i]] <- minage:maxage
-  rem.tmp[[i]] <- rem
-  mx.tmp[[i]] <- mx
-  NE.tmp[[i]] <- N.end
-  vpa.tmp[[i]] <- vpa.abund
-  all.abund.tmp[[i]] <- all.abund
-  full.abund.tmp[[i]] <- abund.age
-  am.tmp[[i]] <- age.mat
-  mr.tmp[[i]] <- missing_rem
-  fs.tmp[[i]] <- full.Fs
-  full.rem.tmp[[i]] <- full.rems
-} #end input data loop
-
-save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,am.tmp,Stocks,ASR_stocks,ASR_long,all.abund.tmp,full.abund.tmp,fs.tmp,full.rem.tmp,file =  paste0(loc,"/Results/model_inputs_all_ages.Rdata"))
-
-```
-
-So now I can try to do some tuning, both forwards and backwards, lets see what we get from that...
-
-```{r tunes}
-
-########################## Now run the tuning sims
-#
-
-load(file = paste0(loc,"/Results/model_inputs_all_ages.Rdata"))
-
-#DK PICK IT UP HERE#
-# OK So the problem isn't so much "high" recruitment events, it's years in which the population abundance jumps like crash, Stock 57 (ICES Haddock NS)
-# Is the best example, look at year 2005, it isn't a outlier in terms of numbers of recruits, but the population jump from 2004 to 2005 is huge and
-# thus it's those years that get us the crazy fecundity numbers, which can easily be ameliorated by having a small fecundity in the age classes
-# that aren't supposed to be mature yet.  Of course, is that BS, maybe!!  Ended the night running all the stocks trying to see what the changes so far brought about.
-
-back.tune.all.res <- NULL
-back.tune.summary <- NULL
-for.tune.all.res <- NULL
-for.tune.summary <- NULL
-for(i in Stocks)
-{
-  years <- years.tmp[[i]]
-  prop.nat.mort <- pnm.tmp[[i]] 
-  #rem <- rem.tmp[[i]] 
-  mx <- mx.tmp[[i]] 
-  N.end <- NE.tmp[[i]] 
-  ages <- ages.tmp[[i]]
-  vpa.abund <- vpa.tmp[[i]] 
-  all.abund <- all.abund.tmp[[i]]
-  fs <-fs.tmp[[i]]
-  full.rem <- full.rem.tmp[[i]]
-  full.abund <- full.abund.tmp[[i]]
-  #all.abund <- full.abund.tmp[[i]]
-  #N.end <- vpa.abund[length(vpa.abund)]
-  #Pick your step size
-  ss.size <- 0.01
-  sensistive.stocks <- c("ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
-                          "ICES-HAWG_NS_Ammodytes_dubius",
-                          "DFO_2J3KL_Gadus_morhua",
-                          "DFO_3Pn-4RS_Gadus_morhua",
-                          "DFO_4T-4VN_Gadus_morhua",
-                          "ICES-WGCSE_IS7a_Gadus_morhua",
-                          "ICES-WGCSE_CS7a_Merlangius_merlangus",
-                          "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua",
-                          "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",
-                          "ICES-WGHANSA_SP8abd_Sardina _pilchardus",
-                          "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus",
-                          "NEFSC-GARMIII_SNE- MA_Limanda_ferruginea",
-                          "NEFSC-GARMIII_MA_Paralichthys_dentatus",
-                          "ICES-WGCSE_CS7e-k_Gadus_morhua",
-                          "DFO_4T_Scomber_scombrus",
-                          "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
-                          "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
-                           "AFSC_GOA_Theragra_chalcogramma")
-
-  if(i %in% sensistive.stocks) ss.size = ss.size/10
-
-   N.start <- all.abund[1]
-   print(i)
-   # The fecundities are 
-   fast.for.tune <- fast.tunes(years,
-                           tuner='fec_nm',
-                           step.size = ss.size, 
-                           abund.ts = all.abund,
-                           ages=ages,
-                           nm = -(log(1-prop.nat.mort)),
-                           fecund = mx,
-                           fm = fs,
-                           abund.age = full.abund, 
-                           catch.age = full.rem, 
-                           N.init = N.start,
-                           direction= 'forwards'
-                           )
-
-   for.tune.all.res[[i]] <- fast.for.tune
-   for.tune.tmp <- data.frame(fast.for.tune$res,Stock = i)
-   for.tune.summary[[i]] <- for.tune.tmp
-
-   N.end <- all.abund[length(all.abund)]
-
-   # fast.back.tune <- fast.tunes(years,
-   #                         tuner='fm',
-   #                         step.size = 0.01, # Make sure n.steps is even please!!
-   #                         abund.ts = all.abund,
-   #                         ages=ages,
-   #                         nm = -(log(1-prop.nat.mort)),
-   #                         fecund = mx,
-   #                         fm = fs,
-   #                         abund.age = full.abund, 
-   #                         catch.age = full.rem, 
-   #                         N.init = N.end,
-   #                         direction= 'backwards'
-   #                         )
-   # 
-   # back.tune.all.res[[i]] <- fast.back.tune
-   # back.tune.tmp <- data.frame(fast.back.tune$res,Stock = i)
-   # back.tune.summary[[i]] <- back.tune.tmp
-
-}
-
-#DFO_2J3KL_Gadus_morhua -27.7984654 2.815738e+08
-#ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax -21.6050608
-# ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax Lotka error
-# ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus # lotka error
-
-# Fixed...
-#ICES-HAWG_NS_Ammodytes_dubius Overshoot
-# ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii  Overshoot
-#ICES-WGNSSK_NS 4-7d,20_Gadus_morhua Overshoot
-# ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus Overshoot
-# ICES-WGCSE_ISbc-ek_Melanogrammus_aeglefinus  Overshoot
-
-#saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_z.Rds")
-#saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_z.Rds")
-# saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_nm.Rds")
-# saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_nm.Rds")
-#saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_fm.Rds")
-#saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_fm.Rds")
-saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_fec_nm.Rds")
-saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_fec_nm.Rds")
-#
-
-```
-
-```{r paper-other-metrics-and-metadata}
-
-# We are now looking at everything, lifetime reproductive success
-model <- "fec_nm"
-for.tune.summary <- readRDS(paste0("D:/Github/ICM/Results/forwards_fully_tuned_summary_",model,".Rds"))
-for.tune.all <- readRDS(paste0("D:/Github/ICM/Results/forwards_fully_tuned_all_res_",model,".Rds"))
-
-load(file =  paste0(loc,"/Results/model_inputs_all_ages.Rdata"))
-# Get the stocks...
-Stocks <- names(for.tune.summary)
-n.stocks <- length(Stocks)
-
-############ Meta data and clean up, could be it's own chunk really, but it's really fast, so meh...
-
-#  A quick way to get the other potentially interesting info for the stock...
-drop <- which(names(ASR_long) %in% c("Year","type","age","value"))
-meta <- NULL
-for(i in Stocks) meta[[i]] <- ASR_long[ASR_long$Stock == i,-drop][1,]
-meta <- do.call('rbind',meta)
-
-# First making a meta data object and adding a bunch of columns to it... very messy!!
-meta$Species[meta$Species == ' harengus']  <- "harengus"
-meta$Species[meta$Species == "Aeglefinus"] <- "aeglefinus"
-meta$Species[meta$Species == "Solea"] <- "solea"
-meta$Genus[meta$Genus == " Hippoglossoides"] <- "Hippoglossoides"
-meta$G.short <- toupper(paste0(substr(meta$Genus,1,1),"."))
-meta$G.Species <- paste0(meta$G.short," ",meta$Species)
-# Simplified Management
-meta$Manage.short <- meta$Management
-meta$Manage.short[grep("TRAC",meta$Management)] <- "DFO-TRAC"
-meta$Manage.short[grep("DFO",meta$Management)] <- "DFO-TRAC"
-meta$Manage.short[grep("NEFSC",meta$Management)] <- "NEFSC"
-meta$Manage.short[grep("ICES",meta$Management)] <- "ICES"
-
-# The 3 pieces of the ocean
-meta$LME <- "NW Atlantic"
-meta$LME[meta$Management == "AFSC"] <- "Pacific (Alaska)"
-meta$LME[grepl("ICES",meta$Management)] <- "NE Atlantic"
-# Some other Area summaries
-meta$Area.broad <- meta$Area
-meta$Area.long <- meta$Area
-meta$Area.narrow <- "" # Leave this blank if not needed
-
-meta$Area.broad[grep("NS",meta$Area)] <- "NS"
-meta$Area.long[grep("NS",meta$Area)] <- "North Sea"
-meta$Area.broad[grep("CS",meta$Area)] <- "CS"
-meta$Area.long[grep("CS",meta$Area)] <- "Celtic Sea"
-meta$Area.broad[grep("ROCK6b",meta$Area)] <- "CS"
-meta$Area.long[grep("ROCK6b",meta$Area)] <- "Celtic Sea Rockall"
-meta$Area.broad[grep("IS",meta$Area)] <- "IS"
-meta$Area.long[grep("IS",meta$Area)] <- "Irish Sea"
-meta$Area.broad[grep("BS",meta$Area)] <- "BS"
-meta$Area.long[grep("BS",meta$Area)] <- "Baltic Sea"
-meta$Area.broad[grep("NEA",meta$Area)] <- "NEA"
-meta$Area.long[grep("NEA",meta$Area)] <- "NE Arctic"
-meta$Area.broad[grep("B28.1",meta$Area)] <- "BS"
-meta$Area.long[grep("B28.1",meta$Area)] <- "Baltic Sea"
-meta$Area.broad[grep("SP8abd",meta$Area)] <- "BoB"
-meta$Area.long[grep("SP8abd",meta$Area)] <- "Bay of Biscay"
-meta$Area.broad[grep("FA",meta$Area)] <- "I-F"
-meta$Area.broad[grep("ICE",meta$Area)] <- "I-F"
-meta$Area.long[grep("FA",meta$Area)] <- "Faroes"
-meta$Area.long[grep("ICE",meta$Area)] <- "Iceland"
-
-meta$Area.broad[grep("GOM",meta$Area)] <- "GOM-GB"
-meta$Area.long[grep("GOM",meta$Area)] <- "Gulf of Maine"
-meta$Area.broad[grep("GB",meta$Area)] <- "GOM-GB"
-meta$Area.long[grep("GB",meta$Area)] <- "Georges Bank"
-meta$Area.broad[grep("5Y",meta$Area)] <- "GOM-GB"
-meta$Area.long[grep("5Y",meta$Area)] <- "NAFO 5Y"
-meta$Area.broad[grep("5Z",meta$Area)] <- "GOM-GB"
-meta$Area.long[grep("5Z",meta$Area)] <- "NAFO 5Z"
-meta$Area.broad[grep("USATL",meta$Area)] <- "GOM-GB" # The fishery is broader than just GOM, but it does also include it.
-meta$Area.long[grep("USATL",meta$Area)] <- "US Atlantic" # The fishery is broader than just GOM, but it does also include it.
-meta$Area.broad[grep("NWA",meta$Area)] <- "GOM-GB" # Mackerel... so that definition is a bit narrow....
-meta$Area.long[grep("NWA",meta$Area)] <- "US Atlantic" # Mackerel... so that definition is a bit narrow....
-#meta$Area1[grep("SNE- MA",meta$Area)] <- "GOM-GB" # YT in US, so no GB so that definition is a bit narrow....
-meta$Area.broad[grep("MA",meta$Area)] <- "GOM-GB" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
-meta$Area.long[grep("MA",meta$Area)] <- "Gulf of Maine" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
-meta$Area.broad[grep("BSAI",meta$Area)] <- "BSAI"
-meta$Area.broad[grep("4T",meta$Area)] <- "GSL"
-meta$Area.long[grep("4T",meta$Area)] <- "NAFO 4T"
-meta$Area.broad[grep("2J3",meta$Area)] <- "NFLD"
-meta$Area.long[grep("2J3",meta$Area)] <- "NFLD"
-meta$Area.broad[grep("3Pn-4RS",meta$Area)] <- "NFLD"
-meta$Area.long[grep("3Pn-4RS",meta$Area)] <- "NFLD"
-meta$Area.long[grep("GOA",meta$Area)] <- "Gulf of Alaska"
-meta$Area.long[grep("AI",meta$Area)] <- "Aleutian Islands"
-meta$Area.long[grep("ESB",meta$Area)] <- "Bering Sea"
-meta$Area.long[grep("BSAI",meta$Area)] <- "Bering Sea & AI"
-meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI-Females"
-meta$Area.long[grep("BSAI-Females",meta$Area)] <- "Bering Sea & AI"
-meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Pollachius_virens"] <- "5b"
-meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5a_Pollachius_virens"] <- "5a"
-meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS4 _Solea_solea"] <- "4"
-meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d._Solea_solea"] <- "7d"
-meta$Area.narrow[meta$Stock == "ICES-WGBFAS_NS IIIa 22-24_Solea_Solea"] <- "22-24"
-meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d_Pleuronectes_platessa"] <- "7d"
-meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4,20_Pleuronectes_platessa"] <- "4 20"
-meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS7e_Pleuronectes_platessa"] <- "7e"
-meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS27.7a_Pleuronectes_platessa"] <- "7a"
-meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Melanogrammus_aeglefinus"] <- "5b"
-meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Melanogrammus_aeglefinus"] <- "5a"
-meta$Area.narrow[meta$Stock == "ICES-WGBFAS_B28.1_Clupea_harengus"] <- "28"
-meta$Area.narrow[meta$Stock == "ICES-WGBFAS_BS 25-29-32_Clupea_harengus" ] <- "25-32"
-meta$Area.narrow[meta$Stock == "ICES-HAWG_WBS 22-24_Clupea_harengus"] <- "22-24"
-meta$Area.narrow[meta$Stock == "DFO_4T-Fall_Clupea_harengus"] <- "Fall"
-meta$Area.narrow[meta$Stock == "DFO_4T-Spring_Clupea_harengus"] <- "Spring"
-meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS27.6a_Merlangius_merlangus"] <- "27.6a"
-meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS7a_Merlangius_merlangus"] <- "7a"
-meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Gadus_morhua"] <- "5a"
-meta$Area.narrow[meta$Stock == "ICES-NWWG_FAPL5b1_Gadus_morhua" ] <- "5b"
-meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua"] <- "4-7 20"
-meta$Area.narrow[meta$Stock == "ICES-WGCSE_NS6a_Gadus_morhua"] <- "6a"
-meta$Area.narrow[meta$Stock == "DFO_2J3KL_Gadus_morhua"] <- "2J 3KL"
-meta$Area.narrow[meta$Stock == "DFO_3Pn-4RS_Gadus_morhua"] <- "3Pn 4RS"
-meta$Area.narrow[meta$Stock == "NEFSC-CERT-TRAC_GB _Gadus_morhua"] <- "East"
-
-meta$Stock.short <- paste0(meta$Area.long," ",meta$Area.narrow," ",meta$G.short," ",meta$Species)
-meta$Stock.no.species <- paste0(meta$Area.long," ",meta$Area.narrow)
-
-for.tune.stocks <- NULL
-fta <- NULL
-
-# Going to rename these female stocks.
-fem.names <- c("AFSC_BASI-Females_Pleuronectes_quadrituberculatus",
-                  "AFSC_EEBSAI-Females_Lepidopsetta_polyxystra",
-                  "AFSC_BSAI-females_Atheresthes_stomais")
-fem.rename <- c("AFSC_BSAI_Pleuronectes_quadrituberculatus",
-                  "AFSC_EEBSAI_Lepidopsetta_polyxystra",
-                  "AFSC_BSAI_Atheresthes_stomais")
-# Going to drop these stocks
-dont <- paste(c("Mles","Males","COASTNOR"),collapse = "|")
-
-meta.sub <- NULL
-for(i in Stocks) 
-{
-  org.nam <- i
-  tmp <- for.tune.summary[[org.nam]]
-  new.stock.nam <- org.nam
-  # Don't bother for these stocks...
-  if(!grepl(dont,tmp$Stock[1]))
-  {
-    # Grab the metadata and add in some new useful things...
-    meta.sub[[i]] <- meta[meta$Stock == org.nam,]
-
-    # Rename the ladies
-    if(tmp$Stock[1] == fem.names[1]) new.stock.nam <- tmp$Stock <- fem.rename[1]
-    if(tmp$Stock[1] == fem.names[2]) new.stock.nam <- tmp$Stock <- fem.rename[2]
-    if(tmp$Stock[1] == fem.names[3]) new.stock.nam <- tmp$Stock <- fem.rename[3]
-
-    meta.sub[[i]]$Stock <- new.stock.nam
-    tmp <- data.frame(tmp,meta.sub[[i]])
-    # For tunes all
-    fta[[new.stock.nam]] <- for.tune.all[[org.nam]]
-    fta[[new.stock.nam]]$meta <- meta.sub[[i]]
-    for.tune.stocks[[new.stock.nam]] <- tmp
-  }# End skip stocks...
-}
-# Now unpack them...
-for.tunes <- do.call("rbind",for.tune.stocks)
-for.tune.all <- fta
-meta.sub <- do.call("rbind",meta.sub)
-
-######################### End Meta data and clean up #####################
-
-# Now some summaries...
-
-# Reset on the stocks...
-Stocks <- sort(names(for.tune.all))
-n.stocks <- length(Stocks)
-
-# Doubling time, no fishing
-dt.res <- NULL
-n.dt.sims <- 20 # Number of simultions...
-n.years <- 100
-for(i in Stocks)
-{
-  try <- for.tunes %>% dplyr::filter(Stock == i)
-  meta.tmp <- meta.sub %>% dplyr::filter(Stock == i)
-  double.time <- NA
-  pop <- 1000
-  tmp.res <- NULL
-for(s in 1:n.dt.sims)
-{
-  tmp <- rep(0,n.years)
-
-  for(y in 2:n.years)
-  {
-    lambda <- sample(na.omit(try$lambda),size=1)
-    pop[y] <- lambda*pop[y-1]
-    if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.years] <- 1
-  } # end the years loop
-  tmp.res[[s]] <- data.frame(year =1:100,doubled = tmp,sim=s)
-  } # end sim loop
-  res.tmp <- do.call("rbind",tmp.res)
-
-dt.res[[i]] <- data.frame(res.tmp,meta.tmp)
-
-} # end Stocks loop
-
-dub.time <- do.call("rbind",dt.res)
-
-dub.time.summary <- dub.time %>% dplyr::group_by(Stock,year)  %>% dplyr::summarise(prop = sum(doubled)/n.dt.sims)
-dub.time.summary <- left_join(dub.time.summary,meta.sub,by="Stock")
-
-# Now to get generation lengths + reproductive rates....
-# First I need to get the fecundity and natural mortalities by cohort instead of year.
-res.fin <- NULL
-res.year.fin <- NULL
-res.lambda.fin <- NULL
-for(i in Stocks)
-{
-  tst <- for.tune.all[[i]]
-  meta.tmp <- tst$meta
-  # Fishing mortality
-  fm.org.tmp <- tst$fm.org
-  fm.tmp <- tst$fm.opt
-  # fecundity
-  fec.tmp <- tst$fecund.opt
-  fec.org.tmp <- tst$fecund.org
-  # Natural mortality
-  m.org.tmp <- exp(-tst$nm.org) # This is survivorship
-  m.tmp <- exp(-tst$nm.opt) # This is survivorship
-  # Total mortality
-  z.tmp <- exp(-tst$z.opt) # This is survivorship
-  z.org.tmp <- exp(-tst$nm.org -fm.org.tmp) # This is survivorship
-
-  ages <- 0:(ncol(fec.tmp)-1)
-  n.ages <- length(ages)
-  years <- tst$res$year
-  n.years <- length(years)
-  # Now I need to grab the fecundities and nat morts by cohort
-  if(n.years > n.ages)
-  {
-  res.cohort <- NULL
-  res.year <- NULL
-  res.lambda <- NULL
-  for(y in 1:(n.years-n.ages+1))
-  {
-    count = 0
-    fs <- NA
-    lx <- 1
-    fs.org <- NA
-    lx.org <- 1
-    lx.year <- 1
-    for(a in 1:n.ages)
-    {
-    fs[a] <- fec.tmp[y+count,a]  
-    fs.org[a] <- fec.org.tmp[y+count,a]  
-    if(a > 1) 
-    {
-      lx[a] <- lx[a-1] * m.tmp[y+count,a]  
-      lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
-      lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
-    }  # end the a > 1 if
-        count <- count + 1
-    }# end the ages loop
-        res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,lx.org = lx.org,age = ages,
-                               mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
-                               x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
-                               cohort=years[y],meta.tmp)
-
-        res.year[[y]] <- data.frame(mx.opt = unlist(fec.tmp[y,]),lx.opt = lx.year,age = ages,
-                               mx.lx.opt = unlist(fec.tmp[y,])*lx.year,
-                               x.mx.lx.opt = unlist(fec.tmp[y,])*lx.year*ages,
-                               year=years[y],meta.tmp)
-
-  } # end the years loop
-
-# Do a years loop to get lambda with no fishing for each year, rather than by cohort...
-  for(yy in 1:n.years)
-  {
-    nm <- as.numeric(tst$nm.opt[yy,])
-    z <- as.numeric(tst$z.opt[yy,])
-    fec <- as.numeric(tst$fecund.opt[yy,])
-    nm.init <- as.numeric(tst$nm.org[yy,])
-    fec.init <- as.numeric(tst$fecund.org[yy,])
-    z.init <- as.numeric(tst$z.org[yy,])
-    lam.no.fish <- exp(simple.lotka.r(Z = nm,fecund = fec,ages=ages)$res)
-    lam.fish <- exp(simple.lotka.r(Z = z,fecund = fec,ages=ages)$res)
-    lam.org.no.fish <- exp(simple.lotka.r(Z = nm.init,fecund = fec.init,ages=ages)$res)
-    lam.org.fish <- exp(simple.lotka.r(Z =  z.init,fecund = fec.init,ages=ages)$res)
-
-    # Now summarize these
-    res.lambda[[yy]] <-  data.frame(lam.no.fish = lam.no.fish,lam.fish = lam.fish,
-                                    lam.org.no.fish = lam.org.no.fish,
-                                    lam.org.fish = lam.org.fish,
-                                    year=years[yy],meta.tmp)
-  } # End the yy loop to get the lambdas...
-# unpack it...
-res.fin[[i]] <- do.call('rbind',res.cohort)
-res.year.fin[[i]] <- do.call('rbind',res.year)
-res.lambda.fin[[i]] <-  do.call('rbind',res.lambda)
-}  # end if to make sure we have enough data to get the cohort estimates.
-
-}# end the stock loop
-
-res.cohort.final <- do.call('rbind',res.fin)
-res.year.final <- do.call('rbind',res.year.fin)
-res.lambda.final <- do.call('rbind',res.lambda.fin)
-
-pop.dam <- res.cohort.final %>% dplyr::group_by(cohort,Stock) %>% dplyr::summarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
-                                                                gen.len.org = sum(x.mx.lx.org)/sum(mx.lx.org),
-                                                                R0.opt = sum(mx.lx.opt),R0.org = sum(mx.lx.org))
-pop.dam <- left_join(pop.dam,meta.sub,by="Stock")
-
-dub.time.summary <- data.frame(dub.time.summary)
-pop.dam <- data.frame(pop.dam)
-# saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",model,".Rds"))
-# saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",model,".Rds"))
-# saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",model,".Rds"))
-save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
-     file=paste0("D:/Github/ICM/Results/all_cleaned_forward_tune_summaries_",model,".Rdata"))
-
-write.csv(meta.sub, "D:/Github/ICM/Data/metadata.csv")
-
-```
-
-```{r simp-figs}
-theme_set(theme_few(base_size = 14))
-model <- 'fec_nm'
-load(file=paste0("D:/Github/ICM/Results/all_cleaned_forward_tune_summaries_",model,".Rdata"))
-
-pop.dam.6 <- pop.dam %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
-for.tunes.6 <- for.tunes %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
-res.lambda.final.6 <- res.lambda.final %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
-dub.time.6 <- dub.time.summary %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
-# Lambda plot
-
-res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(LME,Area.broad) %>%
-                                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(Species,Area.broad) %>%
-                                             dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::group_by(Stock) %>% 
-                                            dplyr::mutate(lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
-                                                          lam.fish.mn = mean(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T))
-
-#hmm <- merge(tst,res.lambda.final.6,by="Stock")
-
-# So this is lambda with fishing included
-lambda.plt <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.no.fish,x=Stock.no.species))  + 
-                                           geom_point(aes(y=lam.no.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-                                           xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_wrap(~G.Species,scales='free')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot("D:/Github/ICM/Figures/tuned/lambda_no_fishing_6.png",lambda.plt,base_width = 12,base_height = 10)
-
-# With fishing
-lambda.plt.fish <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.fish,x=Stock.no.species))  + 
-                                           geom_point(aes(y=lam.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-                                           xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_wrap(~G.Species,scales='free')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot("D:/Github/ICM/Figures/tuned/lambda_with_fishing_6.png",lambda.plt.fish,base_width = 12,base_height = 10)
-
-# Time series of lambdas....
-col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-#col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
-pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
-#pty <- rep(rep(c(21:23),5),20)
-
-lambda.ts.plt <- ggplot(res.lambda.final.6,aes(y=lam.fish,x=year,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
-                            geom_point(size=4) +
-                            geom_smooth(method='gam',formula = y ~ s(x, bs = "cs", fx = TRUE, k = 5),se=F) + 
-                            #scale_y_log10(name = "lambda") +
-                            facet_wrap(~G.Species,scales='free_y') +
-                            scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-                            scale_fill_manual(name = "Stock",values = col.try)+
-                            guides(colour = guide_legend(ncol = 1))+
-                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm'))
-#lambda.ts.plt
-save_plot("D:/Github/ICM/Figures/tuned/lambda_timeseries_6.png",lambda.ts.plt,base_width = 12,base_height = 10)
-
-res.lambda.final.6$decade <- floor(res.lambda.final.6$year/10)*10
-
-tst <- res.lambda.final.6 %>% dplyr::group_by(Stock,decade) %>% dplyr::summarise(mn.lam = mean(lam.fish,na.rm=T),
-                                                                                 med.lam = median(lam.fish,na.rm=T),
-                                                                                 sd.lam = sd(lam.fish,na.rm=T))
-tst <- merge(tst,meta.sub,by="Stock")
-
-tst <- tst %>% dplyr::arrange(Species,Area.broad) %>%
-                                             dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-lambda.dec.mn.plt <- ggplot(tst,aes(y=mn.lam,x=decade,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
-                            geom_jitter(size=4,width = 1) +
-                            scale_x_continuous(breaks=seq(1940,2020,by=10))+
-                            geom_hline(yintercept = 1,linetype='dashed') +
-                            facet_wrap(~G.Species,scales='free_y') +
-                            scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-                            scale_fill_manual(name = "Stock",values = col.try)+
-                            guides(colour = guide_legend(ncol = 1))+
-                            theme(legend.key.width = unit(5,'cm'))
-save_plot("D:/Github/ICM/Figures/tuned/lambda_decades_mean.png",lambda.dec.mn.plt,base_width = 30,base_height = 12)
-
-lambda.dec.med.plt <- ggplot(tst,aes(y=med.lam,x=decade,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
-                            geom_jitter(size=4,width = 1) +
-                            scale_x_continuous(breaks=seq(1940,2020,by=10))+
-                            geom_hline(yintercept = 1,linetype='dashed') +
-                            facet_wrap(~G.Species,scales='free_y') +
-                            scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-                            scale_fill_manual(name = "Stock",values = col.try)+
-                            guides(colour = guide_legend(ncol = 1))+
-                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm'))
-save_plot("D:/Github/ICM/Figures/tuned/lambda_decades_median.png",lambda.dec.med.plt,base_width = 30,base_height = 12)
-
-# Doubling Times
-# Reorder the doubling time, either by Species and LME, or the other way around
-dub.time.summary <- dub.time.summary %>%
-                            dplyr::arrange(Species,LME) %>%
-                            dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-dub.heatmap.ne <- ggplot(dub.time.summary %>% dplyr::filter(LME == "NE Atlantic"), aes(x=year, y=Stock.short, fill= prop)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-dub.heatmap.nw <- ggplot(dub.time.summary %>% dplyr::filter(LME == "NW Atlantic"), aes(x=year, y=Stock.short, fill= prop)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-dub.heatmap.pac <- ggplot(dub.time.summary %>% dplyr::filter(LME == "Pacific (Alaska)"), aes(x=year, y=Stock.short, fill= prop)) + xlab("") + ylab("")+
-                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap <- cowplot::plot_grid(dub.heatmap.pac,dub.heatmap.nw,dub.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-dub.heatmap
-
-save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap.png",dub.heatmap,base_width = 20,base_height = 17)
-
-dub.time.6 <- dub.time.6 %>%
-                            dplyr::arrange(LME) %>%
-                            dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-dub.heatmap.cod <- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "G.
-morhua"), aes(x=year, y=Stock.no.species, fill= prop)) + xlab("") + ylab("")+                                     facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + scale_x_continuous(labels=NULL) +
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"))
-
-dub.heatmap.herring<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "C. harengus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-                              xlab("") + ylab("")+                                    
-                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-
-dub.heatmap.haddock<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "M. aeglefinus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-                              xlab("") + ylab("")+                                    
-                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.125, "cm"))
-
-dub.heatmap.virens<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "P. virens"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-                              xlab("") + ylab("")+                                    
-                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.4, "cm"))
-
-dub.heatmap.solea<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "S. solea"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-                              xlab("") + ylab("")+                                    
-                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-
-dub.heatmap.platessa<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "P. platessa"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-                              xlab("") + ylab("")+                                    
-                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous() +
-                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
-
-dub.heatmap.sp6 <- cowplot::plot_grid(dub.heatmap.cod,dub.heatmap.herring,dub.heatmap.haddock,
-                                 dub.heatmap.virens, dub.heatmap.solea,dub.heatmap.platessa,nrow = 6,rel_heights = c(14,9,8,5,5,4))
-dub.heatmap.sp6
-
-save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap_by_sp6.png",dub.heatmap.sp6,base_width = 20,base_height = 17)
-
-# Generation length
-pop.dam <- pop.dam %>% dplyr::arrange(Species,LME) %>%
-                       dplyr::mutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
-
-pop.dam.6 <- pop.dam.6 %>% dplyr::arrange(LME,Area.broad) %>%
-                       dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-gen.boxplt <- ggplot(pop.dam.6) +
-                            geom_boxplot(aes(y=gen.len.opt,x=Stock.no.species))  + 
-                            xlab("") + scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
-                            facet_wrap(~G.Species,scales='free_x')+
-                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',plot.margin = margin(0,0.5,0,0.5, "cm"),
-                                  axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot("D:/Github/ICM/Figures/tuned/GL_boxplot_no_fish_6_species.png",gen.boxplt,base_width = 12,base_height = 10)
-
-gen.heatmap.ne <- ggplot(pop.dam %>% dplyr::filter(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
-                                              xlab("") + ylab("")+  
-                                              facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                              geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-gen.heatmap.nw <- ggplot(pop.dam %>% dplyr::filter(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-gen.heatmap.pac <- ggplot(pop.dam %>% dplyr::filter(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
-                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-gen.heatmap <- cowplot::plot_grid(gen.heatmap.pac,gen.heatmap.nw,gen.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-gen.heatmap
-
-save_plot("D:/Github/ICM/Figures/tuned/gen_heatmap.png",gen.heatmap,base_width = 20,base_height = 17)
-
-# Lifetime reproductive success (no fishing)
-r0.heatmap.ne <- ggplot(pop.dam %>% dplyr::filter(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-r0.heatmap.nw <- ggplot(pop.dam %>% dplyr::filter(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-r0.heatmap.pac <- ggplot(pop.dam %>% dplyr::filter(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                     xlab("") + ylab("")+
-                                     facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                     geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                     theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                           legend.key.width = unit(3,'cm'))
-
-r0.heatmap <- cowplot::plot_grid(r0.heatmap.pac,r0.heatmap.nw,r0.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-r0.heatmap
-
-save_plot("D:/Github/ICM/Figures/tuned/r0_heatmap.png",r0.heatmap,base_width = 20,base_height = 17)
-
-r0.boxplt <- ggplot(pop.dam.6) +
-                            geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
-                            xlab("") + scale_y_log10(name = "Lifetime Reproductive Output")+
-                            facet_wrap(~G.Species,scales = 'free')+
-                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',plot.margin = margin(0,0.5,0,0.5, "cm"),
-                                  axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot("D:/Github/ICM/Figures/tuned/R0_boxplot_no_fish_6_species.png",r0.boxplt,base_width = 12,base_height = 10)
-
-# Other figures....
-
-# windows(11,11)
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
-
-# 
-# r0.ts.plt <- ggplot(pop.dam.6,aes(y=R0.opt,x=cohort,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) + 
-#                             geom_line(size=2)  + geom_point(size=4) +
-#                             scale_y_log10(name = "Lifetime Reproductive Output") +
-#                             facet_wrap(~G.Species) +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-#                             scale_fill_manual(name = "Stock",values = col.try)+
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
-# r0.ts.plt
-# 
-# save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_6.png",r0.ts.plt,base_width = 30,base_height = 12)
-# 
-# r0.boxplt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
-#                             facet_wrap(~G.Species,scales = 'free')+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none')
-# r0.boxplt
-
-# 
-# windows(11,11)
-# ggplot(pop.dam) + geom_boxplot(aes(y=gen.len.opt,x=Species)) + facet_wrap(~LME,scales='free_x') +
-#                   ylab("Generation Length (years)") + theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# windows(11,11)
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# lty <- rep(c(rep(1,5),rep(2,5),rep(4,5)),20)
-# 
-# gen.ts.plt <- ggplot(pop.dam.6,aes(y=gen.len.opt,x=cohort,group=Stock.short,color=Stock.short,linetype = Stock.short)) + 
-#                             geom_line(size=2)  + 
-#                             scale_y_log10(name = "Generation Length") +
-#                             facet_wrap(~G.Species) +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_linetype_manual(name = "Stock",values = lty) +
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
-# gen.ts.plt
-# save_plot("D:/Github/ICM/Figures/tuned/Gen_time_series_6.png",gen.ts.plt,base_width = 20,base_height = 12)
-
-# 
-# ggplot(for.tunes) + geom_jitter(aes(y=lambda,x=Species,group=Stock.short,color=Stock.short)) + 
-#                     scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10)) +
-#                             theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# ggplot(for.tunes) + geom_jitter(aes(y=lambda.vpa.init,x=Species)) + scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))
-# 
-# unique(for.tunes$Species)
-# windows(11,11)
-# 
-# ggplot(for.tunes) + geom_density(aes(lambda,group=Species,color=Species,fill=Species),alpha = 0.2) + scale_x_continuous(breaks = c(0,0.5,1,2,5,10))
-# 
-# 
-# #options(scipen=999)
-# r0.plt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.05,0.1,0.5,1,5,10,50,100),minor_breaks = NULL) + 
-#                             facet_wrap(~Species,scales = 'free')+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1))
-# save_plot("D:/Github/ICM/Figures/tuned/R0_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
-# 
-# 
-# 
-# vickis.cols <- sort(rep(c( "#172582",  "#F8DC91", "#FBB891", "#FB6A01", "#B80000"),3))
-# linetypes <- rep(c(1,2,4),5)
-# 
-# windows(11,11)
-# cod.r0.ts.plt <- ggplot(pop.dam %>% dplyr::filter(Species == 'morhua')) + geom_line(aes(y=R0.opt,x=cohort,group=Area,color=Area,linetype=Area),size=1.5)  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output", breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
-#                             scale_color_manual(values = vickis.cols) +
-#                             scale_linetype_manual(values = linetypes) +
-#                             theme(legend.key.width  = unit(2, "cm"))
-# cod.r0.ts.plt
-# #save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
-# 
-# 
-# windows(11,11)
-# ggplot(pop.dam %>% dplyr::filter(Species =="morhua")) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
-#                                                         scale_y_log10(name = "Lifetime Reproductive Output",breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) +
-#                                                         theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# # Missing catch questions
-# # first did we do much to the Fecundity term to get here
-# quantile(for.tunes$mean.fec/for.tunes$mean.vpa.fec,probs=seq(0.01,1,0.01),na.rm=T)
-# 
-# quantile((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init,probs=seq(0.01,1,0.01),na.rm=T)
-# quantile((for.tunes$mean.nm-for.tunes$mean.vpa.nm)/for.tunes$mean.vpa.nm,probs=seq(0.01,1,0.01),na.rm=T)
-# 
-# for.tunes$excess.catch <- for.tunes$removals-for.tunes$removals.init
-# for.tunes$per.excess.catch <- 100*((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init)
-# 
-# windows(11,11)
-# bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Species)) + 
-#                                    ylab("Adjustment to catch (%)") +
-#                                    theme(axis.text.x = element_text(angle=45,hjust = 1))
-#                                    
-# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_species.png",bycatch.plt,base_width = 8,base_height = 8)
-#                                    
-# bycatch.plt.cod <- ggplot(for.tunes %>% dplyr::filter(Species == 'morhua')) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + 
-#                                                                               ylab("Adjustment to catch (%)") +
-#                                                                               theme(axis.text.x = element_text(angle=45,hjust = 1))
-#                                                                               
-# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_cod_stock.png",bycatch.plt.cod,base_width = 8,base_height = 8)
-# 
-# # bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + facet_wrap(~Species,scales = 'free_x')
-# #                                    ylab("Adjustment to catch (%)") +
-# #                                    theme(axis.text.x = element_text(angle=45,hjust = 1))
-# # bycatch.plt                                   
-#

### 2024-04-16 Drafts/Paper_1/index.Rmd
Update with age and no age correction
Revised to run the model without using the age-correction (i.e., model without going to age 0, which should work fine since fecundity of anything smaller than recruits is effectively 0 for basically all the stocks).  Results very similar to the 'age corrected' analysis.  A few minor bug fixes as well.  Also have part of the methods written.

--- 2024-04-16 Drafts/Paper_1/Paper_1_frist_draft.Rmd
@@
 ---
-title: "ICM testing"
+title: |
+   "Observed life history characteristics of harvested marine species"
+french_title: "Titre ici (*Nom latin de l'espèce*)"
+author: |
+  David. M. Keith^1^ 
+  Freya M. Keyser^1^
+  Julie M. Charbonneau^2^
+  Heather 'The Boss' Bowlby^1^
+author_list: "Keith, D.M., Keyser, F.M., Charbonneau, J.M., Bowlby, H.T.B."
+address: |
+  ^1^Bedford Institute of Oceanography\
+     Fisheries and Oceans Canada, 1 Challenger Dr.\
+     Dartmouth, Nova Scotia, B2Y 4A2 , Canada\
+  \smallskip
+  ^2^Simon Fraser University\
+     Department of Biology\
+french_address: |
+
+month: ""
+french_month: ""
+year: 2024
+report_number: nnn
+region: "Maritimes Region"
+french_region: "Maritimes Region"
+isbn: ""
+cat_no: ""
+citation_other_language: ""
+
+abstract: |
+  Here is the abstract text.
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+  Start new paragraphs after a blank line and with 2 spaces indent.
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+french_abstract: |
+
+header: "Draft working paper --- Do not cite or circulate" # or "" to omit
 output:
-  #pdf_document: default
-  #html_document: default
-  word_document: 
-    #reference_docx: template.docx
-editor_options:
-  chunk_output_type: console
+ csasdown::resdoc_word:
+   french: false
+   copy_sty: true
+   line_nums: true
+   line_nums_mod: 1
+   lot_lof: false
+   draft_watermark: false
+   include_section_nums: true
+   highlight: tango
+# ------------
+# End of options to set
+knit: (function(input, ...) {
+       csasdown::render('_bookdown.yml')
+      })
+link-citations: true
+bibliography: Y:/Zotero/MAR_SABHU.bib
+# Any extra LaTeX code for the header:
+# header-includes:
+# - \usepackage{tikz}
 ---
 
-The data is now available to test this on at least 81 stocks.
-All of the NE Atlantic stocks (ICES) have been through the QA/QC process and we are happy with those data (Sept 1, 2022).
-Let's see if we can get this to work on all the stocks with sufficient data...
+```{r setup, echo=FALSE, cache=FALSE, message=FALSE, results='hide', warning=FALSE}
+library(knitr)
+if (is_latex_output()) {
+  knitr_figs_dir <- "knitr-figs-pdf/"
+  knitr_cache_dir <- "knitr-cache-pdf/"
+  fig_out_type <- "png"
+} else {
+  knitr_figs_dir <- "knitr-figs-docx/"
+  knitr_cache_dir <- "knitr-cache-docx/"
+  fig_out_type <- "png"
+}
+fig_asp <- 0.618
+fig_width <- 9
+fig_out_width <- "6in"
+fig_dpi <- 180
+fig_align <- "center"
+fig_pos <- "htb"
+opts_chunk$set(
+  collapse = TRUE,
+  warning = FALSE,
+  message = FALSE,
+  comment = "#>",
+  fig.path = knitr_figs_dir,
+  cache.path = knitr_cache_dir,
+  fig.asp = fig_asp,
+  fig.width = fig_width,
+  out.width = fig_out_width,
+  echo = FALSE,
+  #  autodep = TRUE,
+  #  cache = TRUE,
+  cache.comments = FALSE,
+  dev = fig_out_type,
+  dpi = fig_dpi,
+  fig.align = fig_align,
+  fig.pos = fig_pos
+)
+```
 
-```{r, load-stuff,echo=F, message=F, warning=F, fig.width=6, fig.height=4,include=F}
+```{r load-libraries-n-data, echo = FALSE, cache = FALSE, message = FALSE, results = 'hide', warning = FALSE}
+# add other packages here:
+library(dplyr)
+library(readr)
+library(tibble)
+library(csasdown)
 # OK, so using the ICES assessments here's what we get for North Sea cod.
@@
 # If we already have the results don't re-run the models or load data we don't need.
-load.results <- T
+load.results <- F
 # What tunning model are you running or did you run!

### 2024-04-16 Scripts/functions/simple_Lotka_r.r

@@ -37,7 +37,7 @@ simple.lotka.r<-function(yrs = 1,mort = NULL,fecund = NULL,ages = NULL)
     #browser()
     if(!is.null(nrow(fecund))) mx <- fecund[j,] else mx <- fecund
     # Now we are cooking!
-    junk<-optimize(lower=-0.99,upper=5,f = eulerlotka)
+    junk<-optimize(lower=-15,upper=15,f = eulerlotka)
     #browser()
     res[j,] <- c(yrs[j],junk$minimum)
     mx.tmp[[j]] <- mx

### 2024-04-16 Scripts/functions/tuning_sim_fast.r

@@ -4,7 +4,8 @@
 # All the data you need to make it dance...
 # years:          The years you are running the backwards calculation for
 # step.size:      How big is the difference (proportional) in the simulation step.  Default = 0.05 which is about a 5% change for each step
-# tuner:          What are we tuning, the fecundity "f", or natural mortality 'm', or both 'b'
+# tuner:          What are we tuning, options are 'fecund' for fecundity, 'fec_nm' for fecundity and natural mortality, 'z' for natural mortality and 
+#                 fishing mortality, 'nm' for natural mortality, 
 # direction       Allow for forwards and backwards simulations
 # ages:           The age classes of your population
 # nm:             Natural mortality, this wants the instantaneous natural mortality, not the proportional. Should be a matrix the rows are different years
@@ -112,6 +113,24 @@ fast.tunes<-function(years,step.size=0.05,tuner="m",  direction = 'backwards',ag
     # Pull out the estimate from this
     #browser()
     r.est = lotka.est$res$r
+    # If the r.est is bonkers, we reduce fecundity until it isn't
+    while(r.est > 10) 
+    {
+      # if the lotka isn't converging set the age class fecundity to be 90% of what we had if tuning on fecundity
+      if(tuner %in% c("fecund","fec_nm")) fecund.tmp <- 0.9*fecund.tmp 
+      # if tuning on natural mortality increase that by 10%
+      if(tuner %in% c("nm","fec_nm",'z')) nm.tmp <- nm.tmp*1.1
+      # if tuning on z, increase fishing mortality by 10% too.
+      if(tuner == "z") fm.tmp <- fm.tmp*1.1
+      # If chaning nm or fm then we need a new z.tmp object that accounts for that
+      if(tuner != 'fecund') z.tmp <- nm.tmp + fm.tmp
+      
+      lotka.est <- simple.lotka.r(mort = z.tmp,fecund=fecund.tmp,ages=ages)
+      # Pull out the estimate from this
+      #browser()
+      r.est = lotka.est$res$r
+      print("lotka wasn't converging, we pre-tuned the tuner variables in steps of 10% until lotka converged")
+    }
  
     # If going backwards we do the back.projection
     if(direction == 'backwards')
@@ -154,7 +173,8 @@ fast.tunes<-function(years,step.size=0.05,tuner="m",  direction = 'backwards',ag
     # So as long as these three things are TRUE we are in this while. This while is the 'it's a big difference' while
     while(get.better && big.diff &&  not.close.enough) 
[…]

### 2024-04-25 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
I haven't updated in a while update
Working on Methods, Results, Discussion. Doing one last big run on the doubling time estimates.  Miles to go...

@@
 {
-  Stocks <- ASR_long %>%
-                      dplyr::filter(!is.na(value)) %>%
-                      dplyr::group_by(Stock, type) %>%
-                      dplyr::summarize(count=length(unique(value))) %>%
-                      dplyr::group_by(Stock) %>%
-                      dplyr::summarize(types=length(unique(type))) %>%
-                      dplyr::filter(types==5) %>%
-                      dplyr::select(Stock)
-
-  ASR_stocks <- ASR_long %>%
-                          dplyr::filter(Stock %in% Stocks$Stock) %>%
-                          dplyr::filter(!is.na(value)) %>%
-                          dplyr::arrange(Stock, Year, type, as.numeric(age))
+  Stocks <- ASR.long |> 
+                      collapse::fsubset(!is.na(value)) |>
+                      collapse::fgroup_by(Stock, type) |>
+                      collapse::fsummarize(count=length(unique(value))) |>
+                      collapse::fgroup_by(Stock) |>
+                      collapse::fsummarize(types=length(unique(type))) |>
+                      collapse::fsubset(types==5) |>
+                      collapse::fselect(Stock)
+
+  ASR.tmp <- ASR.long 
+  ASR.tmp$age <- as.numeric(ASR.tmp$age)
+  ASR.stocks <- ASR.tmp |> 
+                          collapse::fsubset(Stock %in% Stocks$Stock) |>
+                          collapse::fsubset(!is.na(value)) |>
+                          collapse::roworder(Stock, Year, type, age)
 
@@
   am.tmp <- NULL
-  mr.tmp <- NULL
+  #mr.tmp <- NULL
   abund.tmp <- NULL
@@
   print(i)
-  ASR_sub <- ASR_long %>%
-    dplyr::select(Year, Stock, type, age, value) %>%
-    dplyr::filter(Stock==i)
+  ASR.sub <- ASR.long |>
+    collapse::fselect(Year, Stock, type, age, value) |>
+    collapse::fsubset(Stock==i)
 
     # Dropping the first 7 years as the 8 year olds are all missing
-  if(i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR_sub <- ASR_sub |> collapse::fsubset(Year >= 1972)
-  # maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]))
-  # maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)])
-  # minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)])
-  # forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
+  if(i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR.sub <- ASR.sub |> collapse::fsubset(Year >= 1972)
+  # maxage <- max(as.numeric(ASR.sub$age[!is.na(ASR.sub$value)]))
+  # maxYear <- max(ASR.sub$Year[!is.na(ASR.sub$value)])
+  # minYear <- min(ASR.sub$Year[!is.na(ASR.sub$value)])
+  # forplot <- ASR.sub[as.numeric(ASR.sub$age) < (maxage+1) & ASR.sub$Year %in% minYear:maxYear,]
   # 
@@
 
-  age.mat <- ASR_sub %>% dplyr::filter(type=="AM") %>% dplyr::rename(AM=value) %>% dplyr::select(-type)
+  age.mat <- ASR.sub |> collapse::fsubset(type=="AM") |> dplyr::rename(AM=value) |> collapse::fselect(-type)
   # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
@@
   #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
-  nat.mort <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
-  abund <- ASR_sub %>% dplyr::filter(type=="Num") %>% dplyr::rename(Num=value) %>% dplyr::select(-type)
-  weight.age <- ASR_sub %>% dplyr::filter(type=="WA") %>% dplyr::rename(WA=value) %>% dplyr::select(-type)
+  nat.mort <-  ASR.sub |> collapse::fsubset(type=="NM") |> dplyr::rename(NM=value) |> collapse::fselect(-type)
+  abund <- ASR.sub |> collapse::fsubset(type=="Num") |> dplyr::rename(Num=value) |> collapse::fselect(-type)
+  weight.age <- ASR.sub |> collapse::fsubset(type=="WA") |> dplyr::rename(WA=value) |> collapse::fselect(-type)
   if(i == Stocks[30]) weight.age$WA <- weight.age$WA/1000
-  removals <- ASR_sub %>% dplyr::filter(type=="Catch") %>% dplyr::rename(Catch=value) %>% dplyr::select(-type)
+  removals <- ASR.sub |> collapse::fsubset(type=="Catch") |> dplyr::rename(Catch=value) |> collapse::fselect(-type)
 
@@
 
-  data <- age.mat %>%
-    full_join(nat.mort) %>%
-    full_join(abund) %>%
-    full_join(weight.age) %>%
+  data <- age.mat |>
+    full_join(nat.mort) |>
+    full_join(abund) |>
+    full_join(weight.age) |>
     full_join(removals)
@@
 
-  rem <- data %>% dplyr::group_by(Year,.drop=F) %>% dplyr::summarize(rem=sum(Catch,na.rm=T)) #%>% dplyr::pull(rem)
-
-  missing_rem<- NULL
-  if(any(is.na(rem$rem))) 
-  {
-    missing_rem <- unique(data$Year)[which(is.na(rem$rem))]
-    rem$rem[is.na(rem$rem)] <- median(rem$rem, na.rm=T)
-  }
+  rem <- data |> collapse::fgroup_by(Year) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
+  #rem <- data |> dplyr::group_by(Year,.drop=F) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
+
+  # Never run, so not doing anything.
+  # missing_rem<- NULL
+  # if(any(is.na(rem$rem))) 
+  # {
+  #   missing_rem <- unique(data$Year)[which(is.na(rem$rem))]
+  #   rem$rem[is.na(rem$rem)] <- median(rem$rem, na.rm=T)
+  # }
 
   #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
-  years <- data %>% dplyr::pull(Year) %>% unique() %>% sort()
+  years <- data |> dplyr::pull(Year) |> unique() |> sort()
 
   N.end <- sum(data[data$Year==max(years),]$Num)
-  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
+  vpa.abund <- data |> dplyr::group_by(Year) |> dplyr::summarize(vpa=sum(Num,na.rm=T)) |> pull(vpa)
 
@@
   #tot.ssb
-  annual <- data %>% group_by(Year) %>% summarize(tot.ssb = sum(ssb)) %>% left_join(annual)
-
-  #tst <- data %>% group_by(Year) %>% summarize(tot.ssn = sum(ssn)) %>% left_join(annual)
-
-  #r.p.ssb This needs to be offset by the age of recruits
-  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+1):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage)])
+  annual <- data |> group_by(Year) |> summarize(tot.ssb = sum(ssb)) |> left_join(annual)
+
+  #tst <- data |> group_by(Year) |> summarize(tot.ssn = sum(ssn)) |> left_join(annual)
+
+  #r.p.ssb This needs to be offset by the age of recruits. So here's my lining this up logic.  For age 0, we get
+  # the recruit and SSB estimates from the same survey, thus these age 0 recruits will have been produced by the SSB in the previous year...
+  # So the R in 1970 were produced by SSB in 1969 when min age =0
+  # If min.age = 1 then R in 1970 is produced by SSB in 1968... and so on.
+  # FIX 1 "Recruit year" = SSB year + min.age + 1 (or min.age +2 as SSB.year is the first column)
+  # Now for RPS there's another wrinkle because of this, because our model is N(1970) = lambda * N(1969) and lambda is made up of lx and mx
+  # so if the recruits show up in 1970, the fecundity term that gets us there (irrespective of the age offset) has to be for 1969, becuase
+  # that gets us to the babies that show up in 1970
+  # FIX 2 So "RPS year, recs.per.age year, and mx year" = SSB year + min.age
+  # I believe this to be correct, but we all need to discuss this to make sure the logic holds.
+  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+2):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage-1)],NA)
   # recs.per.age
@@
   {
-    tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
-    tst$Year <- tst$Year + minage
+    tst <- data|> collapse::fsubset(Year == years[j]) |> collapse::fselect(ssb,ssn,Year,age)
+    tst$Year <- tst$Year + minage # We want this to line up the the RPS year, so just adding minage here.
     names(tst) <- c("ssb.offset","ssn.offset","Year","age")
@@
   # Easier to remove the years where we don't have recs.per.age...
-  #data <- data %>% dplyr::filter(Year %in% years[(minage+1):length(years)])
+  #data <- data |> collapse::fsubset(Year %in% years[(minage+1):length(years)])
   # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...
 
-  age.mat <- data %>% dplyr::select("Year", "age", "AM") %>% pivot_wider(names_from=age, values_from = AM) %>% dplyr::select(-Year)
-  prop.nat.mort <- data %>% dplyr::select("Year", "age", "prop.nat.mort") %>% 
-                            pivot_wider(names_from=age, values_from = prop.nat.mort) %>% 
-                            dplyr::select(-Year) %>% as.data.frame
-
-  weight.age <- data %>% dplyr::select("Year", "age", "WA") %>% pivot_wider(names_from=age, values_from = WA) %>% dplyr::select(-Year)
-  mx <- data %>% dplyr::select("Year", "age", "mx") %>% 
-                 pivot_wider(names_from=age, values_from = mx) %>% 
-                 dplyr::select(-Year) %>% as.data.frame()
+  age.mat <- data |> collapse::fselect("Year", "age", "AM") |> 
+                     pivot_wider(names_from=age, values_from = AM) |> collapse::fselect(-Year)
+  prop.nat.mort <- data |> collapse::fselect("Year", "age", "prop.nat.mort") |> 
+                            pivot_wider(names_from=age, values_from = prop.nat.mort) |> 
+                            collapse::fselect(-Year) |> as.data.frame()
+
+  weight.age <- data |> collapse::fselect("Year", "age", "WA") |> pivot_wider(names_from=age, values_from = WA) |> collapse::fselect(-Year)
+  mx <- data |> collapse::fselect("Year", "age", "mx") |> 
+                 pivot_wider(names_from=age, values_from = mx) |> 
+                 collapse::fselect(-Year) |> as.data.frame()
   # Get the abundance matrix
-  abund.age <- data %>% dplyr::select("Year", "age", "Num") %>% 
-                        pivot_wider(names_from=age, values_from = Num) %>% 
-                        dplyr::select(-Year) %>% as.data.frame()
+  abund.age <- data |> collapse::fselect("Year", "age", "Num") |> 
+                        pivot_wider(names_from=age, values_from = Num) |> 
+                        collapse::fselect(-Year) |> as.data.frame()
 
@@
 
-  full.rems <- data %>% dplyr::select("Year", "age", "Catch") %>% pivot_wider(names_from=age, values_from = Catch) %>% dplyr::select(-Year)
-  full.Fs <-  data %>% dplyr::select("Year", "age", "Fs") %>% pivot_wider(names_from=age, values_from = Fs) %>% dplyr::select(-Year)
+  full.rems <- data |> collapse::fselect("Year", "age", "Catch") |> pivot_wider(names_from=age, values_from = Catch) |> collapse::fselect(-Year)
+  full.Fs <-  data |> collapse::fselect("Year", "age", "Fs") |> pivot_wider(names_from=age, values_from = Fs) |> collapse::fselect(-Year)
 
@@
 
-  # For the years of mx without SSB info to inform them
-  if(minage >0 ) 
-  {
-    mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
-    names(mx) <- names(mx.fill)
-   # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
-    mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
+  # I had filled the years with no SSB data to inform them.  instead I'm going to remove those years...
+
+   if(minage >0) 
+  {
+    rm <- -(1:minage)
+    years <- years[rm]
+    prop.nat.mort <- prop.nat.mort[rm,]
+    weight.age <- weight.age[rm,]
+    rem <- rem[rm,]
+    mx <- mx[rm,]
+    vpa.abund <- vpa.abund[rm]
+    age.mat <- age.mat[rm,]
+    abund.age <- abund.age[rm,]
+    full.Fs <- full.Fs[rm,]
+    full.rems <- full.rems[rm,]
    }
+  #   mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
+  #   names(mx) <- names(mx.fill)
+  #  # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
+  #   mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
+  # }
 
@@
     am.tmp[[i]] <- age.mat
-    mr.tmp[[i]] <- missing_rem
+    #mr.tmp[[i]] <- missing_rem
     abund.tmp[[i]] <- abund.age
@@
   save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,
-       am.tmp,Stocks,ASR_stocks,ASR_long,abund.tmp,fs.tmp,full.rem.tmp,
+       am.tmp,Stocks,ASR.stocks,ASR.long,abund.tmp,fs.tmp,full.rem.tmp,
        file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
@@
     #Pick your step size
-    ss.size <- 0.01
+    ss.size <- 0.005
     sensistive.stocks <- c("AFSC_GOA_Theragra_chalcogramma",
@@
                             "NEFSC-GARMIII_MA_Paralichthys_dentatus",
-                            "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus")
+                            "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus",
+                            "NEFSC_NWA_Scomber _scombrus")
 
@@
      for.tune.summary[[i]] <- for.tune.tmp
-
   }
@@
   #  A quick way to get the other potentially interesting info for the stock...
-  drop <- which(names(ASR_long) %in% c("Year","type","age","value"))
+  drop <- which(names(ASR.long) %in% c("Year","type","age","value"))
   meta <- NULL
@@
   {
-    meta[[i]] <- ASR_long[ASR_long$Stock == i,-drop][1,]
+    meta[[i]] <- ASR.long[ASR.long$Stock == i,-drop][1,]
     meta[[i]]$age.min <- min(ages.tmp[[i]])
@@
   dt.res <- NULL
-  n.dt.sims <- 2000 # Number of simulations...
+  n.dt.sims <- 1000 # Increase to 1000 for final run, which takes like a full day or something 
   n.years <- 100
@@
   {
-    try <- for.tunes %>% dplyr::filter(Stock == i)
-    meta.tmp <- meta.sub %>% dplyr::filter(Stock == i)
+    str.time <- Sys.time()
+    try <- for.tune.all[[i]]
+    meta.tmp <- try$meta
+    age.4.sim <- meta.tmp$age.min:meta.tmp$age.max
     double.time <- NA
@@
   {
+
     tmp <- rep(0,n.years)
-
     for(y in 2:n.years)
     {
-      lambda <- sample(na.omit(try$lambda),size=1)
-      pop[y] <- lambda*pop[y-1]
+
+      # Get our sample for this run
+      f.pick <- sample(nrow(try$fecund.opt),size=1)
+      nm.pick <- sample(nrow(try$nm.opt),size=1)
+      fec.samp <- try$fecund.opt[f.pick,]
+      # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
+      nm.samp <- try$nm.opt[nm.pick,] 
+      # now put these into Euler-lotka to get an r estimate
+      res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
+      r.val <- res$res$r
+      # If r is > 5 (lambda = exp(5)) it generally means the simple.lotka didn't converge (bad combo of fec and nm)
+      # So we'll need to resample them until it is < 5
+      while(r.val >= 5)
+      {
+        print("Resampling due to bat shit r value")
+        f.pick <- sample(nrow(try$fecund.opt),size=1)
+        nm.pick <- sample(nrow(try$nm.opt),size=1)
+        fec.samp <- try$fecund.opt[f.pick,]
+        # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
+        nm.samp <- try$nm.opt[nm.pick,] 
+        # now put these into Euler-lotka to get an r estimate
+        res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
+        r.val <- res$res$r
+      } # end while loop
+      pop[y] <- exp(r.val)*pop[y-1]
       if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.years] <- 1
     } # end the years loop
-    tmp.res[[s]] <- data.frame(year =1:100,doubled = tmp,sim=s)
+    tmp.res[[s]] <- data.frame(year =1:n.years,doubled = tmp,sim=s)
+
     } # end sim loop
@@
   dt.res[[i]] <- data.frame(res.tmp,meta.tmp)
-
+  count <- 0
+  print(paste0("Stock ",i," Sim ", s," time =", round(Sys.time()-str.time,digits=1)," minutes Stock number",count+1))
   } # end Stocks loop
@@
 
-  dub.time.summary <- dub.time %>% dplyr::group_by(Stock,year)  %>% dplyr::summarise(prop = sum(doubled)/n.dt.sims)
+  dub.time.summary <- dub.time |> collapse::fgroup_by(Stock,year)  |> collapse::fsummarise(prop = sum(doubled)/n.dt.sims)
   dub.time.summary <- left_join(dub.time.summary,meta.sub,by="Stock")
@@
   # Do a years loop to get lambda with no fishing for each year, rather than by cohort...
-    for(yy in 1:n.years)
+    for(yy in 1:(n.years-1))
     {
@@
 
-  pop.dam <- res.cohort.final %>% dplyr::group_by(cohort,Stock) %>% dplyr::summarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
+  pop.dam <- res.cohort.final |> dplyr::group_by(cohort,Stock) |> dplyr::summarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
                                                                   gen.len.org = sum(x.mx.lx.org)/sum(mx.lx.org),
@@
 load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
-pop.dam <- data.frame(pop.dam)
+res.lambda.fin <- data.frame(res.lambda.final)
+
 six.species <- c('morhua','harengus','aeglefinus','virens','solea','platessa')
-pop.dam.6 <- pop.dam %>% dplyr::filter(Species %in% six.species)
-for.tunes.6 <- for.tunes %>% dplyr::filter(Species %in% six.species)
-dub.time.6 <- dub.time.summary %>% dplyr::filter(Species %in% six.species)
-res.lambda.final$decade <- floor(res.lambda.final$year/10)*10
-res.lambda.final <- res.lambda.final %>% dplyr::group_by(Stock,decade) %>% dplyr::mutate(mn.lam = mean(lam.fish,na.rm=T),
+pop.dam.6 <- pop.dam |> collapse::fsubset(Species %in% six.species)
+for.tunes.6 <- for.tunes |> collapse::fsubset(Species %in% six.species)
+dub.time.6 <- dub.time.summary |> collapse::fsubset(Species %in% six.species)
+res.lambda.fin$decade <- floor(res.lambda.fin$year/10)*10
+res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock,decade) |> collapse::fmutate(mn.lam = mean(lam.fish,na.rm=T),
                                                                                  med.lam = median(lam.fish,na.rm=T),
                                                                                  sd.lam = sd(lam.fish,na.rm=T))
-res.lambda.final <- res.lambda.final %>% dplyr::group_by(Species,decade) %>% dplyr::mutate(lm.spec.mn = mean(mn.lam,na.rm=T))              
-res.lambda.final <- res.lambda.final %>% dplyr::group_by(Stock) %>% 
-                                            dplyr::mutate(lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
+res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Species,decade) |> collapse::fmutate(lm.spec.mn = mean(mn.lam,na.rm=T))              
+res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock) |> 
+                                                          collapse::fmutate(lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
                                                           lam.fish.mn = mean(lam.fish,na.rm=T),
@@
                                                           lam.org.no.fish.med = median(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T),) %>% data.frame()
-
-res.lambda.final.6 <- res.lambda.final %>% dplyr::filter(Species %in% six.species)
+                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T)) |> data.frame()
+
+res.lambda.final.6 <- res.lambda.fin |> collapse::fsubset(Species %in% six.species)
 # Sort the data into a nice order...
-res.lambda.final <- res.lambda.final %>% dplyr::arrange(Species,Area.broad) %>%
-                                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(Species,Area.broad) %>%
-                                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-dub.time <- dub.time %>% dplyr::arrange(LME) %>%
-                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-dub.time.summary <- dub.time.summary %>% dplyr::arrange(LME,Order,Species,Area.broad) %>%
-                                         dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-dub.time.6 <- dub.time.6 %>% dplyr::arrange(LME) %>%
-                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-pop.dam <- pop.dam %>% dplyr::arrange(Species,LME) %>%
-                       dplyr::mutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
-pop.dam.6 <- pop.dam.6 %>% dplyr::arrange(LME,Area.broad) %>%
-                       dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-# res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(LME,Area.broad) %>%
-#                                              dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+res.lambda.fin <- res.lambda.fin |> collapse::roworder(Species,Area.broad) |>
+                                    collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+res.lambda.final.6 <- res.lambda.final.6 |> collapse::roworder(Species,Area.broad) |>
+                                            collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+dub.time <- dub.time |> collapse::roworder(LME) |>
+                        collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+
+dub.time.summary <- dub.time.summary |> collapse::roworder(LME,Order,Species,Area.broad) |>
+                                        collapse::fmutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
+
+dub.time.6 <- dub.time.6 |> collapse::roworder(LME) |>
+                             collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+pop.dam <- pop.dam |> collapse::roworder(Species,LME) |>
+                       collapse::fmutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
+pop.dam.6 <- pop.dam.6 |> collapse::roworder(LME,Area.broad) |>
+                       collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+
+# res.lambda.final.6 <- res.lambda.final.6 |> collapse::roworder(LME,Area.broad) |>
+#                                              collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
 
@@
 #hmm <- merge(tst,res.lambda.final.6,by="Stock")
-# Note the LIMITS I PUT ON THESE BECAUSE 4 STOCKS WERE SHITTY
-plot(res.lambda.final$lam.fish.med ~ res.lambda.final$lam.fish.mn)
+plot(res.lambda.fin$lam.fish.med ~ res.lambda.fin$lam.fish.mn)
 # So this is lambda with fishing included
@@
                                            geom_point(aes(y=lam.no.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-                                           xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10)) + 
+                                           xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
                                            geom_hline(yintercept = 1,linetype='dashed') +
@@
                                            geom_point(aes(y=lam.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-                                           xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,5)) + 
+                                           xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
                                            geom_hline(yintercept = 1,linetype='dashed') +
@@
 
-dub.heatmap.cod <- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "G.
+dub.heatmap.cod <- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "G.
 morhua"), aes(x=year, y=Stock.no.species, fill= prop)) + xlab("") + ylab("")+                                     facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") +
@@
 
-dub.heatmap.herring<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "C. harengus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+dub.heatmap.herring<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "C. harengus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
                               xlab("") + ylab("")+                                    
@@
 
-dub.heatmap.haddock<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "M. aeglefinus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+dub.heatmap.haddock<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "M. aeglefinus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
                               xlab("") + ylab("")+                                    
@@
 
-dub.heatmap.virens<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "P. virens"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+dub.heatmap.virens<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. virens"), aes(x=year, y=Stock.no.species, fill= prop)) + 
                               xlab("") + ylab("")+                                    
@@
 
-dub.heatmap.solea<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "S. solea"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+dub.heatmap.solea<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "S. solea"), aes(x=year, y=Stock.no.species, fill= prop)) + 
                               xlab("") + ylab("")+                                    
@@
 
-dub.heatmap.platessa<- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "P. platessa"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+dub.heatmap.platessa<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. platessa"), aes(x=year, y=Stock.no.species, fill= prop)) + 
                               xlab("") + ylab("")+                                    
@@
 
-dub.time.summary <- dub.time.summary %>%
-                            dplyr::arrange(G.Species,LME,Area.broad) %>%
-                            dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-dub.heatmap.gad <- ggplot(dub.time.summary %>% dplyr::filter(Order == "Gadiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
+dub.time.summary <- dub.time.summary |>
+                            collapse::roworder(G.Species,LME,Area.broad) |>
+                            collapse::fmutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
+
+dub.heatmap.gad <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Gadiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
                             xlab("") + ylab("")+                                    
@@
 
-dub.heatmap.pl <- ggplot(dub.time.summary %>% dplyr::filter(Order == "Pleuronectiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
+dub.heatmap.pl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Pleuronectiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
                             xlab("") + ylab("")+                                    
@@
 
-dub.heatmap.cl <- ggplot(dub.time.summary %>% dplyr::filter(Order == "Clupeiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
+dub.heatmap.cl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Clupeiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
                             xlab("") + ylab("")+
@@
 
-dub.heatmap.per <- ggplot(dub.time.summary %>% dplyr::filter(Order == "Perciformes"), aes(x=year, y=Stock.short, fill= prop)) + 
+dub.heatmap.per <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Perciformes"), aes(x=year, y=Stock.short, fill= prop)) + 
                             xlab("") + ylab("")+
@@
 
-dub.heatmap.scom <- ggplot(dub.time.summary %>% dplyr::filter(Order == "Scombriformes"), aes(x=year, y=Stock.short, fill= prop)) + 
+dub.heatmap.scom <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Scombriformes"), aes(x=year, y=Stock.short, fill= prop)) + 
                             xlab("") + ylab("")+
@@
 
-dub.heatmap.scorp <- ggplot(dub.time.summary %>% dplyr::filter(Order %in% "Scorpaeniformes "), aes(x=year, y=Stock.short, fill= prop)) + 
+dub.heatmap.scorp <- ggplot(dub.time.summary |> collapse::fsubset(Order %in% "Scorpaeniformes "), aes(x=year, y=Stock.short, fill= prop)) + 
                             xlab("") + ylab("")+
@@
 
-gen.heatmap.ne <- ggplot(pop.dam %>% dplyr::filter(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
+gen.heatmap.ne <- ggplot(pop.dam |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
                                               xlab("") + ylab("")+  
@@
 
-gen.heatmap.nw <- ggplot(pop.dam %>% dplyr::filter(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+gen.heatmap.nw <- ggplot(pop.dam |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
                             geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
@@
 
-gen.heatmap.pac <- ggplot(pop.dam %>% dplyr::filter(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
+gen.heatmap.pac <- ggplot(pop.dam |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
                             facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
@@
 
-r0.heatmap.ne <- ggplot(pop.dam %>% dplyr::filter(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
+r0.heatmap.ne <- ggplot(pop.dam |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
                                     xlab("") + ylab("")+
@@
 
-r0.heatmap.nw <- ggplot(pop.dam %>% dplyr::filter(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
+r0.heatmap.nw <- ggplot(pop.dam |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
                                     xlab("") + ylab("")+
@@
 
-r0.heatmap.pac <- ggplot(pop.dam %>% dplyr::filter(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
+r0.heatmap.pac <- ggplot(pop.dam |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
                                      xlab("") + ylab("")+
@@
 
+# FIX: A density dependence figure, this isn't perfect as the lambda's aren't quiet lined up right because of recruitment offset
+# That said, recruitment in these cases also integrates all processes that happens from birth-recruitment
+# So maybe it is kinda reasonable?
+#
+
+# First need to get the abundance and lambdas with no fishing into one object.
+ft.tmp <- for.tunes |> collapse::fselect(year,Stock,vpa.abund,est.abund)
+dd.dat <- left_join(res.lambda.fin,ft.tmp,by=c('year','Stock'))
+# Now I need to get a relative abundance for each stock...
+dd.dat <- dd.dat |> collapse::fgroup_by(Stock) |> collapse::fmutate(max.abund = max(est.abund,na.rm=T))
+dd.dat <- data.frame(dd.dat)
+dd.dat$prop.abund <- dd.dat$est.abund/dd.dat$max.abund
+dd.dat.six <- dd.dat |>collapse::fsubset(Species %in% six.species)
+
+ggplot(dd.dat) + geom_point(aes(x=prop.abund,y=lam.no.fish-1)) + xlab("Proportion of Maximum Abundance") + ylab("r (no fishing)")
+
+# Density dependence by Species
+ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
+                                                   geom_smooth(method="gam") + 
+                                                   geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
+                                                   scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
+                                                   scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) #+
+                                                   #scale_color_manual(values = colrs)
+# Density dependence by stock
+ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Stock.short,group=Stock.short)) + geom_point() + 
+                                                   geom_smooth(method="lm",se = F) + 
+                                                   geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
+                                                   scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
+                                                   scale_y_log10(name = "lambda (no fishing)", limits=c(0.4,2),
+                                                                 breaks = seq(0.4,2,by=0.1)) +
+                                                   theme(legend.position = 'none')
+
+dd.dat.no.bigs <- dd.dat |> collapse::fsubset(lam.no.fish < 2)
+
+ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish)) + geom_point() + 
+                                                    geom_smooth(method="gam") + 
+                                                   geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
+                                                   scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
+                                                   scale_y_continuous(name = "lambda (no fishing)")
+
+ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + geom_point() + 
+                                                    geom_smooth(method="lm",se=F) + 
+                                                   geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
+                                                   scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,2,by=0.1))+
+                                                   scale_y_log10(name = "lambda (no fishing)")
+
+# how about our big 6
+colrs <- c("blue","black","firebrick2","orange",'grey50','grey90')
+ggplot(dd.dat.six,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
+                                                    geom_smooth(method="gam") + 
+                                                   geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
+                                                   scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
+                                                   scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) +
+                                                   scale_color_manual(values = colrs)
+
+dd.dat.six.no.bigs <- dd.dat.six |> collapse::fsubset(lam.no.fish < 2)
+
+ggplot(dd.dat.six.no.bigs,aes(x=prop.abund,y=lam.no.fish-1,color=Species,group=Species)) + geom_point() + 
+                                                    geom_smooth(method="gam") + 
+                                                   geom_hline(yintercept = 0,linewidth=2,linetype='dashed',color='blue') +
+                                                   scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
+                                                   scale_y_continuous(name = "r (no fishing)", breaks = seq(-1,1,by=0.2)) +
+                                                   scale_color_manual(values = colrs)
+
+just.bigs <- dd.dat  |> collapse::fsubset(lam.no.fish > 2) 
+sum(table(just.bigs$Stock.short)) # 48 of 68 are Haddock or cod. 13 of remaining 20 are small low trophic species
+
+dd.dat$lam.ratio <- dd.dat$lam.org.no.fish/dd.dat$lam.no.fish
+dd.dat$lam.ratio.z <- dd.dat$lam.org.fish/dd.dat$lam.fish
+# So the original lambda tended to be somewhere between 7 and 14% higher, depending on me(di)an choice.
+# Could be way off in some years for a few species (Haddock, Cod, Sand lance, horse makerel, pilchard(sardine)... interesting... )
+summary(dd.dat$lam.ratio)
+summary(dd.dat$lam.ratio.z)
+ggplot(dd.dat,aes(y=lam.ratio,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
+ggplot(dd.dat,aes(y=lam.ratio.z,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
 # Other figures....
@@
 # windows(11,11)
-# cod.r0.ts.plt <- ggplot(pop.dam %>% dplyr::filter(Species == 'morhua')) + geom_line(aes(y=R0.opt,x=cohort,group=Area,color=Area,linetype=Area),size=1.5)  + 
+# cod.r0.ts.plt <- ggplot(pop.dam |> collapse::fsubset(Species == 'morhua')) + geom_line(aes(y=R0.opt,x=cohort,group=Area,color=Area,linetype=Area),size=1.5)  + 
 #                             scale_y_log10(name = "Lifetime Reproductive Output", breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
@@
 # windows(11,11)
-# ggplot(pop.dam %>% dplyr::filter(Species =="morhua")) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
+# ggplot(pop.dam |> collapse::fsubset(Species =="morhua")) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
 #                                                         scale_y_log10(name = "Lifetime Reproductive Output",breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) +
@@
 #                                    
-# bycatch.plt.cod <- ggplot(for.tunes %>% dplyr::filter(Species == 'morhua')) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + 
+# bycatch.plt.cod <- ggplot(for.tunes |> collapse::fsubset(Species == 'morhua')) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + 
 #                                                                               ylab("Adjustment to catch (%)") +
@@
 
-# dub.heatmap.no.6 <- ggplot(dub.time.summary %>% dplyr::filter(!Species %in% six.species), aes(x=year, y=Stock.short, fill= prop)) + 
+# dub.heatmap.no.6 <- ggplot(dub.time.summary |> collapse::fsubset(!Species %in% six.species), aes(x=year, y=Stock.short, fill= prop)) + 
 #                               xlab("") + ylab("")+                                    

### 2024-04-25 Drafts/Paper_1/02-intro.Rmd
I haven't updated in a while update
Working on Methods, Results, Discussion. Doing one last big run on the doubling time estimates.  Miles to go...

# INTRODUCTION  {#intro}

Intro – life history paragraph, environmental variation paragraph, management ties paragraph, goals.

theoretical expectations related to productivity and life history for various species (e.g. herring vs. Cod) (ties to regional variation in lifetime reproductive rates and doubling time).

Evidence for specific species to make use of environmental conditions – boom in recruitment.

How our understanding of productivity is used in a management context – projections, reference points, risk, (ties directly to density dependence figure).  
Species-environment relationship – is it different from what we expect and how does that influence our capacity for management of exploited fishes.

The underappreciated influence of regional variation in determining recovery potential of exploited teleosts.  - can’t look at a single species and expect it will behave the same way.

Objectives
  - Quantify the life history variability of exploited marine teleosts
  - Explore regional and taxonomic correlates of life history variability
  - Based on the observed life history, quantify the recovery potential of marine teleosts in the absence of fishing

### 2024-04-25 Drafts/Paper_1/03-methods.Rmd
I haven't updated in a while update
Working on Methods, Results, Discussion. Doing one last big run on the doubling time estimates.  Miles to go...

@@
 Where $x$ is the age, $\alpha$ is the age at first reproduction, $\omega$ is the maximum age, $\lambda$ is the discrete rate of population growth ($\lambda = e^r$), $s_x$ is the survivorship to age $x$, and $f_x$ is the fecundity of individuals of age $x$.
+For stocks in which the minimum age is > 0, this may lead to a slight positive bias in the lambda estimate [@pardoMaximumIntrinsicRate2016].
+
 The discrete time Euler-Lotka equation can be shown to be the characteristic polynomial of the Leslie Matrix, where $f_0$ is the fecundity of the first age class with mature individuals [@leslieUseMatricesCertain1945,@caswellMatrixPopulationModels2001]:
@@
 
-The data necessary to obtain age specific estimates of fecundity and mortality are publicly available from the database  @charbonneauAgestructuredmarinefishdatabase2022.
+The data necessary to obtain initial age specific estimates of fecundity and mortality are publicly available from the database  @charbonneauAgestructuredmarinefishdatabase2022.
 
@@
 
-The number of spawners in year $t$ and age class $a$ ($SSN_{t,a}$) is the proportion of mature individuals ($Mat_{t,a}$) multiplied by the Number of individuals
+The number of spawners in year $y$ and age class $a$ ($SSN_{y,a}$) is the proportion of mature individuals ($Mat_{y,a}$) multiplied by the Number of individuals
 
 $$
-SSN_{t,a} = Mat_{t,a} N_{t,a}
+SSN_{y,a} = Mat_{y,a} N_{y,a}
+$$
+The number of recruits produced per kilogram of spawning biomass $RPS_{y}$ is calculated as
+
+$$
+RPS_{y} = R_{y} SSB_{tot,(y-ra)} 
 $$
 
-# NEED TO SORT OUT THE "NOMENCLATURE" AROUND LINING THESE UP RIGHT!
-
-The number of recruits produced per spawner $RPS_{t}$ is calculated as
+Where $SSB_{yot,y-ra}$ is the total spawning stock biomass in year $y$.
+$R_{y}$ is the number individuals in the youngest age class (hereafter referred to as recruits) offset temporally by the age of the recruits, for example, if the age of the recruits ($ra$) is 2 years , we assume that the recruits in 2010 were produced by the spawning stock biomass in 2008 ($SSB_{tot,y-ra}$).
+The number of recruits produced by each age class ($RPA_{y,a}$) can then be calculated by multiplying the spawner biomass in each age class $SSB_{y-ra,a}$ by the number of number of recruits produced per kilogram of SSB
 
 $$
-RPS_{t+ra} = R_{t+ra} SSB_{t} 
+RPA_{y,a} =  SSB_{(y-ra),a} RPS_{y,a}
 $$
-
-Where $SSB_{t}$ is the total spawning stock biomass in year $t$ and $R_t$ is the number individuals in the youngest age class (hereafter referred to as recruits).
-The spawner abundance ($SSB$) is offset by the age of the recruits ($ra$), for example, if the recruits are two-year olds, we assume that the recruits in 2010 were produced by the spawners in 2008.
-The number of recruits produced by each age class can then be calculated by multiplying the spawner biomass in each age class $S_{t,a}$ by the number of number of recruits produced per kilogram of SSB
+This method assumes that there is no effect of age on reproductive success (i.e., each kilogram of spawning biomass contributes the same to the total total reproductive output, irrespective of their age).
+Finally, the fecundity ($Fec_{y-1,a}$) is calculated as number of offspring produced by each individual in the population, this is offset by one year, as the recruits observed in year $y+1$ are produced in the Euler-Lotka formulation in year $y$.
 
 $$
-RPA_{(t+ra),a} =  SSB_{t,a} RPS_{(t+ra),a}
+Fec_{y,a} =  RPA_{y+1,a} / SSN_{(y-ra+1),a}
 $$
-This method assumes that there is no effect of age on reproductive success (i.e., each kilogram of spawning biomass contributes the same to the total total reproductive output, irrespective of their age).
-Finally, the fecundity is calculated as number of offspring produced by each individual in the population
-
-$$
-Fec_{t,a} =  RPA_{t,a} / SSN_{t,a}
-$$
-
 Due to challenges with separability in typical stock assessment models, natural mortality is often assumed for each age class, in some assessments it varies by age and over time, in other assessments it does not.
@@
 $$
-FM_{t,a} =  Catch_{t,a} / N_{t,a}
+FM_{y,a} =  Catch_{y,a} / N_{y,a}
 $$
-This is combined with the natural mortality to get a total mortality estimate ($Z_{t,a}$) for each age in each year
+This is combined with the natural mortality to get a total mortality estimate ($Z_{y,a}$) for each age in each year
 
 $$
-Z_{t,a} =  FM_{t,a} + NM_{t,a}
+Z_{y,a} =  FM_{y,a} + NM_{y,a}
 $$
@@
 $$
-N_{t+1} = \lambda N_{t}
+N_{y+1} = \lambda{y} N_{y}
 $$
-The result of this was compared to the abundance estimate from the stock assessment for the upcoming year ($N_{t+1}$).
-Where necessary, the fecundity and natural mortality estimates were adjusted until the $\lambda$ estimate from the Euler-Lotka equation resulted in an abundance time-series estimate ($N_{t+1}$) that was less than 5% different from the abundance estimates from the stock assessment (AVERAGE DIFFERNCE WAS 0.XX%).
+The result of this was compared to the abundance estimate from the stock assessment for the upcoming year ($N_{y+1}$).
+Where necessary, the fecundity and natural mortality estimates were adjusted until the $\lambda$ estimate from the Euler-Lotka equation resulted in an abundance time-series estimate ($N_{y+1}$) that was less than 5% different from the abundance estimates from the stock assessment (AVERAGE DIFFERNCE WAS 0.XX%).
 In this way the $\lambda$, fecundity, and natural mortality estimates are obtained for each year in which data are available.
@@
 -->
+
+## Doubling Time
+
+Doubling time was calculated using a simulation approach in which the estimated fecundity and natural mortality for a year were sampled from the historically observed fecundity and natural natural mortality.
+The Euler-Lotka equation was used to estimate the population growth rate and this rate was used to adjust the population biomass accordingly.
+The simulation was run for XX years with YY simulations, the percentage of the simulations in which the population size had doubled was recorded each year.
+If a population had doubled in size, it was removed from the simulation and recorded as having doubled for all subsequent years.
+
+## Lifetime Reproductive Success
+
+The lifetime reproductive success ($R_0$) in the absence of fishing was calculated for each cohort in which fecundity and natural mortality were available for all age classes.
+This was calculated for each cohort as
+
+$$
+R_0 = \sum_{x=\alpha}^{\omega} s_x f_x
+$$
+
+*Here we are treating the plus group as effectively 'terminal', i.e., it assumes that after the last age class the individuals make no contribution, which means these values are probably a bit low, but at this age they really aren't making much of a contribution on average*.
+
+## Generaion Time
+
+The generation time here is defined as the mean age of the spawners of the observed recruits in a cohort over its lifetime ($T_G$) in the absence of fishing was calculated for each cohort in which fecundity and natural mortality were available for all age classes.
+This was calculated for each cohort as.
+
+$$
+T_G = \frac{\sum_{x=\alpha}^{\omega} x s_x f_x}{\sum_{x=\alpha}^{\omega}  s_x f_x}
+$$

### 2024-04-25 Drafts/Paper_1/05-discussion.Rmd
I haven't updated in a while update
Working on Methods, Results, Discussion. Doing one last big run on the doubling time estimates.  Miles to go...

# DISCUSSION {#disin}

I think we disagree with @kindsvaterTenPrinciplesEvolutionary2016 because we can't generalize based on life-history very easily (cod haddock herring).

Looks like density dependence is real. Dave's pet theroy is there is solid evidence of density dependence for many stocks above around 0.4, below 0.4 the evidence hints more at density independence for many stocks, BUT, some stocks have an ability to very occasionally very spectacularly take advantage of the environment.  But not all stocks and species have this ability and the strength and frequency seems to be influenced by where you life and what species you are. Little evidence for spectacular reproduction events in NW Atlantic, while the majority of species assessed in the north sea have this ability. Cod show this dicomaty perfectly....

Looks like the median lambda is around 0.2 at low abundance (mean is much higher because outliers) for many stocks. So potential growth at low abundance is around 20%, tends to trend towards 0 as you approach the maximum observed abundance. This is very interesting b/c on average is suggests that the maximum observed abundance may be a reasonable proxy for the carrying capacity of a stock. Of course there is a great deal of variability around this, which may be related to the timing of the start of the time series in relation to historical fishing activity, fishing pressure, environmental variability, etc... but still it is kinda interesting.

The recovery potential for some species is tied to the variability in their growth rate... Based on historically observed lambdas, all the Haddock stock in this analysis were likely to double in size within a decade of fishing cessation. The worst situation is low lambda + low variability... you can have a low lamda 'most of the time', but if highly variable the stock can take off (this in many ways is what fisheries science is based on)... Also of note these large events do tend to be far more likely when abundance is < 40% of maximum (of course this would be in part because it's easier to go from having \$10 to \$20 than it is to go from \$1,000 to \$2,000).

Idea- realized productivity of cod/haddock has been highly variable. But from life history theory you would have expected that to be herring/smelt. Episodic recruitment events. (boom and bust?) not population boom but more like a baby boom.

Likelihood of stock collapse related to life history characteristics, maybe reframe relative to large productivity events of cohorts – link to idea of cod/haddock above. No expectation that intersection between life history traits and environmental conditions to result in such marked differences among populations within a species in realized productivity.

Center around the idea of equilibrium theory? That management might be fairly good for stocks that aren’t very variable, but when you make a decision based on averages you can make really bad ones.

### 2024-04-25 Drafts/Paper_1/index.Rmd
I haven't updated in a while update
Working on Methods, Results, Discussion. Doing one last big run on the doubling time estimates.  Miles to go...

@@
 title: |
-   "Observed life history characteristics of harvested marine species"
+   "Life history variability influence on the recovery potential of globally exploited teleosts "
 french_title: "Titre ici (*Nom latin de l'espèce*)"
@@
 # If we already have the results don't re-run the models or load data we don't need.
-load.results <- F
+load.results <- T
 # What tunning model are you running or did you run!
@@
   # And binding it all back together
-  ASR_trim <- cbind(ASRsp, ASRdat)
+  ASR.trim <- cbind(ASRsp, ASRdat)
   # need a unique ID for stock
-  #table(ASR_trim$Management, ASR_trim$Species)
-  ASR_trim$Stock <- paste0(ASR_trim$Management, "_", ASR_trim$Area, "_", ASR_trim$Genus, "_", ASR_trim$Species)
+  #table(ASR.trim$Management, ASR.trim$Species)
+  ASR.trim$Stock <- paste0(ASR.trim$Management, "_", ASR.trim$Area, "_", ASR.trim$Genus, "_", ASR.trim$Species)
 
-  ASR_long <- ASR_trim %>%
+  ASR.long <- ASR.trim %>%
     pivot_longer(!c("Management", "Area", "Order", "Family", "Genus", "Species", "Stock", "Year","Meeting_or_reference","Model","Case","Notes")) %>%
@@
   # Something is weird with the mentella stock, I'm going to drop it...
-  ASR_long <- ASR_long %>% dplyr::filter(Stock != "ICES-AFWG_DEEP1-2_Sebastes_mentella")
+  ASR.long <- ASR.long %>% dplyr::filter(Stock != "ICES-AFWG_DEEP1-2_Sebastes_mentella")
 }# end if load results

### 2024-04-25 Scripts/functions/tuning_sim_fast.r

@@ -460,21 +460,21 @@ fast.tunes<-function(years,step.size=0.05,tuner="m",  direction = 'backwards',ag
     {
       index <- which(years == years[y+1])
       #browser() 
-      res$lambda[index] <- exp(r.tunes)
+      res$lambda[index-1] <- exp(r.tunes)
       #browser()
-      res$lambda.vpa.init[index] <- exp(r.est)
-      res$removals[index] <- tot.catch.tmp
-      res$removals.init[index] <- tot.catch.init
-      res$mean.fec[index] <- mean(as.numeric(fecund.tmp))
-      res$mean.vpa.fec[index] <- mean(as.numeric(fecund.init))
-      res$mean.nm[index] <- mean(as.numeric(nm.tmp))
-      res$mean.vpa.nm[index] <- mean(as.numeric(nm.init))
-      fecund.ts[index,] <- fecund.tmp
-      nm.ts[index,] <- nm.tmp
-      fm.ts[index,] <- fm.tmp
-      z.ts[index,] <- z.tmp
+      res$lambda.vpa.init[index-1] <- exp(r.est)
+      res$removals[index-1] <- tot.catch.tmp
+      res$removals.init[index-1] <- tot.catch.init
+      res$mean.fec[index-1] <- mean(as.numeric(fecund.tmp))
+      res$mean.vpa.fec[index-1] <- mean(as.numeric(fecund.init))
+      res$mean.nm[index-1] <- mean(as.numeric(nm.tmp))
+      res$mean.vpa.nm[index-1] <- mean(as.numeric(nm.init))
+      fecund.ts[index-1,] <- fecund.tmp
+      nm.ts[index-1,] <- nm.tmp
+      fm.ts[index-1,] <- fm.tmp
+      z.ts[index-1,] <- z.tmp
     } # end forwards
-    # Get teh results tidied up properly when going backwards, this is all about indices.
+    # FIX... These indicies might be wrong for going backwards now
     if(direction == 'backwards')
     {
       index <- which(years == years[y])

### 2024-05-09 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
Methods results done

@@
 
- # if(i=="ICES-WGBFAS_BS 22-32_Sprattus_sprattus") removals$Catch <- removals$Catch/1000
-
   data <- age.mat |>
@@
   #data <- data |> collapse::fsubset(Year %in% years[(minage+1):length(years)])
-  # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...
 
@@
     fs <-fs.tmp[[i]]
-    full.rem <- rem.tmp[[i]]
+    full.rem <- full.rem.tmp[[i]]
     #full.abund <- full.abund.tmp[[i]]
@@
 
-  #NE Arctic aeglefinus (high and lows)  (21) solved
-  #Faroes 5b P. virens (high and lows)  (29) solved
-
     if(i %in% sensistive.stocks) ss.size = ss.size/10
@@
   meta$Species[meta$Species == "Solea"] <- "solea"
+  meta$Family[meta$Family == "Gadide"] <- "Gadidae"
   meta$Genus[meta$Genus == " Hippoglossoides"] <- "Hippoglossoides"
@@
   meta$LME[grepl("ICES",meta$Management)] <- "NE Atlantic"
+  # An area typo
+  meta$Area[grep("BSAI-females",meta$Area)] <- "BSAI-Females"
+  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI-Females"
   # Some other Area summaries
@@
   meta$Area.broad[grep("ROCK6b",meta$Area)] <- "CS"
-  meta$Area.long[grep("ROCK6b",meta$Area)] <- "Celtic Sea Rockall"
+  meta$Area.long[grep("ROCK6b",meta$Area)] <- "Celtic Sea"
   meta$Area.broad[grep("IS",meta$Area)] <- "IS"
@@
   meta$Area.long[grep("SP8abd",meta$Area)] <- "Bay of Biscay"
-  meta$Area.broad[grep("FA",meta$Area)] <- "I-F"
-  meta$Area.broad[grep("ICE",meta$Area)] <- "I-F"
+  meta$Area.broad[grep("FA",meta$Area)] <- "Ice-Faroe"
+  meta$Area.broad[grep("ICE",meta$Area)] <- "Ice-Faroe"
   meta$Area.long[grep("FA",meta$Area)] <- "Faroes"
@@
 
-  meta$Area.broad[grep("GOM",meta$Area)] <- "GOM-GB"
-  meta$Area.long[grep("GOM",meta$Area)] <- "Gulf of Maine"
-  meta$Area.broad[grep("GB",meta$Area)] <- "GOM-GB"
-  meta$Area.long[grep("GB",meta$Area)] <- "Georges Bank"
-  meta$Area.broad[grep("5Y",meta$Area)] <- "GOM-GB"
-  meta$Area.long[grep("5Y",meta$Area)] <- "NAFO 5Y"
-  meta$Area.broad[grep("5Z",meta$Area)] <- "GOM-GB"
-  meta$Area.long[grep("5Z",meta$Area)] <- "NAFO 5Z"
-  meta$Area.broad[grep("USATL",meta$Area)] <- "GOM-GB" # The fishery is broader than just GOM, but it does also include it.
-  meta$Area.long[grep("USATL",meta$Area)] <- "US Atlantic" # The fishery is broader than just GOM, but it does also include it.
-  meta$Area.broad[grep("NWA",meta$Area)] <- "GOM-GB" # Mackerel... so that definition is a bit narrow....
-  meta$Area.long[grep("NWA",meta$Area)] <- "US Atlantic" # Mackerel... so that definition is a bit narrow....
+  meta$Area.broad[grep("GOM",meta$Area)] <- "NAFO 5-6"
+  meta$Area.long[grep("GOM",meta$Area)] <- "NAFO 5-6"
+  meta$Area.broad[grep("GB",meta$Area)] <- "NAFO 5-6"
+  meta$Area.long[grep("GB",meta$Area)] <- "NAFO 5-6"
+  meta$Area.broad[grep("5Y",meta$Area)] <- "NAFO 5-6"
+  meta$Area.long[grep("5Y",meta$Area)] <- "NAFO 5-6"
+  meta$Area.broad[grep("5Z",meta$Area)] <- "NAFO 5-6"
+  meta$Area.long[grep("5Z",meta$Area)] <- "NAFO 5-6"
+  meta$Area.broad[grep("USATL",meta$Area)] <- "NAFO 5-6" # The fishery is broader than just GOM, but it does also include it.
+  meta$Area.long[grep("USATL",meta$Area)] <- "NAFO 5-6" # The fishery is broader than just GOM, but it does also include it.
+  meta$Area.broad[grep("NWA",meta$Area)] <- "NAFO 5-6" # Mackerel... so that definition is a bit narrow....
+  meta$Area.long[grep("NWA",meta$Area)] <- "NAFO 5-6" # Mackerel... so that definition is a bit narrow....
   #meta$Area1[grep("SNE- MA",meta$Area)] <- "GOM-GB" # YT in US, so no GB so that definition is a bit narrow....
-  meta$Area.broad[grep("MA",meta$Area)] <- "GOM-GB" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
-  meta$Area.long[grep("MA",meta$Area)] <- "Gulf of Maine" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
+  meta$Area.broad[grep("MA",meta$Area)] <- "NAFO 5-6" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
+  meta$Area.long[grep("MA",meta$Area)] <- "NAFO 5-6" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
   meta$Area.broad[grep("BSAI",meta$Area)] <- "BSAI"
-  meta$Area.broad[grep("4T",meta$Area)] <- "GSL"
-  meta$Area.long[grep("4T",meta$Area)] <- "NAFO 4T"
-  meta$Area.broad[grep("2J3",meta$Area)] <- "NFLD"
-  meta$Area.long[grep("2J3",meta$Area)] <- "NFLD"
-  meta$Area.broad[grep("3Pn-4RS",meta$Area)] <- "NFLD"
-  meta$Area.long[grep("3Pn-4RS",meta$Area)] <- "NFLD"
+  meta$Area.broad[grep("4T",meta$Area)] <- "NAFO 2-4"
+  meta$Area.long[grep("4T",meta$Area)] <- "NAFO 2-4"
+  meta$Area.broad[grep("2J3",meta$Area)] <- "NAFO 2-4"
+  meta$Area.long[grep("2J3",meta$Area)] <- "NAFO 2-4"
+  meta$Area.broad[grep("3Pn-4RS",meta$Area)] <- "NAFO 2-4"
+  meta$Area.long[grep("3Pn-4RS",meta$Area)] <- "NAFO 2-4"
   meta$Area.long[grep("GOA",meta$Area)] <- "Gulf of Alaska"
+  # Lumping everything in Berring Sea and AI into both.
   meta$Area.long[grep("AI",meta$Area)] <- "Aleutian Islands"
-  meta$Area.long[grep("ESB",meta$Area)] <- "Bering Sea"
+  meta$Area.long[grep("ESB",meta$Area)] <- "Bering Sea & AI" 
   meta$Area.long[grep("BSAI",meta$Area)] <- "Bering Sea & AI"
-  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI-Females"
+  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI"
+  meta$Area[grep("BSAI-Females",meta$Area)] <- "BSAI"
+  meta$Area[grep("BSAI-females",meta$Area)] <- "BSAI"
   meta$Area.long[grep("BSAI-Females",meta$Area)] <- "Bering Sea & AI"
@@
   meta$Area.narrow[meta$Stock == "ICES-HAWG_WBS 22-24_Clupea_harengus"] <- "22-24"
-  meta$Area.narrow[meta$Stock == "DFO_4T-Fall_Clupea_harengus"] <- "Fall"
-  meta$Area.narrow[meta$Stock == "DFO_4T-Spring_Clupea_harengus"] <- "Spring"
+  meta$Area.narrow[meta$Stock == "DFO_4T-Fall_Clupea_harengus"] <- "Fa-SGSL"
+  meta$Area.narrow[meta$Stock == "DFO_4T-Spring_Clupea_harengus"] <- "Sp-SGSL"
   meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS27.6a_Merlangius_merlangus"] <- "27.6a"
@@
   meta$Area.narrow[meta$Stock == "ICES-WGCSE_NS6a_Gadus_morhua"] <- "6a"
-  meta$Area.narrow[meta$Stock == "DFO_2J3KL_Gadus_morhua"] <- "2J 3KL"
-  meta$Area.narrow[meta$Stock == "DFO_3Pn-4RS_Gadus_morhua"] <- "3Pn 4RS"
-  meta$Area.narrow[meta$Stock == "NEFSC-CERT-TRAC_GB _Gadus_morhua"] <- "East"
-
-  meta$Stock.short <- paste0(meta$Area.long," ",meta$Area.narrow," ",meta$G.short," ",meta$Species)
+  meta$Area.narrow[meta$Stock == "DFO_2J3KL_Gadus_morhua"] <- "NFLD"
+  meta$Area.narrow[meta$Stock == "DFO_3Pn-4RS_Gadus_morhua"] <- "NGSL"
+  meta$Area.narrow[meta$Stock == "NEFSC-CERT-TRAC_GB _Gadus_morhua"] <- "EGB"
+  meta$Area.narrow[meta$Stock == "ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus"] <- "RA"
+  meta$Area.narrow[meta$Stock == "DFO_4T-4VN_Gadus_morhua"] <- "SGSL"
+  meta$Area.narrow[meta$Stock == "DFO_4T_Hippoglossoides _platessoides"] <- "SGSL"
+  meta$Area.narrow[meta$Stock == "DFO_4T_Scomber_scombrus"] <- "SGSL"
+  meta$Area.narrow[meta$Stock == "NEFSC-SAW_GOM_Gadus_morhua"] <- "GOM"
+  meta$Area.narrow[meta$Stock == "NEFSC-GARMIII_GB_Gadus_morhua"] <- "GB"
+  meta$Area.narrow[meta$Stock == "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus"] <- "GOM"
+  meta$Area.narrow[meta$Stock == "CERT-TRAC_GB_Melanogrammus_Aeglefinus"] <- "GB"
+
+  meta$Stock.short <- paste0(meta$Area.broad," ",meta$Area.narrow," ",meta$G.short," ",meta$Species)
   meta$Stock.no.species <- paste0(meta$Area.long," ",meta$Area.narrow)
@@
   dt.res <- NULL
-  n.dt.sims <- 1000 # Increase to 1000 for final run, which takes like a full day or something 
-  n.years <- 100
+  # These are both set in the index file now, go there!!
+  n.dt.sims <- n.dt.sims
+  n.sim.years <- n.sim.years
   for(i in Stocks)
@@
   {
-
-    tmp <- rep(0,n.years)
-    for(y in 2:n.years)
+    tmp <- rep(0,n.sim.yearss)
+    print(paste0("Sim # ", s))
+
+    for(y in 2:n.sim.yearss)
     {
@@
       pop[y] <- exp(r.val)*pop[y-1]
-      if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.years] <- 1
+      if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.sim.yearss] <- 1
     } # end the years loop
-    tmp.res[[s]] <- data.frame(year =1:n.years,doubled = tmp,sim=s)
+    tmp.res[[s]] <- data.frame(year =1:n.sim.yearss,doubled = tmp,sim=s)
 
@@
   count <- 0
-  print(paste0("Stock ",i," Sim ", s," time =", round(Sys.time()-str.time,digits=1)," minutes Stock number",count+1))
+  timer <- round(difftime(Sys.time(),str.time,units='mins'),digits=1)
+  print(paste0("Stock ",i," time =", timer," minutes: Stock # ",count+1))
   } # end Stocks loop
@@
       }# end the ages loop
-          res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,lx.opt = lx,
+          res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,
                                  mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
                                  x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
-                                 zx.opt = zx,zx.opt = zx,
+                                 zx.opt = zx,
                                  mx.zx.opt = fs*zx,mx.zx.org = fs.org*zx.org,
@@
 
-  pop.dam <- res.cohort.final |> dplyr::group_by(cohort,Stock) |> dplyr::summarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
+  pop.dam <- res.cohort.final |> collapse::fgroup_by(cohort,Stock) |> collapse::fsummarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
                                                                                    gen.len.org = sum(x.mx.lx.org)/sum(mx.lx.org),
@@
 
-```{r simp-figs,include=F,echo=F,message=F,warning=F}
+```{r clean-up-and-stats,include=F,echo=F,message=F,warning=F}
 load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
+for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
+
+Stocks <- unique(res.lambda.final$Stock)
 res.lambda.fin <- data.frame(res.lambda.final)
-
 six.species <- c('morhua','harengus','aeglefinus','virens','solea','platessa')
@@
 res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock) |> 
-                                                          collapse::fmutate(lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
+                                                          collapse::fmutate(
+                                                          lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
                                                           lam.fish.mn = mean(lam.fish,na.rm=T),
@@
                                                           lam.org.no.fish.med = median(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T)) |> data.frame()
-
+                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T),
+                                                          lam.no.fish.sd = sd(lam.no.fish,na.rm=T),
+                                                          lam.fish.sd = sd(lam.fish,na.rm=T),
+                                                          lam.org.no.fish.sd = sd(lam.org.no.fish,na.rm=T),
+                                                          lam.org.fish.sd = sd(lam.org.fish,na.rm=T)
+                                                          ) |> data.frame()
+# Get the order right for the stock no species for the boxplots to come later
+sns.order <- c("Baltic Sea ", "Baltic Sea 22-24", "Baltic Sea 25-32", "Baltic Sea 28", 
+               "North Sea ", "North Sea 4", "North Sea 22-24", "North Sea 4-7 20", "North Sea 6a","North Sea 4 20", "North Sea 7d",     
+               "Celtic Sea ","Celtic Sea RA", "Celtic Sea 7a", "Celtic Sea 27.6a", 
+               "Irish Sea ","Irish Sea 7a", "Irish Sea 7e","Bay of Biscay ", "NE Arctic ", 
+               "Faroes 5a", "Faroes 5b",  "Iceland ", "Iceland 5a",
+                "NAFO 2-4 Fa-SGSL", "NAFO 2-4 Sp-SGSL", "NAFO 2-4 SGSL", "NAFO 2-4 NGSL", "NAFO 2-4 NFLD",  
+                "NAFO 5-6 ", "NAFO 5-6 GB", "NAFO 5-6 GOM", "NAFO 5-6 EGB",
+                "Bering Sea & AI ", "Gulf of Alaska ", "Aleutian Islands ")
+
+res.lambda.fin$Stock.no.species <- factor(res.lambda.fin$Stock.no.species,levels = sns.order,ordered = T)
 res.lambda.final.6 <- res.lambda.fin |> collapse::fsubset(Species %in% six.species)
@@
                                     collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+# Making the Aleutian Islands their own Area long...
+res.lambda.fin$Area.long[res.lambda.fin$Area == "AI"] <- "Aleutian Islands"
+res.lambda.fin$Area.long <- factor(res.lambda.fin$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
+                                                                       "Irish Sea","Bay of Biscay","NE Arctic",
+                                                                       "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
+
 res.lambda.final.6 <- res.lambda.final.6 |> collapse::roworder(Species,Area.broad) |>
@@
                        collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-# res.lambda.final.6 <- res.lambda.final.6 |> collapse::roworder(LME,Area.broad) |>
-#                                              collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-################### Figures in main text################### Figures in main text################### Figures in main text###################
-
-#hmm <- merge(tst,res.lambda.final.6,by="Stock")
-plot(res.lambda.fin$lam.fish.med ~ res.lambda.fin$lam.fish.mn)
-# So this is lambda with fishing included
-lambda.plt <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.no.fish,x=Stock.no.species))  + 
-                                           geom_point(aes(y=lam.no.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-                                           xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_wrap(~G.Species,scales='free')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_no_fishing_6_",what.2.tune,".png"),lambda.plt,base_width = 12,base_height = 10)
-
-# With fishing
-lambda.plt.fish <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.fish,x=Stock.no.species))  + 
-                                           geom_point(aes(y=lam.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-                                           xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_wrap(~G.Species,scales='free')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_with_fishing_6_",what.2.tune,".png"),lambda.plt.fish,base_width = 12,base_height = 10)
-
-# Doubling Times
-
-dub.heatmap.cod <- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "G.
-morhua"), aes(x=year, y=Stock.no.species, fill= prop)) + xlab("") + ylab("")+                                     facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + scale_x_continuous(labels=NULL) +
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.herring<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "C. harengus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-                              xlab("") + ylab("")+                                    
-                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-
-dub.heatmap.haddock<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "M. aeglefinus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-                              xlab("") + ylab("")+                                    
-                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.125, "cm"))
-
-dub.heatmap.virens<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. virens"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-                              xlab("") + ylab("")+                                    
-                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.4, "cm"))
-
-dub.heatmap.solea<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "S. solea"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-                              xlab("") + ylab("")+                                    
-                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-
-dub.heatmap.platessa<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. platessa"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-                              xlab("") + ylab("")+                                    
-                              facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous() +
-                              geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
-
-dub.heatmap.sp6 <- cowplot::plot_grid(dub.heatmap.cod,dub.heatmap.herring,dub.heatmap.haddock,
-                                 dub.heatmap.virens, dub.heatmap.solea,dub.heatmap.platessa,nrow = 6,rel_heights = c(14,9,8,5,5,4))
-dub.heatmap.sp6
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_sp6_",what.2.tune,".png"),dub.heatmap.sp6,base_width = 20,base_height = 17)
-
-# Generation length
-
-gen.boxplt <- ggplot(pop.dam.6) +
-                            geom_boxplot(aes(y=gen.len.opt,x=Stock.no.species))  + 
-                            xlab("") + scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
-                            facet_wrap(~G.Species,scales='free_x')+
-                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',plot.margin = margin(0,0.5,0,0.5, "cm"),
-                                  axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_no_fish_6_species_",what.2.tune,".png"),gen.boxplt,base_width = 12,base_height = 10)
-
-# Lifetime reproductive success (no fishing)
-
-r0.boxplt <- ggplot(pop.dam.6) +
-                            geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
-                            xlab("") + scale_y_log10(name = "Lifetime Reproductive Output")+
-                            geom_hline(yintercept = 1,linetype='dashed',color='blue')+
-                            facet_wrap(~G.Species,scales = 'free')+
-                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',plot.margin = margin(0,0.5,0,0.5, "cm"),
-                                  axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_no_fish_6_species_",what.2.tune,".png"),r0.boxplt,base_width = 12,base_height = 10)
-
-################### Supplemental Figures################### Supplemental Figures################### Supplemental Figures################### Supplemental
+pop.dam$Area.long[pop.dam$Area == "AI"] <- "Aleutian Islands"
+pop.dam$Area.long <- factor(pop.dam$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
+                                                         "Irish Sea","Bay of Biscay","NE Arctic",
+                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
+# I'd also like a pop.dam including fishing
+pop.dam.fish <- res.cohort.final |> collapse::fgroup_by(cohort,Stock) |> collapse::fsummarise(gen.len.opt = sum(x.mx.zx.opt)/sum(mx.zx.opt),
+                                                                                   gen.len.org = sum(x.mx.zx.org)/sum(mx.zx.org),
+                                                                                   R0.opt = sum(mx.zx.opt),R0.org = sum(mx.zx.org))
+pop.dam.fish <- left_join(pop.dam.fish,meta.sub,by="Stock")
+pop.dam.fish$Area.long[pop.dam.fish$Area == "AI"] <- "Aleutian Islands"
+pop.dam.fish$Area.long <- factor(pop.dam.fish$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
+                                                         "Irish Sea","Bay of Biscay","NE Arctic",
+                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
+pop.dam <- data.frame(pop.dam)
+
+pop.dam.fish <- pop.dam.fish |> collapse::roworder(Species,LME) |>
+                                collapse::fmutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
+pop.dam.fish.6 <- pop.dam.fish |> collapse::fsubset(Species %in% six.species)
+
+pop.dam.fish.6 <- pop.dam.fish.6 |> collapse::roworder(LME,Area.broad) |>
+                                    collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
+
+# Put the population dynamics stuff together.
+pop.dam$group <- "no fish"
+pop.dam.fish$group <- 'fish'
+pop.dam.all <- rbind(pop.dam,pop.dam.fish)
+
+pop.dam.6$Stock.no.species <- factor(pop.dam.6$Stock.no.species,levels = sns.order,ordered = T)
+pop.dam$Stock.no.species <- factor(pop.dam$Stock.no.species,levels = sns.order,ordered = T)
+pop.dam.fish.6$Stock.no.species <- factor(pop.dam.fish.6$Stock.no.species,levels = sns.order,ordered = T)
+pop.dam.fish$Stock.no.species <- factor(pop.dam.fish$Stock.no.species,levels = sns.order,ordered = T)
+pop.dam.all$Stock.no.species <- factor(pop.dam.all$Stock.no.species,levels = sns.order,ordered = T)
+# Drop the periods....
+pop.dam.all.6 <- pop.dam.all |> collapse::fsubset(!Species %in% six.species)
+pop.dam.all$G.Species <- gsub("\\.","",pop.dam.all$G.Species)
+pop.dam.all$G.Species.short <- substr(pop.dam.all$G.Species,1,5)
+pop.dam.all$G.Species <- gsub("\\.","",pop.dam.all$G.Species)
+pop.dam.all.6 <- pop.dam.all |> collapse::fsubset(Species %in% six.species)
+pop.dam.all.others <- pop.dam.all |> collapse::fsubset(!Species %in% six.species)
 
@@
 dub.time.summary$Order.short[dub.time.summary$Order == "Perciformes"] <- "Perci"
-
-dub.time.summary <- dub.time.summary |>
-                            collapse::roworder(G.Species,LME,Area.broad) |>
-                            collapse::fmutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-dub.heatmap.gad <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Gadiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+                                    
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.45, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.pl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Pleuronectiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+                                    
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"))
-
-dub.heatmap.cl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Clupeiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.35, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.per <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Perciformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.scom <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Scombriformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2.1, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.scorp <- ggplot(dub.time.summary |> collapse::fsubset(Order %in% "Scorpaeniformes "), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + 
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.5, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap <- cowplot::plot_grid(dub.heatmap.gad,dub.heatmap.pl,dub.heatmap.cl,dub.heatmap.per,dub.heatmap.scom,dub.heatmap.scorp,
-                                  nrow = 6,rel_heights = c(39,20,11,4,3,3))
-dub.heatmap
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"),dub.heatmap,base_width = 20,base_height = 20)
-
-# Time series of lambdas....
-col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-#col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
-pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
-#pty <- rep(rep(c(21:23),5),20)
-
-lambda.ts.plt <- ggplot(res.lambda.final.6,aes(y=lam.fish,x=year,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
-                            geom_point(size=4) +
-                            geom_smooth(method='gam',formula = y ~ s(x, bs = "cs", fx = TRUE, k = 5),se=F) + 
-                            #scale_y_log10(name = "lambda") +
-                            facet_wrap(~G.Species,scales='free_y') +
-                            scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-                            scale_fill_manual(name = "Stock",values = col.try)+
-                            guides(colour = guide_legend(ncol = 1))+
-                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm'))
-#lambda.ts.plt
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_timeseries_6_",what.2.tune,".png"),lambda.ts.plt,base_width = 12,base_height = 10)
-
-lambda.dec.plt <- ggplot(res.lambda.final.6,aes(y=med.lam,x=as.factor(decade))) +
-                            geom_boxplot() + scale_y_log10()+
-                            xlab("Decade") + ylab("Lambda") + 
-                            geom_point(aes(x=as.factor(decade),y=lm.spec.mn),color='blue',shape=8,fill='blue')+
-                            #scale_x_continuous(breaks=seq(1940,2020,by=10))+
+# First need to get the abundance and lambdas with no fishing into one object.
+ft.tmp <- for.tunes |> collapse::fselect(year,Stock,vpa.abund,est.abund,removals)
+dd.dat <- left_join(res.lambda.fin,ft.tmp,by=c('year','Stock'))
+# Now I need to get a relative abundance for each stock...
+dd.dat <- dd.dat |> collapse::fgroup_by(Stock) |> collapse::fmutate(max.abund = max(est.abund,na.rm=T))
+dd.dat <- data.frame(dd.dat)
+dd.dat$prop.abund <- dd.dat$est.abund/dd.dat$max.abund
+# Drop nas....
+drops <- -which(is.na(dd.dat$prop.abund))
+dd.dat <- dd.dat[drops,]
+#lump the data into bins
+dd.dat$prop.bin <- "< 10%"
+dd.dat$prop.bin[dd.dat$prop.abund > 0.1 & dd.dat$prop.abund <= 0.2] <- "10-20%"
+dd.dat$prop.bin[dd.dat$prop.abund > 0.2 & dd.dat$prop.abund <= 0.3] <- "20-30%"
+dd.dat$prop.bin[dd.dat$prop.abund > 0.3 & dd.dat$prop.abund <= 0.4] <- "30-40%"
+dd.dat$prop.bin[dd.dat$prop.abund > 0.4 & dd.dat$prop.abund <= 0.6] <- "40-60%"
+dd.dat$prop.bin[dd.dat$prop.abund > 0.6 & dd.dat$prop.abund <= 0.8] <- "60-80%"
+dd.dat$prop.bin[dd.dat$prop.abund > 0.8 & dd.dat$prop.abund <= 1] <- "80-100%"
+dd.dat$prop.bin <- factor(dd.dat$prop.bin,levels=c("< 10%","10-20%","20-30%","30-40%","40-60%","60-80%","80-100%"))
+
+# Subset to the big six
+dd.dat.six <- dd.dat  |>collapse::fsubset(Species %in% six.species)
+
+# This is for the new lambda figures with fishing and no fishing together
+
+res.lambda.fin.long <- res.lambda.fin |> tidyr::pivot_longer(cols = c(lam.no.fish,lam.fish),names_to = 'group',values_to = 'lambda')
+res.lambda.fin.long$Stock.no.species <- factor(res.lambda.fin.long$Stock.no.species,levels = sns.order,ordered = T)
+res.lambda.fin.long$group <- substr(res.lambda.fin.long$group,5,20)
+res.lambda.fin.long$group <- gsub("\\."," ",res.lambda.fin.long$group)
+res.lambda.fin.long.others <- res.lambda.fin.long |> collapse::fsubset(!Species %in% six.species)
+res.lambda.fin.long.others$G.Species <- gsub("\\.","",res.lambda.fin.long.others$G.Species)
+res.lambda.fin.long.others$G.Species.short <- substr(res.lambda.fin.long.others$G.Species,1,5)
+res.lambda.fin.long.6 <- res.lambda.fin.long |> collapse::fsubset(Species %in% six.species)
+res.lambda.fin.long.6$G.Species <- gsub("\\.","",res.lambda.fin.long.6$G.Species)
+
+# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE
+# here is the GAM for no fishing with subsequent processing.
+mod.dd.stock.gam.nf <- gam(log(lam.no.fish) ~   s(prop.abund,k=4) + s(prop.abund,as.factor(Stock.short),bs='fs',k=3) ,data=dd.dat)
+
+# This extracts the GAM fit so we can custom plot it on our own figure
+tmp <- plot(mod.dd.stock.gam.nf, pages = 0)
+no.stock.gam.nf.dat <- data.frame(fit = tmp[[1]]$fit + coefficients(mod.dd.stock.gam.nf)[1],prop.abund = tmp[[1]]$x,se = tmp[[1]]$se,Scenario = "F = 0")
+no.stock.gam.nf.dat$LCI <- no.stock.gam.nf.dat$fit - 1.96*no.stock.gam.nf.dat$se
+no.stock.gam.nf.dat$UCI <- no.stock.gam.nf.dat$fit + 1.96*no.stock.gam.nf.dat$se
+
+#summary(mod.dd.stock.gam.nf)
+#Residuals, definitely still issues here, maybe a bit better than some others, maybe...
+#plot(residuals(mod.dd.stock.gam.nf) ~ fitted(mod.dd.stock.gam.nf))
+# Normality = no
+#qqnorm(residuals(mod.dd.stock.gam.nf))
+#qqline(residuals(mod.dd.stock.gam.nf))
+
+pred.dd.stock.gam.nf <- expand.grid(prop.abund = seq(0, 1, length.out = 250),
+                                         Stock.short=c(unique(dd.dat$Stock.short)))
+tmp <- predict(mod.dd.stock.gam.nf, pred.dd.stock.gam.nf, type = 'response', se.fit = TRUE) 
+# Another fun trick to extract the overall smooth fit, but didn't end up using this method.
+# sms <- smooths(mod.dd.stock.gam.nf)
+# excl <- grepl("as.factor",sms)
+# rm <- sms[excl]
+# tmp.ex <- predict(mod.dd.stock.gam.nf, newdata =pred.dd.stock.gam.nf, type = 'response', se.fit = TRUE,exclude =rm) 
+# Get the fit by stock
+pred.dd.stock.gam.nf$lam.no.fish   <- exp(tmp$fit)
+pred.dd.stock.gam.nf$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
+pred.dd.stock.gam.nf$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
+
+# Thin the data so I can add points to the figure
+tmp <- NULL
+for(i in 1:(77)) 
+{
+  if(i==1) tmp[[i]] <- seq(10,230,length.out=5)
+  if(i>1) tmp[[i]] <- seq(10,230,length.out=5)+250*(i-1)
+}
+thinner.nf <- do.call('c',tmp)
+thin.pred.nf <- pred.dd.stock.gam.nf[thinner.nf,]
+# Now I want to get rid of extrapolation from this prediction data.frame, I think I need to loop it...
+# 
+short.stocks <- unique(dd.dat$Stock.short)
+n.stocks <- length(short.stocks)
+pred.out <- NULL
+thin.out <- NULL
+for(i in short.stocks)
+{
+  # Get the right stocks
+  tmpy <- dd.dat |> collapse::fsubset(Stock.short == i)
+  tmp.pred <- pred.dd.stock.gam.nf |> collapse::fsubset(Stock.short == i)
+  tmp.thin <- thin.pred.nf |> collapse::fsubset(Stock.short == i)
+  # I dont want to predict below the minimum observed abundance
+  mins <- min(tmpy$prop.abund,na.rm=T)
+  pred.out[[i]] <- tmp.pred |> collapse::fsubset(prop.abund >= mins)
+  thin.out[[i]] <- tmp.thin |> collapse::fsubset(prop.abund >= mins)
+}
+
+pred.dd.stock.gam.ss.nf <- do.call('rbind',pred.out)
+thin.pred.nf <- do.call('rbind',thin.out)
+# Combine pred stuff with the meta data for fun plots
+pred.dd.stock.gam.ss.nf <- left_join(pred.dd.stock.gam.ss.nf,meta.sub,by="Stock.short")
+pred.dd.stock.gam.ss.nf <- data.frame(pred.dd.stock.gam.ss.nf)
+thin.pred.nf <- left_join(thin.pred.nf,meta.sub,by="Stock.short")
+# Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
+# By region
+cols.gam <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
+pty.gam <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
+
+# Now do the same thing with the data that includes the effect of fishing.
+
+#mod.dd.stock.gam.fish <- gam(log(lam.fish) ~  as.factor(Stock.short) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.dat)
+mod.dd.stock.gam.fish <- gam(log(lam.fish) ~  s(prop.abund,k=4) + s(prop.abund,as.factor(Stock.short),bs='fs',k=3),data=dd.dat)
+
+tmp <- plot(mod.dd.stock.gam.fish, pages = 0)
+no.stock.gam.fish.dat <- data.frame(fit = tmp[[1]]$fit + coefficients(mod.dd.stock.gam.fish)[1],prop.abund = tmp[[1]]$x,se = tmp[[1]]$se,Scenario = "F > 0")
+no.stock.gam.fish.dat$LCI <- no.stock.gam.fish.dat$fit - 1.96*no.stock.gam.fish.dat$se
+no.stock.gam.fish.dat$UCI <- no.stock.gam.fish.dat$fit + 1.96*no.stock.gam.fish.dat$se
+
+#summary(mod.dd.stock.gam.fish)
+#Residuals, definetly still issues here, maybe a bit better than some others, maybe...
+#plot(residuals(mod.dd.stock.gam.fish) ~ fitted(mod.dd.stock.gam.fish))
+# Normality = no
+#qqnorm(residuals(mod.dd.stock.gam.fish))
+#qqline(residuals(mod.dd.stock.gam.fish))
+
+pred.dd.stock.gam.fish <- expand.grid(prop.abund = seq(0, 1, length.out = 250),
+                                         Stock.short=c(unique(dd.dat$Stock.short)))
+tmp <- predict(mod.dd.stock.gam.fish, pred.dd.stock.gam.fish, type = 'response', se.fit = TRUE) 
+pred.dd.stock.gam.fish$lam.fish   <- exp(tmp$fit)
+pred.dd.stock.gam.fish$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
+pred.dd.stock.gam.fish$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
+
+# Thin the data so I can add points to the figure
+tmp <- NULL
+for(i in 1:(77)) 
+{
+  if(i==1) tmp[[i]] <- seq(10,230,length.out=5)
+  if(i>1) tmp[[i]] <- seq(10,230,length.out=5)+250*(i-1)
+}
+thinner.fish <- do.call('c',tmp)
+thin.pred.fish <- pred.dd.stock.gam.fish[thinner.fish,]
+# Now I want to get rid of extrapolation from this prediction data.frame, I think I need to loop it...
+# 
+short.stocks <- unique(dd.dat$Stock.short)
+pred.out <- NULL
+thin.out <- NULL
+for(i in short.stocks)
+{
+  # Get the right stocks
+  tmpy <- dd.dat |> collapse::fsubset(Stock.short == i)
+  tmp.pred <- pred.dd.stock.gam.fish |> collapse::fsubset(Stock.short == i)
+  tmp.thin <- thin.pred.fish |> collapse::fsubset(Stock.short == i)
+  # I dont want to predict below the minimum observed abundance
+  mins <- min(tmpy$prop.abund,na.rm=T)
+  pred.out[[i]] <- tmp.pred |> collapse::fsubset(prop.abund >= mins)
+  thin.out[[i]] <- tmp.thin |> collapse::fsubset(prop.abund >= mins)
+}
+
+pred.dd.stock.gam.ss.fish <- do.call('rbind',pred.out)
+thin.pred.fish <- do.call('rbind',thin.out)
+# Combine pred stuff with the meta data for fun plots
+pred.dd.stock.gam.ss.fish <- left_join(pred.dd.stock.gam.ss.fish,meta.sub,by="Stock.short")
+pred.dd.stock.gam.ss.fish <- data.frame(pred.dd.stock.gam.ss.fish)
+
+thin.pred.fish <- left_join(thin.pred.fish,meta.sub,by="Stock.short")
+
+# Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
+# By region
+
+# What proportion of the stocks had the lowest 'GAM' estimate happen when the stock was at it's maximum size.
+low.gam <- data.frame(low.pa.fish = NA,diff.low.pa.fish = NA,low.pa.nf = NA,diff.low.pa.nf = NA,Stock = NA,Species = NA)
+count <- 0
+for(i in short.stocks) 
+{
+  count = count +1
+  tmp <- pred.dd.stock.gam.ss.fish |> collapse::fsubset(Stock.short == i)
+  tmp.nf <- pred.dd.stock.gam.ss.nf |> collapse::fsubset(Stock.short == i)
+  low.pa <- data.frame(low.pa.fish = tmp$prop.abund[tmp$lam.fish == min(tmp$lam.fish)],
+                       diff.low.pa.fish = tmp$lam.fish[tmp$lam.fish == min(tmp$lam.fish)] - tmp$lam.fish[tmp$prop.abund == max(tmp$prop.abund)],
+                       low.pa.nf = tmp.nf$prop.abund[tmp.nf$lam.no.fish == min(tmp.nf$lam.no.fish)],
+                       diff.low.pa.nf = tmp.nf$lam.no.fish[tmp.nf$lam.no.fish == min(tmp.nf$lam.no.fish)] - tmp.nf$lam.no.fish[tmp.nf$prop.abund == max(tmp.nf$prop.abund)],
+                       Stock = i,Species = tmp$G.Species[1])
+  low.gam[count,] <- low.pa
+}
+
+# Let's compare lambda at minimum, 0.4, and maximum and make a Table
+comp.lam.diff <- NULL
+comp.lam <- NULL
+comp.all.nf <- NULL
+comp.all.fish <- NULL
+for(i in short.stocks) 
+{
+  tmp <- pred.dd.stock.gam.ss.fish |> collapse::fsubset(Stock.short == i)
+  which.40 <- max(which(tmp$prop.abund <=0.4)) # Some stocks might not have a which 40.
+  which.max <- which(tmp$prop.abund ==1)
+  which.min <- which(tmp$prop.abund == min(tmp$prop.abund))
+  tmp.sub <- tmp[c(which.min,which.40,which.max),]
+  comp.all.fish[[i]] <- tmp.sub
+  tmp.nf <- pred.dd.stock.gam.ss.nf |> collapse::fsubset(Stock.short == i)
+  # I think I'm overkilling as this should be the same was the above witches....
+  which.40.nf <- max(which(tmp.nf$prop.abund <=0.4))
+  which.max.nf <- which(tmp.nf$prop.abund ==1)
+  which.min.nf <- which(tmp.nf$prop.abund ==min(tmp.nf$prop.abund))
+  tmp.nf.sub <- tmp.nf[c(which.min.nf,which.40.nf,which.max.nf),]
+  comp.all.nf[[i]] <- tmp.nf.sub
+  # Now we just want some summaries here I think...
+  comp.lam.diff[[i]] <- data.frame(min.abund = min(tmp.sub$prop.abund,na.rm=T),
+                              lam.fish.min.40 = tmp$lam.fish[which.min] - tmp$lam.fish[which.40],
+                              lam.fish.min.max = tmp$lam.fish[which.min] - tmp$lam.fish[which.max],
+                              lam.fish.40.max = tmp$lam.fish[which.40] - tmp$lam.fish[which.max],
+                              lam.nf.min.40 = tmp.nf$lam.no.fish[which.min.nf] - tmp.nf$lam.no.fish[which.40.nf],
+                              lam.nf.min.max = tmp.nf$lam.no.fish[which.min.nf] - tmp.nf$lam.no.fish[which.max.nf],
+                              lam.nf.40.max = tmp.nf$lam.no.fish[which.40.nf] - tmp.nf$lam.no.fish[which.max.nf],
+                              Stock = i,Species = tmp$G.Species[1])
+
+    comp.lam[[i]] <- data.frame(min.abund = min(tmp.sub$prop.abund,na.rm=T),
+                                lam.fish.min = tmp$lam.fish[which.min] ,
+                                lam.fish.40 = tmp$lam.fish[which.40],
+                                lam.fish.max = tmp$lam.fish[which.max],
+                                lam.nf.min = tmp.nf$lam.no.fish[which.min.nf],
+                                lam.nf.40 = tmp.nf$lam.no.fish[which.40.nf],
+                                lam.nf.max = tmp.nf$lam.no.fish[which.max.nf],
+                                Stock = i,Species = tmp$G.Species[1])
+}
+
+# A table for the estimates at 'interesting' values
+comp.lam.res <- do.call('rbind',comp.lam)
+# I want to turn this into a table....
+comp.lam.res.tab <- comp.lam.res
+# Round the numbers
+comp.lam.res.tab$min.abund <- round(comp.lam.res.tab$min.abund,digits=2)
+rounders <- c("lam.fish.min","lam.fish.40","lam.fish.max",
+              "lam.nf.min","lam.nf.40","lam.nf.max")
+comp.lam.res.tab[,rounders]      <- round(comp.lam.res.tab[,rounders] ,digits=3)
+# Now give it pretty names
+tab.names <- c("Minimum Abundance",
+               "$\\lambda_{F>0}^{Min}$",
+               "$\\lambda_{F>0}^{40}$",
+               "$\\lambda_{F>0}^{Max}$",
+               "$\\lambda_{F=0}^{Min}$",
+               "$\\lambda_{F=0}^{40}$",
+               "$\\lambda_{F=0}^{Max}$",
+               "Stock","Species")
+names(comp.lam.res.tab) <- tab.names
+
+# Now do the same with the differences
+comp.lam.diff.res <- do.call('rbind',comp.lam.diff)
+# I want to turn this into a table....
+comp.lam.diff.res.tab <- comp.lam.diff.res
+# Round the numbers
+comp.lam.diff.res.tab$min.abund <- round(comp.lam.diff.res.tab$min.abund,digits=2)
+rounders <- c("lam.fish.min.40","lam.fish.min.max","lam.fish.40.max",
+                    "lam.nf.min.40","lam.nf.min.max","lam.nf.40.max")
+comp.lam.diff.res.tab[,rounders] <- round(comp.lam.diff.res.tab[,rounders] ,digits=3)
+# Now give it pretty names
+tab.names <- c("Minimum Abundance",
+               "$\\lambda_{F>0}^{Min-40}$",
+               "$\\lambda_{F>0}^{Min-Max}$",
+               "$\\lambda_{F>0}^{40-Min}$",
+               "$\\lambda_{F=0}^{Min-40}$",
+               "$\\lambda_{F=0}^{Min-Max}$",
+               "$\\lambda_{F=0}^{40-Max}$",
+               "Stock","Species")
+names(comp.lam.diff.res.tab) <- tab.names
+
+# Used for the figure showing the number of stocks that have recovered by year x.
+n.dub <- data.frame(years = 1:n.sim.years, count = NA)
+for(i in 1:n.sim.years) n.dub$count[i] <- dub.time.summary |> collapse::fsubset(year==i & prop >= 0.75) |> nrow()
+
+# Compare the population recovery with the variance, using 2010 because all stocks have a value at 2010... 
+# I'm using the overall lambda sd, so the year doesn't actually matter other than to make sure all stocks are included here
+# This is used for the recovery variance figure, is this data good?
+# How many of the stocks had doubled by year 20, with 75% being my standard, which is a high standard
+dub.p.high <- 0.75
+dub.p.low <- 0.5
+n.dub.10 <- dub.time.summary |> collapse::fsubset(year==10 & prop >= dub.p.high) |> nrow()
+n.dub.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop >= dub.p.high) |> nrow()
+# Slow stocks, here we define having a low recovery potential has having < 50% of the simulatoins experience a doubling in size.
+slow.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop < dub.p.low) 
+prop.rec.20 <- dub.time.summary |> collapse::fsubset(year==20) # the proportion that recovers by year 20
+lambda.sds <- res.lambda.fin |> collapse::fsubset(year == 2010)
+lam.sd.p.rec <- left_join(prop.rec.20,lambda.sds,by=names(prop.rec.20)[c(1,4:24)]) 
+lam.sd.p.rec$prop.cat <- "Moderate"
+lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop < dub.p.low] <- "Low"
+lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop >= dub.p.high] <- "High"
+lam.sd.p.rec$prop.cat <- factor(lam.sd.p.rec$prop.cat,levels=c("Low","Moderate","High"))
+
+```
+
+```{r paper-calcs,include=F,echo=F,message=F,warning=F}
+
+# the lambda calcs
+med.lambda.F0 <- round(median(res.lambda.fin$lam.no.fish),digits=3)
+med.r.F0 <- round(median(log(res.lambda.fin$lam.no.fish)),digits=3)*100
+med.lambda.F <- round(median(res.lambda.fin$lam.fish),digits=3)
+med.r.F <- round(median(log(res.lambda.fin$lam.fish)),digits=3)*100
+mn.lambda.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
+mn.r.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
+# Mean - median...
+res.lambda.fin$med.mn.diff.no.fish <- res.lambda.fin$lam.no.fish.med - res.lambda.fin$lam.no.fish.mn
+res.lambda.fin$med.mn.diff.fish <- res.lambda.fin$lam.fish.med - res.lambda.fin$lam.fish.mn
+# How many stocks had the mean higher than the median
+n.mn.higher.med.no.fish <- length(unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.no.fish < 0]))
+n.mn.higher.med.fish <- length(unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.fish < 0]))
+low.mn.lambda.stocks <- unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.fish > 0])
+n.nw.ice <- length(c(grep("NAFO",low.mn.lambda.stocks),grep("Faroe",low.mn.lambda.stocks)))
+n.cod.low.mn <- length(grep("morhua",low.mn.lambda.stocks))
+n.cod <- length(grep("morhua",Stocks))
+
+# Density dependence related numbers
+n.bl.40 <- length(which(!is.na(comp.lam.res$lam.fish.40)))
+n.low.40.nf <- length(which(comp.lam.res$lam.nf.40 < 1))
+n.low.40.fish <-length(which(comp.lam.res$lam.fish.40 < 1))
+low.lam.40.nf <- -round(min(comp.lam.diff.res$lam.nf.40,na.rm=T),digits=3)
+low.4.lam.40.nf <- -round(sort(comp.lam.diff.res$lam.nf.40)[4],digits=3)
+
+# If right isn't this interesting!!! And look, 3 cod stocks from around here all say around 0.4 is the worst.  Most interesting...
+n.low.lam.at.max.fish <- length(which(low.gam$low.pa.fish == 1))
+n.low.lam.at.max.nf <- length(which(low.gam$low.pa.nf == 1))
+low.lam.cods <- low.gam[low.gam$low.pa.nf < 1 & low.gam$Species == "G. morhua",]
+n.cod.lam.not.at.max.nf <- nrow(low.lam.cods)
+pa.low.cod.min <- round(min(low.lam.cods$low.pa.nf),digits=2)
+pa.low.cod.max <- round(max(low.lam.cods$low.pa.nf),digits=2)
+
+# more density dependence numbers
+pa.lam.nf.at.one <- 100*round(no.stock.gam.nf.dat$prop.abund[min(which(no.stock.gam.nf.dat$fit <0))],digits=2)
+pa.lam.fish.at.one <- 100*round(no.stock.gam.fish.dat$prop.abund[min(which(no.stock.gam.fish.dat$fit <0))],digits=2)
+# What is the minimum abundance at which we get a 2 with the fishing lambdas.
+pa.big.threshold <- 0.65
+pa.low.threshold <- 0.8
+lam.low.threshold <- 0.8
+pa.lam.fish.low.bigs <- max(dd.dat$lam.fish[dd.dat$prop.abund >= pa.big.threshold])
+pa.lam.nf.low.bigs <- round(rev(sort(dd.dat$lam.no.fish[dd.dat$prop.abund >= pa.big.threshold]))[2],digits =2)
+# What proportion of the stocks had large declines overall, and then the proportion when the population was below 30%
+dd.dat.high <- dd.dat |> collapse::fsubset(prop.abund >= 0.3)
+prop.low.high.abund <- round(length(which(dd.dat.high$lam.fish < lam.low.threshold)) / nrow(dd.dat.high),digits=3)
+prop.low.all <- round(length(which(dd.dat$lam.fish < lam.low.threshold)) / nrow(dd.dat),digits=3)
+dd.dat.low <- dd.dat |> collapse::fsubset(prop.abund < 0.3)
+prop.low.low.abund <- round(length(which(dd.dat.low$lam.fish < lam.low.threshold)) / nrow(dd.dat.low),digits=3)
+
+# Numbers for the paper, lifetime reproductive growth
+r0.mn <- round(mean(pop.dam$R0.opt,na.rm=T),digits=1)
+r0.med <- round(median(pop.dam$R0.opt,na.rm=T),digits=1)
+# And fishing...
+r0.mn.fish <- round(mean(pop.dam.fish$R0.opt,na.rm=T),digits=1)
+r0.med.fish <- round(median(pop.dam.fish$R0.opt,na.rm=T),digits=1)
+
+# Where are the slow ones from
+n.not.dub.20 <- nrow(slow.20)
+n.alaska <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short== "AFSC"]))
+n.nwa <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("DFO-TRAC","NEFSC")]))
+n.nea <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("ICES")]))
+n.nafo.24 <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Area.broad %in% "NAFO 2-4"]))
+# Now the don't recover ones...
+n.alaska.slow <- length(slow.20$Stock.short[slow.20$Manage.short== "AFSC"])
+n.nwa.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% c("DFO-TRAC","NEFSC")])
+n.nea.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% "ICES"])
+
+# Need to grab all the per.diff's, which I seem to have dropped
+for.diffs <- do.call('rbind',for.tune.summary)
+med.per.diff <- round(median(for.diffs$per.diff,na.rm=T),digits=1)
+# what is lambda difference, about 6%, but that means the original was 7% higher, so that means we are reducing lambda when optimizing
+# If there was 'missing fishing' we are compensating for with this, this is exactly what we'd expect to happen right?
+res.lambda.fin$lam.per.diff <- 100*((res.lambda.fin$lam.org.no.fish - res.lambda.fin$lam.no.fish)/ res.lambda.fin$lam.no.fish)
+med.lam.per.diff <- round(median(res.lambda.fin$lam.per.diff,na.rm=T),digits=1)
+# By stock, can see most are positive, which is in line with missing fishing mortality...
+mod.by.stock.lam.pd <- res.lambda.fin |> collapse::fgroup_by(Stock.short) |> collapse::fsummarise(med = median(lam.per.diff,na.rm=T),
+                                                                                                  mn = mean(lam.per.diff,na.rm=T))
+
+```
+
+```{r main-figs,include=F,echo=F,message=F,warning=F}
+
+# New lambda plot with the fishing and no fishing beside each other
+# This is likely Figure 1
+mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
+                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
+                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
+                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
+                4, 10, byrow = TRUE)
+new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Stock.no.species),color=group)) +
+                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
+                                           scale_x_discrete(NULL, guide = "axis_nested") +
+                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
                                            geom_hline(yintercept = 1,linetype='dashed') +
-                            facet_wrap(~G.Species,scales='free_y') 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_by_decade_6_",what.2.tune,".png"),lambda.dec.plt,base_width = 12,base_height = 12)
-
-gen.heatmap.ne <- ggplot(pop.dam |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
-                                              xlab("") + ylab("")+  
-                                              facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                              geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-gen.heatmap.nw <- ggplot(pop.dam |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-gen.heatmap.pac <- ggplot(pop.dam |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
-                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-gen.heatmap <- cowplot::plot_grid(gen.heatmap.pac,gen.heatmap.nw,gen.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-gen.heatmap
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/gen_heatmap_",what.2.tune,".png"),gen.heatmap,base_width = 20,base_height = 17)
+                                           facet_manual(vars(G.Species),design=mat,scales='free_x')+
+                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
+                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 19,base_height = 15)
+
+# The other stocks, perhaps we put this in a supplement...
+mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
+                7, 7, rep(8,9),
+                9, 9, rep(10,7),11,11),
+                3, 11, byrow = TRUE)
+
+new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(y=lambda,interaction(group,G.Species.short),color=group)) +
+                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
+                                           scale_x_discrete(NULL, guide = "axis_nested") +
+                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
+                                           geom_hline(yintercept = 1,linetype='dashed') +
+                                           facet_manual(vars(Area.long),design=mat,scales='free_x')+
+                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
+                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 19,base_height = 15)
+
+# Standard deviation figure
+colrs.sd <- rep(c(rep('blue',4),rep('orange',4),rep('grey',4),rep('black',4)),20)
+pty.sd <- rep(rep(c(21,4,9,8),4),20)
+
+lam.sd.plt <- ggplot(res.lambda.fin ) + 
+                                       geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
+                                       scale_y_log10("Standard deviation (Lambda)",log_breaks(n=8)) +
+                                       scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
+                                       theme(axis.text.x = element_text(angle =45,hjust=1),
+                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 10)
+
+# Overall density dependence
+# MAIN PAPER FIGURE#
+dd.nf.overall.plt <-ggplot(no.stock.gam.nf.dat , aes(x=prop.abund,y=exp(fit))) + 
+                                geom_point(data = dd.dat,aes(x=prop.abund,y=lam.no.fish),size=2,alpha=0.1) +  
+                                geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI)),alpha=0.5,linewidth=0,fill=u.colors[1])+
+                                geom_line(color=u.colors[1],linewidth=1) + 
+                                xlab("") + 
+                                scale_y_log10(name = "Lambda(F=0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
+                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
+                                theme(legend.text=element_text(size=8),
+                                      legend.spacing.y = unit(-0.1, 'cm'),
+                                      legend.title = element_blank(),
+                                      axis.text.x = element_blank()) + 
+                                 guides(color = guide_legend(ncol=1,byrow=T),
+                                        shape = guide_legend(ncol=1,byrow=T))
+
+# MAIN PAPER FIGURE#
+dd.fish.overall.plt <- ggplot(no.stock.gam.fish.dat, aes(x=prop.abund,y=exp(fit))) + 
+                                geom_point(data = dd.dat,aes(x=prop.abund,y=lam.fish),size=2,alpha=0.1) +  
+                                geom_line(color=u.colors[2],linewidth=2) + 
+                                geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI)),alpha=0.5,fill=u.colors[2])+
+                                xlab("") + 
+                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
+                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed',linewidth=1.5)+
+                                theme(legend.text=element_text(size=8),
+                                      legend.spacing.y = unit(-0.1, 'cm'),
+                                      legend.title = element_blank(),
+                                      axis.text.x = element_blank()) + 
+                                 guides(color = guide_legend(ncol=1,byrow=T),
+                                        shape = guide_legend(ncol=1,byrow=T))
+
+# Main Paper Figure Density dependence with and without fishing, effectively a zoomed in version of the above.
+colrs <- u.colors
+t.smooth <- rbind(no.stock.gam.fish.dat,no.stock.gam.nf.dat)
+dd.fish.nf.plt <- ggplot(t.smooth, aes(x=prop.abund,y=exp(fit),group=Scenario,color=Scenario,fill=Scenario)) + 
+                                 geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI),group=Scenario,fill=Scenario),alpha=0.50,linewidth=0)+
+                                 geom_line(linewidth=1.5) +
+                                 geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
+                                 scale_fill_manual(values = colrs) + scale_color_manual(values = colrs) +
+                                 scale_x_continuous(name = "Proportion of maximum abundance",breaks = seq(0,1,by=0.1)) + 
+                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
+                                 theme(legend.position = c(0.9,0.75))
+
+dd.overall.combo <- plot_grid(dd.nf.overall.plt,dd.fish.overall.plt,dd.fish.nf.plt,nrow=3)
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_overall_",what.2.tune,".png"),dd.overall.combo,base_width = 10,base_height = 10)
+
+new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(y=lambda,interaction(group,G.Species.short),color=group)) +
+                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
+                                           scale_x_discrete(NULL, guide = "axis_nested") +
+                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
+                                           geom_hline(yintercept = 1,linetype='dashed') +
+                                           facet_manual(vars(Area.long),design=mat,scales='free_x')
+
+# Density dependence by stock 
+cols.gam <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
+pty.gam <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
+# Doing this manually because the ordered factor wasn't working... annoying...
+mat <- matrix(c(2, 2,13,13, 5, 5, 9, 9,
+                3, 3,12,12, 6, 6, 8, 8,
+               NA,NA,10,10,11,11,NA,NA,
+               NA,7, 7, 4, 4, 1, 1, NA),
+                4, 8, byrow = TRUE)
+
+dd.stocks.nf.plt <- ggplot(pred.dd.stock.gam.ss.nf,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=G.Species,shape=G.Species)) + 
+                                geom_line() + 
+                                geom_point(data = thin.pred.nf,size=2) +  
+                                xlab("Proportion of maximum abundance") + 
+                                scale_y_log10(name = "Lambda (F=0)",breaks = log_breaks(n=10)) +
+                                geom_ribbon(aes(ymin=lower,ymax=upper,color=G.Species),alpha=0.10,linewidth=0)+
+                                facet_manual(vars(Area.long),design=mat,scales='free_x')+
+                                #facet_wrap(~Area.long)  +
+                                scale_shape_manual(values=pty.gam) +
+                                scale_color_manual(values = cols.gam) + 
+                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
+                                theme(legend.text=element_text(size=8),
+                                      legend.spacing.y = unit(-0.1, 'cm'),
+                                      legend.title = element_blank(),
+                                      axis.text.x = element_text(size=7)) + 
+                                 guides(color = guide_legend(ncol=1,byrow=T),
+                                        shape = guide_legend(ncol=1,byrow=T))
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"),dd.stocks.nf.plt,base_width = 10,base_height = 10)
+
+mat <- matrix(c(2, 2,13,13, 5, 5, 9, 9,
+                3, 3,12,12, 6, 6, 8, 8,
+               NA,NA,10,10,11,11,NA,NA,
+               NA,7, 7, 4, 4, 1, 1, NA),
+                4, 8, byrow = TRUE)
+
+# MAIN PAPER FIGURE#
+dd.stocks.fish.plt <- ggplot(pred.dd.stock.gam.ss.fish,aes(x=prop.abund,y=lam.fish,group=Stock.short,color=G.Species,shape=G.Species)) + 
+                                geom_line() + 
+                                geom_point(data = thin.pred.fish,size=2) +  
+                                geom_ribbon(aes(ymin=lower,ymax=upper,color=G.Species),alpha=0.10,linewidth=0)+
+                                xlab("Proportion of maximum abundance") + 
+                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10)) +
+                                facet_manual(vars(Area.long),design=mat,scales='free_x')+
+                                #facet_wrap(~Area.long)  +
+                                scale_shape_manual(values=pty.gam) +
+                                scale_color_manual(values = cols.gam) + 
+                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
+                                theme(legend.text=element_text(size=8),
+                                      legend.spacing.y = unit(-0.1, 'cm'),
+                                      legend.title = element_blank(),
+                                      axis.text.x = element_text(size=7)) + 
+                                 guides(color = guide_legend(ncol=1,byrow=T),
+                                        shape = guide_legend(ncol=1,byrow=T))
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_fish_stocks_",what.2.tune,".png"),dd.stocks.fish.plt,base_width = 10,base_height = 10)
+
+# Lifetime reproductive success 
+mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
+                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
+                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
+                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
+                4, 10, byrow = TRUE)
+r0.boxplt.6 <- ggplot(pop.dam.all.6) + geom_boxplot(aes(y=R0.opt,interaction(group,Stock.no.species),color=group))  + 
+                                       scale_x_discrete(NULL, guide = "axis_nested") + scale_y_log10(name = "Lifetime Reproductive Output")+
+                                       geom_hline(yintercept = 1,linetype='dashed',color='blue')+
+                                       facet_manual(vars(G.Species),design=mat,scales='free_x')+
+                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
+                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"),r0.boxplt.6,base_width = 19,base_height = 15)
+
+mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
+                7, 7, rep(8,9),
+                9, 9, rep(10,7),11,11),
+                3, 11, byrow = TRUE)
+
+r0.boxplot.others <- ggplot(pop.dam.all.others) +   geom_boxplot(aes(y=R0.opt,interaction(group,G.Species.short),color=group))  + 
+                                                    scale_x_discrete(NULL, guide = "axis_nested") + 
+                                                    scale_y_log10(name = "Lifetime Reproductive Output")+
+                                                    geom_hline(yintercept = 1,linetype='dashed',color='blue')+
+                                                    facet_manual(vars(Area.long),design=mat,scales='free')+
+                                                    theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
+                                                          plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"),r0.boxplot.others,base_width = 15,base_height = 10)
 
@@
 r0.heatmap <- cowplot::plot_grid(r0.heatmap.pac,r0.heatmap.nw,r0.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-r0.heatmap
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_",what.2.tune,".png"),r0.heatmap,base_width = 20,base_height = 17)
-
-# FIX: A density dependence figure, this isn't perfect as the lambda's aren't quiet lined up right because of recruitment offset
-# That said, recruitment in these cases also integrates all processes that happens from birth-recruitment
-# So maybe it is kinda reasonable?
-#
-
-# First need to get the abundance and lambdas with no fishing into one object.
-ft.tmp <- for.tunes |> collapse::fselect(year,Stock,vpa.abund,est.abund)
-dd.dat <- left_join(res.lambda.fin,ft.tmp,by=c('year','Stock'))
-# Now I need to get a relative abundance for each stock...
-dd.dat <- dd.dat |> collapse::fgroup_by(Stock) |> collapse::fmutate(max.abund = max(est.abund,na.rm=T))
-dd.dat <- data.frame(dd.dat)
-dd.dat$prop.abund <- dd.dat$est.abund/dd.dat$max.abund
-dd.dat.six <- dd.dat |>collapse::fsubset(Species %in% six.species)
-
-ggplot(dd.dat) + geom_point(aes(x=prop.abund,y=lam.no.fish-1)) + xlab("Proportion of Maximum Abundance") + ylab("r (no fishing)")
-
-# Density dependence by Species
-ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
-                                                   geom_smooth(method="gam") + 
-                                                   geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-                                                   scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-                                                   scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) #+
-                                                   #scale_color_manual(values = colrs)
-# Density dependence by stock
-ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Stock.short,group=Stock.short)) + geom_point() + 
-                                                   geom_smooth(method="lm",se = F) + 
-                                                   geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-                                                   scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-                                                   scale_y_log10(name = "lambda (no fishing)", limits=c(0.4,2),
-                                                                 breaks = seq(0.4,2,by=0.1)) +
-                                                   theme(legend.position = 'none')
-
-dd.dat.no.bigs <- dd.dat |> collapse::fsubset(lam.no.fish < 2)
-
-ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish)) + geom_point() + 
-                                                    geom_smooth(method="gam") + 
-                                                   geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-                                                   scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-                                                   scale_y_continuous(name = "lambda (no fishing)")
-
-ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + geom_point() + 
-                                                    geom_smooth(method="lm",se=F) + 
-                                                   geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-                                                   scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,2,by=0.1))+
-                                                   scale_y_log10(name = "lambda (no fishing)")
-
-# how about our big 6
-colrs <- c("blue","black","firebrick2","orange",'grey50','grey90')
-ggplot(dd.dat.six,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
-                                                    geom_smooth(method="gam") + 
-                                                   geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-                                                   scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-                                                   scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) +
-                                                   scale_color_manual(values = colrs)
-
-dd.dat.six.no.bigs <- dd.dat.six |> collapse::fsubset(lam.no.fish < 2)
-
-ggplot(dd.dat.six.no.bigs,aes(x=prop.abund,y=lam.no.fish-1,color=Species,group=Species)) + geom_point() + 
-                                                    geom_smooth(method="gam") + 
-                                                   geom_hline(yintercept = 0,linewidth=2,linetype='dashed',color='blue') +
-                                                   scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-                                                   scale_y_continuous(name = "r (no fishing)", breaks = seq(-1,1,by=0.2)) +
-                                                   scale_color_manual(values = colrs)
-
-just.bigs <- dd.dat  |> collapse::fsubset(lam.no.fish > 2) 
-sum(table(just.bigs$Stock.short)) # 48 of 68 are Haddock or cod. 13 of remaining 20 are small low trophic species
-
-dd.dat$lam.ratio <- dd.dat$lam.org.no.fish/dd.dat$lam.no.fish
-dd.dat$lam.ratio.z <- dd.dat$lam.org.fish/dd.dat$lam.fish
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_nf_",what.2.tune,".png"),r0.heatmap,base_width = 20,base_height = 17)
+
+r0.heatmap.ne.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
+                                    xlab("") + ylab("")+
+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
+                                    geom_tile() + 
+                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
+                                                        discrete=FALSE,trans='log') + 
+                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
+
+r0.heatmap.nw.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
+                                    xlab("") + ylab("")+
+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                                    geom_tile() + 
+                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
+                                                        discrete=FALSE,trans='log') + 
+                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
+
+r0.heatmap.pac.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
+                                     xlab("") + ylab("")+
+                                     facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                                     geom_tile() + 
+                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
+                                                        discrete=FALSE,trans='log') + 
+                                     theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
+                                           legend.key.width = unit(3,'cm'))
+
+r0.heatmap.fish <- cowplot::plot_grid(r0.heatmap.pac.fish,r0.heatmap.nw.fish,r0.heatmap.ne.fish,nrow = 3,rel_heights = c(3,4,10))
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_fish_",what.2.tune,".png"),r0.heatmap.fish,base_width = 20,base_height = 17)
+
+# Generation length
+mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
+                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
+                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
+                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
+                4, 10, byrow = TRUE)
+gen.boxplt.6 <- ggplot(pop.dam.all.6) +
+                            geom_boxplot(aes(y=gen.len.opt,interaction(group,Stock.no.species),color=group))  + 
+                            scale_x_discrete(NULL, guide = "axis_nested") +
+                            scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
+                             facet_manual(vars(G.Species),design=mat,scales='free_x')+
+                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
+                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"),gen.boxplt.6,base_width = 19,base_height = 15)
+
+# Then the generation length for others.
+mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
+                7, 7, rep(8,9),
+                9, 9, rep(10,7),11,11),
+                3, 11, byrow = TRUE)
+
+gen.boxplt.others <- ggplot(pop.dam.all.others) +
+                            geom_boxplot(aes(y=gen.len.opt,interaction(group,G.Species.short),color=group))  + 
+                            scale_x_discrete(NULL, guide = "axis_nested") +
+                            scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
+                            facet_manual(vars(Area.long),design=mat,scales='free')+
+                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
+                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"),gen.boxplt.others,base_width = 15,base_height = 10)
+
+gen.heatmap.ne <- ggplot(pop.dam |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
+                                              xlab("") + ylab("")+  
+                                              facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
+                                              geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
+                                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
+
+gen.heatmap.nw <- ggplot(pop.dam |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
+
+gen.heatmap.pac <- ggplot(pop.dam |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
+                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
+                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
+                                  legend.key.width = unit(3,'cm'))
+
+gen.heatmap <- cowplot::plot_grid(gen.heatmap.pac,gen.heatmap.nw,gen.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_nf_",what.2.tune,".png"),gen.heatmap,base_width = 15,base_height = 10)
+
+gen.heatmap.ne.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
+                                              xlab("") + ylab("")+  
+                                              facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
+                                              geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
+                                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
+
+gen.heatmap.nw.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
+
+gen.heatmap.pac.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
+                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
+                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
+                                  legend.key.width = unit(3,'cm'))
+
+gen.heatmap.fish <- cowplot::plot_grid(gen.heatmap.pac.fish,gen.heatmap.nw.fish,gen.heatmap.ne.fish,nrow = 3,rel_heights = c(3,4,10))
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_fish_",what.2.tune,".png"),gen.heatmap.fish,base_width = 15,base_height = 10)
+
+dub.time.summary <- dub.time.summary |> collapse::fsubset(year %in% 1:50) |>
+                            collapse::roworder(G.Species,LME,Area.broad) |>
+                            collapse::fmutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
+
+dub.heatmap.gad <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Gadiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
+                            xlab("") + ylab("")+                                    
+                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.45, "cm"),
+                                  legend.key.width = unit(3,'cm'))
+
+dub.heatmap.pl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Pleuronectiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
+                            xlab("") + ylab("")+                                    
+                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"))
+
+dub.heatmap.cl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Clupeiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
+                            xlab("") + ylab("")+
+                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.35, "cm"),
+                                  legend.key.width = unit(3,'cm'))
+
+dub.heatmap.per <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Perciformes"), aes(x=year, y=Stock.short, fill= prop)) + 
+                            xlab("") + ylab("")+
+                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2, "cm"),
+                                  legend.key.width = unit(3,'cm'))
+
+dub.heatmap.scom <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Scombriformes"), aes(x=year, y=Stock.short, fill= prop)) + 
+                            xlab("") + ylab("")+
+                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2.1, "cm"),
+                                  legend.key.width = unit(3,'cm'))
+
+dub.heatmap.scorp <- ggplot(dub.time.summary |> collapse::fsubset(Order %in% "Scorpaeniformes "), aes(x=year, y=Stock.short, fill= prop)) + 
+                            xlab("") + ylab("")+
+                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + 
+                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.5, "cm"),
+                                  legend.key.width = unit(3,'cm'))
+
+dub.heatmap <- cowplot::plot_grid(dub.heatmap.gad,dub.heatmap.pl,dub.heatmap.cl,dub.heatmap.per,dub.heatmap.scom,dub.heatmap.scorp,
+                                  nrow = 6,rel_heights = c(39,20,11,4,3,3))
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"),dub.heatmap,base_width = 20,base_height = 20)
+
+# Doubling Time Figure 1
+dub.ts.plt <- ggplot(n.dub,aes(x=years,y=count)) + 
+                    geom_line() + 
+                    geom_hline(yintercept = length(Stocks),linetype="dashed") + 
+                    xlab("") + ylab("Number of Stocks")
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_time_series_",what.2.tune,".png"),dub.ts.plt,base_width = 10,base_height = 10)
+
+# Doubling time and variability
+
+# Is there a relationship between median and sd?
+colrs.cat <- c("blue","black","orange")
+pts.cat <- 21:23
+sd.rec.plt <- ggplot(lam.sd.p.rec, aes(y=lam.no.fish.med,x=lam.no.fish.sd,color=prop.cat,group=prop.cat)) + 
+                       geom_point(size =3,aes(shape=prop.cat,fill=prop.cat)) + 
+                       geom_hline(yintercept=1,linetype="dashed") + 
+                       scale_y_continuous(name="median Lambda") + scale_x_continuous(name="standard deviation Lambda") +
+                       scale_color_manual(values=colrs.cat) + scale_fill_manual(values=colrs.cat) +  
+                       scale_shape_manual(values=pts.cat) + theme(legend.title = element_blank())
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"),sd.rec.plt,base_width = 10,base_height = 10)
+
+```
+
+```{r the-others,include=F,echo=F,message=F,warning=F}
+#             
+# 
+# dub.heatmap.cod <- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "G.
+morhua"), aes(x=year, y=Stock.no.species, fill= prop)) + xlab("") + ylab("")+                                     facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") +
+#                             geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + scale_x_continuous(labels=NULL) +
+#                             theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
+#                                   legend.key.width = unit(3,'cm'))
+# 
+# dub.heatmap.herring<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "C. harengus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+#                               xlab("") + ylab("")+                                    
+#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
+# 
+# dub.heatmap.haddock<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "M. aeglefinus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+#                               xlab("") + ylab("")+                                    
+#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.125, "cm"))
+# 
+# dub.heatmap.virens<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. virens"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+#                               xlab("") + ylab("")+                                    
+#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.4, "cm"))
+# 
+# dub.heatmap.solea<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "S. solea"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+#                               xlab("") + ylab("")+                                    
+#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
+#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
+# 
+# dub.heatmap.platessa<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. platessa"), aes(x=year, y=Stock.no.species, fill= prop)) + 
+#                               xlab("") + ylab("")+                                    
+#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous() +
+#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
+#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
+# 
+# 
+# 
+# dub.heatmap.sp6 <- cowplot::plot_grid(dub.heatmap.cod,dub.heatmap.herring,dub.heatmap.haddock,
+#                                  dub.heatmap.virens, dub.heatmap.solea,dub.heatmap.platessa,nrow = 6,rel_heights = c(14,9,8,5,5,4))
+# dub.heatmap.sp6
+# 
+# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_sp6_",what.2.tune,".png"),dub.heatmap.sp6,base_width = 20,base_height = 17)
+# 
+# 
+# # What about a plot of the sd of lamda by stock
+# #colrs.sd <- rep(rep(c("black","blue","orange",'grey'),3),20)
+# #pty.sd <- rep(c(rep(21,4),rep(4,4),rep(9,4)),20)
+# 
+# 
+# # Same plot for the not 6 species
+# 
+# # lam.sd.other.plt <- ggplot(res.lambda.fin |> collapse::fsubset(!Species %in% six.species)) + 
+# #                                        geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
+# #                                        scale_y_log10("sd(lambda)",limits=c(0.05,1.5)) +
+# #                                        scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
+# #                                        theme(axis.text.x = element_text(angle =45,hjust=1),
+# #                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+# # lam.sd.other.plt
+# 
+# 
+# 
+# 
+# # Doubling Times
+# 
+# 
+# # Generation length
+# 
+# # Main text figure!!
+# new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Area.long),color=group)) +
+#                                            #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
+#                                            scale_x_discrete(NULL, guide = "axis_nested") +
+#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
+#                                            geom_hline(yintercept = 1,linetype='dashed') +
+#                                            facet_wrap(~G.Species,scales='free')+
+#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
+#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+# 
+# # The other stocks, plotting these by area
+# # Main Text FIGURE!
+# # More data
+# 
+# 
+# ################### Supplemental Figures################### Supplemental Figures################### Supplemental Figures################### Supplemental 
+# 
+# 
+# 
+# # Time series of lambdas....
+# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
+# #col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
+# pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
+# #pty <- rep(rep(c(21:23),5),20)
+# 
+# lambda.ts.plt <- ggplot(res.lambda.final.6,aes(y=lam.fish,x=year,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
+#                             geom_point(size=4) +
+#                             geom_smooth(method='gam',formula = y ~ s(x, bs = "cs", fx = TRUE, k = 5),se=F) + 
+#                             #scale_y_log10(name = "lambda") +
+#                             facet_wrap(~G.Species,scales='free_y') +
+#                             scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
+#                             scale_fill_manual(name = "Stock",values = col.try)+
+#                             guides(colour = guide_legend(ncol = 1))+
+#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm'))
+# #lambda.ts.plt
+# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_timeseries_6_",what.2.tune,".png"),lambda.ts.plt,base_width = 12,base_height = 10)
+# 
+# 
+# lambda.dec.plt <- ggplot(res.lambda.final.6,aes(y=med.lam,x=as.factor(decade))) +
+#                             geom_boxplot() + scale_y_log10()+
+#                             xlab("Decade") + ylab("Lambda") + 
+#                             geom_point(aes(x=as.factor(decade),y=lm.spec.mn),color='blue',shape=8,fill='blue')+
+#                             #scale_x_continuous(breaks=seq(1940,2020,by=10))+
+#                             geom_hline(yintercept = 1,linetype='dashed') +
+#                             facet_wrap(~G.Species,scales='free_y') 
+# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_by_decade_6_",what.2.tune,".png"),lambda.dec.plt,base_width = 12,base_height = 12)
+# 
+#
+
+# ggplot(dd.dat) + geom_point(aes(x=prop.abund,y=lam.no.fish-1)) + xlab("Proportion of Maximum Abundance") + ylab("r (no fishing)")
+# 
+# # Density dependence by Species
+# ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
+#                                                    geom_smooth(method="gam") + 
+#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
+#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
+#                                                    scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) #+
+#                                                    #scale_color_manual(values = colrs)
+# # Density dependence by stock
+# ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Stock.short,group=Stock.short)) + geom_point() + 
+#                                                    geom_smooth(method="lm",se = F) + 
+#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
+#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
+#                                                    scale_y_log10(name = "lambda (no fishing)", limits=c(0.4,2),
+#                                                                  breaks = seq(0.4,2,by=0.1)) +
+#                                                    theme(legend.position = 'none')
+# 
+# 
+# 
+# 
+# ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish)) + geom_point() + 
+#                                                     geom_smooth(method="gam") + 
+#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
+#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
+#                                                    scale_y_continuous(name = "lambda (no fishing)")
+# 
+# ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + geom_point() + 
+#                                                     geom_smooth(method="lm",se=F) + 
+#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
+#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,2,by=0.1))+
+#                                                    scale_y_log10(name = "lambda (no fishing)")
+# 
+# 
+# # how about our big 6
+# colrs <- c("blue","black","firebrick2","orange",'grey50','grey90')
+# ggplot(dd.dat.six,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
+#                                                     geom_smooth(method="gam") + 
+#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
+#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
+#                                                    scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) +
+#                                                    scale_color_manual(values = colrs)
+# 
+# 
+# ggplot(dd.dat.six.no.bigs,aes(x=prop.abund,y=lam.no.fish-1,color=Species,group=Species)) + geom_point() + 
+#                                                     geom_smooth(method="gam") + 
+#                                                    geom_hline(yintercept = 0,linewidth=2,linetype='dashed',color='blue') +
+#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
+#                                                    scale_y_continuous(name = "r (no fishing)", breaks = seq(-1,1,by=0.2)) +
+#                                                    scale_color_manual(values = colrs)
+
+# Other things I did just randomly scattered here
+
+# 
+# #hmm <- merge(tst,res.lambda.final.6,by="Stock")
+# plot(res.lambda.fin$lam.fish.med ~ res.lambda.fin$lam.fish.mn)
+# # So this is lambda with fishing included
+# lambda.plt <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.no.fish,x=Stock.no.species))  + 
+#                                            geom_point(aes(y=lam.no.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
+#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
+#                                            geom_hline(yintercept = 1,linetype='dashed') +
+#                                            facet_wrap(~G.Species,scales='free')+
+#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
+#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+# 
+# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_no_fishing_6_",what.2.tune,".png"),lambda.plt,base_width = 12,base_height = 10)
+# 
+# # With fishing
+# lambda.plt.fish <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.fish,x=Stock.no.species))  + 
+#                                            geom_point(aes(y=lam.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
+#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
+#                                            geom_hline(yintercept = 1,linetype='dashed') +
+#                                            facet_wrap(~G.Species,scales='free')+
+#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
+#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+# 
+# 
+# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_with_fishing_6_",what.2.tune,".png"),lambda.plt.fish,base_width = 12,base_height = 10)
+# 
+# 
+# 
+# new.lam.plt <- ggplot(res.lambda.fin.long) + geom_boxplot(aes(y=lambda,interaction(group,Order),color=group)) +
+#                                            #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
+#                                            scale_x_discrete(NULL, guide = "axis_nested") +
+#                                            #xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
+#                                            #geom_hline(yintercept = 1,linetype='dashed') +
+#                                            facet_wrap(~Area.long,scales='free')+
+#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
+#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+# 
+# 
+# # The final option I have is to do what I did before and use the bin props
+# We can then do a much more ANOVA kinda analysis, drat this doesn't converge..., estimate the 
+#mod.dd.bins.stock <- glmer(lam.no.fish ~ prop.bin + (1+prop.bin|Stock),data=dd.dat,family=gaussian(link='log'))
+# so go to lmer and log transform... and it is a singular fit
+#mod.dd.bins.stock <- lmer(lam.no.fish ~ prop.bin + (1+prop.bin|Stock),data=dd.dat)
+# So is an intercept model of any real use?
+# mod.dd.bins.stock <- lmer(log(lam.no.fish) ~ prop.bin + (1+prop.bin|Stock.short),data=dd.dat)
+# # A non-random effect model does work with the interaction... I'd much rather lmer....
+# #mod.dd.bins.stock <- lm(lam.no.fish ~ prop.bin*Stock,data=dd.dat)
+# summary(mod.dd.bins.stock)
+# #Residuals, nah, still suck, just some crazy outliers...
+# plot(mod.dd.bins.stock)
+# # Normality = terrible...
+# qqnorm(residuals(mod.dd.bins.stock))
+# qqline(residuals(mod.dd.bins.stock))
+# # So we can predict this ANOVA thing...
+# pred.dd.stock.bins <- expand.grid(prop.bin = unique(dd.dat$prop.bin),
+#                                          #Species=unique(dd.dat$Species),
+#                                          Stock.short=unique(dd.dat$Stock.short))
+# tmp <- predict(mod.dd.bins.stock, pred.dd.stock.bins, type = 'response', se.fit = TRUE) 
+# pred.dd.stock.bins$lam.no.fish   <- exp(tmp$fit)
+# pred.dd.stock.bins$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
+# pred.dd.stock.bins$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
+# # Now to do fun things I need the meta data on the pred dataframe
+# pred.dd.stock.bins <- left_join(pred.dd.stock.bins,meta.sub,by="Stock.short")
+# # Now a problem here is that this includes estimates for bins in which we don't have data.
+# # So we do want to get rid of those
+# real.bins <- unique(paste(dd.dat$Stock.short,"_",dd.dat$prop.bin))
+# # All the bins in the predict object with same names same name...
+# pred.dd.stock.bins$bin.combos <- paste(pred.dd.stock.bins$Stock.short,"_",pred.dd.stock.bins$prop.bin)
+# # Now toss all the predicted bins without data.
+# pred.dd.stock.bins <- pred.dd.stock.bins |> collapse::fsubset(bin.combos %in% real.bins)
+# 
+# # By region
+# cols.1 <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
+# #col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
+# pty.1 <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
+# ggplot(pred.dd.stock.bins,aes(x=prop.bin,y=lam.no.fish,group=Stock.short,color=G.Species)) + 
+#                                 geom_point(aes(shape=G.Species),size=2) + geom_line()  + xlab("Proportion of maximum abundance") + 
+#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
+#                                 facet_wrap(~Area.long)  +
+#                                 scale_shape_manual(values=pty.1) +
+#                                 scale_color_manual(values = cols.1) + 
+#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
+#                                 theme(legend.text=element_text(size=8),
+#                                       legend.spacing.y = unit(-0.1, 'cm'),
+#                                       legend.title = element_blank(),
+#                                       axis.text.x = element_text(size=7)) + 
+#                                  guides(color = guide_legend(ncol=1,byrow=T),
+#                                         shape = guide_legend(ncol=1,byrow=T))
+# 
+# # By Species
+# ggplot(pred.dd.stock.bins,aes(x=prop.bin,y=lam.no.fish,group=Stock.short,color=Area.long)) + 
+#                                 geom_point(aes(shape=Area.long)) + geom_line()  + xlab("Proportion of maximum abundance") + 
+#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
+#                                 facet_wrap(~Order)  +
+#                                 scale_shape_manual(values=pty.1) +
+#                                 scale_color_manual(values = cols.1) + 
+#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
+#                                 theme(legend.text=element_text(size=8),
+#                                       legend.spacing.y = unit(-0.1, 'cm'),
+#                                       legend.title = element_blank(),
+#                                       axis.text.x = element_text(size=7)) + 
+#                                  guides(color = guide_legend(ncol=1,byrow=T),
+#                                         shape = guide_legend(ncol=1,byrow=T))
+# 
+# # No fish vs fish lambda, note that DD is weaker when we account for fishing, that seems a fun result to talk about!
+# 
+# mod.dd.overall.gam.nf <- lm(log(lam.no.fish) ~ (prop.abund),data=dd.dat)
+# mod.dd.overall.gam.fish <- lm(log(lam.fish) ~ (prop.abund),data=dd.dat)
+# 
+# 
+# pred.dd.overall.bins.nf <- data.frame(prop.abund = seq(0,1,length.out=500),group = "F = 0")
+# pred.dd.overall.bins.fish <- data.frame(prop.abund = seq(0,1,length.out=500),group = "F > 0")
+# tmp <- predict(mod.dd.overall.gam.nf, pred.dd.overall.bins, type = 'response', se.fit = TRUE) 
+# tmp.fish <- predict(mod.dd.overall.gam.fish, pred.dd.overall.bins, type = 'response', se.fit = TRUE) 
+# pred.dd.overall.bins.nf$lam   <- exp(tmp$fit)
+# pred.dd.overall.bins.nf$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
+# pred.dd.overall.bins.nf$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
+# 
+# pred.dd.overall.bins.fish$lam   <- exp(tmp.fish$fit)
+# pred.dd.overall.bins.fish$lower <- exp(tmp.fish$fit - 1.96 * tmp.fish$se.fit)
+# pred.dd.overall.bins.fish$upper <- exp(tmp.fish$fit + 1.96 * tmp.fish$se.fit)
+# 
+# pred.dd.overall <- rbind(pred.dd.overall.bins.fish,pred.dd.overall.bins.nf)
+# 
+# ggplot(pred.dd.overall,aes(y=lam,x=prop.abund,group=group,color=group)) + 
+#                                                   geom_line(linewidth=2) + 
+#                                                   geom_ribbon(aes(ymin=lower,ymax=upper),alpha=0.2) + 
+#                                                   geom_hline(yintercept=1,linetype='dashed') + 
+#                                                   xlab("Proportion of Maximum Abundance") + ylab("Lambda")
+# 
+# # OK, so if we compare the 40-60 bin with the 80-100 bin we should see the lambda's in the 40-60 bin are higher...
+# 
+# res.40.60 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("40-60%"))
+# names(res.40.60)[names(res.40.60) == 'lam.no.fish'] <- "lam.40.60"
+# res.80.100 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("80-100%"))
+# names(res.80.100)[names(res.80.100) == 'lam.no.fish'] <- "lam.80.100"
+# 
+# tst <- left_join(res.40.60,res.80.100, by = names(res.40.60)[c(2,6:26)])
+# tst$diff <- tst$lam.40.60 - tst$lam.80.100
+# 
+# hist(tst$diff)
+# 
+# res.lt.10 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("< 10%"))
+# names(res.lt.10)[names(res.lt.10) == 'lam.no.fish'] <- "lam.lt.10"
+# 
+# tst <- left_join(res.40.60,res.lt.10, by = names(res.40.60)[c(2,6:26)])
+# tst$diff <- tst$lam.lt.10 - tst$lam.40.60
+# 
+# hist(tst$diff)
+# 
+# res.10.20 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("10-20%"))
+# names(res.10.20)[names(res.10.20) == 'lam.no.fish'] <- "lam.10.20"
+# 
+# tst <- left_join(res.40.60,res.10.20, by = names(res.40.60)[c(2,6:26)])
+# tst$diff <- tst$lam.10.20 - tst$lam.40.60
+# 
+# hist(tst$diff)
+# 
+# 
+# res.20.30 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("20-30%"))
+# names(res.20.30)[names(res.20.30) == 'lam.no.fish'] <- "lam.20.30"
+# 
+# tst <- left_join(res.40.60,res.20.30, by = names(res.40.60)[c(2,6:26)])
+# tst$diff <- tst$lam.20.30 - tst$lam.40.60
+# 
+# hist(tst$diff)
+# 
+# res.30.40 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("30-40%"))
+# names(res.30.40)[names(res.30.40) == 'lam.no.fish'] <- "lam.30.40"
+# 
+# tst <- left_join(res.40.60,res.30.40, by = names(res.40.60)[c(2,6:26)])
+# tst$diff <- tst$lam.30.40 - tst$lam.40.60
+# 
+# hist(tst$diff)
+
+# 
+# 
+# dd.dat.no.bigs <- dd.dat |> collapse::fsubset(lam.no.fish < 2)
+# dd.dat.six.no.bigs <- dd.dat.six |> collapse::fsubset(lam.no.fish < 2)
+# just.bigs <- dd.dat  |> collapse::fsubset(lam.no.fish > 2) 
+# sum(table(just.bigs$Stock.short)) # 48 of 68 are Haddock or cod. 13 of remaining 20 are small low trophic species
+# 
+# dd.dat$lam.ratio <- dd.dat$lam.org.no.fish/dd.dat$lam.no.fish
+# dd.dat$lam.ratio.z <- dd.dat$lam.org.fish/dd.dat$lam.fish
 # So the original lambda tended to be somewhere between 7 and 14% higher, depending on me(di)an choice.
 # Could be way off in some years for a few species (Haddock, Cod, Sand lance, horse makerel, pilchard(sardine)... interesting... )
-summary(dd.dat$lam.ratio)
-summary(dd.dat$lam.ratio.z)
-ggplot(dd.dat,aes(y=lam.ratio,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
-ggplot(dd.dat,aes(y=lam.ratio.z,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
-# Other figures....
+# summary(dd.dat$lam.ratio)
+# summary(dd.dat$lam.ratio.z)
+# ggplot(dd.dat,aes(y=lam.ratio,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
+# ggplot(dd.dat,aes(y=lam.ratio.z,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
+
+# Playing around to look at explanations for what we see, looked by LME, low and high stocks, but no smoking guns!
+# low.stocks <- unique(dd.dat$Stock.short[dd.dat$prop.abund <= 0.1])
+# dd.lows <- dd.dat |> collapse::fsubset(Stock.short %in% low.stocks)
+# dd.highs <- dd.dat |> collapse::fsubset(!Stock.short %in% low.stocks)
+# mod.dd.stock.gam.lows <- gam(log(lam.no.fish) ~ s(prop.abund,k=4) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.lows )
+# mod.dd.stock.gam.highs <- gam(log(lam.no.fish) ~ s(prop.abund,k=4) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.highs )
+# 
+# pred.dd.stock.gam.tst <- expand.grid(prop.abund = seq(0, 1, length.out = 50),
+#                                          Stock.short = c("Overall",unique(dd.highs$Stock.short)))
+# 
+# tmp <- predict(mod.dd.stock.gam.highs, pred.dd.stock.gam.tst, type = 'response', se.fit = TRUE) 
+# pred.dd.stock.gam.tst$lam.no.fish   <- exp(tmp$fit)
+# pred.dd.stock.gam.tst$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
+# pred.dd.stock.gam.tst$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
+# 
+# ggplot(pred.dd.stock.gam.tst |> collapse::fsubset(Stock.short=='Overall'), aes(x=prop.abund,y=lam.no.fish)) + 
+#                                 geom_point(data = hmm,aes(x=prop.abund,y=lam.no.fish),size=2,alpha=0.1) +  
+#                                 geom_line(color='blue',linewidth=2) + 
+#                                 xlab("Proportion of maximum abundance") + 
+#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
+#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
+#                                 theme(legend.text=element_text(size=8),
+#                                       legend.spacing.y = unit(-0.1, 'cm'),
+#                                       legend.title = element_blank(),
+#                                       axis.text.x = element_text(size=7)) + 
+#                                  guides(color = guide_legend(ncol=1,byrow=T),
+#                                         shape = guide_legend(ncol=1,byrow=T))
+# 
+# 
+# ggplot(pred.dd.stock.gam.tst,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short,shape=Stock.short)) + 
+#                                 geom_line() + 
+#                                 #geom_point(data = thin.pred,size=2) +  
+#                                 xlab("Proportion of maximum abundance") + 
+#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
+#                                 #facet_wrap(~Area.long)  +
+#                                 #scale_shape_manual(values=pty.gam) +
+#                                 #scale_color_manual(values = cols.gam) + 
+#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
+#                                 theme(legend.text=element_text(size=8),
+#                                       legend.spacing.y = unit(-0.1, 'cm'),
+#                                       legend.title = element_blank(),
+#                                       axis.text.x = element_text(size=7)) + 
+#                                  guides(color = guide_legend(ncol=1,byrow=T),
+#                                         shape = guide_legend(ncol=1,byrow=T))
+
+# Is there any density dependence in fishing mortality??
+# dd.dat$mu <- dd.dat$removals/dd.dat$vpa.abund
+# dd.dat$fm <- -log(1-dd.dat$mu)
+# 
+# ggplot(dd.dat , aes(x=prop.abund,y=fm)) + 
+#                                 geom_point() + 
+#                                 geom_smooth(method = 'gam') + 
+#                                 scale_x_continuous(name="Proportion of Maximum Abundance") +
+#                                 scale_y__continuous(name = "Fishing Mortality (instantaneous)")
+# 
+# 
+# qqnorm(log(dd.dat$mu))
+# qqline(log(dd.dat$mu))
+# hist(log(dd.dat$mu))
+# 
+# fm.mod <- lm(log(fm)~prop.abund,data=dd.dat)
+# par(mfrow=c(2,2))
+# plot(fm.mod)
+# par(mfrow=c(1,1))
 
@@
 ```
+
+<!-- Here are the models that we ran but didn't end up using# -->
+<!-- Here are the models that we ran but didn't end up using# -->
+<!-- Here are the models that we ran but didn't end up using# -->
+<!-- Here are the models that we ran but didn't end up using# -->
+<!-- Here are the models that we ran but didn't end up using# -->
+<!-- Here are the models that we ran but didn't end up using# -->
+<!-- Here are the models that we ran but didn't end up using# -->
+
+```{r failed-models}
+
+# A density dependence model, start simple and build...
+# mod.dd.base <- lm(log(lam.no.fish) ~ prop.abund,data=dd.dat)
+# summary(mod.dd.base)
+# 
+# mod.dd.base.fish <- lm(log(lam.fish) ~ prop.abund,data=dd.dat)
+# summary(mod.dd.base.fish)
+# #ggplot(dd.dat, aes(y = lam.no.fish,x=prop.abund)) + geom_point() + geom_smooth(method = 'lm') + scale_y_log10() + geom_hline(yintercept = 1,color='firebrick2',linetype='dashed',linewidth=2)
+# 
+# 
+# # Residuals are nowhere near normal, the fit isn't a disaster but def have the old trumpet shape happening
+# par(mfrow=c(2,2))
+# plot(mod.dd.base)
+# par(mfrow=c(1,1))
+# # This mostly represents the above model...
+# ggplot(dd.dat, aes(y = lam.no.fish,x=prop.abund)) + 
+#                   geom_point() + 
+#                   geom_smooth(method = 'lm') + scale_y_log10() +
+#                   geom_hline(yintercept = 1,color='firebrick2',linetype='dashed',linewidth=2)
+# # What happens with a gam?
+# mod.dd.gam.base <- gam(log(lam.no.fish) ~ s(prop.abund),data=dd.dat)
+# summary(mod.dd.gam.base)
+# # Still see that the residuals are higher at low values
+# plot(residuals(mod.dd.gam.base) ~ dd.dat$prop.abund)
+# # not great...
+# plot(residuals(mod.dd.gam.base) ~ fitted(mod.dd.gam.base))
+# # What's the fit look like?
+# pred.dd.gam.base <- data.frame(prop.abund = seq(0, 1, length.out = 1000))
+# tmp <- predict(mod.dd.gam.base, dd.gam.base.pred, type = 'response', se.fit = TRUE) 
+# 
+# pred.dd.gam.base$lam.no.fish   <- exp(tmp$fit)
+# pred.dd.gam.base$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
+# pred.dd.gam.base$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
+# 
+# # So here's the game fit, I thnk it does do an ok job of showing that no much is happening below maybe 0.3, but then
+# # below 0.15 it starts increasing, suggesting general compensation, but we know the really high values matter here and are
+# # limited to a subset of the stocks, anywho we know the residuals suck, so moving on...
+# ggplot(dd.dat,aes(y=lam.no.fish,x=prop.abund)) + 
+#                   geom_point() + scale_y_log10() +
+#                   geom_ribbon(data=pred.dd.gam.base,aes(ymin=lower,ymax=upper,x=prop.abund),alpha=0.4) +
+#                   geom_line(data = pred.dd.gam.base,aes(y=lam.no.fish, x= prop.abund))
+#     
+# 
+# # What if we did a glm, Gamma with log-link seems a natural thing to try...
+# mod.dd.glm.gamma <- glm(lam.no.fish ~ prop.abund,data=dd.dat,family = Gamma(link='log'))
+# # What's that done...
+# summary(mod.dd.glm.gamma)
+# # Still some pretty gross shit going on here...
+# par(mfrow=c(2,2))
+# plot(mod.dd.glm.gamma)
+# par(mfrow=c(1,1))
+# # Now plot it...
+# pred.dd.glm.base <- data.frame(prop.abund = seq(0, 1, length.out = 1000))
+# tmp <- predict(mod.dd.glm.gamma, dd.gam.base.pred, type = 'response', se.fit = TRUE) 
+# 
+# pred.dd.glm.base$lam.no.fish   <- (tmp$fit)
+# pred.dd.glm.base$lower <- (tmp$fit - 1.96 * tmp$se.fit)
+# pred.dd.glm.base$upper <- (tmp$fit + 1.96 * tmp$se.fit)
+# # Pretty similar, though I think on the linear scale we see the 'rate' may be decreasing as we approach 0
+# # But still not a good model given the above
+# ggplot(dd.dat,aes(y=lam.no.fish,x=prop.abund)) + 
+#                   geom_point() + scale_y_log10() +
+#                   geom_ribbon(data=pred.dd.glm.base,aes(ymin=lower,ymax=upper,x=prop.abund),alpha=0.4) +
+#                   geom_line(data = pred.dd.glm.base,aes(y=lam.no.fish, x= prop.abund))
+#     
+# # Now what if we account for species in these and get an estimate for each species. 
+# # I think this should be done as a random effect, we'll start with linear mixed models and see what happens...
+# 
+# mod.dd.species.re <- lmer(log(lam.no.fish) ~ prop.abund + (1| Species),data=dd.dat)
+# # So that seems reasonable...
+# summary(mod.dd.species.re)
+# #Residuals are still pretty cranky
+# plot(mod.dd.species.re)
+# # Normality still a hot mess
+# qqnorm(residuals(mod.dd.species.re))
+# qqline(residuals(mod.dd.species.re))
+# # draw some lines...
+# pred.dd.lmm.species <- expand.grid(prop.abund = seq(0, 1, length.out = 100),Species=unique(dd.dat$Species))
+# tmp <- predict(mod.dd.species.re, pred.dd.lmm.species, type = 'response', se.fit = TRUE) 
+# pred.dd.lmm.species$lam.no.fish   <- exp(tmp$fit)
+# pred.dd.lmm.species$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
+# pred.dd.lmm.species$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
+# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
+# ggplot(pred.dd.lmm.species,aes(x=prop.abund,y=lam.no.fish,group=Species,color=Species)) + 
+#                                 geom_line()  + 
+#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Species, color=Species)) +
+#                                 scale_y_log10()
+# 
+# # We could also allow the slope to vary by species, might get a bit better, but really won't do the trick...
+# mod.dd.species.slope.re <- lmer(log(lam.no.fish) ~ prop.abund + (1+ prop.abund| Species),data=dd.dat)
+# summary(mod.dd.species.slope.re)
+# #Residuals are still pretty cranky
+# plot(mod.dd.species.slope.re)
+# # Normality still a hot mess
+# qqnorm(residuals(mod.dd.species.slope.re))
+# qqline(residuals(mod.dd.species.slope.re))
+# # draw some lines...
+# pred.dd.lmm.species.slope <- expand.grid(prop.abund = seq(0, 1, length.out = 100),Species=unique(dd.dat$Species))
+# tmp <- predict(mod.dd.species.slope.re, pred.dd.lmm.species.slope, type = 'response', se.fit = TRUE) 
+# pred.dd.lmm.species.slope$lam.no.fish   <- exp(tmp$fit)
+# pred.dd.lmm.species.slope$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
+# pred.dd.lmm.species.slope$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
+# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
+# ggplot(pred.dd.lmm.species.slope,aes(x=prop.abund,y=lam.no.fish,group=Species,color=Species)) + 
+#                                 geom_line()  + 
+#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Species, color=Species)) +
+#                                 scale_y_log10()
+# # Curious what species have high slopes.. Dubious and Esmarkii (North Sea sand lance and mackerel)
+# ranef(mod.dd.species.slope.re)
+# 
+# # So so what if we let the slopes vary by stock
+# mod.dd.stock.re <- lmer(log(lam.no.fish) ~ prop.abund +  (1+ prop.abund | Stock.short),data=dd.dat)
+# summary(mod.dd.stock.re)
+# #Residuals are slightly better I think but still really suck
+# plot(mod.dd.stock.re)
+# # Normality = no
+# qqnorm(residuals(mod.dd.stock.re))
+# qqline(residuals(mod.dd.stock.re))
+# # What's it look like?
+# pred.dd.lmm.stock <- expand.grid(prop.abund = seq(0, 1, length.out = 100),
+#                                          #Species=unique(dd.dat$Species),
+#                                          Stock.short=unique(dd.dat$Stock.short))
+# tmp <- predict(mod.dd.stock.re, pred.dd.lmm.stock, type = 'response', se.fit = TRUE) 
+# pred.dd.lmm.stock$lam.no.fish   <- exp(tmp$fit)
+# pred.dd.lmm.stock$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
+# pred.dd.lmm.stock$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
+# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
+# ggplot(pred.dd.lmm.stock,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + 
+#                                 geom_line()  + 
+#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Stock.short, color=Stock.short)) +
+#                                 scale_y_log10()
+# 
+# # Curious what stocks have high slopes.. Dubious and Esmarkii (North Sea sand lance and mackerel), NS Haddock and Irish Sea Haddock 
+# ranef(mod.dd.stock.re)
+# 
+# 
+# 
+# 
+# # OK, so this all still sucks, wonder if a glmer and gamma would get us anywhere... not really.... 
+# # Tried many variants on the glmer and they all land in the same lousy spot.
+# mod.dd.stock.gamma.re <- glmer(lam.no.fish ~ prop.abund +  (1+ prop.abund | Stock.short),data=dd.dat,family=Gamma(link='log'))
+# # OK...
+# summary(mod.dd.stock.gamma.re)
+# #Residuals, nah, still suck, just some crazy outliers...
+# plot(mod.dd.stock.gamma.re)
+# # Normality = no
+# qqnorm(residuals(mod.dd.stock.gamma.re))
+# qqline(residuals(mod.dd.stock.gamma.re))
+# # And the plot...
+# pred.dd.lmm.stock.gamma <- expand.grid(prop.abund = seq(0, 1, length.out = 100),
+#                                          #Species=unique(dd.dat$Species),
+#                                          Stock.short=unique(dd.dat$Stock.short))
+# tmp <- predict(mod.dd.stock.gamma.re, pred.dd.lmm.stock.gamma, type = 'response', se.fit = TRUE) 
+# pred.dd.lmm.stock.gamma$lam.no.fish   <- (tmp$fit)
+# pred.dd.lmm.stock.gamma$lower <- (tmp$fit - 1.96 * tmp$se.fit)
+# pred.dd.lmm.stock.gamma$upper <- (tmp$fit + 1.96 * tmp$se.fit)
+# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
+# ggplot(pred.dd.lmm.stock.gamma,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + 
+#                                 geom_line()  + 
+#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Stock.short, color=Stock.short)) +
+#                                 scale_y_log10()
+# # None of the above really work at all....
+
+```

### 2024-05-09 Drafts/Paper_1/03-methods.Rmd
Methods results done

@@
 
+**NOTE THAT Walleye Pollock was T. chalcogramma and is now G. chalcogrammus**
 ## Data
@@
 This data repository had sufficient data to run the analysis for 77 stocks from NE Atlantic, NW Atlantic, and the North Pacific, this includes stocks managed by Fisheries and Oceans Canada (DFO), NOAA, and ICES.
-See Appendix X for details on the stocks included.
-These stocks all have age-specific estimates of abundance, biomass, removals, natural mortality, and maturity.
+See Table \@ref(tab:tab-meta) for details on the stocks included.
+The stocks included in this analysis all have age-specific estimates of abundance, biomass, removals, natural mortality, and maturity.
 
-## Incidental Catch Model (ICM)
-## Reconstrutive Life-Table Analysis (REC)
-## Life Table Reconstruction (LITAR)
+## Incidental Catch Model (ICM), Reconstrutive Life-Table Analysis (REC), Life Table Reconstruction (LITAR)
 
@@
 
-The discrete time Euler-Lotka equation can be shown to be the characteristic polynomial of the Leslie Matrix, where $f_0$ is the fecundity of the first age class with mature individuals [@leslieUseMatricesCertain1945,@caswellMatrixPopulationModels2001]:
+The discrete time Euler-Lotka equation can be shown to be the characteristic polynomial of the Leslie Matrix, where $f_0$ is the fecundity of the first age class with mature individuals [@leslieUseMatricesCertain1945, @caswellMatrixPopulationModels2001]:
 
-$$
-
+\begin{align}
   \begin{bmatrix}
@@
   \end{bmatrix}
-$$
+\end{align}
 
@@
 This can be estimated from the available recruitment, age at maturity, and biomass information.
-**Note there is no need to divide by 2 for females because we'd divide the recruits by 2 to get the number of females, and the spawning numbers by 2, which would just cancel out**.
+**Delete this, but Note there is no need to divide by 2 for females because we'd divide the recruits by 2 to get the number of females, and the spawning numbers by 2, which would just cancel out**.
 
@@
 This method assumes that there is no effect of age on reproductive success (i.e., each kilogram of spawning biomass contributes the same to the total total reproductive output, irrespective of their age).
-Finally, the fecundity ($Fec_{y-1,a}$) is calculated as number of offspring produced by each individual in the population, this is offset by one year, as the recruits observed in year $y+1$ are produced in the Euler-Lotka formulation in year $y$.
+Finally, the fecundity ($Fec_{y,a}$) is calculated as number of offspring produced by each individual in the population, this is offset by one year, as the recruits observed in year $y+1$ enter into the Euler-Lotka formulation in year $y$.
 
 $$
-Fec_{y,a} =  RPA_{y+1,a} / SSN_{(y-ra+1),a}
+Fec_{y,a} =  \frac{RPA_{y+1,a}}{SSN_{(y-ra+1),a}}
 $$
@@
 $$
-FM_{y,a} =  Catch_{y,a} / N_{y,a}
+FM_{y,a} =  \frac{Catch_{y,a}}{N_{y,a}}
 $$
@@
 The result of this was compared to the abundance estimate from the stock assessment for the upcoming year ($N_{y+1}$).
-Where necessary, the fecundity and natural mortality estimates were adjusted until the $\lambda$ estimate from the Euler-Lotka equation resulted in an abundance time-series estimate ($N_{y+1}$) that was less than 5% different from the abundance estimates from the stock assessment (AVERAGE DIFFERNCE WAS 0.XX%).
+Where necessary, the fecundity and natural mortality estimates were adjusted until the $\lambda$ estimate from the Euler-Lotka equation resulted in an abundance time-series estimate ($N_{y+1}$) that was within 5% of the abundance estimates from the stock assessment (median difference was `r med.per.diff`).
 In this way the $\lambda$, fecundity, and natural mortality estimates are obtained for each year in which data are available.
-
-WONDER IF I HAVE THE "AVERAGE" DIFFERENCE of NM and FECUNDITY FROM THE ORIGINAL VALUES FROM THE ABOVE or is that opening up pandora's box.
+The realized $\lambda_{F>0}$ included fishing mortality, in addition $\lambda_{F=0}$ could also be calculated by using annual the natural mortality and fecundity estimates.
+$\lambda_{F=0}$ provides an estimate of the potential population growth in the absence of fishing in a give year.
 
@@
 
-Doubling time was calculated using a simulation approach in which the estimated fecundity and natural mortality for a year were sampled from the historically observed fecundity and natural natural mortality.
+Doubling time in the absence of fishing was calculated using a simulation approach in which the estimated fecundity and natural mortality for a projection year were sampled from the fecundity and natural natural mortality estimated in each year for each stock.
 The Euler-Lotka equation was used to estimate the population growth rate and this rate was used to adjust the population biomass accordingly.
-The simulation was run for XX years with YY simulations, the percentage of the simulations in which the population size had doubled was recorded each year.
+The simulation was run for `n.sim.years` years with `r n.dt.sims` simulations, the percentage of the simulations in which the population size had doubled was recorded each year.
 If a population had doubled in size, it was removed from the simulation and recorded as having doubled for all subsequent years.
+This approach implicitly assumes no density dependence effects.
 
@@
 
-The lifetime reproductive success ($R_0$) in the absence of fishing was calculated for each cohort in which fecundity and natural mortality were available for all age classes.
+The lifetime reproductive success ($R_0$)  was calculated for each cohort in which fecundity and natural mortality were available for all age classes.
+It was calculated using only natural mortality (F=0) and with the combined effect of natural mortality and fishing mortality (F>0).
 This was calculated for each cohort as
@@
 
-The generation time here is defined as the mean age of the spawners of the observed recruits in a cohort over its lifetime ($T_G$) in the absence of fishing was calculated for each cohort in which fecundity and natural mortality were available for all age classes.
-This was calculated for each cohort as.
+The generation time was defined as the mean age of the spawners of the observed recruits in a cohort over its lifetime ($T_G$), here we calculated this for each cohort in which fecundity and natural mortality were available for all age classes.
+It was calculated twice, using only natural mortality (F=0) and with the combined effect of natural mortality and fishing mortality (F>0).
 
@@
 $$
+
+## Density Dependence
+
+Density dependence was explored by modelling the estimated $\lambda$ against the proportion of the maximum abundance observed for each stock.
+This was done twice, once using ($\lambda_{F=0}$) and once using ($\lambda_{F>0}$).
+Generalized Additive Models were used to allow for some non-linearity in the relationships (CITE MCGV and WOOD), the overall effect and the effect for each stock was modelled as
+
+\begin{align}
+\lambda_{i,j} \sim N(0,\sigma^2_{i,j}) \\
+E(\lambda_{i,j}) = \mu_{i,j} \\
+log(\mu_{i,j}) =  Prop_{i} + Stock_{j}  \times Prop_{i} \\
+Stocks_{i,j} \sim N(0,\sigma^2_{Stocks})
+\end{align}
+
+The interaction was modeled using the *fs* basis using the mgcv package in R, this treats the smooth curves as random effect and is used when a factor has a large number of levels (CITE!).
+Various alternative modelling methods were explored (various model formulations, alternative error distributions, etc.) but all models had similar challenges overcoming either the underlying non-normality or the heteroskedasticity of the data.
+As such, the uncertainty surrounding the model output should be treated with caution, while we discuss the general trends this model provides we attempted to avoid discussion of the statistical significance of the trends.

### 2024-05-09 Drafts/Paper_1/05-discussion.Rmd
Methods results done

@@
 Looks like density dependence is real.
-Dave's pet theroy is there is solid evidence of density dependence for many stocks above around 0.4, below 0.4 the evidence hints more at density independence for many stocks, BUT, some stocks have an ability to very occasionally very spectacularly take advantage of the environment.
-But not all stocks and species have this ability and the strength and frequency seems to be influenced by where you life and what species you are.
-Little evidence for spectacular reproduction events in NW Atlantic, while the majority of species assessed in the north sea have this ability.
-Cod show this dicomaty perfectly....
+Dave's pet theory is there is solid evidence of density dependence for many stocks above around 0.4, below 0.4 the evidence suggest that density dependence weakens for some stocks, BUT, some stocks have an ability to very occasionally very spectacularly take advantage of the environment.
+But not all stocks and species have this ability and the strength and frequency seems to be influenced by where you live and what species you are.
+Little evidence for high lambda for most stocks in the NW Atlantic, while many stocks assessed in the North Sea had anomalously high lambdas in 1 or more years.
+Cod show this  perfectly....
 
@@
 Center around the idea of equilibrium theory? That management might be fairly good for stocks that aren’t very variable, but when you make a decision based on averages you can make really bad ones.
+
+By ignoring the density dependence patterns observed in this analysis, the doubling time analysis would overestimate the doubling time for stocks that were at low abundance with classic negative density dependence dynamics, while it would underestimate it for stocks with positive density dependence.
+Here perhaps talk about infrequent big events and how using a theoretical rmax within a logistic model isn't a good idea because this will way over-estimate recovery potential at low abundance.
+
+The optimization procedure assumes that both the estimates of abundance and the fishery removals from the stock assessment are correct.
+*A couple sentences about why fisheries removals may be underestimated*.
+This would result in the estimates of the $\lambda$ excluding fishing mortality in this analysis being lower than reality, as this 'missing' mortality was accounted for by reductions in either fecundity or an increase in natural mortality.
+The optimization routine resulted in a median decrease in the no-fishing $\lambda$ estimates of approximately `r med.lam.per.diff`%, the overall directionality of this change is consistent with fishing mortality being generally underestimated.
+
+Fisheries appear to slightly weaken the effects of density dependence overall.
+Maybe due to fisheries having positive density dependence?
+Seemingly below around 0.5 fishing leads to a positive lambda, below 0.5 it is a negative lambda...
+that's kinda kooky cool!
+
+The stocks which reached very low abundance (< 10% of maximum) tended to have high values of lambda, suggesting strong compensation in stocks when they are at extremely low abundance.
+Oddly, the path to this isn't linear, and positive density dependence (or at least density independence was evident between 10 and 40% of maximum abundance).
+
+Probably something worth citing in here @thorsonPredictingRecruitmentDensity2020

### 2024-05-09 Drafts/Paper_1/08-figures.Rmd
Methods results done

@@
 ```
+
+# Figures {-}
+
+```{r lambda-bx-6-fig, echo=F, fig.cap="$\\lambda$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"))
+
+```
+
+\newpage
+```{r lambda-bx-other-fig, echo=F, fig.cap="$\\lambda$ estimates for the remainded of the stocks in this analysis, plotted by the location of the stock.
+The abreviated species name is provided on the x axis."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"))
+
+```
+
+\newpage
+```{r lambda-sd-fig, echo=F, fig.cap="Standard deviation of the $\\lambda$ estimates for each stock, ordered by species, in this analysis. "}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"))
+```
+
+\newpage
+```{r dd-overall-plt, echo=F, fig.cap="Density dependence of $\\lambda$ The top panel shows $\\lambda_{F=0}$ against the proportion of maximum abundance, with a GAM smooth and the GAM estimated 95\\% confidence interval.
+The middle panel shows $\\lambda_{F>0}$ against the proportion of maximum abundance, with a GAM smooth and the GAM estimated 95% confidence interval.
+The bottom panel compares the GAM smooths for $\\lambda_{F=0}$ and $\\lambda_{F>0}$."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_overall_",what.2.tune,".png"))
+```
+
+\newpage
+```{r dd-nf-stock-plt, echo=F, fig.cap="Density dependence of $\\lambda_{F=0}$ for each stock in the analysis plotted regionally."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"))
+```
+
+\newpage
+```{r dd-fish-stock-plt, echo=F, fig.cap="Density dependence of $\\lambda_{F>0}$ for each stock in the analysis plotted regionally."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_fish_stocks_",what.2.tune,".png"))
+```
+
+\newpage
+```{r r0-6-plt, echo=F, fig.cap="$R_0$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"))
+```
+
+\newpage
+```{r r0-other-plt, echo=F, fig.cap="$R_0$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"))
+```
+
+\newpage
+```{r r0-nf-ts-plt, echo=F, fig.cap="$R_0$ estimates for every cohort for each species excluding the effects of fishing."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_nf_",what.2.tune,".png"))
+```
+
+\newpage
+```{r r0-fish-ts-plt, echo=F, fig.cap="$R_0$ estimates for every cohort for each species including the effects of fishing."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_fish_",what.2.tune,".png"))
+```
+
+\newpage
+```{r gl-6-plt, echo=F, fig.cap="Generation length estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"))
+```
+
+\newpage
+```{r gl-other-plt, echo=F, fig.cap="Generation length estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"))
+```
+
+\newpage
+```{r gl-nf-ts-plt, echo=F, fig.cap="Generation length estimates for every cohort for each species excluding the effects of fishing."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_nf_",what.2.tune,".png"))
+```
+
+\newpage
+```{r gl-fish-ts-plt, echo=F, fig.cap="Generation length estimates for every cohort for each species including the effects of fishing."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_fish_",what.2.tune,".png"))
+```
+
+<!-- Now for the Doubling time -->
+
+\newpage
+```{r dub-time-map, echo=F, fig.cap="Doubling time estimate for each stock with no fishing mortality."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"))
+```
+
+\newpage
+```{r dub-ts, echo=F, fig.cap="The number of stocks which doubled in size by a given year with no fishing mortality  The dashed line represents the 77 stocks in the analysis."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_time_series_",what.2.tune,".png"))
+```
+
+\newpage
+```{r dub-vs-sd, echo=F, fig.cap="The number of stocks which doubled in size by a given year with no fishing mortality  The dashed line represents the 77 stocks in the analysis."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"))
+```
+
+# Supplemental Figures {-}

### 2024-05-09 Drafts/Paper_1/index.Rmd
Methods results done

@@
 library(viridis)
+library(arm)
+library(mgcv)
+library(lme4)
+library(scales)
+library(ggh4x)
+library(gratia)
 theme_set(theme_few(base_size = 14))
@@
 loc <- 'D:/GitHub/ICM'
-
+# The parameters for the doubling time simulation
+n.dt.sims <- 1000 # Increase to 1000 for final run, which takes like a full day or something 
+n.sim.years <- 100
 # If we already have the results don't re-run the models or load data we don't need.

### 2024-05-10 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
Change needed for the Multispecies forward simulations

@@
                "$\\lambda_{F>0}^{Min-Max}$",
-               "$\\lambda_{F>0}^{40-Min}$",
+               "$\\lambda_{F>0}^{40-Max}$",
                "$\\lambda_{F=0}^{Min-40}$",

### 2024-05-10 Scripts/functions/simple_forward_sim.r

@@ -134,9 +134,9 @@ simp.for.sim<-function(years,nm=NULL,fecund = NULL,ages =NULL,rems,K=NULL,N.star
       # The exponential model
       if(pop.model == 'exponential') 
       {
-        exp.res <- for.proj(option = "exponential",pop.last = pop.last ,r=r.up)
+        exp.res <- for.proj(option = "exponential",pop.last = pop.last -removals.next ,r=r.up)
         if(exp.res$Pop.current < 0) exp.res$Pop.current =0 # don't let it drop below 0
-        pop.last <- exp.res$Pop.current
+        pop.last <- exp.res$Pop.current 
       } # end if(pop.model == 'exponential') 
       
       # So this one is the exponential, but when above whatever bound you have set the population growth rate becomes more negative
@@ -152,10 +152,10 @@ simp.for.sim<-function(years,nm=NULL,fecund = NULL,ages =NULL,rems,K=NULL,N.star
           ratio <- K[y-1]/pop.last-1
           r.up <- rlnorm(1,ratio,0.05)-1
         }
-        exp.res <- for.proj(option = "exponential",pop.last = pop.last ,r=r.up)
+        exp.res <- for.proj(option = "exponential",pop.last = pop.last -removals.next,r=r.up)
         #browser()
         if(exp.res$Pop.current < 0) exp.res$Pop.current =0 # don't let it drop below 0
-        pop.last <- exp.res$Pop.current
+        pop.last <- exp.res$Pop.current 
       }
       
       # If you are running the logistic model it's all pretty straightforward
@@ -164,7 +164,7 @@ simp.for.sim<-function(years,nm=NULL,fecund = NULL,ages =NULL,rems,K=NULL,N.star
       if(pop.model == 'logistic')
       {
         #browser()
-        exp.res <- for.proj(option = "logistic",pop.last = pop.last,K=K[y-1],r=r.up)
+        exp.res <- for.proj(option = "logistic",pop.last = pop.last -removals.next,K=K[y-1],r=r.up)
         if(exp.res$Pop.current < 0) exp.res$Pop.current =0 # don't let it drop below 0
         pop.last <- min(exp.res$Pop.current)
       }

### 2024-05-10 Scripts/functions/simple_forward_sim.r
Fix of missing removals
Problem in the forward simulations, should consider aligning with what we do for the backwards ones.

@@ -68,6 +68,7 @@ simp.for.sim<-function(years,nm=NULL,fecund = NULL,ages =NULL,rems,K=NULL,N.star
   for(i in 1:n.sims)
   {
     # Using the fecundity and mortality data get the lotka r's for the stock
+    # DK Note: It might make more sense to put the fishing mortality right into here as we've now done with the backwards simulations.
     junk<-simple.lotka.r(yrs = years,mort = nm,ages=ages,fecund=fecund)   
     tmp <-junk$res[,2] 
     if(length(tmp) == 1) tmp <- rep(tmp,n.years)

### 2024-05-21 Drafts/Paper_1/paper_1.Rmd
mid-edit update

--- 2024-05-10 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
@@
+---
+title: |
+   "Life history variability influence on the recovery potential of globally exploited teleosts "
+french_title: "Titre ici (*Nom latin de l'espèce*)"
+author: |
+  David. M. Keith^1^ 
+  Freya M. Keyser^1^
+  Julie M. Charbonneau^2^
+  Heather 'The Boss' Bowlby^1^
+author_list: "Keith, D.M., Keyser, F.M., Charbonneau, J.M., Bowlby, H.T.B."
+address: |
+  ^1^Bedford Institute of Oceanography\
+     Fisheries and Oceans Canada, 1 Challenger Dr.\
+     Dartmouth, Nova Scotia, B2Y 4A2 , Canada\
+  \smallskip
+  ^2^Simon Fraser University\
+     Department of Biology\
+french_address: |
+
+month: ""
+french_month: ""
+year: 2024
+report_number: nnn
+region: "Maritimes Region"
+french_region: "Maritimes Region"
+isbn: ""
+cat_no: ""
+citation_other_language: ""
+
+abstract: |
+  Here is the abstract text.
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+  Start new paragraphs after a blank line and with 2 spaces indent.
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+french_abstract: |
+
+header: "Draft working paper --- Do not cite or circulate" # or "" to omit
+output:
+ csasdown::resdoc_word:
+   french: false
+   copy_sty: true
+   line_nums: true
+   line_nums_mod: 1
+   lot_lof: false
+   draft_watermark: false
+   include_section_nums: true
+   highlight: tango
+# ------------
+# End of options to set
+knit: (function(input, ...) {
+       csasdown::render('_bookdown.yml')
+      })
+link-citations: true
+bibliography: Y:/Zotero/MAR_SABHU.bib
+# Any extra LaTeX code for the header:
+# header-includes:
+# - \usepackage{tikz}
+---
+
+```{r setup, echo=FALSE, cache=FALSE, message=FALSE, results='hide', warning=FALSE}
+library(knitr)
+if (is_latex_output()) {
+  knitr_figs_dir <- "knitr-figs-pdf/"
+  knitr_cache_dir <- "knitr-cache-pdf/"
+  fig_out_type <- "png"
+} else {
+  knitr_figs_dir <- "knitr-figs-docx/"
+  knitr_cache_dir <- "knitr-cache-docx/"
+  fig_out_type <- "png"
+}
+fig_asp <- 0.618
+fig_width <- 9
+fig_out_width <- "6in"
+fig_dpi <- 180
+fig_align <- "center"
+fig_pos <- "htb"
+opts_chunk$set(
+  collapse = TRUE,
+  warning = FALSE,
+  message = FALSE,
+  comment = "#>",
+  fig.path = knitr_figs_dir,
+  cache.path = knitr_cache_dir,
+  fig.asp = fig_asp,
+  fig.width = fig_width,
+  out.width = fig_out_width,
+  echo = FALSE,
+  #  autodep = TRUE,
+  #  cache = TRUE,
+  cache.comments = FALSE,
+  dev = fig_out_type,
+  dpi = fig_dpi,
+  fig.align = fig_align,
+  fig.pos = fig_pos
+)
+```
+
+```{r load-libraries-n-data, echo = FALSE, cache = FALSE, message = FALSE, results = 'hide', warning = FALSE}
+# add other packages here:
+library(dplyr)
+library(readr)
+library(tibble)
+library(csasdown)
+# OK, so using the ICES assessments here's what we get for North Sea cod.
+library(readxl)
+library(tidyverse)
+library(rio)
+library(ggthemes)
+library(cowplot)
+library(gtable)
+library(viridis)
+library(arm)
+library(mgcv)
+library(lme4)
+library(scales)
+library(ggh4x)
+library(gratia)
+theme_set(theme_few(base_size = 14))
+
+# The location of your data
+loc <- 'D:/GitHub/ICM'
+# The parameters for the doubling time simulation
+n.dt.sims <- 1000 # Increase to 1000 for final run, which takes like a full day or something 
+n.sim.years <- 100
+# If we already have the results don't re-run the models or load data we don't need.
+load.results <- F
+# What tunning model are you running or did you run!
+what.2.tune <- 'fec_nm'
+
+#source(paste0(loc,"/Scripts/functions/tuning_sim_fast.R"))
+
+# Download the functions we'll need from github
+funs <- c("https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/simple_Lotka_r.r",
+          "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/backwards_project.r",
+          "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/forward_project.r",
+          "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/tuning_sim_fast.r"
+)
+  # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
+for(fun in funs) 
+{
+  download.file(fun,destfile = basename(fun))
+  source(paste0(getwd(),"/",basename(fun)))
+  file.remove(paste0(getwd(),"/",basename(fun)))
+}
+
+if(load.results==F)
+{
+  # Choose 5 ICES stocks that we have the necessary data for
+  #ASR <- read_xlsx("../Data/ASR_2018.xlsx" sheet = "ICES")
+  ASR1 <- read.csv(paste0(loc,"/Data/ICM_data_NE_atlantic_stocks.csv"))
+  ASR <- read.csv(paste0(loc,"/Data/ICM_data_NW_atlantic_stocks.csv"))
+
+  ASR <- rbind(ASR1,ASR)
+  datatypes <- unique(gsub(x = names(ASR), pattern = "[^a-zA-Z]", replacement=""))
+
+  # Replace 0's in Num.tot with NA so the rest of this works as Freya designed it to...
+  ASR$Num.tot[ASR$Num.tot == 0] <- NA
+  # we want:
+  # Year, Num, WA, Catch, AM, NM, StockID, Management, Area, Order, Family, Genus, Species
+  ASRdat <- ASR[,c(grep(x=names(ASR), "Num"),
+                   grep(x=names(ASR), "WA"),
+                   grep(x=names(ASR), "Catch"),
+                   grep(x=names(ASR), "AM"),
+                   grep(x=names(ASR), "NM"))]
+  # Making all the data numeric that should be numeric
+  ASRdat <- apply(X = ASRdat, 2, as.numeric)
+  # Getting the species info back
+  ASRsp <- ASR[, which(!1:length(names(ASR)) %in% grep(x=names(ASR), ".", fixed=T))]
+  # And binding it all back together
+  ASR.trim <- cbind(ASRsp, ASRdat)
+  # need a unique ID for stock
+  #table(ASR.trim$Management, ASR.trim$Species)
+  ASR.trim$Stock <- paste0(ASR.trim$Management, "_", ASR.trim$Area, "_", ASR.trim$Genus, "_", ASR.trim$Species)
+
+  ASR.long <- ASR.trim %>%
+    pivot_longer(!c("Management", "Area", "Order", "Family", "Genus", "Species", "Stock", "Year","Meeting_or_reference","Model","Case","Notes")) %>%
+    separate(col=name, into=c("type", "age"), sep = "\\.")
+
+  # Something is weird with the mentella stock, I'm going to drop it...
+  ASR.long <- ASR.long %>% dplyr::filter(Stock != "ICES-AFWG_DEEP1-2_Sebastes_mentella")
+}# end if load results
+```
+
+```{r bilingual-code, cache=FALSE}
+options(
+  # Prevent xtable from adding a timestamp comment to the table code it produces
+  xtable.comment = FALSE,
+  # Do not allow kableExtra to load packages, we add them manually in csasdown
+  kableExtra.latex.load_packages = FALSE,
+  # Stop chunk output (echo) running into the margins
+  width = 80,
+  # Do not use scientific notation (stops tables from showing 1.2e3, etc.)
+  scipen = 999)
+
+meta <- rmarkdown::metadata
+meta_out <- rmarkdown::metadata$output
+csl <- "csl/csas.csl"
+options(OutDec = ".")
+if (is.null(getOption("french"))) {
+  stop("`french` was not set up correctly in YAML header in index.Rmd. ",
+       "It must be true or false",
+       call. = FALSE)
+}
+if (getOption("french")) {
+  csl <- "csl/csas-french.csl"
+  options(OutDec = ",")
+}
+
+french <- isTRUE(getOption("french")) # for backwards compatibility
+
+# This hook simplifies document translation for the author.
+# When building in French, it draws a box around paragraphs contained in chunks
+#  which have the option `needs_trans = TRUE`. It also labels
+#  the box with a "Needs translation" tag in red and the chunk label in blue.
+# You need to change the `needs_trans` option to `FALSE` for a chunk once you
+#  have inserted the translated text into it. You will get a utf-8 error if
+#  you leave it as `TRUE` and there is French in the chunk.
+#  This function assumes you are translating from English to French.
+#  If you wrote your document in French and want to translate to English,
+#  put a ! before `getOption("french")` below and add the `need_trans`
+#  chunk options to your English paragraph chunks instead of the French ones.
+#  
+#  IMPORTANT NOTES
+#  - Use `csasdown::render()` to render the document. This runs a
+#    pre-processing step which ensures any inline R chunks
+#    `r print("Like this one")` are taken care of correctly and that all
+#    backslash variables (eg. \pi, \alpha, \@ref, \cite) are all processed
+#    correctly.
+#  - French latex places a space before the colon by default so if you need a colon
+#    with no space before it, use \\hc .
+knit_hooks$set(needs_trans = function(before, options){
+  if(getOption("french") && options$needs_trans){
+    if (before){
+      paste0("\\
+   \\begin{lrbox}{\\userinput}
+   \\begin{minipage}{\\dimexpr\\linewidth-2\\fboxsep-2\\fboxrule}
+   \\textcolor{red}{\\textbf{Needs translation - \\textcolor{blue}{knitr chunk: ", options$label, "}}}
+   \\begin{lstlisting}
+  ")
+    } else {
+      "
+   \\end{lstlisting}
+   \\end{minipage}
+   \\end{lrbox}
+   \\noindent
+   \\fbox{\\usebox{\\userinput}}
+  "
+    }
+  }
+})
+```
+
+---
+title: `r ifelse(fr(), meta$french_title, meta$title)`
+month: `r ifelse(fr(), meta$french_month, meta$month)`
+region: `r ifelse(fr(), meta$french_region, meta$region)`
+csl: `r csl`
+---
+
+<!--chapter:end:tmp-index.Rmd-->
+
 ---
@@
 
-  save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,
+  save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,#mr.tmp,
        am.tmp,Stocks,ASR.stocks,ASR.long,abund.tmp,fs.tmp,full.rem.tmp,
@@
   {
-    tmp <- rep(0,n.sim.yearss)
+    tmp <- rep(0,n.sim.years)
     print(paste0("Sim # ", s))
 
-    for(y in 2:n.sim.yearss)
+    for(y in 2:n.sim.years)
     {
@@
       pop[y] <- exp(r.val)*pop[y-1]
-      if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.sim.yearss] <- 1
+      if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.sim.years] <- 1
     } # end the years loop
-    tmp.res[[s]] <- data.frame(year =1:n.sim.yearss,doubled = tmp,sim=s)
+    tmp.res[[s]] <- data.frame(year =1:n.sim.years,doubled = tmp,sim=s)
 
@@
 # This extracts the GAM fit so we can custom plot it on our own figure
-tmp <- plot(mod.dd.stock.gam.nf, pages = 0)
+tmp <- plot(mod.dd.stock.gam.nf, pages = 0) # Leave a space after this so the code runs (it needs a return as this thing makes a two panel figure)
+
 no.stock.gam.nf.dat <- data.frame(fit = tmp[[1]]$fit + coefficients(mod.dd.stock.gam.nf)[1],prop.abund = tmp[[1]]$x,se = tmp[[1]]$se,Scenario = "F = 0")
@@
 
-tmp <- plot(mod.dd.stock.gam.fish, pages = 0)
+tmp <- plot(mod.dd.stock.gam.fish, pages = 0) # Leave a space after this so the code runs (it needs a return as this thing makes a two panel figure)
+
 no.stock.gam.fish.dat <- data.frame(fit = tmp[[1]]$fit + coefficients(mod.dd.stock.gam.fish)[1],prop.abund = tmp[[1]]$x,se = tmp[[1]]$se,Scenario = "F > 0")
@@
 # the lambda calcs
+n.stock.dfo <- meta.sub |> collapse::fsubset(Manage.short == "DFO-TRAC") |> nrow()
+n.stock.ices <- meta.sub |> collapse::fsubset(Manage.short == "ICES") |> nrow()
+n.stock.noaa <- meta.sub |> collapse::fsubset(Manage.short %in% c("AFSC","NEFSC")) |> nrow()
+n.age.0 <- meta.sub |> collapse::fsubset(age.min == 0) |> nrow()
+n.age.1 <- meta.sub |> collapse::fsubset(age.min == 1) |> nrow()
+n.age.2.plus <- meta.sub |> collapse::fsubset(age.min >= 2) |> nrow()
+min.year <- min(res.lambda.fin$year)
+max.year <- max(res.lambda.fin$year)
+stock.ts.len <- res.lambda.fin |> collapse::fgroup_by(Stock.short) |> collapse::fsummarise(n.years = length(year))
+mn.ts.len <- round(mean(stock.ts.len$n.years),digits=1)
+mn.ts.len <- min(stock.ts.len$n.years)
+mx.ts.len <- max(stock.ts.len$n.years)
+num.orders <- length(unique(meta.sub$Order))
+num.gads <- meta.sub |> collapse::fsubset(Order == "Gadiformes") |> nrow()
+num.pleur <- meta.sub |> collapse::fsubset(Order == "Pleuronectiformes") |> nrow()
+num.scorp <- meta.sub |> collapse::fsubset(Order == "Scorpaeniformes ") |> nrow()
+num.clup <- meta.sub |> collapse::fsubset(Order == "Clupeiformes") |> nrow()
+num.scomb <- meta.sub |> collapse::fsubset(Order == "Scombriformes") |> nrow()
+num.perci <- meta.sub |> collapse::fsubset(Order == "Perciformes") |> nrow()
+
+n.st.spec <- meta.sub |> collapse::fgroup_by(Species ) |> collapse::fsummarise(n.stocks = length(Stock)) 
+n.st.spec <- n.st.spec[rev(order(n.st.spec$n.stocks)),]
+num.cod <- meta.sub |> collapse::fsubset(Species == "morhua") |> nrow()
+num.her <- meta.sub |> collapse::fsubset(Species == "harengus") |> nrow()
+num.had <- meta.sub |> collapse::fsubset(Species == "aeglefinus") |> nrow()
+num.sol <- meta.sub |> collapse::fsubset(Species == "solea") |> nrow()
+num.pol <- meta.sub |> collapse::fsubset(Species == "virens") |> nrow()
+num.plat <- meta.sub |> collapse::fsubset(Species == "platessa") |> nrow()
+
+n.six <- meta.sub |> collapse::fsubset(Species %in% six.species) |> nrow()
+
 med.lambda.F0 <- round(median(res.lambda.fin$lam.no.fish),digits=3)
@@
 ```
+
+<!--chapter:end:tmp-01-analysis_no_age_correction.Rmd-->
+
+# INTRODUCTION  {#intro}
+
+Intro – life history paragraph, environmental variation paragraph, management ties paragraph, goals.
+
+theoretical expectations related to productivity and life history for various species (e.g. herring vs. Cod) (ties to regional variation in lifetime reproductive rates and doubling time).
+
+Evidence for specific species to make use of environmental conditions – boom in recruitment.
+
+How our understanding of productivity is used in a management context – projections, reference points, risk, (ties directly to density dependence figure).  
+Species-environment relationship – is it different from what we expect and how does that influence our capacity for management of exploited fishes.
+
+The under appreciated influence of regional variation in determining recovery potential of exploited teleosts.  - can’t look at a single species and expect it will behave the same way.
+
+Objectives
+  - Quantify the life history variability of exploited marine teleosts
+  - Explore regional and taxonomic correlates of life history variability
+  - Based on the observed life history, quantify the recovery potential of marine teleosts in the absence of fishing
+
+<!--chapter:end:tmp-02-intro.Rmd-->
+
+# Methods {#meth}
+
+## Data
+
+This analysis used age structured fisheries data obtained from stock assessments for stocks in the Atlantic and Pacific Oceans [@charbonneauAgestructuredmarinefishdatabase2022; @charbonneauEffectsFishingMortality2022].
+This repository had sufficient data to run the analysis for 77 stocks from NE Atlantic, NW Atlantic, and the North Pacific, this included stocks managed by International Council for the Exploration of the Sea (ICES; `r n.stock.ices`), NOAA (NOAA;`r n.stock.noaa`), and Fisheries and Oceans Canada (DFO; `r n.stock.dfo` stocks).
+The time series used in this analysis started as early as `r min.year` and the most recent data were from `r max.year`, the average length of the time series for the stocks included in this analysis was `r mn.ts.len` years and the number of years used ranged between `r min.ts.len` and `r max.ts.len` years.
+The stocks used represented `r num.orders` orders, with the most represented orders being the Gadiformes (`r num.gads` stocks), Pleuronectiformes (`r num.pleur` stocks) and Clupeiformes (`r num.clup` stocks).
+The other three orders had relatively few stocks included in the analysis, with `r num.perci` Perciform stocks, `r num.scomb` Scombriform stocks, and just `r num.scorp` Scorpaeniform stock.
+The most common species in this analysis were Atlantic cod (*G.
+morhua*) and the majority of the stocks (`r n.six`) in this analysis were represented by one of six species (*G.
+morhua* (`r num.cod`), *C.
+harengus* (`r num.her`), *M.
+aeglefinus* (`r num.had`),  *P.
+virens* (`r num.pol`), *S.
+solea* (`r num.sol`), and *P.
+platessa* (`r num.plat`)).
+
+These data included age-specific estimates of abundance, weight, biomass, maturity, natural mortality, and fishery removals (Table \@ref(tab:tab-meta)), these data were all required to calculate survival-at-age and fecundity-at-age and to estimate the annual productivity of these stocks.
+For the age structured analysis, the last age class was considered the 'terminal' age in the analysis, thus we implicitly assumed there was no contribution to productivity from older aged individuals.
+In addition, for the majority of the stocks the first age class was age 1 (`r n.age.1` stocks) while another `r n.age.2.plus` of the stocks have a first age of 2 or greater.
+The young age classes not included for these stocks (e.g.
+Age 0) consisted of immature individuals that do not contribute to the productivity of the stock; however it has been noted that the exclusion of immature age classes in these types of analyses may lead to a slight overestimate of productivity [@pardoMaximumIntrinsicRate2016].
+
+## Life Table Reconstruction
+
+The discrete time Euler-Lotka  equation was first proposed by Euler in 1760 (subsequently published by @moserGesetzeLebensdauer1839) and is a special case of the continuous time demographic model first proposed by Lotka in 1907 [@lotkaRelationsBirthRates1907; @sharpeProblemAgedistribution1911; @lotkaRelationBirthRate1918]:
+
+$$
+1 = \sum_{x=\alpha}^{\omega} \lambda^{-x} s_x f_x dx
+$$
+
+Where $x$ is the age, $\alpha$ is the age at first reproduction, $\omega$ is the maximum age, $\lambda$ is the discrete rate of population growth ($\lambda = e^r$), $s_x$ is the survivorship to age $x$, and $f_x$ is the fecundity of individuals of age $x$.
+Note that the discrete time Euler-Lotka equation can be shown to be the characteristic polynomial of the Leslie Matrix, where $f_0$ is the fecundity of the first age class with mature individuals [@leslieUseMatricesCertain1945, @caswellMatrixPopulationModels2001].
+The available stock assessment data are used to calculate survival-at-age and fecundity-at-age to estimate $\lambda$, assuming that each stock represents a discrete population with individual dynamics.
+
+<!-- \begin{align} -->
+<!--   \begin{bmatrix} -->
+<!--     f_0  & f_1 & f_2  & f_3    & ...          & f_{\omega-1} \\ -->
+<!--     s_0  & 0   & 0    & 0      & ...          & 0 \\ -->
+<!--     0    & s_1 & 0    & 0      & ...          & 0 \\ -->
+<!--     0    & 0   & s_2  & 0      & ...          & 0 \\ -->
+<!--     0    & 0   & 0    & \ddots & ...          & 0 \\ -->
+<!--     0    & 0   & 0    & ...    & s_{\omega-2} & 0 \\ -->
+<!--   \end{bmatrix} -->
+<!-- \end{align} -->
+
+### Fecundity-at-age
+
+The number of spawners in year $y$ and age class $a$ ($SSN_{y,a}$) is the proportion of mature individuals ($Mat_{y,a}$) multiplied by the number of individuals in each age
+
+$$
+SSN_{y,a} = Mat_{y,a} N_{y,a}
+$$
+The Euler-Lotka equation requires fecundity to be the number of offspring produced by each female in each age class.
+Given the uncertainty of both fertilization and egg survival, using the number of eggs at a given length or size is inappropriate.
+However, these data do have the number of recruits produced each year, and this can be combined with the spawning stock biomass to obtain an estimate of the number of recruits produced per kilogram of spawning biomass $RPS_{y}$, this is calculated as
+
+$$
+RPS_{y} = R_{y} SSB_{tot,(y-ra)} 
+$$
+
+Where $SSB_{yot,y-ra}$ is the total spawning stock biomass in year $y$.
+$R_{y}$ is the number of individuals in the youngest age class available for a specific stock (hereafter referred to as recruits) offset temporally by the age of the recruits.
+For example, if the age of the recruits ($ra$) is 2 years , we assume that the recruits in 2010 were produced by the spawning stock biomass in 2008 ($SSB_{tot,y-ra}$).
+The number of recruits produced by each age class ($RPA_{y,a}$) can then be calculated by multiplying the spawner biomass in each age class $SSB_{y-ra,a}$ by the number of recruits produced per kilogram of SSB
+
+$$
+RPA_{y,a} =  SSB_{(y-ra),a} RPS_{y}
+$$
+This method does not account for any changes in reproductive success by age, each kilogram of spawning biomass contributes the same to the total total reproductive output, irrespective of their age.
+Finally, the age-specific fecundity ($Fec_{y,a}$) is calculated as number of offspring produced by each individual in the population.
+This is offset by one year, as the recruits observed in year $y+1$ enter into the Euler-Lotka formulation in year $y$.
+
+$$
+Fec_{y,a} =  \frac{RPA_{y+1,a}}{SSN_{(y-ra+1),a}}
+$$
+### Suvival-at-age
+
+The number of animals surviving to each age depends on age-specific mortality rates.
+Commercially-exploited fishes experience fishing mortality (F) once they grow large enough to become vulnerable to the gear (reference).
+Fishing mortality combines with natural mortality (M) to give total mortality (Z) affecting each age class in each year.
+Varying assumptions can be made about natural mortality during stock assessments, where it may be an assumed value for each age (EXAMPLE), allowed to vary over time and by age (EXAMPLE), or input as a constant across ages (EXAMPLE).
+Due to challenges with separability in typical stock assessment models, natural mortality is often assumed for each age class, in some assessments it varies by age and over time, in other assessments it does not.
+Irrespective of this, the stock assessment used in this analysis all provide an estimate of natural mortality by age and year, this value is typically an instantaneous rate and is convert to a proportional natural mortality for the Euler-Lotka model.
+
+The data also contains the number of fish harvested by the fishery each year and for each age.
+This can be combined with the assessed numbers at age to get an estimate of fishing mortality in each year for each age.
+
+$$
+FM_{y,a} =  \frac{Catch_{y,a}}{N_{y,a}}
+$$
+This is combined with the natural mortality to get a total mortality estimate ($Z_{y,a}$) for each age in each year
+
+$$
+Z_{y,a} =  FM_{y,a} + NM_{y,a}
+$$
+### Population Growth Rates $\lambda$
+
+The fecundity, natural mortality, and fishing mortality estimates were then used to obtain an estimate of $\lambda$ for a given year from the Euler-Lotka equation and used to predict the abundance in the following year.
+
+$$
+N_{y+1} = \lambda_{y} N_{y}
+$$
+The Euler-Lotka model was fit using an iterative minimization process, where predicted abundance in the following year was compared to the abundance estimate from the stock assessment for the corresponding year ($N_{y+1}$).
+Where necessary, the annual age-specific fecundity and natural mortality estimates were adjusted until the $\lambda$ estimate from the Euler-Lotka equation resulted in an abundance time-series estimate ($N_{y+1}$) that was within 5% of the abundance estimates from the stock assessment (median difference was `r med.per.diff`).
+This tolerance ensured that our analyses reflected the same understanding of stock productivity, natural mortality and fecundity as in the current assessments; effectively this methodology treats the abundance estimates from the stock assessments as the 'truth'.
+
+The life table reconstruction resulted in stock-specific $\lambda$, fecundity, and natural mortality estimates for each year in which data were available accounting for the age structure and life history characteristics of each stock.
+In other words, we estimated the realized population growth rate using the changes in the population size of the stocks from year to year (realized population growth rates), based on the amount of mortality experienced and annual reproductive success.
+The realized $\lambda$
+included fishing mortality  ($\lambda_{F>0}$), although this method enabled the theoretical population growth rate in the absence of fishing  ($\lambda_{F=0}$) could also be calculated directly fomr the annual the natural mortality and fecundity estimates.
+
+<!-- For consistency in the Euler-lotka estimates across all the stocks, the first age used in the analysis was 'age 0' (which is simply an estimate of abundance of fish in the year they were born).
+For some stocks this information is not available (see Table X, **possibly in an Appendix where we have meta-data**).
+For the stocks in which age 0 information is unavailable, an estimate of the abundance of the younger age classes were back calculated using average natural mortality provided for the youngest age class available.
+-->
+
+## Density Dependence
+
+Life table analyses make no assumptions about population regulation and thus do not incorporate a density-dependent relationship between spawners and recruits (Reference?).
+However, the data itself could be explored for evidence of density-dependence by modelling the estimated annual population growth rate against the proportion of maximum abundance observed that year for each stock.
+This was done twice, once using  ($\lambda_{F=0}$) and once using ($\lambda_{F>0}$).
+Negative density dependence is observed when $\lambda$ increases as abundance declines, positive density dependence occurs when $\lambda$ declines with increasing abundance, while density independence is observed when $\lambda$ is not impacted by changes in abundance.
+
+Generalized Additive Mixed Models were used to allow for some non-linearity in the relationships (CITE MCGV and WOOD), the overall effect and the effect for each stock was modelled as
+
+\begin{align}
+\lambda_{i,j} \sim N(0,\sigma^2_{i,j}) \\
+E(\lambda_{i,j}) = \mu_{i,j} \\
+log(\mu_{i,j}) =  Prop_{i} + Stock_{j}  \times Prop_{i} \\
+Stocks_{i,j} \sim N(0,\sigma^2_{Stocks})
+\end{align}
+
+The interaction was modeled using the *fs* basis using the mgcv package in R, this treats the smooth curves as random effects and is used when a factor has a large number of levels (CITE!).
+Various alternative modelling methods were explored (various model formulations, alternative error distributions, etc.) but all models had similar challenges overcoming either the underlying non-normality or the heteroskedasticity of the data.
+As such, the uncertainty surrounding the model output should be treated with caution, while we discuss the general trends this model provides we attempted to avoid discussion of the statistical significance of the trends.
+
+## Demographic Parameters
+
+There are numerous demographic parameters that can be derived from the outputs of the life table reconstruction.
+Here we focus on two that are strongly linked to recovery potential: lifetime reproductive success and generation time.
+Lifetime reproductive success describes the average number of spawners produced by one female spawner throughout her lifetime
+
+## Lifetime Reproductive Success
+
+The lifetime reproductive success ($R_0$)  was calculated for each cohort in which fecundity and natural mortality were available for all age classes.
+It was calculated using only natural mortality (F=0) and with the combined effect of natural mortality and fishing mortality (F>0).
+This was calculated for each cohort as
+
+$$
+R_0 = \sum_{x=\alpha}^{\omega} s_x f_x
+$$
+
+*Here we are treating the plus group as effectively 'terminal', i.e., it assumes that after the last age class the individuals make no contribution, which means these values are probably a bit low, but at this age they really aren't making much of a contribution on average*.
+
+## Generaion Time
+
+The generation time was defined as the mean age of the spawners of the observed recruits in a cohort over its lifetime ($T_G$), here we calculated this for each cohort in which fecundity and natural mortality were available for all age classes.
+It was calculated twice, using only natural mortality (F=0) and with the combined effect of natural mortality and fishing mortality (F>0).
+
+$$
+T_G = \frac{\sum_{x=\alpha}^{\omega} x s_x f_x}{\sum_{x=\alpha}^{\omega}  s_x f_x}
+$$
+
+## Recovery Potential
+
+The annual fecundity and natural mortality values  varied considerably for each stock.
+To account for this variability when evaluating recovery potential, we used a simulated population projection.
+For `r n.dt.sims` simulations, we took a random sample of the annual values for fecundity and natural mortality, used the life table reconstruction to estimate $\lambda$, and calculated abundance in the following year.
+Abundance of each stock was projected over `n.sim.years` years, and the percentage of the simulations in which the population size had doubled was recorded each year.
+For simplicity, we did not allow for density-dependent effects (e.g.
+potential population decline as abundance exceeds carrying capacity) because of uncertainty surrounding potential maximum population size for each species.
+Once a population had doubled, it was considered to have remained at that abundance or greater for the remainder of the projection.
+
+<!--chapter:end:tmp-03-methods.Rmd-->
+
+# Results {#reses-peses}
+
+<!-- Throughout the results we will focus primarily the six most commonly found species in the analysis (*Gadus morhua, Melogrammus aeglefinus, Clupie harengus, Plueronecties platessa, Polluck virens* and *Solea Solea*).
+The complete results for all of the stocks included in the analysis can be found in the Supplemental material.
+-->
+
+## Population growth rates ($\lambda$)
+
+The overall median population growth rate when excluding the effects of fishing ($\lambda_{F=0}$) was `r med.lambda.F0`, indicating that there was a latent potential for population growth for these stocks of approximately `r med.r.F0`%.
+When the effect of fishing was accounted for, the median population growth rate ($\lambda_{F>0}$) declined to `r med.lambda.F`, which suggested that the populations in this analysis may have been over-fished by approximately `r -med.r.F`% annually.
+However, for many of the stocks included in this analysis large recruitment events resulted in large estimates of $\lambda_{F>0}$, in some years, this led to a skewed distribution of the lambda estimates, with these large events being an integral component of the stocks population dynamics (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-bx-other-fig)).
+The mean $\lambda_{F>0}$ for the stocks in this analysis was `r mn.lambda.F` which would suggest there remains scope for population growth even after fishing.
+The mean$ \lambda_{F>0}$ was lower than the median for just `r n.stocks-n.mn.higher.med.fish` of the `r n.stocks` in this analysis.
+The majority of these stocks (`r n.nw.ice`) were in the central or NW Atlantic, and this included `r n.cod.low.mn`  of the `r n.cod` Atlantic cod stocks in this analysis.
+
+There were regional and species specific trends in both $\lambda_{F=0}$ and $\lambda_{F}$.
+Haddock (*M.
+aeglefinus*) and Atlantic cod (*G.
+morhua*) stocks had some of highest variability in lambda, both at the stock level and between stocks (Figure \@ref(fig:lambda-sd-fig)).
+For these two species, the variability of lambda within a stock declined as you moved from the Eastern Atlantic to the Western Atlantic (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig))).
+The pattern was more pronounced for Atlantic cod, with stocks in the eastern Atlantic tending to have relatively low within stock variability.
+The two other species with stocks found in the NW and NE Atlantic (*C.harengus* and *P.
+virens*) the variability of lambda between the stocks was much lower than for Haddock and Atlantic cod and there were no clear differences between regions (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig))).
+This was largely due to the within stock lambda variability being lower than the within stock variability of Haddock and Atlantic cod stocks in the NE Atlantic (Figure \@ref(fig:lambda-bx-6-fig)).
+Two other stocks (*A.
+dubious* and *T.
+esmarkii*) in the North Sea had highly variably lambda estimates, though notably the lambda was less variable than the estimates for Haddock and Atlantic cod in this area (Figure \@ref(fig:lambda-bx-other-fig)).
+For the remainder of other stocks in this analysis, years in which the value of $\lambda_{F=0}$ exceeded 1.5 were more rare.
+Exceptions to this included *M.
+merlangus* in the Celtic Sea, *P.
+dentatus* and *S.
+Chrysops* in the NW Atlantic, and the Gulf of Alaska *T.
+chalcogramma* stock in the Pacific Ocean (Figure \@ref(fig:lambda-bx-other-fig)).
+
+## Density Dependence
+
+Overall, the evidence suggested that negative density dependence was common as both $\lambda_{F=0}$ and $\lambda_{F>0}$ increased as abundance declined (Figure \@ref(fig:dd-overall-plt)).
+The strength of density dependence appeared to be more pronounced at low and high abundance levels (i.e., changes in abundance had larger impacts on $\lambda$ when abundance was below $\approx$ 0.4 or above $\approx$ 0.7).
+$\lambda_{F=0}$ only declined below 1 when the stocks approached their maximum observed abundance ($\approx$ `r pa.lam.nf.at.one`%), indicating that in the absence of fishing there was a latent capacity for population growth in these stocks.
+However, when accounting for fishing mortality, $\lambda_{F>0}$ was below 1 until the stocks were below approximately `r pa.lam.fish.at.one`% of their maximum abundance.
+At lower abundances, the rate of increase in $\lambda_{F>0}$ was higher than $\lambda_{F=0}$, likely due to reductions in fishing mortality at low abundance, but overall $\lambda_{F>0}$ was lower than $\lambda_{F=0}$, suggesting that some fishing mortality was common even at very low abundance (Figure \@ref(fig:dd-overall-plt)).
+
+Generally, there was an increase in the variability of the $\lambda$ estimates as abundance declines, largely driven by an increase in the magnitude of the maximum value of $\lambda$ and a small increase in the frequency of low $\lambda$ values (Figure \@ref(fig:dd-overall-plt)).
+For example, values of $\lambda_{F>0}$ > `r pa.lam.fish.low.bigs` were not observed at abundances > `100*pa.big.threshold`% of the maximum (similar trends were observed for $\lambda_{F=0}$, with only one point being above `r pa.lam.nf.low.bigs` when the abundance was > `r 100*pa.big.threshold`% of the maximum).
+Similarly, the percentage of $\lambda_{F>0}$ values below `r lam.low.threshold` was `r 100*prop.low.high.abund`% when the proportion of the abundance was >= 0.3, but this increased to `r 100*prop.low.low.abund`% of the data when the proportion of the abundance was below 0.3.
+
+However, these general patterns were highly variable between stocks.
+All of the stocks included in this analysis had $\lambda_{F=0}$ estimates > 1 at their lowest observed abundances (Table \@ref(tab:tab-lambdas) and Figure \@ref(fig:dd-nf-stock-plt)).
+Stocks in the Northwest Atlantic (particularly Atlantic cod) and Alaska had some of the lowest $\lambda_{F=0}$ estimates at low abundance, while several stocks in the North Sea had among the highest $\lambda_{F=0}$ estimates at low abundance (Table \@ref(tab:tab-lambdas)).
+Of the `r n.bl.40` stocks that had declined below 40% of the maximum abundance, only `r `n.low.40.nf` of the stocks had a $\lambda_{F=0}$ estimates < 1 at 40% of their maximum abundance; when the effects of fishing were included `r `n.low.40.nf` of the stocks had $\lambda_{F>0}$ estimates below 1 (Table \@ref(tab:tab-lambdas)).
+
+For the vast majority of stocks the lowest values of both $\lambda_{F=0}$ (`r n.low.lam.at.max.nf` of `r n.stocks`) and $\lambda_{F>0}$ (`r n.low.lam.at.max.fish` of `r n.stocks`) were found near the maximum abundance in the time series (Figures \@ref(fig:dd-nf-stock-plt) and \@ref(fig:dd-fish-stock-plt)).
+Atlantic cod in the Northwest Atlantic comprised `r n.cod.lam.not.at.max.nf` of the `r n.stocks - n.low.lam.at.max.nf` stocks in which the lowest $\lambda$ was observed below the maximum abundance, the low $\lambda$ occurred at population abundances that were remarkably similar for these Atlantic cod stocks (ranging between `r pa.low.cod.min` and `r pa.low.cod.max`).
+For two of the `r n.stocks - n.low.lam.at.max.nf` stocks, the lowest $\lambda_{F=0}$ estimates were less than 0.005 smaller than the estimate at the maximum abundance, for the other four stocks the decline in $\lambda_{F=0}$ from the highest abundance observed was somewhat pronounced, ranging from `r low.4.lam.40.nf` to `r low.lam.40.nf` (Tables \@ref(tab:tab-lambdas) and \@ref(tab:tab-lamda-diffs) and Figures \@ref(fig:dd-nf-stock-plt) and \@ref(fig:dd-fish-stock-plt) ).
+
+## Demographic Parameters
+
+The lifetime reproductive output and generation length were estimated for each cohort in which data were available.
+When excluding fishing mortality, the overall median lifetime reproductive output, (i.e., the number of females produced by one female that survive to reproduce) was `r r0.med` (mean = `r r0.mn`; Figures \@ref(fig:r0-6-plt) and \@ref(fig:r0-other-plt)).
+When the realized fishing mortality was accounted for, the median reproductive output dropped to `r r0.med.fish` (mean = `r r0.mn.fish`), this again highlighted the importance of large reproductive events for survival of these stocks and the latent capacity for population growth (Figures \@ref(fig:r0-6-plt) and \@ref(fig:r0-other-plt)).
+For stocks which were found across the north Atlantic, the lifetime reproductive output when excluding fishing mortality tended to decline as your move west, this again was most evident for the Atlantic cod stocks.
+While the reproductive potential of cohorts within a stock could be highly variable, there were no clear temporal trends in the $R_0$ (Figures \@ref(fig:r0-nf-ts-plt) and \@ref(fig:r0-fish-ts-plt)).
+
+The generation lengths tended to become more similar between stocks both intra- and inter-specifically when accounting fishing mortality (Figures \@ref(fig:gl-6-plt) and \@ref(fig:gl-other-plt)).
+In addition, the generation length of *C.
+harengus*, generally considered a short lived species, in the Central and NW Atlantic tended to be higher than the generation length of Atlantic cod and haddock, especially for the stocks in the NE Atlantic (Figure \@ref(fig:gl-6-plt)).
+There were no obvious patterns in the temporal trends in the generation length (Figures \@ref(fig:gl-nf-ts-plt) and \@ref(fig:gl-fish-ts-plt)).
+
+## Recovery Potential
+
+The recovery potential in the absence of fishing was relatively high for the majority of species (Figure \@ref(fig:dub-time-map)).
+Of the `r n.stocks` stocks in this analysis, `r n.dub.10` had a high recovery potential (we define 'high' as at least `r 100*dub.p.high`% of the simulations having experienced a doubling in size) within 10 years, by year 20 this had increased to `r n.dub.20` stocks (Figure \@ref(fig:dub-ts)).
+
+The stocks in which recovery potential was low (we define low as < `r 100*dub.p.low`% of the simulations experiencing a doubling in size) exhibited clear regional trends.
+Of the `r n.not.dub.20` stocks in this analysis in which the recovery potential was low after 20 years, `r n.alaska.slow` of the stocks were in Alaska (`r n.alaska` stocks in total), and `r n.nwa.slow` stocks in NAFO Regions 2-4 in the NW Atlantic (`r n.nafo.24` stocks were in NAFO Regions 2-4).
+This contrasts to only `r n.nea.slow` of the `r n.nea` stocks in the NE Atlantic with a low recovery potential within 20 years in the absence of fishing (Figure \@ref(fig:dub-time-map)).
+
+The recovery potential was influenced both by $\lambda_{F=0}$ and the variability in $\lambda_{F=0}$.
+Stocks with a median $\lambda_{F=0} < 1$  had moderate (defined as stocks in which 50-75% of the simulations doubled within 20 years) to high (> 75% doubled in size within 20 years) recovery potential whenever the standard deviation in lambda was greater than approximately 0.4 (Figure \@ref(fig:dub-vs-sd)).
+Stocks with a median $\lambda_{F=0}$ near 1 and with low variability were the stocks in which the recovery potential tended to be categorized as low (< 50% of the simulations doubled within 20 years).
+
+<!--chapter:end:tmp-04-results.Rmd-->
+
+# DISCUSSION {#disin}
+
+I think we disagree with @kindsvaterTenPrinciplesEvolutionary2016 because we can't generalize based on life-history very easily (cod haddock herring).
+
+Looks like density dependence is real.
+Dave's pet theory is there is solid evidence of density dependence for many stocks above around 0.4, below 0.4 the evidence suggest that density dependence weakens for some stocks, BUT, some stocks have an ability to very occasionally very spectacularly take advantage of the environment.
+But not all stocks and species have this ability and the strength and frequency seems to be influenced by where you live and what species you are.
+Little evidence for high lambda for most stocks in the NW Atlantic, while many stocks assessed in the North Sea had anomalously high lambdas in 1 or more years.
+Cod show this  perfectly....
+
+Looks like the median lambda is around 0.2 at low abundance (mean is much higher because outliers) for many stocks.
+So potential growth at low abundance is around 20%, tends to trend towards 0 as you approach the maximum observed abundance.
+This is very interesting b/c on average is suggests that the maximum observed abundance may be a reasonable proxy for the carrying capacity of a stock.
+Of course there is a great deal of variability around this, which may be related to the timing of the start of the time series in relation to historical fishing activity, fishing pressure, environmental variability, etc...
+but still it is kinda interesting.
+
+The recovery potential for some species is tied to the variability in their growth rate...
+Based on historically observed lambdas, all the Haddock stock in this analysis were likely to double in size within a decade of fishing cessation.
+The worst situation is low lambda + low variability...
+you can have a low lamda 'most of the time', but if highly variable the stock can take off (this in many ways is what fisheries science is based on)...
+Also of note these large events do tend to be far more likely when abundance is < 40% of maximum (of course this would be in part because it's easier to go from having \$10 to \$20 than it is to go from \$1,000 to \$2,000).
+
+Idea- realized productivity of cod/haddock has been highly variable.
+But from life history theory you would have expected that to be herring/smelt.
+Episodic recruitment events.
+(boom and bust?) not population boom but more like a baby boom.
+
+Likelihood of stock collapse related to life history characteristics, maybe reframe relative to large productivity events of cohorts – link to idea of cod/haddock above.
+No expectation that intersection between life history traits and environmental conditions to result in such marked differences among populations within a species in realized productivity.
+
+Center around the idea of equilibrium theory? That management might be fairly good for stocks that aren’t very variable, but when you make a decision based on averages you can make really bad ones.
+
+By ignoring the density dependence patterns observed in this analysis, the doubling time analysis would overestimate the doubling time for stocks that were at low abundance with classic negative density dependence dynamics, while it would underestimate it for stocks with positive density dependence.
+Here perhaps talk about infrequent big events and how using a theoretical rmax within a logistic model isn't a good idea because this will way over-estimate recovery potential at low abundance.
+
+The optimization procedure assumes that both the estimates of abundance and the fishery removals from the stock assessment are correct.
+*A couple sentences about why fisheries removals may be underestimated*.
+This would result in the estimates of the $\lambda$ excluding fishing mortality in this analysis being lower than reality, as this 'missing' mortality was accounted for by reductions in either fecundity or an increase in natural mortality.
+The optimization routine resulted in a median decrease in the no-fishing $\lambda$ estimates of approximately `r med.lam.per.diff`%, the overall directionality of this change is consistent with fishing mortality being generally underestimated.
+
+Fisheries appear to slightly weaken the effects of density dependence overall.
+Maybe due to fisheries having positive density dependence?
+Seemingly below around 0.5 fishing leads to a positive lambda, below 0.5 it is a negative lambda...
+that's kinda kooky cool!
+
+The stocks which reached very low abundance (< 10% of maximum) tended to have high values of lambda, suggesting strong compensation in stocks when they are at extremely low abundance.
+Oddly, the path to this isn't linear, and positive density dependence (or at least density independence was evident between 10 and 40% of maximum abundance).
+
+Probably something worth citing in here @thorsonPredictingRecruitmentDensity2020
+
+<!--chapter:end:tmp-05-discussion.Rmd-->
+
+<!-- Do not edit this file! -->
+
+\clearpage
+
+# REFERENCES {-}
+
+<!--chapter:end:tmp-06-references.Rmd-->
+
+---
+output:
+  word_document: default
+  html_document: default
+editor_options:
+  chunk_output_type: console
+---
+\clearpage
+\newpage
+
+# Tables {-}
+
+```{r, process}
+# This will be the meta data really...
+# remove columns we don't need.
+
+rm.meta <- which(names(meta.sub) %in% c("Meeting_or_reference","G.short","G.Species","Manage.short","LME","Area.broad","Area.long","Area.narrow","Stock.short","Stock","Model","Case","Notes","Area"))
+meta.4.tab <- meta.sub[,-rm.meta]
+re.ord <- c(8,2:7,1)
+meta.4.tab <- meta.4.tab[,re.ord]
+names(meta.4.tab) <- c("Stock", "Order", "Family", "Genus", "Species", "Minimum Age", "Maximum Age", "Management Body")
+
+```
+
+```{r,tab-lambdas}
+# The table with the lambda values
+csas_table(comp.lam.res.tab,caption ="A comparison of the $\\lambda_{F=0}$ and $\\lambda_{F>0} estimates for stock at the minimum and maximum abundance, along with the estimate at 40\\% of the maximum abundance.
+values greater than 1 indicate that the population would be expected to increase in size, while values less than 1 indicate the population is likely to decline in size")
+```
+
+\newpage
+
+```{r,tab-lamda-diffs}
+# Now make the table for the differences
+csas_table(comp.lam.diff.res.tab,caption ="A comparison of the difference in $\\lambda_{F=0}$ and $\\lambda_{F>0} for each stock at the minimum and maximum abundance, along with the change at 40\\% of the maximum abundance.
+Positive values indicate that the $\\lambda$ estimae has increased as abundance declines (consistent with negative density dependence), while negative values indicate the $\\lambda$ estimate has declined (considtent with positive density dependence)")
+```
+
+```{r,tab-meta}
+# Now make the table for the differences
+csas_table(meta.4.tab,caption ="Summary of the stocks included in this analysis.  The minimun and maximum ages are what was used in the stock assessment.")
+```
+
+<!--chapter:end:tmp-07-tables.Rmd-->
+
+---
+output:
+  pdf_document:
+    fig_caption: yes
+    extra_dependencies: float
+linkcolor: blue
+header-includes: \usepackage{float}
+editor_options:
+  chunk_output_type: console
+---
+
+```{r, include=F, echo=F}
+knitr::opts_knit$set(eval.after = "fig.cap")
+knitr::opts_chunk$set(fig.pos = 'H')
+options(knitr.kable.NA = '')
+require(tidyverse)
+options(tinytex.verbose = TRUE)
+
+```
+
+# Figures {-}
+
+```{r lambda-bx-6-fig, echo=F, fig.cap="$\\lambda$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"))
+
+```
+
+\newpage
+```{r lambda-bx-other-fig, echo=F, fig.cap="$\\lambda$ estimates for the remainded of the stocks in this analysis, plotted by the location of the stock.
+The abreviated species name is provided on the x axis."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"))
+
+```
+
+\newpage
+```{r lambda-sd-fig, echo=F, fig.cap="Standard deviation of the $\\lambda$ estimates for each stock, ordered by species, in this analysis. "}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"))
+```
+
+\newpage
+```{r dd-overall-plt, echo=F, fig.cap="Density dependence of $\\lambda$ The top panel shows $\\lambda_{F=0}$ against the proportion of maximum abundance, with a GAM smooth and the GAM estimated 95\\% confidence interval.
+The middle panel shows $\\lambda_{F>0}$ against the proportion of maximum abundance, with a GAM smooth and the GAM estimated 95% confidence interval.
+The bottom panel compares the GAM smooths for $\\lambda_{F=0}$ and $\\lambda_{F>0}$."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_overall_",what.2.tune,".png"))
+```
+
+\newpage
+```{r dd-nf-stock-plt, echo=F, fig.cap="Density dependence of $\\lambda_{F=0}$ for each stock in the analysis plotted regionally."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"))
+```
+
+\newpage
+```{r dd-fish-stock-plt, echo=F, fig.cap="Density dependence of $\\lambda_{F>0}$ for each stock in the analysis plotted regionally."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_fish_stocks_",what.2.tune,".png"))
+```
+
+\newpage
+```{r r0-6-plt, echo=F, fig.cap="$R_0$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"))
+```
+
+\newpage
+```{r r0-other-plt, echo=F, fig.cap="$R_0$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"))
+```
+
+\newpage
+```{r r0-nf-ts-plt, echo=F, fig.cap="$R_0$ estimates for every cohort for each species excluding the effects of fishing."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_nf_",what.2.tune,".png"))
+```
+
+\newpage
+```{r r0-fish-ts-plt, echo=F, fig.cap="$R_0$ estimates for every cohort for each species including the effects of fishing."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_fish_",what.2.tune,".png"))
+```
+
+\newpage
+```{r gl-6-plt, echo=F, fig.cap="Generation length estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"))
+```
+
+\newpage
+```{r gl-other-plt, echo=F, fig.cap="Generation length estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"))
+```
+
+\newpage
+```{r gl-nf-ts-plt, echo=F, fig.cap="Generation length estimates for every cohort for each species excluding the effects of fishing."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_nf_",what.2.tune,".png"))
+```
+
+\newpage
+```{r gl-fish-ts-plt, echo=F, fig.cap="Generation length estimates for every cohort for each species including the effects of fishing."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_fish_",what.2.tune,".png"))
+```
+
+<!-- Now for the Doubling time -->
+
+\newpage
+```{r dub-time-map, echo=F, fig.cap="Doubling time estimate for each stock with no fishing mortality."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"))
+```
+
+\newpage
+```{r dub-ts, echo=F, fig.cap="The number of stocks which doubled in size by a given year with no fishing mortality  The dashed line represents the 77 stocks in the analysis."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_time_series_",what.2.tune,".png"))
+```
+
+\newpage
+```{r dub-vs-sd, echo=F, fig.cap="The recovery potential (low, moderate, or high) of each stock after 20 years compared to the median $\\lambda_{F=0}$ and the standard deviation of $\\lambda_{F=0}$."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"))
+```
+
+# Supplemental Figures {-}
+
+<!--chapter:end:tmp-08-figures.Rmd-->

### 2024-05-21 Drafts/Paper_1/tmp-03-methods.Rmd
mid-edit update

--- 2024-05-10 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
@@
----
-output: word_document
-editor_options: 
-  chunk_output_type: console
----
+# Methods {#meth}
 
-```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4,include=F,message=F}
+## Data
 
-if(load.results==F)
-{
-  Stocks <- ASR.long |> 
-                      collapse::fsubset(!is.na(value)) |>
-                      collapse::fgroup_by(Stock, type) |>
-                      collapse::fsummarize(count=length(unique(value))) |>
-                      collapse::fgroup_by(Stock) |>
-                      collapse::fsummarize(types=length(unique(type))) |>
-                      collapse::fsubset(types==5) |>
-                      collapse::fselect(Stock)
+This analysis used age structured fisheries data obtained from stock assessments for stocks in the Atlantic and Pacific Oceans [@charbonneauAgestructuredmarinefishdatabase2022; @charbonneauEffectsFishingMortality2022].
+This repository had sufficient data to run the analysis for 77 stocks from NE Atlantic, NW Atlantic, and the North Pacific, this included stocks managed by International Council for the Exploration of the Sea (ICES; `r n.stock.ices`), NOAA (NOAA;`r n.stock.noaa`), and Fisheries and Oceans Canada (DFO; `r n.stock.dfo` stocks).
+The time series used in this analysis started as early as `r min.year` and the most recent data were from `r max.year`, the average length of the time series for the stocks included in this analysis was `r mn.ts.len` years and the number of years used ranged between `r min.ts.len` and `r max.ts.len` years.
+The stocks used represented `r num.orders` orders, with the most represented orders being the Gadiformes (`r num.gads` stocks), Pleuronectiformes (`r num.pleur` stocks) and Clupeiformes (`r num.clup` stocks).
+The other three orders had relatively few stocks included in the analysis, with `r num.perci` Perciform stocks, `r num.scomb` Scombriform stocks, and just `r num.scorp` Scorpaeniform stock.
+The most common species in this analysis were Atlantic cod (*G.
+morhua*) and the majority of the stocks (`r n.six`) in this analysis were represented by one of six species (*G.
+morhua* (`r num.cod`), *C.
+harengus* (`r num.her`), *M.
+aeglefinus* (`r num.had`),  *P.
+virens* (`r num.pol`), *S.
+solea* (`r num.sol`), and *P.
+platessa* (`r num.plat`)).
 
-  ASR.tmp <- ASR.long 
-  ASR.tmp$age <- as.numeric(ASR.tmp$age)
-  ASR.stocks <- ASR.tmp |> 
-                          collapse::fsubset(Stock %in% Stocks$Stock) |>
-                          collapse::fsubset(!is.na(value)) |>
-                          collapse::roworder(Stock, Year, type, age)
+These data included age-specific estimates of abundance, weight, biomass, maturity, natural mortality, and fishery removals (Table \@ref(tab:tab-meta)), these data were all required to calculate survival-at-age and fecundity-at-age and to estimate the annual productivity of these stocks.
+For the age structured analysis, the last age class was considered the 'terminal' age in the analysis, thus we implicitly assumed there was no contribution to productivity from older aged individuals.
+In addition, for the majority of the stocks the first age class was age 1 (`r n.age.1` stocks) while another `r n.age.2.plus` of the stocks have a first age of 2 or greater.
+The young age classes not included for these stocks (e.g.
+Age 0) consisted of immature individuals that do not contribute to the productivity of the stock; however it has been noted that the exclusion of immature age classes in these types of analyses may lead to a slight overestimate of productivity [@pardoMaximumIntrinsicRate2016].
 
-  # print(Stocks)
-  Stocks <- Stocks$Stock
+## Life Table Reconstruction
 
-  # Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
-  #Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
-  # Esmarki doesn't work great as it is assessed using a quarterly model.
-  #Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
-  #i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
-  years.tmp <- NULL
-  pnm.tmp <- NULL
-  waa.tmp <- NULL
-  ages.tmp <- NULL
-  rem.tmp <- NULL
-  mx.tmp <- NULL
-  NE.tmp <- NULL
-  vpa.tmp <- NULL
-  am.tmp <- NULL
-  #mr.tmp <- NULL
-  abund.tmp <- NULL
-  full.abund.tmp <- NULL
-  full.rem.tmp <- NULL
-  fs.tmp <- NULL
-  for(i in Stocks)
-  {
-  print(i)
-  ASR.sub <- ASR.long |>
-    collapse::fselect(Year, Stock, type, age, value) |>
-    collapse::fsubset(Stock==i)
+The discrete time Euler-Lotka  equation was first proposed by Euler in 1760 (subsequently published by @moserGesetzeLebensdauer1839) and is a special case of the continuous time demographic model first proposed by Lotka in 1907 [@lotkaRelationsBirthRates1907; @sharpeProblemAgedistribution1911; @lotkaRelationBirthRate1918]:
 
-    # Dropping the first 7 years as the 8 year olds are all missing
-  if(i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR.sub <- ASR.sub |> collapse::fsubset(Year >= 1972)
-  # maxage <- max(as.numeric(ASR.sub$age[!is.na(ASR.sub$value)]))
-  # maxYear <- max(ASR.sub$Year[!is.na(ASR.sub$value)])
-  # minYear <- min(ASR.sub$Year[!is.na(ASR.sub$value)])
-  # forplot <- ASR.sub[as.numeric(ASR.sub$age) < (maxage+1) & ASR.sub$Year %in% minYear:maxYear,]
-  # 
-  # # summary plots
-  # print(ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
-  #         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
-  #         theme_bw() + 
-  #         ggtitle(i)
-  # )
+$$
+1 = \sum_{x=\alpha}^{\omega} \lambda^{-x} s_x f_x dx
+$$
 
-  age.mat <- ASR.sub |> collapse::fsubset(type=="AM") |> dplyr::rename(AM=value) |> collapse::fselect(-type)
-  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
-  # in case that changes later...
-  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
-  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
-  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
-  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
-  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
-  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0
+Where $x$ is the age, $\alpha$ is the age at first reproduction, $\omega$ is the maximum age, $\lambda$ is the discrete rate of population growth ($\lambda = e^r$), $s_x$ is the survivorship to age $x$, and $f_x$ is the fecundity of individuals of age $x$.
+Note that the discrete time Euler-Lotka equation can be shown to be the characteristic polynomial of the Leslie Matrix, where $f_0$ is the fecundity of the first age class with mature individuals [@leslieUseMatricesCertain1945, @caswellMatrixPopulationModels2001].
+The available stock assessment data are used to calculate survival-at-age and fecundity-at-age to estimate $\lambda$, assuming that each stock represents a discrete population with individual dynamics.
 
-  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
-  nat.mort <-  ASR.sub |> collapse::fsubset(type=="NM") |> dplyr::rename(NM=value) |> collapse::fselect(-type)
-  abund <- ASR.sub |> collapse::fsubset(type=="Num") |> dplyr::rename(Num=value) |> collapse::fselect(-type)
-  weight.age <- ASR.sub |> collapse::fsubset(type=="WA") |> dplyr::rename(WA=value) |> collapse::fselect(-type)
-  if(i == Stocks[30]) weight.age$WA <- weight.age$WA/1000
-  removals <- ASR.sub |> collapse::fsubset(type=="Catch") |> dplyr::rename(Catch=value) |> collapse::fselect(-type)
+<!-- \begin{align} -->
+<!--   \begin{bmatrix} -->
+<!--     f_0  & f_1 & f_2  & f_3    & ...          & f_{\omega-1} \\ -->
+<!--     s_0  & 0   & 0    & 0      & ...          & 0 \\ -->
+<!--     0    & s_1 & 0    & 0      & ...          & 0 \\ -->
+<!--     0    & 0   & s_2  & 0      & ...          & 0 \\ -->
+<!--     0    & 0   & 0    & \ddots & ...          & 0 \\ -->
+<!--     0    & 0   & 0    & ...    & s_{\omega-2} & 0 \\ -->
+<!--   \end{bmatrix} -->
+<!-- \end{align} -->
 
-  data <- age.mat |>
-    full_join(nat.mort) |>
-    full_join(abund) |>
-    full_join(weight.age) |>
-    full_join(removals)
+### Fecundity-at-age
 
-  # Aahh??  Is this NA dropping useful data, needed to quick fix the age at maturity data...
-  data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
-  data <- data[data$available==T,]
+The number of spawners in year $y$ and age class $a$ ($SSN_{y,a}$) is the proportion of mature individuals ($Mat_{y,a}$) multiplied by the number of individuals in each age
 
-  # Tidy up the data for input...
-  data$prop.nat.mort <- 1-exp(-data$NM)
-  #prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))] <- 1-exp(-prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))])
+$$
+SSN_{y,a} = Mat_{y,a} N_{y,a}
+$$
+The Euler-Lotka equation requires fecundity to be the number of offspring produced by each female in each age class.
+Given the uncertainty of both fertilization and egg survival, using the number of eggs at a given length or size is inappropriate.
+However, these data do have the number of recruits produced each year, and this can be combined with the spawning stock biomass to obtain an estimate of the number of recruits produced per kilogram of spawning biomass $RPS_{y}$, this is calculated as
 
-  rem <- data |> collapse::fgroup_by(Year) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
-  #rem <- data |> dplyr::group_by(Year,.drop=F) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
+$$
+RPS_{y} = R_{y} SSB_{tot,(y-ra)} 
+$$
 
-  # Never run, so not doing anything.
-  # missing_rem<- NULL
-  # if(any(is.na(rem$rem))) 
-  # {
-  #   missing_rem <- unique(data$Year)[which(is.na(rem$rem))]
-  #   rem$rem[is.na(rem$rem)] <- median(rem$rem, na.rm=T)
-  # }
+Where $SSB_{yot,y-ra}$ is the total spawning stock biomass in year $y$.
+$R_{y}$ is the number of individuals in the youngest age class available for a specific stock (hereafter referred to as recruits) offset temporally by the age of the recruits.
+For example, if the age of the recruits ($ra$) is 2 years , we assume that the recruits in 2010 were produced by the spawning stock biomass in 2008 ($SSB_{tot,y-ra}$).
+The number of recruits produced by each age class ($RPA_{y,a}$) can then be calculated by multiplying the spawner biomass in each age class $SSB_{y-ra,a}$ by the number of recruits produced per kilogram of SSB
 
-  #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
-  years <- data |> dplyr::pull(Year) |> unique() |> sort()
+$$
+RPA_{y,a} =  SSB_{(y-ra),a} RPS_{y}
+$$
+This method does not account for any changes in reproductive success by age, each kilogram of spawning biomass contributes the same to the total total reproductive output, irrespective of their age.
+Finally, the age-specific fecundity ($Fec_{y,a}$) is calculated as number of offspring produced by each individual in the population.
+This is offset by one year, as the recruits observed in year $y+1$ enter into the Euler-Lotka formulation in year $y$.
 
-  N.end <- sum(data[data$Year==max(years),]$Num)
-  vpa.abund <- data |> dplyr::group_by(Year) |> dplyr::summarize(vpa=sum(Num,na.rm=T)) |> pull(vpa)
+$$
+Fec_{y,a} =  \frac{RPA_{y+1,a}}{SSN_{(y-ra+1),a}}
+$$
+### Suvival-at-age
 
-  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
-  #minage
-  minage <- min(as.numeric(data$age))
-  #maxage
-  maxage <- max(as.numeric(data$age))
-  #recruits
-  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
-  #ssn
-  data$ssn <- data$Num * data$AM
-  #ssb
-  data$ssb <- data$ssn * data$WA #I need to figure out how to line this up with the number of recruits for the right years in the data object.... got it right for the overall r.p.ssb below.
-  #tot.ssb
-  annual <- data |> group_by(Year) |> summarize(tot.ssb = sum(ssb)) |> left_join(annual)
+The number of animals surviving to each age depends on age-specific mortality rates.
+Commercially-exploited fishes experience fishing mortality (F) once they grow large enough to become vulnerable to the gear (reference).
+Fishing mortality combines with natural mortality (M) to give total mortality (Z) affecting each age class in each year.
+Varying assumptions can be made about natural mortality during stock assessments, where it may be an assumed value for each age (EXAMPLE), allowed to vary over time and by age (EXAMPLE), or input as a constant across ages (EXAMPLE).
+Due to challenges with separability in typical stock assessment models, natural mortality is often assumed for each age class, in some assessments it varies by age and over time, in other assessments it does not.
+Irrespective of this, the stock assessment used in this analysis all provide an estimate of natural mortality by age and year, this value is typically an instantaneous rate and is convert to a proportional natural mortality for the Euler-Lotka model.
 
-  #tst <- data |> group_by(Year) |> summarize(tot.ssn = sum(ssn)) |> left_join(annual)
+The data also contains the number of fish harvested by the fishery each year and for each age.
+This can be combined with the assessed numbers at age to get an estimate of fishing mortality in each year for each age.
 
-  #r.p.ssb This needs to be offset by the age of recruits. So here's my lining this up logic.  For age 0, we get
-  # the recruit and SSB estimates from the same survey, thus these age 0 recruits will have been produced by the SSB in the previous year...
-  # So the R in 1970 were produced by SSB in 1969 when min age =0
-  # If min.age = 1 then R in 1970 is produced by SSB in 1968... and so on.
-  # FIX 1 "Recruit year" = SSB year + min.age + 1 (or min.age +2 as SSB.year is the first column)
-  # Now for RPS there's another wrinkle because of this, because our model is N(1970) = lambda * N(1969) and lambda is made up of lx and mx
-  # so if the recruits show up in 1970, the fecundity term that gets us there (irrespective of the age offset) has to be for 1969, becuase
-  # that gets us to the babies that show up in 1970
-  # FIX 2 So "RPS year, recs.per.age year, and mx year" = SSB year + min.age
-  # I believe this to be correct, but we all need to discuss this to make sure the logic holds.
-  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+2):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage-1)],NA)
-  # recs.per.age
-  data <- left_join(data, annual)
-  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
-  tmp <- NULL
-  for(j in 1:length(years))
-  {
-    tst <- data|> collapse::fsubset(Year == years[j]) |> collapse::fselect(ssb,ssn,Year,age)
-    tst$Year <- tst$Year + minage # We want this to line up the the RPS year, so just adding minage here.
-    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
-    tmp[[j]] <- tst
-  }
-  # Unpack the list
-  ssb.off <- do.call('rbind',tmp)
-  # And merge it with the data object
-  data <- left_join(data,ssb.off,by=c("Year","age"))
-  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
-  # mx
-  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
-  # No longer dividing by 2 because we should really divide recruits and ssn by 2 to be female only, but that's pointless so we roll along with this.
-  data$mx <- data$recs.per.age/data$ssn.offset # if(grepl("males",i)) 
-  #if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
-  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
-  # Easier to remove the years where we don't have recs.per.age...
-  #data <- data |> collapse::fsubset(Year %in% years[(minage+1):length(years)])
+$$
+FM_{y,a} =  \frac{Catch_{y,a}}{N_{y,a}}
+$$
+This is combined with the natural mortality to get a total mortality estimate ($Z_{y,a}$) for each age in each year
 
-  age.mat <- data |> collapse::fselect("Year", "age", "AM") |> 
-                     pivot_wider(names_from=age, values_from = AM) |> collapse::fselect(-Year)
-  prop.nat.mort <- data |> collapse::fselect("Year", "age", "prop.nat.mort") |> 
-                            pivot_wider(names_from=age, values_from = prop.nat.mort) |> 
-                            collapse::fselect(-Year) |> as.data.frame()
+$$
+Z_{y,a} =  FM_{y,a} + NM_{y,a}
+$$
+### Population Growth Rates $\lambda$
 
-  weight.age <- data |> collapse::fselect("Year", "age", "WA") |> pivot_wider(names_from=age, values_from = WA) |> collapse::fselect(-Year)
-  mx <- data |> collapse::fselect("Year", "age", "mx") |> 
-                 pivot_wider(names_from=age, values_from = mx) |> 
-                 collapse::fselect(-Year) |> as.data.frame()
-  # Get the abundance matrix
-  abund.age <- data |> collapse::fselect("Year", "age", "Num") |> 
-                        pivot_wider(names_from=age, values_from = Num) |> 
-                        collapse::fselect(-Year) |> as.data.frame()
+The fecundity, natural mortality, and fishing mortality estimates were then used to obtain an estimate of $\lambda$ for a given year from the Euler-Lotka equation and used to predict the abundance in the following year.
 
-  # Now we can save out the catch and get an instantaneous F
-    data$Catch[is.na(data$Catch)] <- 0
-    data$Exp <- data$Catch/data$Num 
-    # If it is exactly 1 that leads to an Inf, which is annoying, so make it 1.1 and fix it with the rest below
-    data$Exp[data$Exp == 1] <- 1.1
-    # And make this an F
-    data$Fs <- -log(1-data$Exp)
-    if(any(is.na(data$Fs)))
-    {
-      fixers <- which(is.na(data$Fs))
-      print(paste0("Had to replace ",length(fixers), ' exploitation rates for stock ',i))
-      for(f in fixers)
-      {
-        yr <- data$Year[f]
-        fs <- max(data$Fs[data$Year == yr],na.rm=T)
-        data$Fs[f] <- fs
-        data$Exp[f] <- 1-exp(-fs)
-      }
-    }
+$$
+N_{y+1} = \lambda_{y} N_{y}
+$$
+The Euler-Lotka model was fit using an iterative minimization process, where predicted abundance in the following year was compared to the abundance estimate from the stock assessment for the corresponding year ($N_{y+1}$).
+Where necessary, the annual age-specific fecundity and natural mortality estimates were adjusted until the $\lambda$ estimate from the Euler-Lotka equation resulted in an abundance time-series estimate ($N_{y+1}$) that was within 5% of the abundance estimates from the stock assessment (median difference was `r med.per.diff`).
+This tolerance ensured that our analyses reflected the same understanding of stock productivity, natural mortality and fecundity as in the current assessments; effectively this methodology treats the abundance estimates from the stock assessments as the 'truth'.
 
-  full.rems <- data |> collapse::fselect("Year", "age", "Catch") |> pivot_wider(names_from=age, values_from = Catch) |> collapse::fselect(-Year)
-  full.Fs <-  data |> collapse::fselect("Year", "age", "Fs") |> pivot_wider(names_from=age, values_from = Fs) |> collapse::fselect(-Year)
+The life table reconstruction resulted in stock-specific $\lambda$, fecundity, and natural mortality estimates for each year in which data were available accounting for the age structure and life history characteristics of each stock.
+In other words, we estimated the realized population growth rate using the changes in the population size of the stocks from year to year (realized population growth rates), based on the amount of mortality experienced and annual reproductive success.
+The realized $\lambda$
+included fishing mortality  ($\lambda_{F>0}$), although this method enabled the theoretical population growth rate in the absence of fishing  ($\lambda_{F=0}$) could also be calculated directly fomr the annual the natural mortality and fecundity estimates.
 
-    if(i == "DFO_2J3KL_Gadus_morhua")
-    {
-      age.mat[,8:10] <- 1
-      prop.nat.mort[,8:10] <- prop.nat.mort[,7]
-      weight.age[12:14,9:10] <- weight.age[12:14,8]
-      weight.age[15,10] <- weight.age[15,9]
-      mx[12:16,9:10] <- mx[12:16,8]
-      mx[17,10] <- mx[17,9]
-      full.Fs[12:14,9:10] <- full.Fs[12:14,8]
-      full.Fs[15,10] <- full.Fs[15,9]
-      abund.age[12:14,9:10] <- abund.age[12:14,8]
-      abund.age[15,10] <- abund.age[15,9]
-      # I could calculate, but this will get us to the same place...
-      full.rems[12:14,9:10] <- full.rems[12:14,8]
-      full.rems[15,10] <- full.rems[15,9]
-    }
+<!-- For consistency in the Euler-lotka estimates across all the stocks, the first age used in the analysis was 'age 0' (which is simply an estimate of abundance of fish in the year they were born).
+For some stocks this information is not available (see Table X, **possibly in an Appendix where we have meta-data**).
+For the stocks in which age 0 information is unavailable, an estimate of the abundance of the younger age classes were back calculated using average natural mortality provided for the youngest age class available.
+-->
 
-    if(i == "DFO_4T-Spring_Clupea_harengus")
-    {
-      age.mat[6:7,10] <- 1
-      prop.nat.mort[6:7,10] <- prop.nat.mort[6:7,9]
-      weight.age[6:7,10] <- weight.age[6:7,9]
-      mx[6:9,10] <- mx[6:9,9]
-      full.Fs[6:7,10] <- full.Fs[6:7,9]
-      abund.age[6:7,10] <- abund.age[6:7,9]
-      full.rems[6:7,10] <- full.rems[6:7,9]
-    }
+## Density Dependence
 
-    if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
-    {
-      age.mat[30,8] <- 1
-      prop.nat.mort[30,8] <- prop.nat.mort[30,7]
-      weight.age[30,8] <- weight.age[29,8]
-      mx[30:31,8] <- mx[30:31,9]
-      full.Fs[30,8] <- full.Fs[30,7]
-      abund.age[30,8] <- abund.age[30,7]
-      full.rems[30,8] <- full.rems[30,7]
-    }
+Life table analyses make no assumptions about population regulation and thus do not incorporate a density-dependent relationship between spawners and recruits (Reference?).
+However, the data itself could be explored for evidence of density-dependence by modelling the estimated annual population growth rate against the proportion of maximum abundance observed that year for each stock.
+This was done twice, once using  ($\lambda_{F=0}$) and once using ($\lambda_{F>0}$).
+Negative density dependence is observed when $\lambda$ increases as abundance declines, positive density dependence occurs when $\lambda$ declines with increasing abundance, while density independence is observed when $\lambda$ is not impacted by changes in abundance.
 
-    if(i == "ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax")
-    {
-      age.mat[c(14,27,40),5] <- age.mat[1,5]
-      prop.nat.mort[c(14,27,40),5] <- prop.nat.mort[1,5]
-      weight.age[c(14,27,40),5] <- weight.age[c(13,26,39),5]
-      mx[c(14,16,27,29,40,42),5] <- mx[c(14,16,27,29,40,42),6]
-      full.Fs[c(14,27,40),5] <- full.Fs[c(14,27,40),4]
-      abund.age[c(14,27,40),5] <- abund.age[c(14,27,40),4]
-      full.rems[c(14,27,40),5] <- full.rems[c(14,27,40),4]
-    }
-    # Clear out some 0's...
-    if( i == "AFSC_EEBSAI_Limanda_aspera")
-    {
-      mx[5,18] <- mean(unlist(mx[5,c(17,19)]))
-      mx[c(6,8),19] <- mx[c(6,8),18]
-      mx[2:7,20] <- mx[2:7,19] 
-    }
+Generalized Additive Mixed Models were used to allow for some non-linearity in the relationships (CITE MCGV and WOOD), the overall effect and the effect for each stock was modelled as
 
-  # I had filled the years with no SSB data to inform them.  instead I'm going to remove those years...
+\begin{align}
+\lambda_{i,j} \sim N(0,\sigma^2_{i,j}) \\
+E(\lambda_{i,j}) = \mu_{i,j} \\
+log(\mu_{i,j}) =  Prop_{i} + Stock_{j}  \times Prop_{i} \\
+Stocks_{i,j} \sim N(0,\sigma^2_{Stocks})
+\end{align}
 
-   if(minage >0) 
-  {
-    rm <- -(1:minage)
-    years <- years[rm]
-    prop.nat.mort <- prop.nat.mort[rm,]
-    weight.age <- weight.age[rm,]
-    rem <- rem[rm,]
-    mx <- mx[rm,]
-    vpa.abund <- vpa.abund[rm]
-    age.mat <- age.mat[rm,]
-    abund.age <- abund.age[rm,]
-    full.Fs <- full.Fs[rm,]
-    full.rems <- full.rems[rm,]
-   }
-  #   mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
-  #   names(mx) <- names(mx.fill)
-  #  # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
-  #   mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
-  # }
+The interaction was modeled using the *fs* basis using the mgcv package in R, this treats the smooth curves as random effects and is used when a factor has a large number of levels (CITE!).
+Various alternative modelling methods were explored (various model formulations, alternative error distributions, etc.) but all models had similar challenges overcoming either the underlying non-normality or the heteroskedasticity of the data.
+As such, the uncertainty surrounding the model output should be treated with caution, while we discuss the general trends this model provides we attempted to avoid discussion of the statistical significance of the trends.
 
-    years.tmp[[i]] <- years
-    pnm.tmp[[i]] <- prop.nat.mort
-    waa.tmp[[i]] <- weight.age
-    ages.tmp[[i]] <- minage:maxage
-    rem.tmp[[i]] <- rem
-    mx.tmp[[i]] <- mx
-    NE.tmp[[i]] <- N.end
-    vpa.tmp[[i]] <- vpa.abund
-    am.tmp[[i]] <- age.mat
-    #mr.tmp[[i]] <- missing_rem
-    abund.tmp[[i]] <- abund.age
-    fs.tmp[[i]] <- full.Fs
-    full.rem.tmp[[i]] <- full.rems
-  } #end input data loop
+## Demographic Parameters
 
-  save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,
-       am.tmp,Stocks,ASR.stocks,ASR.long,abund.tmp,fs.tmp,full.rem.tmp,
-       file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
+There are numerous demographic parameters that can be derived from the outputs of the life table reconstruction.
+Here we focus on two that are strongly linked to recovery potential: lifetime reproductive success and generation time.
+Lifetime reproductive success describes the average number of spawners produced by one female spawner throughout her lifetime
 
-  } # end load results
-```
+## Lifetime Reproductive Success
 
-  So now I can try to do some tuning, both forwards and backwards, lets see what we get from that...
+The lifetime reproductive success ($R_0$)  was calculated for each cohort in which fecundity and natural mortality were available for all age classes.
+It was calculated using only natural mortality (F=0) and with the combined effect of natural mortality and fishing mortality (F>0).
+This was calculated for each cohort as
 
-```{r tunes,include=F,echo=F,warning=F,message=F}
+$$
+R_0 = \sum_{x=\alpha}^{\omega} s_x f_x
+$$
 
-  ########################## Now run the tuning sims
-  #
+*Here we are treating the plus group as effectively 'terminal', i.e., it assumes that after the last age class the individuals make no contribution, which means these values are probably a bit low, but at this age they really aren't making much of a contribution on average*.
 
-  if(load.results==F)
-  {
-  load(file = paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
+## Generaion Time
 
-  for.tune.all.res <- NULL
-  for.tune.summary <- NULL
-  for(i in Stocks)
-  {
-    years <- years.tmp[[i]]
-    prop.nat.mort <- pnm.tmp[[i]] 
-    #rem <- rem.tmp[[i]] 
-    mx <- mx.tmp[[i]] 
-    N.end <- NE.tmp[[i]] 
-    ages <- ages.tmp[[i]]
-    vpa.abund <- vpa.tmp[[i]] 
-    abund <- abund.tmp[[i]]
-    fs <-fs.tmp[[i]]
-    full.rem <- full.rem.tmp[[i]]
-    #full.abund <- full.abund.tmp[[i]]
-    #all.abund <- full.abund.tmp[[i]]
-    #N.end <- vpa.abund[length(vpa.abund)]
-    #Pick your step size
-    ss.size <- 0.005
-    sensistive.stocks <- c("AFSC_GOA_Theragra_chalcogramma",
-                            "DFO_2J3KL_Gadus_morhua",
-                            "DFO_3Pn-4RS_Gadus_morhua",
-                            "DFO_4T-4VN_Gadus_morhua",
-                            "DFO_4T_Scomber_scombrus",
-                            "ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus",
-                            "ICES-AFWG_NEA1-2_Gadus_morhua",
-                            "ICES-HAWG_NS_Ammodytes_dubius",
-                            "ICES-NWWG_FA5b_Pollachius_virens",
-                            "ICES-NWWG_FAPL5b1_Gadus_morhua",
-                            "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
-                            "ICES-WGCSE_IS7a_Gadus_morhua",
-                            "ICES-WGCSE_CS7a_Merlangius_merlangus",
-                            "ICES-WGCSE_CS7e-k_Gadus_morhua",
-                            "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
-                            "ICES-WGHANSA_SP8abd_Sardina _pilchardus", 
-                            "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua",
-                            "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",
-                            "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus",
-                            "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
-                            "NEFSC-GARMIII_SNE- MA_Limanda_ferruginea",
-                            "NEFSC-GARMIII_MA_Paralichthys_dentatus",
-                            "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus",
-                            "NEFSC_NWA_Scomber _scombrus")
+The generation time was defined as the mean age of the spawners of the observed recruits in a cohort over its lifetime ($T_G$), here we calculated this for each cohort in which fecundity and natural mortality were available for all age classes.
+It was calculated twice, using only natural mortality (F=0) and with the combined effect of natural mortality and fishing mortality (F>0).
 
-    if(i %in% sensistive.stocks) ss.size = ss.size/10
+$$
+T_G = \frac{\sum_{x=\alpha}^{\omega} x s_x f_x}{\sum_{x=\alpha}^{\omega}  s_x f_x}
+$$
 
-     N.start <- vpa.abund[1]
-     print(i)
-     # The fecundities are 
-     fast.for.tune <- fast.tunes(years,
-                             tuner=what.2.tune,
-                             step.size = ss.size, 
-                             abund.ts = vpa.abund,
-                             ages=ages,
-                             nm = -(log(1-prop.nat.mort)),
-                             fecund = mx,
-                             fm = fs,
-                             abund.age = abund, 
-                             catch.age = full.rem, 
-                             N.init = N.start,
-                             direction= 'forwards'
-                             )
+## Recovery Potential
 
-     for.tune.all.res[[i]] <- fast.for.tune
-     for.tune.tmp <- data.frame(fast.for.tune$res,Stock = i)
-     for.tune.summary[[i]] <- for.tune.tmp
-  }
-
-  saveRDS(for.tune.summary,paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-  saveRDS(for.tune.all.res,paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
-  # 
-}# end if load results
-
-```
-
-```{r paper-other-metrics-and-metadata,echo=F,include=F,warning=F,message=F}
-
-if(load.results==F)
-{
-  # We are now looking at everything, lifetime reproductive success
-
-  for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-  for.tune.all <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
-
-  load(file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
-  # Get the stocks...
-  Stocks <- names(for.tune.summary)
-  n.stocks <- length(Stocks)
-
-  ############ Meta data and clean up, could be it's own chunk really, but it's really fast, so meh...
-
-  #  A quick way to get the other potentially interesting info for the stock...
-  drop <- which(names(ASR.long) %in% c("Year","type","age","value"))
-  meta <- NULL
-  for(i in Stocks) 
-  {
-    meta[[i]] <- ASR.long[ASR.long$Stock == i,-drop][1,]
-    meta[[i]]$age.min <- min(ages.tmp[[i]])
-    meta[[i]]$age.max <- max(ages.tmp[[i]])
-  }
-  meta <- do.call('rbind',meta)
-
-  # First making a meta data object and adding a bunch of columns to it... very messy!!
-  meta$Species[meta$Species == ' harengus']  <- "harengus"
-  meta$Species[meta$Species == "Aeglefinus"] <- "aeglefinus"
-  meta$Species[meta$Species == "Solea"] <- "solea"
-  meta$Family[meta$Family == "Gadide"] <- "Gadidae"
-  meta$Genus[meta$Genus == " Hippoglossoides"] <- "Hippoglossoides"
-  meta$G.short <- toupper(paste0(substr(meta$Genus,1,1),"."))
-  meta$G.Species <- paste0(meta$G.short," ",meta$Species)
-  # Simplified Management
-  meta$Manage.short <- meta$Management
-  meta$Manage.short[grep("TRAC",meta$Management)] <- "DFO-TRAC"
-  meta$Manage.short[grep("DFO",meta$Management)] <- "DFO-TRAC"
-  meta$Manage.short[grep("NEFSC",meta$Management)] <- "NEFSC"
-  meta$Manage.short[grep("ICES",meta$Management)] <- "ICES"
-
-  # The 3 pieces of the ocean
-  meta$LME <- "NW Atlantic"
-  meta$LME[meta$Management == "AFSC"] <- "Pacific (Alaska)"
-  meta$LME[grepl("ICES",meta$Management)] <- "NE Atlantic"
-  # An area typo
-  meta$Area[grep("BSAI-females",meta$Area)] <- "BSAI-Females"
-  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI-Females"
-  # Some other Area summaries
-  meta$Area.broad <- meta$Area
-  meta$Area.long <- meta$Area
-  meta$Area.narrow <- "" # Leave this blank if not needed
-
-  meta$Area.broad[grep("NS",meta$Area)] <- "NS"
-  meta$Area.long[grep("NS",meta$Area)] <- "North Sea"
-  meta$Area.broad[grep("CS",meta$Area)] <- "CS"
-  meta$Area.long[grep("CS",meta$Area)] <- "Celtic Sea"
-  meta$Area.broad[grep("ROCK6b",meta$Area)] <- "CS"
-  meta$Area.long[grep("ROCK6b",meta$Area)] <- "Celtic Sea"
-  meta$Area.broad[grep("IS",meta$Area)] <- "IS"
-  meta$Area.long[grep("IS",meta$Area)] <- "Irish Sea"
-  meta$Area.broad[grep("BS",meta$Area)] <- "BS"
-  meta$Area.long[grep("BS",meta$Area)] <- "Baltic Sea"
-  meta$Area.broad[grep("NEA",meta$Area)] <- "NEA"
-  meta$Area.long[grep("NEA",meta$Area)] <- "NE Arctic"
-  meta$Area.broad[grep("B28.1",meta$Area)] <- "BS"
-  meta$Area.long[grep("B28.1",meta$Area)] <- "Baltic Sea"
-  meta$Area.broad[grep("SP8abd",meta$Area)] <- "BoB"
-  meta$Area.long[grep("SP8abd",meta$Area)] <- "Bay of Biscay"
-  meta$Area.broad[grep("FA",meta$Area)] <- "Ice-Faroe"
-  meta$Area.broad[grep("ICE",meta$Area)] <- "Ice-Faroe"
-  meta$Area.long[grep("FA",meta$Area)] <- "Faroes"
-  meta$Area.long[grep("ICE",meta$Area)] <- "Iceland"
-
-  meta$Area.broad[grep("GOM",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("GOM",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("GB",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("GB",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("5Y",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("5Y",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("5Z",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("5Z",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("USATL",meta$Area)] <- "NAFO 5-6" # The fishery is broader than just GOM, but it does also include it.
-  meta$Area.long[grep("USATL",meta$Area)] <- "NAFO 5-6" # The fishery is broader than just GOM, but it does also include it.
-  meta$Area.broad[grep("NWA",meta$Area)] <- "NAFO 5-6" # Mackerel... so that definition is a bit narrow....
-  meta$Area.long[grep("NWA",meta$Area)] <- "NAFO 5-6" # Mackerel... so that definition is a bit narrow....
-  #meta$Area1[grep("SNE- MA",meta$Area)] <- "GOM-GB" # YT in US, so no GB so that definition is a bit narrow....
-  meta$Area.broad[grep("MA",meta$Area)] <- "NAFO 5-6" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
-  meta$Area.long[grep("MA",meta$Area)] <- "NAFO 5-6" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
-  meta$Area.broad[grep("BSAI",meta$Area)] <- "BSAI"
-  meta$Area.broad[grep("4T",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("4T",meta$Area)] <- "NAFO 2-4"
-  meta$Area.broad[grep("2J3",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("2J3",meta$Area)] <- "NAFO 2-4"
-  meta$Area.broad[grep("3Pn-4RS",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("3Pn-4RS",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("GOA",meta$Area)] <- "Gulf of Alaska"
-  # Lumping everything in Berring Sea and AI into both.
-  meta$Area.long[grep("AI",meta$Area)] <- "Aleutian Islands"
-  meta$Area.long[grep("ESB",meta$Area)] <- "Bering Sea & AI" 
-  meta$Area.long[grep("BSAI",meta$Area)] <- "Bering Sea & AI"
-  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI"
-  meta$Area[grep("BSAI-Females",meta$Area)] <- "BSAI"
-  meta$Area[grep("BSAI-females",meta$Area)] <- "BSAI"
-  meta$Area.long[grep("BSAI-Females",meta$Area)] <- "Bering Sea & AI"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Pollachius_virens"] <- "5b"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5a_Pollachius_virens"] <- "5a"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS4 _Solea_solea"] <- "4"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d._Solea_solea"] <- "7d"
-  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_NS IIIa 22-24_Solea_Solea"] <- "22-24"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d_Pleuronectes_platessa"] <- "7d"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4,20_Pleuronectes_platessa"] <- "4 20"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS7e_Pleuronectes_platessa"] <- "7e"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS27.7a_Pleuronectes_platessa"] <- "7a"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Melanogrammus_aeglefinus"] <- "5b"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Melanogrammus_aeglefinus"] <- "5a"
-  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_B28.1_Clupea_harengus"] <- "28"
-  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_BS 25-29-32_Clupea_harengus" ] <- "25-32"
-  meta$Area.narrow[meta$Stock == "ICES-HAWG_WBS 22-24_Clupea_harengus"] <- "22-24"
-  meta$Area.narrow[meta$Stock == "DFO_4T-Fall_Clupea_harengus"] <- "Fa-SGSL"
-  meta$Area.narrow[meta$Stock == "DFO_4T-Spring_Clupea_harengus"] <- "Sp-SGSL"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS27.6a_Merlangius_merlangus"] <- "27.6a"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS7a_Merlangius_merlangus"] <- "7a"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Gadus_morhua"] <- "5a"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FAPL5b1_Gadus_morhua" ] <- "5b"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua"] <- "4-7 20"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_NS6a_Gadus_morhua"] <- "6a"
-  meta$Area.narrow[meta$Stock == "DFO_2J3KL_Gadus_morhua"] <- "NFLD"
-  meta$Area.narrow[meta$Stock == "DFO_3Pn-4RS_Gadus_morhua"] <- "NGSL"
-  meta$Area.narrow[meta$Stock == "NEFSC-CERT-TRAC_GB _Gadus_morhua"] <- "EGB"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus"] <- "RA"
-  meta$Area.narrow[meta$Stock == "DFO_4T-4VN_Gadus_morhua"] <- "SGSL"
-  meta$Area.narrow[meta$Stock == "DFO_4T_Hippoglossoides _platessoides"] <- "SGSL"
-  meta$Area.narrow[meta$Stock == "DFO_4T_Scomber_scombrus"] <- "SGSL"
-  meta$Area.narrow[meta$Stock == "NEFSC-SAW_GOM_Gadus_morhua"] <- "GOM"
-  meta$Area.narrow[meta$Stock == "NEFSC-GARMIII_GB_Gadus_morhua"] <- "GB"
-  meta$Area.narrow[meta$Stock == "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus"] <- "GOM"
-  meta$Area.narrow[meta$Stock == "CERT-TRAC_GB_Melanogrammus_Aeglefinus"] <- "GB"
-
-  meta$Stock.short <- paste0(meta$Area.broad," ",meta$Area.narrow," ",meta$G.short," ",meta$Species)
-  meta$Stock.no.species <- paste0(meta$Area.long," ",meta$Area.narrow)
-
-  for.tune.stocks <- NULL
-  fta <- NULL
-
-  # Going to rename these female stocks.
-  fem.names <- c("AFSC_BASI-Females_Pleuronectes_quadrituberculatus",
-                    "AFSC_EEBSAI-Females_Lepidopsetta_polyxystra",
-                    "AFSC_BSAI-females_Atheresthes_stomais")
-  fem.rename <- c("AFSC_BSAI_Pleuronectes_quadrituberculatus",
-                    "AFSC_EEBSAI_Lepidopsetta_polyxystra",
-                    "AFSC_BSAI_Atheresthes_stomais")
-  # Going to drop these stocks
-  dont <- paste(c("Mles","Males","COASTNOR"),collapse = "|")
-
-  meta.sub <- NULL
-  for(i in Stocks) 
-  {
-    org.nam <- i
-    tmp <- for.tune.summary[[org.nam]]
-    new.stock.nam <- org.nam
-    # Don't bother for these stocks...
-    if(!grepl(dont,tmp$Stock[1]))
-    {
-      # Grab the metadata and add in some new useful things...
-      meta.sub[[i]] <- meta[meta$Stock == org.nam,]
-
-      # Rename the ladies
-      if(tmp$Stock[1] == fem.names[1]) new.stock.nam <- tmp$Stock <- fem.rename[1]
-      if(tmp$Stock[1] == fem.names[2]) new.stock.nam <- tmp$Stock <- fem.rename[2]
-      if(tmp$Stock[1] == fem.names[3]) new.stock.nam <- tmp$Stock <- fem.rename[3]
-
-      meta.sub[[i]]$Stock <- new.stock.nam
-      tmp <- data.frame(tmp,meta.sub[[i]])
-      # For tunes all
-      fta[[new.stock.nam]] <- for.tune.all[[org.nam]]
-      fta[[new.stock.nam]]$meta <- meta.sub[[i]]
-      for.tune.stocks[[new.stock.nam]] <- tmp
-    }# End skip stocks...
-  }
-  # Now unpack them...
-  for.tunes <- do.call("rbind",for.tune.stocks)
-  for.tune.all <- fta
-  meta.sub <- do.call("rbind",meta.sub)
-
-  ######################### End Meta data and clean up #####################
-
-  # Now some summaries...
-
-  # Reset on the stocks...
-  Stocks <- sort(names(for.tune.all))
-  n.stocks <- length(Stocks)
-
-  # Doubling time, no fishing
-  dt.res <- NULL
-  # These are both set in the index file now, go there!!
-  n.dt.sims <- n.dt.sims
-  n.sim.years <- n.sim.years
-  for(i in Stocks)
-  {
-    str.time <- Sys.time()
-    try <- for.tune.all[[i]]
-    meta.tmp <- try$meta
-    age.4.sim <- meta.tmp$age.min:meta.tmp$age.max
-    double.time <- NA
-    pop <- 1000
-    tmp.res <- NULL
-  for(s in 1:n.dt.sims)
-  {
-    tmp <- rep(0,n.sim.yearss)
-    print(paste0("Sim # ", s))
-
-    for(y in 2:n.sim.yearss)
-    {
-
-      # Get our sample for this run
-      f.pick <- sample(nrow(try$fecund.opt),size=1)
-      nm.pick <- sample(nrow(try$nm.opt),size=1)
-      fec.samp <- try$fecund.opt[f.pick,]
-      # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
-      nm.samp <- try$nm.opt[nm.pick,] 
-      # now put these into Euler-lotka to get an r estimate
-      res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
-      r.val <- res$res$r
-      # If r is > 5 (lambda = exp(5)) it generally means the simple.lotka didn't converge (bad combo of fec and nm)
-      # So we'll need to resample them until it is < 5
-      while(r.val >= 5)
-      {
-        print("Resampling due to bat shit r value")
-        f.pick <- sample(nrow(try$fecund.opt),size=1)
-        nm.pick <- sample(nrow(try$nm.opt),size=1)
-        fec.samp <- try$fecund.opt[f.pick,]
-        # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
-        nm.samp <- try$nm.opt[nm.pick,] 
-        # now put these into Euler-lotka to get an r estimate
-        res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
-        r.val <- res$res$r
-      } # end while loop
-      pop[y] <- exp(r.val)*pop[y-1]
-      if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.sim.yearss] <- 1
-    } # end the years loop
-    tmp.res[[s]] <- data.frame(year =1:n.sim.yearss,doubled = tmp,sim=s)
-
-    } # end sim loop
-    res.tmp <- do.call("rbind",tmp.res)
-
-  dt.res[[i]] <- data.frame(res.tmp,meta.tmp)
-  count <- 0
-  timer <- round(difftime(Sys.time(),str.time,units='mins'),digits=1)
-  print(paste0("Stock ",i," time =", timer," minutes: Stock # ",count+1))
-  } # end Stocks loop
-
-  dub.time <- do.call("rbind",dt.res)
-
-  dub.time.summary <- dub.time |> collapse::fgroup_by(Stock,year)  |> collapse::fsummarise(prop = sum(doubled)/n.dt.sims)
-  dub.time.summary <- left_join(dub.time.summary,meta.sub,by="Stock")
-
-  # Now to get generation lengths + reproductive rates....
-  # First I need to get the fecundity and natural mortalities by cohort instead of year.
-  res.fin <- NULL
-  res.year.fin <- NULL
-  res.lambda.fin <- NULL
-  for(i in Stocks) # 
-  {
-    tst <- for.tune.all[[i]]
-    meta.tmp <- tst$meta
-    # Fishing mortality
-    fm.org.tmp <- tst$fm.org
-    fm.tmp <- tst$fm.opt
-    # fecundity
-    fec.tmp <- tst$fecund.opt
-    fec.org.tmp <- tst$fecund.org
-    # Natural mortality
-    m.org.tmp <- exp(-tst$nm.org) # This is survivorship
-    m.tmp <- exp(-tst$nm.opt) # This is survivorship
-    # Total mortality
-    z.tmp <- exp(-tst$z.opt) # This is survivorship
-    z.org.tmp <- exp(-tst$nm.org -fm.org.tmp) # This is survivorship
-
-    ages <- meta.tmp$age.min:meta.tmp$age.max
-    n.ages <- length(ages)
-    years <- tst$res$year
-    n.years <- length(years)
-    # Now I need to grab the fecundities and nat morts by cohort
-    if(n.years > n.ages)
-    {
-    res.cohort <- NULL
-    res.year <- NULL
-    res.lambda <- NULL
-    for(y in 1:(n.years-n.ages+1))
-    {
-      count = 0
-      fs <- NA
-      # The lx is no fishing survivorship, zx I'm calling the survivorship including fishing
-      lx <- lx.org <- lx.year <- zx <- zx.org <- zx.year <- 1
-      fs.org <- NA
-
-      for(a in 1:n.ages)
-      {
-      fs[a] <- fec.tmp[y+count,a]  
-      fs.org[a] <- fec.org.tmp[y+count,a]  
-      if(a > 1) 
-      {
-        # No fishing
-        lx[a] <- lx[a-1] * m.tmp[y+count,a]  
-        lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
-        lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
-        # Including fishing
-        zx[a] <- zx[a-1] * z.tmp[y+count,a]  
-        zx.org[a] <- zx.org[a-1]* z.org.tmp[y+count,a]  
-        zx.year[a] <- zx.year[a-1] * z.tmp[y,a]
-      }  # end the a > 1 if
-          count <- count + 1
-      }# end the ages loop
-          res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,
-                                 mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
-                                 x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
-                                 zx.opt = zx,
-                                 mx.zx.opt = fs*zx,mx.zx.org = fs.org*zx.org,
-                                 x.mx.zx.opt = fs*zx*ages,x.mx.zx.org = fs.org*zx.org*ages,
-                                 cohort=years[y],age = ages,meta.tmp)
-
-          res.year[[y]] <- data.frame(mx.opt = unlist(fec.tmp[y,]),lx.opt = lx.year,
-                                 mx.lx.opt = unlist(fec.tmp[y,])*lx.year,
-                                 x.mx.lx.opt = unlist(fec.tmp[y,])*lx.year*ages,
-                                 zx.opt = zx.year,
-                                 mx.zx.opt = unlist(fec.tmp[y,])*lx.year,
-                                 x.mx.zx.opt = unlist(fec.tmp[y,])*lx.year*ages,
-                                 age = ages,year=years[y],meta.tmp)
-
-    } # end the years loop
-
-  # Do a years loop to get lambda with no fishing for each year, rather than by cohort...
-    for(yy in 1:(n.years-1))
-    {
-      nm <- as.numeric(tst$nm.opt[yy,])
-      z <- as.numeric(tst$z.opt[yy,])
-      fec <- as.numeric(tst$fecund.opt[yy,])
-      nm.init <- as.numeric(tst$nm.org[yy,])
-      fec.init <- as.numeric(tst$fecund.org[yy,])
-      z.init <- as.numeric(tst$z.org[yy,])
-      lam.no.fish <- exp(simple.lotka.r(mort = nm,fecund = fec,ages=ages)$res$r)
-      lam.fish <- exp(simple.lotka.r(mort = z,fecund = fec,ages=ages)$res$r)
-      lam.org.no.fish <- exp(simple.lotka.r(mort = nm.init,fecund = fec.init,ages=ages)$res$r)
-      lam.org.fish <- exp(simple.lotka.r(mort =  z.init,fecund = fec.init,ages=ages)$res$r)
-
-      # Now summarize these
-      res.lambda[[yy]] <-  data.frame(lam.no.fish = lam.no.fish,lam.fish = lam.fish,
-                                      lam.org.no.fish = lam.org.no.fish,
-                                      lam.org.fish = lam.org.fish,
-                                      year=years[yy],meta.tmp)
-    } # End the yy loop to get the lambdas...
-  # unpack it...
-  res.fin[[i]] <- do.call('rbind',res.cohort)
-  res.year.fin[[i]] <- do.call('rbind',res.year)
-  res.lambda.fin[[i]] <-  do.call('rbind',res.lambda)
-  }  # end if to make sure we have enough data to get the cohort estimates.
-
-  }# end the stock loop
-
-  res.cohort.final <- do.call('rbind',res.fin)
-  res.year.final <- do.call('rbind',res.year.fin)
-  res.lambda.final <- do.call('rbind',res.lambda.fin)
-
-  pop.dam <- res.cohort.final |> collapse::fgroup_by(cohort,Stock) |> collapse::fsummarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
-                                                                                   gen.len.org = sum(x.mx.lx.org)/sum(mx.lx.org),
-                                                                                   R0.opt = sum(mx.lx.opt),R0.org = sum(mx.lx.org))
-  pop.dam <- left_join(pop.dam,meta.sub,by="Stock")
-
-  dub.time.summary <- data.frame(dub.time.summary)
-  pop.dam <- data.frame(pop.dam)
-  # saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",what.2.tune,".Rds"))
-  # saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",what.2.tune,".Rds"))
-  # saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",what.2.tune,".Rds"))
-  save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
-       file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
-
-  write.csv(meta.sub, paste0(loc,"/Data/metadata_no_age_corection.csv"))
-} # end if load results
-```
-
-```{r clean-up-and-stats,include=F,echo=F,message=F,warning=F}
-load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
-for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-
-Stocks <- unique(res.lambda.final$Stock)
-res.lambda.fin <- data.frame(res.lambda.final)
-six.species <- c('morhua','harengus','aeglefinus','virens','solea','platessa')
-pop.dam.6 <- pop.dam |> collapse::fsubset(Species %in% six.species)
-for.tunes.6 <- for.tunes |> collapse::fsubset(Species %in% six.species)
-dub.time.6 <- dub.time.summary |> collapse::fsubset(Species %in% six.species)
-res.lambda.fin$decade <- floor(res.lambda.fin$year/10)*10
-res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock,decade) |> collapse::fmutate(mn.lam = mean(lam.fish,na.rm=T),
-                                                                                 med.lam = median(lam.fish,na.rm=T),
-                                                                                 sd.lam = sd(lam.fish,na.rm=T))
-res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Species,decade) |> collapse::fmutate(lm.spec.mn = mean(mn.lam,na.rm=T))              
-res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock) |> 
-                                                          collapse::fmutate(
-                                                          lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
-                                                          lam.fish.mn = mean(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T),
-                                                          lam.no.fish.med = median(lam.no.fish,na.rm=T),
-                                                          lam.fish.med = median(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.med = median(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T),
-                                                          lam.no.fish.sd = sd(lam.no.fish,na.rm=T),
-                                                          lam.fish.sd = sd(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.sd = sd(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.sd = sd(lam.org.fish,na.rm=T)
-                                                          ) |> data.frame()
-# Get the order right for the stock no species for the boxplots to come later
-sns.order <- c("Baltic Sea ", "Baltic Sea 22-24", "Baltic Sea 25-32", "Baltic Sea 28", 
-               "North Sea ", "North Sea 4", "North Sea 22-24", "North Sea 4-7 20", "North Sea 6a","North Sea 4 20", "North Sea 7d",     
-               "Celtic Sea ","Celtic Sea RA", "Celtic Sea 7a", "Celtic Sea 27.6a", 
-               "Irish Sea ","Irish Sea 7a", "Irish Sea 7e","Bay of Biscay ", "NE Arctic ", 
-               "Faroes 5a", "Faroes 5b",  "Iceland ", "Iceland 5a",
-                "NAFO 2-4 Fa-SGSL", "NAFO 2-4 Sp-SGSL", "NAFO 2-4 SGSL", "NAFO 2-4 NGSL", "NAFO 2-4 NFLD",  
-                "NAFO 5-6 ", "NAFO 5-6 GB", "NAFO 5-6 GOM", "NAFO 5-6 EGB",
-                "Bering Sea & AI ", "Gulf of Alaska ", "Aleutian Islands ")
-
-res.lambda.fin$Stock.no.species <- factor(res.lambda.fin$Stock.no.species,levels = sns.order,ordered = T)
-res.lambda.final.6 <- res.lambda.fin |> collapse::fsubset(Species %in% six.species)
-# Sort the data into a nice order...
-res.lambda.fin <- res.lambda.fin |> collapse::roworder(Species,Area.broad) |>
-                                    collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-# Making the Aleutian Islands their own Area long...
-res.lambda.fin$Area.long[res.lambda.fin$Area == "AI"] <- "Aleutian Islands"
-res.lambda.fin$Area.long <- factor(res.lambda.fin$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
-                                                                       "Irish Sea","Bay of Biscay","NE Arctic",
-                                                                       "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-
-res.lambda.final.6 <- res.lambda.final.6 |> collapse::roworder(Species,Area.broad) |>
-                                            collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-dub.time <- dub.time |> collapse::roworder(LME) |>
-                        collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-dub.time.summary <- dub.time.summary |> collapse::roworder(LME,Order,Species,Area.broad) |>
-                                        collapse::fmutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-dub.time.6 <- dub.time.6 |> collapse::roworder(LME) |>
-                             collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-pop.dam <- pop.dam |> collapse::roworder(Species,LME) |>
-                       collapse::fmutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
-pop.dam.6 <- pop.dam.6 |> collapse::roworder(LME,Area.broad) |>
-                       collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-pop.dam$Area.long[pop.dam$Area == "AI"] <- "Aleutian Islands"
-pop.dam$Area.long <- factor(pop.dam$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
-                                                         "Irish Sea","Bay of Biscay","NE Arctic",
-                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-# I'd also like a pop.dam including fishing
-pop.dam.fish <- res.cohort.final |> collapse::fgroup_by(cohort,Stock) |> collapse::fsummarise(gen.len.opt = sum(x.mx.zx.opt)/sum(mx.zx.opt),
-                                                                                   gen.len.org = sum(x.mx.zx.org)/sum(mx.zx.org),
-                                                                                   R0.opt = sum(mx.zx.opt),R0.org = sum(mx.zx.org))
-pop.dam.fish <- left_join(pop.dam.fish,meta.sub,by="Stock")
-pop.dam.fish$Area.long[pop.dam.fish$Area == "AI"] <- "Aleutian Islands"
-pop.dam.fish$Area.long <- factor(pop.dam.fish$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
-                                                         "Irish Sea","Bay of Biscay","NE Arctic",
-                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-pop.dam <- data.frame(pop.dam)
-
-pop.dam.fish <- pop.dam.fish |> collapse::roworder(Species,LME) |>
-                                collapse::fmutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
-pop.dam.fish.6 <- pop.dam.fish |> collapse::fsubset(Species %in% six.species)
-
-pop.dam.fish.6 <- pop.dam.fish.6 |> collapse::roworder(LME,Area.broad) |>
-                                    collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-# Put the population dynamics stuff together.
-pop.dam$group <- "no fish"
-pop.dam.fish$group <- 'fish'
-pop.dam.all <- rbind(pop.dam,pop.dam.fish)
-
-pop.dam.6$Stock.no.species <- factor(pop.dam.6$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam$Stock.no.species <- factor(pop.dam$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam.fish.6$Stock.no.species <- factor(pop.dam.fish.6$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam.fish$Stock.no.species <- factor(pop.dam.fish$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam.all$Stock.no.species <- factor(pop.dam.all$Stock.no.species,levels = sns.order,ordered = T)
-# Drop the periods....
-pop.dam.all.6 <- pop.dam.all |> collapse::fsubset(!Species %in% six.species)
-pop.dam.all$G.Species <- gsub("\\.","",pop.dam.all$G.Species)
-pop.dam.all$G.Species.short <- substr(pop.dam.all$G.Species,1,5)
-pop.dam.all$G.Species <- gsub("\\.","",pop.dam.all$G.Species)
-pop.dam.all.6 <- pop.dam.all |> collapse::fsubset(Species %in% six.species)
-pop.dam.all.others <- pop.dam.all |> collapse::fsubset(!Species %in% six.species)
-
-# Reorder the doubling time, either by Species and LME, or the other way around
-
-dub.time.summary$Order.short <- "Gadi"
-dub.time.summary$Order.short[dub.time.summary$Order == "Pleuronectiformes"] <- "Plero"
-dub.time.summary$Order.short[dub.time.summary$Order == "Clupeiformes"] <- "Clupei"
-dub.time.summary$Order.short[dub.time.summary$Order == "Scorpaeniformes "] <- "Scor"
-dub.time.summary$Order.short[dub.time.summary$Order == "Scombriformes"] <- "Scomb"
-dub.time.summary$Order.short[dub.time.summary$Order == "Perciformes"] <- "Perci"
-# First need to get the abundance and lambdas with no fishing into one object.
-ft.tmp <- for.tunes |> collapse::fselect(year,Stock,vpa.abund,est.abund,removals)
-dd.dat <- left_join(res.lambda.fin,ft.tmp,by=c('year','Stock'))
-# Now I need to get a relative abundance for each stock...
-dd.dat <- dd.dat |> collapse::fgroup_by(Stock) |> collapse::fmutate(max.abund = max(est.abund,na.rm=T))
-dd.dat <- data.frame(dd.dat)
-dd.dat$prop.abund <- dd.dat$est.abund/dd.dat$max.abund
-# Drop nas....
-drops <- -which(is.na(dd.dat$prop.abund))
-dd.dat <- dd.dat[drops,]
-#lump the data into bins
-dd.dat$prop.bin <- "< 10%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.1 & dd.dat$prop.abund <= 0.2] <- "10-20%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.2 & dd.dat$prop.abund <= 0.3] <- "20-30%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.3 & dd.dat$prop.abund <= 0.4] <- "30-40%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.4 & dd.dat$prop.abund <= 0.6] <- "40-60%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.6 & dd.dat$prop.abund <= 0.8] <- "60-80%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.8 & dd.dat$prop.abund <= 1] <- "80-100%"
-dd.dat$prop.bin <- factor(dd.dat$prop.bin,levels=c("< 10%","10-20%","20-30%","30-40%","40-60%","60-80%","80-100%"))
-
-# Subset to the big six
-dd.dat.six <- dd.dat  |>collapse::fsubset(Species %in% six.species)
-
-# This is for the new lambda figures with fishing and no fishing together
-
-res.lambda.fin.long <- res.lambda.fin |> tidyr::pivot_longer(cols = c(lam.no.fish,lam.fish),names_to = 'group',values_to = 'lambda')
-res.lambda.fin.long$Stock.no.species <- factor(res.lambda.fin.long$Stock.no.species,levels = sns.order,ordered = T)
-res.lambda.fin.long$group <- substr(res.lambda.fin.long$group,5,20)
-res.lambda.fin.long$group <- gsub("\\."," ",res.lambda.fin.long$group)
-res.lambda.fin.long.others <- res.lambda.fin.long |> collapse::fsubset(!Species %in% six.species)
-res.lambda.fin.long.others$G.Species <- gsub("\\.","",res.lambda.fin.long.others$G.Species)
-res.lambda.fin.long.others$G.Species.short <- substr(res.lambda.fin.long.others$G.Species,1,5)
-res.lambda.fin.long.6 <- res.lambda.fin.long |> collapse::fsubset(Species %in% six.species)
-res.lambda.fin.long.6$G.Species <- gsub("\\.","",res.lambda.fin.long.6$G.Species)
-
-# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE
-# here is the GAM for no fishing with subsequent processing.
-mod.dd.stock.gam.nf <- gam(log(lam.no.fish) ~   s(prop.abund,k=4) + s(prop.abund,as.factor(Stock.short),bs='fs',k=3) ,data=dd.dat)
-
-# This extracts the GAM fit so we can custom plot it on our own figure
-tmp <- plot(mod.dd.stock.gam.nf, pages = 0)
-no.stock.gam.nf.dat <- data.frame(fit = tmp[[1]]$fit + coefficients(mod.dd.stock.gam.nf)[1],prop.abund = tmp[[1]]$x,se = tmp[[1]]$se,Scenario = "F = 0")
-no.stock.gam.nf.dat$LCI <- no.stock.gam.nf.dat$fit - 1.96*no.stock.gam.nf.dat$se
-no.stock.gam.nf.dat$UCI <- no.stock.gam.nf.dat$fit + 1.96*no.stock.gam.nf.dat$se
-
-#summary(mod.dd.stock.gam.nf)
-#Residuals, definitely still issues here, maybe a bit better than some others, maybe...
-#plot(residuals(mod.dd.stock.gam.nf) ~ fitted(mod.dd.stock.gam.nf))
-# Normality = no
-#qqnorm(residuals(mod.dd.stock.gam.nf))
-#qqline(residuals(mod.dd.stock.gam.nf))
-
-pred.dd.stock.gam.nf <- expand.grid(prop.abund = seq(0, 1, length.out = 250),
-                                         Stock.short=c(unique(dd.dat$Stock.short)))
-tmp <- predict(mod.dd.stock.gam.nf, pred.dd.stock.gam.nf, type = 'response', se.fit = TRUE) 
-# Another fun trick to extract the overall smooth fit, but didn't end up using this method.
-# sms <- smooths(mod.dd.stock.gam.nf)
-# excl <- grepl("as.factor",sms)
-# rm <- sms[excl]
-# tmp.ex <- predict(mod.dd.stock.gam.nf, newdata =pred.dd.stock.gam.nf, type = 'response', se.fit = TRUE,exclude =rm) 
-# Get the fit by stock
-pred.dd.stock.gam.nf$lam.no.fish   <- exp(tmp$fit)
-pred.dd.stock.gam.nf$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-pred.dd.stock.gam.nf$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-
-# Thin the data so I can add points to the figure
-tmp <- NULL
-for(i in 1:(77)) 
-{
-  if(i==1) tmp[[i]] <- seq(10,230,length.out=5)
-  if(i>1) tmp[[i]] <- seq(10,230,length.out=5)+250*(i-1)
-}
-thinner.nf <- do.call('c',tmp)
-thin.pred.nf <- pred.dd.stock.gam.nf[thinner.nf,]
-# Now I want to get rid of extrapolation from this prediction data.frame, I think I need to loop it...
-# 
-short.stocks <- unique(dd.dat$Stock.short)
-n.stocks <- length(short.stocks)
-pred.out <- NULL
-thin.out <- NULL
-for(i in short.stocks)
-{
-  # Get the right stocks
-  tmpy <- dd.dat |> collapse::fsubset(Stock.short == i)
-  tmp.pred <- pred.dd.stock.gam.nf |> collapse::fsubset(Stock.short == i)
-  tmp.thin <- thin.pred.nf |> collapse::fsubset(Stock.short == i)
-  # I dont want to predict below the minimum observed abundance
-  mins <- min(tmpy$prop.abund,na.rm=T)
-  pred.out[[i]] <- tmp.pred |> collapse::fsubset(prop.abund >= mins)
-  thin.out[[i]] <- tmp.thin |> collapse::fsubset(prop.abund >= mins)
-}
-
-pred.dd.stock.gam.ss.nf <- do.call('rbind',pred.out)
-thin.pred.nf <- do.call('rbind',thin.out)
-# Combine pred stuff with the meta data for fun plots
-pred.dd.stock.gam.ss.nf <- left_join(pred.dd.stock.gam.ss.nf,meta.sub,by="Stock.short")
-pred.dd.stock.gam.ss.nf <- data.frame(pred.dd.stock.gam.ss.nf)
-thin.pred.nf <- left_join(thin.pred.nf,meta.sub,by="Stock.short")
-# Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# By region
-cols.gam <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
-pty.gam <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
-
-# Now do the same thing with the data that includes the effect of fishing.
-
-#mod.dd.stock.gam.fish <- gam(log(lam.fish) ~  as.factor(Stock.short) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.dat)
-mod.dd.stock.gam.fish <- gam(log(lam.fish) ~  s(prop.abund,k=4) + s(prop.abund,as.factor(Stock.short),bs='fs',k=3),data=dd.dat)
-
-tmp <- plot(mod.dd.stock.gam.fish, pages = 0)
-no.stock.gam.fish.dat <- data.frame(fit = tmp[[1]]$fit + coefficients(mod.dd.stock.gam.fish)[1],prop.abund = tmp[[1]]$x,se = tmp[[1]]$se,Scenario = "F > 0")
-no.stock.gam.fish.dat$LCI <- no.stock.gam.fish.dat$fit - 1.96*no.stock.gam.fish.dat$se
-no.stock.gam.fish.dat$UCI <- no.stock.gam.fish.dat$fit + 1.96*no.stock.gam.fish.dat$se
-
-#summary(mod.dd.stock.gam.fish)
-#Residuals, definetly still issues here, maybe a bit better than some others, maybe...
-#plot(residuals(mod.dd.stock.gam.fish) ~ fitted(mod.dd.stock.gam.fish))
-# Normality = no
-#qqnorm(residuals(mod.dd.stock.gam.fish))
-#qqline(residuals(mod.dd.stock.gam.fish))
-
-pred.dd.stock.gam.fish <- expand.grid(prop.abund = seq(0, 1, length.out = 250),
-                                         Stock.short=c(unique(dd.dat$Stock.short)))
-tmp <- predict(mod.dd.stock.gam.fish, pred.dd.stock.gam.fish, type = 'response', se.fit = TRUE) 
-pred.dd.stock.gam.fish$lam.fish   <- exp(tmp$fit)
-pred.dd.stock.gam.fish$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-pred.dd.stock.gam.fish$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-
-# Thin the data so I can add points to the figure
-tmp <- NULL
-for(i in 1:(77)) 
-{
-  if(i==1) tmp[[i]] <- seq(10,230,length.out=5)
-  if(i>1) tmp[[i]] <- seq(10,230,length.out=5)+250*(i-1)
-}
-thinner.fish <- do.call('c',tmp)
-thin.pred.fish <- pred.dd.stock.gam.fish[thinner.fish,]
-# Now I want to get rid of extrapolation from this prediction data.frame, I think I need to loop it...
-# 
-short.stocks <- unique(dd.dat$Stock.short)
-pred.out <- NULL
-thin.out <- NULL
-for(i in short.stocks)
-{
-  # Get the right stocks
-  tmpy <- dd.dat |> collapse::fsubset(Stock.short == i)
-  tmp.pred <- pred.dd.stock.gam.fish |> collapse::fsubset(Stock.short == i)
-  tmp.thin <- thin.pred.fish |> collapse::fsubset(Stock.short == i)
-  # I dont want to predict below the minimum observed abundance
-  mins <- min(tmpy$prop.abund,na.rm=T)
-  pred.out[[i]] <- tmp.pred |> collapse::fsubset(prop.abund >= mins)
-  thin.out[[i]] <- tmp.thin |> collapse::fsubset(prop.abund >= mins)
-}
-
-pred.dd.stock.gam.ss.fish <- do.call('rbind',pred.out)
-thin.pred.fish <- do.call('rbind',thin.out)
-# Combine pred stuff with the meta data for fun plots
-pred.dd.stock.gam.ss.fish <- left_join(pred.dd.stock.gam.ss.fish,meta.sub,by="Stock.short")
-pred.dd.stock.gam.ss.fish <- data.frame(pred.dd.stock.gam.ss.fish)
-
-thin.pred.fish <- left_join(thin.pred.fish,meta.sub,by="Stock.short")
-
-# Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# By region
-
-# What proportion of the stocks had the lowest 'GAM' estimate happen when the stock was at it's maximum size.
-low.gam <- data.frame(low.pa.fish = NA,diff.low.pa.fish = NA,low.pa.nf = NA,diff.low.pa.nf = NA,Stock = NA,Species = NA)
-count <- 0
-for(i in short.stocks) 
-{
-  count = count +1
-  tmp <- pred.dd.stock.gam.ss.fish |> collapse::fsubset(Stock.short == i)
-  tmp.nf <- pred.dd.stock.gam.ss.nf |> collapse::fsubset(Stock.short == i)
-  low.pa <- data.frame(low.pa.fish = tmp$prop.abund[tmp$lam.fish == min(tmp$lam.fish)],
-                       diff.low.pa.fish = tmp$lam.fish[tmp$lam.fish == min(tmp$lam.fish)] - tmp$lam.fish[tmp$prop.abund == max(tmp$prop.abund)],
-                       low.pa.nf = tmp.nf$prop.abund[tmp.nf$lam.no.fish == min(tmp.nf$lam.no.fish)],
-                       diff.low.pa.nf = tmp.nf$lam.no.fish[tmp.nf$lam.no.fish == min(tmp.nf$lam.no.fish)] - tmp.nf$lam.no.fish[tmp.nf$prop.abund == max(tmp.nf$prop.abund)],
-                       Stock = i,Species = tmp$G.Species[1])
-  low.gam[count,] <- low.pa
-}
-
-# Let's compare lambda at minimum, 0.4, and maximum and make a Table
-comp.lam.diff <- NULL
-comp.lam <- NULL
-comp.all.nf <- NULL
-comp.all.fish <- NULL
-for(i in short.stocks) 
-{
-  tmp <- pred.dd.stock.gam.ss.fish |> collapse::fsubset(Stock.short == i)
-  which.40 <- max(which(tmp$prop.abund <=0.4)) # Some stocks might not have a which 40.
-  which.max <- which(tmp$prop.abund ==1)
-  which.min <- which(tmp$prop.abund == min(tmp$prop.abund))
-  tmp.sub <- tmp[c(which.min,which.40,which.max),]
-  comp.all.fish[[i]] <- tmp.sub
-  tmp.nf <- pred.dd.stock.gam.ss.nf |> collapse::fsubset(Stock.short == i)
-  # I think I'm overkilling as this should be the same was the above witches....
-  which.40.nf <- max(which(tmp.nf$prop.abund <=0.4))
-  which.max.nf <- which(tmp.nf$prop.abund ==1)
-  which.min.nf <- which(tmp.nf$prop.abund ==min(tmp.nf$prop.abund))
-  tmp.nf.sub <- tmp.nf[c(which.min.nf,which.40.nf,which.max.nf),]
-  comp.all.nf[[i]] <- tmp.nf.sub
-  # Now we just want some summaries here I think...
-  comp.lam.diff[[i]] <- data.frame(min.abund = min(tmp.sub$prop.abund,na.rm=T),
-                              lam.fish.min.40 = tmp$lam.fish[which.min] - tmp$lam.fish[which.40],
-                              lam.fish.min.max = tmp$lam.fish[which.min] - tmp$lam.fish[which.max],
-                              lam.fish.40.max = tmp$lam.fish[which.40] - tmp$lam.fish[which.max],
-                              lam.nf.min.40 = tmp.nf$lam.no.fish[which.min.nf] - tmp.nf$lam.no.fish[which.40.nf],
-                              lam.nf.min.max = tmp.nf$lam.no.fish[which.min.nf] - tmp.nf$lam.no.fish[which.max.nf],
-                              lam.nf.40.max = tmp.nf$lam.no.fish[which.40.nf] - tmp.nf$lam.no.fish[which.max.nf],
-                              Stock = i,Species = tmp$G.Species[1])
-
-    comp.lam[[i]] <- data.frame(min.abund = min(tmp.sub$prop.abund,na.rm=T),
-                                lam.fish.min = tmp$lam.fish[which.min] ,
-                                lam.fish.40 = tmp$lam.fish[which.40],
-                                lam.fish.max = tmp$lam.fish[which.max],
-                                lam.nf.min = tmp.nf$lam.no.fish[which.min.nf],
-                                lam.nf.40 = tmp.nf$lam.no.fish[which.40.nf],
-                                lam.nf.max = tmp.nf$lam.no.fish[which.max.nf],
-                                Stock = i,Species = tmp$G.Species[1])
-}
-
-# A table for the estimates at 'interesting' values
-comp.lam.res <- do.call('rbind',comp.lam)
-# I want to turn this into a table....
-comp.lam.res.tab <- comp.lam.res
-# Round the numbers
-comp.lam.res.tab$min.abund <- round(comp.lam.res.tab$min.abund,digits=2)
-rounders <- c("lam.fish.min","lam.fish.40","lam.fish.max",
-              "lam.nf.min","lam.nf.40","lam.nf.max")
-comp.lam.res.tab[,rounders]      <- round(comp.lam.res.tab[,rounders] ,digits=3)
-# Now give it pretty names
-tab.names <- c("Minimum Abundance",
-               "$\\lambda_{F>0}^{Min}$",
-               "$\\lambda_{F>0}^{40}$",
-               "$\\lambda_{F>0}^{Max}$",
-               "$\\lambda_{F=0}^{Min}$",
-               "$\\lambda_{F=0}^{40}$",
-               "$\\lambda_{F=0}^{Max}$",
-               "Stock","Species")
-names(comp.lam.res.tab) <- tab.names
-
-# Now do the same with the differences
-comp.lam.diff.res <- do.call('rbind',comp.lam.diff)
-# I want to turn this into a table....
-comp.lam.diff.res.tab <- comp.lam.diff.res
-# Round the numbers
-comp.lam.diff.res.tab$min.abund <- round(comp.lam.diff.res.tab$min.abund,digits=2)
-rounders <- c("lam.fish.min.40","lam.fish.min.max","lam.fish.40.max",
-                    "lam.nf.min.40","lam.nf.min.max","lam.nf.40.max")
-comp.lam.diff.res.tab[,rounders] <- round(comp.lam.diff.res.tab[,rounders] ,digits=3)
-# Now give it pretty names
-tab.names <- c("Minimum Abundance",
-               "$\\lambda_{F>0}^{Min-40}$",
-               "$\\lambda_{F>0}^{Min-Max}$",
-               "$\\lambda_{F>0}^{40-Max}$",
-               "$\\lambda_{F=0}^{Min-40}$",
-               "$\\lambda_{F=0}^{Min-Max}$",
-               "$\\lambda_{F=0}^{40-Max}$",
-               "Stock","Species")
-names(comp.lam.diff.res.tab) <- tab.names
-
-# Used for the figure showing the number of stocks that have recovered by year x.
-n.dub <- data.frame(years = 1:n.sim.years, count = NA)
-for(i in 1:n.sim.years) n.dub$count[i] <- dub.time.summary |> collapse::fsubset(year==i & prop >= 0.75) |> nrow()
-
-# Compare the population recovery with the variance, using 2010 because all stocks have a value at 2010... 
-# I'm using the overall lambda sd, so the year doesn't actually matter other than to make sure all stocks are included here
-# This is used for the recovery variance figure, is this data good?
-# How many of the stocks had doubled by year 20, with 75% being my standard, which is a high standard
-dub.p.high <- 0.75
-dub.p.low <- 0.5
-n.dub.10 <- dub.time.summary |> collapse::fsubset(year==10 & prop >= dub.p.high) |> nrow()
-n.dub.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop >= dub.p.high) |> nrow()
-# Slow stocks, here we define having a low recovery potential has having < 50% of the simulatoins experience a doubling in size.
-slow.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop < dub.p.low) 
-prop.rec.20 <- dub.time.summary |> collapse::fsubset(year==20) # the proportion that recovers by year 20
-lambda.sds <- res.lambda.fin |> collapse::fsubset(year == 2010)
-lam.sd.p.rec <- left_join(prop.rec.20,lambda.sds,by=names(prop.rec.20)[c(1,4:24)]) 
-lam.sd.p.rec$prop.cat <- "Moderate"
-lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop < dub.p.low] <- "Low"
-lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop >= dub.p.high] <- "High"
-lam.sd.p.rec$prop.cat <- factor(lam.sd.p.rec$prop.cat,levels=c("Low","Moderate","High"))
-
-```
-
-```{r paper-calcs,include=F,echo=F,message=F,warning=F}
-
-# the lambda calcs
-med.lambda.F0 <- round(median(res.lambda.fin$lam.no.fish),digits=3)
-med.r.F0 <- round(median(log(res.lambda.fin$lam.no.fish)),digits=3)*100
-med.lambda.F <- round(median(res.lambda.fin$lam.fish),digits=3)
-med.r.F <- round(median(log(res.lambda.fin$lam.fish)),digits=3)*100
-mn.lambda.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
-mn.r.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
-# Mean - median...
-res.lambda.fin$med.mn.diff.no.fish <- res.lambda.fin$lam.no.fish.med - res.lambda.fin$lam.no.fish.mn
-res.lambda.fin$med.mn.diff.fish <- res.lambda.fin$lam.fish.med - res.lambda.fin$lam.fish.mn
-# How many stocks had the mean higher than the median
-n.mn.higher.med.no.fish <- length(unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.no.fish < 0]))
-n.mn.higher.med.fish <- length(unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.fish < 0]))
-low.mn.lambda.stocks <- unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.fish > 0])
-n.nw.ice <- length(c(grep("NAFO",low.mn.lambda.stocks),grep("Faroe",low.mn.lambda.stocks)))
-n.cod.low.mn <- length(grep("morhua",low.mn.lambda.stocks))
-n.cod <- length(grep("morhua",Stocks))
-
-# Density dependence related numbers
-n.bl.40 <- length(which(!is.na(comp.lam.res$lam.fish.40)))
-n.low.40.nf <- length(which(comp.lam.res$lam.nf.40 < 1))
-n.low.40.fish <-length(which(comp.lam.res$lam.fish.40 < 1))
-low.lam.40.nf <- -round(min(comp.lam.diff.res$lam.nf.40,na.rm=T),digits=3)
-low.4.lam.40.nf <- -round(sort(comp.lam.diff.res$lam.nf.40)[4],digits=3)
-
-# If right isn't this interesting!!! And look, 3 cod stocks from around here all say around 0.4 is the worst.  Most interesting...
-n.low.lam.at.max.fish <- length(which(low.gam$low.pa.fish == 1))
-n.low.lam.at.max.nf <- length(which(low.gam$low.pa.nf == 1))
-low.lam.cods <- low.gam[low.gam$low.pa.nf < 1 & low.gam$Species == "G. morhua",]
-n.cod.lam.not.at.max.nf <- nrow(low.lam.cods)
-pa.low.cod.min <- round(min(low.lam.cods$low.pa.nf),digits=2)
-pa.low.cod.max <- round(max(low.lam.cods$low.pa.nf),digits=2)
-
-# more density dependence numbers
-pa.lam.nf.at.one <- 100*round(no.stock.gam.nf.dat$prop.abund[min(which(no.stock.gam.nf.dat$fit <0))],digits=2)
-pa.lam.fish.at.one <- 100*round(no.stock.gam.fish.dat$prop.abund[min(which(no.stock.gam.fish.dat$fit <0))],digits=2)
-# What is the minimum abundance at which we get a 2 with the fishing lambdas.
-pa.big.threshold <- 0.65
-pa.low.threshold <- 0.8
-lam.low.threshold <- 0.8
-pa.lam.fish.low.bigs <- max(dd.dat$lam.fish[dd.dat$prop.abund >= pa.big.threshold])
-pa.lam.nf.low.bigs <- round(rev(sort(dd.dat$lam.no.fish[dd.dat$prop.abund >= pa.big.threshold]))[2],digits =2)
-# What proportion of the stocks had large declines overall, and then the proportion when the population was below 30%
-dd.dat.high <- dd.dat |> collapse::fsubset(prop.abund >= 0.3)
-prop.low.high.abund <- round(length(which(dd.dat.high$lam.fish < lam.low.threshold)) / nrow(dd.dat.high),digits=3)
-prop.low.all <- round(length(which(dd.dat$lam.fish < lam.low.threshold)) / nrow(dd.dat),digits=3)
-dd.dat.low <- dd.dat |> collapse::fsubset(prop.abund < 0.3)
-prop.low.low.abund <- round(length(which(dd.dat.low$lam.fish < lam.low.threshold)) / nrow(dd.dat.low),digits=3)
-
-# Numbers for the paper, lifetime reproductive growth
-r0.mn <- round(mean(pop.dam$R0.opt,na.rm=T),digits=1)
-r0.med <- round(median(pop.dam$R0.opt,na.rm=T),digits=1)
-# And fishing...
-r0.mn.fish <- round(mean(pop.dam.fish$R0.opt,na.rm=T),digits=1)
-r0.med.fish <- round(median(pop.dam.fish$R0.opt,na.rm=T),digits=1)
-
-# Where are the slow ones from
-n.not.dub.20 <- nrow(slow.20)
-n.alaska <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short== "AFSC"]))
-n.nwa <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("DFO-TRAC","NEFSC")]))
-n.nea <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("ICES")]))
-n.nafo.24 <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Area.broad %in% "NAFO 2-4"]))
-# Now the don't recover ones...
-n.alaska.slow <- length(slow.20$Stock.short[slow.20$Manage.short== "AFSC"])
-n.nwa.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% c("DFO-TRAC","NEFSC")])
-n.nea.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% "ICES"])
-
-# Need to grab all the per.diff's, which I seem to have dropped
-for.diffs <- do.call('rbind',for.tune.summary)
-med.per.diff <- round(median(for.diffs$per.diff,na.rm=T),digits=1)
-# what is lambda difference, about 6%, but that means the original was 7% higher, so that means we are reducing lambda when optimizing
-# If there was 'missing fishing' we are compensating for with this, this is exactly what we'd expect to happen right?
-res.lambda.fin$lam.per.diff <- 100*((res.lambda.fin$lam.org.no.fish - res.lambda.fin$lam.no.fish)/ res.lambda.fin$lam.no.fish)
-med.lam.per.diff <- round(median(res.lambda.fin$lam.per.diff,na.rm=T),digits=1)
-# By stock, can see most are positive, which is in line with missing fishing mortality...
-mod.by.stock.lam.pd <- res.lambda.fin |> collapse::fgroup_by(Stock.short) |> collapse::fsummarise(med = median(lam.per.diff,na.rm=T),
-                                                                                                  mn = mean(lam.per.diff,na.rm=T))
-
-```
-
-```{r main-figs,include=F,echo=F,message=F,warning=F}
-
-# New lambda plot with the fishing and no fishing beside each other
-# This is likely Figure 1
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Stock.no.species),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(G.Species),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 19,base_height = 15)
-
-# The other stocks, perhaps we put this in a supplement...
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(y=lambda,interaction(group,G.Species.short),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(Area.long),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 19,base_height = 15)
-
-# Standard deviation figure
-colrs.sd <- rep(c(rep('blue',4),rep('orange',4),rep('grey',4),rep('black',4)),20)
-pty.sd <- rep(rep(c(21,4,9,8),4),20)
-
-lam.sd.plt <- ggplot(res.lambda.fin ) + 
-                                       geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
-                                       scale_y_log10("Standard deviation (Lambda)",log_breaks(n=8)) +
-                                       scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
-                                       theme(axis.text.x = element_text(angle =45,hjust=1),
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 10)
-
-# Overall density dependence
-# MAIN PAPER FIGURE#
-dd.nf.overall.plt <-ggplot(no.stock.gam.nf.dat , aes(x=prop.abund,y=exp(fit))) + 
-                                geom_point(data = dd.dat,aes(x=prop.abund,y=lam.no.fish),size=2,alpha=0.1) +  
-                                geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI)),alpha=0.5,linewidth=0,fill=u.colors[1])+
-                                geom_line(color=u.colors[1],linewidth=1) + 
-                                xlab("") + 
-                                scale_y_log10(name = "Lambda(F=0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_blank()) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-# MAIN PAPER FIGURE#
-dd.fish.overall.plt <- ggplot(no.stock.gam.fish.dat, aes(x=prop.abund,y=exp(fit))) + 
-                                geom_point(data = dd.dat,aes(x=prop.abund,y=lam.fish),size=2,alpha=0.1) +  
-                                geom_line(color=u.colors[2],linewidth=2) + 
-                                geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI)),alpha=0.5,fill=u.colors[2])+
-                                xlab("") + 
-                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed',linewidth=1.5)+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_blank()) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-# Main Paper Figure Density dependence with and without fishing, effectively a zoomed in version of the above.
-colrs <- u.colors
-t.smooth <- rbind(no.stock.gam.fish.dat,no.stock.gam.nf.dat)
-dd.fish.nf.plt <- ggplot(t.smooth, aes(x=prop.abund,y=exp(fit),group=Scenario,color=Scenario,fill=Scenario)) + 
-                                 geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI),group=Scenario,fill=Scenario),alpha=0.50,linewidth=0)+
-                                 geom_line(linewidth=1.5) +
-                                 geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                 scale_fill_manual(values = colrs) + scale_color_manual(values = colrs) +
-                                 scale_x_continuous(name = "Proportion of maximum abundance",breaks = seq(0,1,by=0.1)) + 
-                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-                                 theme(legend.position = c(0.9,0.75))
-
-dd.overall.combo <- plot_grid(dd.nf.overall.plt,dd.fish.overall.plt,dd.fish.nf.plt,nrow=3)
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_overall_",what.2.tune,".png"),dd.overall.combo,base_width = 10,base_height = 10)
-
-new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(y=lambda,interaction(group,G.Species.short),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(Area.long),design=mat,scales='free_x')
-
-# Density dependence by stock 
-cols.gam <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
-pty.gam <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
-# Doing this manually because the ordered factor wasn't working... annoying...
-mat <- matrix(c(2, 2,13,13, 5, 5, 9, 9,
-                3, 3,12,12, 6, 6, 8, 8,
-               NA,NA,10,10,11,11,NA,NA,
-               NA,7, 7, 4, 4, 1, 1, NA),
-                4, 8, byrow = TRUE)
-
-dd.stocks.nf.plt <- ggplot(pred.dd.stock.gam.ss.nf,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=G.Species,shape=G.Species)) + 
-                                geom_line() + 
-                                geom_point(data = thin.pred.nf,size=2) +  
-                                xlab("Proportion of maximum abundance") + 
-                                scale_y_log10(name = "Lambda (F=0)",breaks = log_breaks(n=10)) +
-                                geom_ribbon(aes(ymin=lower,ymax=upper,color=G.Species),alpha=0.10,linewidth=0)+
-                                facet_manual(vars(Area.long),design=mat,scales='free_x')+
-                                #facet_wrap(~Area.long)  +
-                                scale_shape_manual(values=pty.gam) +
-                                scale_color_manual(values = cols.gam) + 
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_text(size=7)) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"),dd.stocks.nf.plt,base_width = 10,base_height = 10)
-
-mat <- matrix(c(2, 2,13,13, 5, 5, 9, 9,
-                3, 3,12,12, 6, 6, 8, 8,
-               NA,NA,10,10,11,11,NA,NA,
-               NA,7, 7, 4, 4, 1, 1, NA),
-                4, 8, byrow = TRUE)
-
-# MAIN PAPER FIGURE#
-dd.stocks.fish.plt <- ggplot(pred.dd.stock.gam.ss.fish,aes(x=prop.abund,y=lam.fish,group=Stock.short,color=G.Species,shape=G.Species)) + 
-                                geom_line() + 
-                                geom_point(data = thin.pred.fish,size=2) +  
-                                geom_ribbon(aes(ymin=lower,ymax=upper,color=G.Species),alpha=0.10,linewidth=0)+
-                                xlab("Proportion of maximum abundance") + 
-                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10)) +
-                                facet_manual(vars(Area.long),design=mat,scales='free_x')+
-                                #facet_wrap(~Area.long)  +
-                                scale_shape_manual(values=pty.gam) +
-                                scale_color_manual(values = cols.gam) + 
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_text(size=7)) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_fish_stocks_",what.2.tune,".png"),dd.stocks.fish.plt,base_width = 10,base_height = 10)
-
-# Lifetime reproductive success 
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-r0.boxplt.6 <- ggplot(pop.dam.all.6) + geom_boxplot(aes(y=R0.opt,interaction(group,Stock.no.species),color=group))  + 
-                                       scale_x_discrete(NULL, guide = "axis_nested") + scale_y_log10(name = "Lifetime Reproductive Output")+
-                                       geom_hline(yintercept = 1,linetype='dashed',color='blue')+
-                                       facet_manual(vars(G.Species),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"),r0.boxplt.6,base_width = 19,base_height = 15)
-
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-r0.boxplot.others <- ggplot(pop.dam.all.others) +   geom_boxplot(aes(y=R0.opt,interaction(group,G.Species.short),color=group))  + 
-                                                    scale_x_discrete(NULL, guide = "axis_nested") + 
-                                                    scale_y_log10(name = "Lifetime Reproductive Output")+
-                                                    geom_hline(yintercept = 1,linetype='dashed',color='blue')+
-                                                    facet_manual(vars(Area.long),design=mat,scales='free')+
-                                                    theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                          plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"),r0.boxplot.others,base_width = 15,base_height = 10)
-
-r0.heatmap.ne <- ggplot(pop.dam |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-r0.heatmap.nw <- ggplot(pop.dam |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-r0.heatmap.pac <- ggplot(pop.dam |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                     xlab("") + ylab("")+
-                                     facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                     geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                     theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                           legend.key.width = unit(3,'cm'))
-
-r0.heatmap <- cowplot::plot_grid(r0.heatmap.pac,r0.heatmap.nw,r0.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_nf_",what.2.tune,".png"),r0.heatmap,base_width = 20,base_height = 17)
-
-r0.heatmap.ne.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-r0.heatmap.nw.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-r0.heatmap.pac.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                     xlab("") + ylab("")+
-                                     facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                     geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                     theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                           legend.key.width = unit(3,'cm'))
-
-r0.heatmap.fish <- cowplot::plot_grid(r0.heatmap.pac.fish,r0.heatmap.nw.fish,r0.heatmap.ne.fish,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_fish_",what.2.tune,".png"),r0.heatmap.fish,base_width = 20,base_height = 17)
-
-# Generation length
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-gen.boxplt.6 <- ggplot(pop.dam.all.6) +
-                            geom_boxplot(aes(y=gen.len.opt,interaction(group,Stock.no.species),color=group))  + 
-                            scale_x_discrete(NULL, guide = "axis_nested") +
-                            scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
-                             facet_manual(vars(G.Species),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"),gen.boxplt.6,base_width = 19,base_height = 15)
-
-# Then the generation length for others.
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-gen.boxplt.others <- ggplot(pop.dam.all.others) +
-                            geom_boxplot(aes(y=gen.len.opt,interaction(group,G.Species.short),color=group))  + 
-                            scale_x_discrete(NULL, guide = "axis_nested") +
-                            scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
-                            facet_manual(vars(Area.long),design=mat,scales='free')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"),gen.boxplt.others,base_width = 15,base_height = 10)
-
-gen.heatmap.ne <- ggplot(pop.dam |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
-                                              xlab("") + ylab("")+  
-                                              facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                              geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-gen.heatmap.nw <- ggplot(pop.dam |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-gen.heatmap.pac <- ggplot(pop.dam |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
-                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-gen.heatmap <- cowplot::plot_grid(gen.heatmap.pac,gen.heatmap.nw,gen.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_nf_",what.2.tune,".png"),gen.heatmap,base_width = 15,base_height = 10)
-
-gen.heatmap.ne.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
-                                              xlab("") + ylab("")+  
-                                              facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                              geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-gen.heatmap.nw.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-gen.heatmap.pac.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
-                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-gen.heatmap.fish <- cowplot::plot_grid(gen.heatmap.pac.fish,gen.heatmap.nw.fish,gen.heatmap.ne.fish,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_fish_",what.2.tune,".png"),gen.heatmap.fish,base_width = 15,base_height = 10)
-
-dub.time.summary <- dub.time.summary |> collapse::fsubset(year %in% 1:50) |>
-                            collapse::roworder(G.Species,LME,Area.broad) |>
-                            collapse::fmutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-dub.heatmap.gad <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Gadiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+                                    
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.45, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.pl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Pleuronectiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+                                    
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"))
-
-dub.heatmap.cl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Clupeiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.35, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.per <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Perciformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.scom <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Scombriformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2.1, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.scorp <- ggplot(dub.time.summary |> collapse::fsubset(Order %in% "Scorpaeniformes "), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + 
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.5, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap <- cowplot::plot_grid(dub.heatmap.gad,dub.heatmap.pl,dub.heatmap.cl,dub.heatmap.per,dub.heatmap.scom,dub.heatmap.scorp,
-                                  nrow = 6,rel_heights = c(39,20,11,4,3,3))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"),dub.heatmap,base_width = 20,base_height = 20)
-
-# Doubling Time Figure 1
-dub.ts.plt <- ggplot(n.dub,aes(x=years,y=count)) + 
-                    geom_line() + 
-                    geom_hline(yintercept = length(Stocks),linetype="dashed") + 
-                    xlab("") + ylab("Number of Stocks")
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_time_series_",what.2.tune,".png"),dub.ts.plt,base_width = 10,base_height = 10)
-
-# Doubling time and variability
-
-# Is there a relationship between median and sd?
-colrs.cat <- c("blue","black","orange")
-pts.cat <- 21:23
-sd.rec.plt <- ggplot(lam.sd.p.rec, aes(y=lam.no.fish.med,x=lam.no.fish.sd,color=prop.cat,group=prop.cat)) + 
-                       geom_point(size =3,aes(shape=prop.cat,fill=prop.cat)) + 
-                       geom_hline(yintercept=1,linetype="dashed") + 
-                       scale_y_continuous(name="median Lambda") + scale_x_continuous(name="standard deviation Lambda") +
-                       scale_color_manual(values=colrs.cat) + scale_fill_manual(values=colrs.cat) +  
-                       scale_shape_manual(values=pts.cat) + theme(legend.title = element_blank())
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"),sd.rec.plt,base_width = 10,base_height = 10)
-
-```
-
-```{r the-others,include=F,echo=F,message=F,warning=F}
-#             
-# 
-# dub.heatmap.cod <- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "G.
-morhua"), aes(x=year, y=Stock.no.species, fill= prop)) + xlab("") + ylab("")+                                     facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") +
-#                             geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + scale_x_continuous(labels=NULL) +
-#                             theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-#                                   legend.key.width = unit(3,'cm'))
-# 
-# dub.heatmap.herring<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "C. harengus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-# 
-# dub.heatmap.haddock<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "M. aeglefinus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.125, "cm"))
-# 
-# dub.heatmap.virens<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. virens"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.4, "cm"))
-# 
-# dub.heatmap.solea<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "S. solea"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-# 
-# dub.heatmap.platessa<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. platessa"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous() +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
-# 
-# 
-# 
-# dub.heatmap.sp6 <- cowplot::plot_grid(dub.heatmap.cod,dub.heatmap.herring,dub.heatmap.haddock,
-#                                  dub.heatmap.virens, dub.heatmap.solea,dub.heatmap.platessa,nrow = 6,rel_heights = c(14,9,8,5,5,4))
-# dub.heatmap.sp6
-# 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_sp6_",what.2.tune,".png"),dub.heatmap.sp6,base_width = 20,base_height = 17)
-# 
-# 
-# # What about a plot of the sd of lamda by stock
-# #colrs.sd <- rep(rep(c("black","blue","orange",'grey'),3),20)
-# #pty.sd <- rep(c(rep(21,4),rep(4,4),rep(9,4)),20)
-# 
-# 
-# # Same plot for the not 6 species
-# 
-# # lam.sd.other.plt <- ggplot(res.lambda.fin |> collapse::fsubset(!Species %in% six.species)) + 
-# #                                        geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
-# #                                        scale_y_log10("sd(lambda)",limits=c(0.05,1.5)) +
-# #                                        scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
-# #                                        theme(axis.text.x = element_text(angle =45,hjust=1),
-# #                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# # lam.sd.other.plt
-# 
-# 
-# 
-# 
-# # Doubling Times
-# 
-# 
-# # Generation length
-# 
-# # Main text figure!!
-# new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Area.long),color=group)) +
-#                                            #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-#                                            scale_x_discrete(NULL, guide = "axis_nested") +
-#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~G.Species,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# # The other stocks, plotting these by area
-# # Main Text FIGURE!
-# # More data
-# 
-# 
-# ################### Supplemental Figures################### Supplemental Figures################### Supplemental Figures################### Supplemental 
-# 
-# 
-# 
-# # Time series of lambdas....
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# #col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
-# pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
-# #pty <- rep(rep(c(21:23),5),20)
-# 
-# lambda.ts.plt <- ggplot(res.lambda.final.6,aes(y=lam.fish,x=year,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
-#                             geom_point(size=4) +
-#                             geom_smooth(method='gam',formula = y ~ s(x, bs = "cs", fx = TRUE, k = 5),se=F) + 
-#                             #scale_y_log10(name = "lambda") +
-#                             facet_wrap(~G.Species,scales='free_y') +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-#                             scale_fill_manual(name = "Stock",values = col.try)+
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm'))
-# #lambda.ts.plt
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_timeseries_6_",what.2.tune,".png"),lambda.ts.plt,base_width = 12,base_height = 10)
-# 
-# 
-# lambda.dec.plt <- ggplot(res.lambda.final.6,aes(y=med.lam,x=as.factor(decade))) +
-#                             geom_boxplot() + scale_y_log10()+
-#                             xlab("Decade") + ylab("Lambda") + 
-#                             geom_point(aes(x=as.factor(decade),y=lm.spec.mn),color='blue',shape=8,fill='blue')+
-#                             #scale_x_continuous(breaks=seq(1940,2020,by=10))+
-#                             geom_hline(yintercept = 1,linetype='dashed') +
-#                             facet_wrap(~G.Species,scales='free_y') 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_by_decade_6_",what.2.tune,".png"),lambda.dec.plt,base_width = 12,base_height = 12)
-# 
-#
-
-# ggplot(dd.dat) + geom_point(aes(x=prop.abund,y=lam.no.fish-1)) + xlab("Proportion of Maximum Abundance") + ylab("r (no fishing)")
-# 
-# # Density dependence by Species
-# ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
-#                                                    geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) #+
-#                                                    #scale_color_manual(values = colrs)
-# # Density dependence by stock
-# ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Stock.short,group=Stock.short)) + geom_point() + 
-#                                                    geom_smooth(method="lm",se = F) + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)", limits=c(0.4,2),
-#                                                                  breaks = seq(0.4,2,by=0.1)) +
-#                                                    theme(legend.position = 'none')
-# 
-# 
-# 
-# 
-# ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish)) + geom_point() + 
-#                                                     geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_continuous(name = "lambda (no fishing)")
-# 
-# ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + geom_point() + 
-#                                                     geom_smooth(method="lm",se=F) + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,2,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)")
-# 
-# 
-# # how about our big 6
-# colrs <- c("blue","black","firebrick2","orange",'grey50','grey90')
-# ggplot(dd.dat.six,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
-#                                                     geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) +
-#                                                    scale_color_manual(values = colrs)
-# 
-# 
-# ggplot(dd.dat.six.no.bigs,aes(x=prop.abund,y=lam.no.fish-1,color=Species,group=Species)) + geom_point() + 
-#                                                     geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 0,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_continuous(name = "r (no fishing)", breaks = seq(-1,1,by=0.2)) +
-#                                                    scale_color_manual(values = colrs)
-
-# Other things I did just randomly scattered here
-
-# 
-# #hmm <- merge(tst,res.lambda.final.6,by="Stock")
-# plot(res.lambda.fin$lam.fish.med ~ res.lambda.fin$lam.fish.mn)
-# # So this is lambda with fishing included
-# lambda.plt <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.no.fish,x=Stock.no.species))  + 
-#                                            geom_point(aes(y=lam.no.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~G.Species,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_no_fishing_6_",what.2.tune,".png"),lambda.plt,base_width = 12,base_height = 10)
-# 
-# # With fishing
-# lambda.plt.fish <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.fish,x=Stock.no.species))  + 
-#                                            geom_point(aes(y=lam.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~G.Species,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_with_fishing_6_",what.2.tune,".png"),lambda.plt.fish,base_width = 12,base_height = 10)
-# 
-# 
-# 
-# new.lam.plt <- ggplot(res.lambda.fin.long) + geom_boxplot(aes(y=lambda,interaction(group,Order),color=group)) +
-#                                            #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-#                                            scale_x_discrete(NULL, guide = "axis_nested") +
-#                                            #xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            #geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~Area.long,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# 
-# # The final option I have is to do what I did before and use the bin props
-# We can then do a much more ANOVA kinda analysis, drat this doesn't converge..., estimate the 
-#mod.dd.bins.stock <- glmer(lam.no.fish ~ prop.bin + (1+prop.bin|Stock),data=dd.dat,family=gaussian(link='log'))
-# so go to lmer and log transform... and it is a singular fit
-#mod.dd.bins.stock <- lmer(lam.no.fish ~ prop.bin + (1+prop.bin|Stock),data=dd.dat)
-# So is an intercept model of any real use?
-# mod.dd.bins.stock <- lmer(log(lam.no.fish) ~ prop.bin + (1+prop.bin|Stock.short),data=dd.dat)
-# # A non-random effect model does work with the interaction... I'd much rather lmer....
-# #mod.dd.bins.stock <- lm(lam.no.fish ~ prop.bin*Stock,data=dd.dat)
-# summary(mod.dd.bins.stock)
-# #Residuals, nah, still suck, just some crazy outliers...
-# plot(mod.dd.bins.stock)
-# # Normality = terrible...
-# qqnorm(residuals(mod.dd.bins.stock))
-# qqline(residuals(mod.dd.bins.stock))
-# # So we can predict this ANOVA thing...
-# pred.dd.stock.bins <- expand.grid(prop.bin = unique(dd.dat$prop.bin),
-#                                          #Species=unique(dd.dat$Species),
-#                                          Stock.short=unique(dd.dat$Stock.short))
-# tmp <- predict(mod.dd.bins.stock, pred.dd.stock.bins, type = 'response', se.fit = TRUE) 
-# pred.dd.stock.bins$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.stock.bins$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.stock.bins$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Now to do fun things I need the meta data on the pred dataframe
-# pred.dd.stock.bins <- left_join(pred.dd.stock.bins,meta.sub,by="Stock.short")
-# # Now a problem here is that this includes estimates for bins in which we don't have data.
-# # So we do want to get rid of those
-# real.bins <- unique(paste(dd.dat$Stock.short,"_",dd.dat$prop.bin))
-# # All the bins in the predict object with same names same name...
-# pred.dd.stock.bins$bin.combos <- paste(pred.dd.stock.bins$Stock.short,"_",pred.dd.stock.bins$prop.bin)
-# # Now toss all the predicted bins without data.
-# pred.dd.stock.bins <- pred.dd.stock.bins |> collapse::fsubset(bin.combos %in% real.bins)
-# 
-# # By region
-# cols.1 <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
-# #col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
-# pty.1 <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
-# ggplot(pred.dd.stock.bins,aes(x=prop.bin,y=lam.no.fish,group=Stock.short,color=G.Species)) + 
-#                                 geom_point(aes(shape=G.Species),size=2) + geom_line()  + xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 facet_wrap(~Area.long)  +
-#                                 scale_shape_manual(values=pty.1) +
-#                                 scale_color_manual(values = cols.1) + 
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-# 
-# # By Species
-# ggplot(pred.dd.stock.bins,aes(x=prop.bin,y=lam.no.fish,group=Stock.short,color=Area.long)) + 
-#                                 geom_point(aes(shape=Area.long)) + geom_line()  + xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 facet_wrap(~Order)  +
-#                                 scale_shape_manual(values=pty.1) +
-#                                 scale_color_manual(values = cols.1) + 
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-# 
-# # No fish vs fish lambda, note that DD is weaker when we account for fishing, that seems a fun result to talk about!
-# 
-# mod.dd.overall.gam.nf <- lm(log(lam.no.fish) ~ (prop.abund),data=dd.dat)
-# mod.dd.overall.gam.fish <- lm(log(lam.fish) ~ (prop.abund),data=dd.dat)
-# 
-# 
-# pred.dd.overall.bins.nf <- data.frame(prop.abund = seq(0,1,length.out=500),group = "F = 0")
-# pred.dd.overall.bins.fish <- data.frame(prop.abund = seq(0,1,length.out=500),group = "F > 0")
-# tmp <- predict(mod.dd.overall.gam.nf, pred.dd.overall.bins, type = 'response', se.fit = TRUE) 
-# tmp.fish <- predict(mod.dd.overall.gam.fish, pred.dd.overall.bins, type = 'response', se.fit = TRUE) 
-# pred.dd.overall.bins.nf$lam   <- exp(tmp$fit)
-# pred.dd.overall.bins.nf$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.overall.bins.nf$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# 
-# pred.dd.overall.bins.fish$lam   <- exp(tmp.fish$fit)
-# pred.dd.overall.bins.fish$lower <- exp(tmp.fish$fit - 1.96 * tmp.fish$se.fit)
-# pred.dd.overall.bins.fish$upper <- exp(tmp.fish$fit + 1.96 * tmp.fish$se.fit)
-# 
-# pred.dd.overall <- rbind(pred.dd.overall.bins.fish,pred.dd.overall.bins.nf)
-# 
-# ggplot(pred.dd.overall,aes(y=lam,x=prop.abund,group=group,color=group)) + 
-#                                                   geom_line(linewidth=2) + 
-#                                                   geom_ribbon(aes(ymin=lower,ymax=upper),alpha=0.2) + 
-#                                                   geom_hline(yintercept=1,linetype='dashed') + 
-#                                                   xlab("Proportion of Maximum Abundance") + ylab("Lambda")
-# 
-# # OK, so if we compare the 40-60 bin with the 80-100 bin we should see the lambda's in the 40-60 bin are higher...
-# 
-# res.40.60 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("40-60%"))
-# names(res.40.60)[names(res.40.60) == 'lam.no.fish'] <- "lam.40.60"
-# res.80.100 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("80-100%"))
-# names(res.80.100)[names(res.80.100) == 'lam.no.fish'] <- "lam.80.100"
-# 
-# tst <- left_join(res.40.60,res.80.100, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.40.60 - tst$lam.80.100
-# 
-# hist(tst$diff)
-# 
-# res.lt.10 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("< 10%"))
-# names(res.lt.10)[names(res.lt.10) == 'lam.no.fish'] <- "lam.lt.10"
-# 
-# tst <- left_join(res.40.60,res.lt.10, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.lt.10 - tst$lam.40.60
-# 
-# hist(tst$diff)
-# 
-# res.10.20 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("10-20%"))
-# names(res.10.20)[names(res.10.20) == 'lam.no.fish'] <- "lam.10.20"
-# 
-# tst <- left_join(res.40.60,res.10.20, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.10.20 - tst$lam.40.60
-# 
-# hist(tst$diff)
-# 
-# 
-# res.20.30 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("20-30%"))
-# names(res.20.30)[names(res.20.30) == 'lam.no.fish'] <- "lam.20.30"
-# 
-# tst <- left_join(res.40.60,res.20.30, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.20.30 - tst$lam.40.60
-# 
-# hist(tst$diff)
-# 
-# res.30.40 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("30-40%"))
-# names(res.30.40)[names(res.30.40) == 'lam.no.fish'] <- "lam.30.40"
-# 
-# tst <- left_join(res.40.60,res.30.40, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.30.40 - tst$lam.40.60
-# 
-# hist(tst$diff)
-
-# 
-# 
-# dd.dat.no.bigs <- dd.dat |> collapse::fsubset(lam.no.fish < 2)
-# dd.dat.six.no.bigs <- dd.dat.six |> collapse::fsubset(lam.no.fish < 2)
-# just.bigs <- dd.dat  |> collapse::fsubset(lam.no.fish > 2) 
-# sum(table(just.bigs$Stock.short)) # 48 of 68 are Haddock or cod. 13 of remaining 20 are small low trophic species
-# 
-# dd.dat$lam.ratio <- dd.dat$lam.org.no.fish/dd.dat$lam.no.fish
-# dd.dat$lam.ratio.z <- dd.dat$lam.org.fish/dd.dat$lam.fish
-# So the original lambda tended to be somewhere between 7 and 14% higher, depending on me(di)an choice.
-# Could be way off in some years for a few species (Haddock, Cod, Sand lance, horse makerel, pilchard(sardine)... interesting... )
-# summary(dd.dat$lam.ratio)
-# summary(dd.dat$lam.ratio.z)
-# ggplot(dd.dat,aes(y=lam.ratio,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
-# ggplot(dd.dat,aes(y=lam.ratio.z,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
-
-# Playing around to look at explanations for what we see, looked by LME, low and high stocks, but no smoking guns!
-# low.stocks <- unique(dd.dat$Stock.short[dd.dat$prop.abund <= 0.1])
-# dd.lows <- dd.dat |> collapse::fsubset(Stock.short %in% low.stocks)
-# dd.highs <- dd.dat |> collapse::fsubset(!Stock.short %in% low.stocks)
-# mod.dd.stock.gam.lows <- gam(log(lam.no.fish) ~ s(prop.abund,k=4) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.lows )
-# mod.dd.stock.gam.highs <- gam(log(lam.no.fish) ~ s(prop.abund,k=4) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.highs )
-# 
-# pred.dd.stock.gam.tst <- expand.grid(prop.abund = seq(0, 1, length.out = 50),
-#                                          Stock.short = c("Overall",unique(dd.highs$Stock.short)))
-# 
-# tmp <- predict(mod.dd.stock.gam.highs, pred.dd.stock.gam.tst, type = 'response', se.fit = TRUE) 
-# pred.dd.stock.gam.tst$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.stock.gam.tst$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.stock.gam.tst$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# 
-# ggplot(pred.dd.stock.gam.tst |> collapse::fsubset(Stock.short=='Overall'), aes(x=prop.abund,y=lam.no.fish)) + 
-#                                 geom_point(data = hmm,aes(x=prop.abund,y=lam.no.fish),size=2,alpha=0.1) +  
-#                                 geom_line(color='blue',linewidth=2) + 
-#                                 xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-# 
-# 
-# ggplot(pred.dd.stock.gam.tst,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short,shape=Stock.short)) + 
-#                                 geom_line() + 
-#                                 #geom_point(data = thin.pred,size=2) +  
-#                                 xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 #facet_wrap(~Area.long)  +
-#                                 #scale_shape_manual(values=pty.gam) +
-#                                 #scale_color_manual(values = cols.gam) + 
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-
-# Is there any density dependence in fishing mortality??
-# dd.dat$mu <- dd.dat$removals/dd.dat$vpa.abund
-# dd.dat$fm <- -log(1-dd.dat$mu)
-# 
-# ggplot(dd.dat , aes(x=prop.abund,y=fm)) + 
-#                                 geom_point() + 
-#                                 geom_smooth(method = 'gam') + 
-#                                 scale_x_continuous(name="Proportion of Maximum Abundance") +
-#                                 scale_y__continuous(name = "Fishing Mortality (instantaneous)")
-# 
-# 
-# qqnorm(log(dd.dat$mu))
-# qqline(log(dd.dat$mu))
-# hist(log(dd.dat$mu))
-# 
-# fm.mod <- lm(log(fm)~prop.abund,data=dd.dat)
-# par(mfrow=c(2,2))
-# plot(fm.mod)
-# par(mfrow=c(1,1))
-
-# windows(11,11)
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
-
-# 
-# r0.ts.plt <- ggplot(pop.dam.6,aes(y=R0.opt,x=cohort,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) + 
-#                             geom_line(size=2)  + geom_point(size=4) +
-#                             scale_y_log10(name = "Lifetime Reproductive Output") +
-#                             facet_wrap(~G.Species) +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-#                             scale_fill_manual(name = "Stock",values = col.try)+
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
-# r0.ts.plt
-# 
-# save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_6.png",r0.ts.plt,base_width = 30,base_height = 12)
-# 
-# r0.boxplt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
-#                             facet_wrap(~G.Species,scales = 'free')+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none')
-# r0.boxplt
-
-# 
-# windows(11,11)
-# ggplot(pop.dam) + geom_boxplot(aes(y=gen.len.opt,x=Species)) + facet_wrap(~LME,scales='free_x') +
-#                   ylab("Generation Length (years)") + theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# windows(11,11)
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# lty <- rep(c(rep(1,5),rep(2,5),rep(4,5)),20)
-# 
-# gen.ts.plt <- ggplot(pop.dam.6,aes(y=gen.len.opt,x=cohort,group=Stock.short,color=Stock.short,linetype = Stock.short)) + 
-#                             geom_line(size=2)  + 
-#                             scale_y_log10(name = "Generation Length") +
-#                             facet_wrap(~G.Species) +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_linetype_manual(name = "Stock",values = lty) +
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
-# gen.ts.plt
-# save_plot("D:/Github/ICM/Figures/tuned/Gen_time_series_6.png",gen.ts.plt,base_width = 20,base_height = 12)
-
-# 
-# ggplot(for.tunes) + geom_jitter(aes(y=lambda,x=Species,group=Stock.short,color=Stock.short)) + 
-#                     scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10)) +
-#                             theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# ggplot(for.tunes) + geom_jitter(aes(y=lambda.vpa.init,x=Species)) + scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))
-# 
-# unique(for.tunes$Species)
-# windows(11,11)
-# 
-# ggplot(for.tunes) + geom_density(aes(lambda,group=Species,color=Species,fill=Species),alpha = 0.2) + scale_x_continuous(breaks = c(0,0.5,1,2,5,10))
-# 
-# 
-# #options(scipen=999)
-# r0.plt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.05,0.1,0.5,1,5,10,50,100),minor_breaks = NULL) + 
-#                             facet_wrap(~Species,scales = 'free')+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1))
-# save_plot("D:/Github/ICM/Figures/tuned/R0_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
-# 
-# 
-# 
-# vickis.cols <- sort(rep(c( "#172582",  "#F8DC91", "#FBB891", "#FB6A01", "#B80000"),3))
-# linetypes <- rep(c(1,2,4),5)
-# 
-# windows(11,11)
-# cod.r0.ts.plt <- ggplot(pop.dam |> collapse::fsubset(Species == 'morhua')) + geom_line(aes(y=R0.opt,x=cohort,group=Area,color=Area,linetype=Area),size=1.5)  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output", breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
-#                             scale_color_manual(values = vickis.cols) +
-#                             scale_linetype_manual(values = linetypes) +
-#                             theme(legend.key.width  = unit(2, "cm"))
-# cod.r0.ts.plt
-# #save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
-# 
-# 
-# windows(11,11)
-# ggplot(pop.dam |> collapse::fsubset(Species =="morhua")) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
-#                                                         scale_y_log10(name = "Lifetime Reproductive Output",breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) +
-#                                                         theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# # Missing catch questions
-# # first did we do much to the Fecundity term to get here
-# quantile(for.tunes$mean.fec/for.tunes$mean.vpa.fec,probs=seq(0.01,1,0.01),na.rm=T)
-# 
-# quantile((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init,probs=seq(0.01,1,0.01),na.rm=T)
-# quantile((for.tunes$mean.nm-for.tunes$mean.vpa.nm)/for.tunes$mean.vpa.nm,probs=seq(0.01,1,0.01),na.rm=T)
-# 
-# for.tunes$excess.catch <- for.tunes$removals-for.tunes$removals.init
-# for.tunes$per.excess.catch <- 100*((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init)
-# 
-# windows(11,11)
-# bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Species)) + 
-#                                    ylab("Adjustment to catch (%)") +
-#                                    theme(axis.text.x = element_text(angle=45,hjust = 1))
-#                                    
-# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_species.png",bycatch.plt,base_width = 8,base_height = 8)
-#                                    
-# bycatch.plt.cod <- ggplot(for.tunes |> collapse::fsubset(Species == 'morhua')) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + 
-#                                                                               ylab("Adjustment to catch (%)") +
-#                                                                               theme(axis.text.x = element_text(angle=45,hjust = 1))
-#                                                                               
-# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_cod_stock.png",bycatch.plt.cod,base_width = 8,base_height = 8)
-# 
-# # bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + facet_wrap(~Species,scales = 'free_x')
-# #                                    ylab("Adjustment to catch (%)") +
-# #                                    theme(axis.text.x = element_text(angle=45,hjust = 1))
-# # bycatch.plt                                   
-#
-
-# Doubling time for the rest of the stocks...
-
-# dub.heatmap.no.6 <- ggplot(dub.time.summary |> collapse::fsubset(!Species %in% six.species), aes(x=year, y=Stock.short, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               #facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + 
-#                               scale_x_continuous() +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
-```
-
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-
-```{r failed-models}
-
-# A density dependence model, start simple and build...
-# mod.dd.base <- lm(log(lam.no.fish) ~ prop.abund,data=dd.dat)
-# summary(mod.dd.base)
-# 
-# mod.dd.base.fish <- lm(log(lam.fish) ~ prop.abund,data=dd.dat)
-# summary(mod.dd.base.fish)
-# #ggplot(dd.dat, aes(y = lam.no.fish,x=prop.abund)) + geom_point() + geom_smooth(method = 'lm') + scale_y_log10() + geom_hline(yintercept = 1,color='firebrick2',linetype='dashed',linewidth=2)
-# 
-# 
-# # Residuals are nowhere near normal, the fit isn't a disaster but def have the old trumpet shape happening
-# par(mfrow=c(2,2))
-# plot(mod.dd.base)
-# par(mfrow=c(1,1))
-# # This mostly represents the above model...
-# ggplot(dd.dat, aes(y = lam.no.fish,x=prop.abund)) + 
-#                   geom_point() + 
-#                   geom_smooth(method = 'lm') + scale_y_log10() +
-#                   geom_hline(yintercept = 1,color='firebrick2',linetype='dashed',linewidth=2)
-# # What happens with a gam?
-# mod.dd.gam.base <- gam(log(lam.no.fish) ~ s(prop.abund),data=dd.dat)
-# summary(mod.dd.gam.base)
-# # Still see that the residuals are higher at low values
-# plot(residuals(mod.dd.gam.base) ~ dd.dat$prop.abund)
-# # not great...
-# plot(residuals(mod.dd.gam.base) ~ fitted(mod.dd.gam.base))
-# # What's the fit look like?
-# pred.dd.gam.base <- data.frame(prop.abund = seq(0, 1, length.out = 1000))
-# tmp <- predict(mod.dd.gam.base, dd.gam.base.pred, type = 'response', se.fit = TRUE) 
-# 
-# pred.dd.gam.base$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.gam.base$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.gam.base$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# 
-# # So here's the game fit, I thnk it does do an ok job of showing that no much is happening below maybe 0.3, but then
-# # below 0.15 it starts increasing, suggesting general compensation, but we know the really high values matter here and are
-# # limited to a subset of the stocks, anywho we know the residuals suck, so moving on...
-# ggplot(dd.dat,aes(y=lam.no.fish,x=prop.abund)) + 
-#                   geom_point() + scale_y_log10() +
-#                   geom_ribbon(data=pred.dd.gam.base,aes(ymin=lower,ymax=upper,x=prop.abund),alpha=0.4) +
-#                   geom_line(data = pred.dd.gam.base,aes(y=lam.no.fish, x= prop.abund))
-#     
-# 
-# # What if we did a glm, Gamma with log-link seems a natural thing to try...
-# mod.dd.glm.gamma <- glm(lam.no.fish ~ prop.abund,data=dd.dat,family = Gamma(link='log'))
-# # What's that done...
-# summary(mod.dd.glm.gamma)
-# # Still some pretty gross shit going on here...
-# par(mfrow=c(2,2))
-# plot(mod.dd.glm.gamma)
-# par(mfrow=c(1,1))
-# # Now plot it...
-# pred.dd.glm.base <- data.frame(prop.abund = seq(0, 1, length.out = 1000))
-# tmp <- predict(mod.dd.glm.gamma, dd.gam.base.pred, type = 'response', se.fit = TRUE) 
-# 
-# pred.dd.glm.base$lam.no.fish   <- (tmp$fit)
-# pred.dd.glm.base$lower <- (tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.glm.base$upper <- (tmp$fit + 1.96 * tmp$se.fit)
-# # Pretty similar, though I think on the linear scale we see the 'rate' may be decreasing as we approach 0
-# # But still not a good model given the above
-# ggplot(dd.dat,aes(y=lam.no.fish,x=prop.abund)) + 
-#                   geom_point() + scale_y_log10() +
-#                   geom_ribbon(data=pred.dd.glm.base,aes(ymin=lower,ymax=upper,x=prop.abund),alpha=0.4) +
-#                   geom_line(data = pred.dd.glm.base,aes(y=lam.no.fish, x= prop.abund))
-#     
-# # Now what if we account for species in these and get an estimate for each species. 
-# # I think this should be done as a random effect, we'll start with linear mixed models and see what happens...
-# 
-# mod.dd.species.re <- lmer(log(lam.no.fish) ~ prop.abund + (1| Species),data=dd.dat)
-# # So that seems reasonable...
-# summary(mod.dd.species.re)
-# #Residuals are still pretty cranky
-# plot(mod.dd.species.re)
-# # Normality still a hot mess
-# qqnorm(residuals(mod.dd.species.re))
-# qqline(residuals(mod.dd.species.re))
-# # draw some lines...
-# pred.dd.lmm.species <- expand.grid(prop.abund = seq(0, 1, length.out = 100),Species=unique(dd.dat$Species))
-# tmp <- predict(mod.dd.species.re, pred.dd.lmm.species, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.species$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.lmm.species$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.species$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.species,aes(x=prop.abund,y=lam.no.fish,group=Species,color=Species)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Species, color=Species)) +
-#                                 scale_y_log10()
-# 
-# # We could also allow the slope to vary by species, might get a bit better, but really won't do the trick...
-# mod.dd.species.slope.re <- lmer(log(lam.no.fish) ~ prop.abund + (1+ prop.abund| Species),data=dd.dat)
-# summary(mod.dd.species.slope.re)
-# #Residuals are still pretty cranky
-# plot(mod.dd.species.slope.re)
-# # Normality still a hot mess
-# qqnorm(residuals(mod.dd.species.slope.re))
-# qqline(residuals(mod.dd.species.slope.re))
-# # draw some lines...
-# pred.dd.lmm.species.slope <- expand.grid(prop.abund = seq(0, 1, length.out = 100),Species=unique(dd.dat$Species))
-# tmp <- predict(mod.dd.species.slope.re, pred.dd.lmm.species.slope, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.species.slope$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.lmm.species.slope$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.species.slope$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.species.slope,aes(x=prop.abund,y=lam.no.fish,group=Species,color=Species)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Species, color=Species)) +
-#                                 scale_y_log10()
-# # Curious what species have high slopes.. Dubious and Esmarkii (North Sea sand lance and mackerel)
-# ranef(mod.dd.species.slope.re)
-# 
-# # So so what if we let the slopes vary by stock
-# mod.dd.stock.re <- lmer(log(lam.no.fish) ~ prop.abund +  (1+ prop.abund | Stock.short),data=dd.dat)
-# summary(mod.dd.stock.re)
-# #Residuals are slightly better I think but still really suck
-# plot(mod.dd.stock.re)
-# # Normality = no
-# qqnorm(residuals(mod.dd.stock.re))
-# qqline(residuals(mod.dd.stock.re))
-# # What's it look like?
-# pred.dd.lmm.stock <- expand.grid(prop.abund = seq(0, 1, length.out = 100),
-#                                          #Species=unique(dd.dat$Species),
-#                                          Stock.short=unique(dd.dat$Stock.short))
-# tmp <- predict(mod.dd.stock.re, pred.dd.lmm.stock, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.stock$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.lmm.stock$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.stock$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.stock,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Stock.short, color=Stock.short)) +
-#                                 scale_y_log10()
-# 
-# # Curious what stocks have high slopes.. Dubious and Esmarkii (North Sea sand lance and mackerel), NS Haddock and Irish Sea Haddock 
-# ranef(mod.dd.stock.re)
-# 
-# 
-# 
-# 
-# # OK, so this all still sucks, wonder if a glmer and gamma would get us anywhere... not really.... 
-# # Tried many variants on the glmer and they all land in the same lousy spot.
-# mod.dd.stock.gamma.re <- glmer(lam.no.fish ~ prop.abund +  (1+ prop.abund | Stock.short),data=dd.dat,family=Gamma(link='log'))
-# # OK...
-# summary(mod.dd.stock.gamma.re)
-# #Residuals, nah, still suck, just some crazy outliers...
-# plot(mod.dd.stock.gamma.re)
-# # Normality = no
-# qqnorm(residuals(mod.dd.stock.gamma.re))
-# qqline(residuals(mod.dd.stock.gamma.re))
-# # And the plot...
-# pred.dd.lmm.stock.gamma <- expand.grid(prop.abund = seq(0, 1, length.out = 100),
-#                                          #Species=unique(dd.dat$Species),
-#                                          Stock.short=unique(dd.dat$Stock.short))
-# tmp <- predict(mod.dd.stock.gamma.re, pred.dd.lmm.stock.gamma, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.stock.gamma$lam.no.fish   <- (tmp$fit)
-# pred.dd.lmm.stock.gamma$lower <- (tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.stock.gamma$upper <- (tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.stock.gamma,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Stock.short, color=Stock.short)) +
-#                                 scale_y_log10()
-# # None of the above really work at all....
-
-```
+The annual fecundity and natural mortality values  varied considerably for each stock.
+To account for this variability when evaluating recovery potential, we used a simulated population projection.
+For `r n.dt.sims` simulations, we took a random sample of the annual values for fecundity and natural mortality, used the life table reconstruction to estimate $\lambda$, and calculated abundance in the following year.
+Abundance of each stock was projected over `n.sim.years` years, and the percentage of the simulations in which the population size had doubled was recorded each year.
+For simplicity, we did not allow for density-dependent effects (e.g.
+potential population decline as abundance exceeds carrying capacity) because of uncertainty surrounding potential maximum population size for each species.
+Once a population had doubled, it was considered to have remained at that abundance or greater for the remainder of the projection.

### 2024-05-21 Drafts/Paper_1/tmp-04-results.Rmd
mid-edit update

--- 2024-05-10 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
@@
----
-output: word_document
-editor_options: 
-  chunk_output_type: console
----
+# Results {#reses-peses}
 
-```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4,include=F,message=F}
+<!-- Throughout the results we will focus primarily the six most commonly found species in the analysis (*Gadus morhua, Melogrammus aeglefinus, Clupie harengus, Plueronecties platessa, Polluck virens* and *Solea Solea*).
+The complete results for all of the stocks included in the analysis can be found in the Supplemental material.
+-->
 
-if(load.results==F)
-{
-  Stocks <- ASR.long |> 
-                      collapse::fsubset(!is.na(value)) |>
-                      collapse::fgroup_by(Stock, type) |>
-                      collapse::fsummarize(count=length(unique(value))) |>
-                      collapse::fgroup_by(Stock) |>
-                      collapse::fsummarize(types=length(unique(type))) |>
-                      collapse::fsubset(types==5) |>
-                      collapse::fselect(Stock)
+## Population growth rates ($\lambda$)
 
-  ASR.tmp <- ASR.long 
-  ASR.tmp$age <- as.numeric(ASR.tmp$age)
-  ASR.stocks <- ASR.tmp |> 
-                          collapse::fsubset(Stock %in% Stocks$Stock) |>
-                          collapse::fsubset(!is.na(value)) |>
-                          collapse::roworder(Stock, Year, type, age)
+The overall median population growth rate when excluding the effects of fishing ($\lambda_{F=0}$) was `r med.lambda.F0`, indicating that there was a latent potential for population growth for these stocks of approximately `r med.r.F0`%.
+When the effect of fishing was accounted for, the median population growth rate ($\lambda_{F>0}$) declined to `r med.lambda.F`, which suggested that the populations in this analysis may have been over-fished by approximately `r -med.r.F`% annually.
+However, for many of the stocks included in this analysis large recruitment events resulted in large estimates of $\lambda_{F>0}$, in some years, this led to a skewed distribution of the lambda estimates, with these large events being an integral component of the stocks population dynamics (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-bx-other-fig)).
+The mean $\lambda_{F>0}$ for the stocks in this analysis was `r mn.lambda.F` which would suggest there remains scope for population growth even after fishing.
+The mean$ \lambda_{F>0}$ was lower than the median for just `r n.stocks-n.mn.higher.med.fish` of the `r n.stocks` in this analysis.
+The majority of these stocks (`r n.nw.ice`) were in the central or NW Atlantic, and this included `r n.cod.low.mn`  of the `r n.cod` Atlantic cod stocks in this analysis.
 
-  # print(Stocks)
-  Stocks <- Stocks$Stock
+There were regional and species specific trends in both $\lambda_{F=0}$ and $\lambda_{F}$.
+Haddock (*M.
+aeglefinus*) and Atlantic cod (*G.
+morhua*) stocks had some of highest variability in lambda, both at the stock level and between stocks (Figure \@ref(fig:lambda-sd-fig)).
+For these two species, the variability of lambda within a stock declined as you moved from the Eastern Atlantic to the Western Atlantic (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig))).
+The pattern was more pronounced for Atlantic cod, with stocks in the eastern Atlantic tending to have relatively low within stock variability.
+The two other species with stocks found in the NW and NE Atlantic (*C.harengus* and *P.
+virens*) the variability of lambda between the stocks was much lower than for Haddock and Atlantic cod and there were no clear differences between regions (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig))).
+This was largely due to the within stock lambda variability being lower than the within stock variability of Haddock and Atlantic cod stocks in the NE Atlantic (Figure \@ref(fig:lambda-bx-6-fig)).
+Two other stocks (*A.
+dubious* and *T.
+esmarkii*) in the North Sea had highly variably lambda estimates, though notably the lambda was less variable than the estimates for Haddock and Atlantic cod in this area (Figure \@ref(fig:lambda-bx-other-fig)).
+For the remainder of other stocks in this analysis, years in which the value of $\lambda_{F=0}$ exceeded 1.5 were more rare.
+Exceptions to this included *M.
+merlangus* in the Celtic Sea, *P.
+dentatus* and *S.
+Chrysops* in the NW Atlantic, and the Gulf of Alaska *T.
+chalcogramma* stock in the Pacific Ocean (Figure \@ref(fig:lambda-bx-other-fig)).
 
-  # Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
-  #Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
-  # Esmarki doesn't work great as it is assessed using a quarterly model.
-  #Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
-  #i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
-  years.tmp <- NULL
-  pnm.tmp <- NULL
-  waa.tmp <- NULL
-  ages.tmp <- NULL
-  rem.tmp <- NULL
-  mx.tmp <- NULL
-  NE.tmp <- NULL
-  vpa.tmp <- NULL
-  am.tmp <- NULL
-  #mr.tmp <- NULL
-  abund.tmp <- NULL
-  full.abund.tmp <- NULL
-  full.rem.tmp <- NULL
-  fs.tmp <- NULL
-  for(i in Stocks)
-  {
-  print(i)
-  ASR.sub <- ASR.long |>
-    collapse::fselect(Year, Stock, type, age, value) |>
-    collapse::fsubset(Stock==i)
+## Density Dependence
 
-    # Dropping the first 7 years as the 8 year olds are all missing
-  if(i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR.sub <- ASR.sub |> collapse::fsubset(Year >= 1972)
-  # maxage <- max(as.numeric(ASR.sub$age[!is.na(ASR.sub$value)]))
-  # maxYear <- max(ASR.sub$Year[!is.na(ASR.sub$value)])
-  # minYear <- min(ASR.sub$Year[!is.na(ASR.sub$value)])
-  # forplot <- ASR.sub[as.numeric(ASR.sub$age) < (maxage+1) & ASR.sub$Year %in% minYear:maxYear,]
-  # 
-  # # summary plots
-  # print(ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
-  #         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
-  #         theme_bw() + 
-  #         ggtitle(i)
-  # )
+Overall, the evidence suggested that negative density dependence was common as both $\lambda_{F=0}$ and $\lambda_{F>0}$ increased as abundance declined (Figure \@ref(fig:dd-overall-plt)).
+The strength of density dependence appeared to be more pronounced at low and high abundance levels (i.e., changes in abundance had larger impacts on $\lambda$ when abundance was below $\approx$ 0.4 or above $\approx$ 0.7).
+$\lambda_{F=0}$ only declined below 1 when the stocks approached their maximum observed abundance ($\approx$ `r pa.lam.nf.at.one`%), indicating that in the absence of fishing there was a latent capacity for population growth in these stocks.
+However, when accounting for fishing mortality, $\lambda_{F>0}$ was below 1 until the stocks were below approximately `r pa.lam.fish.at.one`% of their maximum abundance.
+At lower abundances, the rate of increase in $\lambda_{F>0}$ was higher than $\lambda_{F=0}$, likely due to reductions in fishing mortality at low abundance, but overall $\lambda_{F>0}$ was lower than $\lambda_{F=0}$, suggesting that some fishing mortality was common even at very low abundance (Figure \@ref(fig:dd-overall-plt)).
 
-  age.mat <- ASR.sub |> collapse::fsubset(type=="AM") |> dplyr::rename(AM=value) |> collapse::fselect(-type)
-  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
-  # in case that changes later...
-  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
-  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
-  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
-  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
-  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
-  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0
+Generally, there was an increase in the variability of the $\lambda$ estimates as abundance declines, largely driven by an increase in the magnitude of the maximum value of $\lambda$ and a small increase in the frequency of low $\lambda$ values (Figure \@ref(fig:dd-overall-plt)).
+For example, values of $\lambda_{F>0}$ > `r pa.lam.fish.low.bigs` were not observed at abundances > `100*pa.big.threshold`% of the maximum (similar trends were observed for $\lambda_{F=0}$, with only one point being above `r pa.lam.nf.low.bigs` when the abundance was > `r 100*pa.big.threshold`% of the maximum).
+Similarly, the percentage of $\lambda_{F>0}$ values below `r lam.low.threshold` was `r 100*prop.low.high.abund`% when the proportion of the abundance was >= 0.3, but this increased to `r 100*prop.low.low.abund`% of the data when the proportion of the abundance was below 0.3.
 
-  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
-  nat.mort <-  ASR.sub |> collapse::fsubset(type=="NM") |> dplyr::rename(NM=value) |> collapse::fselect(-type)
-  abund <- ASR.sub |> collapse::fsubset(type=="Num") |> dplyr::rename(Num=value) |> collapse::fselect(-type)
-  weight.age <- ASR.sub |> collapse::fsubset(type=="WA") |> dplyr::rename(WA=value) |> collapse::fselect(-type)
-  if(i == Stocks[30]) weight.age$WA <- weight.age$WA/1000
-  removals <- ASR.sub |> collapse::fsubset(type=="Catch") |> dplyr::rename(Catch=value) |> collapse::fselect(-type)
+However, these general patterns were highly variable between stocks.
+All of the stocks included in this analysis had $\lambda_{F=0}$ estimates > 1 at their lowest observed abundances (Table \@ref(tab:tab-lambdas) and Figure \@ref(fig:dd-nf-stock-plt)).
+Stocks in the Northwest Atlantic (particularly Atlantic cod) and Alaska had some of the lowest $\lambda_{F=0}$ estimates at low abundance, while several stocks in the North Sea had among the highest $\lambda_{F=0}$ estimates at low abundance (Table \@ref(tab:tab-lambdas)).
+Of the `r n.bl.40` stocks that had declined below 40% of the maximum abundance, only `r `n.low.40.nf` of the stocks had a $\lambda_{F=0}$ estimates < 1 at 40% of their maximum abundance; when the effects of fishing were included `r `n.low.40.nf` of the stocks had $\lambda_{F>0}$ estimates below 1 (Table \@ref(tab:tab-lambdas)).
 
-  data <- age.mat |>
-    full_join(nat.mort) |>
-    full_join(abund) |>
-    full_join(weight.age) |>
-    full_join(removals)
+For the vast majority of stocks the lowest values of both $\lambda_{F=0}$ (`r n.low.lam.at.max.nf` of `r n.stocks`) and $\lambda_{F>0}$ (`r n.low.lam.at.max.fish` of `r n.stocks`) were found near the maximum abundance in the time series (Figures \@ref(fig:dd-nf-stock-plt) and \@ref(fig:dd-fish-stock-plt)).
+Atlantic cod in the Northwest Atlantic comprised `r n.cod.lam.not.at.max.nf` of the `r n.stocks - n.low.lam.at.max.nf` stocks in which the lowest $\lambda$ was observed below the maximum abundance, the low $\lambda$ occurred at population abundances that were remarkably similar for these Atlantic cod stocks (ranging between `r pa.low.cod.min` and `r pa.low.cod.max`).
+For two of the `r n.stocks - n.low.lam.at.max.nf` stocks, the lowest $\lambda_{F=0}$ estimates were less than 0.005 smaller than the estimate at the maximum abundance, for the other four stocks the decline in $\lambda_{F=0}$ from the highest abundance observed was somewhat pronounced, ranging from `r low.4.lam.40.nf` to `r low.lam.40.nf` (Tables \@ref(tab:tab-lambdas) and \@ref(tab:tab-lamda-diffs) and Figures \@ref(fig:dd-nf-stock-plt) and \@ref(fig:dd-fish-stock-plt) ).
 
-  # Aahh??  Is this NA dropping useful data, needed to quick fix the age at maturity data...
-  data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
-  data <- data[data$available==T,]
+## Demographic Parameters
 
-  # Tidy up the data for input...
-  data$prop.nat.mort <- 1-exp(-data$NM)
-  #prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))] <- 1-exp(-prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))])
+The lifetime reproductive output and generation length were estimated for each cohort in which data were available.
+When excluding fishing mortality, the overall median lifetime reproductive output, (i.e., the number of females produced by one female that survive to reproduce) was `r r0.med` (mean = `r r0.mn`; Figures \@ref(fig:r0-6-plt) and \@ref(fig:r0-other-plt)).
+When the realized fishing mortality was accounted for, the median reproductive output dropped to `r r0.med.fish` (mean = `r r0.mn.fish`), this again highlighted the importance of large reproductive events for survival of these stocks and the latent capacity for population growth (Figures \@ref(fig:r0-6-plt) and \@ref(fig:r0-other-plt)).
+For stocks which were found across the north Atlantic, the lifetime reproductive output when excluding fishing mortality tended to decline as your move west, this again was most evident for the Atlantic cod stocks.
+While the reproductive potential of cohorts within a stock could be highly variable, there were no clear temporal trends in the $R_0$ (Figures \@ref(fig:r0-nf-ts-plt) and \@ref(fig:r0-fish-ts-plt)).
 
-  rem <- data |> collapse::fgroup_by(Year) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
-  #rem <- data |> dplyr::group_by(Year,.drop=F) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
+The generation lengths tended to become more similar between stocks both intra- and inter-specifically when accounting fishing mortality (Figures \@ref(fig:gl-6-plt) and \@ref(fig:gl-other-plt)).
+In addition, the generation length of *C.
+harengus*, generally considered a short lived species, in the Central and NW Atlantic tended to be higher than the generation length of Atlantic cod and haddock, especially for the stocks in the NE Atlantic (Figure \@ref(fig:gl-6-plt)).
+There were no obvious patterns in the temporal trends in the generation length (Figures \@ref(fig:gl-nf-ts-plt) and \@ref(fig:gl-fish-ts-plt)).
 
-  # Never run, so not doing anything.
-  # missing_rem<- NULL
-  # if(any(is.na(rem$rem))) 
-  # {
-  #   missing_rem <- unique(data$Year)[which(is.na(rem$rem))]
-  #   rem$rem[is.na(rem$rem)] <- median(rem$rem, na.rm=T)
-  # }
+## Recovery Potential
 
-  #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
-  years <- data |> dplyr::pull(Year) |> unique() |> sort()
+The recovery potential in the absence of fishing was relatively high for the majority of species (Figure \@ref(fig:dub-time-map)).
+Of the `r n.stocks` stocks in this analysis, `r n.dub.10` had a high recovery potential (we define 'high' as at least `r 100*dub.p.high`% of the simulations having experienced a doubling in size) within 10 years, by year 20 this had increased to `r n.dub.20` stocks (Figure \@ref(fig:dub-ts)).
 
-  N.end <- sum(data[data$Year==max(years),]$Num)
-  vpa.abund <- data |> dplyr::group_by(Year) |> dplyr::summarize(vpa=sum(Num,na.rm=T)) |> pull(vpa)
+The stocks in which recovery potential was low (we define low as < `r 100*dub.p.low`% of the simulations experiencing a doubling in size) exhibited clear regional trends.
+Of the `r n.not.dub.20` stocks in this analysis in which the recovery potential was low after 20 years, `r n.alaska.slow` of the stocks were in Alaska (`r n.alaska` stocks in total), and `r n.nwa.slow` stocks in NAFO Regions 2-4 in the NW Atlantic (`r n.nafo.24` stocks were in NAFO Regions 2-4).
+This contrasts to only `r n.nea.slow` of the `r n.nea` stocks in the NE Atlantic with a low recovery potential within 20 years in the absence of fishing (Figure \@ref(fig:dub-time-map)).
 
-  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
-  #minage
-  minage <- min(as.numeric(data$age))
-  #maxage
-  maxage <- max(as.numeric(data$age))
-  #recruits
-  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
-  #ssn
-  data$ssn <- data$Num * data$AM
-  #ssb
-  data$ssb <- data$ssn * data$WA #I need to figure out how to line this up with the number of recruits for the right years in the data object.... got it right for the overall r.p.ssb below.
-  #tot.ssb
-  annual <- data |> group_by(Year) |> summarize(tot.ssb = sum(ssb)) |> left_join(annual)
-
-  #tst <- data |> group_by(Year) |> summarize(tot.ssn = sum(ssn)) |> left_join(annual)
-
-  #r.p.ssb This needs to be offset by the age of recruits. So here's my lining this up logic.  For age 0, we get
-  # the recruit and SSB estimates from the same survey, thus these age 0 recruits will have been produced by the SSB in the previous year...
-  # So the R in 1970 were produced by SSB in 1969 when min age =0
-  # If min.age = 1 then R in 1970 is produced by SSB in 1968... and so on.
-  # FIX 1 "Recruit year" = SSB year + min.age + 1 (or min.age +2 as SSB.year is the first column)
-  # Now for RPS there's another wrinkle because of this, because our model is N(1970) = lambda * N(1969) and lambda is made up of lx and mx
-  # so if the recruits show up in 1970, the fecundity term that gets us there (irrespective of the age offset) has to be for 1969, becuase
-  # that gets us to the babies that show up in 1970
-  # FIX 2 So "RPS year, recs.per.age year, and mx year" = SSB year + min.age
-  # I believe this to be correct, but we all need to discuss this to make sure the logic holds.
-  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+2):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage-1)],NA)
-  # recs.per.age
-  data <- left_join(data, annual)
-  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
-  tmp <- NULL
-  for(j in 1:length(years))
-  {
-    tst <- data|> collapse::fsubset(Year == years[j]) |> collapse::fselect(ssb,ssn,Year,age)
-    tst$Year <- tst$Year + minage # We want this to line up the the RPS year, so just adding minage here.
-    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
-    tmp[[j]] <- tst
-  }
-  # Unpack the list
-  ssb.off <- do.call('rbind',tmp)
-  # And merge it with the data object
-  data <- left_join(data,ssb.off,by=c("Year","age"))
-  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
-  # mx
-  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
-  # No longer dividing by 2 because we should really divide recruits and ssn by 2 to be female only, but that's pointless so we roll along with this.
-  data$mx <- data$recs.per.age/data$ssn.offset # if(grepl("males",i)) 
-  #if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
-  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
-  # Easier to remove the years where we don't have recs.per.age...
-  #data <- data |> collapse::fsubset(Year %in% years[(minage+1):length(years)])
-
-  age.mat <- data |> collapse::fselect("Year", "age", "AM") |> 
-                     pivot_wider(names_from=age, values_from = AM) |> collapse::fselect(-Year)
-  prop.nat.mort <- data |> collapse::fselect("Year", "age", "prop.nat.mort") |> 
-                            pivot_wider(names_from=age, values_from = prop.nat.mort) |> 
-                            collapse::fselect(-Year) |> as.data.frame()
-
-  weight.age <- data |> collapse::fselect("Year", "age", "WA") |> pivot_wider(names_from=age, values_from = WA) |> collapse::fselect(-Year)
-  mx <- data |> collapse::fselect("Year", "age", "mx") |> 
-                 pivot_wider(names_from=age, values_from = mx) |> 
-                 collapse::fselect(-Year) |> as.data.frame()
-  # Get the abundance matrix
-  abund.age <- data |> collapse::fselect("Year", "age", "Num") |> 
-                        pivot_wider(names_from=age, values_from = Num) |> 
-                        collapse::fselect(-Year) |> as.data.frame()
-
-  # Now we can save out the catch and get an instantaneous F
-    data$Catch[is.na(data$Catch)] <- 0
-    data$Exp <- data$Catch/data$Num 
-    # If it is exactly 1 that leads to an Inf, which is annoying, so make it 1.1 and fix it with the rest below
-    data$Exp[data$Exp == 1] <- 1.1
-    # And make this an F
-    data$Fs <- -log(1-data$Exp)
-    if(any(is.na(data$Fs)))
-    {
-      fixers <- which(is.na(data$Fs))
-      print(paste0("Had to replace ",length(fixers), ' exploitation rates for stock ',i))
-      for(f in fixers)
-      {
-        yr <- data$Year[f]
-        fs <- max(data$Fs[data$Year == yr],na.rm=T)
-        data$Fs[f] <- fs
-        data$Exp[f] <- 1-exp(-fs)
-      }
-    }
-
-  full.rems <- data |> collapse::fselect("Year", "age", "Catch") |> pivot_wider(names_from=age, values_from = Catch) |> collapse::fselect(-Year)
-  full.Fs <-  data |> collapse::fselect("Year", "age", "Fs") |> pivot_wider(names_from=age, values_from = Fs) |> collapse::fselect(-Year)
-
-    if(i == "DFO_2J3KL_Gadus_morhua")
-    {
-      age.mat[,8:10] <- 1
-      prop.nat.mort[,8:10] <- prop.nat.mort[,7]
-      weight.age[12:14,9:10] <- weight.age[12:14,8]
-      weight.age[15,10] <- weight.age[15,9]
-      mx[12:16,9:10] <- mx[12:16,8]
-      mx[17,10] <- mx[17,9]
-      full.Fs[12:14,9:10] <- full.Fs[12:14,8]
-      full.Fs[15,10] <- full.Fs[15,9]
-      abund.age[12:14,9:10] <- abund.age[12:14,8]
-      abund.age[15,10] <- abund.age[15,9]
-      # I could calculate, but this will get us to the same place...
-      full.rems[12:14,9:10] <- full.rems[12:14,8]
-      full.rems[15,10] <- full.rems[15,9]
-    }
-
-    if(i == "DFO_4T-Spring_Clupea_harengus")
-    {
-      age.mat[6:7,10] <- 1
-      prop.nat.mort[6:7,10] <- prop.nat.mort[6:7,9]
-      weight.age[6:7,10] <- weight.age[6:7,9]
-      mx[6:9,10] <- mx[6:9,9]
-      full.Fs[6:7,10] <- full.Fs[6:7,9]
-      abund.age[6:7,10] <- abund.age[6:7,9]
-      full.rems[6:7,10] <- full.rems[6:7,9]
-    }
-
-    if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
-    {
-      age.mat[30,8] <- 1
-      prop.nat.mort[30,8] <- prop.nat.mort[30,7]
-      weight.age[30,8] <- weight.age[29,8]
-      mx[30:31,8] <- mx[30:31,9]
-      full.Fs[30,8] <- full.Fs[30,7]
-      abund.age[30,8] <- abund.age[30,7]
-      full.rems[30,8] <- full.rems[30,7]
-    }
-
-    if(i == "ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax")
-    {
-      age.mat[c(14,27,40),5] <- age.mat[1,5]
-      prop.nat.mort[c(14,27,40),5] <- prop.nat.mort[1,5]
-      weight.age[c(14,27,40),5] <- weight.age[c(13,26,39),5]
-      mx[c(14,16,27,29,40,42),5] <- mx[c(14,16,27,29,40,42),6]
-      full.Fs[c(14,27,40),5] <- full.Fs[c(14,27,40),4]
-      abund.age[c(14,27,40),5] <- abund.age[c(14,27,40),4]
-      full.rems[c(14,27,40),5] <- full.rems[c(14,27,40),4]
-    }
-    # Clear out some 0's...
-    if( i == "AFSC_EEBSAI_Limanda_aspera")
-    {
-      mx[5,18] <- mean(unlist(mx[5,c(17,19)]))
-      mx[c(6,8),19] <- mx[c(6,8),18]
-      mx[2:7,20] <- mx[2:7,19] 
-    }
-
-  # I had filled the years with no SSB data to inform them.  instead I'm going to remove those years...
-
-   if(minage >0) 
-  {
-    rm <- -(1:minage)
-    years <- years[rm]
-    prop.nat.mort <- prop.nat.mort[rm,]
-    weight.age <- weight.age[rm,]
-    rem <- rem[rm,]
-    mx <- mx[rm,]
-    vpa.abund <- vpa.abund[rm]
-    age.mat <- age.mat[rm,]
-    abund.age <- abund.age[rm,]
-    full.Fs <- full.Fs[rm,]
-    full.rems <- full.rems[rm,]
-   }
-  #   mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
-  #   names(mx) <- names(mx.fill)
-  #  # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
-  #   mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
-  # }
-
-    years.tmp[[i]] <- years
-    pnm.tmp[[i]] <- prop.nat.mort
-    waa.tmp[[i]] <- weight.age
-    ages.tmp[[i]] <- minage:maxage
-    rem.tmp[[i]] <- rem
-    mx.tmp[[i]] <- mx
-    NE.tmp[[i]] <- N.end
-    vpa.tmp[[i]] <- vpa.abund
-    am.tmp[[i]] <- age.mat
-    #mr.tmp[[i]] <- missing_rem
-    abund.tmp[[i]] <- abund.age
-    fs.tmp[[i]] <- full.Fs
-    full.rem.tmp[[i]] <- full.rems
-  } #end input data loop
-
-  save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,
-       am.tmp,Stocks,ASR.stocks,ASR.long,abund.tmp,fs.tmp,full.rem.tmp,
-       file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
-
-  } # end load results
-```
-
-  So now I can try to do some tuning, both forwards and backwards, lets see what we get from that...
-
-```{r tunes,include=F,echo=F,warning=F,message=F}
-
-  ########################## Now run the tuning sims
-  #
-
-  if(load.results==F)
-  {
-  load(file = paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
-
-  for.tune.all.res <- NULL
-  for.tune.summary <- NULL
-  for(i in Stocks)
-  {
-    years <- years.tmp[[i]]
-    prop.nat.mort <- pnm.tmp[[i]] 
-    #rem <- rem.tmp[[i]] 
-    mx <- mx.tmp[[i]] 
-    N.end <- NE.tmp[[i]] 
-    ages <- ages.tmp[[i]]
-    vpa.abund <- vpa.tmp[[i]] 
-    abund <- abund.tmp[[i]]
-    fs <-fs.tmp[[i]]
-    full.rem <- full.rem.tmp[[i]]
-    #full.abund <- full.abund.tmp[[i]]
-    #all.abund <- full.abund.tmp[[i]]
-    #N.end <- vpa.abund[length(vpa.abund)]
-    #Pick your step size
-    ss.size <- 0.005
-    sensistive.stocks <- c("AFSC_GOA_Theragra_chalcogramma",
-                            "DFO_2J3KL_Gadus_morhua",
-                            "DFO_3Pn-4RS_Gadus_morhua",
-                            "DFO_4T-4VN_Gadus_morhua",
-                            "DFO_4T_Scomber_scombrus",
-                            "ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus",
-                            "ICES-AFWG_NEA1-2_Gadus_morhua",
-                            "ICES-HAWG_NS_Ammodytes_dubius",
-                            "ICES-NWWG_FA5b_Pollachius_virens",
-                            "ICES-NWWG_FAPL5b1_Gadus_morhua",
-                            "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
-                            "ICES-WGCSE_IS7a_Gadus_morhua",
-                            "ICES-WGCSE_CS7a_Merlangius_merlangus",
-                            "ICES-WGCSE_CS7e-k_Gadus_morhua",
-                            "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
-                            "ICES-WGHANSA_SP8abd_Sardina _pilchardus", 
-                            "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua",
-                            "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",
-                            "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus",
-                            "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
-                            "NEFSC-GARMIII_SNE- MA_Limanda_ferruginea",
-                            "NEFSC-GARMIII_MA_Paralichthys_dentatus",
-                            "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus",
-                            "NEFSC_NWA_Scomber _scombrus")
-
-    if(i %in% sensistive.stocks) ss.size = ss.size/10
-
-     N.start <- vpa.abund[1]
-     print(i)
-     # The fecundities are 
-     fast.for.tune <- fast.tunes(years,
-                             tuner=what.2.tune,
-                             step.size = ss.size, 
-                             abund.ts = vpa.abund,
-                             ages=ages,
-                             nm = -(log(1-prop.nat.mort)),
-                             fecund = mx,
-                             fm = fs,
-                             abund.age = abund, 
-                             catch.age = full.rem, 
-                             N.init = N.start,
-                             direction= 'forwards'
-                             )
-
-     for.tune.all.res[[i]] <- fast.for.tune
-     for.tune.tmp <- data.frame(fast.for.tune$res,Stock = i)
-     for.tune.summary[[i]] <- for.tune.tmp
-  }
-
-  saveRDS(for.tune.summary,paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-  saveRDS(for.tune.all.res,paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
-  # 
-}# end if load results
-
-```
-
-```{r paper-other-metrics-and-metadata,echo=F,include=F,warning=F,message=F}
-
-if(load.results==F)
-{
-  # We are now looking at everything, lifetime reproductive success
-
-  for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-  for.tune.all <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
-
-  load(file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
-  # Get the stocks...
-  Stocks <- names(for.tune.summary)
-  n.stocks <- length(Stocks)
-
-  ############ Meta data and clean up, could be it's own chunk really, but it's really fast, so meh...
-
-  #  A quick way to get the other potentially interesting info for the stock...
-  drop <- which(names(ASR.long) %in% c("Year","type","age","value"))
-  meta <- NULL
-  for(i in Stocks) 
-  {
-    meta[[i]] <- ASR.long[ASR.long$Stock == i,-drop][1,]
-    meta[[i]]$age.min <- min(ages.tmp[[i]])
-    meta[[i]]$age.max <- max(ages.tmp[[i]])
-  }
-  meta <- do.call('rbind',meta)
-
-  # First making a meta data object and adding a bunch of columns to it... very messy!!
-  meta$Species[meta$Species == ' harengus']  <- "harengus"
-  meta$Species[meta$Species == "Aeglefinus"] <- "aeglefinus"
-  meta$Species[meta$Species == "Solea"] <- "solea"
-  meta$Family[meta$Family == "Gadide"] <- "Gadidae"
-  meta$Genus[meta$Genus == " Hippoglossoides"] <- "Hippoglossoides"
-  meta$G.short <- toupper(paste0(substr(meta$Genus,1,1),"."))
-  meta$G.Species <- paste0(meta$G.short," ",meta$Species)
-  # Simplified Management
-  meta$Manage.short <- meta$Management
-  meta$Manage.short[grep("TRAC",meta$Management)] <- "DFO-TRAC"
-  meta$Manage.short[grep("DFO",meta$Management)] <- "DFO-TRAC"
-  meta$Manage.short[grep("NEFSC",meta$Management)] <- "NEFSC"
-  meta$Manage.short[grep("ICES",meta$Management)] <- "ICES"
-
-  # The 3 pieces of the ocean
-  meta$LME <- "NW Atlantic"
-  meta$LME[meta$Management == "AFSC"] <- "Pacific (Alaska)"
-  meta$LME[grepl("ICES",meta$Management)] <- "NE Atlantic"
-  # An area typo
-  meta$Area[grep("BSAI-females",meta$Area)] <- "BSAI-Females"
-  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI-Females"
-  # Some other Area summaries
-  meta$Area.broad <- meta$Area
-  meta$Area.long <- meta$Area
-  meta$Area.narrow <- "" # Leave this blank if not needed
-
-  meta$Area.broad[grep("NS",meta$Area)] <- "NS"
-  meta$Area.long[grep("NS",meta$Area)] <- "North Sea"
-  meta$Area.broad[grep("CS",meta$Area)] <- "CS"
-  meta$Area.long[grep("CS",meta$Area)] <- "Celtic Sea"
-  meta$Area.broad[grep("ROCK6b",meta$Area)] <- "CS"
-  meta$Area.long[grep("ROCK6b",meta$Area)] <- "Celtic Sea"
-  meta$Area.broad[grep("IS",meta$Area)] <- "IS"
-  meta$Area.long[grep("IS",meta$Area)] <- "Irish Sea"
-  meta$Area.broad[grep("BS",meta$Area)] <- "BS"
-  meta$Area.long[grep("BS",meta$Area)] <- "Baltic Sea"
-  meta$Area.broad[grep("NEA",meta$Area)] <- "NEA"
-  meta$Area.long[grep("NEA",meta$Area)] <- "NE Arctic"
-  meta$Area.broad[grep("B28.1",meta$Area)] <- "BS"
-  meta$Area.long[grep("B28.1",meta$Area)] <- "Baltic Sea"
-  meta$Area.broad[grep("SP8abd",meta$Area)] <- "BoB"
-  meta$Area.long[grep("SP8abd",meta$Area)] <- "Bay of Biscay"
-  meta$Area.broad[grep("FA",meta$Area)] <- "Ice-Faroe"
-  meta$Area.broad[grep("ICE",meta$Area)] <- "Ice-Faroe"
-  meta$Area.long[grep("FA",meta$Area)] <- "Faroes"
-  meta$Area.long[grep("ICE",meta$Area)] <- "Iceland"
-
-  meta$Area.broad[grep("GOM",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("GOM",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("GB",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("GB",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("5Y",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("5Y",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("5Z",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("5Z",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("USATL",meta$Area)] <- "NAFO 5-6" # The fishery is broader than just GOM, but it does also include it.
-  meta$Area.long[grep("USATL",meta$Area)] <- "NAFO 5-6" # The fishery is broader than just GOM, but it does also include it.
-  meta$Area.broad[grep("NWA",meta$Area)] <- "NAFO 5-6" # Mackerel... so that definition is a bit narrow....
-  meta$Area.long[grep("NWA",meta$Area)] <- "NAFO 5-6" # Mackerel... so that definition is a bit narrow....
-  #meta$Area1[grep("SNE- MA",meta$Area)] <- "GOM-GB" # YT in US, so no GB so that definition is a bit narrow....
-  meta$Area.broad[grep("MA",meta$Area)] <- "NAFO 5-6" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
-  meta$Area.long[grep("MA",meta$Area)] <- "NAFO 5-6" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
-  meta$Area.broad[grep("BSAI",meta$Area)] <- "BSAI"
-  meta$Area.broad[grep("4T",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("4T",meta$Area)] <- "NAFO 2-4"
-  meta$Area.broad[grep("2J3",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("2J3",meta$Area)] <- "NAFO 2-4"
-  meta$Area.broad[grep("3Pn-4RS",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("3Pn-4RS",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("GOA",meta$Area)] <- "Gulf of Alaska"
-  # Lumping everything in Berring Sea and AI into both.
-  meta$Area.long[grep("AI",meta$Area)] <- "Aleutian Islands"
-  meta$Area.long[grep("ESB",meta$Area)] <- "Bering Sea & AI" 
-  meta$Area.long[grep("BSAI",meta$Area)] <- "Bering Sea & AI"
-  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI"
-  meta$Area[grep("BSAI-Females",meta$Area)] <- "BSAI"
-  meta$Area[grep("BSAI-females",meta$Area)] <- "BSAI"
-  meta$Area.long[grep("BSAI-Females",meta$Area)] <- "Bering Sea & AI"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Pollachius_virens"] <- "5b"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5a_Pollachius_virens"] <- "5a"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS4 _Solea_solea"] <- "4"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d._Solea_solea"] <- "7d"
-  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_NS IIIa 22-24_Solea_Solea"] <- "22-24"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d_Pleuronectes_platessa"] <- "7d"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4,20_Pleuronectes_platessa"] <- "4 20"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS7e_Pleuronectes_platessa"] <- "7e"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS27.7a_Pleuronectes_platessa"] <- "7a"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Melanogrammus_aeglefinus"] <- "5b"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Melanogrammus_aeglefinus"] <- "5a"
-  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_B28.1_Clupea_harengus"] <- "28"
-  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_BS 25-29-32_Clupea_harengus" ] <- "25-32"
-  meta$Area.narrow[meta$Stock == "ICES-HAWG_WBS 22-24_Clupea_harengus"] <- "22-24"
-  meta$Area.narrow[meta$Stock == "DFO_4T-Fall_Clupea_harengus"] <- "Fa-SGSL"
-  meta$Area.narrow[meta$Stock == "DFO_4T-Spring_Clupea_harengus"] <- "Sp-SGSL"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS27.6a_Merlangius_merlangus"] <- "27.6a"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS7a_Merlangius_merlangus"] <- "7a"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Gadus_morhua"] <- "5a"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FAPL5b1_Gadus_morhua" ] <- "5b"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua"] <- "4-7 20"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_NS6a_Gadus_morhua"] <- "6a"
-  meta$Area.narrow[meta$Stock == "DFO_2J3KL_Gadus_morhua"] <- "NFLD"
-  meta$Area.narrow[meta$Stock == "DFO_3Pn-4RS_Gadus_morhua"] <- "NGSL"
-  meta$Area.narrow[meta$Stock == "NEFSC-CERT-TRAC_GB _Gadus_morhua"] <- "EGB"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus"] <- "RA"
-  meta$Area.narrow[meta$Stock == "DFO_4T-4VN_Gadus_morhua"] <- "SGSL"
-  meta$Area.narrow[meta$Stock == "DFO_4T_Hippoglossoides _platessoides"] <- "SGSL"
-  meta$Area.narrow[meta$Stock == "DFO_4T_Scomber_scombrus"] <- "SGSL"
-  meta$Area.narrow[meta$Stock == "NEFSC-SAW_GOM_Gadus_morhua"] <- "GOM"
-  meta$Area.narrow[meta$Stock == "NEFSC-GARMIII_GB_Gadus_morhua"] <- "GB"
-  meta$Area.narrow[meta$Stock == "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus"] <- "GOM"
-  meta$Area.narrow[meta$Stock == "CERT-TRAC_GB_Melanogrammus_Aeglefinus"] <- "GB"
-
-  meta$Stock.short <- paste0(meta$Area.broad," ",meta$Area.narrow," ",meta$G.short," ",meta$Species)
-  meta$Stock.no.species <- paste0(meta$Area.long," ",meta$Area.narrow)
-
-  for.tune.stocks <- NULL
-  fta <- NULL
-
-  # Going to rename these female stocks.
-  fem.names <- c("AFSC_BASI-Females_Pleuronectes_quadrituberculatus",
-                    "AFSC_EEBSAI-Females_Lepidopsetta_polyxystra",
-                    "AFSC_BSAI-females_Atheresthes_stomais")
-  fem.rename <- c("AFSC_BSAI_Pleuronectes_quadrituberculatus",
-                    "AFSC_EEBSAI_Lepidopsetta_polyxystra",
-                    "AFSC_BSAI_Atheresthes_stomais")
-  # Going to drop these stocks
-  dont <- paste(c("Mles","Males","COASTNOR"),collapse = "|")
-
-  meta.sub <- NULL
-  for(i in Stocks) 
-  {
-    org.nam <- i
-    tmp <- for.tune.summary[[org.nam]]
-    new.stock.nam <- org.nam
-    # Don't bother for these stocks...
-    if(!grepl(dont,tmp$Stock[1]))
-    {
-      # Grab the metadata and add in some new useful things...
-      meta.sub[[i]] <- meta[meta$Stock == org.nam,]
-
-      # Rename the ladies
-      if(tmp$Stock[1] == fem.names[1]) new.stock.nam <- tmp$Stock <- fem.rename[1]
-      if(tmp$Stock[1] == fem.names[2]) new.stock.nam <- tmp$Stock <- fem.rename[2]
-      if(tmp$Stock[1] == fem.names[3]) new.stock.nam <- tmp$Stock <- fem.rename[3]
-
-      meta.sub[[i]]$Stock <- new.stock.nam
-      tmp <- data.frame(tmp,meta.sub[[i]])
-      # For tunes all
-      fta[[new.stock.nam]] <- for.tune.all[[org.nam]]
-      fta[[new.stock.nam]]$meta <- meta.sub[[i]]
-      for.tune.stocks[[new.stock.nam]] <- tmp
-    }# End skip stocks...
-  }
-  # Now unpack them...
-  for.tunes <- do.call("rbind",for.tune.stocks)
-  for.tune.all <- fta
-  meta.sub <- do.call("rbind",meta.sub)
-
-  ######################### End Meta data and clean up #####################
-
-  # Now some summaries...
-
-  # Reset on the stocks...
-  Stocks <- sort(names(for.tune.all))
-  n.stocks <- length(Stocks)
-
-  # Doubling time, no fishing
-  dt.res <- NULL
-  # These are both set in the index file now, go there!!
-  n.dt.sims <- n.dt.sims
-  n.sim.years <- n.sim.years
-  for(i in Stocks)
-  {
-    str.time <- Sys.time()
-    try <- for.tune.all[[i]]
-    meta.tmp <- try$meta
-    age.4.sim <- meta.tmp$age.min:meta.tmp$age.max
-    double.time <- NA
-    pop <- 1000
-    tmp.res <- NULL
-  for(s in 1:n.dt.sims)
-  {
-    tmp <- rep(0,n.sim.yearss)
-    print(paste0("Sim # ", s))
-
-    for(y in 2:n.sim.yearss)
-    {
-
-      # Get our sample for this run
-      f.pick <- sample(nrow(try$fecund.opt),size=1)
-      nm.pick <- sample(nrow(try$nm.opt),size=1)
-      fec.samp <- try$fecund.opt[f.pick,]
-      # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
-      nm.samp <- try$nm.opt[nm.pick,] 
-      # now put these into Euler-lotka to get an r estimate
-      res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
-      r.val <- res$res$r
-      # If r is > 5 (lambda = exp(5)) it generally means the simple.lotka didn't converge (bad combo of fec and nm)
-      # So we'll need to resample them until it is < 5
-      while(r.val >= 5)
-      {
-        print("Resampling due to bat shit r value")
-        f.pick <- sample(nrow(try$fecund.opt),size=1)
-        nm.pick <- sample(nrow(try$nm.opt),size=1)
-        fec.samp <- try$fecund.opt[f.pick,]
-        # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
-        nm.samp <- try$nm.opt[nm.pick,] 
-        # now put these into Euler-lotka to get an r estimate
-        res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
-        r.val <- res$res$r
-      } # end while loop
-      pop[y] <- exp(r.val)*pop[y-1]
-      if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.sim.yearss] <- 1
-    } # end the years loop
-    tmp.res[[s]] <- data.frame(year =1:n.sim.yearss,doubled = tmp,sim=s)
-
-    } # end sim loop
-    res.tmp <- do.call("rbind",tmp.res)
-
-  dt.res[[i]] <- data.frame(res.tmp,meta.tmp)
-  count <- 0
-  timer <- round(difftime(Sys.time(),str.time,units='mins'),digits=1)
-  print(paste0("Stock ",i," time =", timer," minutes: Stock # ",count+1))
-  } # end Stocks loop
-
-  dub.time <- do.call("rbind",dt.res)
-
-  dub.time.summary <- dub.time |> collapse::fgroup_by(Stock,year)  |> collapse::fsummarise(prop = sum(doubled)/n.dt.sims)
-  dub.time.summary <- left_join(dub.time.summary,meta.sub,by="Stock")
-
-  # Now to get generation lengths + reproductive rates....
-  # First I need to get the fecundity and natural mortalities by cohort instead of year.
-  res.fin <- NULL
-  res.year.fin <- NULL
-  res.lambda.fin <- NULL
-  for(i in Stocks) # 
-  {
-    tst <- for.tune.all[[i]]
-    meta.tmp <- tst$meta
-    # Fishing mortality
-    fm.org.tmp <- tst$fm.org
-    fm.tmp <- tst$fm.opt
-    # fecundity
-    fec.tmp <- tst$fecund.opt
-    fec.org.tmp <- tst$fecund.org
-    # Natural mortality
-    m.org.tmp <- exp(-tst$nm.org) # This is survivorship
-    m.tmp <- exp(-tst$nm.opt) # This is survivorship
-    # Total mortality
-    z.tmp <- exp(-tst$z.opt) # This is survivorship
-    z.org.tmp <- exp(-tst$nm.org -fm.org.tmp) # This is survivorship
-
-    ages <- meta.tmp$age.min:meta.tmp$age.max
-    n.ages <- length(ages)
-    years <- tst$res$year
-    n.years <- length(years)
-    # Now I need to grab the fecundities and nat morts by cohort
-    if(n.years > n.ages)
-    {
-    res.cohort <- NULL
-    res.year <- NULL
-    res.lambda <- NULL
-    for(y in 1:(n.years-n.ages+1))
-    {
-      count = 0
-      fs <- NA
-      # The lx is no fishing survivorship, zx I'm calling the survivorship including fishing
-      lx <- lx.org <- lx.year <- zx <- zx.org <- zx.year <- 1
-      fs.org <- NA
-
-      for(a in 1:n.ages)
-      {
-      fs[a] <- fec.tmp[y+count,a]  
-      fs.org[a] <- fec.org.tmp[y+count,a]  
-      if(a > 1) 
-      {
-        # No fishing
-        lx[a] <- lx[a-1] * m.tmp[y+count,a]  
-        lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
-        lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
-        # Including fishing
-        zx[a] <- zx[a-1] * z.tmp[y+count,a]  
-        zx.org[a] <- zx.org[a-1]* z.org.tmp[y+count,a]  
-        zx.year[a] <- zx.year[a-1] * z.tmp[y,a]
-      }  # end the a > 1 if
-          count <- count + 1
-      }# end the ages loop
-          res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,
-                                 mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
-                                 x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
-                                 zx.opt = zx,
-                                 mx.zx.opt = fs*zx,mx.zx.org = fs.org*zx.org,
-                                 x.mx.zx.opt = fs*zx*ages,x.mx.zx.org = fs.org*zx.org*ages,
-                                 cohort=years[y],age = ages,meta.tmp)
-
-          res.year[[y]] <- data.frame(mx.opt = unlist(fec.tmp[y,]),lx.opt = lx.year,
-                                 mx.lx.opt = unlist(fec.tmp[y,])*lx.year,
-                                 x.mx.lx.opt = unlist(fec.tmp[y,])*lx.year*ages,
-                                 zx.opt = zx.year,
-                                 mx.zx.opt = unlist(fec.tmp[y,])*lx.year,
-                                 x.mx.zx.opt = unlist(fec.tmp[y,])*lx.year*ages,
-                                 age = ages,year=years[y],meta.tmp)
-
-    } # end the years loop
-
-  # Do a years loop to get lambda with no fishing for each year, rather than by cohort...
-    for(yy in 1:(n.years-1))
-    {
-      nm <- as.numeric(tst$nm.opt[yy,])
-      z <- as.numeric(tst$z.opt[yy,])
-      fec <- as.numeric(tst$fecund.opt[yy,])
-      nm.init <- as.numeric(tst$nm.org[yy,])
-      fec.init <- as.numeric(tst$fecund.org[yy,])
-      z.init <- as.numeric(tst$z.org[yy,])
-      lam.no.fish <- exp(simple.lotka.r(mort = nm,fecund = fec,ages=ages)$res$r)
-      lam.fish <- exp(simple.lotka.r(mort = z,fecund = fec,ages=ages)$res$r)
-      lam.org.no.fish <- exp(simple.lotka.r(mort = nm.init,fecund = fec.init,ages=ages)$res$r)
-      lam.org.fish <- exp(simple.lotka.r(mort =  z.init,fecund = fec.init,ages=ages)$res$r)
-
-      # Now summarize these
-      res.lambda[[yy]] <-  data.frame(lam.no.fish = lam.no.fish,lam.fish = lam.fish,
-                                      lam.org.no.fish = lam.org.no.fish,
-                                      lam.org.fish = lam.org.fish,
-                                      year=years[yy],meta.tmp)
-    } # End the yy loop to get the lambdas...
-  # unpack it...
-  res.fin[[i]] <- do.call('rbind',res.cohort)
-  res.year.fin[[i]] <- do.call('rbind',res.year)
-  res.lambda.fin[[i]] <-  do.call('rbind',res.lambda)
-  }  # end if to make sure we have enough data to get the cohort estimates.
-
-  }# end the stock loop
-
-  res.cohort.final <- do.call('rbind',res.fin)
-  res.year.final <- do.call('rbind',res.year.fin)
-  res.lambda.final <- do.call('rbind',res.lambda.fin)
-
-  pop.dam <- res.cohort.final |> collapse::fgroup_by(cohort,Stock) |> collapse::fsummarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
-                                                                                   gen.len.org = sum(x.mx.lx.org)/sum(mx.lx.org),
-                                                                                   R0.opt = sum(mx.lx.opt),R0.org = sum(mx.lx.org))
-  pop.dam <- left_join(pop.dam,meta.sub,by="Stock")
-
-  dub.time.summary <- data.frame(dub.time.summary)
-  pop.dam <- data.frame(pop.dam)
-  # saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",what.2.tune,".Rds"))
-  # saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",what.2.tune,".Rds"))
-  # saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",what.2.tune,".Rds"))
-  save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
-       file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
-
-  write.csv(meta.sub, paste0(loc,"/Data/metadata_no_age_corection.csv"))
-} # end if load results
-```
-
-```{r clean-up-and-stats,include=F,echo=F,message=F,warning=F}
-load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
-for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-
-Stocks <- unique(res.lambda.final$Stock)
-res.lambda.fin <- data.frame(res.lambda.final)
-six.species <- c('morhua','harengus','aeglefinus','virens','solea','platessa')
-pop.dam.6 <- pop.dam |> collapse::fsubset(Species %in% six.species)
-for.tunes.6 <- for.tunes |> collapse::fsubset(Species %in% six.species)
-dub.time.6 <- dub.time.summary |> collapse::fsubset(Species %in% six.species)
-res.lambda.fin$decade <- floor(res.lambda.fin$year/10)*10
-res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock,decade) |> collapse::fmutate(mn.lam = mean(lam.fish,na.rm=T),
-                                                                                 med.lam = median(lam.fish,na.rm=T),
-                                                                                 sd.lam = sd(lam.fish,na.rm=T))
-res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Species,decade) |> collapse::fmutate(lm.spec.mn = mean(mn.lam,na.rm=T))              
-res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock) |> 
-                                                          collapse::fmutate(
-                                                          lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
-                                                          lam.fish.mn = mean(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T),
-                                                          lam.no.fish.med = median(lam.no.fish,na.rm=T),
-                                                          lam.fish.med = median(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.med = median(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T),
-                                                          lam.no.fish.sd = sd(lam.no.fish,na.rm=T),
-                                                          lam.fish.sd = sd(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.sd = sd(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.sd = sd(lam.org.fish,na.rm=T)
-                                                          ) |> data.frame()
-# Get the order right for the stock no species for the boxplots to come later
-sns.order <- c("Baltic Sea ", "Baltic Sea 22-24", "Baltic Sea 25-32", "Baltic Sea 28", 
-               "North Sea ", "North Sea 4", "North Sea 22-24", "North Sea 4-7 20", "North Sea 6a","North Sea 4 20", "North Sea 7d",     
-               "Celtic Sea ","Celtic Sea RA", "Celtic Sea 7a", "Celtic Sea 27.6a", 
-               "Irish Sea ","Irish Sea 7a", "Irish Sea 7e","Bay of Biscay ", "NE Arctic ", 
-               "Faroes 5a", "Faroes 5b",  "Iceland ", "Iceland 5a",
-                "NAFO 2-4 Fa-SGSL", "NAFO 2-4 Sp-SGSL", "NAFO 2-4 SGSL", "NAFO 2-4 NGSL", "NAFO 2-4 NFLD",  
-                "NAFO 5-6 ", "NAFO 5-6 GB", "NAFO 5-6 GOM", "NAFO 5-6 EGB",
-                "Bering Sea & AI ", "Gulf of Alaska ", "Aleutian Islands ")
-
-res.lambda.fin$Stock.no.species <- factor(res.lambda.fin$Stock.no.species,levels = sns.order,ordered = T)
-res.lambda.final.6 <- res.lambda.fin |> collapse::fsubset(Species %in% six.species)
-# Sort the data into a nice order...
-res.lambda.fin <- res.lambda.fin |> collapse::roworder(Species,Area.broad) |>
-                                    collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-# Making the Aleutian Islands their own Area long...
-res.lambda.fin$Area.long[res.lambda.fin$Area == "AI"] <- "Aleutian Islands"
-res.lambda.fin$Area.long <- factor(res.lambda.fin$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
-                                                                       "Irish Sea","Bay of Biscay","NE Arctic",
-                                                                       "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-
-res.lambda.final.6 <- res.lambda.final.6 |> collapse::roworder(Species,Area.broad) |>
-                                            collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-dub.time <- dub.time |> collapse::roworder(LME) |>
-                        collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-dub.time.summary <- dub.time.summary |> collapse::roworder(LME,Order,Species,Area.broad) |>
-                                        collapse::fmutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-dub.time.6 <- dub.time.6 |> collapse::roworder(LME) |>
-                             collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-pop.dam <- pop.dam |> collapse::roworder(Species,LME) |>
-                       collapse::fmutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
-pop.dam.6 <- pop.dam.6 |> collapse::roworder(LME,Area.broad) |>
-                       collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-pop.dam$Area.long[pop.dam$Area == "AI"] <- "Aleutian Islands"
-pop.dam$Area.long <- factor(pop.dam$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
-                                                         "Irish Sea","Bay of Biscay","NE Arctic",
-                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-# I'd also like a pop.dam including fishing
-pop.dam.fish <- res.cohort.final |> collapse::fgroup_by(cohort,Stock) |> collapse::fsummarise(gen.len.opt = sum(x.mx.zx.opt)/sum(mx.zx.opt),
-                                                                                   gen.len.org = sum(x.mx.zx.org)/sum(mx.zx.org),
-                                                                                   R0.opt = sum(mx.zx.opt),R0.org = sum(mx.zx.org))
-pop.dam.fish <- left_join(pop.dam.fish,meta.sub,by="Stock")
-pop.dam.fish$Area.long[pop.dam.fish$Area == "AI"] <- "Aleutian Islands"
-pop.dam.fish$Area.long <- factor(pop.dam.fish$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
-                                                         "Irish Sea","Bay of Biscay","NE Arctic",
-                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-pop.dam <- data.frame(pop.dam)
-
-pop.dam.fish <- pop.dam.fish |> collapse::roworder(Species,LME) |>
-                                collapse::fmutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
-pop.dam.fish.6 <- pop.dam.fish |> collapse::fsubset(Species %in% six.species)
-
-pop.dam.fish.6 <- pop.dam.fish.6 |> collapse::roworder(LME,Area.broad) |>
-                                    collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-# Put the population dynamics stuff together.
-pop.dam$group <- "no fish"
-pop.dam.fish$group <- 'fish'
-pop.dam.all <- rbind(pop.dam,pop.dam.fish)
-
-pop.dam.6$Stock.no.species <- factor(pop.dam.6$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam$Stock.no.species <- factor(pop.dam$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam.fish.6$Stock.no.species <- factor(pop.dam.fish.6$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam.fish$Stock.no.species <- factor(pop.dam.fish$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam.all$Stock.no.species <- factor(pop.dam.all$Stock.no.species,levels = sns.order,ordered = T)
-# Drop the periods....
-pop.dam.all.6 <- pop.dam.all |> collapse::fsubset(!Species %in% six.species)
-pop.dam.all$G.Species <- gsub("\\.","",pop.dam.all$G.Species)
-pop.dam.all$G.Species.short <- substr(pop.dam.all$G.Species,1,5)
-pop.dam.all$G.Species <- gsub("\\.","",pop.dam.all$G.Species)
-pop.dam.all.6 <- pop.dam.all |> collapse::fsubset(Species %in% six.species)
-pop.dam.all.others <- pop.dam.all |> collapse::fsubset(!Species %in% six.species)
-
-# Reorder the doubling time, either by Species and LME, or the other way around
-
-dub.time.summary$Order.short <- "Gadi"
-dub.time.summary$Order.short[dub.time.summary$Order == "Pleuronectiformes"] <- "Plero"
-dub.time.summary$Order.short[dub.time.summary$Order == "Clupeiformes"] <- "Clupei"
-dub.time.summary$Order.short[dub.time.summary$Order == "Scorpaeniformes "] <- "Scor"
-dub.time.summary$Order.short[dub.time.summary$Order == "Scombriformes"] <- "Scomb"
-dub.time.summary$Order.short[dub.time.summary$Order == "Perciformes"] <- "Perci"
-# First need to get the abundance and lambdas with no fishing into one object.
-ft.tmp <- for.tunes |> collapse::fselect(year,Stock,vpa.abund,est.abund,removals)
-dd.dat <- left_join(res.lambda.fin,ft.tmp,by=c('year','Stock'))
-# Now I need to get a relative abundance for each stock...
-dd.dat <- dd.dat |> collapse::fgroup_by(Stock) |> collapse::fmutate(max.abund = max(est.abund,na.rm=T))
-dd.dat <- data.frame(dd.dat)
-dd.dat$prop.abund <- dd.dat$est.abund/dd.dat$max.abund
-# Drop nas....
-drops <- -which(is.na(dd.dat$prop.abund))
-dd.dat <- dd.dat[drops,]
-#lump the data into bins
-dd.dat$prop.bin <- "< 10%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.1 & dd.dat$prop.abund <= 0.2] <- "10-20%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.2 & dd.dat$prop.abund <= 0.3] <- "20-30%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.3 & dd.dat$prop.abund <= 0.4] <- "30-40%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.4 & dd.dat$prop.abund <= 0.6] <- "40-60%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.6 & dd.dat$prop.abund <= 0.8] <- "60-80%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.8 & dd.dat$prop.abund <= 1] <- "80-100%"
-dd.dat$prop.bin <- factor(dd.dat$prop.bin,levels=c("< 10%","10-20%","20-30%","30-40%","40-60%","60-80%","80-100%"))
-
-# Subset to the big six
-dd.dat.six <- dd.dat  |>collapse::fsubset(Species %in% six.species)
-
-# This is for the new lambda figures with fishing and no fishing together
-
-res.lambda.fin.long <- res.lambda.fin |> tidyr::pivot_longer(cols = c(lam.no.fish,lam.fish),names_to = 'group',values_to = 'lambda')
-res.lambda.fin.long$Stock.no.species <- factor(res.lambda.fin.long$Stock.no.species,levels = sns.order,ordered = T)
-res.lambda.fin.long$group <- substr(res.lambda.fin.long$group,5,20)
-res.lambda.fin.long$group <- gsub("\\."," ",res.lambda.fin.long$group)
-res.lambda.fin.long.others <- res.lambda.fin.long |> collapse::fsubset(!Species %in% six.species)
-res.lambda.fin.long.others$G.Species <- gsub("\\.","",res.lambda.fin.long.others$G.Species)
-res.lambda.fin.long.others$G.Species.short <- substr(res.lambda.fin.long.others$G.Species,1,5)
-res.lambda.fin.long.6 <- res.lambda.fin.long |> collapse::fsubset(Species %in% six.species)
-res.lambda.fin.long.6$G.Species <- gsub("\\.","",res.lambda.fin.long.6$G.Species)
-
-# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE
-# here is the GAM for no fishing with subsequent processing.
-mod.dd.stock.gam.nf <- gam(log(lam.no.fish) ~   s(prop.abund,k=4) + s(prop.abund,as.factor(Stock.short),bs='fs',k=3) ,data=dd.dat)
-
-# This extracts the GAM fit so we can custom plot it on our own figure
-tmp <- plot(mod.dd.stock.gam.nf, pages = 0)
-no.stock.gam.nf.dat <- data.frame(fit = tmp[[1]]$fit + coefficients(mod.dd.stock.gam.nf)[1],prop.abund = tmp[[1]]$x,se = tmp[[1]]$se,Scenario = "F = 0")
-no.stock.gam.nf.dat$LCI <- no.stock.gam.nf.dat$fit - 1.96*no.stock.gam.nf.dat$se
-no.stock.gam.nf.dat$UCI <- no.stock.gam.nf.dat$fit + 1.96*no.stock.gam.nf.dat$se
-
-#summary(mod.dd.stock.gam.nf)
-#Residuals, definitely still issues here, maybe a bit better than some others, maybe...
-#plot(residuals(mod.dd.stock.gam.nf) ~ fitted(mod.dd.stock.gam.nf))
-# Normality = no
-#qqnorm(residuals(mod.dd.stock.gam.nf))
-#qqline(residuals(mod.dd.stock.gam.nf))
-
-pred.dd.stock.gam.nf <- expand.grid(prop.abund = seq(0, 1, length.out = 250),
-                                         Stock.short=c(unique(dd.dat$Stock.short)))
-tmp <- predict(mod.dd.stock.gam.nf, pred.dd.stock.gam.nf, type = 'response', se.fit = TRUE) 
-# Another fun trick to extract the overall smooth fit, but didn't end up using this method.
-# sms <- smooths(mod.dd.stock.gam.nf)
-# excl <- grepl("as.factor",sms)
-# rm <- sms[excl]
-# tmp.ex <- predict(mod.dd.stock.gam.nf, newdata =pred.dd.stock.gam.nf, type = 'response', se.fit = TRUE,exclude =rm) 
-# Get the fit by stock
-pred.dd.stock.gam.nf$lam.no.fish   <- exp(tmp$fit)
-pred.dd.stock.gam.nf$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-pred.dd.stock.gam.nf$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-
-# Thin the data so I can add points to the figure
-tmp <- NULL
-for(i in 1:(77)) 
-{
-  if(i==1) tmp[[i]] <- seq(10,230,length.out=5)
-  if(i>1) tmp[[i]] <- seq(10,230,length.out=5)+250*(i-1)
-}
-thinner.nf <- do.call('c',tmp)
-thin.pred.nf <- pred.dd.stock.gam.nf[thinner.nf,]
-# Now I want to get rid of extrapolation from this prediction data.frame, I think I need to loop it...
-# 
-short.stocks <- unique(dd.dat$Stock.short)
-n.stocks <- length(short.stocks)
-pred.out <- NULL
-thin.out <- NULL
-for(i in short.stocks)
-{
-  # Get the right stocks
-  tmpy <- dd.dat |> collapse::fsubset(Stock.short == i)
-  tmp.pred <- pred.dd.stock.gam.nf |> collapse::fsubset(Stock.short == i)
-  tmp.thin <- thin.pred.nf |> collapse::fsubset(Stock.short == i)
-  # I dont want to predict below the minimum observed abundance
-  mins <- min(tmpy$prop.abund,na.rm=T)
-  pred.out[[i]] <- tmp.pred |> collapse::fsubset(prop.abund >= mins)
-  thin.out[[i]] <- tmp.thin |> collapse::fsubset(prop.abund >= mins)
-}
-
-pred.dd.stock.gam.ss.nf <- do.call('rbind',pred.out)
-thin.pred.nf <- do.call('rbind',thin.out)
-# Combine pred stuff with the meta data for fun plots
-pred.dd.stock.gam.ss.nf <- left_join(pred.dd.stock.gam.ss.nf,meta.sub,by="Stock.short")
-pred.dd.stock.gam.ss.nf <- data.frame(pred.dd.stock.gam.ss.nf)
-thin.pred.nf <- left_join(thin.pred.nf,meta.sub,by="Stock.short")
-# Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# By region
-cols.gam <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
-pty.gam <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
-
-# Now do the same thing with the data that includes the effect of fishing.
-
-#mod.dd.stock.gam.fish <- gam(log(lam.fish) ~  as.factor(Stock.short) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.dat)
-mod.dd.stock.gam.fish <- gam(log(lam.fish) ~  s(prop.abund,k=4) + s(prop.abund,as.factor(Stock.short),bs='fs',k=3),data=dd.dat)
-
-tmp <- plot(mod.dd.stock.gam.fish, pages = 0)
-no.stock.gam.fish.dat <- data.frame(fit = tmp[[1]]$fit + coefficients(mod.dd.stock.gam.fish)[1],prop.abund = tmp[[1]]$x,se = tmp[[1]]$se,Scenario = "F > 0")
-no.stock.gam.fish.dat$LCI <- no.stock.gam.fish.dat$fit - 1.96*no.stock.gam.fish.dat$se
-no.stock.gam.fish.dat$UCI <- no.stock.gam.fish.dat$fit + 1.96*no.stock.gam.fish.dat$se
-
-#summary(mod.dd.stock.gam.fish)
-#Residuals, definetly still issues here, maybe a bit better than some others, maybe...
-#plot(residuals(mod.dd.stock.gam.fish) ~ fitted(mod.dd.stock.gam.fish))
-# Normality = no
-#qqnorm(residuals(mod.dd.stock.gam.fish))
-#qqline(residuals(mod.dd.stock.gam.fish))
-
-pred.dd.stock.gam.fish <- expand.grid(prop.abund = seq(0, 1, length.out = 250),
-                                         Stock.short=c(unique(dd.dat$Stock.short)))
-tmp <- predict(mod.dd.stock.gam.fish, pred.dd.stock.gam.fish, type = 'response', se.fit = TRUE) 
-pred.dd.stock.gam.fish$lam.fish   <- exp(tmp$fit)
-pred.dd.stock.gam.fish$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-pred.dd.stock.gam.fish$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-
-# Thin the data so I can add points to the figure
-tmp <- NULL
-for(i in 1:(77)) 
-{
-  if(i==1) tmp[[i]] <- seq(10,230,length.out=5)
-  if(i>1) tmp[[i]] <- seq(10,230,length.out=5)+250*(i-1)
-}
-thinner.fish <- do.call('c',tmp)
-thin.pred.fish <- pred.dd.stock.gam.fish[thinner.fish,]
-# Now I want to get rid of extrapolation from this prediction data.frame, I think I need to loop it...
-# 
-short.stocks <- unique(dd.dat$Stock.short)
-pred.out <- NULL
-thin.out <- NULL
-for(i in short.stocks)
-{
-  # Get the right stocks
-  tmpy <- dd.dat |> collapse::fsubset(Stock.short == i)
-  tmp.pred <- pred.dd.stock.gam.fish |> collapse::fsubset(Stock.short == i)
-  tmp.thin <- thin.pred.fish |> collapse::fsubset(Stock.short == i)
-  # I dont want to predict below the minimum observed abundance
-  mins <- min(tmpy$prop.abund,na.rm=T)
-  pred.out[[i]] <- tmp.pred |> collapse::fsubset(prop.abund >= mins)
-  thin.out[[i]] <- tmp.thin |> collapse::fsubset(prop.abund >= mins)
-}
-
-pred.dd.stock.gam.ss.fish <- do.call('rbind',pred.out)
-thin.pred.fish <- do.call('rbind',thin.out)
-# Combine pred stuff with the meta data for fun plots
-pred.dd.stock.gam.ss.fish <- left_join(pred.dd.stock.gam.ss.fish,meta.sub,by="Stock.short")
-pred.dd.stock.gam.ss.fish <- data.frame(pred.dd.stock.gam.ss.fish)
-
-thin.pred.fish <- left_join(thin.pred.fish,meta.sub,by="Stock.short")
-
-# Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# By region
-
-# What proportion of the stocks had the lowest 'GAM' estimate happen when the stock was at it's maximum size.
-low.gam <- data.frame(low.pa.fish = NA,diff.low.pa.fish = NA,low.pa.nf = NA,diff.low.pa.nf = NA,Stock = NA,Species = NA)
-count <- 0
-for(i in short.stocks) 
-{
-  count = count +1
-  tmp <- pred.dd.stock.gam.ss.fish |> collapse::fsubset(Stock.short == i)
-  tmp.nf <- pred.dd.stock.gam.ss.nf |> collapse::fsubset(Stock.short == i)
-  low.pa <- data.frame(low.pa.fish = tmp$prop.abund[tmp$lam.fish == min(tmp$lam.fish)],
-                       diff.low.pa.fish = tmp$lam.fish[tmp$lam.fish == min(tmp$lam.fish)] - tmp$lam.fish[tmp$prop.abund == max(tmp$prop.abund)],
-                       low.pa.nf = tmp.nf$prop.abund[tmp.nf$lam.no.fish == min(tmp.nf$lam.no.fish)],
-                       diff.low.pa.nf = tmp.nf$lam.no.fish[tmp.nf$lam.no.fish == min(tmp.nf$lam.no.fish)] - tmp.nf$lam.no.fish[tmp.nf$prop.abund == max(tmp.nf$prop.abund)],
-                       Stock = i,Species = tmp$G.Species[1])
-  low.gam[count,] <- low.pa
-}
-
-# Let's compare lambda at minimum, 0.4, and maximum and make a Table
-comp.lam.diff <- NULL
-comp.lam <- NULL
-comp.all.nf <- NULL
-comp.all.fish <- NULL
-for(i in short.stocks) 
-{
-  tmp <- pred.dd.stock.gam.ss.fish |> collapse::fsubset(Stock.short == i)
-  which.40 <- max(which(tmp$prop.abund <=0.4)) # Some stocks might not have a which 40.
-  which.max <- which(tmp$prop.abund ==1)
-  which.min <- which(tmp$prop.abund == min(tmp$prop.abund))
-  tmp.sub <- tmp[c(which.min,which.40,which.max),]
-  comp.all.fish[[i]] <- tmp.sub
-  tmp.nf <- pred.dd.stock.gam.ss.nf |> collapse::fsubset(Stock.short == i)
-  # I think I'm overkilling as this should be the same was the above witches....
-  which.40.nf <- max(which(tmp.nf$prop.abund <=0.4))
-  which.max.nf <- which(tmp.nf$prop.abund ==1)
-  which.min.nf <- which(tmp.nf$prop.abund ==min(tmp.nf$prop.abund))
-  tmp.nf.sub <- tmp.nf[c(which.min.nf,which.40.nf,which.max.nf),]
-  comp.all.nf[[i]] <- tmp.nf.sub
-  # Now we just want some summaries here I think...
-  comp.lam.diff[[i]] <- data.frame(min.abund = min(tmp.sub$prop.abund,na.rm=T),
-                              lam.fish.min.40 = tmp$lam.fish[which.min] - tmp$lam.fish[which.40],
-                              lam.fish.min.max = tmp$lam.fish[which.min] - tmp$lam.fish[which.max],
-                              lam.fish.40.max = tmp$lam.fish[which.40] - tmp$lam.fish[which.max],
-                              lam.nf.min.40 = tmp.nf$lam.no.fish[which.min.nf] - tmp.nf$lam.no.fish[which.40.nf],
-                              lam.nf.min.max = tmp.nf$lam.no.fish[which.min.nf] - tmp.nf$lam.no.fish[which.max.nf],
-                              lam.nf.40.max = tmp.nf$lam.no.fish[which.40.nf] - tmp.nf$lam.no.fish[which.max.nf],
-                              Stock = i,Species = tmp$G.Species[1])
-
-    comp.lam[[i]] <- data.frame(min.abund = min(tmp.sub$prop.abund,na.rm=T),
-                                lam.fish.min = tmp$lam.fish[which.min] ,
-                                lam.fish.40 = tmp$lam.fish[which.40],
-                                lam.fish.max = tmp$lam.fish[which.max],
-                                lam.nf.min = tmp.nf$lam.no.fish[which.min.nf],
-                                lam.nf.40 = tmp.nf$lam.no.fish[which.40.nf],
-                                lam.nf.max = tmp.nf$lam.no.fish[which.max.nf],
-                                Stock = i,Species = tmp$G.Species[1])
-}
-
-# A table for the estimates at 'interesting' values
-comp.lam.res <- do.call('rbind',comp.lam)
-# I want to turn this into a table....
-comp.lam.res.tab <- comp.lam.res
-# Round the numbers
-comp.lam.res.tab$min.abund <- round(comp.lam.res.tab$min.abund,digits=2)
-rounders <- c("lam.fish.min","lam.fish.40","lam.fish.max",
-              "lam.nf.min","lam.nf.40","lam.nf.max")
-comp.lam.res.tab[,rounders]      <- round(comp.lam.res.tab[,rounders] ,digits=3)
-# Now give it pretty names
-tab.names <- c("Minimum Abundance",
-               "$\\lambda_{F>0}^{Min}$",
-               "$\\lambda_{F>0}^{40}$",
-               "$\\lambda_{F>0}^{Max}$",
-               "$\\lambda_{F=0}^{Min}$",
-               "$\\lambda_{F=0}^{40}$",
-               "$\\lambda_{F=0}^{Max}$",
-               "Stock","Species")
-names(comp.lam.res.tab) <- tab.names
-
-# Now do the same with the differences
-comp.lam.diff.res <- do.call('rbind',comp.lam.diff)
-# I want to turn this into a table....
-comp.lam.diff.res.tab <- comp.lam.diff.res
-# Round the numbers
-comp.lam.diff.res.tab$min.abund <- round(comp.lam.diff.res.tab$min.abund,digits=2)
-rounders <- c("lam.fish.min.40","lam.fish.min.max","lam.fish.40.max",
-                    "lam.nf.min.40","lam.nf.min.max","lam.nf.40.max")
-comp.lam.diff.res.tab[,rounders] <- round(comp.lam.diff.res.tab[,rounders] ,digits=3)
-# Now give it pretty names
-tab.names <- c("Minimum Abundance",
-               "$\\lambda_{F>0}^{Min-40}$",
-               "$\\lambda_{F>0}^{Min-Max}$",
-               "$\\lambda_{F>0}^{40-Max}$",
-               "$\\lambda_{F=0}^{Min-40}$",
-               "$\\lambda_{F=0}^{Min-Max}$",
-               "$\\lambda_{F=0}^{40-Max}$",
-               "Stock","Species")
-names(comp.lam.diff.res.tab) <- tab.names
-
-# Used for the figure showing the number of stocks that have recovered by year x.
-n.dub <- data.frame(years = 1:n.sim.years, count = NA)
-for(i in 1:n.sim.years) n.dub$count[i] <- dub.time.summary |> collapse::fsubset(year==i & prop >= 0.75) |> nrow()
-
-# Compare the population recovery with the variance, using 2010 because all stocks have a value at 2010... 
-# I'm using the overall lambda sd, so the year doesn't actually matter other than to make sure all stocks are included here
-# This is used for the recovery variance figure, is this data good?
-# How many of the stocks had doubled by year 20, with 75% being my standard, which is a high standard
-dub.p.high <- 0.75
-dub.p.low <- 0.5
-n.dub.10 <- dub.time.summary |> collapse::fsubset(year==10 & prop >= dub.p.high) |> nrow()
-n.dub.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop >= dub.p.high) |> nrow()
-# Slow stocks, here we define having a low recovery potential has having < 50% of the simulatoins experience a doubling in size.
-slow.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop < dub.p.low) 
-prop.rec.20 <- dub.time.summary |> collapse::fsubset(year==20) # the proportion that recovers by year 20
-lambda.sds <- res.lambda.fin |> collapse::fsubset(year == 2010)
-lam.sd.p.rec <- left_join(prop.rec.20,lambda.sds,by=names(prop.rec.20)[c(1,4:24)]) 
-lam.sd.p.rec$prop.cat <- "Moderate"
-lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop < dub.p.low] <- "Low"
-lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop >= dub.p.high] <- "High"
-lam.sd.p.rec$prop.cat <- factor(lam.sd.p.rec$prop.cat,levels=c("Low","Moderate","High"))
-
-```
-
-```{r paper-calcs,include=F,echo=F,message=F,warning=F}
-
-# the lambda calcs
-med.lambda.F0 <- round(median(res.lambda.fin$lam.no.fish),digits=3)
-med.r.F0 <- round(median(log(res.lambda.fin$lam.no.fish)),digits=3)*100
-med.lambda.F <- round(median(res.lambda.fin$lam.fish),digits=3)
-med.r.F <- round(median(log(res.lambda.fin$lam.fish)),digits=3)*100
-mn.lambda.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
-mn.r.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
-# Mean - median...
-res.lambda.fin$med.mn.diff.no.fish <- res.lambda.fin$lam.no.fish.med - res.lambda.fin$lam.no.fish.mn
-res.lambda.fin$med.mn.diff.fish <- res.lambda.fin$lam.fish.med - res.lambda.fin$lam.fish.mn
-# How many stocks had the mean higher than the median
-n.mn.higher.med.no.fish <- length(unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.no.fish < 0]))
-n.mn.higher.med.fish <- length(unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.fish < 0]))
-low.mn.lambda.stocks <- unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.fish > 0])
-n.nw.ice <- length(c(grep("NAFO",low.mn.lambda.stocks),grep("Faroe",low.mn.lambda.stocks)))
-n.cod.low.mn <- length(grep("morhua",low.mn.lambda.stocks))
-n.cod <- length(grep("morhua",Stocks))
-
-# Density dependence related numbers
-n.bl.40 <- length(which(!is.na(comp.lam.res$lam.fish.40)))
-n.low.40.nf <- length(which(comp.lam.res$lam.nf.40 < 1))
-n.low.40.fish <-length(which(comp.lam.res$lam.fish.40 < 1))
-low.lam.40.nf <- -round(min(comp.lam.diff.res$lam.nf.40,na.rm=T),digits=3)
-low.4.lam.40.nf <- -round(sort(comp.lam.diff.res$lam.nf.40)[4],digits=3)
-
-# If right isn't this interesting!!! And look, 3 cod stocks from around here all say around 0.4 is the worst.  Most interesting...
-n.low.lam.at.max.fish <- length(which(low.gam$low.pa.fish == 1))
-n.low.lam.at.max.nf <- length(which(low.gam$low.pa.nf == 1))
-low.lam.cods <- low.gam[low.gam$low.pa.nf < 1 & low.gam$Species == "G. morhua",]
-n.cod.lam.not.at.max.nf <- nrow(low.lam.cods)
-pa.low.cod.min <- round(min(low.lam.cods$low.pa.nf),digits=2)
-pa.low.cod.max <- round(max(low.lam.cods$low.pa.nf),digits=2)
-
-# more density dependence numbers
-pa.lam.nf.at.one <- 100*round(no.stock.gam.nf.dat$prop.abund[min(which(no.stock.gam.nf.dat$fit <0))],digits=2)
-pa.lam.fish.at.one <- 100*round(no.stock.gam.fish.dat$prop.abund[min(which(no.stock.gam.fish.dat$fit <0))],digits=2)
-# What is the minimum abundance at which we get a 2 with the fishing lambdas.
-pa.big.threshold <- 0.65
-pa.low.threshold <- 0.8
-lam.low.threshold <- 0.8
-pa.lam.fish.low.bigs <- max(dd.dat$lam.fish[dd.dat$prop.abund >= pa.big.threshold])
-pa.lam.nf.low.bigs <- round(rev(sort(dd.dat$lam.no.fish[dd.dat$prop.abund >= pa.big.threshold]))[2],digits =2)
-# What proportion of the stocks had large declines overall, and then the proportion when the population was below 30%
-dd.dat.high <- dd.dat |> collapse::fsubset(prop.abund >= 0.3)
-prop.low.high.abund <- round(length(which(dd.dat.high$lam.fish < lam.low.threshold)) / nrow(dd.dat.high),digits=3)
-prop.low.all <- round(length(which(dd.dat$lam.fish < lam.low.threshold)) / nrow(dd.dat),digits=3)
-dd.dat.low <- dd.dat |> collapse::fsubset(prop.abund < 0.3)
-prop.low.low.abund <- round(length(which(dd.dat.low$lam.fish < lam.low.threshold)) / nrow(dd.dat.low),digits=3)
-
-# Numbers for the paper, lifetime reproductive growth
-r0.mn <- round(mean(pop.dam$R0.opt,na.rm=T),digits=1)
-r0.med <- round(median(pop.dam$R0.opt,na.rm=T),digits=1)
-# And fishing...
-r0.mn.fish <- round(mean(pop.dam.fish$R0.opt,na.rm=T),digits=1)
-r0.med.fish <- round(median(pop.dam.fish$R0.opt,na.rm=T),digits=1)
-
-# Where are the slow ones from
-n.not.dub.20 <- nrow(slow.20)
-n.alaska <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short== "AFSC"]))
-n.nwa <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("DFO-TRAC","NEFSC")]))
-n.nea <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("ICES")]))
-n.nafo.24 <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Area.broad %in% "NAFO 2-4"]))
-# Now the don't recover ones...
-n.alaska.slow <- length(slow.20$Stock.short[slow.20$Manage.short== "AFSC"])
-n.nwa.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% c("DFO-TRAC","NEFSC")])
-n.nea.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% "ICES"])
-
-# Need to grab all the per.diff's, which I seem to have dropped
-for.diffs <- do.call('rbind',for.tune.summary)
-med.per.diff <- round(median(for.diffs$per.diff,na.rm=T),digits=1)
-# what is lambda difference, about 6%, but that means the original was 7% higher, so that means we are reducing lambda when optimizing
-# If there was 'missing fishing' we are compensating for with this, this is exactly what we'd expect to happen right?
-res.lambda.fin$lam.per.diff <- 100*((res.lambda.fin$lam.org.no.fish - res.lambda.fin$lam.no.fish)/ res.lambda.fin$lam.no.fish)
-med.lam.per.diff <- round(median(res.lambda.fin$lam.per.diff,na.rm=T),digits=1)
-# By stock, can see most are positive, which is in line with missing fishing mortality...
-mod.by.stock.lam.pd <- res.lambda.fin |> collapse::fgroup_by(Stock.short) |> collapse::fsummarise(med = median(lam.per.diff,na.rm=T),
-                                                                                                  mn = mean(lam.per.diff,na.rm=T))
-
-```
-
-```{r main-figs,include=F,echo=F,message=F,warning=F}
-
-# New lambda plot with the fishing and no fishing beside each other
-# This is likely Figure 1
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Stock.no.species),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(G.Species),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 19,base_height = 15)
-
-# The other stocks, perhaps we put this in a supplement...
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(y=lambda,interaction(group,G.Species.short),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(Area.long),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 19,base_height = 15)
-
-# Standard deviation figure
-colrs.sd <- rep(c(rep('blue',4),rep('orange',4),rep('grey',4),rep('black',4)),20)
-pty.sd <- rep(rep(c(21,4,9,8),4),20)
-
-lam.sd.plt <- ggplot(res.lambda.fin ) + 
-                                       geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
-                                       scale_y_log10("Standard deviation (Lambda)",log_breaks(n=8)) +
-                                       scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
-                                       theme(axis.text.x = element_text(angle =45,hjust=1),
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 10)
-
-# Overall density dependence
-# MAIN PAPER FIGURE#
-dd.nf.overall.plt <-ggplot(no.stock.gam.nf.dat , aes(x=prop.abund,y=exp(fit))) + 
-                                geom_point(data = dd.dat,aes(x=prop.abund,y=lam.no.fish),size=2,alpha=0.1) +  
-                                geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI)),alpha=0.5,linewidth=0,fill=u.colors[1])+
-                                geom_line(color=u.colors[1],linewidth=1) + 
-                                xlab("") + 
-                                scale_y_log10(name = "Lambda(F=0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_blank()) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-# MAIN PAPER FIGURE#
-dd.fish.overall.plt <- ggplot(no.stock.gam.fish.dat, aes(x=prop.abund,y=exp(fit))) + 
-                                geom_point(data = dd.dat,aes(x=prop.abund,y=lam.fish),size=2,alpha=0.1) +  
-                                geom_line(color=u.colors[2],linewidth=2) + 
-                                geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI)),alpha=0.5,fill=u.colors[2])+
-                                xlab("") + 
-                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed',linewidth=1.5)+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_blank()) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-# Main Paper Figure Density dependence with and without fishing, effectively a zoomed in version of the above.
-colrs <- u.colors
-t.smooth <- rbind(no.stock.gam.fish.dat,no.stock.gam.nf.dat)
-dd.fish.nf.plt <- ggplot(t.smooth, aes(x=prop.abund,y=exp(fit),group=Scenario,color=Scenario,fill=Scenario)) + 
-                                 geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI),group=Scenario,fill=Scenario),alpha=0.50,linewidth=0)+
-                                 geom_line(linewidth=1.5) +
-                                 geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                 scale_fill_manual(values = colrs) + scale_color_manual(values = colrs) +
-                                 scale_x_continuous(name = "Proportion of maximum abundance",breaks = seq(0,1,by=0.1)) + 
-                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-                                 theme(legend.position = c(0.9,0.75))
-
-dd.overall.combo <- plot_grid(dd.nf.overall.plt,dd.fish.overall.plt,dd.fish.nf.plt,nrow=3)
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_overall_",what.2.tune,".png"),dd.overall.combo,base_width = 10,base_height = 10)
-
-new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(y=lambda,interaction(group,G.Species.short),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(Area.long),design=mat,scales='free_x')
-
-# Density dependence by stock 
-cols.gam <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
-pty.gam <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
-# Doing this manually because the ordered factor wasn't working... annoying...
-mat <- matrix(c(2, 2,13,13, 5, 5, 9, 9,
-                3, 3,12,12, 6, 6, 8, 8,
-               NA,NA,10,10,11,11,NA,NA,
-               NA,7, 7, 4, 4, 1, 1, NA),
-                4, 8, byrow = TRUE)
-
-dd.stocks.nf.plt <- ggplot(pred.dd.stock.gam.ss.nf,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=G.Species,shape=G.Species)) + 
-                                geom_line() + 
-                                geom_point(data = thin.pred.nf,size=2) +  
-                                xlab("Proportion of maximum abundance") + 
-                                scale_y_log10(name = "Lambda (F=0)",breaks = log_breaks(n=10)) +
-                                geom_ribbon(aes(ymin=lower,ymax=upper,color=G.Species),alpha=0.10,linewidth=0)+
-                                facet_manual(vars(Area.long),design=mat,scales='free_x')+
-                                #facet_wrap(~Area.long)  +
-                                scale_shape_manual(values=pty.gam) +
-                                scale_color_manual(values = cols.gam) + 
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_text(size=7)) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"),dd.stocks.nf.plt,base_width = 10,base_height = 10)
-
-mat <- matrix(c(2, 2,13,13, 5, 5, 9, 9,
-                3, 3,12,12, 6, 6, 8, 8,
-               NA,NA,10,10,11,11,NA,NA,
-               NA,7, 7, 4, 4, 1, 1, NA),
-                4, 8, byrow = TRUE)
-
-# MAIN PAPER FIGURE#
-dd.stocks.fish.plt <- ggplot(pred.dd.stock.gam.ss.fish,aes(x=prop.abund,y=lam.fish,group=Stock.short,color=G.Species,shape=G.Species)) + 
-                                geom_line() + 
-                                geom_point(data = thin.pred.fish,size=2) +  
-                                geom_ribbon(aes(ymin=lower,ymax=upper,color=G.Species),alpha=0.10,linewidth=0)+
-                                xlab("Proportion of maximum abundance") + 
-                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10)) +
-                                facet_manual(vars(Area.long),design=mat,scales='free_x')+
-                                #facet_wrap(~Area.long)  +
-                                scale_shape_manual(values=pty.gam) +
-                                scale_color_manual(values = cols.gam) + 
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_text(size=7)) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_fish_stocks_",what.2.tune,".png"),dd.stocks.fish.plt,base_width = 10,base_height = 10)
-
-# Lifetime reproductive success 
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-r0.boxplt.6 <- ggplot(pop.dam.all.6) + geom_boxplot(aes(y=R0.opt,interaction(group,Stock.no.species),color=group))  + 
-                                       scale_x_discrete(NULL, guide = "axis_nested") + scale_y_log10(name = "Lifetime Reproductive Output")+
-                                       geom_hline(yintercept = 1,linetype='dashed',color='blue')+
-                                       facet_manual(vars(G.Species),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"),r0.boxplt.6,base_width = 19,base_height = 15)
-
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-r0.boxplot.others <- ggplot(pop.dam.all.others) +   geom_boxplot(aes(y=R0.opt,interaction(group,G.Species.short),color=group))  + 
-                                                    scale_x_discrete(NULL, guide = "axis_nested") + 
-                                                    scale_y_log10(name = "Lifetime Reproductive Output")+
-                                                    geom_hline(yintercept = 1,linetype='dashed',color='blue')+
-                                                    facet_manual(vars(Area.long),design=mat,scales='free')+
-                                                    theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                          plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"),r0.boxplot.others,base_width = 15,base_height = 10)
-
-r0.heatmap.ne <- ggplot(pop.dam |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-r0.heatmap.nw <- ggplot(pop.dam |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-r0.heatmap.pac <- ggplot(pop.dam |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                     xlab("") + ylab("")+
-                                     facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                     geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                     theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                           legend.key.width = unit(3,'cm'))
-
-r0.heatmap <- cowplot::plot_grid(r0.heatmap.pac,r0.heatmap.nw,r0.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_nf_",what.2.tune,".png"),r0.heatmap,base_width = 20,base_height = 17)
-
-r0.heatmap.ne.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-r0.heatmap.nw.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-r0.heatmap.pac.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                     xlab("") + ylab("")+
-                                     facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                     geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                     theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                           legend.key.width = unit(3,'cm'))
-
-r0.heatmap.fish <- cowplot::plot_grid(r0.heatmap.pac.fish,r0.heatmap.nw.fish,r0.heatmap.ne.fish,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_fish_",what.2.tune,".png"),r0.heatmap.fish,base_width = 20,base_height = 17)
-
-# Generation length
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-gen.boxplt.6 <- ggplot(pop.dam.all.6) +
-                            geom_boxplot(aes(y=gen.len.opt,interaction(group,Stock.no.species),color=group))  + 
-                            scale_x_discrete(NULL, guide = "axis_nested") +
-                            scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
-                             facet_manual(vars(G.Species),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"),gen.boxplt.6,base_width = 19,base_height = 15)
-
-# Then the generation length for others.
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-gen.boxplt.others <- ggplot(pop.dam.all.others) +
-                            geom_boxplot(aes(y=gen.len.opt,interaction(group,G.Species.short),color=group))  + 
-                            scale_x_discrete(NULL, guide = "axis_nested") +
-                            scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
-                            facet_manual(vars(Area.long),design=mat,scales='free')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"),gen.boxplt.others,base_width = 15,base_height = 10)
-
-gen.heatmap.ne <- ggplot(pop.dam |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
-                                              xlab("") + ylab("")+  
-                                              facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                              geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-gen.heatmap.nw <- ggplot(pop.dam |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-gen.heatmap.pac <- ggplot(pop.dam |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
-                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-gen.heatmap <- cowplot::plot_grid(gen.heatmap.pac,gen.heatmap.nw,gen.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_nf_",what.2.tune,".png"),gen.heatmap,base_width = 15,base_height = 10)
-
-gen.heatmap.ne.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
-                                              xlab("") + ylab("")+  
-                                              facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                              geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-gen.heatmap.nw.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-gen.heatmap.pac.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
-                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-gen.heatmap.fish <- cowplot::plot_grid(gen.heatmap.pac.fish,gen.heatmap.nw.fish,gen.heatmap.ne.fish,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_fish_",what.2.tune,".png"),gen.heatmap.fish,base_width = 15,base_height = 10)
-
-dub.time.summary <- dub.time.summary |> collapse::fsubset(year %in% 1:50) |>
-                            collapse::roworder(G.Species,LME,Area.broad) |>
-                            collapse::fmutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-dub.heatmap.gad <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Gadiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+                                    
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.45, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.pl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Pleuronectiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+                                    
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"))
-
-dub.heatmap.cl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Clupeiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.35, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.per <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Perciformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.scom <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Scombriformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2.1, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.scorp <- ggplot(dub.time.summary |> collapse::fsubset(Order %in% "Scorpaeniformes "), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + 
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.5, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap <- cowplot::plot_grid(dub.heatmap.gad,dub.heatmap.pl,dub.heatmap.cl,dub.heatmap.per,dub.heatmap.scom,dub.heatmap.scorp,
-                                  nrow = 6,rel_heights = c(39,20,11,4,3,3))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"),dub.heatmap,base_width = 20,base_height = 20)
-
-# Doubling Time Figure 1
-dub.ts.plt <- ggplot(n.dub,aes(x=years,y=count)) + 
-                    geom_line() + 
-                    geom_hline(yintercept = length(Stocks),linetype="dashed") + 
-                    xlab("") + ylab("Number of Stocks")
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_time_series_",what.2.tune,".png"),dub.ts.plt,base_width = 10,base_height = 10)
-
-# Doubling time and variability
-
-# Is there a relationship between median and sd?
-colrs.cat <- c("blue","black","orange")
-pts.cat <- 21:23
-sd.rec.plt <- ggplot(lam.sd.p.rec, aes(y=lam.no.fish.med,x=lam.no.fish.sd,color=prop.cat,group=prop.cat)) + 
-                       geom_point(size =3,aes(shape=prop.cat,fill=prop.cat)) + 
-                       geom_hline(yintercept=1,linetype="dashed") + 
-                       scale_y_continuous(name="median Lambda") + scale_x_continuous(name="standard deviation Lambda") +
-                       scale_color_manual(values=colrs.cat) + scale_fill_manual(values=colrs.cat) +  
-                       scale_shape_manual(values=pts.cat) + theme(legend.title = element_blank())
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"),sd.rec.plt,base_width = 10,base_height = 10)
-
-```
-
-```{r the-others,include=F,echo=F,message=F,warning=F}
-#             
-# 
-# dub.heatmap.cod <- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "G.
-morhua"), aes(x=year, y=Stock.no.species, fill= prop)) + xlab("") + ylab("")+                                     facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") +
-#                             geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + scale_x_continuous(labels=NULL) +
-#                             theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-#                                   legend.key.width = unit(3,'cm'))
-# 
-# dub.heatmap.herring<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "C. harengus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-# 
-# dub.heatmap.haddock<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "M. aeglefinus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.125, "cm"))
-# 
-# dub.heatmap.virens<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. virens"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.4, "cm"))
-# 
-# dub.heatmap.solea<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "S. solea"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-# 
-# dub.heatmap.platessa<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. platessa"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous() +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
-# 
-# 
-# 
-# dub.heatmap.sp6 <- cowplot::plot_grid(dub.heatmap.cod,dub.heatmap.herring,dub.heatmap.haddock,
-#                                  dub.heatmap.virens, dub.heatmap.solea,dub.heatmap.platessa,nrow = 6,rel_heights = c(14,9,8,5,5,4))
-# dub.heatmap.sp6
-# 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_sp6_",what.2.tune,".png"),dub.heatmap.sp6,base_width = 20,base_height = 17)
-# 
-# 
-# # What about a plot of the sd of lamda by stock
-# #colrs.sd <- rep(rep(c("black","blue","orange",'grey'),3),20)
-# #pty.sd <- rep(c(rep(21,4),rep(4,4),rep(9,4)),20)
-# 
-# 
-# # Same plot for the not 6 species
-# 
-# # lam.sd.other.plt <- ggplot(res.lambda.fin |> collapse::fsubset(!Species %in% six.species)) + 
-# #                                        geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
-# #                                        scale_y_log10("sd(lambda)",limits=c(0.05,1.5)) +
-# #                                        scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
-# #                                        theme(axis.text.x = element_text(angle =45,hjust=1),
-# #                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# # lam.sd.other.plt
-# 
-# 
-# 
-# 
-# # Doubling Times
-# 
-# 
-# # Generation length
-# 
-# # Main text figure!!
-# new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Area.long),color=group)) +
-#                                            #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-#                                            scale_x_discrete(NULL, guide = "axis_nested") +
-#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~G.Species,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# # The other stocks, plotting these by area
-# # Main Text FIGURE!
-# # More data
-# 
-# 
-# ################### Supplemental Figures################### Supplemental Figures################### Supplemental Figures################### Supplemental 
-# 
-# 
-# 
-# # Time series of lambdas....
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# #col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
-# pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
-# #pty <- rep(rep(c(21:23),5),20)
-# 
-# lambda.ts.plt <- ggplot(res.lambda.final.6,aes(y=lam.fish,x=year,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
-#                             geom_point(size=4) +
-#                             geom_smooth(method='gam',formula = y ~ s(x, bs = "cs", fx = TRUE, k = 5),se=F) + 
-#                             #scale_y_log10(name = "lambda") +
-#                             facet_wrap(~G.Species,scales='free_y') +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-#                             scale_fill_manual(name = "Stock",values = col.try)+
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm'))
-# #lambda.ts.plt
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_timeseries_6_",what.2.tune,".png"),lambda.ts.plt,base_width = 12,base_height = 10)
-# 
-# 
-# lambda.dec.plt <- ggplot(res.lambda.final.6,aes(y=med.lam,x=as.factor(decade))) +
-#                             geom_boxplot() + scale_y_log10()+
-#                             xlab("Decade") + ylab("Lambda") + 
-#                             geom_point(aes(x=as.factor(decade),y=lm.spec.mn),color='blue',shape=8,fill='blue')+
-#                             #scale_x_continuous(breaks=seq(1940,2020,by=10))+
-#                             geom_hline(yintercept = 1,linetype='dashed') +
-#                             facet_wrap(~G.Species,scales='free_y') 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_by_decade_6_",what.2.tune,".png"),lambda.dec.plt,base_width = 12,base_height = 12)
-# 
-#
-
-# ggplot(dd.dat) + geom_point(aes(x=prop.abund,y=lam.no.fish-1)) + xlab("Proportion of Maximum Abundance") + ylab("r (no fishing)")
-# 
-# # Density dependence by Species
-# ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
-#                                                    geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) #+
-#                                                    #scale_color_manual(values = colrs)
-# # Density dependence by stock
-# ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Stock.short,group=Stock.short)) + geom_point() + 
-#                                                    geom_smooth(method="lm",se = F) + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)", limits=c(0.4,2),
-#                                                                  breaks = seq(0.4,2,by=0.1)) +
-#                                                    theme(legend.position = 'none')
-# 
-# 
-# 
-# 
-# ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish)) + geom_point() + 
-#                                                     geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_continuous(name = "lambda (no fishing)")
-# 
-# ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + geom_point() + 
-#                                                     geom_smooth(method="lm",se=F) + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,2,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)")
-# 
-# 
-# # how about our big 6
-# colrs <- c("blue","black","firebrick2","orange",'grey50','grey90')
-# ggplot(dd.dat.six,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
-#                                                     geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) +
-#                                                    scale_color_manual(values = colrs)
-# 
-# 
-# ggplot(dd.dat.six.no.bigs,aes(x=prop.abund,y=lam.no.fish-1,color=Species,group=Species)) + geom_point() + 
-#                                                     geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 0,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_continuous(name = "r (no fishing)", breaks = seq(-1,1,by=0.2)) +
-#                                                    scale_color_manual(values = colrs)
-
-# Other things I did just randomly scattered here
-
-# 
-# #hmm <- merge(tst,res.lambda.final.6,by="Stock")
-# plot(res.lambda.fin$lam.fish.med ~ res.lambda.fin$lam.fish.mn)
-# # So this is lambda with fishing included
-# lambda.plt <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.no.fish,x=Stock.no.species))  + 
-#                                            geom_point(aes(y=lam.no.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~G.Species,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_no_fishing_6_",what.2.tune,".png"),lambda.plt,base_width = 12,base_height = 10)
-# 
-# # With fishing
-# lambda.plt.fish <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.fish,x=Stock.no.species))  + 
-#                                            geom_point(aes(y=lam.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~G.Species,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_with_fishing_6_",what.2.tune,".png"),lambda.plt.fish,base_width = 12,base_height = 10)
-# 
-# 
-# 
-# new.lam.plt <- ggplot(res.lambda.fin.long) + geom_boxplot(aes(y=lambda,interaction(group,Order),color=group)) +
-#                                            #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-#                                            scale_x_discrete(NULL, guide = "axis_nested") +
-#                                            #xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            #geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~Area.long,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# 
-# # The final option I have is to do what I did before and use the bin props
-# We can then do a much more ANOVA kinda analysis, drat this doesn't converge..., estimate the 
-#mod.dd.bins.stock <- glmer(lam.no.fish ~ prop.bin + (1+prop.bin|Stock),data=dd.dat,family=gaussian(link='log'))
-# so go to lmer and log transform... and it is a singular fit
-#mod.dd.bins.stock <- lmer(lam.no.fish ~ prop.bin + (1+prop.bin|Stock),data=dd.dat)
-# So is an intercept model of any real use?
-# mod.dd.bins.stock <- lmer(log(lam.no.fish) ~ prop.bin + (1+prop.bin|Stock.short),data=dd.dat)
-# # A non-random effect model does work with the interaction... I'd much rather lmer....
-# #mod.dd.bins.stock <- lm(lam.no.fish ~ prop.bin*Stock,data=dd.dat)
-# summary(mod.dd.bins.stock)
-# #Residuals, nah, still suck, just some crazy outliers...
-# plot(mod.dd.bins.stock)
-# # Normality = terrible...
-# qqnorm(residuals(mod.dd.bins.stock))
-# qqline(residuals(mod.dd.bins.stock))
-# # So we can predict this ANOVA thing...
-# pred.dd.stock.bins <- expand.grid(prop.bin = unique(dd.dat$prop.bin),
-#                                          #Species=unique(dd.dat$Species),
-#                                          Stock.short=unique(dd.dat$Stock.short))
-# tmp <- predict(mod.dd.bins.stock, pred.dd.stock.bins, type = 'response', se.fit = TRUE) 
-# pred.dd.stock.bins$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.stock.bins$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.stock.bins$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Now to do fun things I need the meta data on the pred dataframe
-# pred.dd.stock.bins <- left_join(pred.dd.stock.bins,meta.sub,by="Stock.short")
-# # Now a problem here is that this includes estimates for bins in which we don't have data.
-# # So we do want to get rid of those
-# real.bins <- unique(paste(dd.dat$Stock.short,"_",dd.dat$prop.bin))
-# # All the bins in the predict object with same names same name...
-# pred.dd.stock.bins$bin.combos <- paste(pred.dd.stock.bins$Stock.short,"_",pred.dd.stock.bins$prop.bin)
-# # Now toss all the predicted bins without data.
-# pred.dd.stock.bins <- pred.dd.stock.bins |> collapse::fsubset(bin.combos %in% real.bins)
-# 
-# # By region
-# cols.1 <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
-# #col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
-# pty.1 <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
-# ggplot(pred.dd.stock.bins,aes(x=prop.bin,y=lam.no.fish,group=Stock.short,color=G.Species)) + 
-#                                 geom_point(aes(shape=G.Species),size=2) + geom_line()  + xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 facet_wrap(~Area.long)  +
-#                                 scale_shape_manual(values=pty.1) +
-#                                 scale_color_manual(values = cols.1) + 
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-# 
-# # By Species
-# ggplot(pred.dd.stock.bins,aes(x=prop.bin,y=lam.no.fish,group=Stock.short,color=Area.long)) + 
-#                                 geom_point(aes(shape=Area.long)) + geom_line()  + xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 facet_wrap(~Order)  +
-#                                 scale_shape_manual(values=pty.1) +
-#                                 scale_color_manual(values = cols.1) + 
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-# 
-# # No fish vs fish lambda, note that DD is weaker when we account for fishing, that seems a fun result to talk about!
-# 
-# mod.dd.overall.gam.nf <- lm(log(lam.no.fish) ~ (prop.abund),data=dd.dat)
-# mod.dd.overall.gam.fish <- lm(log(lam.fish) ~ (prop.abund),data=dd.dat)
-# 
-# 
-# pred.dd.overall.bins.nf <- data.frame(prop.abund = seq(0,1,length.out=500),group = "F = 0")
-# pred.dd.overall.bins.fish <- data.frame(prop.abund = seq(0,1,length.out=500),group = "F > 0")
-# tmp <- predict(mod.dd.overall.gam.nf, pred.dd.overall.bins, type = 'response', se.fit = TRUE) 
-# tmp.fish <- predict(mod.dd.overall.gam.fish, pred.dd.overall.bins, type = 'response', se.fit = TRUE) 
-# pred.dd.overall.bins.nf$lam   <- exp(tmp$fit)
-# pred.dd.overall.bins.nf$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.overall.bins.nf$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# 
-# pred.dd.overall.bins.fish$lam   <- exp(tmp.fish$fit)
-# pred.dd.overall.bins.fish$lower <- exp(tmp.fish$fit - 1.96 * tmp.fish$se.fit)
-# pred.dd.overall.bins.fish$upper <- exp(tmp.fish$fit + 1.96 * tmp.fish$se.fit)
-# 
-# pred.dd.overall <- rbind(pred.dd.overall.bins.fish,pred.dd.overall.bins.nf)
-# 
-# ggplot(pred.dd.overall,aes(y=lam,x=prop.abund,group=group,color=group)) + 
-#                                                   geom_line(linewidth=2) + 
-#                                                   geom_ribbon(aes(ymin=lower,ymax=upper),alpha=0.2) + 
-#                                                   geom_hline(yintercept=1,linetype='dashed') + 
-#                                                   xlab("Proportion of Maximum Abundance") + ylab("Lambda")
-# 
-# # OK, so if we compare the 40-60 bin with the 80-100 bin we should see the lambda's in the 40-60 bin are higher...
-# 
-# res.40.60 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("40-60%"))
-# names(res.40.60)[names(res.40.60) == 'lam.no.fish'] <- "lam.40.60"
-# res.80.100 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("80-100%"))
-# names(res.80.100)[names(res.80.100) == 'lam.no.fish'] <- "lam.80.100"
-# 
-# tst <- left_join(res.40.60,res.80.100, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.40.60 - tst$lam.80.100
-# 
-# hist(tst$diff)
-# 
-# res.lt.10 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("< 10%"))
-# names(res.lt.10)[names(res.lt.10) == 'lam.no.fish'] <- "lam.lt.10"
-# 
-# tst <- left_join(res.40.60,res.lt.10, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.lt.10 - tst$lam.40.60
-# 
-# hist(tst$diff)
-# 
-# res.10.20 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("10-20%"))
-# names(res.10.20)[names(res.10.20) == 'lam.no.fish'] <- "lam.10.20"
-# 
-# tst <- left_join(res.40.60,res.10.20, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.10.20 - tst$lam.40.60
-# 
-# hist(tst$diff)
-# 
-# 
-# res.20.30 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("20-30%"))
-# names(res.20.30)[names(res.20.30) == 'lam.no.fish'] <- "lam.20.30"
-# 
-# tst <- left_join(res.40.60,res.20.30, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.20.30 - tst$lam.40.60
-# 
-# hist(tst$diff)
-# 
-# res.30.40 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("30-40%"))
-# names(res.30.40)[names(res.30.40) == 'lam.no.fish'] <- "lam.30.40"
-# 
-# tst <- left_join(res.40.60,res.30.40, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.30.40 - tst$lam.40.60
-# 
-# hist(tst$diff)
-
-# 
-# 
-# dd.dat.no.bigs <- dd.dat |> collapse::fsubset(lam.no.fish < 2)
-# dd.dat.six.no.bigs <- dd.dat.six |> collapse::fsubset(lam.no.fish < 2)
-# just.bigs <- dd.dat  |> collapse::fsubset(lam.no.fish > 2) 
-# sum(table(just.bigs$Stock.short)) # 48 of 68 are Haddock or cod. 13 of remaining 20 are small low trophic species
-# 
-# dd.dat$lam.ratio <- dd.dat$lam.org.no.fish/dd.dat$lam.no.fish
-# dd.dat$lam.ratio.z <- dd.dat$lam.org.fish/dd.dat$lam.fish
-# So the original lambda tended to be somewhere between 7 and 14% higher, depending on me(di)an choice.
-# Could be way off in some years for a few species (Haddock, Cod, Sand lance, horse makerel, pilchard(sardine)... interesting... )
-# summary(dd.dat$lam.ratio)
-# summary(dd.dat$lam.ratio.z)
-# ggplot(dd.dat,aes(y=lam.ratio,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
-# ggplot(dd.dat,aes(y=lam.ratio.z,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
-
-# Playing around to look at explanations for what we see, looked by LME, low and high stocks, but no smoking guns!
-# low.stocks <- unique(dd.dat$Stock.short[dd.dat$prop.abund <= 0.1])
-# dd.lows <- dd.dat |> collapse::fsubset(Stock.short %in% low.stocks)
-# dd.highs <- dd.dat |> collapse::fsubset(!Stock.short %in% low.stocks)
-# mod.dd.stock.gam.lows <- gam(log(lam.no.fish) ~ s(prop.abund,k=4) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.lows )
-# mod.dd.stock.gam.highs <- gam(log(lam.no.fish) ~ s(prop.abund,k=4) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.highs )
-# 
-# pred.dd.stock.gam.tst <- expand.grid(prop.abund = seq(0, 1, length.out = 50),
-#                                          Stock.short = c("Overall",unique(dd.highs$Stock.short)))
-# 
-# tmp <- predict(mod.dd.stock.gam.highs, pred.dd.stock.gam.tst, type = 'response', se.fit = TRUE) 
-# pred.dd.stock.gam.tst$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.stock.gam.tst$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.stock.gam.tst$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# 
-# ggplot(pred.dd.stock.gam.tst |> collapse::fsubset(Stock.short=='Overall'), aes(x=prop.abund,y=lam.no.fish)) + 
-#                                 geom_point(data = hmm,aes(x=prop.abund,y=lam.no.fish),size=2,alpha=0.1) +  
-#                                 geom_line(color='blue',linewidth=2) + 
-#                                 xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-# 
-# 
-# ggplot(pred.dd.stock.gam.tst,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short,shape=Stock.short)) + 
-#                                 geom_line() + 
-#                                 #geom_point(data = thin.pred,size=2) +  
-#                                 xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 #facet_wrap(~Area.long)  +
-#                                 #scale_shape_manual(values=pty.gam) +
-#                                 #scale_color_manual(values = cols.gam) + 
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-
-# Is there any density dependence in fishing mortality??
-# dd.dat$mu <- dd.dat$removals/dd.dat$vpa.abund
-# dd.dat$fm <- -log(1-dd.dat$mu)
-# 
-# ggplot(dd.dat , aes(x=prop.abund,y=fm)) + 
-#                                 geom_point() + 
-#                                 geom_smooth(method = 'gam') + 
-#                                 scale_x_continuous(name="Proportion of Maximum Abundance") +
-#                                 scale_y__continuous(name = "Fishing Mortality (instantaneous)")
-# 
-# 
-# qqnorm(log(dd.dat$mu))
-# qqline(log(dd.dat$mu))
-# hist(log(dd.dat$mu))
-# 
-# fm.mod <- lm(log(fm)~prop.abund,data=dd.dat)
-# par(mfrow=c(2,2))
-# plot(fm.mod)
-# par(mfrow=c(1,1))
-
-# windows(11,11)
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
-
-# 
-# r0.ts.plt <- ggplot(pop.dam.6,aes(y=R0.opt,x=cohort,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) + 
-#                             geom_line(size=2)  + geom_point(size=4) +
-#                             scale_y_log10(name = "Lifetime Reproductive Output") +
-#                             facet_wrap(~G.Species) +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-#                             scale_fill_manual(name = "Stock",values = col.try)+
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
-# r0.ts.plt
-# 
-# save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_6.png",r0.ts.plt,base_width = 30,base_height = 12)
-# 
-# r0.boxplt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
-#                             facet_wrap(~G.Species,scales = 'free')+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none')
-# r0.boxplt
-
-# 
-# windows(11,11)
-# ggplot(pop.dam) + geom_boxplot(aes(y=gen.len.opt,x=Species)) + facet_wrap(~LME,scales='free_x') +
-#                   ylab("Generation Length (years)") + theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# windows(11,11)
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# lty <- rep(c(rep(1,5),rep(2,5),rep(4,5)),20)
-# 
-# gen.ts.plt <- ggplot(pop.dam.6,aes(y=gen.len.opt,x=cohort,group=Stock.short,color=Stock.short,linetype = Stock.short)) + 
-#                             geom_line(size=2)  + 
-#                             scale_y_log10(name = "Generation Length") +
-#                             facet_wrap(~G.Species) +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_linetype_manual(name = "Stock",values = lty) +
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
-# gen.ts.plt
-# save_plot("D:/Github/ICM/Figures/tuned/Gen_time_series_6.png",gen.ts.plt,base_width = 20,base_height = 12)
-
-# 
-# ggplot(for.tunes) + geom_jitter(aes(y=lambda,x=Species,group=Stock.short,color=Stock.short)) + 
-#                     scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10)) +
-#                             theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# ggplot(for.tunes) + geom_jitter(aes(y=lambda.vpa.init,x=Species)) + scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))
-# 
-# unique(for.tunes$Species)
-# windows(11,11)
-# 
-# ggplot(for.tunes) + geom_density(aes(lambda,group=Species,color=Species,fill=Species),alpha = 0.2) + scale_x_continuous(breaks = c(0,0.5,1,2,5,10))
-# 
-# 
-# #options(scipen=999)
-# r0.plt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.05,0.1,0.5,1,5,10,50,100),minor_breaks = NULL) + 
-#                             facet_wrap(~Species,scales = 'free')+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1))
-# save_plot("D:/Github/ICM/Figures/tuned/R0_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
-# 
-# 
-# 
-# vickis.cols <- sort(rep(c( "#172582",  "#F8DC91", "#FBB891", "#FB6A01", "#B80000"),3))
-# linetypes <- rep(c(1,2,4),5)
-# 
-# windows(11,11)
-# cod.r0.ts.plt <- ggplot(pop.dam |> collapse::fsubset(Species == 'morhua')) + geom_line(aes(y=R0.opt,x=cohort,group=Area,color=Area,linetype=Area),size=1.5)  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output", breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
-#                             scale_color_manual(values = vickis.cols) +
-#                             scale_linetype_manual(values = linetypes) +
-#                             theme(legend.key.width  = unit(2, "cm"))
-# cod.r0.ts.plt
-# #save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
-# 
-# 
-# windows(11,11)
-# ggplot(pop.dam |> collapse::fsubset(Species =="morhua")) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
-#                                                         scale_y_log10(name = "Lifetime Reproductive Output",breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) +
-#                                                         theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# # Missing catch questions
-# # first did we do much to the Fecundity term to get here
-# quantile(for.tunes$mean.fec/for.tunes$mean.vpa.fec,probs=seq(0.01,1,0.01),na.rm=T)
-# 
-# quantile((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init,probs=seq(0.01,1,0.01),na.rm=T)
-# quantile((for.tunes$mean.nm-for.tunes$mean.vpa.nm)/for.tunes$mean.vpa.nm,probs=seq(0.01,1,0.01),na.rm=T)
-# 
-# for.tunes$excess.catch <- for.tunes$removals-for.tunes$removals.init
-# for.tunes$per.excess.catch <- 100*((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init)
-# 
-# windows(11,11)
-# bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Species)) + 
-#                                    ylab("Adjustment to catch (%)") +
-#                                    theme(axis.text.x = element_text(angle=45,hjust = 1))
-#                                    
-# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_species.png",bycatch.plt,base_width = 8,base_height = 8)
-#                                    
-# bycatch.plt.cod <- ggplot(for.tunes |> collapse::fsubset(Species == 'morhua')) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + 
-#                                                                               ylab("Adjustment to catch (%)") +
-#                                                                               theme(axis.text.x = element_text(angle=45,hjust = 1))
-#                                                                               
-# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_cod_stock.png",bycatch.plt.cod,base_width = 8,base_height = 8)
-# 
-# # bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + facet_wrap(~Species,scales = 'free_x')
-# #                                    ylab("Adjustment to catch (%)") +
-# #                                    theme(axis.text.x = element_text(angle=45,hjust = 1))
-# # bycatch.plt                                   
-#
-
-# Doubling time for the rest of the stocks...
-
-# dub.heatmap.no.6 <- ggplot(dub.time.summary |> collapse::fsubset(!Species %in% six.species), aes(x=year, y=Stock.short, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               #facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + 
-#                               scale_x_continuous() +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
-```
-
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-
-```{r failed-models}
-
-# A density dependence model, start simple and build...
-# mod.dd.base <- lm(log(lam.no.fish) ~ prop.abund,data=dd.dat)
-# summary(mod.dd.base)
-# 
-# mod.dd.base.fish <- lm(log(lam.fish) ~ prop.abund,data=dd.dat)
-# summary(mod.dd.base.fish)
-# #ggplot(dd.dat, aes(y = lam.no.fish,x=prop.abund)) + geom_point() + geom_smooth(method = 'lm') + scale_y_log10() + geom_hline(yintercept = 1,color='firebrick2',linetype='dashed',linewidth=2)
-# 
-# 
-# # Residuals are nowhere near normal, the fit isn't a disaster but def have the old trumpet shape happening
-# par(mfrow=c(2,2))
-# plot(mod.dd.base)
-# par(mfrow=c(1,1))
-# # This mostly represents the above model...
-# ggplot(dd.dat, aes(y = lam.no.fish,x=prop.abund)) + 
-#                   geom_point() + 
-#                   geom_smooth(method = 'lm') + scale_y_log10() +
-#                   geom_hline(yintercept = 1,color='firebrick2',linetype='dashed',linewidth=2)
-# # What happens with a gam?
-# mod.dd.gam.base <- gam(log(lam.no.fish) ~ s(prop.abund),data=dd.dat)
-# summary(mod.dd.gam.base)
-# # Still see that the residuals are higher at low values
-# plot(residuals(mod.dd.gam.base) ~ dd.dat$prop.abund)
-# # not great...
-# plot(residuals(mod.dd.gam.base) ~ fitted(mod.dd.gam.base))
-# # What's the fit look like?
-# pred.dd.gam.base <- data.frame(prop.abund = seq(0, 1, length.out = 1000))
-# tmp <- predict(mod.dd.gam.base, dd.gam.base.pred, type = 'response', se.fit = TRUE) 
-# 
-# pred.dd.gam.base$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.gam.base$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.gam.base$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# 
-# # So here's the game fit, I thnk it does do an ok job of showing that no much is happening below maybe 0.3, but then
-# # below 0.15 it starts increasing, suggesting general compensation, but we know the really high values matter here and are
-# # limited to a subset of the stocks, anywho we know the residuals suck, so moving on...
-# ggplot(dd.dat,aes(y=lam.no.fish,x=prop.abund)) + 
-#                   geom_point() + scale_y_log10() +
-#                   geom_ribbon(data=pred.dd.gam.base,aes(ymin=lower,ymax=upper,x=prop.abund),alpha=0.4) +
-#                   geom_line(data = pred.dd.gam.base,aes(y=lam.no.fish, x= prop.abund))
-#     
-# 
-# # What if we did a glm, Gamma with log-link seems a natural thing to try...
-# mod.dd.glm.gamma <- glm(lam.no.fish ~ prop.abund,data=dd.dat,family = Gamma(link='log'))
-# # What's that done...
-# summary(mod.dd.glm.gamma)
-# # Still some pretty gross shit going on here...
-# par(mfrow=c(2,2))
-# plot(mod.dd.glm.gamma)
-# par(mfrow=c(1,1))
-# # Now plot it...
-# pred.dd.glm.base <- data.frame(prop.abund = seq(0, 1, length.out = 1000))
-# tmp <- predict(mod.dd.glm.gamma, dd.gam.base.pred, type = 'response', se.fit = TRUE) 
-# 
-# pred.dd.glm.base$lam.no.fish   <- (tmp$fit)
-# pred.dd.glm.base$lower <- (tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.glm.base$upper <- (tmp$fit + 1.96 * tmp$se.fit)
-# # Pretty similar, though I think on the linear scale we see the 'rate' may be decreasing as we approach 0
-# # But still not a good model given the above
-# ggplot(dd.dat,aes(y=lam.no.fish,x=prop.abund)) + 
-#                   geom_point() + scale_y_log10() +
-#                   geom_ribbon(data=pred.dd.glm.base,aes(ymin=lower,ymax=upper,x=prop.abund),alpha=0.4) +
-#                   geom_line(data = pred.dd.glm.base,aes(y=lam.no.fish, x= prop.abund))
-#     
-# # Now what if we account for species in these and get an estimate for each species. 
-# # I think this should be done as a random effect, we'll start with linear mixed models and see what happens...
-# 
-# mod.dd.species.re <- lmer(log(lam.no.fish) ~ prop.abund + (1| Species),data=dd.dat)
-# # So that seems reasonable...
-# summary(mod.dd.species.re)
-# #Residuals are still pretty cranky
-# plot(mod.dd.species.re)
-# # Normality still a hot mess
-# qqnorm(residuals(mod.dd.species.re))
-# qqline(residuals(mod.dd.species.re))
-# # draw some lines...
-# pred.dd.lmm.species <- expand.grid(prop.abund = seq(0, 1, length.out = 100),Species=unique(dd.dat$Species))
-# tmp <- predict(mod.dd.species.re, pred.dd.lmm.species, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.species$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.lmm.species$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.species$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.species,aes(x=prop.abund,y=lam.no.fish,group=Species,color=Species)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Species, color=Species)) +
-#                                 scale_y_log10()
-# 
-# # We could also allow the slope to vary by species, might get a bit better, but really won't do the trick...
-# mod.dd.species.slope.re <- lmer(log(lam.no.fish) ~ prop.abund + (1+ prop.abund| Species),data=dd.dat)
-# summary(mod.dd.species.slope.re)
-# #Residuals are still pretty cranky
-# plot(mod.dd.species.slope.re)
-# # Normality still a hot mess
-# qqnorm(residuals(mod.dd.species.slope.re))
-# qqline(residuals(mod.dd.species.slope.re))
-# # draw some lines...
-# pred.dd.lmm.species.slope <- expand.grid(prop.abund = seq(0, 1, length.out = 100),Species=unique(dd.dat$Species))
-# tmp <- predict(mod.dd.species.slope.re, pred.dd.lmm.species.slope, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.species.slope$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.lmm.species.slope$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.species.slope$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.species.slope,aes(x=prop.abund,y=lam.no.fish,group=Species,color=Species)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Species, color=Species)) +
-#                                 scale_y_log10()
-# # Curious what species have high slopes.. Dubious and Esmarkii (North Sea sand lance and mackerel)
-# ranef(mod.dd.species.slope.re)
-# 
-# # So so what if we let the slopes vary by stock
-# mod.dd.stock.re <- lmer(log(lam.no.fish) ~ prop.abund +  (1+ prop.abund | Stock.short),data=dd.dat)
-# summary(mod.dd.stock.re)
-# #Residuals are slightly better I think but still really suck
-# plot(mod.dd.stock.re)
-# # Normality = no
-# qqnorm(residuals(mod.dd.stock.re))
-# qqline(residuals(mod.dd.stock.re))
-# # What's it look like?
-# pred.dd.lmm.stock <- expand.grid(prop.abund = seq(0, 1, length.out = 100),
-#                                          #Species=unique(dd.dat$Species),
-#                                          Stock.short=unique(dd.dat$Stock.short))
-# tmp <- predict(mod.dd.stock.re, pred.dd.lmm.stock, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.stock$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.lmm.stock$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.stock$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.stock,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Stock.short, color=Stock.short)) +
-#                                 scale_y_log10()
-# 
-# # Curious what stocks have high slopes.. Dubious and Esmarkii (North Sea sand lance and mackerel), NS Haddock and Irish Sea Haddock 
-# ranef(mod.dd.stock.re)
-# 
-# 
-# 
-# 
-# # OK, so this all still sucks, wonder if a glmer and gamma would get us anywhere... not really.... 
-# # Tried many variants on the glmer and they all land in the same lousy spot.
-# mod.dd.stock.gamma.re <- glmer(lam.no.fish ~ prop.abund +  (1+ prop.abund | Stock.short),data=dd.dat,family=Gamma(link='log'))
-# # OK...
-# summary(mod.dd.stock.gamma.re)
-# #Residuals, nah, still suck, just some crazy outliers...
-# plot(mod.dd.stock.gamma.re)
-# # Normality = no
-# qqnorm(residuals(mod.dd.stock.gamma.re))
-# qqline(residuals(mod.dd.stock.gamma.re))
-# # And the plot...
-# pred.dd.lmm.stock.gamma <- expand.grid(prop.abund = seq(0, 1, length.out = 100),
-#                                          #Species=unique(dd.dat$Species),
-#                                          Stock.short=unique(dd.dat$Stock.short))
-# tmp <- predict(mod.dd.stock.gamma.re, pred.dd.lmm.stock.gamma, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.stock.gamma$lam.no.fish   <- (tmp$fit)
-# pred.dd.lmm.stock.gamma$lower <- (tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.stock.gamma$upper <- (tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.stock.gamma,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Stock.short, color=Stock.short)) +
-#                                 scale_y_log10()
-# # None of the above really work at all....
-
-```
+The recovery potential was influenced both by $\lambda_{F=0}$ and the variability in $\lambda_{F=0}$.
+Stocks with a median $\lambda_{F=0} < 1$  had moderate (defined as stocks in which 50-75% of the simulations doubled within 20 years) to high (> 75% doubled in size within 20 years) recovery potential whenever the standard deviation in lambda was greater than approximately 0.4 (Figure \@ref(fig:dub-vs-sd)).
+Stocks with a median $\lambda_{F=0}$ near 1 and with low variability were the stocks in which the recovery potential tended to be categorized as low (< 50% of the simulations doubled within 20 years).

### 2024-05-21 Drafts/Paper_1/tmp-07-tables.Rmd
mid-edit update

--- 2024-05-10 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
@@
 ---
-output: word_document
+output:
+  word_document: default
+  html_document: default
 editor_options:
@@
 ---
+\clearpage
+\newpage
 
-```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4,include=F,message=F}
+# Tables {-}
 
-if(load.results==F)
-{
-  Stocks <- ASR.long |> 
-                      collapse::fsubset(!is.na(value)) |>
-                      collapse::fgroup_by(Stock, type) |>
-                      collapse::fsummarize(count=length(unique(value))) |>
-                      collapse::fgroup_by(Stock) |>
-                      collapse::fsummarize(types=length(unique(type))) |>
-                      collapse::fsubset(types==5) |>
-                      collapse::fselect(Stock)
+```{r, process}
+# This will be the meta data really...
+# remove columns we don't need.
 
-  ASR.tmp <- ASR.long 
-  ASR.tmp$age <- as.numeric(ASR.tmp$age)
-  ASR.stocks <- ASR.tmp |> 
-                          collapse::fsubset(Stock %in% Stocks$Stock) |>
-                          collapse::fsubset(!is.na(value)) |>
-                          collapse::roworder(Stock, Year, type, age)
-
-  # print(Stocks)
-  Stocks <- Stocks$Stock
-
-  # Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
-  #Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
-  # Esmarki doesn't work great as it is assessed using a quarterly model.
-  #Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
-  #i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
-  years.tmp <- NULL
-  pnm.tmp <- NULL
-  waa.tmp <- NULL
-  ages.tmp <- NULL
-  rem.tmp <- NULL
-  mx.tmp <- NULL
-  NE.tmp <- NULL
-  vpa.tmp <- NULL
-  am.tmp <- NULL
-  #mr.tmp <- NULL
-  abund.tmp <- NULL
-  full.abund.tmp <- NULL
-  full.rem.tmp <- NULL
-  fs.tmp <- NULL
-  for(i in Stocks)
-  {
-  print(i)
-  ASR.sub <- ASR.long |>
-    collapse::fselect(Year, Stock, type, age, value) |>
-    collapse::fsubset(Stock==i)
-
-    # Dropping the first 7 years as the 8 year olds are all missing
-  if(i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR.sub <- ASR.sub |> collapse::fsubset(Year >= 1972)
-  # maxage <- max(as.numeric(ASR.sub$age[!is.na(ASR.sub$value)]))
-  # maxYear <- max(ASR.sub$Year[!is.na(ASR.sub$value)])
-  # minYear <- min(ASR.sub$Year[!is.na(ASR.sub$value)])
-  # forplot <- ASR.sub[as.numeric(ASR.sub$age) < (maxage+1) & ASR.sub$Year %in% minYear:maxYear,]
-  # 
-  # # summary plots
-  # print(ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
-  #         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
-  #         theme_bw() + 
-  #         ggtitle(i)
-  # )
-
-  age.mat <- ASR.sub |> collapse::fsubset(type=="AM") |> dplyr::rename(AM=value) |> collapse::fselect(-type)
-  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
-  # in case that changes later...
-  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
-  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
-  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
-  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
-  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
-  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0
-
-  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
-  nat.mort <-  ASR.sub |> collapse::fsubset(type=="NM") |> dplyr::rename(NM=value) |> collapse::fselect(-type)
-  abund <- ASR.sub |> collapse::fsubset(type=="Num") |> dplyr::rename(Num=value) |> collapse::fselect(-type)
-  weight.age <- ASR.sub |> collapse::fsubset(type=="WA") |> dplyr::rename(WA=value) |> collapse::fselect(-type)
-  if(i == Stocks[30]) weight.age$WA <- weight.age$WA/1000
-  removals <- ASR.sub |> collapse::fsubset(type=="Catch") |> dplyr::rename(Catch=value) |> collapse::fselect(-type)
-
-  data <- age.mat |>
-    full_join(nat.mort) |>
-    full_join(abund) |>
-    full_join(weight.age) |>
-    full_join(removals)
-
-  # Aahh??  Is this NA dropping useful data, needed to quick fix the age at maturity data...
-  data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
-  data <- data[data$available==T,]
-
-  # Tidy up the data for input...
-  data$prop.nat.mort <- 1-exp(-data$NM)
-  #prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))] <- 1-exp(-prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))])
-
-  rem <- data |> collapse::fgroup_by(Year) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
-  #rem <- data |> dplyr::group_by(Year,.drop=F) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
-
-  # Never run, so not doing anything.
-  # missing_rem<- NULL
-  # if(any(is.na(rem$rem))) 
-  # {
-  #   missing_rem <- unique(data$Year)[which(is.na(rem$rem))]
-  #   rem$rem[is.na(rem$rem)] <- median(rem$rem, na.rm=T)
-  # }
-
-  #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
-  years <- data |> dplyr::pull(Year) |> unique() |> sort()
-
-  N.end <- sum(data[data$Year==max(years),]$Num)
-  vpa.abund <- data |> dplyr::group_by(Year) |> dplyr::summarize(vpa=sum(Num,na.rm=T)) |> pull(vpa)
-
-  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
-  #minage
-  minage <- min(as.numeric(data$age))
-  #maxage
-  maxage <- max(as.numeric(data$age))
-  #recruits
-  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
-  #ssn
-  data$ssn <- data$Num * data$AM
-  #ssb
-  data$ssb <- data$ssn * data$WA #I need to figure out how to line this up with the number of recruits for the right years in the data object.... got it right for the overall r.p.ssb below.
-  #tot.ssb
-  annual <- data |> group_by(Year) |> summarize(tot.ssb = sum(ssb)) |> left_join(annual)
-
-  #tst <- data |> group_by(Year) |> summarize(tot.ssn = sum(ssn)) |> left_join(annual)
-
-  #r.p.ssb This needs to be offset by the age of recruits. So here's my lining this up logic.  For age 0, we get
-  # the recruit and SSB estimates from the same survey, thus these age 0 recruits will have been produced by the SSB in the previous year...
-  # So the R in 1970 were produced by SSB in 1969 when min age =0
-  # If min.age = 1 then R in 1970 is produced by SSB in 1968... and so on.
-  # FIX 1 "Recruit year" = SSB year + min.age + 1 (or min.age +2 as SSB.year is the first column)
-  # Now for RPS there's another wrinkle because of this, because our model is N(1970) = lambda * N(1969) and lambda is made up of lx and mx
-  # so if the recruits show up in 1970, the fecundity term that gets us there (irrespective of the age offset) has to be for 1969, becuase
-  # that gets us to the babies that show up in 1970
-  # FIX 2 So "RPS year, recs.per.age year, and mx year" = SSB year + min.age
-  # I believe this to be correct, but we all need to discuss this to make sure the logic holds.
-  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+2):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage-1)],NA)
-  # recs.per.age
-  data <- left_join(data, annual)
-  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
-  tmp <- NULL
-  for(j in 1:length(years))
-  {
-    tst <- data|> collapse::fsubset(Year == years[j]) |> collapse::fselect(ssb,ssn,Year,age)
-    tst$Year <- tst$Year + minage # We want this to line up the the RPS year, so just adding minage here.
-    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
-    tmp[[j]] <- tst
-  }
-  # Unpack the list
-  ssb.off <- do.call('rbind',tmp)
-  # And merge it with the data object
-  data <- left_join(data,ssb.off,by=c("Year","age"))
-  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
-  # mx
-  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
-  # No longer dividing by 2 because we should really divide recruits and ssn by 2 to be female only, but that's pointless so we roll along with this.
-  data$mx <- data$recs.per.age/data$ssn.offset # if(grepl("males",i)) 
-  #if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
-  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
-  # Easier to remove the years where we don't have recs.per.age...
-  #data <- data |> collapse::fsubset(Year %in% years[(minage+1):length(years)])
-
-  age.mat <- data |> collapse::fselect("Year", "age", "AM") |> 
-                     pivot_wider(names_from=age, values_from = AM) |> collapse::fselect(-Year)
-  prop.nat.mort <- data |> collapse::fselect("Year", "age", "prop.nat.mort") |> 
-                            pivot_wider(names_from=age, values_from = prop.nat.mort) |> 
-                            collapse::fselect(-Year) |> as.data.frame()
-
-  weight.age <- data |> collapse::fselect("Year", "age", "WA") |> pivot_wider(names_from=age, values_from = WA) |> collapse::fselect(-Year)
-  mx <- data |> collapse::fselect("Year", "age", "mx") |> 
-                 pivot_wider(names_from=age, values_from = mx) |> 
-                 collapse::fselect(-Year) |> as.data.frame()
-  # Get the abundance matrix
-  abund.age <- data |> collapse::fselect("Year", "age", "Num") |> 
-                        pivot_wider(names_from=age, values_from = Num) |> 
-                        collapse::fselect(-Year) |> as.data.frame()
-
-  # Now we can save out the catch and get an instantaneous F
-    data$Catch[is.na(data$Catch)] <- 0
-    data$Exp <- data$Catch/data$Num 
-    # If it is exactly 1 that leads to an Inf, which is annoying, so make it 1.1 and fix it with the rest below
-    data$Exp[data$Exp == 1] <- 1.1
-    # And make this an F
-    data$Fs <- -log(1-data$Exp)
-    if(any(is.na(data$Fs)))
-    {
-      fixers <- which(is.na(data$Fs))
-      print(paste0("Had to replace ",length(fixers), ' exploitation rates for stock ',i))
-      for(f in fixers)
-      {
-        yr <- data$Year[f]
-        fs <- max(data$Fs[data$Year == yr],na.rm=T)
-        data$Fs[f] <- fs
-        data$Exp[f] <- 1-exp(-fs)
-      }
-    }
-
-  full.rems <- data |> collapse::fselect("Year", "age", "Catch") |> pivot_wider(names_from=age, values_from = Catch) |> collapse::fselect(-Year)
-  full.Fs <-  data |> collapse::fselect("Year", "age", "Fs") |> pivot_wider(names_from=age, values_from = Fs) |> collapse::fselect(-Year)
-
-    if(i == "DFO_2J3KL_Gadus_morhua")
-    {
-      age.mat[,8:10] <- 1
-      prop.nat.mort[,8:10] <- prop.nat.mort[,7]
-      weight.age[12:14,9:10] <- weight.age[12:14,8]
-      weight.age[15,10] <- weight.age[15,9]
-      mx[12:16,9:10] <- mx[12:16,8]
-      mx[17,10] <- mx[17,9]
-      full.Fs[12:14,9:10] <- full.Fs[12:14,8]
-      full.Fs[15,10] <- full.Fs[15,9]
-      abund.age[12:14,9:10] <- abund.age[12:14,8]
-      abund.age[15,10] <- abund.age[15,9]
-      # I could calculate, but this will get us to the same place...
-      full.rems[12:14,9:10] <- full.rems[12:14,8]
-      full.rems[15,10] <- full.rems[15,9]
-    }
-
-    if(i == "DFO_4T-Spring_Clupea_harengus")
-    {
-      age.mat[6:7,10] <- 1
-      prop.nat.mort[6:7,10] <- prop.nat.mort[6:7,9]
-      weight.age[6:7,10] <- weight.age[6:7,9]
-      mx[6:9,10] <- mx[6:9,9]
-      full.Fs[6:7,10] <- full.Fs[6:7,9]
-      abund.age[6:7,10] <- abund.age[6:7,9]
-      full.rems[6:7,10] <- full.rems[6:7,9]
-    }
-
-    if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
-    {
-      age.mat[30,8] <- 1
-      prop.nat.mort[30,8] <- prop.nat.mort[30,7]
-      weight.age[30,8] <- weight.age[29,8]
-      mx[30:31,8] <- mx[30:31,9]
-      full.Fs[30,8] <- full.Fs[30,7]
-      abund.age[30,8] <- abund.age[30,7]
-      full.rems[30,8] <- full.rems[30,7]
-    }
-
-    if(i == "ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax")
-    {
-      age.mat[c(14,27,40),5] <- age.mat[1,5]
-      prop.nat.mort[c(14,27,40),5] <- prop.nat.mort[1,5]
-      weight.age[c(14,27,40),5] <- weight.age[c(13,26,39),5]
-      mx[c(14,16,27,29,40,42),5] <- mx[c(14,16,27,29,40,42),6]
-      full.Fs[c(14,27,40),5] <- full.Fs[c(14,27,40),4]
-      abund.age[c(14,27,40),5] <- abund.age[c(14,27,40),4]
-      full.rems[c(14,27,40),5] <- full.rems[c(14,27,40),4]
-    }
-    # Clear out some 0's...
-    if( i == "AFSC_EEBSAI_Limanda_aspera")
-    {
-      mx[5,18] <- mean(unlist(mx[5,c(17,19)]))
-      mx[c(6,8),19] <- mx[c(6,8),18]
-      mx[2:7,20] <- mx[2:7,19] 
-    }
-
-  # I had filled the years with no SSB data to inform them.  instead I'm going to remove those years...
-
-   if(minage >0) 
-  {
-    rm <- -(1:minage)
-    years <- years[rm]
-    prop.nat.mort <- prop.nat.mort[rm,]
-    weight.age <- weight.age[rm,]
-    rem <- rem[rm,]
-    mx <- mx[rm,]
-    vpa.abund <- vpa.abund[rm]
-    age.mat <- age.mat[rm,]
-    abund.age <- abund.age[rm,]
-    full.Fs <- full.Fs[rm,]
-    full.rems <- full.rems[rm,]
-   }
-  #   mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
-  #   names(mx) <- names(mx.fill)
-  #  # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
-  #   mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
-  # }
-
-    years.tmp[[i]] <- years
-    pnm.tmp[[i]] <- prop.nat.mort
-    waa.tmp[[i]] <- weight.age
-    ages.tmp[[i]] <- minage:maxage
-    rem.tmp[[i]] <- rem
-    mx.tmp[[i]] <- mx
-    NE.tmp[[i]] <- N.end
-    vpa.tmp[[i]] <- vpa.abund
-    am.tmp[[i]] <- age.mat
-    #mr.tmp[[i]] <- missing_rem
-    abund.tmp[[i]] <- abund.age
-    fs.tmp[[i]] <- full.Fs
-    full.rem.tmp[[i]] <- full.rems
-  } #end input data loop
-
-  save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,
-       am.tmp,Stocks,ASR.stocks,ASR.long,abund.tmp,fs.tmp,full.rem.tmp,
-       file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
-
-  } # end load results
-```
-
-  So now I can try to do some tuning, both forwards and backwards, lets see what we get from that...
-
-```{r tunes,include=F,echo=F,warning=F,message=F}
-
-  ########################## Now run the tuning sims
-  #
-
-  if(load.results==F)
-  {
-  load(file = paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
-
-  for.tune.all.res <- NULL
-  for.tune.summary <- NULL
-  for(i in Stocks)
-  {
-    years <- years.tmp[[i]]
-    prop.nat.mort <- pnm.tmp[[i]] 
-    #rem <- rem.tmp[[i]] 
-    mx <- mx.tmp[[i]] 
-    N.end <- NE.tmp[[i]] 
-    ages <- ages.tmp[[i]]
-    vpa.abund <- vpa.tmp[[i]] 
-    abund <- abund.tmp[[i]]
-    fs <-fs.tmp[[i]]
-    full.rem <- full.rem.tmp[[i]]
-    #full.abund <- full.abund.tmp[[i]]
-    #all.abund <- full.abund.tmp[[i]]
-    #N.end <- vpa.abund[length(vpa.abund)]
-    #Pick your step size
-    ss.size <- 0.005
-    sensistive.stocks <- c("AFSC_GOA_Theragra_chalcogramma",
-                            "DFO_2J3KL_Gadus_morhua",
-                            "DFO_3Pn-4RS_Gadus_morhua",
-                            "DFO_4T-4VN_Gadus_morhua",
-                            "DFO_4T_Scomber_scombrus",
-                            "ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus",
-                            "ICES-AFWG_NEA1-2_Gadus_morhua",
-                            "ICES-HAWG_NS_Ammodytes_dubius",
-                            "ICES-NWWG_FA5b_Pollachius_virens",
-                            "ICES-NWWG_FAPL5b1_Gadus_morhua",
-                            "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
-                            "ICES-WGCSE_IS7a_Gadus_morhua",
-                            "ICES-WGCSE_CS7a_Merlangius_merlangus",
-                            "ICES-WGCSE_CS7e-k_Gadus_morhua",
-                            "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
-                            "ICES-WGHANSA_SP8abd_Sardina _pilchardus", 
-                            "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua",
-                            "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",
-                            "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus",
-                            "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
-                            "NEFSC-GARMIII_SNE- MA_Limanda_ferruginea",
-                            "NEFSC-GARMIII_MA_Paralichthys_dentatus",
-                            "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus",
-                            "NEFSC_NWA_Scomber _scombrus")
-
-    if(i %in% sensistive.stocks) ss.size = ss.size/10
-
-     N.start <- vpa.abund[1]
-     print(i)
-     # The fecundities are 
-     fast.for.tune <- fast.tunes(years,
-                             tuner=what.2.tune,
-                             step.size = ss.size, 
-                             abund.ts = vpa.abund,
-                             ages=ages,
-                             nm = -(log(1-prop.nat.mort)),
-                             fecund = mx,
-                             fm = fs,
-                             abund.age = abund, 
-                             catch.age = full.rem, 
-                             N.init = N.start,
-                             direction= 'forwards'
-                             )
-
-     for.tune.all.res[[i]] <- fast.for.tune
-     for.tune.tmp <- data.frame(fast.for.tune$res,Stock = i)
-     for.tune.summary[[i]] <- for.tune.tmp
-  }
-
-  saveRDS(for.tune.summary,paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-  saveRDS(for.tune.all.res,paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
-  # 
-}# end if load results
+rm.meta <- which(names(meta.sub) %in% c("Meeting_or_reference","G.short","G.Species","Manage.short","LME","Area.broad","Area.long","Area.narrow","Stock.short","Stock","Model","Case","Notes","Area"))
+meta.4.tab <- meta.sub[,-rm.meta]
+re.ord <- c(8,2:7,1)
+meta.4.tab <- meta.4.tab[,re.ord]
+names(meta.4.tab) <- c("Stock", "Order", "Family", "Genus", "Species", "Minimum Age", "Maximum Age", "Management Body")
 
@@
 
-```{r paper-other-metrics-and-metadata,echo=F,include=F,warning=F,message=F}
-
-if(load.results==F)
-{
-  # We are now looking at everything, lifetime reproductive success
-
-  for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-  for.tune.all <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
-
-  load(file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
-  # Get the stocks...
-  Stocks <- names(for.tune.summary)
-  n.stocks <- length(Stocks)
-
-  ############ Meta data and clean up, could be it's own chunk really, but it's really fast, so meh...
-
-  #  A quick way to get the other potentially interesting info for the stock...
-  drop <- which(names(ASR.long) %in% c("Year","type","age","value"))
-  meta <- NULL
-  for(i in Stocks) 
-  {
-    meta[[i]] <- ASR.long[ASR.long$Stock == i,-drop][1,]
-    meta[[i]]$age.min <- min(ages.tmp[[i]])
-    meta[[i]]$age.max <- max(ages.tmp[[i]])
-  }
-  meta <- do.call('rbind',meta)
-
-  # First making a meta data object and adding a bunch of columns to it... very messy!!
-  meta$Species[meta$Species == ' harengus']  <- "harengus"
-  meta$Species[meta$Species == "Aeglefinus"] <- "aeglefinus"
-  meta$Species[meta$Species == "Solea"] <- "solea"
-  meta$Family[meta$Family == "Gadide"] <- "Gadidae"
-  meta$Genus[meta$Genus == " Hippoglossoides"] <- "Hippoglossoides"
-  meta$G.short <- toupper(paste0(substr(meta$Genus,1,1),"."))
-  meta$G.Species <- paste0(meta$G.short," ",meta$Species)
-  # Simplified Management
-  meta$Manage.short <- meta$Management
-  meta$Manage.short[grep("TRAC",meta$Management)] <- "DFO-TRAC"
-  meta$Manage.short[grep("DFO",meta$Management)] <- "DFO-TRAC"
-  meta$Manage.short[grep("NEFSC",meta$Management)] <- "NEFSC"
-  meta$Manage.short[grep("ICES",meta$Management)] <- "ICES"
-
-  # The 3 pieces of the ocean
-  meta$LME <- "NW Atlantic"
-  meta$LME[meta$Management == "AFSC"] <- "Pacific (Alaska)"
-  meta$LME[grepl("ICES",meta$Management)] <- "NE Atlantic"
-  # An area typo
-  meta$Area[grep("BSAI-females",meta$Area)] <- "BSAI-Females"
-  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI-Females"
-  # Some other Area summaries
-  meta$Area.broad <- meta$Area
-  meta$Area.long <- meta$Area
-  meta$Area.narrow <- "" # Leave this blank if not needed
-
-  meta$Area.broad[grep("NS",meta$Area)] <- "NS"
-  meta$Area.long[grep("NS",meta$Area)] <- "North Sea"
-  meta$Area.broad[grep("CS",meta$Area)] <- "CS"
-  meta$Area.long[grep("CS",meta$Area)] <- "Celtic Sea"
-  meta$Area.broad[grep("ROCK6b",meta$Area)] <- "CS"
-  meta$Area.long[grep("ROCK6b",meta$Area)] <- "Celtic Sea"
-  meta$Area.broad[grep("IS",meta$Area)] <- "IS"
-  meta$Area.long[grep("IS",meta$Area)] <- "Irish Sea"
-  meta$Area.broad[grep("BS",meta$Area)] <- "BS"
-  meta$Area.long[grep("BS",meta$Area)] <- "Baltic Sea"
-  meta$Area.broad[grep("NEA",meta$Area)] <- "NEA"
-  meta$Area.long[grep("NEA",meta$Area)] <- "NE Arctic"
-  meta$Area.broad[grep("B28.1",meta$Area)] <- "BS"
-  meta$Area.long[grep("B28.1",meta$Area)] <- "Baltic Sea"
-  meta$Area.broad[grep("SP8abd",meta$Area)] <- "BoB"
-  meta$Area.long[grep("SP8abd",meta$Area)] <- "Bay of Biscay"
-  meta$Area.broad[grep("FA",meta$Area)] <- "Ice-Faroe"
-  meta$Area.broad[grep("ICE",meta$Area)] <- "Ice-Faroe"
-  meta$Area.long[grep("FA",meta$Area)] <- "Faroes"
-  meta$Area.long[grep("ICE",meta$Area)] <- "Iceland"
-
-  meta$Area.broad[grep("GOM",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("GOM",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("GB",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("GB",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("5Y",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("5Y",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("5Z",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("5Z",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("USATL",meta$Area)] <- "NAFO 5-6" # The fishery is broader than just GOM, but it does also include it.
-  meta$Area.long[grep("USATL",meta$Area)] <- "NAFO 5-6" # The fishery is broader than just GOM, but it does also include it.
-  meta$Area.broad[grep("NWA",meta$Area)] <- "NAFO 5-6" # Mackerel... so that definition is a bit narrow....
-  meta$Area.long[grep("NWA",meta$Area)] <- "NAFO 5-6" # Mackerel... so that definition is a bit narrow....
-  #meta$Area1[grep("SNE- MA",meta$Area)] <- "GOM-GB" # YT in US, so no GB so that definition is a bit narrow....
-  meta$Area.broad[grep("MA",meta$Area)] <- "NAFO 5-6" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
-  meta$Area.long[grep("MA",meta$Area)] <- "NAFO 5-6" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
-  meta$Area.broad[grep("BSAI",meta$Area)] <- "BSAI"
-  meta$Area.broad[grep("4T",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("4T",meta$Area)] <- "NAFO 2-4"
-  meta$Area.broad[grep("2J3",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("2J3",meta$Area)] <- "NAFO 2-4"
-  meta$Area.broad[grep("3Pn-4RS",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("3Pn-4RS",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("GOA",meta$Area)] <- "Gulf of Alaska"
-  # Lumping everything in Berring Sea and AI into both.
-  meta$Area.long[grep("AI",meta$Area)] <- "Aleutian Islands"
-  meta$Area.long[grep("ESB",meta$Area)] <- "Bering Sea & AI" 
-  meta$Area.long[grep("BSAI",meta$Area)] <- "Bering Sea & AI"
-  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI"
-  meta$Area[grep("BSAI-Females",meta$Area)] <- "BSAI"
-  meta$Area[grep("BSAI-females",meta$Area)] <- "BSAI"
-  meta$Area.long[grep("BSAI-Females",meta$Area)] <- "Bering Sea & AI"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Pollachius_virens"] <- "5b"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5a_Pollachius_virens"] <- "5a"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS4 _Solea_solea"] <- "4"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d._Solea_solea"] <- "7d"
-  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_NS IIIa 22-24_Solea_Solea"] <- "22-24"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d_Pleuronectes_platessa"] <- "7d"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4,20_Pleuronectes_platessa"] <- "4 20"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS7e_Pleuronectes_platessa"] <- "7e"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS27.7a_Pleuronectes_platessa"] <- "7a"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Melanogrammus_aeglefinus"] <- "5b"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Melanogrammus_aeglefinus"] <- "5a"
-  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_B28.1_Clupea_harengus"] <- "28"
-  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_BS 25-29-32_Clupea_harengus" ] <- "25-32"
-  meta$Area.narrow[meta$Stock == "ICES-HAWG_WBS 22-24_Clupea_harengus"] <- "22-24"
-  meta$Area.narrow[meta$Stock == "DFO_4T-Fall_Clupea_harengus"] <- "Fa-SGSL"
-  meta$Area.narrow[meta$Stock == "DFO_4T-Spring_Clupea_harengus"] <- "Sp-SGSL"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS27.6a_Merlangius_merlangus"] <- "27.6a"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS7a_Merlangius_merlangus"] <- "7a"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Gadus_morhua"] <- "5a"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FAPL5b1_Gadus_morhua" ] <- "5b"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua"] <- "4-7 20"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_NS6a_Gadus_morhua"] <- "6a"
-  meta$Area.narrow[meta$Stock == "DFO_2J3KL_Gadus_morhua"] <- "NFLD"
-  meta$Area.narrow[meta$Stock == "DFO_3Pn-4RS_Gadus_morhua"] <- "NGSL"
-  meta$Area.narrow[meta$Stock == "NEFSC-CERT-TRAC_GB _Gadus_morhua"] <- "EGB"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus"] <- "RA"
-  meta$Area.narrow[meta$Stock == "DFO_4T-4VN_Gadus_morhua"] <- "SGSL"
-  meta$Area.narrow[meta$Stock == "DFO_4T_Hippoglossoides _platessoides"] <- "SGSL"
-  meta$Area.narrow[meta$Stock == "DFO_4T_Scomber_scombrus"] <- "SGSL"
-  meta$Area.narrow[meta$Stock == "NEFSC-SAW_GOM_Gadus_morhua"] <- "GOM"
-  meta$Area.narrow[meta$Stock == "NEFSC-GARMIII_GB_Gadus_morhua"] <- "GB"
-  meta$Area.narrow[meta$Stock == "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus"] <- "GOM"
-  meta$Area.narrow[meta$Stock == "CERT-TRAC_GB_Melanogrammus_Aeglefinus"] <- "GB"
-
-  meta$Stock.short <- paste0(meta$Area.broad," ",meta$Area.narrow," ",meta$G.short," ",meta$Species)
-  meta$Stock.no.species <- paste0(meta$Area.long," ",meta$Area.narrow)
-
-  for.tune.stocks <- NULL
-  fta <- NULL
-
-  # Going to rename these female stocks.
-  fem.names <- c("AFSC_BASI-Females_Pleuronectes_quadrituberculatus",
-                    "AFSC_EEBSAI-Females_Lepidopsetta_polyxystra",
-                    "AFSC_BSAI-females_Atheresthes_stomais")
-  fem.rename <- c("AFSC_BSAI_Pleuronectes_quadrituberculatus",
-                    "AFSC_EEBSAI_Lepidopsetta_polyxystra",
-                    "AFSC_BSAI_Atheresthes_stomais")
-  # Going to drop these stocks
-  dont <- paste(c("Mles","Males","COASTNOR"),collapse = "|")
-
-  meta.sub <- NULL
-  for(i in Stocks) 
-  {
-    org.nam <- i
-    tmp <- for.tune.summary[[org.nam]]
-    new.stock.nam <- org.nam
-    # Don't bother for these stocks...
-    if(!grepl(dont,tmp$Stock[1]))
-    {
-      # Grab the metadata and add in some new useful things...
-      meta.sub[[i]] <- meta[meta$Stock == org.nam,]
-
-      # Rename the ladies
-      if(tmp$Stock[1] == fem.names[1]) new.stock.nam <- tmp$Stock <- fem.rename[1]
-      if(tmp$Stock[1] == fem.names[2]) new.stock.nam <- tmp$Stock <- fem.rename[2]
-      if(tmp$Stock[1] == fem.names[3]) new.stock.nam <- tmp$Stock <- fem.rename[3]
-
-      meta.sub[[i]]$Stock <- new.stock.nam
-      tmp <- data.frame(tmp,meta.sub[[i]])
-      # For tunes all
-      fta[[new.stock.nam]] <- for.tune.all[[org.nam]]
-      fta[[new.stock.nam]]$meta <- meta.sub[[i]]
-      for.tune.stocks[[new.stock.nam]] <- tmp
-    }# End skip stocks...
-  }
-  # Now unpack them...
-  for.tunes <- do.call("rbind",for.tune.stocks)
-  for.tune.all <- fta
-  meta.sub <- do.call("rbind",meta.sub)
-
-  ######################### End Meta data and clean up #####################
-
-  # Now some summaries...
-
-  # Reset on the stocks...
-  Stocks <- sort(names(for.tune.all))
-  n.stocks <- length(Stocks)
-
-  # Doubling time, no fishing
-  dt.res <- NULL
-  # These are both set in the index file now, go there!!
-  n.dt.sims <- n.dt.sims
-  n.sim.years <- n.sim.years
-  for(i in Stocks)
-  {
-    str.time <- Sys.time()
-    try <- for.tune.all[[i]]
-    meta.tmp <- try$meta
-    age.4.sim <- meta.tmp$age.min:meta.tmp$age.max
-    double.time <- NA
-    pop <- 1000
-    tmp.res <- NULL
-  for(s in 1:n.dt.sims)
-  {
-    tmp <- rep(0,n.sim.yearss)
-    print(paste0("Sim # ", s))
-
-    for(y in 2:n.sim.yearss)
-    {
-
-      # Get our sample for this run
-      f.pick <- sample(nrow(try$fecund.opt),size=1)
-      nm.pick <- sample(nrow(try$nm.opt),size=1)
-      fec.samp <- try$fecund.opt[f.pick,]
-      # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
-      nm.samp <- try$nm.opt[nm.pick,] 
-      # now put these into Euler-lotka to get an r estimate
-      res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
-      r.val <- res$res$r
-      # If r is > 5 (lambda = exp(5)) it generally means the simple.lotka didn't converge (bad combo of fec and nm)
-      # So we'll need to resample them until it is < 5
-      while(r.val >= 5)
-      {
-        print("Resampling due to bat shit r value")
-        f.pick <- sample(nrow(try$fecund.opt),size=1)
-        nm.pick <- sample(nrow(try$nm.opt),size=1)
-        fec.samp <- try$fecund.opt[f.pick,]
-        # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
-        nm.samp <- try$nm.opt[nm.pick,] 
-        # now put these into Euler-lotka to get an r estimate
-        res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
-        r.val <- res$res$r
-      } # end while loop
-      pop[y] <- exp(r.val)*pop[y-1]
-      if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.sim.yearss] <- 1
-    } # end the years loop
-    tmp.res[[s]] <- data.frame(year =1:n.sim.yearss,doubled = tmp,sim=s)
-
-    } # end sim loop
-    res.tmp <- do.call("rbind",tmp.res)
-
-  dt.res[[i]] <- data.frame(res.tmp,meta.tmp)
-  count <- 0
-  timer <- round(difftime(Sys.time(),str.time,units='mins'),digits=1)
-  print(paste0("Stock ",i," time =", timer," minutes: Stock # ",count+1))
-  } # end Stocks loop
-
-  dub.time <- do.call("rbind",dt.res)
-
-  dub.time.summary <- dub.time |> collapse::fgroup_by(Stock,year)  |> collapse::fsummarise(prop = sum(doubled)/n.dt.sims)
-  dub.time.summary <- left_join(dub.time.summary,meta.sub,by="Stock")
-
-  # Now to get generation lengths + reproductive rates....
-  # First I need to get the fecundity and natural mortalities by cohort instead of year.
-  res.fin <- NULL
-  res.year.fin <- NULL
-  res.lambda.fin <- NULL
-  for(i in Stocks) # 
-  {
-    tst <- for.tune.all[[i]]
-    meta.tmp <- tst$meta
-    # Fishing mortality
-    fm.org.tmp <- tst$fm.org
-    fm.tmp <- tst$fm.opt
-    # fecundity
-    fec.tmp <- tst$fecund.opt
-    fec.org.tmp <- tst$fecund.org
-    # Natural mortality
-    m.org.tmp <- exp(-tst$nm.org) # This is survivorship
-    m.tmp <- exp(-tst$nm.opt) # This is survivorship
-    # Total mortality
-    z.tmp <- exp(-tst$z.opt) # This is survivorship
-    z.org.tmp <- exp(-tst$nm.org -fm.org.tmp) # This is survivorship
-
-    ages <- meta.tmp$age.min:meta.tmp$age.max
-    n.ages <- length(ages)
-    years <- tst$res$year
-    n.years <- length(years)
-    # Now I need to grab the fecundities and nat morts by cohort
-    if(n.years > n.ages)
-    {
-    res.cohort <- NULL
-    res.year <- NULL
-    res.lambda <- NULL
-    for(y in 1:(n.years-n.ages+1))
-    {
-      count = 0
-      fs <- NA
-      # The lx is no fishing survivorship, zx I'm calling the survivorship including fishing
-      lx <- lx.org <- lx.year <- zx <- zx.org <- zx.year <- 1
-      fs.org <- NA
-
-      for(a in 1:n.ages)
-      {
-      fs[a] <- fec.tmp[y+count,a]  
-      fs.org[a] <- fec.org.tmp[y+count,a]  
-      if(a > 1) 
-      {
-        # No fishing
-        lx[a] <- lx[a-1] * m.tmp[y+count,a]  
-        lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
-        lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
-        # Including fishing
-        zx[a] <- zx[a-1] * z.tmp[y+count,a]  
-        zx.org[a] <- zx.org[a-1]* z.org.tmp[y+count,a]  
-        zx.year[a] <- zx.year[a-1] * z.tmp[y,a]
-      }  # end the a > 1 if
-          count <- count + 1
-      }# end the ages loop
-          res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,
-                                 mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
-                                 x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
-                                 zx.opt = zx,
-                                 mx.zx.opt = fs*zx,mx.zx.org = fs.org*zx.org,
-                                 x.mx.zx.opt = fs*zx*ages,x.mx.zx.org = fs.org*zx.org*ages,
-                                 cohort=years[y],age = ages,meta.tmp)
-
-          res.year[[y]] <- data.frame(mx.opt = unlist(fec.tmp[y,]),lx.opt = lx.year,
-                                 mx.lx.opt = unlist(fec.tmp[y,])*lx.year,
-                                 x.mx.lx.opt = unlist(fec.tmp[y,])*lx.year*ages,
-                                 zx.opt = zx.year,
-                                 mx.zx.opt = unlist(fec.tmp[y,])*lx.year,
-                                 x.mx.zx.opt = unlist(fec.tmp[y,])*lx.year*ages,
-                                 age = ages,year=years[y],meta.tmp)
-
-    } # end the years loop
-
-  # Do a years loop to get lambda with no fishing for each year, rather than by cohort...
-    for(yy in 1:(n.years-1))
-    {
-      nm <- as.numeric(tst$nm.opt[yy,])
-      z <- as.numeric(tst$z.opt[yy,])
-      fec <- as.numeric(tst$fecund.opt[yy,])
-      nm.init <- as.numeric(tst$nm.org[yy,])
-      fec.init <- as.numeric(tst$fecund.org[yy,])
-      z.init <- as.numeric(tst$z.org[yy,])
-      lam.no.fish <- exp(simple.lotka.r(mort = nm,fecund = fec,ages=ages)$res$r)
-      lam.fish <- exp(simple.lotka.r(mort = z,fecund = fec,ages=ages)$res$r)
-      lam.org.no.fish <- exp(simple.lotka.r(mort = nm.init,fecund = fec.init,ages=ages)$res$r)
-      lam.org.fish <- exp(simple.lotka.r(mort =  z.init,fecund = fec.init,ages=ages)$res$r)
-
-      # Now summarize these
-      res.lambda[[yy]] <-  data.frame(lam.no.fish = lam.no.fish,lam.fish = lam.fish,
-                                      lam.org.no.fish = lam.org.no.fish,
-                                      lam.org.fish = lam.org.fish,
-                                      year=years[yy],meta.tmp)
-    } # End the yy loop to get the lambdas...
-  # unpack it...
-  res.fin[[i]] <- do.call('rbind',res.cohort)
-  res.year.fin[[i]] <- do.call('rbind',res.year)
-  res.lambda.fin[[i]] <-  do.call('rbind',res.lambda)
-  }  # end if to make sure we have enough data to get the cohort estimates.
-
-  }# end the stock loop
-
-  res.cohort.final <- do.call('rbind',res.fin)
-  res.year.final <- do.call('rbind',res.year.fin)
-  res.lambda.final <- do.call('rbind',res.lambda.fin)
-
-  pop.dam <- res.cohort.final |> collapse::fgroup_by(cohort,Stock) |> collapse::fsummarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
-                                                                                   gen.len.org = sum(x.mx.lx.org)/sum(mx.lx.org),
-                                                                                   R0.opt = sum(mx.lx.opt),R0.org = sum(mx.lx.org))
-  pop.dam <- left_join(pop.dam,meta.sub,by="Stock")
-
-  dub.time.summary <- data.frame(dub.time.summary)
-  pop.dam <- data.frame(pop.dam)
-  # saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",what.2.tune,".Rds"))
-  # saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",what.2.tune,".Rds"))
-  # saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",what.2.tune,".Rds"))
-  save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
-       file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
-
-  write.csv(meta.sub, paste0(loc,"/Data/metadata_no_age_corection.csv"))
-} # end if load results
+```{r,tab-lambdas}
+# The table with the lambda values
+csas_table(comp.lam.res.tab,caption ="A comparison of the $\\lambda_{F=0}$ and $\\lambda_{F>0} estimates for stock at the minimum and maximum abundance, along with the estimate at 40\\% of the maximum abundance.
+values greater than 1 indicate that the population would be expected to increase in size, while values less than 1 indicate the population is likely to decline in size")
 ```
 
-```{r clean-up-and-stats,include=F,echo=F,message=F,warning=F}
-load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
-for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
+\newpage
 
-Stocks <- unique(res.lambda.final$Stock)
-res.lambda.fin <- data.frame(res.lambda.final)
-six.species <- c('morhua','harengus','aeglefinus','virens','solea','platessa')
-pop.dam.6 <- pop.dam |> collapse::fsubset(Species %in% six.species)
-for.tunes.6 <- for.tunes |> collapse::fsubset(Species %in% six.species)
-dub.time.6 <- dub.time.summary |> collapse::fsubset(Species %in% six.species)
-res.lambda.fin$decade <- floor(res.lambda.fin$year/10)*10
-res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock,decade) |> collapse::fmutate(mn.lam = mean(lam.fish,na.rm=T),
-                                                                                 med.lam = median(lam.fish,na.rm=T),
-                                                                                 sd.lam = sd(lam.fish,na.rm=T))
-res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Species,decade) |> collapse::fmutate(lm.spec.mn = mean(mn.lam,na.rm=T))              
-res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock) |> 
-                                                          collapse::fmutate(
-                                                          lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
-                                                          lam.fish.mn = mean(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T),
-                                                          lam.no.fish.med = median(lam.no.fish,na.rm=T),
-                                                          lam.fish.med = median(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.med = median(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T),
-                                                          lam.no.fish.sd = sd(lam.no.fish,na.rm=T),
-                                                          lam.fish.sd = sd(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.sd = sd(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.sd = sd(lam.org.fish,na.rm=T)
-                                                          ) |> data.frame()
-# Get the order right for the stock no species for the boxplots to come later
-sns.order <- c("Baltic Sea ", "Baltic Sea 22-24", "Baltic Sea 25-32", "Baltic Sea 28", 
-               "North Sea ", "North Sea 4", "North Sea 22-24", "North Sea 4-7 20", "North Sea 6a","North Sea 4 20", "North Sea 7d",     
-               "Celtic Sea ","Celtic Sea RA", "Celtic Sea 7a", "Celtic Sea 27.6a", 
-               "Irish Sea ","Irish Sea 7a", "Irish Sea 7e","Bay of Biscay ", "NE Arctic ", 
-               "Faroes 5a", "Faroes 5b",  "Iceland ", "Iceland 5a",
-                "NAFO 2-4 Fa-SGSL", "NAFO 2-4 Sp-SGSL", "NAFO 2-4 SGSL", "NAFO 2-4 NGSL", "NAFO 2-4 NFLD",  
-                "NAFO 5-6 ", "NAFO 5-6 GB", "NAFO 5-6 GOM", "NAFO 5-6 EGB",
-                "Bering Sea & AI ", "Gulf of Alaska ", "Aleutian Islands ")
-
-res.lambda.fin$Stock.no.species <- factor(res.lambda.fin$Stock.no.species,levels = sns.order,ordered = T)
-res.lambda.final.6 <- res.lambda.fin |> collapse::fsubset(Species %in% six.species)
-# Sort the data into a nice order...
-res.lambda.fin <- res.lambda.fin |> collapse::roworder(Species,Area.broad) |>
-                                    collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-# Making the Aleutian Islands their own Area long...
-res.lambda.fin$Area.long[res.lambda.fin$Area == "AI"] <- "Aleutian Islands"
-res.lambda.fin$Area.long <- factor(res.lambda.fin$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
-                                                                       "Irish Sea","Bay of Biscay","NE Arctic",
-                                                                       "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-
-res.lambda.final.6 <- res.lambda.final.6 |> collapse::roworder(Species,Area.broad) |>
-                                            collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-dub.time <- dub.time |> collapse::roworder(LME) |>
-                        collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-dub.time.summary <- dub.time.summary |> collapse::roworder(LME,Order,Species,Area.broad) |>
-                                        collapse::fmutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-dub.time.6 <- dub.time.6 |> collapse::roworder(LME) |>
-                             collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-pop.dam <- pop.dam |> collapse::roworder(Species,LME) |>
-                       collapse::fmutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
-pop.dam.6 <- pop.dam.6 |> collapse::roworder(LME,Area.broad) |>
-                       collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-pop.dam$Area.long[pop.dam$Area == "AI"] <- "Aleutian Islands"
-pop.dam$Area.long <- factor(pop.dam$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
-                                                         "Irish Sea","Bay of Biscay","NE Arctic",
-                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-# I'd also like a pop.dam including fishing
-pop.dam.fish <- res.cohort.final |> collapse::fgroup_by(cohort,Stock) |> collapse::fsummarise(gen.len.opt = sum(x.mx.zx.opt)/sum(mx.zx.opt),
-                                                                                   gen.len.org = sum(x.mx.zx.org)/sum(mx.zx.org),
-                                                                                   R0.opt = sum(mx.zx.opt),R0.org = sum(mx.zx.org))
-pop.dam.fish <- left_join(pop.dam.fish,meta.sub,by="Stock")
-pop.dam.fish$Area.long[pop.dam.fish$Area == "AI"] <- "Aleutian Islands"
-pop.dam.fish$Area.long <- factor(pop.dam.fish$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
-                                                         "Irish Sea","Bay of Biscay","NE Arctic",
-                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-pop.dam <- data.frame(pop.dam)
-
-pop.dam.fish <- pop.dam.fish |> collapse::roworder(Species,LME) |>
-                                collapse::fmutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
-pop.dam.fish.6 <- pop.dam.fish |> collapse::fsubset(Species %in% six.species)
-
-pop.dam.fish.6 <- pop.dam.fish.6 |> collapse::roworder(LME,Area.broad) |>
-                                    collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-# Put the population dynamics stuff together.
-pop.dam$group <- "no fish"
-pop.dam.fish$group <- 'fish'
-pop.dam.all <- rbind(pop.dam,pop.dam.fish)
-
-pop.dam.6$Stock.no.species <- factor(pop.dam.6$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam$Stock.no.species <- factor(pop.dam$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam.fish.6$Stock.no.species <- factor(pop.dam.fish.6$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam.fish$Stock.no.species <- factor(pop.dam.fish$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam.all$Stock.no.species <- factor(pop.dam.all$Stock.no.species,levels = sns.order,ordered = T)
-# Drop the periods....
-pop.dam.all.6 <- pop.dam.all |> collapse::fsubset(!Species %in% six.species)
-pop.dam.all$G.Species <- gsub("\\.","",pop.dam.all$G.Species)
-pop.dam.all$G.Species.short <- substr(pop.dam.all$G.Species,1,5)
-pop.dam.all$G.Species <- gsub("\\.","",pop.dam.all$G.Species)
-pop.dam.all.6 <- pop.dam.all |> collapse::fsubset(Species %in% six.species)
-pop.dam.all.others <- pop.dam.all |> collapse::fsubset(!Species %in% six.species)
-
-# Reorder the doubling time, either by Species and LME, or the other way around
-
-dub.time.summary$Order.short <- "Gadi"
-dub.time.summary$Order.short[dub.time.summary$Order == "Pleuronectiformes"] <- "Plero"
-dub.time.summary$Order.short[dub.time.summary$Order == "Clupeiformes"] <- "Clupei"
-dub.time.summary$Order.short[dub.time.summary$Order == "Scorpaeniformes "] <- "Scor"
-dub.time.summary$Order.short[dub.time.summary$Order == "Scombriformes"] <- "Scomb"
-dub.time.summary$Order.short[dub.time.summary$Order == "Perciformes"] <- "Perci"
-# First need to get the abundance and lambdas with no fishing into one object.
-ft.tmp <- for.tunes |> collapse::fselect(year,Stock,vpa.abund,est.abund,removals)
-dd.dat <- left_join(res.lambda.fin,ft.tmp,by=c('year','Stock'))
-# Now I need to get a relative abundance for each stock...
-dd.dat <- dd.dat |> collapse::fgroup_by(Stock) |> collapse::fmutate(max.abund = max(est.abund,na.rm=T))
-dd.dat <- data.frame(dd.dat)
-dd.dat$prop.abund <- dd.dat$est.abund/dd.dat$max.abund
-# Drop nas....
-drops <- -which(is.na(dd.dat$prop.abund))
-dd.dat <- dd.dat[drops,]
-#lump the data into bins
-dd.dat$prop.bin <- "< 10%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.1 & dd.dat$prop.abund <= 0.2] <- "10-20%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.2 & dd.dat$prop.abund <= 0.3] <- "20-30%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.3 & dd.dat$prop.abund <= 0.4] <- "30-40%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.4 & dd.dat$prop.abund <= 0.6] <- "40-60%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.6 & dd.dat$prop.abund <= 0.8] <- "60-80%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.8 & dd.dat$prop.abund <= 1] <- "80-100%"
-dd.dat$prop.bin <- factor(dd.dat$prop.bin,levels=c("< 10%","10-20%","20-30%","30-40%","40-60%","60-80%","80-100%"))
-
-# Subset to the big six
-dd.dat.six <- dd.dat  |>collapse::fsubset(Species %in% six.species)
-
-# This is for the new lambda figures with fishing and no fishing together
-
-res.lambda.fin.long <- res.lambda.fin |> tidyr::pivot_longer(cols = c(lam.no.fish,lam.fish),names_to = 'group',values_to = 'lambda')
-res.lambda.fin.long$Stock.no.species <- factor(res.lambda.fin.long$Stock.no.species,levels = sns.order,ordered = T)
-res.lambda.fin.long$group <- substr(res.lambda.fin.long$group,5,20)
-res.lambda.fin.long$group <- gsub("\\."," ",res.lambda.fin.long$group)
-res.lambda.fin.long.others <- res.lambda.fin.long |> collapse::fsubset(!Species %in% six.species)
-res.lambda.fin.long.others$G.Species <- gsub("\\.","",res.lambda.fin.long.others$G.Species)
-res.lambda.fin.long.others$G.Species.short <- substr(res.lambda.fin.long.others$G.Species,1,5)
-res.lambda.fin.long.6 <- res.lambda.fin.long |> collapse::fsubset(Species %in% six.species)
-res.lambda.fin.long.6$G.Species <- gsub("\\.","",res.lambda.fin.long.6$G.Species)
-
-# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE
-# here is the GAM for no fishing with subsequent processing.
-mod.dd.stock.gam.nf <- gam(log(lam.no.fish) ~   s(prop.abund,k=4) + s(prop.abund,as.factor(Stock.short),bs='fs',k=3) ,data=dd.dat)
-
-# This extracts the GAM fit so we can custom plot it on our own figure
-tmp <- plot(mod.dd.stock.gam.nf, pages = 0)
-no.stock.gam.nf.dat <- data.frame(fit = tmp[[1]]$fit + coefficients(mod.dd.stock.gam.nf)[1],prop.abund = tmp[[1]]$x,se = tmp[[1]]$se,Scenario = "F = 0")
-no.stock.gam.nf.dat$LCI <- no.stock.gam.nf.dat$fit - 1.96*no.stock.gam.nf.dat$se
-no.stock.gam.nf.dat$UCI <- no.stock.gam.nf.dat$fit + 1.96*no.stock.gam.nf.dat$se
-
-#summary(mod.dd.stock.gam.nf)
-#Residuals, definitely still issues here, maybe a bit better than some others, maybe...
-#plot(residuals(mod.dd.stock.gam.nf) ~ fitted(mod.dd.stock.gam.nf))
-# Normality = no
-#qqnorm(residuals(mod.dd.stock.gam.nf))
-#qqline(residuals(mod.dd.stock.gam.nf))
-
-pred.dd.stock.gam.nf <- expand.grid(prop.abund = seq(0, 1, length.out = 250),
-                                         Stock.short=c(unique(dd.dat$Stock.short)))
-tmp <- predict(mod.dd.stock.gam.nf, pred.dd.stock.gam.nf, type = 'response', se.fit = TRUE) 
-# Another fun trick to extract the overall smooth fit, but didn't end up using this method.
-# sms <- smooths(mod.dd.stock.gam.nf)
-# excl <- grepl("as.factor",sms)
-# rm <- sms[excl]
-# tmp.ex <- predict(mod.dd.stock.gam.nf, newdata =pred.dd.stock.gam.nf, type = 'response', se.fit = TRUE,exclude =rm) 
-# Get the fit by stock
-pred.dd.stock.gam.nf$lam.no.fish   <- exp(tmp$fit)
-pred.dd.stock.gam.nf$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-pred.dd.stock.gam.nf$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-
-# Thin the data so I can add points to the figure
-tmp <- NULL
-for(i in 1:(77)) 
-{
-  if(i==1) tmp[[i]] <- seq(10,230,length.out=5)
-  if(i>1) tmp[[i]] <- seq(10,230,length.out=5)+250*(i-1)
-}
-thinner.nf <- do.call('c',tmp)
-thin.pred.nf <- pred.dd.stock.gam.nf[thinner.nf,]
-# Now I want to get rid of extrapolation from this prediction data.frame, I think I need to loop it...
-# 
-short.stocks <- unique(dd.dat$Stock.short)
-n.stocks <- length(short.stocks)
-pred.out <- NULL
-thin.out <- NULL
-for(i in short.stocks)
-{
-  # Get the right stocks
-  tmpy <- dd.dat |> collapse::fsubset(Stock.short == i)
-  tmp.pred <- pred.dd.stock.gam.nf |> collapse::fsubset(Stock.short == i)
-  tmp.thin <- thin.pred.nf |> collapse::fsubset(Stock.short == i)
-  # I dont want to predict below the minimum observed abundance
-  mins <- min(tmpy$prop.abund,na.rm=T)
-  pred.out[[i]] <- tmp.pred |> collapse::fsubset(prop.abund >= mins)
-  thin.out[[i]] <- tmp.thin |> collapse::fsubset(prop.abund >= mins)
-}
-
-pred.dd.stock.gam.ss.nf <- do.call('rbind',pred.out)
-thin.pred.nf <- do.call('rbind',thin.out)
-# Combine pred stuff with the meta data for fun plots
-pred.dd.stock.gam.ss.nf <- left_join(pred.dd.stock.gam.ss.nf,meta.sub,by="Stock.short")
-pred.dd.stock.gam.ss.nf <- data.frame(pred.dd.stock.gam.ss.nf)
-thin.pred.nf <- left_join(thin.pred.nf,meta.sub,by="Stock.short")
-# Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# By region
-cols.gam <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
-pty.gam <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
-
-# Now do the same thing with the data that includes the effect of fishing.
-
-#mod.dd.stock.gam.fish <- gam(log(lam.fish) ~  as.factor(Stock.short) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.dat)
-mod.dd.stock.gam.fish <- gam(log(lam.fish) ~  s(prop.abund,k=4) + s(prop.abund,as.factor(Stock.short),bs='fs',k=3),data=dd.dat)
-
-tmp <- plot(mod.dd.stock.gam.fish, pages = 0)
-no.stock.gam.fish.dat <- data.frame(fit = tmp[[1]]$fit + coefficients(mod.dd.stock.gam.fish)[1],prop.abund = tmp[[1]]$x,se = tmp[[1]]$se,Scenario = "F > 0")
-no.stock.gam.fish.dat$LCI <- no.stock.gam.fish.dat$fit - 1.96*no.stock.gam.fish.dat$se
-no.stock.gam.fish.dat$UCI <- no.stock.gam.fish.dat$fit + 1.96*no.stock.gam.fish.dat$se
-
-#summary(mod.dd.stock.gam.fish)
-#Residuals, definetly still issues here, maybe a bit better than some others, maybe...
-#plot(residuals(mod.dd.stock.gam.fish) ~ fitted(mod.dd.stock.gam.fish))
-# Normality = no
-#qqnorm(residuals(mod.dd.stock.gam.fish))
-#qqline(residuals(mod.dd.stock.gam.fish))
-
-pred.dd.stock.gam.fish <- expand.grid(prop.abund = seq(0, 1, length.out = 250),
-                                         Stock.short=c(unique(dd.dat$Stock.short)))
-tmp <- predict(mod.dd.stock.gam.fish, pred.dd.stock.gam.fish, type = 'response', se.fit = TRUE) 
-pred.dd.stock.gam.fish$lam.fish   <- exp(tmp$fit)
-pred.dd.stock.gam.fish$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-pred.dd.stock.gam.fish$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-
-# Thin the data so I can add points to the figure
-tmp <- NULL
-for(i in 1:(77)) 
-{
-  if(i==1) tmp[[i]] <- seq(10,230,length.out=5)
-  if(i>1) tmp[[i]] <- seq(10,230,length.out=5)+250*(i-1)
-}
-thinner.fish <- do.call('c',tmp)
-thin.pred.fish <- pred.dd.stock.gam.fish[thinner.fish,]
-# Now I want to get rid of extrapolation from this prediction data.frame, I think I need to loop it...
-# 
-short.stocks <- unique(dd.dat$Stock.short)
-pred.out <- NULL
-thin.out <- NULL
-for(i in short.stocks)
-{
-  # Get the right stocks
-  tmpy <- dd.dat |> collapse::fsubset(Stock.short == i)
-  tmp.pred <- pred.dd.stock.gam.fish |> collapse::fsubset(Stock.short == i)
-  tmp.thin <- thin.pred.fish |> collapse::fsubset(Stock.short == i)
-  # I dont want to predict below the minimum observed abundance
-  mins <- min(tmpy$prop.abund,na.rm=T)
-  pred.out[[i]] <- tmp.pred |> collapse::fsubset(prop.abund >= mins)
-  thin.out[[i]] <- tmp.thin |> collapse::fsubset(prop.abund >= mins)
-}
-
-pred.dd.stock.gam.ss.fish <- do.call('rbind',pred.out)
-thin.pred.fish <- do.call('rbind',thin.out)
-# Combine pred stuff with the meta data for fun plots
-pred.dd.stock.gam.ss.fish <- left_join(pred.dd.stock.gam.ss.fish,meta.sub,by="Stock.short")
-pred.dd.stock.gam.ss.fish <- data.frame(pred.dd.stock.gam.ss.fish)
-
-thin.pred.fish <- left_join(thin.pred.fish,meta.sub,by="Stock.short")
-
-# Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# By region
-
-# What proportion of the stocks had the lowest 'GAM' estimate happen when the stock was at it's maximum size.
-low.gam <- data.frame(low.pa.fish = NA,diff.low.pa.fish = NA,low.pa.nf = NA,diff.low.pa.nf = NA,Stock = NA,Species = NA)
-count <- 0
-for(i in short.stocks) 
-{
-  count = count +1
-  tmp <- pred.dd.stock.gam.ss.fish |> collapse::fsubset(Stock.short == i)
-  tmp.nf <- pred.dd.stock.gam.ss.nf |> collapse::fsubset(Stock.short == i)
-  low.pa <- data.frame(low.pa.fish = tmp$prop.abund[tmp$lam.fish == min(tmp$lam.fish)],
-                       diff.low.pa.fish = tmp$lam.fish[tmp$lam.fish == min(tmp$lam.fish)] - tmp$lam.fish[tmp$prop.abund == max(tmp$prop.abund)],
-                       low.pa.nf = tmp.nf$prop.abund[tmp.nf$lam.no.fish == min(tmp.nf$lam.no.fish)],
-                       diff.low.pa.nf = tmp.nf$lam.no.fish[tmp.nf$lam.no.fish == min(tmp.nf$lam.no.fish)] - tmp.nf$lam.no.fish[tmp.nf$prop.abund == max(tmp.nf$prop.abund)],
-                       Stock = i,Species = tmp$G.Species[1])
-  low.gam[count,] <- low.pa
-}
-
-# Let's compare lambda at minimum, 0.4, and maximum and make a Table
-comp.lam.diff <- NULL
-comp.lam <- NULL
-comp.all.nf <- NULL
-comp.all.fish <- NULL
-for(i in short.stocks) 
-{
-  tmp <- pred.dd.stock.gam.ss.fish |> collapse::fsubset(Stock.short == i)
-  which.40 <- max(which(tmp$prop.abund <=0.4)) # Some stocks might not have a which 40.
-  which.max <- which(tmp$prop.abund ==1)
-  which.min <- which(tmp$prop.abund == min(tmp$prop.abund))
-  tmp.sub <- tmp[c(which.min,which.40,which.max),]
-  comp.all.fish[[i]] <- tmp.sub
-  tmp.nf <- pred.dd.stock.gam.ss.nf |> collapse::fsubset(Stock.short == i)
-  # I think I'm overkilling as this should be the same was the above witches....
-  which.40.nf <- max(which(tmp.nf$prop.abund <=0.4))
-  which.max.nf <- which(tmp.nf$prop.abund ==1)
-  which.min.nf <- which(tmp.nf$prop.abund ==min(tmp.nf$prop.abund))
-  tmp.nf.sub <- tmp.nf[c(which.min.nf,which.40.nf,which.max.nf),]
-  comp.all.nf[[i]] <- tmp.nf.sub
-  # Now we just want some summaries here I think...
-  comp.lam.diff[[i]] <- data.frame(min.abund = min(tmp.sub$prop.abund,na.rm=T),
-                              lam.fish.min.40 = tmp$lam.fish[which.min] - tmp$lam.fish[which.40],
-                              lam.fish.min.max = tmp$lam.fish[which.min] - tmp$lam.fish[which.max],
-                              lam.fish.40.max = tmp$lam.fish[which.40] - tmp$lam.fish[which.max],
-                              lam.nf.min.40 = tmp.nf$lam.no.fish[which.min.nf] - tmp.nf$lam.no.fish[which.40.nf],
-                              lam.nf.min.max = tmp.nf$lam.no.fish[which.min.nf] - tmp.nf$lam.no.fish[which.max.nf],
-                              lam.nf.40.max = tmp.nf$lam.no.fish[which.40.nf] - tmp.nf$lam.no.fish[which.max.nf],
-                              Stock = i,Species = tmp$G.Species[1])
-
-    comp.lam[[i]] <- data.frame(min.abund = min(tmp.sub$prop.abund,na.rm=T),
-                                lam.fish.min = tmp$lam.fish[which.min] ,
-                                lam.fish.40 = tmp$lam.fish[which.40],
-                                lam.fish.max = tmp$lam.fish[which.max],
-                                lam.nf.min = tmp.nf$lam.no.fish[which.min.nf],
-                                lam.nf.40 = tmp.nf$lam.no.fish[which.40.nf],
-                                lam.nf.max = tmp.nf$lam.no.fish[which.max.nf],
-                                Stock = i,Species = tmp$G.Species[1])
-}
-
-# A table for the estimates at 'interesting' values
-comp.lam.res <- do.call('rbind',comp.lam)
-# I want to turn this into a table....
-comp.lam.res.tab <- comp.lam.res
-# Round the numbers
-comp.lam.res.tab$min.abund <- round(comp.lam.res.tab$min.abund,digits=2)
-rounders <- c("lam.fish.min","lam.fish.40","lam.fish.max",
-              "lam.nf.min","lam.nf.40","lam.nf.max")
-comp.lam.res.tab[,rounders]      <- round(comp.lam.res.tab[,rounders] ,digits=3)
-# Now give it pretty names
-tab.names <- c("Minimum Abundance",
-               "$\\lambda_{F>0}^{Min}$",
-               "$\\lambda_{F>0}^{40}$",
-               "$\\lambda_{F>0}^{Max}$",
-               "$\\lambda_{F=0}^{Min}$",
-               "$\\lambda_{F=0}^{40}$",
-               "$\\lambda_{F=0}^{Max}$",
-               "Stock","Species")
-names(comp.lam.res.tab) <- tab.names
-
-# Now do the same with the differences
-comp.lam.diff.res <- do.call('rbind',comp.lam.diff)
-# I want to turn this into a table....
-comp.lam.diff.res.tab <- comp.lam.diff.res
-# Round the numbers
-comp.lam.diff.res.tab$min.abund <- round(comp.lam.diff.res.tab$min.abund,digits=2)
-rounders <- c("lam.fish.min.40","lam.fish.min.max","lam.fish.40.max",
-                    "lam.nf.min.40","lam.nf.min.max","lam.nf.40.max")
-comp.lam.diff.res.tab[,rounders] <- round(comp.lam.diff.res.tab[,rounders] ,digits=3)
-# Now give it pretty names
-tab.names <- c("Minimum Abundance",
-               "$\\lambda_{F>0}^{Min-40}$",
-               "$\\lambda_{F>0}^{Min-Max}$",
-               "$\\lambda_{F>0}^{40-Max}$",
-               "$\\lambda_{F=0}^{Min-40}$",
-               "$\\lambda_{F=0}^{Min-Max}$",
-               "$\\lambda_{F=0}^{40-Max}$",
-               "Stock","Species")
-names(comp.lam.diff.res.tab) <- tab.names
-
-# Used for the figure showing the number of stocks that have recovered by year x.
-n.dub <- data.frame(years = 1:n.sim.years, count = NA)
-for(i in 1:n.sim.years) n.dub$count[i] <- dub.time.summary |> collapse::fsubset(year==i & prop >= 0.75) |> nrow()
-
-# Compare the population recovery with the variance, using 2010 because all stocks have a value at 2010... 
-# I'm using the overall lambda sd, so the year doesn't actually matter other than to make sure all stocks are included here
-# This is used for the recovery variance figure, is this data good?
-# How many of the stocks had doubled by year 20, with 75% being my standard, which is a high standard
-dub.p.high <- 0.75
-dub.p.low <- 0.5
-n.dub.10 <- dub.time.summary |> collapse::fsubset(year==10 & prop >= dub.p.high) |> nrow()
-n.dub.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop >= dub.p.high) |> nrow()
-# Slow stocks, here we define having a low recovery potential has having < 50% of the simulatoins experience a doubling in size.
-slow.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop < dub.p.low) 
-prop.rec.20 <- dub.time.summary |> collapse::fsubset(year==20) # the proportion that recovers by year 20
-lambda.sds <- res.lambda.fin |> collapse::fsubset(year == 2010)
-lam.sd.p.rec <- left_join(prop.rec.20,lambda.sds,by=names(prop.rec.20)[c(1,4:24)]) 
-lam.sd.p.rec$prop.cat <- "Moderate"
-lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop < dub.p.low] <- "Low"
-lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop >= dub.p.high] <- "High"
-lam.sd.p.rec$prop.cat <- factor(lam.sd.p.rec$prop.cat,levels=c("Low","Moderate","High"))
-
+```{r,tab-lamda-diffs}
+# Now make the table for the differences
+csas_table(comp.lam.diff.res.tab,caption ="A comparison of the difference in $\\lambda_{F=0}$ and $\\lambda_{F>0} for each stock at the minimum and maximum abundance, along with the change at 40\\% of the maximum abundance.
+Positive values indicate that the $\\lambda$ estimae has increased as abundance declines (consistent with negative density dependence), while negative values indicate the $\\lambda$ estimate has declined (considtent with positive density dependence)")
 ```
 
-```{r paper-calcs,include=F,echo=F,message=F,warning=F}
-
-# the lambda calcs
-med.lambda.F0 <- round(median(res.lambda.fin$lam.no.fish),digits=3)
-med.r.F0 <- round(median(log(res.lambda.fin$lam.no.fish)),digits=3)*100
-med.lambda.F <- round(median(res.lambda.fin$lam.fish),digits=3)
-med.r.F <- round(median(log(res.lambda.fin$lam.fish)),digits=3)*100
-mn.lambda.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
-mn.r.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
-# Mean - median...
-res.lambda.fin$med.mn.diff.no.fish <- res.lambda.fin$lam.no.fish.med - res.lambda.fin$lam.no.fish.mn
-res.lambda.fin$med.mn.diff.fish <- res.lambda.fin$lam.fish.med - res.lambda.fin$lam.fish.mn
-# How many stocks had the mean higher than the median
-n.mn.higher.med.no.fish <- length(unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.no.fish < 0]))
-n.mn.higher.med.fish <- length(unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.fish < 0]))
-low.mn.lambda.stocks <- unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.fish > 0])
-n.nw.ice <- length(c(grep("NAFO",low.mn.lambda.stocks),grep("Faroe",low.mn.lambda.stocks)))
-n.cod.low.mn <- length(grep("morhua",low.mn.lambda.stocks))
-n.cod <- length(grep("morhua",Stocks))
-
-# Density dependence related numbers
-n.bl.40 <- length(which(!is.na(comp.lam.res$lam.fish.40)))
-n.low.40.nf <- length(which(comp.lam.res$lam.nf.40 < 1))
-n.low.40.fish <-length(which(comp.lam.res$lam.fish.40 < 1))
-low.lam.40.nf <- -round(min(comp.lam.diff.res$lam.nf.40,na.rm=T),digits=3)
-low.4.lam.40.nf <- -round(sort(comp.lam.diff.res$lam.nf.40)[4],digits=3)
-
-# If right isn't this interesting!!! And look, 3 cod stocks from around here all say around 0.4 is the worst.  Most interesting...
-n.low.lam.at.max.fish <- length(which(low.gam$low.pa.fish == 1))
-n.low.lam.at.max.nf <- length(which(low.gam$low.pa.nf == 1))
-low.lam.cods <- low.gam[low.gam$low.pa.nf < 1 & low.gam$Species == "G. morhua",]
-n.cod.lam.not.at.max.nf <- nrow(low.lam.cods)
-pa.low.cod.min <- round(min(low.lam.cods$low.pa.nf),digits=2)
-pa.low.cod.max <- round(max(low.lam.cods$low.pa.nf),digits=2)
-
-# more density dependence numbers
-pa.lam.nf.at.one <- 100*round(no.stock.gam.nf.dat$prop.abund[min(which(no.stock.gam.nf.dat$fit <0))],digits=2)
-pa.lam.fish.at.one <- 100*round(no.stock.gam.fish.dat$prop.abund[min(which(no.stock.gam.fish.dat$fit <0))],digits=2)
-# What is the minimum abundance at which we get a 2 with the fishing lambdas.
-pa.big.threshold <- 0.65
-pa.low.threshold <- 0.8
-lam.low.threshold <- 0.8
-pa.lam.fish.low.bigs <- max(dd.dat$lam.fish[dd.dat$prop.abund >= pa.big.threshold])
-pa.lam.nf.low.bigs <- round(rev(sort(dd.dat$lam.no.fish[dd.dat$prop.abund >= pa.big.threshold]))[2],digits =2)
-# What proportion of the stocks had large declines overall, and then the proportion when the population was below 30%
-dd.dat.high <- dd.dat |> collapse::fsubset(prop.abund >= 0.3)
-prop.low.high.abund <- round(length(which(dd.dat.high$lam.fish < lam.low.threshold)) / nrow(dd.dat.high),digits=3)
-prop.low.all <- round(length(which(dd.dat$lam.fish < lam.low.threshold)) / nrow(dd.dat),digits=3)
-dd.dat.low <- dd.dat |> collapse::fsubset(prop.abund < 0.3)
-prop.low.low.abund <- round(length(which(dd.dat.low$lam.fish < lam.low.threshold)) / nrow(dd.dat.low),digits=3)
-
-# Numbers for the paper, lifetime reproductive growth
-r0.mn <- round(mean(pop.dam$R0.opt,na.rm=T),digits=1)
-r0.med <- round(median(pop.dam$R0.opt,na.rm=T),digits=1)
-# And fishing...
-r0.mn.fish <- round(mean(pop.dam.fish$R0.opt,na.rm=T),digits=1)
-r0.med.fish <- round(median(pop.dam.fish$R0.opt,na.rm=T),digits=1)
-
-# Where are the slow ones from
-n.not.dub.20 <- nrow(slow.20)
-n.alaska <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short== "AFSC"]))
-n.nwa <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("DFO-TRAC","NEFSC")]))
-n.nea <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("ICES")]))
-n.nafo.24 <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Area.broad %in% "NAFO 2-4"]))
-# Now the don't recover ones...
-n.alaska.slow <- length(slow.20$Stock.short[slow.20$Manage.short== "AFSC"])
-n.nwa.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% c("DFO-TRAC","NEFSC")])
-n.nea.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% "ICES"])
-
-# Need to grab all the per.diff's, which I seem to have dropped
-for.diffs <- do.call('rbind',for.tune.summary)
-med.per.diff <- round(median(for.diffs$per.diff,na.rm=T),digits=1)
-# what is lambda difference, about 6%, but that means the original was 7% higher, so that means we are reducing lambda when optimizing
-# If there was 'missing fishing' we are compensating for with this, this is exactly what we'd expect to happen right?
-res.lambda.fin$lam.per.diff <- 100*((res.lambda.fin$lam.org.no.fish - res.lambda.fin$lam.no.fish)/ res.lambda.fin$lam.no.fish)
-med.lam.per.diff <- round(median(res.lambda.fin$lam.per.diff,na.rm=T),digits=1)
-# By stock, can see most are positive, which is in line with missing fishing mortality...
-mod.by.stock.lam.pd <- res.lambda.fin |> collapse::fgroup_by(Stock.short) |> collapse::fsummarise(med = median(lam.per.diff,na.rm=T),
-                                                                                                  mn = mean(lam.per.diff,na.rm=T))
-
+```{r,tab-meta}
+# Now make the table for the differences
+csas_table(meta.4.tab,caption ="Summary of the stocks included in this analysis.  The minimun and maximum ages are what was used in the stock assessment.")
 ```
-
-```{r main-figs,include=F,echo=F,message=F,warning=F}
-
-# New lambda plot with the fishing and no fishing beside each other
-# This is likely Figure 1
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Stock.no.species),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(G.Species),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 19,base_height = 15)
-
-# The other stocks, perhaps we put this in a supplement...
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(y=lambda,interaction(group,G.Species.short),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(Area.long),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 19,base_height = 15)
-
-# Standard deviation figure
-colrs.sd <- rep(c(rep('blue',4),rep('orange',4),rep('grey',4),rep('black',4)),20)
-pty.sd <- rep(rep(c(21,4,9,8),4),20)
-
-lam.sd.plt <- ggplot(res.lambda.fin ) + 
-                                       geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
-                                       scale_y_log10("Standard deviation (Lambda)",log_breaks(n=8)) +
-                                       scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
-                                       theme(axis.text.x = element_text(angle =45,hjust=1),
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 10)
-
-# Overall density dependence
-# MAIN PAPER FIGURE#
-dd.nf.overall.plt <-ggplot(no.stock.gam.nf.dat , aes(x=prop.abund,y=exp(fit))) + 
-                                geom_point(data = dd.dat,aes(x=prop.abund,y=lam.no.fish),size=2,alpha=0.1) +  
-                                geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI)),alpha=0.5,linewidth=0,fill=u.colors[1])+
-                                geom_line(color=u.colors[1],linewidth=1) + 
-                                xlab("") + 
-                                scale_y_log10(name = "Lambda(F=0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_blank()) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-# MAIN PAPER FIGURE#
-dd.fish.overall.plt <- ggplot(no.stock.gam.fish.dat, aes(x=prop.abund,y=exp(fit))) + 
-                                geom_point(data = dd.dat,aes(x=prop.abund,y=lam.fish),size=2,alpha=0.1) +  
-                                geom_line(color=u.colors[2],linewidth=2) + 
-                                geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI)),alpha=0.5,fill=u.colors[2])+
-                                xlab("") + 
-                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed',linewidth=1.5)+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_blank()) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-# Main Paper Figure Density dependence with and without fishing, effectively a zoomed in version of the above.
-colrs <- u.colors
-t.smooth <- rbind(no.stock.gam.fish.dat,no.stock.gam.nf.dat)
-dd.fish.nf.plt <- ggplot(t.smooth, aes(x=prop.abund,y=exp(fit),group=Scenario,color=Scenario,fill=Scenario)) + 
-                                 geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI),group=Scenario,fill=Scenario),alpha=0.50,linewidth=0)+
-                                 geom_line(linewidth=1.5) +
-                                 geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                 scale_fill_manual(values = colrs) + scale_color_manual(values = colrs) +
-                                 scale_x_continuous(name = "Proportion of maximum abundance",breaks = seq(0,1,by=0.1)) + 
-                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-                                 theme(legend.position = c(0.9,0.75))
-
-dd.overall.combo <- plot_grid(dd.nf.overall.plt,dd.fish.overall.plt,dd.fish.nf.plt,nrow=3)
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_overall_",what.2.tune,".png"),dd.overall.combo,base_width = 10,base_height = 10)
-
-new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(y=lambda,interaction(group,G.Species.short),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(Area.long),design=mat,scales='free_x')
-
-# Density dependence by stock 
-cols.gam <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
-pty.gam <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
-# Doing this manually because the ordered factor wasn't working... annoying...
-mat <- matrix(c(2, 2,13,13, 5, 5, 9, 9,
-                3, 3,12,12, 6, 6, 8, 8,
-               NA,NA,10,10,11,11,NA,NA,
-               NA,7, 7, 4, 4, 1, 1, NA),
-                4, 8, byrow = TRUE)
-
-dd.stocks.nf.plt <- ggplot(pred.dd.stock.gam.ss.nf,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=G.Species,shape=G.Species)) + 
-                                geom_line() + 
-                                geom_point(data = thin.pred.nf,size=2) +  
-                                xlab("Proportion of maximum abundance") + 
-                                scale_y_log10(name = "Lambda (F=0)",breaks = log_breaks(n=10)) +
-                                geom_ribbon(aes(ymin=lower,ymax=upper,color=G.Species),alpha=0.10,linewidth=0)+
-                                facet_manual(vars(Area.long),design=mat,scales='free_x')+
-                                #facet_wrap(~Area.long)  +
-                                scale_shape_manual(values=pty.gam) +
-                                scale_color_manual(values = cols.gam) + 
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_text(size=7)) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"),dd.stocks.nf.plt,base_width = 10,base_height = 10)
-
-mat <- matrix(c(2, 2,13,13, 5, 5, 9, 9,
-                3, 3,12,12, 6, 6, 8, 8,
-               NA,NA,10,10,11,11,NA,NA,
-               NA,7, 7, 4, 4, 1, 1, NA),
-                4, 8, byrow = TRUE)
-
-# MAIN PAPER FIGURE#
-dd.stocks.fish.plt <- ggplot(pred.dd.stock.gam.ss.fish,aes(x=prop.abund,y=lam.fish,group=Stock.short,color=G.Species,shape=G.Species)) + 
-                                geom_line() + 
-                                geom_point(data = thin.pred.fish,size=2) +  
-                                geom_ribbon(aes(ymin=lower,ymax=upper,color=G.Species),alpha=0.10,linewidth=0)+
-                                xlab("Proportion of maximum abundance") + 
-                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10)) +
-                                facet_manual(vars(Area.long),design=mat,scales='free_x')+
-                                #facet_wrap(~Area.long)  +
-                                scale_shape_manual(values=pty.gam) +
-                                scale_color_manual(values = cols.gam) + 
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_text(size=7)) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_fish_stocks_",what.2.tune,".png"),dd.stocks.fish.plt,base_width = 10,base_height = 10)
-
-# Lifetime reproductive success 
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-r0.boxplt.6 <- ggplot(pop.dam.all.6) + geom_boxplot(aes(y=R0.opt,interaction(group,Stock.no.species),color=group))  + 
-                                       scale_x_discrete(NULL, guide = "axis_nested") + scale_y_log10(name = "Lifetime Reproductive Output")+
-                                       geom_hline(yintercept = 1,linetype='dashed',color='blue')+
-                                       facet_manual(vars(G.Species),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"),r0.boxplt.6,base_width = 19,base_height = 15)
-
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-r0.boxplot.others <- ggplot(pop.dam.all.others) +   geom_boxplot(aes(y=R0.opt,interaction(group,G.Species.short),color=group))  + 
-                                                    scale_x_discrete(NULL, guide = "axis_nested") + 
-                                                    scale_y_log10(name = "Lifetime Reproductive Output")+
-                                                    geom_hline(yintercept = 1,linetype='dashed',color='blue')+
-                                                    facet_manual(vars(Area.long),design=mat,scales='free')+
-                                                    theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                          plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"),r0.boxplot.others,base_width = 15,base_height = 10)
-
-r0.heatmap.ne <- ggplot(pop.dam |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-r0.heatmap.nw <- ggplot(pop.dam |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-r0.heatmap.pac <- ggplot(pop.dam |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                     xlab("") + ylab("")+
-                                     facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                     geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                     theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                           legend.key.width = unit(3,'cm'))
-
-r0.heatmap <- cowplot::plot_grid(r0.heatmap.pac,r0.heatmap.nw,r0.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_nf_",what.2.tune,".png"),r0.heatmap,base_width = 20,base_height = 17)
-
-r0.heatmap.ne.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-r0.heatmap.nw.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-r0.heatmap.pac.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                     xlab("") + ylab("")+
-                                     facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                     geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                     theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                           legend.key.width = unit(3,'cm'))
-
-r0.heatmap.fish <- cowplot::plot_grid(r0.heatmap.pac.fish,r0.heatmap.nw.fish,r0.heatmap.ne.fish,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_fish_",what.2.tune,".png"),r0.heatmap.fish,base_width = 20,base_height = 17)
-
-# Generation length
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-gen.boxplt.6 <- ggplot(pop.dam.all.6) +
-                            geom_boxplot(aes(y=gen.len.opt,interaction(group,Stock.no.species),color=group))  + 
-                            scale_x_discrete(NULL, guide = "axis_nested") +
-                            scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
-                             facet_manual(vars(G.Species),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"),gen.boxplt.6,base_width = 19,base_height = 15)
-
-# Then the generation length for others.
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-gen.boxplt.others <- ggplot(pop.dam.all.others) +
-                            geom_boxplot(aes(y=gen.len.opt,interaction(group,G.Species.short),color=group))  + 
-                            scale_x_discrete(NULL, guide = "axis_nested") +
-                            scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
-                            facet_manual(vars(Area.long),design=mat,scales='free')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"),gen.boxplt.others,base_width = 15,base_height = 10)
-
-gen.heatmap.ne <- ggplot(pop.dam |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
-                                              xlab("") + ylab("")+  
-                                              facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                              geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-gen.heatmap.nw <- ggplot(pop.dam |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-gen.heatmap.pac <- ggplot(pop.dam |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
-                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-gen.heatmap <- cowplot::plot_grid(gen.heatmap.pac,gen.heatmap.nw,gen.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_nf_",what.2.tune,".png"),gen.heatmap,base_width = 15,base_height = 10)
-
-gen.heatmap.ne.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
-                                              xlab("") + ylab("")+  
-                                              facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                              geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-gen.heatmap.nw.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-gen.heatmap.pac.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
-                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-gen.heatmap.fish <- cowplot::plot_grid(gen.heatmap.pac.fish,gen.heatmap.nw.fish,gen.heatmap.ne.fish,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_fish_",what.2.tune,".png"),gen.heatmap.fish,base_width = 15,base_height = 10)
-
-dub.time.summary <- dub.time.summary |> collapse::fsubset(year %in% 1:50) |>
-                            collapse::roworder(G.Species,LME,Area.broad) |>
-                            collapse::fmutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-dub.heatmap.gad <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Gadiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+                                    
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.45, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.pl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Pleuronectiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+                                    
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"))
-
-dub.heatmap.cl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Clupeiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.35, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.per <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Perciformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.scom <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Scombriformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2.1, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.scorp <- ggplot(dub.time.summary |> collapse::fsubset(Order %in% "Scorpaeniformes "), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + 
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.5, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap <- cowplot::plot_grid(dub.heatmap.gad,dub.heatmap.pl,dub.heatmap.cl,dub.heatmap.per,dub.heatmap.scom,dub.heatmap.scorp,
-                                  nrow = 6,rel_heights = c(39,20,11,4,3,3))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"),dub.heatmap,base_width = 20,base_height = 20)
-
-# Doubling Time Figure 1
-dub.ts.plt <- ggplot(n.dub,aes(x=years,y=count)) + 
-                    geom_line() + 
-                    geom_hline(yintercept = length(Stocks),linetype="dashed") + 
-                    xlab("") + ylab("Number of Stocks")
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_time_series_",what.2.tune,".png"),dub.ts.plt,base_width = 10,base_height = 10)
-
-# Doubling time and variability
-
-# Is there a relationship between median and sd?
-colrs.cat <- c("blue","black","orange")
-pts.cat <- 21:23
-sd.rec.plt <- ggplot(lam.sd.p.rec, aes(y=lam.no.fish.med,x=lam.no.fish.sd,color=prop.cat,group=prop.cat)) + 
-                       geom_point(size =3,aes(shape=prop.cat,fill=prop.cat)) + 
-                       geom_hline(yintercept=1,linetype="dashed") + 
-                       scale_y_continuous(name="median Lambda") + scale_x_continuous(name="standard deviation Lambda") +
-                       scale_color_manual(values=colrs.cat) + scale_fill_manual(values=colrs.cat) +  
-                       scale_shape_manual(values=pts.cat) + theme(legend.title = element_blank())
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"),sd.rec.plt,base_width = 10,base_height = 10)
-
-```
-
-```{r the-others,include=F,echo=F,message=F,warning=F}
-#             
-# 
-# dub.heatmap.cod <- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "G.
-morhua"), aes(x=year, y=Stock.no.species, fill= prop)) + xlab("") + ylab("")+                                     facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") +
-#                             geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + scale_x_continuous(labels=NULL) +
-#                             theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-#                                   legend.key.width = unit(3,'cm'))
-# 
-# dub.heatmap.herring<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "C. harengus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-# 
-# dub.heatmap.haddock<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "M. aeglefinus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.125, "cm"))
-# 
-# dub.heatmap.virens<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. virens"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.4, "cm"))
-# 
-# dub.heatmap.solea<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "S. solea"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-# 
-# dub.heatmap.platessa<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. platessa"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous() +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
-# 
-# 
-# 
-# dub.heatmap.sp6 <- cowplot::plot_grid(dub.heatmap.cod,dub.heatmap.herring,dub.heatmap.haddock,
-#                                  dub.heatmap.virens, dub.heatmap.solea,dub.heatmap.platessa,nrow = 6,rel_heights = c(14,9,8,5,5,4))
-# dub.heatmap.sp6
-# 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_sp6_",what.2.tune,".png"),dub.heatmap.sp6,base_width = 20,base_height = 17)
-# 
-# 
-# # What about a plot of the sd of lamda by stock
-# #colrs.sd <- rep(rep(c("black","blue","orange",'grey'),3),20)
-# #pty.sd <- rep(c(rep(21,4),rep(4,4),rep(9,4)),20)
-# 
-# 
-# # Same plot for the not 6 species
-# 
-# # lam.sd.other.plt <- ggplot(res.lambda.fin |> collapse::fsubset(!Species %in% six.species)) + 
-# #                                        geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
-# #                                        scale_y_log10("sd(lambda)",limits=c(0.05,1.5)) +
-# #                                        scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
-# #                                        theme(axis.text.x = element_text(angle =45,hjust=1),
-# #                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# # lam.sd.other.plt
-# 
-# 
-# 
-# 
-# # Doubling Times
-# 
-# 
-# # Generation length
-# 
-# # Main text figure!!
-# new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Area.long),color=group)) +
-#                                            #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-#                                            scale_x_discrete(NULL, guide = "axis_nested") +
-#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~G.Species,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# # The other stocks, plotting these by area
-# # Main Text FIGURE!
-# # More data
-# 
-# 
-# ################### Supplemental Figures################### Supplemental Figures################### Supplemental Figures################### Supplemental 
-# 
-# 
-# 
-# # Time series of lambdas....
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# #col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
-# pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
-# #pty <- rep(rep(c(21:23),5),20)
-# 
-# lambda.ts.plt <- ggplot(res.lambda.final.6,aes(y=lam.fish,x=year,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
-#                             geom_point(size=4) +
-#                             geom_smooth(method='gam',formula = y ~ s(x, bs = "cs", fx = TRUE, k = 5),se=F) + 
-#                             #scale_y_log10(name = "lambda") +
-#                             facet_wrap(~G.Species,scales='free_y') +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-#                             scale_fill_manual(name = "Stock",values = col.try)+
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm'))
-# #lambda.ts.plt
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_timeseries_6_",what.2.tune,".png"),lambda.ts.plt,base_width = 12,base_height = 10)
-# 
-# 
-# lambda.dec.plt <- ggplot(res.lambda.final.6,aes(y=med.lam,x=as.factor(decade))) +
-#                             geom_boxplot() + scale_y_log10()+
-#                             xlab("Decade") + ylab("Lambda") + 
-#                             geom_point(aes(x=as.factor(decade),y=lm.spec.mn),color='blue',shape=8,fill='blue')+
-#                             #scale_x_continuous(breaks=seq(1940,2020,by=10))+
-#                             geom_hline(yintercept = 1,linetype='dashed') +
-#                             facet_wrap(~G.Species,scales='free_y') 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_by_decade_6_",what.2.tune,".png"),lambda.dec.plt,base_width = 12,base_height = 12)
-# 
-#
-
-# ggplot(dd.dat) + geom_point(aes(x=prop.abund,y=lam.no.fish-1)) + xlab("Proportion of Maximum Abundance") + ylab("r (no fishing)")
-# 
-# # Density dependence by Species
-# ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
-#                                                    geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) #+
-#                                                    #scale_color_manual(values = colrs)
-# # Density dependence by stock
-# ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Stock.short,group=Stock.short)) + geom_point() + 
-#                                                    geom_smooth(method="lm",se = F) + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)", limits=c(0.4,2),
-#                                                                  breaks = seq(0.4,2,by=0.1)) +
-#                                                    theme(legend.position = 'none')
-# 
-# 
-# 
-# 
-# ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish)) + geom_point() + 
-#                                                     geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_continuous(name = "lambda (no fishing)")
-# 
-# ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + geom_point() + 
-#                                                     geom_smooth(method="lm",se=F) + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,2,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)")
-# 
-# 
-# # how about our big 6
-# colrs <- c("blue","black","firebrick2","orange",'grey50','grey90')
-# ggplot(dd.dat.six,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
-#                                                     geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) +
-#                                                    scale_color_manual(values = colrs)
-# 
-# 
-# ggplot(dd.dat.six.no.bigs,aes(x=prop.abund,y=lam.no.fish-1,color=Species,group=Species)) + geom_point() + 
-#                                                     geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 0,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_continuous(name = "r (no fishing)", breaks = seq(-1,1,by=0.2)) +
-#                                                    scale_color_manual(values = colrs)
-
-# Other things I did just randomly scattered here
-
-# 
-# #hmm <- merge(tst,res.lambda.final.6,by="Stock")
-# plot(res.lambda.fin$lam.fish.med ~ res.lambda.fin$lam.fish.mn)
-# # So this is lambda with fishing included
-# lambda.plt <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.no.fish,x=Stock.no.species))  + 
-#                                            geom_point(aes(y=lam.no.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~G.Species,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_no_fishing_6_",what.2.tune,".png"),lambda.plt,base_width = 12,base_height = 10)
-# 
-# # With fishing
-# lambda.plt.fish <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.fish,x=Stock.no.species))  + 
-#                                            geom_point(aes(y=lam.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~G.Species,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_with_fishing_6_",what.2.tune,".png"),lambda.plt.fish,base_width = 12,base_height = 10)
-# 
-# 
-# 
-# new.lam.plt <- ggplot(res.lambda.fin.long) + geom_boxplot(aes(y=lambda,interaction(group,Order),color=group)) +
-#                                            #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-#                                            scale_x_discrete(NULL, guide = "axis_nested") +
-#                                            #xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            #geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~Area.long,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# 
-# # The final option I have is to do what I did before and use the bin props
-# We can then do a much more ANOVA kinda analysis, drat this doesn't converge..., estimate the 
-#mod.dd.bins.stock <- glmer(lam.no.fish ~ prop.bin + (1+prop.bin|Stock),data=dd.dat,family=gaussian(link='log'))
-# so go to lmer and log transform... and it is a singular fit
-#mod.dd.bins.stock <- lmer(lam.no.fish ~ prop.bin + (1+prop.bin|Stock),data=dd.dat)
-# So is an intercept model of any real use?
-# mod.dd.bins.stock <- lmer(log(lam.no.fish) ~ prop.bin + (1+prop.bin|Stock.short),data=dd.dat)
-# # A non-random effect model does work with the interaction... I'd much rather lmer....
-# #mod.dd.bins.stock <- lm(lam.no.fish ~ prop.bin*Stock,data=dd.dat)
-# summary(mod.dd.bins.stock)
-# #Residuals, nah, still suck, just some crazy outliers...
-# plot(mod.dd.bins.stock)
-# # Normality = terrible...
-# qqnorm(residuals(mod.dd.bins.stock))
-# qqline(residuals(mod.dd.bins.stock))
-# # So we can predict this ANOVA thing...
-# pred.dd.stock.bins <- expand.grid(prop.bin = unique(dd.dat$prop.bin),
-#                                          #Species=unique(dd.dat$Species),
-#                                          Stock.short=unique(dd.dat$Stock.short))
-# tmp <- predict(mod.dd.bins.stock, pred.dd.stock.bins, type = 'response', se.fit = TRUE) 
-# pred.dd.stock.bins$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.stock.bins$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.stock.bins$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Now to do fun things I need the meta data on the pred dataframe
-# pred.dd.stock.bins <- left_join(pred.dd.stock.bins,meta.sub,by="Stock.short")
-# # Now a problem here is that this includes estimates for bins in which we don't have data.
-# # So we do want to get rid of those
-# real.bins <- unique(paste(dd.dat$Stock.short,"_",dd.dat$prop.bin))
-# # All the bins in the predict object with same names same name...
-# pred.dd.stock.bins$bin.combos <- paste(pred.dd.stock.bins$Stock.short,"_",pred.dd.stock.bins$prop.bin)
-# # Now toss all the predicted bins without data.
-# pred.dd.stock.bins <- pred.dd.stock.bins |> collapse::fsubset(bin.combos %in% real.bins)
-# 
-# # By region
-# cols.1 <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
-# #col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
-# pty.1 <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
-# ggplot(pred.dd.stock.bins,aes(x=prop.bin,y=lam.no.fish,group=Stock.short,color=G.Species)) + 
-#                                 geom_point(aes(shape=G.Species),size=2) + geom_line()  + xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 facet_wrap(~Area.long)  +
-#                                 scale_shape_manual(values=pty.1) +
-#                                 scale_color_manual(values = cols.1) + 
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-# 
-# # By Species
-# ggplot(pred.dd.stock.bins,aes(x=prop.bin,y=lam.no.fish,group=Stock.short,color=Area.long)) + 
-#                                 geom_point(aes(shape=Area.long)) + geom_line()  + xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 facet_wrap(~Order)  +
-#                                 scale_shape_manual(values=pty.1) +
-#                                 scale_color_manual(values = cols.1) + 
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-# 
-# # No fish vs fish lambda, note that DD is weaker when we account for fishing, that seems a fun result to talk about!
-# 
-# mod.dd.overall.gam.nf <- lm(log(lam.no.fish) ~ (prop.abund),data=dd.dat)
-# mod.dd.overall.gam.fish <- lm(log(lam.fish) ~ (prop.abund),data=dd.dat)
-# 
-# 
-# pred.dd.overall.bins.nf <- data.frame(prop.abund = seq(0,1,length.out=500),group = "F = 0")
-# pred.dd.overall.bins.fish <- data.frame(prop.abund = seq(0,1,length.out=500),group = "F > 0")
-# tmp <- predict(mod.dd.overall.gam.nf, pred.dd.overall.bins, type = 'response', se.fit = TRUE) 
-# tmp.fish <- predict(mod.dd.overall.gam.fish, pred.dd.overall.bins, type = 'response', se.fit = TRUE) 
-# pred.dd.overall.bins.nf$lam   <- exp(tmp$fit)
-# pred.dd.overall.bins.nf$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.overall.bins.nf$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# 
-# pred.dd.overall.bins.fish$lam   <- exp(tmp.fish$fit)
-# pred.dd.overall.bins.fish$lower <- exp(tmp.fish$fit - 1.96 * tmp.fish$se.fit)
-# pred.dd.overall.bins.fish$upper <- exp(tmp.fish$fit + 1.96 * tmp.fish$se.fit)
-# 
-# pred.dd.overall <- rbind(pred.dd.overall.bins.fish,pred.dd.overall.bins.nf)
-# 
-# ggplot(pred.dd.overall,aes(y=lam,x=prop.abund,group=group,color=group)) + 
-#                                                   geom_line(linewidth=2) + 
-#                                                   geom_ribbon(aes(ymin=lower,ymax=upper),alpha=0.2) + 
-#                                                   geom_hline(yintercept=1,linetype='dashed') + 
-#                                                   xlab("Proportion of Maximum Abundance") + ylab("Lambda")
-# 
-# # OK, so if we compare the 40-60 bin with the 80-100 bin we should see the lambda's in the 40-60 bin are higher...
-# 
-# res.40.60 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("40-60%"))
-# names(res.40.60)[names(res.40.60) == 'lam.no.fish'] <- "lam.40.60"
-# res.80.100 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("80-100%"))
-# names(res.80.100)[names(res.80.100) == 'lam.no.fish'] <- "lam.80.100"
-# 
-# tst <- left_join(res.40.60,res.80.100, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.40.60 - tst$lam.80.100
-# 
-# hist(tst$diff)
-# 
-# res.lt.10 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("< 10%"))
-# names(res.lt.10)[names(res.lt.10) == 'lam.no.fish'] <- "lam.lt.10"
-# 
-# tst <- left_join(res.40.60,res.lt.10, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.lt.10 - tst$lam.40.60
-# 
-# hist(tst$diff)
-# 
-# res.10.20 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("10-20%"))
-# names(res.10.20)[names(res.10.20) == 'lam.no.fish'] <- "lam.10.20"
-# 
-# tst <- left_join(res.40.60,res.10.20, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.10.20 - tst$lam.40.60
-# 
-# hist(tst$diff)
-# 
-# 
-# res.20.30 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("20-30%"))
-# names(res.20.30)[names(res.20.30) == 'lam.no.fish'] <- "lam.20.30"
-# 
-# tst <- left_join(res.40.60,res.20.30, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.20.30 - tst$lam.40.60
-# 
-# hist(tst$diff)
-# 
-# res.30.40 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("30-40%"))
-# names(res.30.40)[names(res.30.40) == 'lam.no.fish'] <- "lam.30.40"
-# 
-# tst <- left_join(res.40.60,res.30.40, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.30.40 - tst$lam.40.60
-# 
-# hist(tst$diff)
-
-# 
-# 
-# dd.dat.no.bigs <- dd.dat |> collapse::fsubset(lam.no.fish < 2)
-# dd.dat.six.no.bigs <- dd.dat.six |> collapse::fsubset(lam.no.fish < 2)
-# just.bigs <- dd.dat  |> collapse::fsubset(lam.no.fish > 2) 
-# sum(table(just.bigs$Stock.short)) # 48 of 68 are Haddock or cod. 13 of remaining 20 are small low trophic species
-# 
-# dd.dat$lam.ratio <- dd.dat$lam.org.no.fish/dd.dat$lam.no.fish
-# dd.dat$lam.ratio.z <- dd.dat$lam.org.fish/dd.dat$lam.fish
-# So the original lambda tended to be somewhere between 7 and 14% higher, depending on me(di)an choice.
-# Could be way off in some years for a few species (Haddock, Cod, Sand lance, horse makerel, pilchard(sardine)... interesting... )
-# summary(dd.dat$lam.ratio)
-# summary(dd.dat$lam.ratio.z)
-# ggplot(dd.dat,aes(y=lam.ratio,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
-# ggplot(dd.dat,aes(y=lam.ratio.z,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
-
-# Playing around to look at explanations for what we see, looked by LME, low and high stocks, but no smoking guns!
-# low.stocks <- unique(dd.dat$Stock.short[dd.dat$prop.abund <= 0.1])
-# dd.lows <- dd.dat |> collapse::fsubset(Stock.short %in% low.stocks)
-# dd.highs <- dd.dat |> collapse::fsubset(!Stock.short %in% low.stocks)
-# mod.dd.stock.gam.lows <- gam(log(lam.no.fish) ~ s(prop.abund,k=4) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.lows )
-# mod.dd.stock.gam.highs <- gam(log(lam.no.fish) ~ s(prop.abund,k=4) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.highs )
-# 
-# pred.dd.stock.gam.tst <- expand.grid(prop.abund = seq(0, 1, length.out = 50),
-#                                          Stock.short = c("Overall",unique(dd.highs$Stock.short)))
-# 
-# tmp <- predict(mod.dd.stock.gam.highs, pred.dd.stock.gam.tst, type = 'response', se.fit = TRUE) 
-# pred.dd.stock.gam.tst$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.stock.gam.tst$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.stock.gam.tst$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# 
-# ggplot(pred.dd.stock.gam.tst |> collapse::fsubset(Stock.short=='Overall'), aes(x=prop.abund,y=lam.no.fish)) + 
-#                                 geom_point(data = hmm,aes(x=prop.abund,y=lam.no.fish),size=2,alpha=0.1) +  
-#                                 geom_line(color='blue',linewidth=2) + 
-#                                 xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-# 
-# 
-# ggplot(pred.dd.stock.gam.tst,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short,shape=Stock.short)) + 
-#                                 geom_line() + 
-#                                 #geom_point(data = thin.pred,size=2) +  
-#                                 xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 #facet_wrap(~Area.long)  +
-#                                 #scale_shape_manual(values=pty.gam) +
-#                                 #scale_color_manual(values = cols.gam) + 
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-
-# Is there any density dependence in fishing mortality??
-# dd.dat$mu <- dd.dat$removals/dd.dat$vpa.abund
-# dd.dat$fm <- -log(1-dd.dat$mu)
-# 
-# ggplot(dd.dat , aes(x=prop.abund,y=fm)) + 
-#                                 geom_point() + 
-#                                 geom_smooth(method = 'gam') + 
-#                                 scale_x_continuous(name="Proportion of Maximum Abundance") +
-#                                 scale_y__continuous(name = "Fishing Mortality (instantaneous)")
-# 
-# 
-# qqnorm(log(dd.dat$mu))
-# qqline(log(dd.dat$mu))
-# hist(log(dd.dat$mu))
-# 
-# fm.mod <- lm(log(fm)~prop.abund,data=dd.dat)
-# par(mfrow=c(2,2))
-# plot(fm.mod)
-# par(mfrow=c(1,1))
-
-# windows(11,11)
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
-
-# 
-# r0.ts.plt <- ggplot(pop.dam.6,aes(y=R0.opt,x=cohort,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) + 
-#                             geom_line(size=2)  + geom_point(size=4) +
-#                             scale_y_log10(name = "Lifetime Reproductive Output") +
-#                             facet_wrap(~G.Species) +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-#                             scale_fill_manual(name = "Stock",values = col.try)+
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
-# r0.ts.plt
-# 
-# save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_6.png",r0.ts.plt,base_width = 30,base_height = 12)
-# 
-# r0.boxplt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
-#                             facet_wrap(~G.Species,scales = 'free')+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none')
-# r0.boxplt
-
-# 
-# windows(11,11)
-# ggplot(pop.dam) + geom_boxplot(aes(y=gen.len.opt,x=Species)) + facet_wrap(~LME,scales='free_x') +
-#                   ylab("Generation Length (years)") + theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# windows(11,11)
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# lty <- rep(c(rep(1,5),rep(2,5),rep(4,5)),20)
-# 
-# gen.ts.plt <- ggplot(pop.dam.6,aes(y=gen.len.opt,x=cohort,group=Stock.short,color=Stock.short,linetype = Stock.short)) + 
-#                             geom_line(size=2)  + 
-#                             scale_y_log10(name = "Generation Length") +
-#                             facet_wrap(~G.Species) +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_linetype_manual(name = "Stock",values = lty) +
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
-# gen.ts.plt
-# save_plot("D:/Github/ICM/Figures/tuned/Gen_time_series_6.png",gen.ts.plt,base_width = 20,base_height = 12)
-
-# 
-# ggplot(for.tunes) + geom_jitter(aes(y=lambda,x=Species,group=Stock.short,color=Stock.short)) + 
-#                     scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10)) +
-#                             theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# ggplot(for.tunes) + geom_jitter(aes(y=lambda.vpa.init,x=Species)) + scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))
-# 
-# unique(for.tunes$Species)
-# windows(11,11)
-# 
-# ggplot(for.tunes) + geom_density(aes(lambda,group=Species,color=Species,fill=Species),alpha = 0.2) + scale_x_continuous(breaks = c(0,0.5,1,2,5,10))
-# 
-# 
-# #options(scipen=999)
-# r0.plt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.05,0.1,0.5,1,5,10,50,100),minor_breaks = NULL) + 
-#                             facet_wrap(~Species,scales = 'free')+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1))
-# save_plot("D:/Github/ICM/Figures/tuned/R0_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
-# 
-# 
-# 
-# vickis.cols <- sort(rep(c( "#172582",  "#F8DC91", "#FBB891", "#FB6A01", "#B80000"),3))
-# linetypes <- rep(c(1,2,4),5)
-# 
-# windows(11,11)
-# cod.r0.ts.plt <- ggplot(pop.dam |> collapse::fsubset(Species == 'morhua')) + geom_line(aes(y=R0.opt,x=cohort,group=Area,color=Area,linetype=Area),size=1.5)  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output", breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
-#                             scale_color_manual(values = vickis.cols) +
-#                             scale_linetype_manual(values = linetypes) +
-#                             theme(legend.key.width  = unit(2, "cm"))
-# cod.r0.ts.plt
-# #save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
-# 
-# 
-# windows(11,11)
-# ggplot(pop.dam |> collapse::fsubset(Species =="morhua")) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
-#                                                         scale_y_log10(name = "Lifetime Reproductive Output",breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) +
-#                                                         theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# # Missing catch questions
-# # first did we do much to the Fecundity term to get here
-# quantile(for.tunes$mean.fec/for.tunes$mean.vpa.fec,probs=seq(0.01,1,0.01),na.rm=T)
-# 
-# quantile((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init,probs=seq(0.01,1,0.01),na.rm=T)
-# quantile((for.tunes$mean.nm-for.tunes$mean.vpa.nm)/for.tunes$mean.vpa.nm,probs=seq(0.01,1,0.01),na.rm=T)
-# 
-# for.tunes$excess.catch <- for.tunes$removals-for.tunes$removals.init
-# for.tunes$per.excess.catch <- 100*((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init)
-# 
-# windows(11,11)
-# bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Species)) + 
-#                                    ylab("Adjustment to catch (%)") +
-#                                    theme(axis.text.x = element_text(angle=45,hjust = 1))
-#                                    
-# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_species.png",bycatch.plt,base_width = 8,base_height = 8)
-#                                    
-# bycatch.plt.cod <- ggplot(for.tunes |> collapse::fsubset(Species == 'morhua')) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + 
-#                                                                               ylab("Adjustment to catch (%)") +
-#                                                                               theme(axis.text.x = element_text(angle=45,hjust = 1))
-#                                                                               
-# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_cod_stock.png",bycatch.plt.cod,base_width = 8,base_height = 8)
-# 
-# # bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + facet_wrap(~Species,scales = 'free_x')
-# #                                    ylab("Adjustment to catch (%)") +
-# #                                    theme(axis.text.x = element_text(angle=45,hjust = 1))
-# # bycatch.plt                                   
-#
-
-# Doubling time for the rest of the stocks...
-
-# dub.heatmap.no.6 <- ggplot(dub.time.summary |> collapse::fsubset(!Species %in% six.species), aes(x=year, y=Stock.short, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               #facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + 
-#                               scale_x_continuous() +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
-```
-
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-
-```{r failed-models}
-
-# A density dependence model, start simple and build...
-# mod.dd.base <- lm(log(lam.no.fish) ~ prop.abund,data=dd.dat)
-# summary(mod.dd.base)
-# 
-# mod.dd.base.fish <- lm(log(lam.fish) ~ prop.abund,data=dd.dat)
-# summary(mod.dd.base.fish)
-# #ggplot(dd.dat, aes(y = lam.no.fish,x=prop.abund)) + geom_point() + geom_smooth(method = 'lm') + scale_y_log10() + geom_hline(yintercept = 1,color='firebrick2',linetype='dashed',linewidth=2)
-# 
-# 
-# # Residuals are nowhere near normal, the fit isn't a disaster but def have the old trumpet shape happening
-# par(mfrow=c(2,2))
-# plot(mod.dd.base)
-# par(mfrow=c(1,1))
-# # This mostly represents the above model...
-# ggplot(dd.dat, aes(y = lam.no.fish,x=prop.abund)) + 
-#                   geom_point() + 
-#                   geom_smooth(method = 'lm') + scale_y_log10() +
-#                   geom_hline(yintercept = 1,color='firebrick2',linetype='dashed',linewidth=2)
-# # What happens with a gam?
-# mod.dd.gam.base <- gam(log(lam.no.fish) ~ s(prop.abund),data=dd.dat)
-# summary(mod.dd.gam.base)
-# # Still see that the residuals are higher at low values
-# plot(residuals(mod.dd.gam.base) ~ dd.dat$prop.abund)
-# # not great...
-# plot(residuals(mod.dd.gam.base) ~ fitted(mod.dd.gam.base))
-# # What's the fit look like?
-# pred.dd.gam.base <- data.frame(prop.abund = seq(0, 1, length.out = 1000))
-# tmp <- predict(mod.dd.gam.base, dd.gam.base.pred, type = 'response', se.fit = TRUE) 
-# 
-# pred.dd.gam.base$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.gam.base$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.gam.base$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# 
-# # So here's the game fit, I thnk it does do an ok job of showing that no much is happening below maybe 0.3, but then
-# # below 0.15 it starts increasing, suggesting general compensation, but we know the really high values matter here and are
-# # limited to a subset of the stocks, anywho we know the residuals suck, so moving on...
-# ggplot(dd.dat,aes(y=lam.no.fish,x=prop.abund)) + 
-#                   geom_point() + scale_y_log10() +
-#                   geom_ribbon(data=pred.dd.gam.base,aes(ymin=lower,ymax=upper,x=prop.abund),alpha=0.4) +
-#                   geom_line(data = pred.dd.gam.base,aes(y=lam.no.fish, x= prop.abund))
-#     
-# 
-# # What if we did a glm, Gamma with log-link seems a natural thing to try...
-# mod.dd.glm.gamma <- glm(lam.no.fish ~ prop.abund,data=dd.dat,family = Gamma(link='log'))
-# # What's that done...
-# summary(mod.dd.glm.gamma)
-# # Still some pretty gross shit going on here...
-# par(mfrow=c(2,2))
-# plot(mod.dd.glm.gamma)
-# par(mfrow=c(1,1))
-# # Now plot it...
-# pred.dd.glm.base <- data.frame(prop.abund = seq(0, 1, length.out = 1000))
-# tmp <- predict(mod.dd.glm.gamma, dd.gam.base.pred, type = 'response', se.fit = TRUE) 
-# 
-# pred.dd.glm.base$lam.no.fish   <- (tmp$fit)
-# pred.dd.glm.base$lower <- (tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.glm.base$upper <- (tmp$fit + 1.96 * tmp$se.fit)
-# # Pretty similar, though I think on the linear scale we see the 'rate' may be decreasing as we approach 0
-# # But still not a good model given the above
-# ggplot(dd.dat,aes(y=lam.no.fish,x=prop.abund)) + 
-#                   geom_point() + scale_y_log10() +
-#                   geom_ribbon(data=pred.dd.glm.base,aes(ymin=lower,ymax=upper,x=prop.abund),alpha=0.4) +
-#                   geom_line(data = pred.dd.glm.base,aes(y=lam.no.fish, x= prop.abund))
-#     
-# # Now what if we account for species in these and get an estimate for each species. 
-# # I think this should be done as a random effect, we'll start with linear mixed models and see what happens...
-# 
-# mod.dd.species.re <- lmer(log(lam.no.fish) ~ prop.abund + (1| Species),data=dd.dat)
-# # So that seems reasonable...
-# summary(mod.dd.species.re)
-# #Residuals are still pretty cranky
-# plot(mod.dd.species.re)
-# # Normality still a hot mess
-# qqnorm(residuals(mod.dd.species.re))
-# qqline(residuals(mod.dd.species.re))
-# # draw some lines...
-# pred.dd.lmm.species <- expand.grid(prop.abund = seq(0, 1, length.out = 100),Species=unique(dd.dat$Species))
-# tmp <- predict(mod.dd.species.re, pred.dd.lmm.species, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.species$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.lmm.species$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.species$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.species,aes(x=prop.abund,y=lam.no.fish,group=Species,color=Species)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Species, color=Species)) +
-#                                 scale_y_log10()
-# 
-# # We could also allow the slope to vary by species, might get a bit better, but really won't do the trick...
-# mod.dd.species.slope.re <- lmer(log(lam.no.fish) ~ prop.abund + (1+ prop.abund| Species),data=dd.dat)
-# summary(mod.dd.species.slope.re)
-# #Residuals are still pretty cranky
-# plot(mod.dd.species.slope.re)
-# # Normality still a hot mess
-# qqnorm(residuals(mod.dd.species.slope.re))
-# qqline(residuals(mod.dd.species.slope.re))
-# # draw some lines...
-# pred.dd.lmm.species.slope <- expand.grid(prop.abund = seq(0, 1, length.out = 100),Species=unique(dd.dat$Species))
-# tmp <- predict(mod.dd.species.slope.re, pred.dd.lmm.species.slope, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.species.slope$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.lmm.species.slope$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.species.slope$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.species.slope,aes(x=prop.abund,y=lam.no.fish,group=Species,color=Species)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Species, color=Species)) +
-#                                 scale_y_log10()
-# # Curious what species have high slopes.. Dubious and Esmarkii (North Sea sand lance and mackerel)
-# ranef(mod.dd.species.slope.re)
-# 
-# # So so what if we let the slopes vary by stock
-# mod.dd.stock.re <- lmer(log(lam.no.fish) ~ prop.abund +  (1+ prop.abund | Stock.short),data=dd.dat)
-# summary(mod.dd.stock.re)
-# #Residuals are slightly better I think but still really suck
-# plot(mod.dd.stock.re)
-# # Normality = no
-# qqnorm(residuals(mod.dd.stock.re))
-# qqline(residuals(mod.dd.stock.re))
-# # What's it look like?
-# pred.dd.lmm.stock <- expand.grid(prop.abund = seq(0, 1, length.out = 100),
-#                                          #Species=unique(dd.dat$Species),
-#                                          Stock.short=unique(dd.dat$Stock.short))
-# tmp <- predict(mod.dd.stock.re, pred.dd.lmm.stock, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.stock$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.lmm.stock$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.stock$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.stock,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Stock.short, color=Stock.short)) +
-#                                 scale_y_log10()
-# 
-# # Curious what stocks have high slopes.. Dubious and Esmarkii (North Sea sand lance and mackerel), NS Haddock and Irish Sea Haddock 
-# ranef(mod.dd.stock.re)
-# 
-# 
-# 
-# 
-# # OK, so this all still sucks, wonder if a glmer and gamma would get us anywhere... not really.... 
-# # Tried many variants on the glmer and they all land in the same lousy spot.
-# mod.dd.stock.gamma.re <- glmer(lam.no.fish ~ prop.abund +  (1+ prop.abund | Stock.short),data=dd.dat,family=Gamma(link='log'))
-# # OK...
-# summary(mod.dd.stock.gamma.re)
-# #Residuals, nah, still suck, just some crazy outliers...
-# plot(mod.dd.stock.gamma.re)
-# # Normality = no
-# qqnorm(residuals(mod.dd.stock.gamma.re))
-# qqline(residuals(mod.dd.stock.gamma.re))
-# # And the plot...
-# pred.dd.lmm.stock.gamma <- expand.grid(prop.abund = seq(0, 1, length.out = 100),
-#                                          #Species=unique(dd.dat$Species),
-#                                          Stock.short=unique(dd.dat$Stock.short))
-# tmp <- predict(mod.dd.stock.gamma.re, pred.dd.lmm.stock.gamma, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.stock.gamma$lam.no.fish   <- (tmp$fit)
-# pred.dd.lmm.stock.gamma$lower <- (tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.stock.gamma$upper <- (tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.stock.gamma,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Stock.short, color=Stock.short)) +
-#                                 scale_y_log10()
-# # None of the above really work at all....
-
-```

### 2024-05-21 Drafts/Paper_1/tmp-08-figures.Rmd
mid-edit update

--- 2024-05-10 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
@@
 ---
-output: word_document
+output:
+  pdf_document:
+    fig_caption: yes
+    extra_dependencies: float
+linkcolor: blue
+header-includes: \usepackage{float}
 editor_options:
@@
 
-```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4,include=F,message=F}
-
-if(load.results==F)
-{
-  Stocks <- ASR.long |> 
-                      collapse::fsubset(!is.na(value)) |>
-                      collapse::fgroup_by(Stock, type) |>
-                      collapse::fsummarize(count=length(unique(value))) |>
-                      collapse::fgroup_by(Stock) |>
-                      collapse::fsummarize(types=length(unique(type))) |>
-                      collapse::fsubset(types==5) |>
-                      collapse::fselect(Stock)
-
-  ASR.tmp <- ASR.long 
-  ASR.tmp$age <- as.numeric(ASR.tmp$age)
-  ASR.stocks <- ASR.tmp |> 
-                          collapse::fsubset(Stock %in% Stocks$Stock) |>
-                          collapse::fsubset(!is.na(value)) |>
-                          collapse::roworder(Stock, Year, type, age)
-
-  # print(Stocks)
-  Stocks <- Stocks$Stock
-
-  # Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
-  #Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
-  # Esmarki doesn't work great as it is assessed using a quarterly model.
-  #Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
-  #i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
-  years.tmp <- NULL
-  pnm.tmp <- NULL
-  waa.tmp <- NULL
-  ages.tmp <- NULL
-  rem.tmp <- NULL
-  mx.tmp <- NULL
-  NE.tmp <- NULL
-  vpa.tmp <- NULL
-  am.tmp <- NULL
-  #mr.tmp <- NULL
-  abund.tmp <- NULL
-  full.abund.tmp <- NULL
-  full.rem.tmp <- NULL
-  fs.tmp <- NULL
-  for(i in Stocks)
-  {
-  print(i)
-  ASR.sub <- ASR.long |>
-    collapse::fselect(Year, Stock, type, age, value) |>
-    collapse::fsubset(Stock==i)
-
-    # Dropping the first 7 years as the 8 year olds are all missing
-  if(i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR.sub <- ASR.sub |> collapse::fsubset(Year >= 1972)
-  # maxage <- max(as.numeric(ASR.sub$age[!is.na(ASR.sub$value)]))
-  # maxYear <- max(ASR.sub$Year[!is.na(ASR.sub$value)])
-  # minYear <- min(ASR.sub$Year[!is.na(ASR.sub$value)])
-  # forplot <- ASR.sub[as.numeric(ASR.sub$age) < (maxage+1) & ASR.sub$Year %in% minYear:maxYear,]
-  # 
-  # # summary plots
-  # print(ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
-  #         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
-  #         theme_bw() + 
-  #         ggtitle(i)
-  # )
-
-  age.mat <- ASR.sub |> collapse::fsubset(type=="AM") |> dplyr::rename(AM=value) |> collapse::fselect(-type)
-  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
-  # in case that changes later...
-  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
-  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
-  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
-  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
-  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
-  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0
-
-  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
-  nat.mort <-  ASR.sub |> collapse::fsubset(type=="NM") |> dplyr::rename(NM=value) |> collapse::fselect(-type)
-  abund <- ASR.sub |> collapse::fsubset(type=="Num") |> dplyr::rename(Num=value) |> collapse::fselect(-type)
-  weight.age <- ASR.sub |> collapse::fsubset(type=="WA") |> dplyr::rename(WA=value) |> collapse::fselect(-type)
-  if(i == Stocks[30]) weight.age$WA <- weight.age$WA/1000
-  removals <- ASR.sub |> collapse::fsubset(type=="Catch") |> dplyr::rename(Catch=value) |> collapse::fselect(-type)
-
-  data <- age.mat |>
-    full_join(nat.mort) |>
-    full_join(abund) |>
-    full_join(weight.age) |>
-    full_join(removals)
-
-  # Aahh??  Is this NA dropping useful data, needed to quick fix the age at maturity data...
-  data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
-  data <- data[data$available==T,]
-
-  # Tidy up the data for input...
-  data$prop.nat.mort <- 1-exp(-data$NM)
-  #prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))] <- 1-exp(-prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))])
-
-  rem <- data |> collapse::fgroup_by(Year) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
-  #rem <- data |> dplyr::group_by(Year,.drop=F) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
-
-  # Never run, so not doing anything.
-  # missing_rem<- NULL
-  # if(any(is.na(rem$rem))) 
-  # {
-  #   missing_rem <- unique(data$Year)[which(is.na(rem$rem))]
-  #   rem$rem[is.na(rem$rem)] <- median(rem$rem, na.rm=T)
-  # }
-
-  #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
-  years <- data |> dplyr::pull(Year) |> unique() |> sort()
-
-  N.end <- sum(data[data$Year==max(years),]$Num)
-  vpa.abund <- data |> dplyr::group_by(Year) |> dplyr::summarize(vpa=sum(Num,na.rm=T)) |> pull(vpa)
-
-  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
-  #minage
-  minage <- min(as.numeric(data$age))
-  #maxage
-  maxage <- max(as.numeric(data$age))
-  #recruits
-  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
-  #ssn
-  data$ssn <- data$Num * data$AM
-  #ssb
-  data$ssb <- data$ssn * data$WA #I need to figure out how to line this up with the number of recruits for the right years in the data object.... got it right for the overall r.p.ssb below.
-  #tot.ssb
-  annual <- data |> group_by(Year) |> summarize(tot.ssb = sum(ssb)) |> left_join(annual)
-
-  #tst <- data |> group_by(Year) |> summarize(tot.ssn = sum(ssn)) |> left_join(annual)
-
-  #r.p.ssb This needs to be offset by the age of recruits. So here's my lining this up logic.  For age 0, we get
-  # the recruit and SSB estimates from the same survey, thus these age 0 recruits will have been produced by the SSB in the previous year...
-  # So the R in 1970 were produced by SSB in 1969 when min age =0
-  # If min.age = 1 then R in 1970 is produced by SSB in 1968... and so on.
-  # FIX 1 "Recruit year" = SSB year + min.age + 1 (or min.age +2 as SSB.year is the first column)
-  # Now for RPS there's another wrinkle because of this, because our model is N(1970) = lambda * N(1969) and lambda is made up of lx and mx
-  # so if the recruits show up in 1970, the fecundity term that gets us there (irrespective of the age offset) has to be for 1969, becuase
-  # that gets us to the babies that show up in 1970
-  # FIX 2 So "RPS year, recs.per.age year, and mx year" = SSB year + min.age
-  # I believe this to be correct, but we all need to discuss this to make sure the logic holds.
-  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+2):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage-1)],NA)
-  # recs.per.age
-  data <- left_join(data, annual)
-  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
-  tmp <- NULL
-  for(j in 1:length(years))
-  {
-    tst <- data|> collapse::fsubset(Year == years[j]) |> collapse::fselect(ssb,ssn,Year,age)
-    tst$Year <- tst$Year + minage # We want this to line up the the RPS year, so just adding minage here.
-    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
-    tmp[[j]] <- tst
-  }
-  # Unpack the list
-  ssb.off <- do.call('rbind',tmp)
-  # And merge it with the data object
-  data <- left_join(data,ssb.off,by=c("Year","age"))
-  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
-  # mx
-  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
-  # No longer dividing by 2 because we should really divide recruits and ssn by 2 to be female only, but that's pointless so we roll along with this.
-  data$mx <- data$recs.per.age/data$ssn.offset # if(grepl("males",i)) 
-  #if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
-  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
-  # Easier to remove the years where we don't have recs.per.age...
-  #data <- data |> collapse::fsubset(Year %in% years[(minage+1):length(years)])
-
-  age.mat <- data |> collapse::fselect("Year", "age", "AM") |> 
-                     pivot_wider(names_from=age, values_from = AM) |> collapse::fselect(-Year)
-  prop.nat.mort <- data |> collapse::fselect("Year", "age", "prop.nat.mort") |> 
-                            pivot_wider(names_from=age, values_from = prop.nat.mort) |> 
-                            collapse::fselect(-Year) |> as.data.frame()
-
-  weight.age <- data |> collapse::fselect("Year", "age", "WA") |> pivot_wider(names_from=age, values_from = WA) |> collapse::fselect(-Year)
-  mx <- data |> collapse::fselect("Year", "age", "mx") |> 
-                 pivot_wider(names_from=age, values_from = mx) |> 
-                 collapse::fselect(-Year) |> as.data.frame()
-  # Get the abundance matrix
-  abund.age <- data |> collapse::fselect("Year", "age", "Num") |> 
-                        pivot_wider(names_from=age, values_from = Num) |> 
-                        collapse::fselect(-Year) |> as.data.frame()
-
-  # Now we can save out the catch and get an instantaneous F
-    data$Catch[is.na(data$Catch)] <- 0
-    data$Exp <- data$Catch/data$Num 
-    # If it is exactly 1 that leads to an Inf, which is annoying, so make it 1.1 and fix it with the rest below
-    data$Exp[data$Exp == 1] <- 1.1
-    # And make this an F
-    data$Fs <- -log(1-data$Exp)
-    if(any(is.na(data$Fs)))
-    {
-      fixers <- which(is.na(data$Fs))
-      print(paste0("Had to replace ",length(fixers), ' exploitation rates for stock ',i))
-      for(f in fixers)
-      {
-        yr <- data$Year[f]
-        fs <- max(data$Fs[data$Year == yr],na.rm=T)
-        data$Fs[f] <- fs
-        data$Exp[f] <- 1-exp(-fs)
-      }
-    }
-
-  full.rems <- data |> collapse::fselect("Year", "age", "Catch") |> pivot_wider(names_from=age, values_from = Catch) |> collapse::fselect(-Year)
-  full.Fs <-  data |> collapse::fselect("Year", "age", "Fs") |> pivot_wider(names_from=age, values_from = Fs) |> collapse::fselect(-Year)
-
-    if(i == "DFO_2J3KL_Gadus_morhua")
-    {
-      age.mat[,8:10] <- 1
-      prop.nat.mort[,8:10] <- prop.nat.mort[,7]
-      weight.age[12:14,9:10] <- weight.age[12:14,8]
-      weight.age[15,10] <- weight.age[15,9]
-      mx[12:16,9:10] <- mx[12:16,8]
-      mx[17,10] <- mx[17,9]
-      full.Fs[12:14,9:10] <- full.Fs[12:14,8]
-      full.Fs[15,10] <- full.Fs[15,9]
-      abund.age[12:14,9:10] <- abund.age[12:14,8]
-      abund.age[15,10] <- abund.age[15,9]
-      # I could calculate, but this will get us to the same place...
-      full.rems[12:14,9:10] <- full.rems[12:14,8]
-      full.rems[15,10] <- full.rems[15,9]
-    }
-
-    if(i == "DFO_4T-Spring_Clupea_harengus")
-    {
-      age.mat[6:7,10] <- 1
-      prop.nat.mort[6:7,10] <- prop.nat.mort[6:7,9]
-      weight.age[6:7,10] <- weight.age[6:7,9]
-      mx[6:9,10] <- mx[6:9,9]
-      full.Fs[6:7,10] <- full.Fs[6:7,9]
-      abund.age[6:7,10] <- abund.age[6:7,9]
-      full.rems[6:7,10] <- full.rems[6:7,9]
-    }
-
-    if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
-    {
-      age.mat[30,8] <- 1
-      prop.nat.mort[30,8] <- prop.nat.mort[30,7]
-      weight.age[30,8] <- weight.age[29,8]
-      mx[30:31,8] <- mx[30:31,9]
-      full.Fs[30,8] <- full.Fs[30,7]
-      abund.age[30,8] <- abund.age[30,7]
-      full.rems[30,8] <- full.rems[30,7]
-    }
-
-    if(i == "ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax")
-    {
-      age.mat[c(14,27,40),5] <- age.mat[1,5]
-      prop.nat.mort[c(14,27,40),5] <- prop.nat.mort[1,5]
-      weight.age[c(14,27,40),5] <- weight.age[c(13,26,39),5]
-      mx[c(14,16,27,29,40,42),5] <- mx[c(14,16,27,29,40,42),6]
-      full.Fs[c(14,27,40),5] <- full.Fs[c(14,27,40),4]
-      abund.age[c(14,27,40),5] <- abund.age[c(14,27,40),4]
-      full.rems[c(14,27,40),5] <- full.rems[c(14,27,40),4]
-    }
-    # Clear out some 0's...
-    if( i == "AFSC_EEBSAI_Limanda_aspera")
-    {
-      mx[5,18] <- mean(unlist(mx[5,c(17,19)]))
-      mx[c(6,8),19] <- mx[c(6,8),18]
-      mx[2:7,20] <- mx[2:7,19] 
-    }
-
-  # I had filled the years with no SSB data to inform them.  instead I'm going to remove those years...
-
-   if(minage >0) 
-  {
-    rm <- -(1:minage)
-    years <- years[rm]
-    prop.nat.mort <- prop.nat.mort[rm,]
-    weight.age <- weight.age[rm,]
-    rem <- rem[rm,]
-    mx <- mx[rm,]
-    vpa.abund <- vpa.abund[rm]
-    age.mat <- age.mat[rm,]
-    abund.age <- abund.age[rm,]
-    full.Fs <- full.Fs[rm,]
-    full.rems <- full.rems[rm,]
-   }
-  #   mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
-  #   names(mx) <- names(mx.fill)
-  #  # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
-  #   mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
-  # }
-
-    years.tmp[[i]] <- years
-    pnm.tmp[[i]] <- prop.nat.mort
-    waa.tmp[[i]] <- weight.age
-    ages.tmp[[i]] <- minage:maxage
-    rem.tmp[[i]] <- rem
-    mx.tmp[[i]] <- mx
-    NE.tmp[[i]] <- N.end
-    vpa.tmp[[i]] <- vpa.abund
-    am.tmp[[i]] <- age.mat
-    #mr.tmp[[i]] <- missing_rem
-    abund.tmp[[i]] <- abund.age
-    fs.tmp[[i]] <- full.Fs
-    full.rem.tmp[[i]] <- full.rems
-  } #end input data loop
-
-  save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,
-       am.tmp,Stocks,ASR.stocks,ASR.long,abund.tmp,fs.tmp,full.rem.tmp,
-       file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
-
-  } # end load results
-```
-
-  So now I can try to do some tuning, both forwards and backwards, lets see what we get from that...
-
-```{r tunes,include=F,echo=F,warning=F,message=F}
-
-  ########################## Now run the tuning sims
-  #
-
-  if(load.results==F)
-  {
-  load(file = paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
-
-  for.tune.all.res <- NULL
-  for.tune.summary <- NULL
-  for(i in Stocks)
-  {
-    years <- years.tmp[[i]]
-    prop.nat.mort <- pnm.tmp[[i]] 
-    #rem <- rem.tmp[[i]] 
-    mx <- mx.tmp[[i]] 
-    N.end <- NE.tmp[[i]] 
-    ages <- ages.tmp[[i]]
-    vpa.abund <- vpa.tmp[[i]] 
-    abund <- abund.tmp[[i]]
-    fs <-fs.tmp[[i]]
-    full.rem <- full.rem.tmp[[i]]
-    #full.abund <- full.abund.tmp[[i]]
-    #all.abund <- full.abund.tmp[[i]]
-    #N.end <- vpa.abund[length(vpa.abund)]
-    #Pick your step size
-    ss.size <- 0.005
-    sensistive.stocks <- c("AFSC_GOA_Theragra_chalcogramma",
-                            "DFO_2J3KL_Gadus_morhua",
-                            "DFO_3Pn-4RS_Gadus_morhua",
-                            "DFO_4T-4VN_Gadus_morhua",
-                            "DFO_4T_Scomber_scombrus",
-                            "ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus",
-                            "ICES-AFWG_NEA1-2_Gadus_morhua",
-                            "ICES-HAWG_NS_Ammodytes_dubius",
-                            "ICES-NWWG_FA5b_Pollachius_virens",
-                            "ICES-NWWG_FAPL5b1_Gadus_morhua",
-                            "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
-                            "ICES-WGCSE_IS7a_Gadus_morhua",
-                            "ICES-WGCSE_CS7a_Merlangius_merlangus",
-                            "ICES-WGCSE_CS7e-k_Gadus_morhua",
-                            "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
-                            "ICES-WGHANSA_SP8abd_Sardina _pilchardus", 
-                            "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua",
-                            "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",
-                            "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus",
-                            "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
-                            "NEFSC-GARMIII_SNE- MA_Limanda_ferruginea",
-                            "NEFSC-GARMIII_MA_Paralichthys_dentatus",
-                            "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus",
-                            "NEFSC_NWA_Scomber _scombrus")
-
-    if(i %in% sensistive.stocks) ss.size = ss.size/10
-
-     N.start <- vpa.abund[1]
-     print(i)
-     # The fecundities are 
-     fast.for.tune <- fast.tunes(years,
-                             tuner=what.2.tune,
-                             step.size = ss.size, 
-                             abund.ts = vpa.abund,
-                             ages=ages,
-                             nm = -(log(1-prop.nat.mort)),
-                             fecund = mx,
-                             fm = fs,
-                             abund.age = abund, 
-                             catch.age = full.rem, 
-                             N.init = N.start,
-                             direction= 'forwards'
-                             )
-
-     for.tune.all.res[[i]] <- fast.for.tune
-     for.tune.tmp <- data.frame(fast.for.tune$res,Stock = i)
-     for.tune.summary[[i]] <- for.tune.tmp
-  }
-
-  saveRDS(for.tune.summary,paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-  saveRDS(for.tune.all.res,paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
-  # 
-}# end if load results
+```{r, include=F, echo=F}
+knitr::opts_knit$set(eval.after = "fig.cap")
+knitr::opts_chunk$set(fig.pos = 'H')
+options(knitr.kable.NA = '')
+require(tidyverse)
+options(tinytex.verbose = TRUE)
 
@@
 
-```{r paper-other-metrics-and-metadata,echo=F,include=F,warning=F,message=F}
+# Figures {-}
 
-if(load.results==F)
-{
-  # We are now looking at everything, lifetime reproductive success
-
-  for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-  for.tune.all <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
-
-  load(file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
-  # Get the stocks...
-  Stocks <- names(for.tune.summary)
-  n.stocks <- length(Stocks)
-
-  ############ Meta data and clean up, could be it's own chunk really, but it's really fast, so meh...
-
-  #  A quick way to get the other potentially interesting info for the stock...
-  drop <- which(names(ASR.long) %in% c("Year","type","age","value"))
-  meta <- NULL
-  for(i in Stocks) 
-  {
-    meta[[i]] <- ASR.long[ASR.long$Stock == i,-drop][1,]
-    meta[[i]]$age.min <- min(ages.tmp[[i]])
-    meta[[i]]$age.max <- max(ages.tmp[[i]])
-  }
-  meta <- do.call('rbind',meta)
-
-  # First making a meta data object and adding a bunch of columns to it... very messy!!
-  meta$Species[meta$Species == ' harengus']  <- "harengus"
-  meta$Species[meta$Species == "Aeglefinus"] <- "aeglefinus"
-  meta$Species[meta$Species == "Solea"] <- "solea"
-  meta$Family[meta$Family == "Gadide"] <- "Gadidae"
-  meta$Genus[meta$Genus == " Hippoglossoides"] <- "Hippoglossoides"
-  meta$G.short <- toupper(paste0(substr(meta$Genus,1,1),"."))
-  meta$G.Species <- paste0(meta$G.short," ",meta$Species)
-  # Simplified Management
-  meta$Manage.short <- meta$Management
-  meta$Manage.short[grep("TRAC",meta$Management)] <- "DFO-TRAC"
-  meta$Manage.short[grep("DFO",meta$Management)] <- "DFO-TRAC"
-  meta$Manage.short[grep("NEFSC",meta$Management)] <- "NEFSC"
-  meta$Manage.short[grep("ICES",meta$Management)] <- "ICES"
-
-  # The 3 pieces of the ocean
-  meta$LME <- "NW Atlantic"
-  meta$LME[meta$Management == "AFSC"] <- "Pacific (Alaska)"
-  meta$LME[grepl("ICES",meta$Management)] <- "NE Atlantic"
-  # An area typo
-  meta$Area[grep("BSAI-females",meta$Area)] <- "BSAI-Females"
-  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI-Females"
-  # Some other Area summaries
-  meta$Area.broad <- meta$Area
-  meta$Area.long <- meta$Area
-  meta$Area.narrow <- "" # Leave this blank if not needed
-
-  meta$Area.broad[grep("NS",meta$Area)] <- "NS"
-  meta$Area.long[grep("NS",meta$Area)] <- "North Sea"
-  meta$Area.broad[grep("CS",meta$Area)] <- "CS"
-  meta$Area.long[grep("CS",meta$Area)] <- "Celtic Sea"
-  meta$Area.broad[grep("ROCK6b",meta$Area)] <- "CS"
-  meta$Area.long[grep("ROCK6b",meta$Area)] <- "Celtic Sea"
-  meta$Area.broad[grep("IS",meta$Area)] <- "IS"
-  meta$Area.long[grep("IS",meta$Area)] <- "Irish Sea"
-  meta$Area.broad[grep("BS",meta$Area)] <- "BS"
-  meta$Area.long[grep("BS",meta$Area)] <- "Baltic Sea"
-  meta$Area.broad[grep("NEA",meta$Area)] <- "NEA"
-  meta$Area.long[grep("NEA",meta$Area)] <- "NE Arctic"
-  meta$Area.broad[grep("B28.1",meta$Area)] <- "BS"
-  meta$Area.long[grep("B28.1",meta$Area)] <- "Baltic Sea"
-  meta$Area.broad[grep("SP8abd",meta$Area)] <- "BoB"
-  meta$Area.long[grep("SP8abd",meta$Area)] <- "Bay of Biscay"
-  meta$Area.broad[grep("FA",meta$Area)] <- "Ice-Faroe"
-  meta$Area.broad[grep("ICE",meta$Area)] <- "Ice-Faroe"
-  meta$Area.long[grep("FA",meta$Area)] <- "Faroes"
-  meta$Area.long[grep("ICE",meta$Area)] <- "Iceland"
-
-  meta$Area.broad[grep("GOM",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("GOM",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("GB",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("GB",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("5Y",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("5Y",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("5Z",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("5Z",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("USATL",meta$Area)] <- "NAFO 5-6" # The fishery is broader than just GOM, but it does also include it.
-  meta$Area.long[grep("USATL",meta$Area)] <- "NAFO 5-6" # The fishery is broader than just GOM, but it does also include it.
-  meta$Area.broad[grep("NWA",meta$Area)] <- "NAFO 5-6" # Mackerel... so that definition is a bit narrow....
-  meta$Area.long[grep("NWA",meta$Area)] <- "NAFO 5-6" # Mackerel... so that definition is a bit narrow....
-  #meta$Area1[grep("SNE- MA",meta$Area)] <- "GOM-GB" # YT in US, so no GB so that definition is a bit narrow....
-  meta$Area.broad[grep("MA",meta$Area)] <- "NAFO 5-6" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
-  meta$Area.long[grep("MA",meta$Area)] <- "NAFO 5-6" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
-  meta$Area.broad[grep("BSAI",meta$Area)] <- "BSAI"
-  meta$Area.broad[grep("4T",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("4T",meta$Area)] <- "NAFO 2-4"
-  meta$Area.broad[grep("2J3",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("2J3",meta$Area)] <- "NAFO 2-4"
-  meta$Area.broad[grep("3Pn-4RS",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("3Pn-4RS",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("GOA",meta$Area)] <- "Gulf of Alaska"
-  # Lumping everything in Berring Sea and AI into both.
-  meta$Area.long[grep("AI",meta$Area)] <- "Aleutian Islands"
-  meta$Area.long[grep("ESB",meta$Area)] <- "Bering Sea & AI" 
-  meta$Area.long[grep("BSAI",meta$Area)] <- "Bering Sea & AI"
-  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI"
-  meta$Area[grep("BSAI-Females",meta$Area)] <- "BSAI"
-  meta$Area[grep("BSAI-females",meta$Area)] <- "BSAI"
-  meta$Area.long[grep("BSAI-Females",meta$Area)] <- "Bering Sea & AI"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Pollachius_virens"] <- "5b"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5a_Pollachius_virens"] <- "5a"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS4 _Solea_solea"] <- "4"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d._Solea_solea"] <- "7d"
-  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_NS IIIa 22-24_Solea_Solea"] <- "22-24"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d_Pleuronectes_platessa"] <- "7d"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4,20_Pleuronectes_platessa"] <- "4 20"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS7e_Pleuronectes_platessa"] <- "7e"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS27.7a_Pleuronectes_platessa"] <- "7a"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Melanogrammus_aeglefinus"] <- "5b"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Melanogrammus_aeglefinus"] <- "5a"
-  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_B28.1_Clupea_harengus"] <- "28"
-  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_BS 25-29-32_Clupea_harengus" ] <- "25-32"
-  meta$Area.narrow[meta$Stock == "ICES-HAWG_WBS 22-24_Clupea_harengus"] <- "22-24"
-  meta$Area.narrow[meta$Stock == "DFO_4T-Fall_Clupea_harengus"] <- "Fa-SGSL"
-  meta$Area.narrow[meta$Stock == "DFO_4T-Spring_Clupea_harengus"] <- "Sp-SGSL"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS27.6a_Merlangius_merlangus"] <- "27.6a"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS7a_Merlangius_merlangus"] <- "7a"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Gadus_morhua"] <- "5a"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FAPL5b1_Gadus_morhua" ] <- "5b"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua"] <- "4-7 20"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_NS6a_Gadus_morhua"] <- "6a"
-  meta$Area.narrow[meta$Stock == "DFO_2J3KL_Gadus_morhua"] <- "NFLD"
-  meta$Area.narrow[meta$Stock == "DFO_3Pn-4RS_Gadus_morhua"] <- "NGSL"
-  meta$Area.narrow[meta$Stock == "NEFSC-CERT-TRAC_GB _Gadus_morhua"] <- "EGB"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus"] <- "RA"
-  meta$Area.narrow[meta$Stock == "DFO_4T-4VN_Gadus_morhua"] <- "SGSL"
-  meta$Area.narrow[meta$Stock == "DFO_4T_Hippoglossoides _platessoides"] <- "SGSL"
-  meta$Area.narrow[meta$Stock == "DFO_4T_Scomber_scombrus"] <- "SGSL"
-  meta$Area.narrow[meta$Stock == "NEFSC-SAW_GOM_Gadus_morhua"] <- "GOM"
-  meta$Area.narrow[meta$Stock == "NEFSC-GARMIII_GB_Gadus_morhua"] <- "GB"
-  meta$Area.narrow[meta$Stock == "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus"] <- "GOM"
-  meta$Area.narrow[meta$Stock == "CERT-TRAC_GB_Melanogrammus_Aeglefinus"] <- "GB"
-
-  meta$Stock.short <- paste0(meta$Area.broad," ",meta$Area.narrow," ",meta$G.short," ",meta$Species)
-  meta$Stock.no.species <- paste0(meta$Area.long," ",meta$Area.narrow)
-
-  for.tune.stocks <- NULL
-  fta <- NULL
-
-  # Going to rename these female stocks.
-  fem.names <- c("AFSC_BASI-Females_Pleuronectes_quadrituberculatus",
-                    "AFSC_EEBSAI-Females_Lepidopsetta_polyxystra",
-                    "AFSC_BSAI-females_Atheresthes_stomais")
-  fem.rename <- c("AFSC_BSAI_Pleuronectes_quadrituberculatus",
-                    "AFSC_EEBSAI_Lepidopsetta_polyxystra",
-                    "AFSC_BSAI_Atheresthes_stomais")
-  # Going to drop these stocks
-  dont <- paste(c("Mles","Males","COASTNOR"),collapse = "|")
-
-  meta.sub <- NULL
-  for(i in Stocks) 
-  {
-    org.nam <- i
-    tmp <- for.tune.summary[[org.nam]]
-    new.stock.nam <- org.nam
-    # Don't bother for these stocks...
-    if(!grepl(dont,tmp$Stock[1]))
-    {
-      # Grab the metadata and add in some new useful things...
-      meta.sub[[i]] <- meta[meta$Stock == org.nam,]
-
-      # Rename the ladies
-      if(tmp$Stock[1] == fem.names[1]) new.stock.nam <- tmp$Stock <- fem.rename[1]
-      if(tmp$Stock[1] == fem.names[2]) new.stock.nam <- tmp$Stock <- fem.rename[2]
-      if(tmp$Stock[1] == fem.names[3]) new.stock.nam <- tmp$Stock <- fem.rename[3]
-
-      meta.sub[[i]]$Stock <- new.stock.nam
-      tmp <- data.frame(tmp,meta.sub[[i]])
-      # For tunes all
-      fta[[new.stock.nam]] <- for.tune.all[[org.nam]]
-      fta[[new.stock.nam]]$meta <- meta.sub[[i]]
-      for.tune.stocks[[new.stock.nam]] <- tmp
-    }# End skip stocks...
-  }
-  # Now unpack them...
-  for.tunes <- do.call("rbind",for.tune.stocks)
-  for.tune.all <- fta
-  meta.sub <- do.call("rbind",meta.sub)
-
-  ######################### End Meta data and clean up #####################
-
-  # Now some summaries...
-
-  # Reset on the stocks...
-  Stocks <- sort(names(for.tune.all))
-  n.stocks <- length(Stocks)
-
-  # Doubling time, no fishing
-  dt.res <- NULL
-  # These are both set in the index file now, go there!!
-  n.dt.sims <- n.dt.sims
-  n.sim.years <- n.sim.years
-  for(i in Stocks)
-  {
-    str.time <- Sys.time()
-    try <- for.tune.all[[i]]
-    meta.tmp <- try$meta
-    age.4.sim <- meta.tmp$age.min:meta.tmp$age.max
-    double.time <- NA
-    pop <- 1000
-    tmp.res <- NULL
-  for(s in 1:n.dt.sims)
-  {
-    tmp <- rep(0,n.sim.yearss)
-    print(paste0("Sim # ", s))
-
-    for(y in 2:n.sim.yearss)
-    {
-
-      # Get our sample for this run
-      f.pick <- sample(nrow(try$fecund.opt),size=1)
-      nm.pick <- sample(nrow(try$nm.opt),size=1)
-      fec.samp <- try$fecund.opt[f.pick,]
-      # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
-      nm.samp <- try$nm.opt[nm.pick,] 
-      # now put these into Euler-lotka to get an r estimate
-      res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
-      r.val <- res$res$r
-      # If r is > 5 (lambda = exp(5)) it generally means the simple.lotka didn't converge (bad combo of fec and nm)
-      # So we'll need to resample them until it is < 5
-      while(r.val >= 5)
-      {
-        print("Resampling due to bat shit r value")
-        f.pick <- sample(nrow(try$fecund.opt),size=1)
-        nm.pick <- sample(nrow(try$nm.opt),size=1)
-        fec.samp <- try$fecund.opt[f.pick,]
-        # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
-        nm.samp <- try$nm.opt[nm.pick,] 
-        # now put these into Euler-lotka to get an r estimate
-        res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
-        r.val <- res$res$r
-      } # end while loop
-      pop[y] <- exp(r.val)*pop[y-1]
-      if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.sim.yearss] <- 1
-    } # end the years loop
-    tmp.res[[s]] <- data.frame(year =1:n.sim.yearss,doubled = tmp,sim=s)
-
-    } # end sim loop
-    res.tmp <- do.call("rbind",tmp.res)
-
-  dt.res[[i]] <- data.frame(res.tmp,meta.tmp)
-  count <- 0
-  timer <- round(difftime(Sys.time(),str.time,units='mins'),digits=1)
-  print(paste0("Stock ",i," time =", timer," minutes: Stock # ",count+1))
-  } # end Stocks loop
-
-  dub.time <- do.call("rbind",dt.res)
-
-  dub.time.summary <- dub.time |> collapse::fgroup_by(Stock,year)  |> collapse::fsummarise(prop = sum(doubled)/n.dt.sims)
-  dub.time.summary <- left_join(dub.time.summary,meta.sub,by="Stock")
-
-  # Now to get generation lengths + reproductive rates....
-  # First I need to get the fecundity and natural mortalities by cohort instead of year.
-  res.fin <- NULL
-  res.year.fin <- NULL
-  res.lambda.fin <- NULL
-  for(i in Stocks) # 
-  {
-    tst <- for.tune.all[[i]]
-    meta.tmp <- tst$meta
-    # Fishing mortality
-    fm.org.tmp <- tst$fm.org
-    fm.tmp <- tst$fm.opt
-    # fecundity
-    fec.tmp <- tst$fecund.opt
-    fec.org.tmp <- tst$fecund.org
-    # Natural mortality
-    m.org.tmp <- exp(-tst$nm.org) # This is survivorship
-    m.tmp <- exp(-tst$nm.opt) # This is survivorship
-    # Total mortality
-    z.tmp <- exp(-tst$z.opt) # This is survivorship
-    z.org.tmp <- exp(-tst$nm.org -fm.org.tmp) # This is survivorship
-
-    ages <- meta.tmp$age.min:meta.tmp$age.max
-    n.ages <- length(ages)
-    years <- tst$res$year
-    n.years <- length(years)
-    # Now I need to grab the fecundities and nat morts by cohort
-    if(n.years > n.ages)
-    {
-    res.cohort <- NULL
-    res.year <- NULL
-    res.lambda <- NULL
-    for(y in 1:(n.years-n.ages+1))
-    {
-      count = 0
-      fs <- NA
-      # The lx is no fishing survivorship, zx I'm calling the survivorship including fishing
-      lx <- lx.org <- lx.year <- zx <- zx.org <- zx.year <- 1
-      fs.org <- NA
-
-      for(a in 1:n.ages)
-      {
-      fs[a] <- fec.tmp[y+count,a]  
-      fs.org[a] <- fec.org.tmp[y+count,a]  
-      if(a > 1) 
-      {
-        # No fishing
-        lx[a] <- lx[a-1] * m.tmp[y+count,a]  
-        lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
-        lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
-        # Including fishing
-        zx[a] <- zx[a-1] * z.tmp[y+count,a]  
-        zx.org[a] <- zx.org[a-1]* z.org.tmp[y+count,a]  
-        zx.year[a] <- zx.year[a-1] * z.tmp[y,a]
-      }  # end the a > 1 if
-          count <- count + 1
-      }# end the ages loop
-          res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,
-                                 mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
-                                 x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
-                                 zx.opt = zx,
-                                 mx.zx.opt = fs*zx,mx.zx.org = fs.org*zx.org,
-                                 x.mx.zx.opt = fs*zx*ages,x.mx.zx.org = fs.org*zx.org*ages,
-                                 cohort=years[y],age = ages,meta.tmp)
-
-          res.year[[y]] <- data.frame(mx.opt = unlist(fec.tmp[y,]),lx.opt = lx.year,
-                                 mx.lx.opt = unlist(fec.tmp[y,])*lx.year,
-                                 x.mx.lx.opt = unlist(fec.tmp[y,])*lx.year*ages,
-                                 zx.opt = zx.year,
-                                 mx.zx.opt = unlist(fec.tmp[y,])*lx.year,
-                                 x.mx.zx.opt = unlist(fec.tmp[y,])*lx.year*ages,
-                                 age = ages,year=years[y],meta.tmp)
-
-    } # end the years loop
-
-  # Do a years loop to get lambda with no fishing for each year, rather than by cohort...
-    for(yy in 1:(n.years-1))
-    {
-      nm <- as.numeric(tst$nm.opt[yy,])
-      z <- as.numeric(tst$z.opt[yy,])
-      fec <- as.numeric(tst$fecund.opt[yy,])
-      nm.init <- as.numeric(tst$nm.org[yy,])
-      fec.init <- as.numeric(tst$fecund.org[yy,])
-      z.init <- as.numeric(tst$z.org[yy,])
-      lam.no.fish <- exp(simple.lotka.r(mort = nm,fecund = fec,ages=ages)$res$r)
-      lam.fish <- exp(simple.lotka.r(mort = z,fecund = fec,ages=ages)$res$r)
-      lam.org.no.fish <- exp(simple.lotka.r(mort = nm.init,fecund = fec.init,ages=ages)$res$r)
-      lam.org.fish <- exp(simple.lotka.r(mort =  z.init,fecund = fec.init,ages=ages)$res$r)
-
-      # Now summarize these
-      res.lambda[[yy]] <-  data.frame(lam.no.fish = lam.no.fish,lam.fish = lam.fish,
-                                      lam.org.no.fish = lam.org.no.fish,
-                                      lam.org.fish = lam.org.fish,
-                                      year=years[yy],meta.tmp)
-    } # End the yy loop to get the lambdas...
-  # unpack it...
-  res.fin[[i]] <- do.call('rbind',res.cohort)
-  res.year.fin[[i]] <- do.call('rbind',res.year)
-  res.lambda.fin[[i]] <-  do.call('rbind',res.lambda)
-  }  # end if to make sure we have enough data to get the cohort estimates.
-
-  }# end the stock loop
-
-  res.cohort.final <- do.call('rbind',res.fin)
-  res.year.final <- do.call('rbind',res.year.fin)
-  res.lambda.final <- do.call('rbind',res.lambda.fin)
-
-  pop.dam <- res.cohort.final |> collapse::fgroup_by(cohort,Stock) |> collapse::fsummarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
-                                                                                   gen.len.org = sum(x.mx.lx.org)/sum(mx.lx.org),
-                                                                                   R0.opt = sum(mx.lx.opt),R0.org = sum(mx.lx.org))
-  pop.dam <- left_join(pop.dam,meta.sub,by="Stock")
-
-  dub.time.summary <- data.frame(dub.time.summary)
-  pop.dam <- data.frame(pop.dam)
-  # saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",what.2.tune,".Rds"))
-  # saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",what.2.tune,".Rds"))
-  # saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",what.2.tune,".Rds"))
-  save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
-       file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
-
-  write.csv(meta.sub, paste0(loc,"/Data/metadata_no_age_corection.csv"))
-} # end if load results
-```
-
-```{r clean-up-and-stats,include=F,echo=F,message=F,warning=F}
-load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
-for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-
-Stocks <- unique(res.lambda.final$Stock)
-res.lambda.fin <- data.frame(res.lambda.final)
-six.species <- c('morhua','harengus','aeglefinus','virens','solea','platessa')
-pop.dam.6 <- pop.dam |> collapse::fsubset(Species %in% six.species)
-for.tunes.6 <- for.tunes |> collapse::fsubset(Species %in% six.species)
-dub.time.6 <- dub.time.summary |> collapse::fsubset(Species %in% six.species)
-res.lambda.fin$decade <- floor(res.lambda.fin$year/10)*10
-res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock,decade) |> collapse::fmutate(mn.lam = mean(lam.fish,na.rm=T),
-                                                                                 med.lam = median(lam.fish,na.rm=T),
-                                                                                 sd.lam = sd(lam.fish,na.rm=T))
-res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Species,decade) |> collapse::fmutate(lm.spec.mn = mean(mn.lam,na.rm=T))              
-res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock) |> 
-                                                          collapse::fmutate(
-                                                          lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
-                                                          lam.fish.mn = mean(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T),
-                                                          lam.no.fish.med = median(lam.no.fish,na.rm=T),
-                                                          lam.fish.med = median(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.med = median(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T),
-                                                          lam.no.fish.sd = sd(lam.no.fish,na.rm=T),
-                                                          lam.fish.sd = sd(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.sd = sd(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.sd = sd(lam.org.fish,na.rm=T)
-                                                          ) |> data.frame()
-# Get the order right for the stock no species for the boxplots to come later
-sns.order <- c("Baltic Sea ", "Baltic Sea 22-24", "Baltic Sea 25-32", "Baltic Sea 28", 
-               "North Sea ", "North Sea 4", "North Sea 22-24", "North Sea 4-7 20", "North Sea 6a","North Sea 4 20", "North Sea 7d",     
-               "Celtic Sea ","Celtic Sea RA", "Celtic Sea 7a", "Celtic Sea 27.6a", 
-               "Irish Sea ","Irish Sea 7a", "Irish Sea 7e","Bay of Biscay ", "NE Arctic ", 
-               "Faroes 5a", "Faroes 5b",  "Iceland ", "Iceland 5a",
-                "NAFO 2-4 Fa-SGSL", "NAFO 2-4 Sp-SGSL", "NAFO 2-4 SGSL", "NAFO 2-4 NGSL", "NAFO 2-4 NFLD",  
-                "NAFO 5-6 ", "NAFO 5-6 GB", "NAFO 5-6 GOM", "NAFO 5-6 EGB",
-                "Bering Sea & AI ", "Gulf of Alaska ", "Aleutian Islands ")
-
-res.lambda.fin$Stock.no.species <- factor(res.lambda.fin$Stock.no.species,levels = sns.order,ordered = T)
-res.lambda.final.6 <- res.lambda.fin |> collapse::fsubset(Species %in% six.species)
-# Sort the data into a nice order...
-res.lambda.fin <- res.lambda.fin |> collapse::roworder(Species,Area.broad) |>
-                                    collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-# Making the Aleutian Islands their own Area long...
-res.lambda.fin$Area.long[res.lambda.fin$Area == "AI"] <- "Aleutian Islands"
-res.lambda.fin$Area.long <- factor(res.lambda.fin$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
-                                                                       "Irish Sea","Bay of Biscay","NE Arctic",
-                                                                       "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-
-res.lambda.final.6 <- res.lambda.final.6 |> collapse::roworder(Species,Area.broad) |>
-                                            collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-dub.time <- dub.time |> collapse::roworder(LME) |>
-                        collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-dub.time.summary <- dub.time.summary |> collapse::roworder(LME,Order,Species,Area.broad) |>
-                                        collapse::fmutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-dub.time.6 <- dub.time.6 |> collapse::roworder(LME) |>
-                             collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-pop.dam <- pop.dam |> collapse::roworder(Species,LME) |>
-                       collapse::fmutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
-pop.dam.6 <- pop.dam.6 |> collapse::roworder(LME,Area.broad) |>
-                       collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-pop.dam$Area.long[pop.dam$Area == "AI"] <- "Aleutian Islands"
-pop.dam$Area.long <- factor(pop.dam$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
-                                                         "Irish Sea","Bay of Biscay","NE Arctic",
-                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-# I'd also like a pop.dam including fishing
-pop.dam.fish <- res.cohort.final |> collapse::fgroup_by(cohort,Stock) |> collapse::fsummarise(gen.len.opt = sum(x.mx.zx.opt)/sum(mx.zx.opt),
-                                                                                   gen.len.org = sum(x.mx.zx.org)/sum(mx.zx.org),
-                                                                                   R0.opt = sum(mx.zx.opt),R0.org = sum(mx.zx.org))
-pop.dam.fish <- left_join(pop.dam.fish,meta.sub,by="Stock")
-pop.dam.fish$Area.long[pop.dam.fish$Area == "AI"] <- "Aleutian Islands"
-pop.dam.fish$Area.long <- factor(pop.dam.fish$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
-                                                         "Irish Sea","Bay of Biscay","NE Arctic",
-                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-pop.dam <- data.frame(pop.dam)
-
-pop.dam.fish <- pop.dam.fish |> collapse::roworder(Species,LME) |>
-                                collapse::fmutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
-pop.dam.fish.6 <- pop.dam.fish |> collapse::fsubset(Species %in% six.species)
-
-pop.dam.fish.6 <- pop.dam.fish.6 |> collapse::roworder(LME,Area.broad) |>
-                                    collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-# Put the population dynamics stuff together.
-pop.dam$group <- "no fish"
-pop.dam.fish$group <- 'fish'
-pop.dam.all <- rbind(pop.dam,pop.dam.fish)
-
-pop.dam.6$Stock.no.species <- factor(pop.dam.6$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam$Stock.no.species <- factor(pop.dam$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam.fish.6$Stock.no.species <- factor(pop.dam.fish.6$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam.fish$Stock.no.species <- factor(pop.dam.fish$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam.all$Stock.no.species <- factor(pop.dam.all$Stock.no.species,levels = sns.order,ordered = T)
-# Drop the periods....
-pop.dam.all.6 <- pop.dam.all |> collapse::fsubset(!Species %in% six.species)
-pop.dam.all$G.Species <- gsub("\\.","",pop.dam.all$G.Species)
-pop.dam.all$G.Species.short <- substr(pop.dam.all$G.Species,1,5)
-pop.dam.all$G.Species <- gsub("\\.","",pop.dam.all$G.Species)
-pop.dam.all.6 <- pop.dam.all |> collapse::fsubset(Species %in% six.species)
-pop.dam.all.others <- pop.dam.all |> collapse::fsubset(!Species %in% six.species)
-
-# Reorder the doubling time, either by Species and LME, or the other way around
-
-dub.time.summary$Order.short <- "Gadi"
-dub.time.summary$Order.short[dub.time.summary$Order == "Pleuronectiformes"] <- "Plero"
-dub.time.summary$Order.short[dub.time.summary$Order == "Clupeiformes"] <- "Clupei"
-dub.time.summary$Order.short[dub.time.summary$Order == "Scorpaeniformes "] <- "Scor"
-dub.time.summary$Order.short[dub.time.summary$Order == "Scombriformes"] <- "Scomb"
-dub.time.summary$Order.short[dub.time.summary$Order == "Perciformes"] <- "Perci"
-# First need to get the abundance and lambdas with no fishing into one object.
-ft.tmp <- for.tunes |> collapse::fselect(year,Stock,vpa.abund,est.abund,removals)
-dd.dat <- left_join(res.lambda.fin,ft.tmp,by=c('year','Stock'))
-# Now I need to get a relative abundance for each stock...
-dd.dat <- dd.dat |> collapse::fgroup_by(Stock) |> collapse::fmutate(max.abund = max(est.abund,na.rm=T))
-dd.dat <- data.frame(dd.dat)
-dd.dat$prop.abund <- dd.dat$est.abund/dd.dat$max.abund
-# Drop nas....
-drops <- -which(is.na(dd.dat$prop.abund))
-dd.dat <- dd.dat[drops,]
-#lump the data into bins
-dd.dat$prop.bin <- "< 10%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.1 & dd.dat$prop.abund <= 0.2] <- "10-20%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.2 & dd.dat$prop.abund <= 0.3] <- "20-30%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.3 & dd.dat$prop.abund <= 0.4] <- "30-40%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.4 & dd.dat$prop.abund <= 0.6] <- "40-60%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.6 & dd.dat$prop.abund <= 0.8] <- "60-80%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.8 & dd.dat$prop.abund <= 1] <- "80-100%"
-dd.dat$prop.bin <- factor(dd.dat$prop.bin,levels=c("< 10%","10-20%","20-30%","30-40%","40-60%","60-80%","80-100%"))
-
-# Subset to the big six
-dd.dat.six <- dd.dat  |>collapse::fsubset(Species %in% six.species)
-
-# This is for the new lambda figures with fishing and no fishing together
-
-res.lambda.fin.long <- res.lambda.fin |> tidyr::pivot_longer(cols = c(lam.no.fish,lam.fish),names_to = 'group',values_to = 'lambda')
-res.lambda.fin.long$Stock.no.species <- factor(res.lambda.fin.long$Stock.no.species,levels = sns.order,ordered = T)
-res.lambda.fin.long$group <- substr(res.lambda.fin.long$group,5,20)
-res.lambda.fin.long$group <- gsub("\\."," ",res.lambda.fin.long$group)
-res.lambda.fin.long.others <- res.lambda.fin.long |> collapse::fsubset(!Species %in% six.species)
-res.lambda.fin.long.others$G.Species <- gsub("\\.","",res.lambda.fin.long.others$G.Species)
-res.lambda.fin.long.others$G.Species.short <- substr(res.lambda.fin.long.others$G.Species,1,5)
-res.lambda.fin.long.6 <- res.lambda.fin.long |> collapse::fsubset(Species %in% six.species)
-res.lambda.fin.long.6$G.Species <- gsub("\\.","",res.lambda.fin.long.6$G.Species)
-
-# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE
-# here is the GAM for no fishing with subsequent processing.
-mod.dd.stock.gam.nf <- gam(log(lam.no.fish) ~   s(prop.abund,k=4) + s(prop.abund,as.factor(Stock.short),bs='fs',k=3) ,data=dd.dat)
-
-# This extracts the GAM fit so we can custom plot it on our own figure
-tmp <- plot(mod.dd.stock.gam.nf, pages = 0)
-no.stock.gam.nf.dat <- data.frame(fit = tmp[[1]]$fit + coefficients(mod.dd.stock.gam.nf)[1],prop.abund = tmp[[1]]$x,se = tmp[[1]]$se,Scenario = "F = 0")
-no.stock.gam.nf.dat$LCI <- no.stock.gam.nf.dat$fit - 1.96*no.stock.gam.nf.dat$se
-no.stock.gam.nf.dat$UCI <- no.stock.gam.nf.dat$fit + 1.96*no.stock.gam.nf.dat$se
-
-#summary(mod.dd.stock.gam.nf)
-#Residuals, definitely still issues here, maybe a bit better than some others, maybe...
-#plot(residuals(mod.dd.stock.gam.nf) ~ fitted(mod.dd.stock.gam.nf))
-# Normality = no
-#qqnorm(residuals(mod.dd.stock.gam.nf))
-#qqline(residuals(mod.dd.stock.gam.nf))
-
-pred.dd.stock.gam.nf <- expand.grid(prop.abund = seq(0, 1, length.out = 250),
-                                         Stock.short=c(unique(dd.dat$Stock.short)))
-tmp <- predict(mod.dd.stock.gam.nf, pred.dd.stock.gam.nf, type = 'response', se.fit = TRUE) 
-# Another fun trick to extract the overall smooth fit, but didn't end up using this method.
-# sms <- smooths(mod.dd.stock.gam.nf)
-# excl <- grepl("as.factor",sms)
-# rm <- sms[excl]
-# tmp.ex <- predict(mod.dd.stock.gam.nf, newdata =pred.dd.stock.gam.nf, type = 'response', se.fit = TRUE,exclude =rm) 
-# Get the fit by stock
-pred.dd.stock.gam.nf$lam.no.fish   <- exp(tmp$fit)
-pred.dd.stock.gam.nf$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-pred.dd.stock.gam.nf$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-
-# Thin the data so I can add points to the figure
-tmp <- NULL
-for(i in 1:(77)) 
-{
-  if(i==1) tmp[[i]] <- seq(10,230,length.out=5)
-  if(i>1) tmp[[i]] <- seq(10,230,length.out=5)+250*(i-1)
-}
-thinner.nf <- do.call('c',tmp)
-thin.pred.nf <- pred.dd.stock.gam.nf[thinner.nf,]
-# Now I want to get rid of extrapolation from this prediction data.frame, I think I need to loop it...
-# 
-short.stocks <- unique(dd.dat$Stock.short)
-n.stocks <- length(short.stocks)
-pred.out <- NULL
-thin.out <- NULL
-for(i in short.stocks)
-{
-  # Get the right stocks
-  tmpy <- dd.dat |> collapse::fsubset(Stock.short == i)
-  tmp.pred <- pred.dd.stock.gam.nf |> collapse::fsubset(Stock.short == i)
-  tmp.thin <- thin.pred.nf |> collapse::fsubset(Stock.short == i)
-  # I dont want to predict below the minimum observed abundance
-  mins <- min(tmpy$prop.abund,na.rm=T)
-  pred.out[[i]] <- tmp.pred |> collapse::fsubset(prop.abund >= mins)
-  thin.out[[i]] <- tmp.thin |> collapse::fsubset(prop.abund >= mins)
-}
-
-pred.dd.stock.gam.ss.nf <- do.call('rbind',pred.out)
-thin.pred.nf <- do.call('rbind',thin.out)
-# Combine pred stuff with the meta data for fun plots
-pred.dd.stock.gam.ss.nf <- left_join(pred.dd.stock.gam.ss.nf,meta.sub,by="Stock.short")
-pred.dd.stock.gam.ss.nf <- data.frame(pred.dd.stock.gam.ss.nf)
-thin.pred.nf <- left_join(thin.pred.nf,meta.sub,by="Stock.short")
-# Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# By region
-cols.gam <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
-pty.gam <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
-
-# Now do the same thing with the data that includes the effect of fishing.
-
-#mod.dd.stock.gam.fish <- gam(log(lam.fish) ~  as.factor(Stock.short) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.dat)
-mod.dd.stock.gam.fish <- gam(log(lam.fish) ~  s(prop.abund,k=4) + s(prop.abund,as.factor(Stock.short),bs='fs',k=3),data=dd.dat)
-
-tmp <- plot(mod.dd.stock.gam.fish, pages = 0)
-no.stock.gam.fish.dat <- data.frame(fit = tmp[[1]]$fit + coefficients(mod.dd.stock.gam.fish)[1],prop.abund = tmp[[1]]$x,se = tmp[[1]]$se,Scenario = "F > 0")
-no.stock.gam.fish.dat$LCI <- no.stock.gam.fish.dat$fit - 1.96*no.stock.gam.fish.dat$se
-no.stock.gam.fish.dat$UCI <- no.stock.gam.fish.dat$fit + 1.96*no.stock.gam.fish.dat$se
-
-#summary(mod.dd.stock.gam.fish)
-#Residuals, definetly still issues here, maybe a bit better than some others, maybe...
-#plot(residuals(mod.dd.stock.gam.fish) ~ fitted(mod.dd.stock.gam.fish))
-# Normality = no
-#qqnorm(residuals(mod.dd.stock.gam.fish))
-#qqline(residuals(mod.dd.stock.gam.fish))
-
-pred.dd.stock.gam.fish <- expand.grid(prop.abund = seq(0, 1, length.out = 250),
-                                         Stock.short=c(unique(dd.dat$Stock.short)))
-tmp <- predict(mod.dd.stock.gam.fish, pred.dd.stock.gam.fish, type = 'response', se.fit = TRUE) 
-pred.dd.stock.gam.fish$lam.fish   <- exp(tmp$fit)
-pred.dd.stock.gam.fish$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-pred.dd.stock.gam.fish$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-
-# Thin the data so I can add points to the figure
-tmp <- NULL
-for(i in 1:(77)) 
-{
-  if(i==1) tmp[[i]] <- seq(10,230,length.out=5)
-  if(i>1) tmp[[i]] <- seq(10,230,length.out=5)+250*(i-1)
-}
-thinner.fish <- do.call('c',tmp)
-thin.pred.fish <- pred.dd.stock.gam.fish[thinner.fish,]
-# Now I want to get rid of extrapolation from this prediction data.frame, I think I need to loop it...
-# 
-short.stocks <- unique(dd.dat$Stock.short)
-pred.out <- NULL
-thin.out <- NULL
-for(i in short.stocks)
-{
-  # Get the right stocks
-  tmpy <- dd.dat |> collapse::fsubset(Stock.short == i)
-  tmp.pred <- pred.dd.stock.gam.fish |> collapse::fsubset(Stock.short == i)
-  tmp.thin <- thin.pred.fish |> collapse::fsubset(Stock.short == i)
-  # I dont want to predict below the minimum observed abundance
-  mins <- min(tmpy$prop.abund,na.rm=T)
-  pred.out[[i]] <- tmp.pred |> collapse::fsubset(prop.abund >= mins)
-  thin.out[[i]] <- tmp.thin |> collapse::fsubset(prop.abund >= mins)
-}
-
-pred.dd.stock.gam.ss.fish <- do.call('rbind',pred.out)
-thin.pred.fish <- do.call('rbind',thin.out)
-# Combine pred stuff with the meta data for fun plots
-pred.dd.stock.gam.ss.fish <- left_join(pred.dd.stock.gam.ss.fish,meta.sub,by="Stock.short")
-pred.dd.stock.gam.ss.fish <- data.frame(pred.dd.stock.gam.ss.fish)
-
-thin.pred.fish <- left_join(thin.pred.fish,meta.sub,by="Stock.short")
-
-# Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# By region
-
-# What proportion of the stocks had the lowest 'GAM' estimate happen when the stock was at it's maximum size.
-low.gam <- data.frame(low.pa.fish = NA,diff.low.pa.fish = NA,low.pa.nf = NA,diff.low.pa.nf = NA,Stock = NA,Species = NA)
-count <- 0
-for(i in short.stocks) 
-{
-  count = count +1
-  tmp <- pred.dd.stock.gam.ss.fish |> collapse::fsubset(Stock.short == i)
-  tmp.nf <- pred.dd.stock.gam.ss.nf |> collapse::fsubset(Stock.short == i)
-  low.pa <- data.frame(low.pa.fish = tmp$prop.abund[tmp$lam.fish == min(tmp$lam.fish)],
-                       diff.low.pa.fish = tmp$lam.fish[tmp$lam.fish == min(tmp$lam.fish)] - tmp$lam.fish[tmp$prop.abund == max(tmp$prop.abund)],
-                       low.pa.nf = tmp.nf$prop.abund[tmp.nf$lam.no.fish == min(tmp.nf$lam.no.fish)],
-                       diff.low.pa.nf = tmp.nf$lam.no.fish[tmp.nf$lam.no.fish == min(tmp.nf$lam.no.fish)] - tmp.nf$lam.no.fish[tmp.nf$prop.abund == max(tmp.nf$prop.abund)],
-                       Stock = i,Species = tmp$G.Species[1])
-  low.gam[count,] <- low.pa
-}
-
-# Let's compare lambda at minimum, 0.4, and maximum and make a Table
-comp.lam.diff <- NULL
-comp.lam <- NULL
-comp.all.nf <- NULL
-comp.all.fish <- NULL
-for(i in short.stocks) 
-{
-  tmp <- pred.dd.stock.gam.ss.fish |> collapse::fsubset(Stock.short == i)
-  which.40 <- max(which(tmp$prop.abund <=0.4)) # Some stocks might not have a which 40.
-  which.max <- which(tmp$prop.abund ==1)
-  which.min <- which(tmp$prop.abund == min(tmp$prop.abund))
-  tmp.sub <- tmp[c(which.min,which.40,which.max),]
-  comp.all.fish[[i]] <- tmp.sub
-  tmp.nf <- pred.dd.stock.gam.ss.nf |> collapse::fsubset(Stock.short == i)
-  # I think I'm overkilling as this should be the same was the above witches....
-  which.40.nf <- max(which(tmp.nf$prop.abund <=0.4))
-  which.max.nf <- which(tmp.nf$prop.abund ==1)
-  which.min.nf <- which(tmp.nf$prop.abund ==min(tmp.nf$prop.abund))
-  tmp.nf.sub <- tmp.nf[c(which.min.nf,which.40.nf,which.max.nf),]
-  comp.all.nf[[i]] <- tmp.nf.sub
-  # Now we just want some summaries here I think...
-  comp.lam.diff[[i]] <- data.frame(min.abund = min(tmp.sub$prop.abund,na.rm=T),
-                              lam.fish.min.40 = tmp$lam.fish[which.min] - tmp$lam.fish[which.40],
-                              lam.fish.min.max = tmp$lam.fish[which.min] - tmp$lam.fish[which.max],
-                              lam.fish.40.max = tmp$lam.fish[which.40] - tmp$lam.fish[which.max],
-                              lam.nf.min.40 = tmp.nf$lam.no.fish[which.min.nf] - tmp.nf$lam.no.fish[which.40.nf],
-                              lam.nf.min.max = tmp.nf$lam.no.fish[which.min.nf] - tmp.nf$lam.no.fish[which.max.nf],
-                              lam.nf.40.max = tmp.nf$lam.no.fish[which.40.nf] - tmp.nf$lam.no.fish[which.max.nf],
-                              Stock = i,Species = tmp$G.Species[1])
-
-    comp.lam[[i]] <- data.frame(min.abund = min(tmp.sub$prop.abund,na.rm=T),
-                                lam.fish.min = tmp$lam.fish[which.min] ,
-                                lam.fish.40 = tmp$lam.fish[which.40],
-                                lam.fish.max = tmp$lam.fish[which.max],
-                                lam.nf.min = tmp.nf$lam.no.fish[which.min.nf],
-                                lam.nf.40 = tmp.nf$lam.no.fish[which.40.nf],
-                                lam.nf.max = tmp.nf$lam.no.fish[which.max.nf],
-                                Stock = i,Species = tmp$G.Species[1])
-}
-
-# A table for the estimates at 'interesting' values
-comp.lam.res <- do.call('rbind',comp.lam)
-# I want to turn this into a table....
-comp.lam.res.tab <- comp.lam.res
-# Round the numbers
-comp.lam.res.tab$min.abund <- round(comp.lam.res.tab$min.abund,digits=2)
-rounders <- c("lam.fish.min","lam.fish.40","lam.fish.max",
-              "lam.nf.min","lam.nf.40","lam.nf.max")
-comp.lam.res.tab[,rounders]      <- round(comp.lam.res.tab[,rounders] ,digits=3)
-# Now give it pretty names
-tab.names <- c("Minimum Abundance",
-               "$\\lambda_{F>0}^{Min}$",
-               "$\\lambda_{F>0}^{40}$",
-               "$\\lambda_{F>0}^{Max}$",
-               "$\\lambda_{F=0}^{Min}$",
-               "$\\lambda_{F=0}^{40}$",
-               "$\\lambda_{F=0}^{Max}$",
-               "Stock","Species")
-names(comp.lam.res.tab) <- tab.names
-
-# Now do the same with the differences
-comp.lam.diff.res <- do.call('rbind',comp.lam.diff)
-# I want to turn this into a table....
-comp.lam.diff.res.tab <- comp.lam.diff.res
-# Round the numbers
-comp.lam.diff.res.tab$min.abund <- round(comp.lam.diff.res.tab$min.abund,digits=2)
-rounders <- c("lam.fish.min.40","lam.fish.min.max","lam.fish.40.max",
-                    "lam.nf.min.40","lam.nf.min.max","lam.nf.40.max")
-comp.lam.diff.res.tab[,rounders] <- round(comp.lam.diff.res.tab[,rounders] ,digits=3)
-# Now give it pretty names
-tab.names <- c("Minimum Abundance",
-               "$\\lambda_{F>0}^{Min-40}$",
-               "$\\lambda_{F>0}^{Min-Max}$",
-               "$\\lambda_{F>0}^{40-Max}$",
-               "$\\lambda_{F=0}^{Min-40}$",
-               "$\\lambda_{F=0}^{Min-Max}$",
-               "$\\lambda_{F=0}^{40-Max}$",
-               "Stock","Species")
-names(comp.lam.diff.res.tab) <- tab.names
-
-# Used for the figure showing the number of stocks that have recovered by year x.
-n.dub <- data.frame(years = 1:n.sim.years, count = NA)
-for(i in 1:n.sim.years) n.dub$count[i] <- dub.time.summary |> collapse::fsubset(year==i & prop >= 0.75) |> nrow()
-
-# Compare the population recovery with the variance, using 2010 because all stocks have a value at 2010... 
-# I'm using the overall lambda sd, so the year doesn't actually matter other than to make sure all stocks are included here
-# This is used for the recovery variance figure, is this data good?
-# How many of the stocks had doubled by year 20, with 75% being my standard, which is a high standard
-dub.p.high <- 0.75
-dub.p.low <- 0.5
-n.dub.10 <- dub.time.summary |> collapse::fsubset(year==10 & prop >= dub.p.high) |> nrow()
-n.dub.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop >= dub.p.high) |> nrow()
-# Slow stocks, here we define having a low recovery potential has having < 50% of the simulatoins experience a doubling in size.
-slow.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop < dub.p.low) 
-prop.rec.20 <- dub.time.summary |> collapse::fsubset(year==20) # the proportion that recovers by year 20
-lambda.sds <- res.lambda.fin |> collapse::fsubset(year == 2010)
-lam.sd.p.rec <- left_join(prop.rec.20,lambda.sds,by=names(prop.rec.20)[c(1,4:24)]) 
-lam.sd.p.rec$prop.cat <- "Moderate"
-lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop < dub.p.low] <- "Low"
-lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop >= dub.p.high] <- "High"
-lam.sd.p.rec$prop.cat <- factor(lam.sd.p.rec$prop.cat,levels=c("Low","Moderate","High"))
+```{r lambda-bx-6-fig, echo=F, fig.cap="$\\lambda$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"))
 
@@
 
-```{r paper-calcs,include=F,echo=F,message=F,warning=F}
-
-# the lambda calcs
-med.lambda.F0 <- round(median(res.lambda.fin$lam.no.fish),digits=3)
-med.r.F0 <- round(median(log(res.lambda.fin$lam.no.fish)),digits=3)*100
-med.lambda.F <- round(median(res.lambda.fin$lam.fish),digits=3)
-med.r.F <- round(median(log(res.lambda.fin$lam.fish)),digits=3)*100
-mn.lambda.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
-mn.r.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
-# Mean - median...
-res.lambda.fin$med.mn.diff.no.fish <- res.lambda.fin$lam.no.fish.med - res.lambda.fin$lam.no.fish.mn
-res.lambda.fin$med.mn.diff.fish <- res.lambda.fin$lam.fish.med - res.lambda.fin$lam.fish.mn
-# How many stocks had the mean higher than the median
-n.mn.higher.med.no.fish <- length(unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.no.fish < 0]))
-n.mn.higher.med.fish <- length(unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.fish < 0]))
-low.mn.lambda.stocks <- unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.fish > 0])
-n.nw.ice <- length(c(grep("NAFO",low.mn.lambda.stocks),grep("Faroe",low.mn.lambda.stocks)))
-n.cod.low.mn <- length(grep("morhua",low.mn.lambda.stocks))
-n.cod <- length(grep("morhua",Stocks))
-
-# Density dependence related numbers
-n.bl.40 <- length(which(!is.na(comp.lam.res$lam.fish.40)))
-n.low.40.nf <- length(which(comp.lam.res$lam.nf.40 < 1))
-n.low.40.fish <-length(which(comp.lam.res$lam.fish.40 < 1))
-low.lam.40.nf <- -round(min(comp.lam.diff.res$lam.nf.40,na.rm=T),digits=3)
-low.4.lam.40.nf <- -round(sort(comp.lam.diff.res$lam.nf.40)[4],digits=3)
-
-# If right isn't this interesting!!! And look, 3 cod stocks from around here all say around 0.4 is the worst.  Most interesting...
-n.low.lam.at.max.fish <- length(which(low.gam$low.pa.fish == 1))
-n.low.lam.at.max.nf <- length(which(low.gam$low.pa.nf == 1))
-low.lam.cods <- low.gam[low.gam$low.pa.nf < 1 & low.gam$Species == "G. morhua",]
-n.cod.lam.not.at.max.nf <- nrow(low.lam.cods)
-pa.low.cod.min <- round(min(low.lam.cods$low.pa.nf),digits=2)
-pa.low.cod.max <- round(max(low.lam.cods$low.pa.nf),digits=2)
-
-# more density dependence numbers
-pa.lam.nf.at.one <- 100*round(no.stock.gam.nf.dat$prop.abund[min(which(no.stock.gam.nf.dat$fit <0))],digits=2)
-pa.lam.fish.at.one <- 100*round(no.stock.gam.fish.dat$prop.abund[min(which(no.stock.gam.fish.dat$fit <0))],digits=2)
-# What is the minimum abundance at which we get a 2 with the fishing lambdas.
-pa.big.threshold <- 0.65
-pa.low.threshold <- 0.8
-lam.low.threshold <- 0.8
-pa.lam.fish.low.bigs <- max(dd.dat$lam.fish[dd.dat$prop.abund >= pa.big.threshold])
-pa.lam.nf.low.bigs <- round(rev(sort(dd.dat$lam.no.fish[dd.dat$prop.abund >= pa.big.threshold]))[2],digits =2)
-# What proportion of the stocks had large declines overall, and then the proportion when the population was below 30%
-dd.dat.high <- dd.dat |> collapse::fsubset(prop.abund >= 0.3)
-prop.low.high.abund <- round(length(which(dd.dat.high$lam.fish < lam.low.threshold)) / nrow(dd.dat.high),digits=3)
-prop.low.all <- round(length(which(dd.dat$lam.fish < lam.low.threshold)) / nrow(dd.dat),digits=3)
-dd.dat.low <- dd.dat |> collapse::fsubset(prop.abund < 0.3)
-prop.low.low.abund <- round(length(which(dd.dat.low$lam.fish < lam.low.threshold)) / nrow(dd.dat.low),digits=3)
-
-# Numbers for the paper, lifetime reproductive growth
-r0.mn <- round(mean(pop.dam$R0.opt,na.rm=T),digits=1)
-r0.med <- round(median(pop.dam$R0.opt,na.rm=T),digits=1)
-# And fishing...
-r0.mn.fish <- round(mean(pop.dam.fish$R0.opt,na.rm=T),digits=1)
-r0.med.fish <- round(median(pop.dam.fish$R0.opt,na.rm=T),digits=1)
-
-# Where are the slow ones from
-n.not.dub.20 <- nrow(slow.20)
-n.alaska <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short== "AFSC"]))
-n.nwa <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("DFO-TRAC","NEFSC")]))
-n.nea <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("ICES")]))
-n.nafo.24 <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Area.broad %in% "NAFO 2-4"]))
-# Now the don't recover ones...
-n.alaska.slow <- length(slow.20$Stock.short[slow.20$Manage.short== "AFSC"])
-n.nwa.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% c("DFO-TRAC","NEFSC")])
-n.nea.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% "ICES"])
-
-# Need to grab all the per.diff's, which I seem to have dropped
-for.diffs <- do.call('rbind',for.tune.summary)
-med.per.diff <- round(median(for.diffs$per.diff,na.rm=T),digits=1)
-# what is lambda difference, about 6%, but that means the original was 7% higher, so that means we are reducing lambda when optimizing
-# If there was 'missing fishing' we are compensating for with this, this is exactly what we'd expect to happen right?
-res.lambda.fin$lam.per.diff <- 100*((res.lambda.fin$lam.org.no.fish - res.lambda.fin$lam.no.fish)/ res.lambda.fin$lam.no.fish)
-med.lam.per.diff <- round(median(res.lambda.fin$lam.per.diff,na.rm=T),digits=1)
-# By stock, can see most are positive, which is in line with missing fishing mortality...
-mod.by.stock.lam.pd <- res.lambda.fin |> collapse::fgroup_by(Stock.short) |> collapse::fsummarise(med = median(lam.per.diff,na.rm=T),
-                                                                                                  mn = mean(lam.per.diff,na.rm=T))
+\newpage
+```{r lambda-bx-other-fig, echo=F, fig.cap="$\\lambda$ estimates for the remainded of the stocks in this analysis, plotted by the location of the stock.
+The abreviated species name is provided on the x axis."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"))
 
@@
 
-```{r main-figs,include=F,echo=F,message=F,warning=F}
-
-# New lambda plot with the fishing and no fishing beside each other
-# This is likely Figure 1
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Stock.no.species),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(G.Species),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 19,base_height = 15)
-
-# The other stocks, perhaps we put this in a supplement...
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(y=lambda,interaction(group,G.Species.short),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(Area.long),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 19,base_height = 15)
-
-# Standard deviation figure
-colrs.sd <- rep(c(rep('blue',4),rep('orange',4),rep('grey',4),rep('black',4)),20)
-pty.sd <- rep(rep(c(21,4,9,8),4),20)
-
-lam.sd.plt <- ggplot(res.lambda.fin ) + 
-                                       geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
-                                       scale_y_log10("Standard deviation (Lambda)",log_breaks(n=8)) +
-                                       scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
-                                       theme(axis.text.x = element_text(angle =45,hjust=1),
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 10)
-
-# Overall density dependence
-# MAIN PAPER FIGURE#
-dd.nf.overall.plt <-ggplot(no.stock.gam.nf.dat , aes(x=prop.abund,y=exp(fit))) + 
-                                geom_point(data = dd.dat,aes(x=prop.abund,y=lam.no.fish),size=2,alpha=0.1) +  
-                                geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI)),alpha=0.5,linewidth=0,fill=u.colors[1])+
-                                geom_line(color=u.colors[1],linewidth=1) + 
-                                xlab("") + 
-                                scale_y_log10(name = "Lambda(F=0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_blank()) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-# MAIN PAPER FIGURE#
-dd.fish.overall.plt <- ggplot(no.stock.gam.fish.dat, aes(x=prop.abund,y=exp(fit))) + 
-                                geom_point(data = dd.dat,aes(x=prop.abund,y=lam.fish),size=2,alpha=0.1) +  
-                                geom_line(color=u.colors[2],linewidth=2) + 
-                                geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI)),alpha=0.5,fill=u.colors[2])+
-                                xlab("") + 
-                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed',linewidth=1.5)+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_blank()) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-# Main Paper Figure Density dependence with and without fishing, effectively a zoomed in version of the above.
-colrs <- u.colors
-t.smooth <- rbind(no.stock.gam.fish.dat,no.stock.gam.nf.dat)
-dd.fish.nf.plt <- ggplot(t.smooth, aes(x=prop.abund,y=exp(fit),group=Scenario,color=Scenario,fill=Scenario)) + 
-                                 geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI),group=Scenario,fill=Scenario),alpha=0.50,linewidth=0)+
-                                 geom_line(linewidth=1.5) +
-                                 geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                 scale_fill_manual(values = colrs) + scale_color_manual(values = colrs) +
-                                 scale_x_continuous(name = "Proportion of maximum abundance",breaks = seq(0,1,by=0.1)) + 
-                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-                                 theme(legend.position = c(0.9,0.75))
-
-dd.overall.combo <- plot_grid(dd.nf.overall.plt,dd.fish.overall.plt,dd.fish.nf.plt,nrow=3)
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_overall_",what.2.tune,".png"),dd.overall.combo,base_width = 10,base_height = 10)
-
-new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(y=lambda,interaction(group,G.Species.short),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(Area.long),design=mat,scales='free_x')
-
-# Density dependence by stock 
-cols.gam <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
-pty.gam <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
-# Doing this manually because the ordered factor wasn't working... annoying...
-mat <- matrix(c(2, 2,13,13, 5, 5, 9, 9,
-                3, 3,12,12, 6, 6, 8, 8,
-               NA,NA,10,10,11,11,NA,NA,
-               NA,7, 7, 4, 4, 1, 1, NA),
-                4, 8, byrow = TRUE)
-
-dd.stocks.nf.plt <- ggplot(pred.dd.stock.gam.ss.nf,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=G.Species,shape=G.Species)) + 
-                                geom_line() + 
-                                geom_point(data = thin.pred.nf,size=2) +  
-                                xlab("Proportion of maximum abundance") + 
-                                scale_y_log10(name = "Lambda (F=0)",breaks = log_breaks(n=10)) +
-                                geom_ribbon(aes(ymin=lower,ymax=upper,color=G.Species),alpha=0.10,linewidth=0)+
-                                facet_manual(vars(Area.long),design=mat,scales='free_x')+
-                                #facet_wrap(~Area.long)  +
-                                scale_shape_manual(values=pty.gam) +
-                                scale_color_manual(values = cols.gam) + 
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_text(size=7)) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"),dd.stocks.nf.plt,base_width = 10,base_height = 10)
-
-mat <- matrix(c(2, 2,13,13, 5, 5, 9, 9,
-                3, 3,12,12, 6, 6, 8, 8,
-               NA,NA,10,10,11,11,NA,NA,
-               NA,7, 7, 4, 4, 1, 1, NA),
-                4, 8, byrow = TRUE)
-
-# MAIN PAPER FIGURE#
-dd.stocks.fish.plt <- ggplot(pred.dd.stock.gam.ss.fish,aes(x=prop.abund,y=lam.fish,group=Stock.short,color=G.Species,shape=G.Species)) + 
-                                geom_line() + 
-                                geom_point(data = thin.pred.fish,size=2) +  
-                                geom_ribbon(aes(ymin=lower,ymax=upper,color=G.Species),alpha=0.10,linewidth=0)+
-                                xlab("Proportion of maximum abundance") + 
-                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10)) +
-                                facet_manual(vars(Area.long),design=mat,scales='free_x')+
-                                #facet_wrap(~Area.long)  +
-                                scale_shape_manual(values=pty.gam) +
-                                scale_color_manual(values = cols.gam) + 
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_text(size=7)) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_fish_stocks_",what.2.tune,".png"),dd.stocks.fish.plt,base_width = 10,base_height = 10)
-
-# Lifetime reproductive success 
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-r0.boxplt.6 <- ggplot(pop.dam.all.6) + geom_boxplot(aes(y=R0.opt,interaction(group,Stock.no.species),color=group))  + 
-                                       scale_x_discrete(NULL, guide = "axis_nested") + scale_y_log10(name = "Lifetime Reproductive Output")+
-                                       geom_hline(yintercept = 1,linetype='dashed',color='blue')+
-                                       facet_manual(vars(G.Species),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"),r0.boxplt.6,base_width = 19,base_height = 15)
-
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-r0.boxplot.others <- ggplot(pop.dam.all.others) +   geom_boxplot(aes(y=R0.opt,interaction(group,G.Species.short),color=group))  + 
-                                                    scale_x_discrete(NULL, guide = "axis_nested") + 
-                                                    scale_y_log10(name = "Lifetime Reproductive Output")+
-                                                    geom_hline(yintercept = 1,linetype='dashed',color='blue')+
-                                                    facet_manual(vars(Area.long),design=mat,scales='free')+
-                                                    theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                          plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"),r0.boxplot.others,base_width = 15,base_height = 10)
-
-r0.heatmap.ne <- ggplot(pop.dam |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-r0.heatmap.nw <- ggplot(pop.dam |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-r0.heatmap.pac <- ggplot(pop.dam |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                     xlab("") + ylab("")+
-                                     facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                     geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                     theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                           legend.key.width = unit(3,'cm'))
-
-r0.heatmap <- cowplot::plot_grid(r0.heatmap.pac,r0.heatmap.nw,r0.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_nf_",what.2.tune,".png"),r0.heatmap,base_width = 20,base_height = 17)
-
-r0.heatmap.ne.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-r0.heatmap.nw.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-r0.heatmap.pac.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                     xlab("") + ylab("")+
-                                     facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                     geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                     theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                           legend.key.width = unit(3,'cm'))
-
-r0.heatmap.fish <- cowplot::plot_grid(r0.heatmap.pac.fish,r0.heatmap.nw.fish,r0.heatmap.ne.fish,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_fish_",what.2.tune,".png"),r0.heatmap.fish,base_width = 20,base_height = 17)
-
-# Generation length
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-gen.boxplt.6 <- ggplot(pop.dam.all.6) +
-                            geom_boxplot(aes(y=gen.len.opt,interaction(group,Stock.no.species),color=group))  + 
-                            scale_x_discrete(NULL, guide = "axis_nested") +
-                            scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
-                             facet_manual(vars(G.Species),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"),gen.boxplt.6,base_width = 19,base_height = 15)
-
-# Then the generation length for others.
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-gen.boxplt.others <- ggplot(pop.dam.all.others) +
-                            geom_boxplot(aes(y=gen.len.opt,interaction(group,G.Species.short),color=group))  + 
-                            scale_x_discrete(NULL, guide = "axis_nested") +
-                            scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
-                            facet_manual(vars(Area.long),design=mat,scales='free')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"),gen.boxplt.others,base_width = 15,base_height = 10)
-
-gen.heatmap.ne <- ggplot(pop.dam |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
-                                              xlab("") + ylab("")+  
-                                              facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                              geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-gen.heatmap.nw <- ggplot(pop.dam |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-gen.heatmap.pac <- ggplot(pop.dam |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
-                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-gen.heatmap <- cowplot::plot_grid(gen.heatmap.pac,gen.heatmap.nw,gen.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_nf_",what.2.tune,".png"),gen.heatmap,base_width = 15,base_height = 10)
-
-gen.heatmap.ne.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
-                                              xlab("") + ylab("")+  
-                                              facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                              geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-gen.heatmap.nw.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-gen.heatmap.pac.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
-                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-gen.heatmap.fish <- cowplot::plot_grid(gen.heatmap.pac.fish,gen.heatmap.nw.fish,gen.heatmap.ne.fish,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_fish_",what.2.tune,".png"),gen.heatmap.fish,base_width = 15,base_height = 10)
-
-dub.time.summary <- dub.time.summary |> collapse::fsubset(year %in% 1:50) |>
-                            collapse::roworder(G.Species,LME,Area.broad) |>
-                            collapse::fmutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-dub.heatmap.gad <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Gadiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+                                    
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.45, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.pl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Pleuronectiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+                                    
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"))
-
-dub.heatmap.cl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Clupeiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.35, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.per <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Perciformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.scom <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Scombriformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2.1, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.scorp <- ggplot(dub.time.summary |> collapse::fsubset(Order %in% "Scorpaeniformes "), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + 
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.5, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap <- cowplot::plot_grid(dub.heatmap.gad,dub.heatmap.pl,dub.heatmap.cl,dub.heatmap.per,dub.heatmap.scom,dub.heatmap.scorp,
-                                  nrow = 6,rel_heights = c(39,20,11,4,3,3))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"),dub.heatmap,base_width = 20,base_height = 20)
-
-# Doubling Time Figure 1
-dub.ts.plt <- ggplot(n.dub,aes(x=years,y=count)) + 
-                    geom_line() + 
-                    geom_hline(yintercept = length(Stocks),linetype="dashed") + 
-                    xlab("") + ylab("Number of Stocks")
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_time_series_",what.2.tune,".png"),dub.ts.plt,base_width = 10,base_height = 10)
-
-# Doubling time and variability
-
-# Is there a relationship between median and sd?
-colrs.cat <- c("blue","black","orange")
-pts.cat <- 21:23
-sd.rec.plt <- ggplot(lam.sd.p.rec, aes(y=lam.no.fish.med,x=lam.no.fish.sd,color=prop.cat,group=prop.cat)) + 
-                       geom_point(size =3,aes(shape=prop.cat,fill=prop.cat)) + 
-                       geom_hline(yintercept=1,linetype="dashed") + 
-                       scale_y_continuous(name="median Lambda") + scale_x_continuous(name="standard deviation Lambda") +
-                       scale_color_manual(values=colrs.cat) + scale_fill_manual(values=colrs.cat) +  
-                       scale_shape_manual(values=pts.cat) + theme(legend.title = element_blank())
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"),sd.rec.plt,base_width = 10,base_height = 10)
-
+\newpage
+```{r lambda-sd-fig, echo=F, fig.cap="Standard deviation of the $\\lambda$ estimates for each stock, ordered by species, in this analysis. "}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"))
 ```
 
-```{r the-others,include=F,echo=F,message=F,warning=F}
-#             
-# 
-# dub.heatmap.cod <- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "G.
-morhua"), aes(x=year, y=Stock.no.species, fill= prop)) + xlab("") + ylab("")+                                     facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") +
-#                             geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + scale_x_continuous(labels=NULL) +
-#                             theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-#                                   legend.key.width = unit(3,'cm'))
-# 
-# dub.heatmap.herring<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "C. harengus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-# 
-# dub.heatmap.haddock<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "M. aeglefinus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.125, "cm"))
-# 
-# dub.heatmap.virens<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. virens"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.4, "cm"))
-# 
-# dub.heatmap.solea<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "S. solea"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-# 
-# dub.heatmap.platessa<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. platessa"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous() +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
-# 
-# 
-# 
-# dub.heatmap.sp6 <- cowplot::plot_grid(dub.heatmap.cod,dub.heatmap.herring,dub.heatmap.haddock,
-#                                  dub.heatmap.virens, dub.heatmap.solea,dub.heatmap.platessa,nrow = 6,rel_heights = c(14,9,8,5,5,4))
-# dub.heatmap.sp6
-# 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_sp6_",what.2.tune,".png"),dub.heatmap.sp6,base_width = 20,base_height = 17)
-# 
-# 
-# # What about a plot of the sd of lamda by stock
-# #colrs.sd <- rep(rep(c("black","blue","orange",'grey'),3),20)
-# #pty.sd <- rep(c(rep(21,4),rep(4,4),rep(9,4)),20)
-# 
-# 
-# # Same plot for the not 6 species
-# 
-# # lam.sd.other.plt <- ggplot(res.lambda.fin |> collapse::fsubset(!Species %in% six.species)) + 
-# #                                        geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
-# #                                        scale_y_log10("sd(lambda)",limits=c(0.05,1.5)) +
-# #                                        scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
-# #                                        theme(axis.text.x = element_text(angle =45,hjust=1),
-# #                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# # lam.sd.other.plt
-# 
-# 
-# 
-# 
-# # Doubling Times
-# 
-# 
-# # Generation length
-# 
-# # Main text figure!!
-# new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Area.long),color=group)) +
-#                                            #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-#                                            scale_x_discrete(NULL, guide = "axis_nested") +
-#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~G.Species,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# # The other stocks, plotting these by area
-# # Main Text FIGURE!
-# # More data
-# 
-# 
-# ################### Supplemental Figures################### Supplemental Figures################### Supplemental Figures################### Supplemental 
-# 
-# 
-# 
-# # Time series of lambdas....
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# #col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
-# pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
-# #pty <- rep(rep(c(21:23),5),20)
-# 
-# lambda.ts.plt <- ggplot(res.lambda.final.6,aes(y=lam.fish,x=year,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
-#                             geom_point(size=4) +
-#                             geom_smooth(method='gam',formula = y ~ s(x, bs = "cs", fx = TRUE, k = 5),se=F) + 
-#                             #scale_y_log10(name = "lambda") +
-#                             facet_wrap(~G.Species,scales='free_y') +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-#                             scale_fill_manual(name = "Stock",values = col.try)+
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm'))
-# #lambda.ts.plt
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_timeseries_6_",what.2.tune,".png"),lambda.ts.plt,base_width = 12,base_height = 10)
-# 
-# 
-# lambda.dec.plt <- ggplot(res.lambda.final.6,aes(y=med.lam,x=as.factor(decade))) +
-#                             geom_boxplot() + scale_y_log10()+
-#                             xlab("Decade") + ylab("Lambda") + 
-#                             geom_point(aes(x=as.factor(decade),y=lm.spec.mn),color='blue',shape=8,fill='blue')+
-#                             #scale_x_continuous(breaks=seq(1940,2020,by=10))+
-#                             geom_hline(yintercept = 1,linetype='dashed') +
-#                             facet_wrap(~G.Species,scales='free_y') 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_by_decade_6_",what.2.tune,".png"),lambda.dec.plt,base_width = 12,base_height = 12)
-# 
-#
-
-# ggplot(dd.dat) + geom_point(aes(x=prop.abund,y=lam.no.fish-1)) + xlab("Proportion of Maximum Abundance") + ylab("r (no fishing)")
-# 
-# # Density dependence by Species
-# ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
-#                                                    geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) #+
-#                                                    #scale_color_manual(values = colrs)
-# # Density dependence by stock
-# ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Stock.short,group=Stock.short)) + geom_point() + 
-#                                                    geom_smooth(method="lm",se = F) + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)", limits=c(0.4,2),
-#                                                                  breaks = seq(0.4,2,by=0.1)) +
-#                                                    theme(legend.position = 'none')
-# 
-# 
-# 
-# 
-# ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish)) + geom_point() + 
-#                                                     geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_continuous(name = "lambda (no fishing)")
-# 
-# ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + geom_point() + 
-#                                                     geom_smooth(method="lm",se=F) + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,2,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)")
-# 
-# 
-# # how about our big 6
-# colrs <- c("blue","black","firebrick2","orange",'grey50','grey90')
-# ggplot(dd.dat.six,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
-#                                                     geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) +
-#                                                    scale_color_manual(values = colrs)
-# 
-# 
-# ggplot(dd.dat.six.no.bigs,aes(x=prop.abund,y=lam.no.fish-1,color=Species,group=Species)) + geom_point() + 
-#                                                     geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 0,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_continuous(name = "r (no fishing)", breaks = seq(-1,1,by=0.2)) +
-#                                                    scale_color_manual(values = colrs)
-
-# Other things I did just randomly scattered here
-
-# 
-# #hmm <- merge(tst,res.lambda.final.6,by="Stock")
-# plot(res.lambda.fin$lam.fish.med ~ res.lambda.fin$lam.fish.mn)
-# # So this is lambda with fishing included
-# lambda.plt <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.no.fish,x=Stock.no.species))  + 
-#                                            geom_point(aes(y=lam.no.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~G.Species,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_no_fishing_6_",what.2.tune,".png"),lambda.plt,base_width = 12,base_height = 10)
-# 
-# # With fishing
-# lambda.plt.fish <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.fish,x=Stock.no.species))  + 
-#                                            geom_point(aes(y=lam.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~G.Species,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_with_fishing_6_",what.2.tune,".png"),lambda.plt.fish,base_width = 12,base_height = 10)
-# 
-# 
-# 
-# new.lam.plt <- ggplot(res.lambda.fin.long) + geom_boxplot(aes(y=lambda,interaction(group,Order),color=group)) +
-#                                            #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-#                                            scale_x_discrete(NULL, guide = "axis_nested") +
-#                                            #xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            #geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~Area.long,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# 
-# # The final option I have is to do what I did before and use the bin props
-# We can then do a much more ANOVA kinda analysis, drat this doesn't converge..., estimate the 
-#mod.dd.bins.stock <- glmer(lam.no.fish ~ prop.bin + (1+prop.bin|Stock),data=dd.dat,family=gaussian(link='log'))
-# so go to lmer and log transform... and it is a singular fit
-#mod.dd.bins.stock <- lmer(lam.no.fish ~ prop.bin + (1+prop.bin|Stock),data=dd.dat)
-# So is an intercept model of any real use?
-# mod.dd.bins.stock <- lmer(log(lam.no.fish) ~ prop.bin + (1+prop.bin|Stock.short),data=dd.dat)
-# # A non-random effect model does work with the interaction... I'd much rather lmer....
-# #mod.dd.bins.stock <- lm(lam.no.fish ~ prop.bin*Stock,data=dd.dat)
-# summary(mod.dd.bins.stock)
-# #Residuals, nah, still suck, just some crazy outliers...
-# plot(mod.dd.bins.stock)
-# # Normality = terrible...
-# qqnorm(residuals(mod.dd.bins.stock))
-# qqline(residuals(mod.dd.bins.stock))
-# # So we can predict this ANOVA thing...
-# pred.dd.stock.bins <- expand.grid(prop.bin = unique(dd.dat$prop.bin),
-#                                          #Species=unique(dd.dat$Species),
-#                                          Stock.short=unique(dd.dat$Stock.short))
-# tmp <- predict(mod.dd.bins.stock, pred.dd.stock.bins, type = 'response', se.fit = TRUE) 
-# pred.dd.stock.bins$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.stock.bins$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.stock.bins$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Now to do fun things I need the meta data on the pred dataframe
-# pred.dd.stock.bins <- left_join(pred.dd.stock.bins,meta.sub,by="Stock.short")
-# # Now a problem here is that this includes estimates for bins in which we don't have data.
-# # So we do want to get rid of those
-# real.bins <- unique(paste(dd.dat$Stock.short,"_",dd.dat$prop.bin))
-# # All the bins in the predict object with same names same name...
-# pred.dd.stock.bins$bin.combos <- paste(pred.dd.stock.bins$Stock.short,"_",pred.dd.stock.bins$prop.bin)
-# # Now toss all the predicted bins without data.
-# pred.dd.stock.bins <- pred.dd.stock.bins |> collapse::fsubset(bin.combos %in% real.bins)
-# 
-# # By region
-# cols.1 <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
-# #col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
-# pty.1 <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
-# ggplot(pred.dd.stock.bins,aes(x=prop.bin,y=lam.no.fish,group=Stock.short,color=G.Species)) + 
-#                                 geom_point(aes(shape=G.Species),size=2) + geom_line()  + xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 facet_wrap(~Area.long)  +
-#                                 scale_shape_manual(values=pty.1) +
-#                                 scale_color_manual(values = cols.1) + 
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-# 
-# # By Species
-# ggplot(pred.dd.stock.bins,aes(x=prop.bin,y=lam.no.fish,group=Stock.short,color=Area.long)) + 
-#                                 geom_point(aes(shape=Area.long)) + geom_line()  + xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 facet_wrap(~Order)  +
-#                                 scale_shape_manual(values=pty.1) +
-#                                 scale_color_manual(values = cols.1) + 
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-# 
-# # No fish vs fish lambda, note that DD is weaker when we account for fishing, that seems a fun result to talk about!
-# 
-# mod.dd.overall.gam.nf <- lm(log(lam.no.fish) ~ (prop.abund),data=dd.dat)
-# mod.dd.overall.gam.fish <- lm(log(lam.fish) ~ (prop.abund),data=dd.dat)
-# 
-# 
-# pred.dd.overall.bins.nf <- data.frame(prop.abund = seq(0,1,length.out=500),group = "F = 0")
-# pred.dd.overall.bins.fish <- data.frame(prop.abund = seq(0,1,length.out=500),group = "F > 0")
-# tmp <- predict(mod.dd.overall.gam.nf, pred.dd.overall.bins, type = 'response', se.fit = TRUE) 
-# tmp.fish <- predict(mod.dd.overall.gam.fish, pred.dd.overall.bins, type = 'response', se.fit = TRUE) 
-# pred.dd.overall.bins.nf$lam   <- exp(tmp$fit)
-# pred.dd.overall.bins.nf$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.overall.bins.nf$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# 
-# pred.dd.overall.bins.fish$lam   <- exp(tmp.fish$fit)
-# pred.dd.overall.bins.fish$lower <- exp(tmp.fish$fit - 1.96 * tmp.fish$se.fit)
-# pred.dd.overall.bins.fish$upper <- exp(tmp.fish$fit + 1.96 * tmp.fish$se.fit)
-# 
-# pred.dd.overall <- rbind(pred.dd.overall.bins.fish,pred.dd.overall.bins.nf)
-# 
-# ggplot(pred.dd.overall,aes(y=lam,x=prop.abund,group=group,color=group)) + 
-#                                                   geom_line(linewidth=2) + 
-#                                                   geom_ribbon(aes(ymin=lower,ymax=upper),alpha=0.2) + 
-#                                                   geom_hline(yintercept=1,linetype='dashed') + 
-#                                                   xlab("Proportion of Maximum Abundance") + ylab("Lambda")
-# 
-# # OK, so if we compare the 40-60 bin with the 80-100 bin we should see the lambda's in the 40-60 bin are higher...
-# 
-# res.40.60 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("40-60%"))
-# names(res.40.60)[names(res.40.60) == 'lam.no.fish'] <- "lam.40.60"
-# res.80.100 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("80-100%"))
-# names(res.80.100)[names(res.80.100) == 'lam.no.fish'] <- "lam.80.100"
-# 
-# tst <- left_join(res.40.60,res.80.100, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.40.60 - tst$lam.80.100
-# 
-# hist(tst$diff)
-# 
-# res.lt.10 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("< 10%"))
-# names(res.lt.10)[names(res.lt.10) == 'lam.no.fish'] <- "lam.lt.10"
-# 
-# tst <- left_join(res.40.60,res.lt.10, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.lt.10 - tst$lam.40.60
-# 
-# hist(tst$diff)
-# 
-# res.10.20 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("10-20%"))
-# names(res.10.20)[names(res.10.20) == 'lam.no.fish'] <- "lam.10.20"
-# 
-# tst <- left_join(res.40.60,res.10.20, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.10.20 - tst$lam.40.60
-# 
-# hist(tst$diff)
-# 
-# 
-# res.20.30 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("20-30%"))
-# names(res.20.30)[names(res.20.30) == 'lam.no.fish'] <- "lam.20.30"
-# 
-# tst <- left_join(res.40.60,res.20.30, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.20.30 - tst$lam.40.60
-# 
-# hist(tst$diff)
-# 
-# res.30.40 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("30-40%"))
-# names(res.30.40)[names(res.30.40) == 'lam.no.fish'] <- "lam.30.40"
-# 
-# tst <- left_join(res.40.60,res.30.40, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.30.40 - tst$lam.40.60
-# 
-# hist(tst$diff)
-
-# 
-# 
-# dd.dat.no.bigs <- dd.dat |> collapse::fsubset(lam.no.fish < 2)
-# dd.dat.six.no.bigs <- dd.dat.six |> collapse::fsubset(lam.no.fish < 2)
-# just.bigs <- dd.dat  |> collapse::fsubset(lam.no.fish > 2) 
-# sum(table(just.bigs$Stock.short)) # 48 of 68 are Haddock or cod. 13 of remaining 20 are small low trophic species
-# 
-# dd.dat$lam.ratio <- dd.dat$lam.org.no.fish/dd.dat$lam.no.fish
-# dd.dat$lam.ratio.z <- dd.dat$lam.org.fish/dd.dat$lam.fish
-# So the original lambda tended to be somewhere between 7 and 14% higher, depending on me(di)an choice.
-# Could be way off in some years for a few species (Haddock, Cod, Sand lance, horse makerel, pilchard(sardine)... interesting... )
-# summary(dd.dat$lam.ratio)
-# summary(dd.dat$lam.ratio.z)
-# ggplot(dd.dat,aes(y=lam.ratio,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
-# ggplot(dd.dat,aes(y=lam.ratio.z,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
-
-# Playing around to look at explanations for what we see, looked by LME, low and high stocks, but no smoking guns!
-# low.stocks <- unique(dd.dat$Stock.short[dd.dat$prop.abund <= 0.1])
-# dd.lows <- dd.dat |> collapse::fsubset(Stock.short %in% low.stocks)
-# dd.highs <- dd.dat |> collapse::fsubset(!Stock.short %in% low.stocks)
-# mod.dd.stock.gam.lows <- gam(log(lam.no.fish) ~ s(prop.abund,k=4) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.lows )
-# mod.dd.stock.gam.highs <- gam(log(lam.no.fish) ~ s(prop.abund,k=4) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.highs )
-# 
-# pred.dd.stock.gam.tst <- expand.grid(prop.abund = seq(0, 1, length.out = 50),
-#                                          Stock.short = c("Overall",unique(dd.highs$Stock.short)))
-# 
-# tmp <- predict(mod.dd.stock.gam.highs, pred.dd.stock.gam.tst, type = 'response', se.fit = TRUE) 
-# pred.dd.stock.gam.tst$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.stock.gam.tst$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.stock.gam.tst$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# 
-# ggplot(pred.dd.stock.gam.tst |> collapse::fsubset(Stock.short=='Overall'), aes(x=prop.abund,y=lam.no.fish)) + 
-#                                 geom_point(data = hmm,aes(x=prop.abund,y=lam.no.fish),size=2,alpha=0.1) +  
-#                                 geom_line(color='blue',linewidth=2) + 
-#                                 xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-# 
-# 
-# ggplot(pred.dd.stock.gam.tst,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short,shape=Stock.short)) + 
-#                                 geom_line() + 
-#                                 #geom_point(data = thin.pred,size=2) +  
-#                                 xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 #facet_wrap(~Area.long)  +
-#                                 #scale_shape_manual(values=pty.gam) +
-#                                 #scale_color_manual(values = cols.gam) + 
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-
-# Is there any density dependence in fishing mortality??
-# dd.dat$mu <- dd.dat$removals/dd.dat$vpa.abund
-# dd.dat$fm <- -log(1-dd.dat$mu)
-# 
-# ggplot(dd.dat , aes(x=prop.abund,y=fm)) + 
-#                                 geom_point() + 
-#                                 geom_smooth(method = 'gam') + 
-#                                 scale_x_continuous(name="Proportion of Maximum Abundance") +
-#                                 scale_y__continuous(name = "Fishing Mortality (instantaneous)")
-# 
-# 
-# qqnorm(log(dd.dat$mu))
-# qqline(log(dd.dat$mu))
-# hist(log(dd.dat$mu))
-# 
-# fm.mod <- lm(log(fm)~prop.abund,data=dd.dat)
-# par(mfrow=c(2,2))
-# plot(fm.mod)
-# par(mfrow=c(1,1))
-
-# windows(11,11)
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
-
-# 
-# r0.ts.plt <- ggplot(pop.dam.6,aes(y=R0.opt,x=cohort,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) + 
-#                             geom_line(size=2)  + geom_point(size=4) +
-#                             scale_y_log10(name = "Lifetime Reproductive Output") +
-#                             facet_wrap(~G.Species) +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-#                             scale_fill_manual(name = "Stock",values = col.try)+
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
-# r0.ts.plt
-# 
-# save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_6.png",r0.ts.plt,base_width = 30,base_height = 12)
-# 
-# r0.boxplt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
-#                             facet_wrap(~G.Species,scales = 'free')+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none')
-# r0.boxplt
-
-# 
-# windows(11,11)
-# ggplot(pop.dam) + geom_boxplot(aes(y=gen.len.opt,x=Species)) + facet_wrap(~LME,scales='free_x') +
-#                   ylab("Generation Length (years)") + theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# windows(11,11)
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# lty <- rep(c(rep(1,5),rep(2,5),rep(4,5)),20)
-# 
-# gen.ts.plt <- ggplot(pop.dam.6,aes(y=gen.len.opt,x=cohort,group=Stock.short,color=Stock.short,linetype = Stock.short)) + 
-#                             geom_line(size=2)  + 
-#                             scale_y_log10(name = "Generation Length") +
-#                             facet_wrap(~G.Species) +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_linetype_manual(name = "Stock",values = lty) +
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
-# gen.ts.plt
-# save_plot("D:/Github/ICM/Figures/tuned/Gen_time_series_6.png",gen.ts.plt,base_width = 20,base_height = 12)
-
-# 
-# ggplot(for.tunes) + geom_jitter(aes(y=lambda,x=Species,group=Stock.short,color=Stock.short)) + 
-#                     scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10)) +
-#                             theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# ggplot(for.tunes) + geom_jitter(aes(y=lambda.vpa.init,x=Species)) + scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))
-# 
-# unique(for.tunes$Species)
-# windows(11,11)
-# 
-# ggplot(for.tunes) + geom_density(aes(lambda,group=Species,color=Species,fill=Species),alpha = 0.2) + scale_x_continuous(breaks = c(0,0.5,1,2,5,10))
-# 
-# 
-# #options(scipen=999)
-# r0.plt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.05,0.1,0.5,1,5,10,50,100),minor_breaks = NULL) + 
-#                             facet_wrap(~Species,scales = 'free')+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1))
-# save_plot("D:/Github/ICM/Figures/tuned/R0_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
-# 
-# 
-# 
-# vickis.cols <- sort(rep(c( "#172582",  "#F8DC91", "#FBB891", "#FB6A01", "#B80000"),3))
-# linetypes <- rep(c(1,2,4),5)
-# 
-# windows(11,11)
-# cod.r0.ts.plt <- ggplot(pop.dam |> collapse::fsubset(Species == 'morhua')) + geom_line(aes(y=R0.opt,x=cohort,group=Area,color=Area,linetype=Area),size=1.5)  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output", breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
-#                             scale_color_manual(values = vickis.cols) +
-#                             scale_linetype_manual(values = linetypes) +
-#                             theme(legend.key.width  = unit(2, "cm"))
-# cod.r0.ts.plt
-# #save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
-# 
-# 
-# windows(11,11)
-# ggplot(pop.dam |> collapse::fsubset(Species =="morhua")) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
-#                                                         scale_y_log10(name = "Lifetime Reproductive Output",breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) +
-#                                                         theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# # Missing catch questions
-# # first did we do much to the Fecundity term to get here
-# quantile(for.tunes$mean.fec/for.tunes$mean.vpa.fec,probs=seq(0.01,1,0.01),na.rm=T)
-# 
-# quantile((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init,probs=seq(0.01,1,0.01),na.rm=T)
-# quantile((for.tunes$mean.nm-for.tunes$mean.vpa.nm)/for.tunes$mean.vpa.nm,probs=seq(0.01,1,0.01),na.rm=T)
-# 
-# for.tunes$excess.catch <- for.tunes$removals-for.tunes$removals.init
-# for.tunes$per.excess.catch <- 100*((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init)
-# 
-# windows(11,11)
-# bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Species)) + 
-#                                    ylab("Adjustment to catch (%)") +
-#                                    theme(axis.text.x = element_text(angle=45,hjust = 1))
-#                                    
-# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_species.png",bycatch.plt,base_width = 8,base_height = 8)
-#                                    
-# bycatch.plt.cod <- ggplot(for.tunes |> collapse::fsubset(Species == 'morhua')) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + 
-#                                                                               ylab("Adjustment to catch (%)") +
-#                                                                               theme(axis.text.x = element_text(angle=45,hjust = 1))
-#                                                                               
-# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_cod_stock.png",bycatch.plt.cod,base_width = 8,base_height = 8)
-# 
-# # bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + facet_wrap(~Species,scales = 'free_x')
-# #                                    ylab("Adjustment to catch (%)") +
-# #                                    theme(axis.text.x = element_text(angle=45,hjust = 1))
-# # bycatch.plt                                   
-#
-
-# Doubling time for the rest of the stocks...
-
-# dub.heatmap.no.6 <- ggplot(dub.time.summary |> collapse::fsubset(!Species %in% six.species), aes(x=year, y=Stock.short, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               #facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + 
-#                               scale_x_continuous() +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
+\newpage
+```{r dd-overall-plt, echo=F, fig.cap="Density dependence of $\\lambda$ The top panel shows $\\lambda_{F=0}$ against the proportion of maximum abundance, with a GAM smooth and the GAM estimated 95\\% confidence interval.
+The middle panel shows $\\lambda_{F>0}$ against the proportion of maximum abundance, with a GAM smooth and the GAM estimated 95% confidence interval.
+The bottom panel compares the GAM smooths for $\\lambda_{F=0}$ and $\\lambda_{F>0}$."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_overall_",what.2.tune,".png"))
 ```
 
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
+\newpage
+```{r dd-nf-stock-plt, echo=F, fig.cap="Density dependence of $\\lambda_{F=0}$ for each stock in the analysis plotted regionally."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"))
+```
 
-```{r failed-models}
+\newpage
+```{r dd-fish-stock-plt, echo=F, fig.cap="Density dependence of $\\lambda_{F>0}$ for each stock in the analysis plotted regionally."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_fish_stocks_",what.2.tune,".png"))
+```
 
-# A density dependence model, start simple and build...
-# mod.dd.base <- lm(log(lam.no.fish) ~ prop.abund,data=dd.dat)
-# summary(mod.dd.base)
-# 
-# mod.dd.base.fish <- lm(log(lam.fish) ~ prop.abund,data=dd.dat)
-# summary(mod.dd.base.fish)
-# #ggplot(dd.dat, aes(y = lam.no.fish,x=prop.abund)) + geom_point() + geom_smooth(method = 'lm') + scale_y_log10() + geom_hline(yintercept = 1,color='firebrick2',linetype='dashed',linewidth=2)
-# 
-# 
-# # Residuals are nowhere near normal, the fit isn't a disaster but def have the old trumpet shape happening
-# par(mfrow=c(2,2))
-# plot(mod.dd.base)
-# par(mfrow=c(1,1))
-# # This mostly represents the above model...
-# ggplot(dd.dat, aes(y = lam.no.fish,x=prop.abund)) + 
-#                   geom_point() + 
-#                   geom_smooth(method = 'lm') + scale_y_log10() +
-#                   geom_hline(yintercept = 1,color='firebrick2',linetype='dashed',linewidth=2)
-# # What happens with a gam?
-# mod.dd.gam.base <- gam(log(lam.no.fish) ~ s(prop.abund),data=dd.dat)
-# summary(mod.dd.gam.base)
-# # Still see that the residuals are higher at low values
-# plot(residuals(mod.dd.gam.base) ~ dd.dat$prop.abund)
-# # not great...
-# plot(residuals(mod.dd.gam.base) ~ fitted(mod.dd.gam.base))
-# # What's the fit look like?
-# pred.dd.gam.base <- data.frame(prop.abund = seq(0, 1, length.out = 1000))
-# tmp <- predict(mod.dd.gam.base, dd.gam.base.pred, type = 'response', se.fit = TRUE) 
-# 
-# pred.dd.gam.base$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.gam.base$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.gam.base$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# 
-# # So here's the game fit, I thnk it does do an ok job of showing that no much is happening below maybe 0.3, but then
-# # below 0.15 it starts increasing, suggesting general compensation, but we know the really high values matter here and are
-# # limited to a subset of the stocks, anywho we know the residuals suck, so moving on...
-# ggplot(dd.dat,aes(y=lam.no.fish,x=prop.abund)) + 
-#                   geom_point() + scale_y_log10() +
-#                   geom_ribbon(data=pred.dd.gam.base,aes(ymin=lower,ymax=upper,x=prop.abund),alpha=0.4) +
-#                   geom_line(data = pred.dd.gam.base,aes(y=lam.no.fish, x= prop.abund))
-#     
-# 
-# # What if we did a glm, Gamma with log-link seems a natural thing to try...
-# mod.dd.glm.gamma <- glm(lam.no.fish ~ prop.abund,data=dd.dat,family = Gamma(link='log'))
-# # What's that done...
-# summary(mod.dd.glm.gamma)
-# # Still some pretty gross shit going on here...
-# par(mfrow=c(2,2))
-# plot(mod.dd.glm.gamma)
-# par(mfrow=c(1,1))
-# # Now plot it...
-# pred.dd.glm.base <- data.frame(prop.abund = seq(0, 1, length.out = 1000))
-# tmp <- predict(mod.dd.glm.gamma, dd.gam.base.pred, type = 'response', se.fit = TRUE) 
-# 
-# pred.dd.glm.base$lam.no.fish   <- (tmp$fit)
-# pred.dd.glm.base$lower <- (tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.glm.base$upper <- (tmp$fit + 1.96 * tmp$se.fit)
-# # Pretty similar, though I think on the linear scale we see the 'rate' may be decreasing as we approach 0
-# # But still not a good model given the above
-# ggplot(dd.dat,aes(y=lam.no.fish,x=prop.abund)) + 
-#                   geom_point() + scale_y_log10() +
-#                   geom_ribbon(data=pred.dd.glm.base,aes(ymin=lower,ymax=upper,x=prop.abund),alpha=0.4) +
-#                   geom_line(data = pred.dd.glm.base,aes(y=lam.no.fish, x= prop.abund))
-#     
-# # Now what if we account for species in these and get an estimate for each species. 
-# # I think this should be done as a random effect, we'll start with linear mixed models and see what happens...
-# 
-# mod.dd.species.re <- lmer(log(lam.no.fish) ~ prop.abund + (1| Species),data=dd.dat)
-# # So that seems reasonable...
-# summary(mod.dd.species.re)
-# #Residuals are still pretty cranky
-# plot(mod.dd.species.re)
-# # Normality still a hot mess
-# qqnorm(residuals(mod.dd.species.re))
-# qqline(residuals(mod.dd.species.re))
-# # draw some lines...
-# pred.dd.lmm.species <- expand.grid(prop.abund = seq(0, 1, length.out = 100),Species=unique(dd.dat$Species))
-# tmp <- predict(mod.dd.species.re, pred.dd.lmm.species, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.species$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.lmm.species$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.species$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.species,aes(x=prop.abund,y=lam.no.fish,group=Species,color=Species)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Species, color=Species)) +
-#                                 scale_y_log10()
-# 
-# # We could also allow the slope to vary by species, might get a bit better, but really won't do the trick...
-# mod.dd.species.slope.re <- lmer(log(lam.no.fish) ~ prop.abund + (1+ prop.abund| Species),data=dd.dat)
-# summary(mod.dd.species.slope.re)
-# #Residuals are still pretty cranky
-# plot(mod.dd.species.slope.re)
-# # Normality still a hot mess
-# qqnorm(residuals(mod.dd.species.slope.re))
-# qqline(residuals(mod.dd.species.slope.re))
-# # draw some lines...
-# pred.dd.lmm.species.slope <- expand.grid(prop.abund = seq(0, 1, length.out = 100),Species=unique(dd.dat$Species))
-# tmp <- predict(mod.dd.species.slope.re, pred.dd.lmm.species.slope, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.species.slope$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.lmm.species.slope$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.species.slope$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.species.slope,aes(x=prop.abund,y=lam.no.fish,group=Species,color=Species)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Species, color=Species)) +
-#                                 scale_y_log10()
-# # Curious what species have high slopes.. Dubious and Esmarkii (North Sea sand lance and mackerel)
-# ranef(mod.dd.species.slope.re)
-# 
-# # So so what if we let the slopes vary by stock
-# mod.dd.stock.re <- lmer(log(lam.no.fish) ~ prop.abund +  (1+ prop.abund | Stock.short),data=dd.dat)
-# summary(mod.dd.stock.re)
-# #Residuals are slightly better I think but still really suck
-# plot(mod.dd.stock.re)
-# # Normality = no
-# qqnorm(residuals(mod.dd.stock.re))
-# qqline(residuals(mod.dd.stock.re))
-# # What's it look like?
-# pred.dd.lmm.stock <- expand.grid(prop.abund = seq(0, 1, length.out = 100),
-#                                          #Species=unique(dd.dat$Species),
-#                                          Stock.short=unique(dd.dat$Stock.short))
-# tmp <- predict(mod.dd.stock.re, pred.dd.lmm.stock, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.stock$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.lmm.stock$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.stock$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.stock,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Stock.short, color=Stock.short)) +
-#                                 scale_y_log10()
-# 
-# # Curious what stocks have high slopes.. Dubious and Esmarkii (North Sea sand lance and mackerel), NS Haddock and Irish Sea Haddock 
-# ranef(mod.dd.stock.re)
-# 
-# 
-# 
-# 
-# # OK, so this all still sucks, wonder if a glmer and gamma would get us anywhere... not really.... 
-# # Tried many variants on the glmer and they all land in the same lousy spot.
-# mod.dd.stock.gamma.re <- glmer(lam.no.fish ~ prop.abund +  (1+ prop.abund | Stock.short),data=dd.dat,family=Gamma(link='log'))
-# # OK...
-# summary(mod.dd.stock.gamma.re)
-# #Residuals, nah, still suck, just some crazy outliers...
-# plot(mod.dd.stock.gamma.re)
-# # Normality = no
-# qqnorm(residuals(mod.dd.stock.gamma.re))
-# qqline(residuals(mod.dd.stock.gamma.re))
-# # And the plot...
-# pred.dd.lmm.stock.gamma <- expand.grid(prop.abund = seq(0, 1, length.out = 100),
-#                                          #Species=unique(dd.dat$Species),
-#                                          Stock.short=unique(dd.dat$Stock.short))
-# tmp <- predict(mod.dd.stock.gamma.re, pred.dd.lmm.stock.gamma, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.stock.gamma$lam.no.fish   <- (tmp$fit)
-# pred.dd.lmm.stock.gamma$lower <- (tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.stock.gamma$upper <- (tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.stock.gamma,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Stock.short, color=Stock.short)) +
-#                                 scale_y_log10()
-# # None of the above really work at all....
+\newpage
+```{r r0-6-plt, echo=F, fig.cap="$R_0$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"))
+```
 
+\newpage
+```{r r0-other-plt, echo=F, fig.cap="$R_0$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"))
 ```
+
+\newpage
+```{r r0-nf-ts-plt, echo=F, fig.cap="$R_0$ estimates for every cohort for each species excluding the effects of fishing."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_nf_",what.2.tune,".png"))
+```
+
+\newpage
+```{r r0-fish-ts-plt, echo=F, fig.cap="$R_0$ estimates for every cohort for each species including the effects of fishing."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_fish_",what.2.tune,".png"))
+```
+
+\newpage
+```{r gl-6-plt, echo=F, fig.cap="Generation length estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"))
+```
+
+\newpage
+```{r gl-other-plt, echo=F, fig.cap="Generation length estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"))
+```
+
+\newpage
+```{r gl-nf-ts-plt, echo=F, fig.cap="Generation length estimates for every cohort for each species excluding the effects of fishing."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_nf_",what.2.tune,".png"))
+```
+
+\newpage
+```{r gl-fish-ts-plt, echo=F, fig.cap="Generation length estimates for every cohort for each species including the effects of fishing."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_fish_",what.2.tune,".png"))
+```
+
+<!-- Now for the Doubling time -->
+
+\newpage
+```{r dub-time-map, echo=F, fig.cap="Doubling time estimate for each stock with no fishing mortality."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"))
+```
+
+\newpage
+```{r dub-ts, echo=F, fig.cap="The number of stocks which doubled in size by a given year with no fishing mortality  The dashed line represents the 77 stocks in the analysis."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_time_series_",what.2.tune,".png"))
+```
+
+\newpage
+```{r dub-vs-sd, echo=F, fig.cap="The recovery potential (low, moderate, or high) of each stock after 20 years compared to the median $\\lambda_{F=0}$ and the standard deviation of $\\lambda_{F=0}$."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"))
+```
+
+# Supplemental Figures {-}

### 2024-05-21 Drafts/Paper_1/tmp-index.Rmd
mid-edit update

--- 2024-05-10 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
@@
 ---
-output: word_document
-editor_options: 
-  chunk_output_type: console
+title: |
+   "Life history variability influence on the recovery potential of globally exploited teleosts "
+french_title: "Titre ici (*Nom latin de l'espèce*)"
+author: |
+  David. M. Keith^1^ 
+  Freya M. Keyser^1^
+  Julie M. Charbonneau^2^
+  Heather 'The Boss' Bowlby^1^
+author_list: "Keith, D.M., Keyser, F.M., Charbonneau, J.M., Bowlby, H.T.B."
+address: |
+  ^1^Bedford Institute of Oceanography\
+     Fisheries and Oceans Canada, 1 Challenger Dr.\
+     Dartmouth, Nova Scotia, B2Y 4A2 , Canada\
+  \smallskip
+  ^2^Simon Fraser University\
+     Department of Biology\
+french_address: |
+
+month: ""
+french_month: ""
+year: 2024
+report_number: nnn
+region: "Maritimes Region"
+french_region: "Maritimes Region"
+isbn: ""
+cat_no: ""
+citation_other_language: ""
+
+abstract: |
+  Here is the abstract text.
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+  Start new paragraphs after a blank line and with 2 spaces indent.
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+french_abstract: |
+
+header: "Draft working paper --- Do not cite or circulate" # or "" to omit
+output:
+ csasdown::resdoc_word:
+   french: false
+   copy_sty: true
+   line_nums: true
+   line_nums_mod: 1
+   lot_lof: false
+   draft_watermark: false
+   include_section_nums: true
+   highlight: tango
+# ------------
+# End of options to set
+knit: (function(input, ...) {
+       csasdown::render('_bookdown.yml')
+      })
+link-citations: true
+bibliography: Y:/Zotero/MAR_SABHU.bib
+# Any extra LaTeX code for the header:
+# header-includes:
+# - \usepackage{tikz}
 ---
 
-```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4,include=F,message=F}
+```{r setup, echo=FALSE, cache=FALSE, message=FALSE, results='hide', warning=FALSE}
+library(knitr)
+if (is_latex_output()) {
+  knitr_figs_dir <- "knitr-figs-pdf/"
+  knitr_cache_dir <- "knitr-cache-pdf/"
+  fig_out_type <- "png"
+} else {
+  knitr_figs_dir <- "knitr-figs-docx/"
+  knitr_cache_dir <- "knitr-cache-docx/"
+  fig_out_type <- "png"
+}
+fig_asp <- 0.618
+fig_width <- 9
+fig_out_width <- "6in"
+fig_dpi <- 180
+fig_align <- "center"
+fig_pos <- "htb"
+opts_chunk$set(
+  collapse = TRUE,
+  warning = FALSE,
+  message = FALSE,
+  comment = "#>",
+  fig.path = knitr_figs_dir,
+  cache.path = knitr_cache_dir,
+  fig.asp = fig_asp,
+  fig.width = fig_width,
+  out.width = fig_out_width,
+  echo = FALSE,
+  #  autodep = TRUE,
+  #  cache = TRUE,
+  cache.comments = FALSE,
+  dev = fig_out_type,
+  dpi = fig_dpi,
+  fig.align = fig_align,
+  fig.pos = fig_pos
+)
+```
+
+```{r load-libraries-n-data, echo = FALSE, cache = FALSE, message = FALSE, results = 'hide', warning = FALSE}
+# add other packages here:
+library(dplyr)
+library(readr)
+library(tibble)
+library(csasdown)
+# OK, so using the ICES assessments here's what we get for North Sea cod.
+library(readxl)
+library(tidyverse)
+library(rio)
+library(ggthemes)
+library(cowplot)
+library(gtable)
+library(viridis)
+library(arm)
+library(mgcv)
+library(lme4)
+library(scales)
+library(ggh4x)
+library(gratia)
+theme_set(theme_few(base_size = 14))
+
+# The location of your data
+loc <- 'D:/GitHub/ICM'
+# The parameters for the doubling time simulation
+n.dt.sims <- 1000 # Increase to 1000 for final run, which takes like a full day or something 
+n.sim.years <- 100
+# If we already have the results don't re-run the models or load data we don't need.
+load.results <- F
+# What tunning model are you running or did you run!
+what.2.tune <- 'fec_nm'
+
+#source(paste0(loc,"/Scripts/functions/tuning_sim_fast.R"))
+
+# Download the functions we'll need from github
+funs <- c("https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/simple_Lotka_r.r",
+          "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/backwards_project.r",
+          "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/forward_project.r",
+          "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/tuning_sim_fast.r"
+)
+  # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
+for(fun in funs) 
+{
+  download.file(fun,destfile = basename(fun))
+  source(paste0(getwd(),"/",basename(fun)))
+  file.remove(paste0(getwd(),"/",basename(fun)))
+}
 
@@
 {
-  Stocks <- ASR.long |> 
-                      collapse::fsubset(!is.na(value)) |>
-                      collapse::fgroup_by(Stock, type) |>
-                      collapse::fsummarize(count=length(unique(value))) |>
-                      collapse::fgroup_by(Stock) |>
-                      collapse::fsummarize(types=length(unique(type))) |>
-                      collapse::fsubset(types==5) |>
-                      collapse::fselect(Stock)
+  # Choose 5 ICES stocks that we have the necessary data for
+  #ASR <- read_xlsx("../Data/ASR_2018.xlsx" sheet = "ICES")
+  ASR1 <- read.csv(paste0(loc,"/Data/ICM_data_NE_atlantic_stocks.csv"))
+  ASR <- read.csv(paste0(loc,"/Data/ICM_data_NW_atlantic_stocks.csv"))
 
-  ASR.tmp <- ASR.long 
-  ASR.tmp$age <- as.numeric(ASR.tmp$age)
-  ASR.stocks <- ASR.tmp |> 
-                          collapse::fsubset(Stock %in% Stocks$Stock) |>
-                          collapse::fsubset(!is.na(value)) |>
-                          collapse::roworder(Stock, Year, type, age)
+  ASR <- rbind(ASR1,ASR)
+  datatypes <- unique(gsub(x = names(ASR), pattern = "[^a-zA-Z]", replacement=""))
 
-  # print(Stocks)
-  Stocks <- Stocks$Stock
+  # Replace 0's in Num.tot with NA so the rest of this works as Freya designed it to...
+  ASR$Num.tot[ASR$Num.tot == 0] <- NA
+  # we want:
+  # Year, Num, WA, Catch, AM, NM, StockID, Management, Area, Order, Family, Genus, Species
+  ASRdat <- ASR[,c(grep(x=names(ASR), "Num"),
+                   grep(x=names(ASR), "WA"),
+                   grep(x=names(ASR), "Catch"),
+                   grep(x=names(ASR), "AM"),
+                   grep(x=names(ASR), "NM"))]
+  # Making all the data numeric that should be numeric
+  ASRdat <- apply(X = ASRdat, 2, as.numeric)
+  # Getting the species info back
+  ASRsp <- ASR[, which(!1:length(names(ASR)) %in% grep(x=names(ASR), ".", fixed=T))]
+  # And binding it all back together
+  ASR.trim <- cbind(ASRsp, ASRdat)
+  # need a unique ID for stock
+  #table(ASR.trim$Management, ASR.trim$Species)
+  ASR.trim$Stock <- paste0(ASR.trim$Management, "_", ASR.trim$Area, "_", ASR.trim$Genus, "_", ASR.trim$Species)
 
-  # Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
-  #Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
-  # Esmarki doesn't work great as it is assessed using a quarterly model.
-  #Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
-  #i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
-  years.tmp <- NULL
-  pnm.tmp <- NULL
-  waa.tmp <- NULL
-  ages.tmp <- NULL
-  rem.tmp <- NULL
-  mx.tmp <- NULL
-  NE.tmp <- NULL
-  vpa.tmp <- NULL
-  am.tmp <- NULL
-  #mr.tmp <- NULL
-  abund.tmp <- NULL
-  full.abund.tmp <- NULL
-  full.rem.tmp <- NULL
-  fs.tmp <- NULL
-  for(i in Stocks)
-  {
-  print(i)
-  ASR.sub <- ASR.long |>
-    collapse::fselect(Year, Stock, type, age, value) |>
-    collapse::fsubset(Stock==i)
+  ASR.long <- ASR.trim %>%
+    pivot_longer(!c("Management", "Area", "Order", "Family", "Genus", "Species", "Stock", "Year","Meeting_or_reference","Model","Case","Notes")) %>%
+    separate(col=name, into=c("type", "age"), sep = "\\.")
 
-    # Dropping the first 7 years as the 8 year olds are all missing
-  if(i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR.sub <- ASR.sub |> collapse::fsubset(Year >= 1972)
-  # maxage <- max(as.numeric(ASR.sub$age[!is.na(ASR.sub$value)]))
-  # maxYear <- max(ASR.sub$Year[!is.na(ASR.sub$value)])
-  # minYear <- min(ASR.sub$Year[!is.na(ASR.sub$value)])
-  # forplot <- ASR.sub[as.numeric(ASR.sub$age) < (maxage+1) & ASR.sub$Year %in% minYear:maxYear,]
+  # Something is weird with the mentella stock, I'm going to drop it...
+  ASR.long <- ASR.long %>% dplyr::filter(Stock != "ICES-AFWG_DEEP1-2_Sebastes_mentella")
+}# end if load results
+```
+
+```{r bilingual-code, cache=FALSE}
+options(
+  # Prevent xtable from adding a timestamp comment to the table code it produces
+  xtable.comment = FALSE,
+  # Do not allow kableExtra to load packages, we add them manually in csasdown
+  kableExtra.latex.load_packages = FALSE,
+  # Stop chunk output (echo) running into the margins
+  width = 80,
+  # Do not use scientific notation (stops tables from showing 1.2e3, etc.)
+  scipen = 999)
+
+meta <- rmarkdown::metadata
+meta_out <- rmarkdown::metadata$output
+csl <- "csl/csas.csl"
+options(OutDec = ".")
+if (is.null(getOption("french"))) {
+  stop("`french` was not set up correctly in YAML header in index.Rmd. ",
+       "It must be true or false",
+       call. = FALSE)
+}
+if (getOption("french")) {
+  csl <- "csl/csas-french.csl"
+  options(OutDec = ",")
+}
+
+french <- isTRUE(getOption("french")) # for backwards compatibility
+
+# This hook simplifies document translation for the author.
+# When building in French, it draws a box around paragraphs contained in chunks
+#  which have the option `needs_trans = TRUE`. It also labels
+#  the box with a "Needs translation" tag in red and the chunk label in blue.
+# You need to change the `needs_trans` option to `FALSE` for a chunk once you
+#  have inserted the translated text into it. You will get a utf-8 error if
+#  you leave it as `TRUE` and there is French in the chunk.
+#  This function assumes you are translating from English to French.
+#  If you wrote your document in French and want to translate to English,
+#  put a ! before `getOption("french")` below and add the `need_trans`
+#  chunk options to your English paragraph chunks instead of the French ones.
 #  
-  # # summary plots
-  # print(ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
-  #         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
-  #         theme_bw() + 
-  #         ggtitle(i)
-  # )
-
-  age.mat <- ASR.sub |> collapse::fsubset(type=="AM") |> dplyr::rename(AM=value) |> collapse::fselect(-type)
-  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
-  # in case that changes later...
-  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
-  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
-  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
-  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
-  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
-  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0
-
-  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
-  nat.mort <-  ASR.sub |> collapse::fsubset(type=="NM") |> dplyr::rename(NM=value) |> collapse::fselect(-type)
-  abund <- ASR.sub |> collapse::fsubset(type=="Num") |> dplyr::rename(Num=value) |> collapse::fselect(-type)
-  weight.age <- ASR.sub |> collapse::fsubset(type=="WA") |> dplyr::rename(WA=value) |> collapse::fselect(-type)
-  if(i == Stocks[30]) weight.age$WA <- weight.age$WA/1000
-  removals <- ASR.sub |> collapse::fsubset(type=="Catch") |> dplyr::rename(Catch=value) |> collapse::fselect(-type)
-
-  data <- age.mat |>
-    full_join(nat.mort) |>
-    full_join(abund) |>
-    full_join(weight.age) |>
-    full_join(removals)
-
-  # Aahh??  Is this NA dropping useful data, needed to quick fix the age at maturity data...
-  data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
-  data <- data[data$available==T,]
-
-  # Tidy up the data for input...
-  data$prop.nat.mort <- 1-exp(-data$NM)
-  #prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))] <- 1-exp(-prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))])
-
-  rem <- data |> collapse::fgroup_by(Year) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
-  #rem <- data |> dplyr::group_by(Year,.drop=F) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
-
-  # Never run, so not doing anything.
-  # missing_rem<- NULL
-  # if(any(is.na(rem$rem))) 
-  # {
-  #   missing_rem <- unique(data$Year)[which(is.na(rem$rem))]
-  #   rem$rem[is.na(rem$rem)] <- median(rem$rem, na.rm=T)
-  # }
-
-  #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
-  years <- data |> dplyr::pull(Year) |> unique() |> sort()
-
-  N.end <- sum(data[data$Year==max(years),]$Num)
-  vpa.abund <- data |> dplyr::group_by(Year) |> dplyr::summarize(vpa=sum(Num,na.rm=T)) |> pull(vpa)
-
-  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
-  #minage
-  minage <- min(as.numeric(data$age))
-  #maxage
-  maxage <- max(as.numeric(data$age))
-  #recruits
-  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
-  #ssn
-  data$ssn <- data$Num * data$AM
-  #ssb
-  data$ssb <- data$ssn * data$WA #I need to figure out how to line this up with the number of recruits for the right years in the data object.... got it right for the overall r.p.ssb below.
-  #tot.ssb
-  annual <- data |> group_by(Year) |> summarize(tot.ssb = sum(ssb)) |> left_join(annual)
-
-  #tst <- data |> group_by(Year) |> summarize(tot.ssn = sum(ssn)) |> left_join(annual)
-
-  #r.p.ssb This needs to be offset by the age of recruits. So here's my lining this up logic.  For age 0, we get
-  # the recruit and SSB estimates from the same survey, thus these age 0 recruits will have been produced by the SSB in the previous year...
-  # So the R in 1970 were produced by SSB in 1969 when min age =0
-  # If min.age = 1 then R in 1970 is produced by SSB in 1968... and so on.
-  # FIX 1 "Recruit year" = SSB year + min.age + 1 (or min.age +2 as SSB.year is the first column)
-  # Now for RPS there's another wrinkle because of this, because our model is N(1970) = lambda * N(1969) and lambda is made up of lx and mx
-  # so if the recruits show up in 1970, the fecundity term that gets us there (irrespective of the age offset) has to be for 1969, becuase
-  # that gets us to the babies that show up in 1970
-  # FIX 2 So "RPS year, recs.per.age year, and mx year" = SSB year + min.age
-  # I believe this to be correct, but we all need to discuss this to make sure the logic holds.
-  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+2):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage-1)],NA)
-  # recs.per.age
-  data <- left_join(data, annual)
-  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
-  tmp <- NULL
-  for(j in 1:length(years))
-  {
-    tst <- data|> collapse::fsubset(Year == years[j]) |> collapse::fselect(ssb,ssn,Year,age)
-    tst$Year <- tst$Year + minage # We want this to line up the the RPS year, so just adding minage here.
-    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
-    tmp[[j]] <- tst
-  }
-  # Unpack the list
-  ssb.off <- do.call('rbind',tmp)
-  # And merge it with the data object
-  data <- left_join(data,ssb.off,by=c("Year","age"))
-  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
-  # mx
-  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
-  # No longer dividing by 2 because we should really divide recruits and ssn by 2 to be female only, but that's pointless so we roll along with this.
-  data$mx <- data$recs.per.age/data$ssn.offset # if(grepl("males",i)) 
-  #if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
-  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
-  # Easier to remove the years where we don't have recs.per.age...
-  #data <- data |> collapse::fsubset(Year %in% years[(minage+1):length(years)])
-
-  age.mat <- data |> collapse::fselect("Year", "age", "AM") |> 
-                     pivot_wider(names_from=age, values_from = AM) |> collapse::fselect(-Year)
-  prop.nat.mort <- data |> collapse::fselect("Year", "age", "prop.nat.mort") |> 
-                            pivot_wider(names_from=age, values_from = prop.nat.mort) |> 
-                            collapse::fselect(-Year) |> as.data.frame()
-
-  weight.age <- data |> collapse::fselect("Year", "age", "WA") |> pivot_wider(names_from=age, values_from = WA) |> collapse::fselect(-Year)
-  mx <- data |> collapse::fselect("Year", "age", "mx") |> 
-                 pivot_wider(names_from=age, values_from = mx) |> 
-                 collapse::fselect(-Year) |> as.data.frame()
-  # Get the abundance matrix
-  abund.age <- data |> collapse::fselect("Year", "age", "Num") |> 
-                        pivot_wider(names_from=age, values_from = Num) |> 
-                        collapse::fselect(-Year) |> as.data.frame()
-
-  # Now we can save out the catch and get an instantaneous F
-    data$Catch[is.na(data$Catch)] <- 0
-    data$Exp <- data$Catch/data$Num 
-    # If it is exactly 1 that leads to an Inf, which is annoying, so make it 1.1 and fix it with the rest below
-    data$Exp[data$Exp == 1] <- 1.1
-    # And make this an F
-    data$Fs <- -log(1-data$Exp)
-    if(any(is.na(data$Fs)))
-    {
-      fixers <- which(is.na(data$Fs))
-      print(paste0("Had to replace ",length(fixers), ' exploitation rates for stock ',i))
-      for(f in fixers)
-      {
-        yr <- data$Year[f]
-        fs <- max(data$Fs[data$Year == yr],na.rm=T)
-        data$Fs[f] <- fs
-        data$Exp[f] <- 1-exp(-fs)
+#  IMPORTANT NOTES
+#  - Use `csasdown::render()` to render the document. This runs a
+#    pre-processing step which ensures any inline R chunks
+#    `r print("Like this one")` are taken care of correctly and that all
+#    backslash variables (eg. \pi, \alpha, \@ref, \cite) are all processed
+#    correctly.
+#  - French latex places a space before the colon by default so if you need a colon
+#    with no space before it, use \\hc .
+knit_hooks$set(needs_trans = function(before, options){
+  if(getOption("french") && options$needs_trans){
+    if (before){
+      paste0("\\
+   \\begin{lrbox}{\\userinput}
+   \\begin{minipage}{\\dimexpr\\linewidth-2\\fboxsep-2\\fboxrule}
+   \\textcolor{red}{\\textbf{Needs translation - \\textcolor{blue}{knitr chunk: ", options$label, "}}}
+   \\begin{lstlisting}
+  ")
+    } else {
+      "
+   \\end{lstlisting}
+   \\end{minipage}
+   \\end{lrbox}
+   \\noindent
+   \\fbox{\\usebox{\\userinput}}
+  "
     }
   }
-
-  full.rems <- data |> collapse::fselect("Year", "age", "Catch") |> pivot_wider(names_from=age, values_from = Catch) |> collapse::fselect(-Year)
-  full.Fs <-  data |> collapse::fselect("Year", "age", "Fs") |> pivot_wider(names_from=age, values_from = Fs) |> collapse::fselect(-Year)
-
-    if(i == "DFO_2J3KL_Gadus_morhua")
-    {
-      age.mat[,8:10] <- 1
-      prop.nat.mort[,8:10] <- prop.nat.mort[,7]
-      weight.age[12:14,9:10] <- weight.age[12:14,8]
-      weight.age[15,10] <- weight.age[15,9]
-      mx[12:16,9:10] <- mx[12:16,8]
-      mx[17,10] <- mx[17,9]
-      full.Fs[12:14,9:10] <- full.Fs[12:14,8]
-      full.Fs[15,10] <- full.Fs[15,9]
-      abund.age[12:14,9:10] <- abund.age[12:14,8]
-      abund.age[15,10] <- abund.age[15,9]
-      # I could calculate, but this will get us to the same place...
-      full.rems[12:14,9:10] <- full.rems[12:14,8]
-      full.rems[15,10] <- full.rems[15,9]
-    }
-
-    if(i == "DFO_4T-Spring_Clupea_harengus")
-    {
-      age.mat[6:7,10] <- 1
-      prop.nat.mort[6:7,10] <- prop.nat.mort[6:7,9]
-      weight.age[6:7,10] <- weight.age[6:7,9]
-      mx[6:9,10] <- mx[6:9,9]
-      full.Fs[6:7,10] <- full.Fs[6:7,9]
-      abund.age[6:7,10] <- abund.age[6:7,9]
-      full.rems[6:7,10] <- full.rems[6:7,9]
-    }
-
-    if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
-    {
-      age.mat[30,8] <- 1
-      prop.nat.mort[30,8] <- prop.nat.mort[30,7]
-      weight.age[30,8] <- weight.age[29,8]
-      mx[30:31,8] <- mx[30:31,9]
-      full.Fs[30,8] <- full.Fs[30,7]
-      abund.age[30,8] <- abund.age[30,7]
-      full.rems[30,8] <- full.rems[30,7]
-    }
-
-    if(i == "ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax")
-    {
-      age.mat[c(14,27,40),5] <- age.mat[1,5]
-      prop.nat.mort[c(14,27,40),5] <- prop.nat.mort[1,5]
-      weight.age[c(14,27,40),5] <- weight.age[c(13,26,39),5]
-      mx[c(14,16,27,29,40,42),5] <- mx[c(14,16,27,29,40,42),6]
-      full.Fs[c(14,27,40),5] <- full.Fs[c(14,27,40),4]
-      abund.age[c(14,27,40),5] <- abund.age[c(14,27,40),4]
-      full.rems[c(14,27,40),5] <- full.rems[c(14,27,40),4]
-    }
-    # Clear out some 0's...
-    if( i == "AFSC_EEBSAI_Limanda_aspera")
-    {
-      mx[5,18] <- mean(unlist(mx[5,c(17,19)]))
-      mx[c(6,8),19] <- mx[c(6,8),18]
-      mx[2:7,20] <- mx[2:7,19] 
-    }
-
-  # I had filled the years with no SSB data to inform them.  instead I'm going to remove those years...
-
-   if(minage >0) 
-  {
-    rm <- -(1:minage)
-    years <- years[rm]
-    prop.nat.mort <- prop.nat.mort[rm,]
-    weight.age <- weight.age[rm,]
-    rem <- rem[rm,]
-    mx <- mx[rm,]
-    vpa.abund <- vpa.abund[rm]
-    age.mat <- age.mat[rm,]
-    abund.age <- abund.age[rm,]
-    full.Fs <- full.Fs[rm,]
-    full.rems <- full.rems[rm,]
-   }
-  #   mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
-  #   names(mx) <- names(mx.fill)
-  #  # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
-  #   mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
-  # }
-
-    years.tmp[[i]] <- years
-    pnm.tmp[[i]] <- prop.nat.mort
-    waa.tmp[[i]] <- weight.age
-    ages.tmp[[i]] <- minage:maxage
-    rem.tmp[[i]] <- rem
-    mx.tmp[[i]] <- mx
-    NE.tmp[[i]] <- N.end
-    vpa.tmp[[i]] <- vpa.abund
-    am.tmp[[i]] <- age.mat
-    #mr.tmp[[i]] <- missing_rem
-    abund.tmp[[i]] <- abund.age
-    fs.tmp[[i]] <- full.Fs
-    full.rem.tmp[[i]] <- full.rems
-  } #end input data loop
-
-  save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,
-       am.tmp,Stocks,ASR.stocks,ASR.long,abund.tmp,fs.tmp,full.rem.tmp,
-       file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
-
-  } # end load results
+})
 ```
 
-  So now I can try to do some tuning, both forwards and backwards, lets see what we get from that...
-
-```{r tunes,include=F,echo=F,warning=F,message=F}
-
-  ########################## Now run the tuning sims
-  #
-
-  if(load.results==F)
-  {
-  load(file = paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
-
-  for.tune.all.res <- NULL
-  for.tune.summary <- NULL
-  for(i in Stocks)
-  {
-    years <- years.tmp[[i]]
-    prop.nat.mort <- pnm.tmp[[i]] 
-    #rem <- rem.tmp[[i]] 
-    mx <- mx.tmp[[i]] 
-    N.end <- NE.tmp[[i]] 
-    ages <- ages.tmp[[i]]
-    vpa.abund <- vpa.tmp[[i]] 
-    abund <- abund.tmp[[i]]
-    fs <-fs.tmp[[i]]
-    full.rem <- full.rem.tmp[[i]]
-    #full.abund <- full.abund.tmp[[i]]
-    #all.abund <- full.abund.tmp[[i]]
-    #N.end <- vpa.abund[length(vpa.abund)]
-    #Pick your step size
-    ss.size <- 0.005
-    sensistive.stocks <- c("AFSC_GOA_Theragra_chalcogramma",
-                            "DFO_2J3KL_Gadus_morhua",
-                            "DFO_3Pn-4RS_Gadus_morhua",
-                            "DFO_4T-4VN_Gadus_morhua",
-                            "DFO_4T_Scomber_scombrus",
-                            "ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus",
-                            "ICES-AFWG_NEA1-2_Gadus_morhua",
-                            "ICES-HAWG_NS_Ammodytes_dubius",
-                            "ICES-NWWG_FA5b_Pollachius_virens",
-                            "ICES-NWWG_FAPL5b1_Gadus_morhua",
-                            "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
-                            "ICES-WGCSE_IS7a_Gadus_morhua",
-                            "ICES-WGCSE_CS7a_Merlangius_merlangus",
-                            "ICES-WGCSE_CS7e-k_Gadus_morhua",
-                            "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
-                            "ICES-WGHANSA_SP8abd_Sardina _pilchardus", 
-                            "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua",
-                            "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",
-                            "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus",
-                            "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
-                            "NEFSC-GARMIII_SNE- MA_Limanda_ferruginea",
-                            "NEFSC-GARMIII_MA_Paralichthys_dentatus",
-                            "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus",
-                            "NEFSC_NWA_Scomber _scombrus")
-
-    if(i %in% sensistive.stocks) ss.size = ss.size/10
-
-     N.start <- vpa.abund[1]
-     print(i)
-     # The fecundities are 
-     fast.for.tune <- fast.tunes(years,
-                             tuner=what.2.tune,
-                             step.size = ss.size, 
-                             abund.ts = vpa.abund,
-                             ages=ages,
-                             nm = -(log(1-prop.nat.mort)),
-                             fecund = mx,
-                             fm = fs,
-                             abund.age = abund, 
-                             catch.age = full.rem, 
-                             N.init = N.start,
-                             direction= 'forwards'
-                             )
-
-     for.tune.all.res[[i]] <- fast.for.tune
-     for.tune.tmp <- data.frame(fast.for.tune$res,Stock = i)
-     for.tune.summary[[i]] <- for.tune.tmp
-  }
-
-  saveRDS(for.tune.summary,paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-  saveRDS(for.tune.all.res,paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
-  # 
-}# end if load results
-
-```
-
-```{r paper-other-metrics-and-metadata,echo=F,include=F,warning=F,message=F}
-
-if(load.results==F)
-{
-  # We are now looking at everything, lifetime reproductive success
-
-  for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-  for.tune.all <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
-
-  load(file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
-  # Get the stocks...
-  Stocks <- names(for.tune.summary)
-  n.stocks <- length(Stocks)
-
-  ############ Meta data and clean up, could be it's own chunk really, but it's really fast, so meh...
-
-  #  A quick way to get the other potentially interesting info for the stock...
-  drop <- which(names(ASR.long) %in% c("Year","type","age","value"))
-  meta <- NULL
-  for(i in Stocks) 
-  {
-    meta[[i]] <- ASR.long[ASR.long$Stock == i,-drop][1,]
-    meta[[i]]$age.min <- min(ages.tmp[[i]])
-    meta[[i]]$age.max <- max(ages.tmp[[i]])
-  }
-  meta <- do.call('rbind',meta)
-
-  # First making a meta data object and adding a bunch of columns to it... very messy!!
-  meta$Species[meta$Species == ' harengus']  <- "harengus"
-  meta$Species[meta$Species == "Aeglefinus"] <- "aeglefinus"
-  meta$Species[meta$Species == "Solea"] <- "solea"
-  meta$Family[meta$Family == "Gadide"] <- "Gadidae"
-  meta$Genus[meta$Genus == " Hippoglossoides"] <- "Hippoglossoides"
-  meta$G.short <- toupper(paste0(substr(meta$Genus,1,1),"."))
-  meta$G.Species <- paste0(meta$G.short," ",meta$Species)
-  # Simplified Management
-  meta$Manage.short <- meta$Management
-  meta$Manage.short[grep("TRAC",meta$Management)] <- "DFO-TRAC"
-  meta$Manage.short[grep("DFO",meta$Management)] <- "DFO-TRAC"
-  meta$Manage.short[grep("NEFSC",meta$Management)] <- "NEFSC"
-  meta$Manage.short[grep("ICES",meta$Management)] <- "ICES"
-
-  # The 3 pieces of the ocean
-  meta$LME <- "NW Atlantic"
-  meta$LME[meta$Management == "AFSC"] <- "Pacific (Alaska)"
-  meta$LME[grepl("ICES",meta$Management)] <- "NE Atlantic"
-  # An area typo
-  meta$Area[grep("BSAI-females",meta$Area)] <- "BSAI-Females"
-  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI-Females"
-  # Some other Area summaries
-  meta$Area.broad <- meta$Area
-  meta$Area.long <- meta$Area
-  meta$Area.narrow <- "" # Leave this blank if not needed
-
-  meta$Area.broad[grep("NS",meta$Area)] <- "NS"
-  meta$Area.long[grep("NS",meta$Area)] <- "North Sea"
-  meta$Area.broad[grep("CS",meta$Area)] <- "CS"
-  meta$Area.long[grep("CS",meta$Area)] <- "Celtic Sea"
-  meta$Area.broad[grep("ROCK6b",meta$Area)] <- "CS"
-  meta$Area.long[grep("ROCK6b",meta$Area)] <- "Celtic Sea"
-  meta$Area.broad[grep("IS",meta$Area)] <- "IS"
-  meta$Area.long[grep("IS",meta$Area)] <- "Irish Sea"
-  meta$Area.broad[grep("BS",meta$Area)] <- "BS"
-  meta$Area.long[grep("BS",meta$Area)] <- "Baltic Sea"
-  meta$Area.broad[grep("NEA",meta$Area)] <- "NEA"
-  meta$Area.long[grep("NEA",meta$Area)] <- "NE Arctic"
-  meta$Area.broad[grep("B28.1",meta$Area)] <- "BS"
-  meta$Area.long[grep("B28.1",meta$Area)] <- "Baltic Sea"
-  meta$Area.broad[grep("SP8abd",meta$Area)] <- "BoB"
-  meta$Area.long[grep("SP8abd",meta$Area)] <- "Bay of Biscay"
-  meta$Area.broad[grep("FA",meta$Area)] <- "Ice-Faroe"
-  meta$Area.broad[grep("ICE",meta$Area)] <- "Ice-Faroe"
-  meta$Area.long[grep("FA",meta$Area)] <- "Faroes"
-  meta$Area.long[grep("ICE",meta$Area)] <- "Iceland"
-
-  meta$Area.broad[grep("GOM",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("GOM",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("GB",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("GB",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("5Y",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("5Y",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("5Z",meta$Area)] <- "NAFO 5-6"
-  meta$Area.long[grep("5Z",meta$Area)] <- "NAFO 5-6"
-  meta$Area.broad[grep("USATL",meta$Area)] <- "NAFO 5-6" # The fishery is broader than just GOM, but it does also include it.
-  meta$Area.long[grep("USATL",meta$Area)] <- "NAFO 5-6" # The fishery is broader than just GOM, but it does also include it.
-  meta$Area.broad[grep("NWA",meta$Area)] <- "NAFO 5-6" # Mackerel... so that definition is a bit narrow....
-  meta$Area.long[grep("NWA",meta$Area)] <- "NAFO 5-6" # Mackerel... so that definition is a bit narrow....
-  #meta$Area1[grep("SNE- MA",meta$Area)] <- "GOM-GB" # YT in US, so no GB so that definition is a bit narrow....
-  meta$Area.broad[grep("MA",meta$Area)] <- "NAFO 5-6" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
-  meta$Area.long[grep("MA",meta$Area)] <- "NAFO 5-6" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
-  meta$Area.broad[grep("BSAI",meta$Area)] <- "BSAI"
-  meta$Area.broad[grep("4T",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("4T",meta$Area)] <- "NAFO 2-4"
-  meta$Area.broad[grep("2J3",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("2J3",meta$Area)] <- "NAFO 2-4"
-  meta$Area.broad[grep("3Pn-4RS",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("3Pn-4RS",meta$Area)] <- "NAFO 2-4"
-  meta$Area.long[grep("GOA",meta$Area)] <- "Gulf of Alaska"
-  # Lumping everything in Berring Sea and AI into both.
-  meta$Area.long[grep("AI",meta$Area)] <- "Aleutian Islands"
-  meta$Area.long[grep("ESB",meta$Area)] <- "Bering Sea & AI" 
-  meta$Area.long[grep("BSAI",meta$Area)] <- "Bering Sea & AI"
-  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI"
-  meta$Area[grep("BSAI-Females",meta$Area)] <- "BSAI"
-  meta$Area[grep("BSAI-females",meta$Area)] <- "BSAI"
-  meta$Area.long[grep("BSAI-Females",meta$Area)] <- "Bering Sea & AI"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Pollachius_virens"] <- "5b"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5a_Pollachius_virens"] <- "5a"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS4 _Solea_solea"] <- "4"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d._Solea_solea"] <- "7d"
-  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_NS IIIa 22-24_Solea_Solea"] <- "22-24"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d_Pleuronectes_platessa"] <- "7d"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4,20_Pleuronectes_platessa"] <- "4 20"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS7e_Pleuronectes_platessa"] <- "7e"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS27.7a_Pleuronectes_platessa"] <- "7a"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Melanogrammus_aeglefinus"] <- "5b"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Melanogrammus_aeglefinus"] <- "5a"
-  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_B28.1_Clupea_harengus"] <- "28"
-  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_BS 25-29-32_Clupea_harengus" ] <- "25-32"
-  meta$Area.narrow[meta$Stock == "ICES-HAWG_WBS 22-24_Clupea_harengus"] <- "22-24"
-  meta$Area.narrow[meta$Stock == "DFO_4T-Fall_Clupea_harengus"] <- "Fa-SGSL"
-  meta$Area.narrow[meta$Stock == "DFO_4T-Spring_Clupea_harengus"] <- "Sp-SGSL"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS27.6a_Merlangius_merlangus"] <- "27.6a"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS7a_Merlangius_merlangus"] <- "7a"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Gadus_morhua"] <- "5a"
-  meta$Area.narrow[meta$Stock == "ICES-NWWG_FAPL5b1_Gadus_morhua" ] <- "5b"
-  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua"] <- "4-7 20"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_NS6a_Gadus_morhua"] <- "6a"
-  meta$Area.narrow[meta$Stock == "DFO_2J3KL_Gadus_morhua"] <- "NFLD"
-  meta$Area.narrow[meta$Stock == "DFO_3Pn-4RS_Gadus_morhua"] <- "NGSL"
-  meta$Area.narrow[meta$Stock == "NEFSC-CERT-TRAC_GB _Gadus_morhua"] <- "EGB"
-  meta$Area.narrow[meta$Stock == "ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus"] <- "RA"
-  meta$Area.narrow[meta$Stock == "DFO_4T-4VN_Gadus_morhua"] <- "SGSL"
-  meta$Area.narrow[meta$Stock == "DFO_4T_Hippoglossoides _platessoides"] <- "SGSL"
-  meta$Area.narrow[meta$Stock == "DFO_4T_Scomber_scombrus"] <- "SGSL"
-  meta$Area.narrow[meta$Stock == "NEFSC-SAW_GOM_Gadus_morhua"] <- "GOM"
-  meta$Area.narrow[meta$Stock == "NEFSC-GARMIII_GB_Gadus_morhua"] <- "GB"
-  meta$Area.narrow[meta$Stock == "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus"] <- "GOM"
-  meta$Area.narrow[meta$Stock == "CERT-TRAC_GB_Melanogrammus_Aeglefinus"] <- "GB"
-
-  meta$Stock.short <- paste0(meta$Area.broad," ",meta$Area.narrow," ",meta$G.short," ",meta$Species)
-  meta$Stock.no.species <- paste0(meta$Area.long," ",meta$Area.narrow)
-
-  for.tune.stocks <- NULL
-  fta <- NULL
-
-  # Going to rename these female stocks.
-  fem.names <- c("AFSC_BASI-Females_Pleuronectes_quadrituberculatus",
-                    "AFSC_EEBSAI-Females_Lepidopsetta_polyxystra",
-                    "AFSC_BSAI-females_Atheresthes_stomais")
-  fem.rename <- c("AFSC_BSAI_Pleuronectes_quadrituberculatus",
-                    "AFSC_EEBSAI_Lepidopsetta_polyxystra",
-                    "AFSC_BSAI_Atheresthes_stomais")
-  # Going to drop these stocks
-  dont <- paste(c("Mles","Males","COASTNOR"),collapse = "|")
-
-  meta.sub <- NULL
-  for(i in Stocks) 
-  {
-    org.nam <- i
-    tmp <- for.tune.summary[[org.nam]]
-    new.stock.nam <- org.nam
-    # Don't bother for these stocks...
-    if(!grepl(dont,tmp$Stock[1]))
-    {
-      # Grab the metadata and add in some new useful things...
-      meta.sub[[i]] <- meta[meta$Stock == org.nam,]
-
-      # Rename the ladies
-      if(tmp$Stock[1] == fem.names[1]) new.stock.nam <- tmp$Stock <- fem.rename[1]
-      if(tmp$Stock[1] == fem.names[2]) new.stock.nam <- tmp$Stock <- fem.rename[2]
-      if(tmp$Stock[1] == fem.names[3]) new.stock.nam <- tmp$Stock <- fem.rename[3]
-
-      meta.sub[[i]]$Stock <- new.stock.nam
-      tmp <- data.frame(tmp,meta.sub[[i]])
-      # For tunes all
-      fta[[new.stock.nam]] <- for.tune.all[[org.nam]]
-      fta[[new.stock.nam]]$meta <- meta.sub[[i]]
-      for.tune.stocks[[new.stock.nam]] <- tmp
-    }# End skip stocks...
-  }
-  # Now unpack them...
-  for.tunes <- do.call("rbind",for.tune.stocks)
-  for.tune.all <- fta
-  meta.sub <- do.call("rbind",meta.sub)
-
-  ######################### End Meta data and clean up #####################
-
-  # Now some summaries...
-
-  # Reset on the stocks...
-  Stocks <- sort(names(for.tune.all))
-  n.stocks <- length(Stocks)
-
-  # Doubling time, no fishing
-  dt.res <- NULL
-  # These are both set in the index file now, go there!!
-  n.dt.sims <- n.dt.sims
-  n.sim.years <- n.sim.years
-  for(i in Stocks)
-  {
-    str.time <- Sys.time()
-    try <- for.tune.all[[i]]
-    meta.tmp <- try$meta
-    age.4.sim <- meta.tmp$age.min:meta.tmp$age.max
-    double.time <- NA
-    pop <- 1000
-    tmp.res <- NULL
-  for(s in 1:n.dt.sims)
-  {
-    tmp <- rep(0,n.sim.yearss)
-    print(paste0("Sim # ", s))
-
-    for(y in 2:n.sim.yearss)
-    {
-
-      # Get our sample for this run
-      f.pick <- sample(nrow(try$fecund.opt),size=1)
-      nm.pick <- sample(nrow(try$nm.opt),size=1)
-      fec.samp <- try$fecund.opt[f.pick,]
-      # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
-      nm.samp <- try$nm.opt[nm.pick,] 
-      # now put these into Euler-lotka to get an r estimate
-      res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
-      r.val <- res$res$r
-      # If r is > 5 (lambda = exp(5)) it generally means the simple.lotka didn't converge (bad combo of fec and nm)
-      # So we'll need to resample them until it is < 5
-      while(r.val >= 5)
-      {
-        print("Resampling due to bat shit r value")
-        f.pick <- sample(nrow(try$fecund.opt),size=1)
-        nm.pick <- sample(nrow(try$nm.opt),size=1)
-        fec.samp <- try$fecund.opt[f.pick,]
-        # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
-        nm.samp <- try$nm.opt[nm.pick,] 
-        # now put these into Euler-lotka to get an r estimate
-        res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
-        r.val <- res$res$r
-      } # end while loop
-      pop[y] <- exp(r.val)*pop[y-1]
-      if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.sim.yearss] <- 1
-    } # end the years loop
-    tmp.res[[s]] <- data.frame(year =1:n.sim.yearss,doubled = tmp,sim=s)
-
-    } # end sim loop
-    res.tmp <- do.call("rbind",tmp.res)
-
-  dt.res[[i]] <- data.frame(res.tmp,meta.tmp)
-  count <- 0
-  timer <- round(difftime(Sys.time(),str.time,units='mins'),digits=1)
-  print(paste0("Stock ",i," time =", timer," minutes: Stock # ",count+1))
-  } # end Stocks loop
-
-  dub.time <- do.call("rbind",dt.res)
-
-  dub.time.summary <- dub.time |> collapse::fgroup_by(Stock,year)  |> collapse::fsummarise(prop = sum(doubled)/n.dt.sims)
-  dub.time.summary <- left_join(dub.time.summary,meta.sub,by="Stock")
-
-  # Now to get generation lengths + reproductive rates....
-  # First I need to get the fecundity and natural mortalities by cohort instead of year.
-  res.fin <- NULL
-  res.year.fin <- NULL
-  res.lambda.fin <- NULL
-  for(i in Stocks) # 
-  {
-    tst <- for.tune.all[[i]]
-    meta.tmp <- tst$meta
-    # Fishing mortality
-    fm.org.tmp <- tst$fm.org
-    fm.tmp <- tst$fm.opt
-    # fecundity
-    fec.tmp <- tst$fecund.opt
-    fec.org.tmp <- tst$fecund.org
-    # Natural mortality
-    m.org.tmp <- exp(-tst$nm.org) # This is survivorship
-    m.tmp <- exp(-tst$nm.opt) # This is survivorship
-    # Total mortality
-    z.tmp <- exp(-tst$z.opt) # This is survivorship
-    z.org.tmp <- exp(-tst$nm.org -fm.org.tmp) # This is survivorship
-
-    ages <- meta.tmp$age.min:meta.tmp$age.max
-    n.ages <- length(ages)
-    years <- tst$res$year
-    n.years <- length(years)
-    # Now I need to grab the fecundities and nat morts by cohort
-    if(n.years > n.ages)
-    {
-    res.cohort <- NULL
-    res.year <- NULL
-    res.lambda <- NULL
-    for(y in 1:(n.years-n.ages+1))
-    {
-      count = 0
-      fs <- NA
-      # The lx is no fishing survivorship, zx I'm calling the survivorship including fishing
-      lx <- lx.org <- lx.year <- zx <- zx.org <- zx.year <- 1
-      fs.org <- NA
-
-      for(a in 1:n.ages)
-      {
-      fs[a] <- fec.tmp[y+count,a]  
-      fs.org[a] <- fec.org.tmp[y+count,a]  
-      if(a > 1) 
-      {
-        # No fishing
-        lx[a] <- lx[a-1] * m.tmp[y+count,a]  
-        lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
-        lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
-        # Including fishing
-        zx[a] <- zx[a-1] * z.tmp[y+count,a]  
-        zx.org[a] <- zx.org[a-1]* z.org.tmp[y+count,a]  
-        zx.year[a] <- zx.year[a-1] * z.tmp[y,a]
-      }  # end the a > 1 if
-          count <- count + 1
-      }# end the ages loop
-          res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,
-                                 mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
-                                 x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
-                                 zx.opt = zx,
-                                 mx.zx.opt = fs*zx,mx.zx.org = fs.org*zx.org,
-                                 x.mx.zx.opt = fs*zx*ages,x.mx.zx.org = fs.org*zx.org*ages,
-                                 cohort=years[y],age = ages,meta.tmp)
-
-          res.year[[y]] <- data.frame(mx.opt = unlist(fec.tmp[y,]),lx.opt = lx.year,
-                                 mx.lx.opt = unlist(fec.tmp[y,])*lx.year,
-                                 x.mx.lx.opt = unlist(fec.tmp[y,])*lx.year*ages,
-                                 zx.opt = zx.year,
-                                 mx.zx.opt = unlist(fec.tmp[y,])*lx.year,
-                                 x.mx.zx.opt = unlist(fec.tmp[y,])*lx.year*ages,
-                                 age = ages,year=years[y],meta.tmp)
-
-    } # end the years loop
-
-  # Do a years loop to get lambda with no fishing for each year, rather than by cohort...
-    for(yy in 1:(n.years-1))
-    {
-      nm <- as.numeric(tst$nm.opt[yy,])
-      z <- as.numeric(tst$z.opt[yy,])
-      fec <- as.numeric(tst$fecund.opt[yy,])
-      nm.init <- as.numeric(tst$nm.org[yy,])
-      fec.init <- as.numeric(tst$fecund.org[yy,])
-      z.init <- as.numeric(tst$z.org[yy,])
-      lam.no.fish <- exp(simple.lotka.r(mort = nm,fecund = fec,ages=ages)$res$r)
-      lam.fish <- exp(simple.lotka.r(mort = z,fecund = fec,ages=ages)$res$r)
-      lam.org.no.fish <- exp(simple.lotka.r(mort = nm.init,fecund = fec.init,ages=ages)$res$r)
-      lam.org.fish <- exp(simple.lotka.r(mort =  z.init,fecund = fec.init,ages=ages)$res$r)
-
-      # Now summarize these
-      res.lambda[[yy]] <-  data.frame(lam.no.fish = lam.no.fish,lam.fish = lam.fish,
-                                      lam.org.no.fish = lam.org.no.fish,
-                                      lam.org.fish = lam.org.fish,
-                                      year=years[yy],meta.tmp)
-    } # End the yy loop to get the lambdas...
-  # unpack it...
-  res.fin[[i]] <- do.call('rbind',res.cohort)
-  res.year.fin[[i]] <- do.call('rbind',res.year)
-  res.lambda.fin[[i]] <-  do.call('rbind',res.lambda)
-  }  # end if to make sure we have enough data to get the cohort estimates.
-
-  }# end the stock loop
-
-  res.cohort.final <- do.call('rbind',res.fin)
-  res.year.final <- do.call('rbind',res.year.fin)
-  res.lambda.final <- do.call('rbind',res.lambda.fin)
-
-  pop.dam <- res.cohort.final |> collapse::fgroup_by(cohort,Stock) |> collapse::fsummarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
-                                                                                   gen.len.org = sum(x.mx.lx.org)/sum(mx.lx.org),
-                                                                                   R0.opt = sum(mx.lx.opt),R0.org = sum(mx.lx.org))
-  pop.dam <- left_join(pop.dam,meta.sub,by="Stock")
-
-  dub.time.summary <- data.frame(dub.time.summary)
-  pop.dam <- data.frame(pop.dam)
-  # saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",what.2.tune,".Rds"))
-  # saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",what.2.tune,".Rds"))
-  # saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",what.2.tune,".Rds"))
-  save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
-       file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
-
-  write.csv(meta.sub, paste0(loc,"/Data/metadata_no_age_corection.csv"))
-} # end if load results
-```
-
-```{r clean-up-and-stats,include=F,echo=F,message=F,warning=F}
-load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
-for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-
-Stocks <- unique(res.lambda.final$Stock)
-res.lambda.fin <- data.frame(res.lambda.final)
-six.species <- c('morhua','harengus','aeglefinus','virens','solea','platessa')
-pop.dam.6 <- pop.dam |> collapse::fsubset(Species %in% six.species)
-for.tunes.6 <- for.tunes |> collapse::fsubset(Species %in% six.species)
-dub.time.6 <- dub.time.summary |> collapse::fsubset(Species %in% six.species)
-res.lambda.fin$decade <- floor(res.lambda.fin$year/10)*10
-res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock,decade) |> collapse::fmutate(mn.lam = mean(lam.fish,na.rm=T),
-                                                                                 med.lam = median(lam.fish,na.rm=T),
-                                                                                 sd.lam = sd(lam.fish,na.rm=T))
-res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Species,decade) |> collapse::fmutate(lm.spec.mn = mean(mn.lam,na.rm=T))              
-res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock) |> 
-                                                          collapse::fmutate(
-                                                          lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
-                                                          lam.fish.mn = mean(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T),
-                                                          lam.no.fish.med = median(lam.no.fish,na.rm=T),
-                                                          lam.fish.med = median(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.med = median(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T),
-                                                          lam.no.fish.sd = sd(lam.no.fish,na.rm=T),
-                                                          lam.fish.sd = sd(lam.fish,na.rm=T),
-                                                          lam.org.no.fish.sd = sd(lam.org.no.fish,na.rm=T),
-                                                          lam.org.fish.sd = sd(lam.org.fish,na.rm=T)
-                                                          ) |> data.frame()
-# Get the order right for the stock no species for the boxplots to come later
-sns.order <- c("Baltic Sea ", "Baltic Sea 22-24", "Baltic Sea 25-32", "Baltic Sea 28", 
-               "North Sea ", "North Sea 4", "North Sea 22-24", "North Sea 4-7 20", "North Sea 6a","North Sea 4 20", "North Sea 7d",     
-               "Celtic Sea ","Celtic Sea RA", "Celtic Sea 7a", "Celtic Sea 27.6a", 
-               "Irish Sea ","Irish Sea 7a", "Irish Sea 7e","Bay of Biscay ", "NE Arctic ", 
-               "Faroes 5a", "Faroes 5b",  "Iceland ", "Iceland 5a",
-                "NAFO 2-4 Fa-SGSL", "NAFO 2-4 Sp-SGSL", "NAFO 2-4 SGSL", "NAFO 2-4 NGSL", "NAFO 2-4 NFLD",  
-                "NAFO 5-6 ", "NAFO 5-6 GB", "NAFO 5-6 GOM", "NAFO 5-6 EGB",
-                "Bering Sea & AI ", "Gulf of Alaska ", "Aleutian Islands ")
-
-res.lambda.fin$Stock.no.species <- factor(res.lambda.fin$Stock.no.species,levels = sns.order,ordered = T)
-res.lambda.final.6 <- res.lambda.fin |> collapse::fsubset(Species %in% six.species)
-# Sort the data into a nice order...
-res.lambda.fin <- res.lambda.fin |> collapse::roworder(Species,Area.broad) |>
-                                    collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-# Making the Aleutian Islands their own Area long...
-res.lambda.fin$Area.long[res.lambda.fin$Area == "AI"] <- "Aleutian Islands"
-res.lambda.fin$Area.long <- factor(res.lambda.fin$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
-                                                                       "Irish Sea","Bay of Biscay","NE Arctic",
-                                                                       "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-
-res.lambda.final.6 <- res.lambda.final.6 |> collapse::roworder(Species,Area.broad) |>
-                                            collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-dub.time <- dub.time |> collapse::roworder(LME) |>
-                        collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-dub.time.summary <- dub.time.summary |> collapse::roworder(LME,Order,Species,Area.broad) |>
-                                        collapse::fmutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-dub.time.6 <- dub.time.6 |> collapse::roworder(LME) |>
-                             collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-pop.dam <- pop.dam |> collapse::roworder(Species,LME) |>
-                       collapse::fmutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
-pop.dam.6 <- pop.dam.6 |> collapse::roworder(LME,Area.broad) |>
-                       collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-pop.dam$Area.long[pop.dam$Area == "AI"] <- "Aleutian Islands"
-pop.dam$Area.long <- factor(pop.dam$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
-                                                         "Irish Sea","Bay of Biscay","NE Arctic",
-                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-# I'd also like a pop.dam including fishing
-pop.dam.fish <- res.cohort.final |> collapse::fgroup_by(cohort,Stock) |> collapse::fsummarise(gen.len.opt = sum(x.mx.zx.opt)/sum(mx.zx.opt),
-                                                                                   gen.len.org = sum(x.mx.zx.org)/sum(mx.zx.org),
-                                                                                   R0.opt = sum(mx.zx.opt),R0.org = sum(mx.zx.org))
-pop.dam.fish <- left_join(pop.dam.fish,meta.sub,by="Stock")
-pop.dam.fish$Area.long[pop.dam.fish$Area == "AI"] <- "Aleutian Islands"
-pop.dam.fish$Area.long <- factor(pop.dam.fish$Area.long,levels = c("Baltic Sea", "North Sea","Celtic Sea",
-                                                         "Irish Sea","Bay of Biscay","NE Arctic",
-                                                         "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-pop.dam <- data.frame(pop.dam)
-
-pop.dam.fish <- pop.dam.fish |> collapse::roworder(Species,LME) |>
-                                collapse::fmutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
-pop.dam.fish.6 <- pop.dam.fish |> collapse::fsubset(Species %in% six.species)
-
-pop.dam.fish.6 <- pop.dam.fish.6 |> collapse::roworder(LME,Area.broad) |>
-                                    collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
-
-# Put the population dynamics stuff together.
-pop.dam$group <- "no fish"
-pop.dam.fish$group <- 'fish'
-pop.dam.all <- rbind(pop.dam,pop.dam.fish)
-
-pop.dam.6$Stock.no.species <- factor(pop.dam.6$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam$Stock.no.species <- factor(pop.dam$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam.fish.6$Stock.no.species <- factor(pop.dam.fish.6$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam.fish$Stock.no.species <- factor(pop.dam.fish$Stock.no.species,levels = sns.order,ordered = T)
-pop.dam.all$Stock.no.species <- factor(pop.dam.all$Stock.no.species,levels = sns.order,ordered = T)
-# Drop the periods....
-pop.dam.all.6 <- pop.dam.all |> collapse::fsubset(!Species %in% six.species)
-pop.dam.all$G.Species <- gsub("\\.","",pop.dam.all$G.Species)
-pop.dam.all$G.Species.short <- substr(pop.dam.all$G.Species,1,5)
-pop.dam.all$G.Species <- gsub("\\.","",pop.dam.all$G.Species)
-pop.dam.all.6 <- pop.dam.all |> collapse::fsubset(Species %in% six.species)
-pop.dam.all.others <- pop.dam.all |> collapse::fsubset(!Species %in% six.species)
-
-# Reorder the doubling time, either by Species and LME, or the other way around
-
-dub.time.summary$Order.short <- "Gadi"
-dub.time.summary$Order.short[dub.time.summary$Order == "Pleuronectiformes"] <- "Plero"
-dub.time.summary$Order.short[dub.time.summary$Order == "Clupeiformes"] <- "Clupei"
-dub.time.summary$Order.short[dub.time.summary$Order == "Scorpaeniformes "] <- "Scor"
-dub.time.summary$Order.short[dub.time.summary$Order == "Scombriformes"] <- "Scomb"
-dub.time.summary$Order.short[dub.time.summary$Order == "Perciformes"] <- "Perci"
-# First need to get the abundance and lambdas with no fishing into one object.
-ft.tmp <- for.tunes |> collapse::fselect(year,Stock,vpa.abund,est.abund,removals)
-dd.dat <- left_join(res.lambda.fin,ft.tmp,by=c('year','Stock'))
-# Now I need to get a relative abundance for each stock...
-dd.dat <- dd.dat |> collapse::fgroup_by(Stock) |> collapse::fmutate(max.abund = max(est.abund,na.rm=T))
-dd.dat <- data.frame(dd.dat)
-dd.dat$prop.abund <- dd.dat$est.abund/dd.dat$max.abund
-# Drop nas....
-drops <- -which(is.na(dd.dat$prop.abund))
-dd.dat <- dd.dat[drops,]
-#lump the data into bins
-dd.dat$prop.bin <- "< 10%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.1 & dd.dat$prop.abund <= 0.2] <- "10-20%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.2 & dd.dat$prop.abund <= 0.3] <- "20-30%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.3 & dd.dat$prop.abund <= 0.4] <- "30-40%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.4 & dd.dat$prop.abund <= 0.6] <- "40-60%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.6 & dd.dat$prop.abund <= 0.8] <- "60-80%"
-dd.dat$prop.bin[dd.dat$prop.abund > 0.8 & dd.dat$prop.abund <= 1] <- "80-100%"
-dd.dat$prop.bin <- factor(dd.dat$prop.bin,levels=c("< 10%","10-20%","20-30%","30-40%","40-60%","60-80%","80-100%"))
-
-# Subset to the big six
-dd.dat.six <- dd.dat  |>collapse::fsubset(Species %in% six.species)
-
-# This is for the new lambda figures with fishing and no fishing together
-
-res.lambda.fin.long <- res.lambda.fin |> tidyr::pivot_longer(cols = c(lam.no.fish,lam.fish),names_to = 'group',values_to = 'lambda')
-res.lambda.fin.long$Stock.no.species <- factor(res.lambda.fin.long$Stock.no.species,levels = sns.order,ordered = T)
-res.lambda.fin.long$group <- substr(res.lambda.fin.long$group,5,20)
-res.lambda.fin.long$group <- gsub("\\."," ",res.lambda.fin.long$group)
-res.lambda.fin.long.others <- res.lambda.fin.long |> collapse::fsubset(!Species %in% six.species)
-res.lambda.fin.long.others$G.Species <- gsub("\\.","",res.lambda.fin.long.others$G.Species)
-res.lambda.fin.long.others$G.Species.short <- substr(res.lambda.fin.long.others$G.Species,1,5)
-res.lambda.fin.long.6 <- res.lambda.fin.long |> collapse::fsubset(Species %in% six.species)
-res.lambda.fin.long.6$G.Species <- gsub("\\.","",res.lambda.fin.long.6$G.Species)
-
-# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE# GAM FOR DENSITY DEPENENCE
-# here is the GAM for no fishing with subsequent processing.
-mod.dd.stock.gam.nf <- gam(log(lam.no.fish) ~   s(prop.abund,k=4) + s(prop.abund,as.factor(Stock.short),bs='fs',k=3) ,data=dd.dat)
-
-# This extracts the GAM fit so we can custom plot it on our own figure
-tmp <- plot(mod.dd.stock.gam.nf, pages = 0)
-no.stock.gam.nf.dat <- data.frame(fit = tmp[[1]]$fit + coefficients(mod.dd.stock.gam.nf)[1],prop.abund = tmp[[1]]$x,se = tmp[[1]]$se,Scenario = "F = 0")
-no.stock.gam.nf.dat$LCI <- no.stock.gam.nf.dat$fit - 1.96*no.stock.gam.nf.dat$se
-no.stock.gam.nf.dat$UCI <- no.stock.gam.nf.dat$fit + 1.96*no.stock.gam.nf.dat$se
-
-#summary(mod.dd.stock.gam.nf)
-#Residuals, definitely still issues here, maybe a bit better than some others, maybe...
-#plot(residuals(mod.dd.stock.gam.nf) ~ fitted(mod.dd.stock.gam.nf))
-# Normality = no
-#qqnorm(residuals(mod.dd.stock.gam.nf))
-#qqline(residuals(mod.dd.stock.gam.nf))
-
-pred.dd.stock.gam.nf <- expand.grid(prop.abund = seq(0, 1, length.out = 250),
-                                         Stock.short=c(unique(dd.dat$Stock.short)))
-tmp <- predict(mod.dd.stock.gam.nf, pred.dd.stock.gam.nf, type = 'response', se.fit = TRUE) 
-# Another fun trick to extract the overall smooth fit, but didn't end up using this method.
-# sms <- smooths(mod.dd.stock.gam.nf)
-# excl <- grepl("as.factor",sms)
-# rm <- sms[excl]
-# tmp.ex <- predict(mod.dd.stock.gam.nf, newdata =pred.dd.stock.gam.nf, type = 'response', se.fit = TRUE,exclude =rm) 
-# Get the fit by stock
-pred.dd.stock.gam.nf$lam.no.fish   <- exp(tmp$fit)
-pred.dd.stock.gam.nf$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-pred.dd.stock.gam.nf$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-
-# Thin the data so I can add points to the figure
-tmp <- NULL
-for(i in 1:(77)) 
-{
-  if(i==1) tmp[[i]] <- seq(10,230,length.out=5)
-  if(i>1) tmp[[i]] <- seq(10,230,length.out=5)+250*(i-1)
-}
-thinner.nf <- do.call('c',tmp)
-thin.pred.nf <- pred.dd.stock.gam.nf[thinner.nf,]
-# Now I want to get rid of extrapolation from this prediction data.frame, I think I need to loop it...
-# 
-short.stocks <- unique(dd.dat$Stock.short)
-n.stocks <- length(short.stocks)
-pred.out <- NULL
-thin.out <- NULL
-for(i in short.stocks)
-{
-  # Get the right stocks
-  tmpy <- dd.dat |> collapse::fsubset(Stock.short == i)
-  tmp.pred <- pred.dd.stock.gam.nf |> collapse::fsubset(Stock.short == i)
-  tmp.thin <- thin.pred.nf |> collapse::fsubset(Stock.short == i)
-  # I dont want to predict below the minimum observed abundance
-  mins <- min(tmpy$prop.abund,na.rm=T)
-  pred.out[[i]] <- tmp.pred |> collapse::fsubset(prop.abund >= mins)
-  thin.out[[i]] <- tmp.thin |> collapse::fsubset(prop.abund >= mins)
-}
-
-pred.dd.stock.gam.ss.nf <- do.call('rbind',pred.out)
-thin.pred.nf <- do.call('rbind',thin.out)
-# Combine pred stuff with the meta data for fun plots
-pred.dd.stock.gam.ss.nf <- left_join(pred.dd.stock.gam.ss.nf,meta.sub,by="Stock.short")
-pred.dd.stock.gam.ss.nf <- data.frame(pred.dd.stock.gam.ss.nf)
-thin.pred.nf <- left_join(thin.pred.nf,meta.sub,by="Stock.short")
-# Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# By region
-cols.gam <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
-pty.gam <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
-
-# Now do the same thing with the data that includes the effect of fishing.
-
-#mod.dd.stock.gam.fish <- gam(log(lam.fish) ~  as.factor(Stock.short) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.dat)
-mod.dd.stock.gam.fish <- gam(log(lam.fish) ~  s(prop.abund,k=4) + s(prop.abund,as.factor(Stock.short),bs='fs',k=3),data=dd.dat)
-
-tmp <- plot(mod.dd.stock.gam.fish, pages = 0)
-no.stock.gam.fish.dat <- data.frame(fit = tmp[[1]]$fit + coefficients(mod.dd.stock.gam.fish)[1],prop.abund = tmp[[1]]$x,se = tmp[[1]]$se,Scenario = "F > 0")
-no.stock.gam.fish.dat$LCI <- no.stock.gam.fish.dat$fit - 1.96*no.stock.gam.fish.dat$se
-no.stock.gam.fish.dat$UCI <- no.stock.gam.fish.dat$fit + 1.96*no.stock.gam.fish.dat$se
-
-#summary(mod.dd.stock.gam.fish)
-#Residuals, definetly still issues here, maybe a bit better than some others, maybe...
-#plot(residuals(mod.dd.stock.gam.fish) ~ fitted(mod.dd.stock.gam.fish))
-# Normality = no
-#qqnorm(residuals(mod.dd.stock.gam.fish))
-#qqline(residuals(mod.dd.stock.gam.fish))
-
-pred.dd.stock.gam.fish <- expand.grid(prop.abund = seq(0, 1, length.out = 250),
-                                         Stock.short=c(unique(dd.dat$Stock.short)))
-tmp <- predict(mod.dd.stock.gam.fish, pred.dd.stock.gam.fish, type = 'response', se.fit = TRUE) 
-pred.dd.stock.gam.fish$lam.fish   <- exp(tmp$fit)
-pred.dd.stock.gam.fish$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-pred.dd.stock.gam.fish$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-
-# Thin the data so I can add points to the figure
-tmp <- NULL
-for(i in 1:(77)) 
-{
-  if(i==1) tmp[[i]] <- seq(10,230,length.out=5)
-  if(i>1) tmp[[i]] <- seq(10,230,length.out=5)+250*(i-1)
-}
-thinner.fish <- do.call('c',tmp)
-thin.pred.fish <- pred.dd.stock.gam.fish[thinner.fish,]
-# Now I want to get rid of extrapolation from this prediction data.frame, I think I need to loop it...
-# 
-short.stocks <- unique(dd.dat$Stock.short)
-pred.out <- NULL
-thin.out <- NULL
-for(i in short.stocks)
-{
-  # Get the right stocks
-  tmpy <- dd.dat |> collapse::fsubset(Stock.short == i)
-  tmp.pred <- pred.dd.stock.gam.fish |> collapse::fsubset(Stock.short == i)
-  tmp.thin <- thin.pred.fish |> collapse::fsubset(Stock.short == i)
-  # I dont want to predict below the minimum observed abundance
-  mins <- min(tmpy$prop.abund,na.rm=T)
-  pred.out[[i]] <- tmp.pred |> collapse::fsubset(prop.abund >= mins)
-  thin.out[[i]] <- tmp.thin |> collapse::fsubset(prop.abund >= mins)
-}
-
-pred.dd.stock.gam.ss.fish <- do.call('rbind',pred.out)
-thin.pred.fish <- do.call('rbind',thin.out)
-# Combine pred stuff with the meta data for fun plots
-pred.dd.stock.gam.ss.fish <- left_join(pred.dd.stock.gam.ss.fish,meta.sub,by="Stock.short")
-pred.dd.stock.gam.ss.fish <- data.frame(pred.dd.stock.gam.ss.fish)
-
-thin.pred.fish <- left_join(thin.pred.fish,meta.sub,by="Stock.short")
-
-# Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# By region
-
-# What proportion of the stocks had the lowest 'GAM' estimate happen when the stock was at it's maximum size.
-low.gam <- data.frame(low.pa.fish = NA,diff.low.pa.fish = NA,low.pa.nf = NA,diff.low.pa.nf = NA,Stock = NA,Species = NA)
-count <- 0
-for(i in short.stocks) 
-{
-  count = count +1
-  tmp <- pred.dd.stock.gam.ss.fish |> collapse::fsubset(Stock.short == i)
-  tmp.nf <- pred.dd.stock.gam.ss.nf |> collapse::fsubset(Stock.short == i)
-  low.pa <- data.frame(low.pa.fish = tmp$prop.abund[tmp$lam.fish == min(tmp$lam.fish)],
-                       diff.low.pa.fish = tmp$lam.fish[tmp$lam.fish == min(tmp$lam.fish)] - tmp$lam.fish[tmp$prop.abund == max(tmp$prop.abund)],
-                       low.pa.nf = tmp.nf$prop.abund[tmp.nf$lam.no.fish == min(tmp.nf$lam.no.fish)],
-                       diff.low.pa.nf = tmp.nf$lam.no.fish[tmp.nf$lam.no.fish == min(tmp.nf$lam.no.fish)] - tmp.nf$lam.no.fish[tmp.nf$prop.abund == max(tmp.nf$prop.abund)],
-                       Stock = i,Species = tmp$G.Species[1])
-  low.gam[count,] <- low.pa
-}
-
-# Let's compare lambda at minimum, 0.4, and maximum and make a Table
-comp.lam.diff <- NULL
-comp.lam <- NULL
-comp.all.nf <- NULL
-comp.all.fish <- NULL
-for(i in short.stocks) 
-{
-  tmp <- pred.dd.stock.gam.ss.fish |> collapse::fsubset(Stock.short == i)
-  which.40 <- max(which(tmp$prop.abund <=0.4)) # Some stocks might not have a which 40.
-  which.max <- which(tmp$prop.abund ==1)
-  which.min <- which(tmp$prop.abund == min(tmp$prop.abund))
-  tmp.sub <- tmp[c(which.min,which.40,which.max),]
-  comp.all.fish[[i]] <- tmp.sub
-  tmp.nf <- pred.dd.stock.gam.ss.nf |> collapse::fsubset(Stock.short == i)
-  # I think I'm overkilling as this should be the same was the above witches....
-  which.40.nf <- max(which(tmp.nf$prop.abund <=0.4))
-  which.max.nf <- which(tmp.nf$prop.abund ==1)
-  which.min.nf <- which(tmp.nf$prop.abund ==min(tmp.nf$prop.abund))
-  tmp.nf.sub <- tmp.nf[c(which.min.nf,which.40.nf,which.max.nf),]
-  comp.all.nf[[i]] <- tmp.nf.sub
-  # Now we just want some summaries here I think...
-  comp.lam.diff[[i]] <- data.frame(min.abund = min(tmp.sub$prop.abund,na.rm=T),
-                              lam.fish.min.40 = tmp$lam.fish[which.min] - tmp$lam.fish[which.40],
-                              lam.fish.min.max = tmp$lam.fish[which.min] - tmp$lam.fish[which.max],
-                              lam.fish.40.max = tmp$lam.fish[which.40] - tmp$lam.fish[which.max],
-                              lam.nf.min.40 = tmp.nf$lam.no.fish[which.min.nf] - tmp.nf$lam.no.fish[which.40.nf],
-                              lam.nf.min.max = tmp.nf$lam.no.fish[which.min.nf] - tmp.nf$lam.no.fish[which.max.nf],
-                              lam.nf.40.max = tmp.nf$lam.no.fish[which.40.nf] - tmp.nf$lam.no.fish[which.max.nf],
-                              Stock = i,Species = tmp$G.Species[1])
-
-    comp.lam[[i]] <- data.frame(min.abund = min(tmp.sub$prop.abund,na.rm=T),
-                                lam.fish.min = tmp$lam.fish[which.min] ,
-                                lam.fish.40 = tmp$lam.fish[which.40],
-                                lam.fish.max = tmp$lam.fish[which.max],
-                                lam.nf.min = tmp.nf$lam.no.fish[which.min.nf],
-                                lam.nf.40 = tmp.nf$lam.no.fish[which.40.nf],
-                                lam.nf.max = tmp.nf$lam.no.fish[which.max.nf],
-                                Stock = i,Species = tmp$G.Species[1])
-}
-
-# A table for the estimates at 'interesting' values
-comp.lam.res <- do.call('rbind',comp.lam)
-# I want to turn this into a table....
-comp.lam.res.tab <- comp.lam.res
-# Round the numbers
-comp.lam.res.tab$min.abund <- round(comp.lam.res.tab$min.abund,digits=2)
-rounders <- c("lam.fish.min","lam.fish.40","lam.fish.max",
-              "lam.nf.min","lam.nf.40","lam.nf.max")
-comp.lam.res.tab[,rounders]      <- round(comp.lam.res.tab[,rounders] ,digits=3)
-# Now give it pretty names
-tab.names <- c("Minimum Abundance",
-               "$\\lambda_{F>0}^{Min}$",
-               "$\\lambda_{F>0}^{40}$",
-               "$\\lambda_{F>0}^{Max}$",
-               "$\\lambda_{F=0}^{Min}$",
-               "$\\lambda_{F=0}^{40}$",
-               "$\\lambda_{F=0}^{Max}$",
-               "Stock","Species")
-names(comp.lam.res.tab) <- tab.names
-
-# Now do the same with the differences
-comp.lam.diff.res <- do.call('rbind',comp.lam.diff)
-# I want to turn this into a table....
-comp.lam.diff.res.tab <- comp.lam.diff.res
-# Round the numbers
-comp.lam.diff.res.tab$min.abund <- round(comp.lam.diff.res.tab$min.abund,digits=2)
-rounders <- c("lam.fish.min.40","lam.fish.min.max","lam.fish.40.max",
-                    "lam.nf.min.40","lam.nf.min.max","lam.nf.40.max")
-comp.lam.diff.res.tab[,rounders] <- round(comp.lam.diff.res.tab[,rounders] ,digits=3)
-# Now give it pretty names
-tab.names <- c("Minimum Abundance",
-               "$\\lambda_{F>0}^{Min-40}$",
-               "$\\lambda_{F>0}^{Min-Max}$",
-               "$\\lambda_{F>0}^{40-Max}$",
-               "$\\lambda_{F=0}^{Min-40}$",
-               "$\\lambda_{F=0}^{Min-Max}$",
-               "$\\lambda_{F=0}^{40-Max}$",
-               "Stock","Species")
-names(comp.lam.diff.res.tab) <- tab.names
-
-# Used for the figure showing the number of stocks that have recovered by year x.
-n.dub <- data.frame(years = 1:n.sim.years, count = NA)
-for(i in 1:n.sim.years) n.dub$count[i] <- dub.time.summary |> collapse::fsubset(year==i & prop >= 0.75) |> nrow()
-
-# Compare the population recovery with the variance, using 2010 because all stocks have a value at 2010... 
-# I'm using the overall lambda sd, so the year doesn't actually matter other than to make sure all stocks are included here
-# This is used for the recovery variance figure, is this data good?
-# How many of the stocks had doubled by year 20, with 75% being my standard, which is a high standard
-dub.p.high <- 0.75
-dub.p.low <- 0.5
-n.dub.10 <- dub.time.summary |> collapse::fsubset(year==10 & prop >= dub.p.high) |> nrow()
-n.dub.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop >= dub.p.high) |> nrow()
-# Slow stocks, here we define having a low recovery potential has having < 50% of the simulatoins experience a doubling in size.
-slow.20 <- dub.time.summary |> collapse::fsubset(year==20 & prop < dub.p.low) 
-prop.rec.20 <- dub.time.summary |> collapse::fsubset(year==20) # the proportion that recovers by year 20
-lambda.sds <- res.lambda.fin |> collapse::fsubset(year == 2010)
-lam.sd.p.rec <- left_join(prop.rec.20,lambda.sds,by=names(prop.rec.20)[c(1,4:24)]) 
-lam.sd.p.rec$prop.cat <- "Moderate"
-lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop < dub.p.low] <- "Low"
-lam.sd.p.rec$prop.cat[lam.sd.p.rec$prop >= dub.p.high] <- "High"
-lam.sd.p.rec$prop.cat <- factor(lam.sd.p.rec$prop.cat,levels=c("Low","Moderate","High"))
-
-```
-
-```{r paper-calcs,include=F,echo=F,message=F,warning=F}
-
-# the lambda calcs
-med.lambda.F0 <- round(median(res.lambda.fin$lam.no.fish),digits=3)
-med.r.F0 <- round(median(log(res.lambda.fin$lam.no.fish)),digits=3)*100
-med.lambda.F <- round(median(res.lambda.fin$lam.fish),digits=3)
-med.r.F <- round(median(log(res.lambda.fin$lam.fish)),digits=3)*100
-mn.lambda.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
-mn.r.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
-# Mean - median...
-res.lambda.fin$med.mn.diff.no.fish <- res.lambda.fin$lam.no.fish.med - res.lambda.fin$lam.no.fish.mn
-res.lambda.fin$med.mn.diff.fish <- res.lambda.fin$lam.fish.med - res.lambda.fin$lam.fish.mn
-# How many stocks had the mean higher than the median
-n.mn.higher.med.no.fish <- length(unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.no.fish < 0]))
-n.mn.higher.med.fish <- length(unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.fish < 0]))
-low.mn.lambda.stocks <- unique(res.lambda.fin$Stock.short[res.lambda.fin$med.mn.diff.fish > 0])
-n.nw.ice <- length(c(grep("NAFO",low.mn.lambda.stocks),grep("Faroe",low.mn.lambda.stocks)))
-n.cod.low.mn <- length(grep("morhua",low.mn.lambda.stocks))
-n.cod <- length(grep("morhua",Stocks))
-
-# Density dependence related numbers
-n.bl.40 <- length(which(!is.na(comp.lam.res$lam.fish.40)))
-n.low.40.nf <- length(which(comp.lam.res$lam.nf.40 < 1))
-n.low.40.fish <-length(which(comp.lam.res$lam.fish.40 < 1))
-low.lam.40.nf <- -round(min(comp.lam.diff.res$lam.nf.40,na.rm=T),digits=3)
-low.4.lam.40.nf <- -round(sort(comp.lam.diff.res$lam.nf.40)[4],digits=3)
-
-# If right isn't this interesting!!! And look, 3 cod stocks from around here all say around 0.4 is the worst.  Most interesting...
-n.low.lam.at.max.fish <- length(which(low.gam$low.pa.fish == 1))
-n.low.lam.at.max.nf <- length(which(low.gam$low.pa.nf == 1))
-low.lam.cods <- low.gam[low.gam$low.pa.nf < 1 & low.gam$Species == "G. morhua",]
-n.cod.lam.not.at.max.nf <- nrow(low.lam.cods)
-pa.low.cod.min <- round(min(low.lam.cods$low.pa.nf),digits=2)
-pa.low.cod.max <- round(max(low.lam.cods$low.pa.nf),digits=2)
-
-# more density dependence numbers
-pa.lam.nf.at.one <- 100*round(no.stock.gam.nf.dat$prop.abund[min(which(no.stock.gam.nf.dat$fit <0))],digits=2)
-pa.lam.fish.at.one <- 100*round(no.stock.gam.fish.dat$prop.abund[min(which(no.stock.gam.fish.dat$fit <0))],digits=2)
-# What is the minimum abundance at which we get a 2 with the fishing lambdas.
-pa.big.threshold <- 0.65
-pa.low.threshold <- 0.8
-lam.low.threshold <- 0.8
-pa.lam.fish.low.bigs <- max(dd.dat$lam.fish[dd.dat$prop.abund >= pa.big.threshold])
-pa.lam.nf.low.bigs <- round(rev(sort(dd.dat$lam.no.fish[dd.dat$prop.abund >= pa.big.threshold]))[2],digits =2)
-# What proportion of the stocks had large declines overall, and then the proportion when the population was below 30%
-dd.dat.high <- dd.dat |> collapse::fsubset(prop.abund >= 0.3)
-prop.low.high.abund <- round(length(which(dd.dat.high$lam.fish < lam.low.threshold)) / nrow(dd.dat.high),digits=3)
-prop.low.all <- round(length(which(dd.dat$lam.fish < lam.low.threshold)) / nrow(dd.dat),digits=3)
-dd.dat.low <- dd.dat |> collapse::fsubset(prop.abund < 0.3)
-prop.low.low.abund <- round(length(which(dd.dat.low$lam.fish < lam.low.threshold)) / nrow(dd.dat.low),digits=3)
-
-# Numbers for the paper, lifetime reproductive growth
-r0.mn <- round(mean(pop.dam$R0.opt,na.rm=T),digits=1)
-r0.med <- round(median(pop.dam$R0.opt,na.rm=T),digits=1)
-# And fishing...
-r0.mn.fish <- round(mean(pop.dam.fish$R0.opt,na.rm=T),digits=1)
-r0.med.fish <- round(median(pop.dam.fish$R0.opt,na.rm=T),digits=1)
-
-# Where are the slow ones from
-n.not.dub.20 <- nrow(slow.20)
-n.alaska <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short== "AFSC"]))
-n.nwa <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("DFO-TRAC","NEFSC")]))
-n.nea <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Manage.short %in% c("ICES")]))
-n.nafo.24 <- length(unique(dub.time.summary$Stock.short[dub.time.summary$Area.broad %in% "NAFO 2-4"]))
-# Now the don't recover ones...
-n.alaska.slow <- length(slow.20$Stock.short[slow.20$Manage.short== "AFSC"])
-n.nwa.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% c("DFO-TRAC","NEFSC")])
-n.nea.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% "ICES"])
-
-# Need to grab all the per.diff's, which I seem to have dropped
-for.diffs <- do.call('rbind',for.tune.summary)
-med.per.diff <- round(median(for.diffs$per.diff,na.rm=T),digits=1)
-# what is lambda difference, about 6%, but that means the original was 7% higher, so that means we are reducing lambda when optimizing
-# If there was 'missing fishing' we are compensating for with this, this is exactly what we'd expect to happen right?
-res.lambda.fin$lam.per.diff <- 100*((res.lambda.fin$lam.org.no.fish - res.lambda.fin$lam.no.fish)/ res.lambda.fin$lam.no.fish)
-med.lam.per.diff <- round(median(res.lambda.fin$lam.per.diff,na.rm=T),digits=1)
-# By stock, can see most are positive, which is in line with missing fishing mortality...
-mod.by.stock.lam.pd <- res.lambda.fin |> collapse::fgroup_by(Stock.short) |> collapse::fsummarise(med = median(lam.per.diff,na.rm=T),
-                                                                                                  mn = mean(lam.per.diff,na.rm=T))
-
-```
-
-```{r main-figs,include=F,echo=F,message=F,warning=F}
-
-# New lambda plot with the fishing and no fishing beside each other
-# This is likely Figure 1
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Stock.no.species),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(G.Species),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 19,base_height = 15)
-
-# The other stocks, perhaps we put this in a supplement...
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(y=lambda,interaction(group,G.Species.short),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(Area.long),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 19,base_height = 15)
-
-# Standard deviation figure
-colrs.sd <- rep(c(rep('blue',4),rep('orange',4),rep('grey',4),rep('black',4)),20)
-pty.sd <- rep(rep(c(21,4,9,8),4),20)
-
-lam.sd.plt <- ggplot(res.lambda.fin ) + 
-                                       geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
-                                       scale_y_log10("Standard deviation (Lambda)",log_breaks(n=8)) +
-                                       scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
-                                       theme(axis.text.x = element_text(angle =45,hjust=1),
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 10)
-
-# Overall density dependence
-# MAIN PAPER FIGURE#
-dd.nf.overall.plt <-ggplot(no.stock.gam.nf.dat , aes(x=prop.abund,y=exp(fit))) + 
-                                geom_point(data = dd.dat,aes(x=prop.abund,y=lam.no.fish),size=2,alpha=0.1) +  
-                                geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI)),alpha=0.5,linewidth=0,fill=u.colors[1])+
-                                geom_line(color=u.colors[1],linewidth=1) + 
-                                xlab("") + 
-                                scale_y_log10(name = "Lambda(F=0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_blank()) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-# MAIN PAPER FIGURE#
-dd.fish.overall.plt <- ggplot(no.stock.gam.fish.dat, aes(x=prop.abund,y=exp(fit))) + 
-                                geom_point(data = dd.dat,aes(x=prop.abund,y=lam.fish),size=2,alpha=0.1) +  
-                                geom_line(color=u.colors[2],linewidth=2) + 
-                                geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI)),alpha=0.5,fill=u.colors[2])+
-                                xlab("") + 
-                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed',linewidth=1.5)+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_blank()) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-# Main Paper Figure Density dependence with and without fishing, effectively a zoomed in version of the above.
-colrs <- u.colors
-t.smooth <- rbind(no.stock.gam.fish.dat,no.stock.gam.nf.dat)
-dd.fish.nf.plt <- ggplot(t.smooth, aes(x=prop.abund,y=exp(fit),group=Scenario,color=Scenario,fill=Scenario)) + 
-                                 geom_ribbon(aes(ymin=exp(LCI),ymax=exp(UCI),group=Scenario,fill=Scenario),alpha=0.50,linewidth=0)+
-                                 geom_line(linewidth=1.5) +
-                                 geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                 scale_fill_manual(values = colrs) + scale_color_manual(values = colrs) +
-                                 scale_x_continuous(name = "Proportion of maximum abundance",breaks = seq(0,1,by=0.1)) + 
-                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-                                 theme(legend.position = c(0.9,0.75))
-
-dd.overall.combo <- plot_grid(dd.nf.overall.plt,dd.fish.overall.plt,dd.fish.nf.plt,nrow=3)
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_overall_",what.2.tune,".png"),dd.overall.combo,base_width = 10,base_height = 10)
-
-new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(y=lambda,interaction(group,G.Species.short),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(Area.long),design=mat,scales='free_x')
-
-# Density dependence by stock 
-cols.gam <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
-pty.gam <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
-# Doing this manually because the ordered factor wasn't working... annoying...
-mat <- matrix(c(2, 2,13,13, 5, 5, 9, 9,
-                3, 3,12,12, 6, 6, 8, 8,
-               NA,NA,10,10,11,11,NA,NA,
-               NA,7, 7, 4, 4, 1, 1, NA),
-                4, 8, byrow = TRUE)
-
-dd.stocks.nf.plt <- ggplot(pred.dd.stock.gam.ss.nf,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=G.Species,shape=G.Species)) + 
-                                geom_line() + 
-                                geom_point(data = thin.pred.nf,size=2) +  
-                                xlab("Proportion of maximum abundance") + 
-                                scale_y_log10(name = "Lambda (F=0)",breaks = log_breaks(n=10)) +
-                                geom_ribbon(aes(ymin=lower,ymax=upper,color=G.Species),alpha=0.10,linewidth=0)+
-                                facet_manual(vars(Area.long),design=mat,scales='free_x')+
-                                #facet_wrap(~Area.long)  +
-                                scale_shape_manual(values=pty.gam) +
-                                scale_color_manual(values = cols.gam) + 
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_text(size=7)) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"),dd.stocks.nf.plt,base_width = 10,base_height = 10)
-
-mat <- matrix(c(2, 2,13,13, 5, 5, 9, 9,
-                3, 3,12,12, 6, 6, 8, 8,
-               NA,NA,10,10,11,11,NA,NA,
-               NA,7, 7, 4, 4, 1, 1, NA),
-                4, 8, byrow = TRUE)
-
-# MAIN PAPER FIGURE#
-dd.stocks.fish.plt <- ggplot(pred.dd.stock.gam.ss.fish,aes(x=prop.abund,y=lam.fish,group=Stock.short,color=G.Species,shape=G.Species)) + 
-                                geom_line() + 
-                                geom_point(data = thin.pred.fish,size=2) +  
-                                geom_ribbon(aes(ymin=lower,ymax=upper,color=G.Species),alpha=0.10,linewidth=0)+
-                                xlab("Proportion of maximum abundance") + 
-                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10)) +
-                                facet_manual(vars(Area.long),design=mat,scales='free_x')+
-                                #facet_wrap(~Area.long)  +
-                                scale_shape_manual(values=pty.gam) +
-                                scale_color_manual(values = cols.gam) + 
-                                geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
-                                theme(legend.text=element_text(size=8),
-                                      legend.spacing.y = unit(-0.1, 'cm'),
-                                      legend.title = element_blank(),
-                                      axis.text.x = element_text(size=7)) + 
-                                 guides(color = guide_legend(ncol=1,byrow=T),
-                                        shape = guide_legend(ncol=1,byrow=T))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_fish_stocks_",what.2.tune,".png"),dd.stocks.fish.plt,base_width = 10,base_height = 10)
-
-# Lifetime reproductive success 
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-r0.boxplt.6 <- ggplot(pop.dam.all.6) + geom_boxplot(aes(y=R0.opt,interaction(group,Stock.no.species),color=group))  + 
-                                       scale_x_discrete(NULL, guide = "axis_nested") + scale_y_log10(name = "Lifetime Reproductive Output")+
-                                       geom_hline(yintercept = 1,linetype='dashed',color='blue')+
-                                       facet_manual(vars(G.Species),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"),r0.boxplt.6,base_width = 19,base_height = 15)
-
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-r0.boxplot.others <- ggplot(pop.dam.all.others) +   geom_boxplot(aes(y=R0.opt,interaction(group,G.Species.short),color=group))  + 
-                                                    scale_x_discrete(NULL, guide = "axis_nested") + 
-                                                    scale_y_log10(name = "Lifetime Reproductive Output")+
-                                                    geom_hline(yintercept = 1,linetype='dashed',color='blue')+
-                                                    facet_manual(vars(Area.long),design=mat,scales='free')+
-                                                    theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                          plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"),r0.boxplot.others,base_width = 15,base_height = 10)
-
-r0.heatmap.ne <- ggplot(pop.dam |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-r0.heatmap.nw <- ggplot(pop.dam |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-r0.heatmap.pac <- ggplot(pop.dam |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                     xlab("") + ylab("")+
-                                     facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                     geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                     theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                           legend.key.width = unit(3,'cm'))
-
-r0.heatmap <- cowplot::plot_grid(r0.heatmap.pac,r0.heatmap.nw,r0.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_nf_",what.2.tune,".png"),r0.heatmap,base_width = 20,base_height = 17)
-
-r0.heatmap.ne.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-r0.heatmap.nw.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                    xlab("") + ylab("")+
-                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                    geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-r0.heatmap.pac.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
-                                     xlab("") + ylab("")+
-                                     facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                                     geom_tile() + 
-                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
-                                                        discrete=FALSE,trans='log') + 
-                                     theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                           legend.key.width = unit(3,'cm'))
-
-r0.heatmap.fish <- cowplot::plot_grid(r0.heatmap.pac.fish,r0.heatmap.nw.fish,r0.heatmap.ne.fish,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_fish_",what.2.tune,".png"),r0.heatmap.fish,base_width = 20,base_height = 17)
-
-# Generation length
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-gen.boxplt.6 <- ggplot(pop.dam.all.6) +
-                            geom_boxplot(aes(y=gen.len.opt,interaction(group,Stock.no.species),color=group))  + 
-                            scale_x_discrete(NULL, guide = "axis_nested") +
-                            scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
-                             facet_manual(vars(G.Species),design=mat,scales='free_x')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"),gen.boxplt.6,base_width = 19,base_height = 15)
-
-# Then the generation length for others.
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-gen.boxplt.others <- ggplot(pop.dam.all.others) +
-                            geom_boxplot(aes(y=gen.len.opt,interaction(group,G.Species.short),color=group))  + 
-                            scale_x_discrete(NULL, guide = "axis_nested") +
-                            scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
-                            facet_manual(vars(Area.long),design=mat,scales='free')+
-                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"),gen.boxplt.others,base_width = 15,base_height = 10)
-
-gen.heatmap.ne <- ggplot(pop.dam |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
-                                              xlab("") + ylab("")+  
-                                              facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                              geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-gen.heatmap.nw <- ggplot(pop.dam |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-gen.heatmap.pac <- ggplot(pop.dam |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
-                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-gen.heatmap <- cowplot::plot_grid(gen.heatmap.pac,gen.heatmap.nw,gen.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_nf_",what.2.tune,".png"),gen.heatmap,base_width = 15,base_height = 10)
-
-gen.heatmap.ne.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + 
-                                              xlab("") + ylab("")+  
-                                              facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
-                                              geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                                              theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))
-
-gen.heatmap.nw.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "NW Atlantic"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))
-
-gen.heatmap.pac.fish <- ggplot(pop.dam.fish |> collapse::fsubset(LME == "Pacific (Alaska)"), aes(x=cohort, y=Stock.short, fill= gen.len.opt)) + xlab("") + ylab("")+
-                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Generation length (years)",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-gen.heatmap.fish <- cowplot::plot_grid(gen.heatmap.pac.fish,gen.heatmap.nw.fish,gen.heatmap.ne.fish,nrow = 3,rel_heights = c(3,4,10))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_fish_",what.2.tune,".png"),gen.heatmap.fish,base_width = 15,base_height = 10)
-
-dub.time.summary <- dub.time.summary |> collapse::fsubset(year %in% 1:50) |>
-                            collapse::roworder(G.Species,LME,Area.broad) |>
-                            collapse::fmutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))
-
-dub.heatmap.gad <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Gadiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+                                    
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.45, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.pl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Pleuronectiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+                                    
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"))
-
-dub.heatmap.cl <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Clupeiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.35, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.per <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Perciformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.scom <- ggplot(dub.time.summary |> collapse::fsubset(Order == "Scombriformes"), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2.1, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap.scorp <- ggplot(dub.time.summary |> collapse::fsubset(Order %in% "Scorpaeniformes "), aes(x=year, y=Stock.short, fill= prop)) + 
-                            xlab("") + ylab("")+
-                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + 
-                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.5, "cm"),
-                                  legend.key.width = unit(3,'cm'))
-
-dub.heatmap <- cowplot::plot_grid(dub.heatmap.gad,dub.heatmap.pl,dub.heatmap.cl,dub.heatmap.per,dub.heatmap.scom,dub.heatmap.scorp,
-                                  nrow = 6,rel_heights = c(39,20,11,4,3,3))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"),dub.heatmap,base_width = 20,base_height = 20)
-
-# Doubling Time Figure 1
-dub.ts.plt <- ggplot(n.dub,aes(x=years,y=count)) + 
-                    geom_line() + 
-                    geom_hline(yintercept = length(Stocks),linetype="dashed") + 
-                    xlab("") + ylab("Number of Stocks")
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_time_series_",what.2.tune,".png"),dub.ts.plt,base_width = 10,base_height = 10)
-
-# Doubling time and variability
-
-# Is there a relationship between median and sd?
-colrs.cat <- c("blue","black","orange")
-pts.cat <- 21:23
-sd.rec.plt <- ggplot(lam.sd.p.rec, aes(y=lam.no.fish.med,x=lam.no.fish.sd,color=prop.cat,group=prop.cat)) + 
-                       geom_point(size =3,aes(shape=prop.cat,fill=prop.cat)) + 
-                       geom_hline(yintercept=1,linetype="dashed") + 
-                       scale_y_continuous(name="median Lambda") + scale_x_continuous(name="standard deviation Lambda") +
-                       scale_color_manual(values=colrs.cat) + scale_fill_manual(values=colrs.cat) +  
-                       scale_shape_manual(values=pts.cat) + theme(legend.title = element_blank())
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"),sd.rec.plt,base_width = 10,base_height = 10)
-
-```
-
-```{r the-others,include=F,echo=F,message=F,warning=F}
-#             
-# 
-# dub.heatmap.cod <- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "G.
-morhua"), aes(x=year, y=Stock.no.species, fill= prop)) + xlab("") + ylab("")+                                     facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") +
-#                             geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + scale_x_continuous(labels=NULL) +
-#                             theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
-#                                   legend.key.width = unit(3,'cm'))
-# 
-# dub.heatmap.herring<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "C. harengus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-# 
-# dub.heatmap.haddock<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "M. aeglefinus"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.125, "cm"))
-# 
-# dub.heatmap.virens<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. virens"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.4, "cm"))
-# 
-# dub.heatmap.solea<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "S. solea"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.4, "cm"))
-# 
-# dub.heatmap.platessa<- ggplot(dub.time.6 |> collapse::fsubset(G.Species == "P. platessa"), aes(x=year, y=Stock.no.species, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous() +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
-# 
-# 
-# 
-# dub.heatmap.sp6 <- cowplot::plot_grid(dub.heatmap.cod,dub.heatmap.herring,dub.heatmap.haddock,
-#                                  dub.heatmap.virens, dub.heatmap.solea,dub.heatmap.platessa,nrow = 6,rel_heights = c(14,9,8,5,5,4))
-# dub.heatmap.sp6
-# 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_sp6_",what.2.tune,".png"),dub.heatmap.sp6,base_width = 20,base_height = 17)
-# 
-# 
-# # What about a plot of the sd of lamda by stock
-# #colrs.sd <- rep(rep(c("black","blue","orange",'grey'),3),20)
-# #pty.sd <- rep(c(rep(21,4),rep(4,4),rep(9,4)),20)
-# 
-# 
-# # Same plot for the not 6 species
-# 
-# # lam.sd.other.plt <- ggplot(res.lambda.fin |> collapse::fsubset(!Species %in% six.species)) + 
-# #                                        geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
-# #                                        scale_y_log10("sd(lambda)",limits=c(0.05,1.5)) +
-# #                                        scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
-# #                                        theme(axis.text.x = element_text(angle =45,hjust=1),
-# #                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# # lam.sd.other.plt
-# 
-# 
-# 
-# 
-# # Doubling Times
-# 
-# 
-# # Generation length
-# 
-# # Main text figure!!
-# new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Area.long),color=group)) +
-#                                            #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-#                                            scale_x_discrete(NULL, guide = "axis_nested") +
-#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~G.Species,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# # The other stocks, plotting these by area
-# # Main Text FIGURE!
-# # More data
-# 
-# 
-# ################### Supplemental Figures################### Supplemental Figures################### Supplemental Figures################### Supplemental 
-# 
-# 
-# 
-# # Time series of lambdas....
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# #col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
-# pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
-# #pty <- rep(rep(c(21:23),5),20)
-# 
-# lambda.ts.plt <- ggplot(res.lambda.final.6,aes(y=lam.fish,x=year,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
-#                             geom_point(size=4) +
-#                             geom_smooth(method='gam',formula = y ~ s(x, bs = "cs", fx = TRUE, k = 5),se=F) + 
-#                             #scale_y_log10(name = "lambda") +
-#                             facet_wrap(~G.Species,scales='free_y') +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-#                             scale_fill_manual(name = "Stock",values = col.try)+
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm'))
-# #lambda.ts.plt
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_timeseries_6_",what.2.tune,".png"),lambda.ts.plt,base_width = 12,base_height = 10)
-# 
-# 
-# lambda.dec.plt <- ggplot(res.lambda.final.6,aes(y=med.lam,x=as.factor(decade))) +
-#                             geom_boxplot() + scale_y_log10()+
-#                             xlab("Decade") + ylab("Lambda") + 
-#                             geom_point(aes(x=as.factor(decade),y=lm.spec.mn),color='blue',shape=8,fill='blue')+
-#                             #scale_x_continuous(breaks=seq(1940,2020,by=10))+
-#                             geom_hline(yintercept = 1,linetype='dashed') +
-#                             facet_wrap(~G.Species,scales='free_y') 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_by_decade_6_",what.2.tune,".png"),lambda.dec.plt,base_width = 12,base_height = 12)
-# 
-#
-
-# ggplot(dd.dat) + geom_point(aes(x=prop.abund,y=lam.no.fish-1)) + xlab("Proportion of Maximum Abundance") + ylab("r (no fishing)")
-# 
-# # Density dependence by Species
-# ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
-#                                                    geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) #+
-#                                                    #scale_color_manual(values = colrs)
-# # Density dependence by stock
-# ggplot(dd.dat,aes(x=prop.abund,y=lam.no.fish,color=Stock.short,group=Stock.short)) + geom_point() + 
-#                                                    geom_smooth(method="lm",se = F) + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)", limits=c(0.4,2),
-#                                                                  breaks = seq(0.4,2,by=0.1)) +
-#                                                    theme(legend.position = 'none')
-# 
-# 
-# 
-# 
-# ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish)) + geom_point() + 
-#                                                     geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_continuous(name = "lambda (no fishing)")
-# 
-# ggplot(dd.dat.no.bigs,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + geom_point() + 
-#                                                     geom_smooth(method="lm",se=F) + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,2,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)")
-# 
-# 
-# # how about our big 6
-# colrs <- c("blue","black","firebrick2","orange",'grey50','grey90')
-# ggplot(dd.dat.six,aes(x=prop.abund,y=lam.no.fish,color=Species,group=Species)) + geom_point() + 
-#                                                     geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 1,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_log10(name = "lambda (no fishing)", breaks = c(0.5,0.75,1,1.5,2.5,3.5,5,7.5,10,12.5)) +
-#                                                    scale_color_manual(values = colrs)
-# 
-# 
-# ggplot(dd.dat.six.no.bigs,aes(x=prop.abund,y=lam.no.fish-1,color=Species,group=Species)) + geom_point() + 
-#                                                     geom_smooth(method="gam") + 
-#                                                    geom_hline(yintercept = 0,linewidth=2,linetype='dashed',color='blue') +
-#                                                    scale_x_continuous(name = "Proportion of Maximum Abundance", breaks = seq(0,1,by=0.1))+
-#                                                    scale_y_continuous(name = "r (no fishing)", breaks = seq(-1,1,by=0.2)) +
-#                                                    scale_color_manual(values = colrs)
-
-# Other things I did just randomly scattered here
-
-# 
-# #hmm <- merge(tst,res.lambda.final.6,by="Stock")
-# plot(res.lambda.fin$lam.fish.med ~ res.lambda.fin$lam.fish.mn)
-# # So this is lambda with fishing included
-# lambda.plt <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.no.fish,x=Stock.no.species))  + 
-#                                            geom_point(aes(y=lam.no.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~G.Species,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_no_fishing_6_",what.2.tune,".png"),lambda.plt,base_width = 12,base_height = 10)
-# 
-# # With fishing
-# lambda.plt.fish <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.fish,x=Stock.no.species))  + 
-#                                            geom_point(aes(y=lam.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
-#                                            xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~G.Species,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_with_fishing_6_",what.2.tune,".png"),lambda.plt.fish,base_width = 12,base_height = 10)
-# 
-# 
-# 
-# new.lam.plt <- ggplot(res.lambda.fin.long) + geom_boxplot(aes(y=lambda,interaction(group,Order),color=group)) +
-#                                            #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-#                                            scale_x_discrete(NULL, guide = "axis_nested") +
-#                                            #xlab("") + scale_y_log10("lambda",breaks = c(0.1,0.4,0.6,0.8,1,1.25,1.75,3,5,10),limits=c(0.4,10)) + 
-#                                            #geom_hline(yintercept = 1,linetype='dashed') +
-#                                            facet_wrap(~Area.long,scales='free')+
-#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
-#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-# 
-# 
-# # The final option I have is to do what I did before and use the bin props
-# We can then do a much more ANOVA kinda analysis, drat this doesn't converge..., estimate the 
-#mod.dd.bins.stock <- glmer(lam.no.fish ~ prop.bin + (1+prop.bin|Stock),data=dd.dat,family=gaussian(link='log'))
-# so go to lmer and log transform... and it is a singular fit
-#mod.dd.bins.stock <- lmer(lam.no.fish ~ prop.bin + (1+prop.bin|Stock),data=dd.dat)
-# So is an intercept model of any real use?
-# mod.dd.bins.stock <- lmer(log(lam.no.fish) ~ prop.bin + (1+prop.bin|Stock.short),data=dd.dat)
-# # A non-random effect model does work with the interaction... I'd much rather lmer....
-# #mod.dd.bins.stock <- lm(lam.no.fish ~ prop.bin*Stock,data=dd.dat)
-# summary(mod.dd.bins.stock)
-# #Residuals, nah, still suck, just some crazy outliers...
-# plot(mod.dd.bins.stock)
-# # Normality = terrible...
-# qqnorm(residuals(mod.dd.bins.stock))
-# qqline(residuals(mod.dd.bins.stock))
-# # So we can predict this ANOVA thing...
-# pred.dd.stock.bins <- expand.grid(prop.bin = unique(dd.dat$prop.bin),
-#                                          #Species=unique(dd.dat$Species),
-#                                          Stock.short=unique(dd.dat$Stock.short))
-# tmp <- predict(mod.dd.bins.stock, pred.dd.stock.bins, type = 'response', se.fit = TRUE) 
-# pred.dd.stock.bins$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.stock.bins$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.stock.bins$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Now to do fun things I need the meta data on the pred dataframe
-# pred.dd.stock.bins <- left_join(pred.dd.stock.bins,meta.sub,by="Stock.short")
-# # Now a problem here is that this includes estimates for bins in which we don't have data.
-# # So we do want to get rid of those
-# real.bins <- unique(paste(dd.dat$Stock.short,"_",dd.dat$prop.bin))
-# # All the bins in the predict object with same names same name...
-# pred.dd.stock.bins$bin.combos <- paste(pred.dd.stock.bins$Stock.short,"_",pred.dd.stock.bins$prop.bin)
-# # Now toss all the predicted bins without data.
-# pred.dd.stock.bins <- pred.dd.stock.bins |> collapse::fsubset(bin.combos %in% real.bins)
-# 
-# # By region
-# cols.1 <- rep(c("black","blue","orange",'firebrick2','lightgreen'),6)
-# #col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
-# pty.1 <- c(rep(0,5),rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5))
-# ggplot(pred.dd.stock.bins,aes(x=prop.bin,y=lam.no.fish,group=Stock.short,color=G.Species)) + 
-#                                 geom_point(aes(shape=G.Species),size=2) + geom_line()  + xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 facet_wrap(~Area.long)  +
-#                                 scale_shape_manual(values=pty.1) +
-#                                 scale_color_manual(values = cols.1) + 
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-# 
-# # By Species
-# ggplot(pred.dd.stock.bins,aes(x=prop.bin,y=lam.no.fish,group=Stock.short,color=Area.long)) + 
-#                                 geom_point(aes(shape=Area.long)) + geom_line()  + xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 facet_wrap(~Order)  +
-#                                 scale_shape_manual(values=pty.1) +
-#                                 scale_color_manual(values = cols.1) + 
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-# 
-# # No fish vs fish lambda, note that DD is weaker when we account for fishing, that seems a fun result to talk about!
-# 
-# mod.dd.overall.gam.nf <- lm(log(lam.no.fish) ~ (prop.abund),data=dd.dat)
-# mod.dd.overall.gam.fish <- lm(log(lam.fish) ~ (prop.abund),data=dd.dat)
-# 
-# 
-# pred.dd.overall.bins.nf <- data.frame(prop.abund = seq(0,1,length.out=500),group = "F = 0")
-# pred.dd.overall.bins.fish <- data.frame(prop.abund = seq(0,1,length.out=500),group = "F > 0")
-# tmp <- predict(mod.dd.overall.gam.nf, pred.dd.overall.bins, type = 'response', se.fit = TRUE) 
-# tmp.fish <- predict(mod.dd.overall.gam.fish, pred.dd.overall.bins, type = 'response', se.fit = TRUE) 
-# pred.dd.overall.bins.nf$lam   <- exp(tmp$fit)
-# pred.dd.overall.bins.nf$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.overall.bins.nf$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# 
-# pred.dd.overall.bins.fish$lam   <- exp(tmp.fish$fit)
-# pred.dd.overall.bins.fish$lower <- exp(tmp.fish$fit - 1.96 * tmp.fish$se.fit)
-# pred.dd.overall.bins.fish$upper <- exp(tmp.fish$fit + 1.96 * tmp.fish$se.fit)
-# 
-# pred.dd.overall <- rbind(pred.dd.overall.bins.fish,pred.dd.overall.bins.nf)
-# 
-# ggplot(pred.dd.overall,aes(y=lam,x=prop.abund,group=group,color=group)) + 
-#                                                   geom_line(linewidth=2) + 
-#                                                   geom_ribbon(aes(ymin=lower,ymax=upper),alpha=0.2) + 
-#                                                   geom_hline(yintercept=1,linetype='dashed') + 
-#                                                   xlab("Proportion of Maximum Abundance") + ylab("Lambda")
-# 
-# # OK, so if we compare the 40-60 bin with the 80-100 bin we should see the lambda's in the 40-60 bin are higher...
-# 
-# res.40.60 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("40-60%"))
-# names(res.40.60)[names(res.40.60) == 'lam.no.fish'] <- "lam.40.60"
-# res.80.100 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("80-100%"))
-# names(res.80.100)[names(res.80.100) == 'lam.no.fish'] <- "lam.80.100"
-# 
-# tst <- left_join(res.40.60,res.80.100, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.40.60 - tst$lam.80.100
-# 
-# hist(tst$diff)
-# 
-# res.lt.10 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("< 10%"))
-# names(res.lt.10)[names(res.lt.10) == 'lam.no.fish'] <- "lam.lt.10"
-# 
-# tst <- left_join(res.40.60,res.lt.10, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.lt.10 - tst$lam.40.60
-# 
-# hist(tst$diff)
-# 
-# res.10.20 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("10-20%"))
-# names(res.10.20)[names(res.10.20) == 'lam.no.fish'] <- "lam.10.20"
-# 
-# tst <- left_join(res.40.60,res.10.20, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.10.20 - tst$lam.40.60
-# 
-# hist(tst$diff)
-# 
-# 
-# res.20.30 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("20-30%"))
-# names(res.20.30)[names(res.20.30) == 'lam.no.fish'] <- "lam.20.30"
-# 
-# tst <- left_join(res.40.60,res.20.30, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.20.30 - tst$lam.40.60
-# 
-# hist(tst$diff)
-# 
-# res.30.40 <- pred.dd.stock.bins |> collapse::fsubset(prop.bin %in% c("30-40%"))
-# names(res.30.40)[names(res.30.40) == 'lam.no.fish'] <- "lam.30.40"
-# 
-# tst <- left_join(res.40.60,res.30.40, by = names(res.40.60)[c(2,6:26)])
-# tst$diff <- tst$lam.30.40 - tst$lam.40.60
-# 
-# hist(tst$diff)
-
-# 
-# 
-# dd.dat.no.bigs <- dd.dat |> collapse::fsubset(lam.no.fish < 2)
-# dd.dat.six.no.bigs <- dd.dat.six |> collapse::fsubset(lam.no.fish < 2)
-# just.bigs <- dd.dat  |> collapse::fsubset(lam.no.fish > 2) 
-# sum(table(just.bigs$Stock.short)) # 48 of 68 are Haddock or cod. 13 of remaining 20 are small low trophic species
-# 
-# dd.dat$lam.ratio <- dd.dat$lam.org.no.fish/dd.dat$lam.no.fish
-# dd.dat$lam.ratio.z <- dd.dat$lam.org.fish/dd.dat$lam.fish
-# So the original lambda tended to be somewhere between 7 and 14% higher, depending on me(di)an choice.
-# Could be way off in some years for a few species (Haddock, Cod, Sand lance, horse makerel, pilchard(sardine)... interesting... )
-# summary(dd.dat$lam.ratio)
-# summary(dd.dat$lam.ratio.z)
-# ggplot(dd.dat,aes(y=lam.ratio,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
-# ggplot(dd.dat,aes(y=lam.ratio.z,x=Species)) + geom_violin() + scale_y_log10() + geom_hline(yintercept =1) + theme_few(base_size=9)
-
-# Playing around to look at explanations for what we see, looked by LME, low and high stocks, but no smoking guns!
-# low.stocks <- unique(dd.dat$Stock.short[dd.dat$prop.abund <= 0.1])
-# dd.lows <- dd.dat |> collapse::fsubset(Stock.short %in% low.stocks)
-# dd.highs <- dd.dat |> collapse::fsubset(!Stock.short %in% low.stocks)
-# mod.dd.stock.gam.lows <- gam(log(lam.no.fish) ~ s(prop.abund,k=4) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.lows )
-# mod.dd.stock.gam.highs <- gam(log(lam.no.fish) ~ s(prop.abund,k=4) + s(prop.abund,by=as.factor(Stock.short),k=3),data=dd.highs )
-# 
-# pred.dd.stock.gam.tst <- expand.grid(prop.abund = seq(0, 1, length.out = 50),
-#                                          Stock.short = c("Overall",unique(dd.highs$Stock.short)))
-# 
-# tmp <- predict(mod.dd.stock.gam.highs, pred.dd.stock.gam.tst, type = 'response', se.fit = TRUE) 
-# pred.dd.stock.gam.tst$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.stock.gam.tst$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.stock.gam.tst$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# 
-# ggplot(pred.dd.stock.gam.tst |> collapse::fsubset(Stock.short=='Overall'), aes(x=prop.abund,y=lam.no.fish)) + 
-#                                 geom_point(data = hmm,aes(x=prop.abund,y=lam.no.fish),size=2,alpha=0.1) +  
-#                                 geom_line(color='blue',linewidth=2) + 
-#                                 xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-# 
-# 
-# ggplot(pred.dd.stock.gam.tst,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short,shape=Stock.short)) + 
-#                                 geom_line() + 
-#                                 #geom_point(data = thin.pred,size=2) +  
-#                                 xlab("Proportion of maximum abundance") + 
-#                                 scale_y_log10(name = "Lambda",breaks = log_breaks(n=8)) +
-#                                 #facet_wrap(~Area.long)  +
-#                                 #scale_shape_manual(values=pty.gam) +
-#                                 #scale_color_manual(values = cols.gam) + 
-#                                 geom_hline(yintercept = 1,color='grey',linetype = 'dashed')+
-#                                 theme(legend.text=element_text(size=8),
-#                                       legend.spacing.y = unit(-0.1, 'cm'),
-#                                       legend.title = element_blank(),
-#                                       axis.text.x = element_text(size=7)) + 
-#                                  guides(color = guide_legend(ncol=1,byrow=T),
-#                                         shape = guide_legend(ncol=1,byrow=T))
-
-# Is there any density dependence in fishing mortality??
-# dd.dat$mu <- dd.dat$removals/dd.dat$vpa.abund
-# dd.dat$fm <- -log(1-dd.dat$mu)
-# 
-# ggplot(dd.dat , aes(x=prop.abund,y=fm)) + 
-#                                 geom_point() + 
-#                                 geom_smooth(method = 'gam') + 
-#                                 scale_x_continuous(name="Proportion of Maximum Abundance") +
-#                                 scale_y__continuous(name = "Fishing Mortality (instantaneous)")
-# 
-# 
-# qqnorm(log(dd.dat$mu))
-# qqline(log(dd.dat$mu))
-# hist(log(dd.dat$mu))
-# 
-# fm.mod <- lm(log(fm)~prop.abund,data=dd.dat)
-# par(mfrow=c(2,2))
-# plot(fm.mod)
-# par(mfrow=c(1,1))
-
-# windows(11,11)
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
-
-# 
-# r0.ts.plt <- ggplot(pop.dam.6,aes(y=R0.opt,x=cohort,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) + 
-#                             geom_line(size=2)  + geom_point(size=4) +
-#                             scale_y_log10(name = "Lifetime Reproductive Output") +
-#                             facet_wrap(~G.Species) +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
-#                             scale_fill_manual(name = "Stock",values = col.try)+
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
-# r0.ts.plt
-# 
-# save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_6.png",r0.ts.plt,base_width = 30,base_height = 12)
-# 
-# r0.boxplt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
-#                             facet_wrap(~G.Species,scales = 'free')+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none')
-# r0.boxplt
-
-# 
-# windows(11,11)
-# ggplot(pop.dam) + geom_boxplot(aes(y=gen.len.opt,x=Species)) + facet_wrap(~LME,scales='free_x') +
-#                   ylab("Generation Length (years)") + theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# windows(11,11)
-# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
-# lty <- rep(c(rep(1,5),rep(2,5),rep(4,5)),20)
-# 
-# gen.ts.plt <- ggplot(pop.dam.6,aes(y=gen.len.opt,x=cohort,group=Stock.short,color=Stock.short,linetype = Stock.short)) + 
-#                             geom_line(size=2)  + 
-#                             scale_y_log10(name = "Generation Length") +
-#                             facet_wrap(~G.Species) +
-#                             scale_color_manual(name = "Stock",values = col.try) + scale_linetype_manual(name = "Stock",values = lty) +
-#                             guides(colour = guide_legend(ncol = 1))+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
-# gen.ts.plt
-# save_plot("D:/Github/ICM/Figures/tuned/Gen_time_series_6.png",gen.ts.plt,base_width = 20,base_height = 12)
-
-# 
-# ggplot(for.tunes) + geom_jitter(aes(y=lambda,x=Species,group=Stock.short,color=Stock.short)) + 
-#                     scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10)) +
-#                             theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# ggplot(for.tunes) + geom_jitter(aes(y=lambda.vpa.init,x=Species)) + scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))
-# 
-# unique(for.tunes$Species)
-# windows(11,11)
-# 
-# ggplot(for.tunes) + geom_density(aes(lambda,group=Species,color=Species,fill=Species),alpha = 0.2) + scale_x_continuous(breaks = c(0,0.5,1,2,5,10))
-# 
-# 
-# #options(scipen=999)
-# r0.plt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.05,0.1,0.5,1,5,10,50,100),minor_breaks = NULL) + 
-#                             facet_wrap(~Species,scales = 'free')+
-#                             theme(axis.text.x = element_text(angle =45,hjust=1))
-# save_plot("D:/Github/ICM/Figures/tuned/R0_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
-# 
-# 
-# 
-# vickis.cols <- sort(rep(c( "#172582",  "#F8DC91", "#FBB891", "#FB6A01", "#B80000"),3))
-# linetypes <- rep(c(1,2,4),5)
-# 
-# windows(11,11)
-# cod.r0.ts.plt <- ggplot(pop.dam |> collapse::fsubset(Species == 'morhua')) + geom_line(aes(y=R0.opt,x=cohort,group=Area,color=Area,linetype=Area),size=1.5)  + 
-#                             scale_y_log10(name = "Lifetime Reproductive Output", breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
-#                             scale_color_manual(values = vickis.cols) +
-#                             scale_linetype_manual(values = linetypes) +
-#                             theme(legend.key.width  = unit(2, "cm"))
-# cod.r0.ts.plt
-# #save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
-# 
-# 
-# windows(11,11)
-# ggplot(pop.dam |> collapse::fsubset(Species =="morhua")) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
-#                                                         scale_y_log10(name = "Lifetime Reproductive Output",breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) +
-#                                                         theme(axis.text.x = element_text(angle =45,hjust=1))
-# 
-# # Missing catch questions
-# # first did we do much to the Fecundity term to get here
-# quantile(for.tunes$mean.fec/for.tunes$mean.vpa.fec,probs=seq(0.01,1,0.01),na.rm=T)
-# 
-# quantile((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init,probs=seq(0.01,1,0.01),na.rm=T)
-# quantile((for.tunes$mean.nm-for.tunes$mean.vpa.nm)/for.tunes$mean.vpa.nm,probs=seq(0.01,1,0.01),na.rm=T)
-# 
-# for.tunes$excess.catch <- for.tunes$removals-for.tunes$removals.init
-# for.tunes$per.excess.catch <- 100*((for.tunes$removals-for.tunes$removals.init)/for.tunes$removals.init)
-# 
-# windows(11,11)
-# bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Species)) + 
-#                                    ylab("Adjustment to catch (%)") +
-#                                    theme(axis.text.x = element_text(angle=45,hjust = 1))
-#                                    
-# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_species.png",bycatch.plt,base_width = 8,base_height = 8)
-#                                    
-# bycatch.plt.cod <- ggplot(for.tunes |> collapse::fsubset(Species == 'morhua')) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + 
-#                                                                               ylab("Adjustment to catch (%)") +
-#                                                                               theme(axis.text.x = element_text(angle=45,hjust = 1))
-#                                                                               
-# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_cod_stock.png",bycatch.plt.cod,base_width = 8,base_height = 8)
-# 
-# # bycatch.plt <- ggplot(for.tunes) + geom_boxplot(aes(y=per.excess.catch,x=Area)) + facet_wrap(~Species,scales = 'free_x')
-# #                                    ylab("Adjustment to catch (%)") +
-# #                                    theme(axis.text.x = element_text(angle=45,hjust = 1))
-# # bycatch.plt                                   
-#
-
-# Doubling time for the rest of the stocks...
-
-# dub.heatmap.no.6 <- ggplot(dub.time.summary |> collapse::fsubset(!Species %in% six.species), aes(x=year, y=Stock.short, fill= prop)) + 
-#                               xlab("") + ylab("")+                                    
-#                               #facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + 
-#                               scale_x_continuous() +
-#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
-#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
-```
-
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-<!-- Here are the models that we ran but didn't end up using# -->
-
-```{r failed-models}
-
-# A density dependence model, start simple and build...
-# mod.dd.base <- lm(log(lam.no.fish) ~ prop.abund,data=dd.dat)
-# summary(mod.dd.base)
-# 
-# mod.dd.base.fish <- lm(log(lam.fish) ~ prop.abund,data=dd.dat)
-# summary(mod.dd.base.fish)
-# #ggplot(dd.dat, aes(y = lam.no.fish,x=prop.abund)) + geom_point() + geom_smooth(method = 'lm') + scale_y_log10() + geom_hline(yintercept = 1,color='firebrick2',linetype='dashed',linewidth=2)
-# 
-# 
-# # Residuals are nowhere near normal, the fit isn't a disaster but def have the old trumpet shape happening
-# par(mfrow=c(2,2))
-# plot(mod.dd.base)
-# par(mfrow=c(1,1))
-# # This mostly represents the above model...
-# ggplot(dd.dat, aes(y = lam.no.fish,x=prop.abund)) + 
-#                   geom_point() + 
-#                   geom_smooth(method = 'lm') + scale_y_log10() +
-#                   geom_hline(yintercept = 1,color='firebrick2',linetype='dashed',linewidth=2)
-# # What happens with a gam?
-# mod.dd.gam.base <- gam(log(lam.no.fish) ~ s(prop.abund),data=dd.dat)
-# summary(mod.dd.gam.base)
-# # Still see that the residuals are higher at low values
-# plot(residuals(mod.dd.gam.base) ~ dd.dat$prop.abund)
-# # not great...
-# plot(residuals(mod.dd.gam.base) ~ fitted(mod.dd.gam.base))
-# # What's the fit look like?
-# pred.dd.gam.base <- data.frame(prop.abund = seq(0, 1, length.out = 1000))
-# tmp <- predict(mod.dd.gam.base, dd.gam.base.pred, type = 'response', se.fit = TRUE) 
-# 
-# pred.dd.gam.base$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.gam.base$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.gam.base$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# 
-# # So here's the game fit, I thnk it does do an ok job of showing that no much is happening below maybe 0.3, but then
-# # below 0.15 it starts increasing, suggesting general compensation, but we know the really high values matter here and are
-# # limited to a subset of the stocks, anywho we know the residuals suck, so moving on...
-# ggplot(dd.dat,aes(y=lam.no.fish,x=prop.abund)) + 
-#                   geom_point() + scale_y_log10() +
-#                   geom_ribbon(data=pred.dd.gam.base,aes(ymin=lower,ymax=upper,x=prop.abund),alpha=0.4) +
-#                   geom_line(data = pred.dd.gam.base,aes(y=lam.no.fish, x= prop.abund))
-#     
-# 
-# # What if we did a glm, Gamma with log-link seems a natural thing to try...
-# mod.dd.glm.gamma <- glm(lam.no.fish ~ prop.abund,data=dd.dat,family = Gamma(link='log'))
-# # What's that done...
-# summary(mod.dd.glm.gamma)
-# # Still some pretty gross shit going on here...
-# par(mfrow=c(2,2))
-# plot(mod.dd.glm.gamma)
-# par(mfrow=c(1,1))
-# # Now plot it...
-# pred.dd.glm.base <- data.frame(prop.abund = seq(0, 1, length.out = 1000))
-# tmp <- predict(mod.dd.glm.gamma, dd.gam.base.pred, type = 'response', se.fit = TRUE) 
-# 
-# pred.dd.glm.base$lam.no.fish   <- (tmp$fit)
-# pred.dd.glm.base$lower <- (tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.glm.base$upper <- (tmp$fit + 1.96 * tmp$se.fit)
-# # Pretty similar, though I think on the linear scale we see the 'rate' may be decreasing as we approach 0
-# # But still not a good model given the above
-# ggplot(dd.dat,aes(y=lam.no.fish,x=prop.abund)) + 
-#                   geom_point() + scale_y_log10() +
-#                   geom_ribbon(data=pred.dd.glm.base,aes(ymin=lower,ymax=upper,x=prop.abund),alpha=0.4) +
-#                   geom_line(data = pred.dd.glm.base,aes(y=lam.no.fish, x= prop.abund))
-#     
-# # Now what if we account for species in these and get an estimate for each species. 
-# # I think this should be done as a random effect, we'll start with linear mixed models and see what happens...
-# 
-# mod.dd.species.re <- lmer(log(lam.no.fish) ~ prop.abund + (1| Species),data=dd.dat)
-# # So that seems reasonable...
-# summary(mod.dd.species.re)
-# #Residuals are still pretty cranky
-# plot(mod.dd.species.re)
-# # Normality still a hot mess
-# qqnorm(residuals(mod.dd.species.re))
-# qqline(residuals(mod.dd.species.re))
-# # draw some lines...
-# pred.dd.lmm.species <- expand.grid(prop.abund = seq(0, 1, length.out = 100),Species=unique(dd.dat$Species))
-# tmp <- predict(mod.dd.species.re, pred.dd.lmm.species, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.species$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.lmm.species$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.species$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.species,aes(x=prop.abund,y=lam.no.fish,group=Species,color=Species)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Species, color=Species)) +
-#                                 scale_y_log10()
-# 
-# # We could also allow the slope to vary by species, might get a bit better, but really won't do the trick...
-# mod.dd.species.slope.re <- lmer(log(lam.no.fish) ~ prop.abund + (1+ prop.abund| Species),data=dd.dat)
-# summary(mod.dd.species.slope.re)
-# #Residuals are still pretty cranky
-# plot(mod.dd.species.slope.re)
-# # Normality still a hot mess
-# qqnorm(residuals(mod.dd.species.slope.re))
-# qqline(residuals(mod.dd.species.slope.re))
-# # draw some lines...
-# pred.dd.lmm.species.slope <- expand.grid(prop.abund = seq(0, 1, length.out = 100),Species=unique(dd.dat$Species))
-# tmp <- predict(mod.dd.species.slope.re, pred.dd.lmm.species.slope, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.species.slope$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.lmm.species.slope$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.species.slope$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.species.slope,aes(x=prop.abund,y=lam.no.fish,group=Species,color=Species)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Species, color=Species)) +
-#                                 scale_y_log10()
-# # Curious what species have high slopes.. Dubious and Esmarkii (North Sea sand lance and mackerel)
-# ranef(mod.dd.species.slope.re)
-# 
-# # So so what if we let the slopes vary by stock
-# mod.dd.stock.re <- lmer(log(lam.no.fish) ~ prop.abund +  (1+ prop.abund | Stock.short),data=dd.dat)
-# summary(mod.dd.stock.re)
-# #Residuals are slightly better I think but still really suck
-# plot(mod.dd.stock.re)
-# # Normality = no
-# qqnorm(residuals(mod.dd.stock.re))
-# qqline(residuals(mod.dd.stock.re))
-# # What's it look like?
-# pred.dd.lmm.stock <- expand.grid(prop.abund = seq(0, 1, length.out = 100),
-#                                          #Species=unique(dd.dat$Species),
-#                                          Stock.short=unique(dd.dat$Stock.short))
-# tmp <- predict(mod.dd.stock.re, pred.dd.lmm.stock, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.stock$lam.no.fish   <- exp(tmp$fit)
-# pred.dd.lmm.stock$lower <- exp(tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.stock$upper <- exp(tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.stock,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Stock.short, color=Stock.short)) +
-#                                 scale_y_log10()
-# 
-# # Curious what stocks have high slopes.. Dubious and Esmarkii (North Sea sand lance and mackerel), NS Haddock and Irish Sea Haddock 
-# ranef(mod.dd.stock.re)
-# 
-# 
-# 
-# 
-# # OK, so this all still sucks, wonder if a glmer and gamma would get us anywhere... not really.... 
-# # Tried many variants on the glmer and they all land in the same lousy spot.
-# mod.dd.stock.gamma.re <- glmer(lam.no.fish ~ prop.abund +  (1+ prop.abund | Stock.short),data=dd.dat,family=Gamma(link='log'))
-# # OK...
-# summary(mod.dd.stock.gamma.re)
-# #Residuals, nah, still suck, just some crazy outliers...
-# plot(mod.dd.stock.gamma.re)
-# # Normality = no
-# qqnorm(residuals(mod.dd.stock.gamma.re))
-# qqline(residuals(mod.dd.stock.gamma.re))
-# # And the plot...
-# pred.dd.lmm.stock.gamma <- expand.grid(prop.abund = seq(0, 1, length.out = 100),
-#                                          #Species=unique(dd.dat$Species),
-#                                          Stock.short=unique(dd.dat$Stock.short))
-# tmp <- predict(mod.dd.stock.gamma.re, pred.dd.lmm.stock.gamma, type = 'response', se.fit = TRUE) 
-# pred.dd.lmm.stock.gamma$lam.no.fish   <- (tmp$fit)
-# pred.dd.lmm.stock.gamma$lower <- (tmp$fit - 1.96 * tmp$se.fit)
-# pred.dd.lmm.stock.gamma$upper <- (tmp$fit + 1.96 * tmp$se.fit)
-# # Here are the fits (sans SE cause messy + didn't put the overall relationship on here)
-# ggplot(pred.dd.lmm.stock.gamma,aes(x=prop.abund,y=lam.no.fish,group=Stock.short,color=Stock.short)) + 
-#                                 geom_line()  + 
-#                                 geom_point(data=dd.dat,aes(x=prop.abund,y=lam.no.fish,group=Stock.short, color=Stock.short)) +
-#                                 scale_y_log10()
-# # None of the above really work at all....
-
-```
+---
+title: `r ifelse(fr(), meta$french_title, meta$title)`
+month: `r ifelse(fr(), meta$french_month, meta$month)`
+region: `r ifelse(fr(), meta$french_region, meta$region)`
+csl: `r csl`
+---

### 2024-05-24 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
Absract and Intro
Also have corrected a couple species names

@@
 tab.names <- c("Minimum Abundance",
-               "$\\lambda_{F>0}^{Min}$",
-               "$\\lambda_{F>0}^{40}$",
-               "$\\lambda_{F>0}^{Max}$",
-               "$\\lambda_{F=0}^{Min}$",
-               "$\\lambda_{F=0}^{40}$",
-               "$\\lambda_{F=0}^{Max}$",
+               "$\\lambda_{FM>0}^{Min}$",
+               "$\\lambda_{FM>0}^{40}$",
+               "$\\lambda_{FM>0}^{Max}$",
+               "$\\lambda_{FM=0}^{Min}$",
+               "$\\lambda_{FM=0}^{40}$",
+               "$\\lambda_{FM=0}^{Max}$",
                "Stock","Species")
@@
 tab.names <- c("Minimum Abundance",
-               "$\\lambda_{F>0}^{Min-40}$",
-               "$\\lambda_{F>0}^{Min-Max}$",
-               "$\\lambda_{F>0}^{40-Max}$",
-               "$\\lambda_{F=0}^{Min-40}$",
-               "$\\lambda_{F=0}^{Min-Max}$",
-               "$\\lambda_{F=0}^{40-Max}$",
+               "$\\lambda_{FM>0}^{Min-40}$",
+               "$\\lambda_{FM>0}^{Min-Max}$",
+               "$\\lambda_{FM>0}^{40-Max}$",
+               "$\\lambda_{FM=0}^{Min-40}$",
+               "$\\lambda_{FM=0}^{Min-Max}$",
+               "$\\lambda_{FM=0}^{40-Max}$",
                "Stock","Species")
@@
 # the lambda calcs
+n.stock.dfo <- meta.sub |> collapse::fsubset(Manage.short == "DFO-TRAC") |> nrow()
+n.stock.ices <- meta.sub |> collapse::fsubset(Manage.short == "ICES") |> nrow()
+n.stock.noaa <- meta.sub |> collapse::fsubset(Manage.short %in% c("AFSC","NEFSC")) |> nrow()
+n.age.0 <- meta.sub |> collapse::fsubset(age.min == 0) |> nrow()
+n.age.1 <- meta.sub |> collapse::fsubset(age.min == 1) |> nrow()
+n.age.2.plus <- meta.sub |> collapse::fsubset(age.min >= 2) |> nrow()
+min.year <- min(res.lambda.fin$year)
+max.year <- max(res.lambda.fin$year)
+stock.ts.len <- res.lambda.fin |> collapse::fgroup_by(Stock.short) |> collapse::fsummarise(n.years = length(year))
+mn.ts.len <- round(mean(stock.ts.len$n.years),digits=1)
+min.ts.len <- min(stock.ts.len$n.years)
+max.ts.len <- max(stock.ts.len$n.years)
+num.orders <- length(unique(meta.sub$Order))
+num.gads <- meta.sub |> collapse::fsubset(Order == "Gadiformes") |> nrow()
+num.pleur <- meta.sub |> collapse::fsubset(Order == "Pleuronectiformes") |> nrow()
+num.scorp <- meta.sub |> collapse::fsubset(Order == "Scorpaeniformes ") |> nrow()
+num.clup <- meta.sub |> collapse::fsubset(Order == "Clupeiformes") |> nrow()
+num.scomb <- meta.sub |> collapse::fsubset(Order == "Scombriformes") |> nrow()
+num.perci <- meta.sub |> collapse::fsubset(Order == "Perciformes") |> nrow()
+
+n.st.spec <- meta.sub |> collapse::fgroup_by(Species ) |> collapse::fsummarise(n.stocks = length(Stock)) 
+n.st.spec <- n.st.spec[rev(order(n.st.spec$n.stocks)),]
+num.cod <- meta.sub |> collapse::fsubset(Species == "morhua") |> nrow()
+num.her <- meta.sub |> collapse::fsubset(Species == "harengus") |> nrow()
+num.had <- meta.sub |> collapse::fsubset(Species == "aeglefinus") |> nrow()
+num.sol <- meta.sub |> collapse::fsubset(Species == "solea") |> nrow()
+num.pol <- meta.sub |> collapse::fsubset(Species == "virens") |> nrow()
+num.plat <- meta.sub |> collapse::fsubset(Species == "platessa") |> nrow()
+
+n.six <- meta.sub |> collapse::fsubset(Species %in% six.species) |> nrow()
+
 med.lambda.F0 <- round(median(res.lambda.fin$lam.no.fish),digits=3)
@@
 med.lambda.F <- round(median(res.lambda.fin$lam.fish),digits=3)
-med.r.F <- round(median(log(res.lambda.fin$lam.fish)),digits=3)*100
+med.r.F <- round(median(log(res.lambda.fin$lam.fish)),digits=3)*100 # median in insensitive to doing median(log(lambda)) or log(median(lamdba)), which makes sense... it's the same point...
 mn.lambda.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
-mn.r.F <- round(mean(res.lambda.fin$lam.fish),digits=2)
+# What proportion of the years was lambda < 1 when accounting for fishing
+prop.lam.fish.lt.1 <- 100*round(length(which(res.lambda.fin$lam.fish < 1))/nrow(res.lambda.fin),digits=2)
+# So if I take the log of the mean of the lambda's I get 0.02, if I take the mean of log(lambda) I get -0.02.
+So that's solidly equivocal, but obviously with fishing it is shockingly close to 0 overall
+# but also this does make sense really, if it was way less than 0 then everything collapses...
+mn.r.F <- round(log(mean(res.lambda.fin$lam.fish)),digits=2) 
+# Curious the number of stock in which the mean with fishing is > 1 overall
+lambda.by.stock <- res.lambda.fin |> collapse::fgroup_by(Stock.short) |> collapse::fsummarise(mn.lam.nf = mean(lam.no.fish,na.rm=T),
+                                                                                              mn.lam.fish = mean(lam.fish,na.rm=T),
+                                                                                              med.lam.nf = median(lam.no.fish,na.rm=T),
+                                                                                              med.lam.fish = median(lam.fish,na.rm=T))
+
+num.mn.lambda.fish.lt.1 <- length(which(lambda.by.stock$mn.lam.fish < 1))
+
 # Mean - median...
@@
                                 xlab("") + 
-                                scale_y_log10(name = "Lambda(F=0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
+                                scale_y_log10(name = "Lambda(FM=0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
                                 geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
@@
                                 xlab("") + 
-                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
+                                scale_y_log10(name = "Lambda (FM>0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
                                 geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed',linewidth=1.5)+
@@
                                 xlab("Proportion of maximum abundance") + 
-                                scale_y_log10(name = "Lambda (F=0)",breaks = log_breaks(n=10)) +
+                                scale_y_log10(name = "Lambda (FM=0)",breaks = log_breaks(n=10)) +
                                 geom_ribbon(aes(ymin=lower,ymax=upper,color=G.Species),alpha=0.10,linewidth=0)+
@@
                                 xlab("Proportion of maximum abundance") + 
-                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10)) +
+                                scale_y_log10(name = "Lambda (FM>0)",breaks = log_breaks(n=10)) +
                                 facet_manual(vars(Area.long),design=mat,scales='free_x')+

### 2024-05-24 Drafts/Paper_1/02-intro.Rmd
Methods results done
Absract and Intro
Also have corrected a couple species names

@@
 # INTRODUCTION  {#intro}
+
+Marine fishes were once believed to be extremely resilient to the effects of fishing.
+However, high profile collapses of large fisheries and a subsequent lack of rebuilding (ref, ref) have fundamentally challenged this perception.
+Much of fisheries science throughout the second half of the 20th century was  built around the concept of maximum sustainable yield (MSY), from the outset this concept was controversial and even had an epitaph written almost half a century ago [@larkinEpitaphConceptMaximum1977; @finleyAllFishSea2019].
+However, the ecological concepts underpinning MSY theory and their use has  proven remarkable resilient themselves, in part, because 1) the population dynamics are relatively simple and intuitive, 2) they provide a means of developing tractable mechanistic models, 3) fisheries science built robust methodologies to collect the necessary data for these models, and 4) the management frameworks had been implemented around these models and they provide a very useful tactical decision making platform.
+As such, the concerns around the sustainability of *modern* fisheries science techniques shows little sign of being resolved [@wormRebuildingGlobalFisheries2009; Maybe cite an EAFM and MPA paper?].
+
+The view that marine populations are highly resilient likely originates from the views of some of the first fisheries scientists who suggested that marine fisheries were effectively inexhaustible [e.g., mcintoshFisheriesInterNationalCouncil1919a; @mcintoshFisheriesInternationalCouncil1919].
+These ideas were subsequently married to the theoretical results from some of the earliest population dynamic models [e.g., @verhulstNoticeLoiQue1838] and lead to the development of *modern* fisheries science and MSY theory [@rickerStockRecruitment1954; @schaeferAspectsDynamicsPopulations1954; @bevertonDynamicsExploitedFish1957; ].
+Fundamentally, the belief was that the annual reproductive output and/or juvenile survival rates would increase as abundance declines, otherwise fisheries would collapse (REF), while the old paradigm that fisheries were inexhaustible was no longer supported, the new paradigm indicated that increased harvesting activity would result in the increased *productivity* of a population.
+The subsequent models developed assumed that marine fishes would retain a latent capacity for increase, even if managed in such a way that fisheries removals balance population growth (under equilibrium conditions).
+This means that populations always have the ability to increase in size, and their lifetime reproductive rates in the absence of fishing would be expected to be greater than one (ref, ref).
+At the time many of these fisheries scientists identified the challenges and limitations of their modelling frameworks, including concerns about how applicable these concepts were for species with different life history characteristics, e.g., how different would the fisheries impact be on long lived species with low fecundity and short lived species with high fecundity (CITE SOMETHING).
+
+Life history characteristics are now considered indicative of a species’ compensatory capacity and are increasingly used within data-limited assessment approaches to provide management advice (ref).
+Theory suggests that small fishes, characterized by numerous offspring, rapid growth, early maturity and short lifespans, should have greater compensatory capacity, resilience to environmental variability and consequently, be better able to withstand fishing pressure (Kindsvader et al.
+2016.
+Ref, ref).
+Life histories characterized by longer lifespans and later maturity, or those with lower per-capita reproductive output are considered less resilient.
+Furthermore, closely related species are anticipated to be more similar than distantly related species owing to a shared evolutionary history (Thorson fishlife).
+This has led to the general impression that forage fishes or populations at lower trophic levels are better able to take advantage of favorable environmental conditions and grow more quickly, particularly from low abundance (ref, ref).
+This resilience should manifest as a high latent capacity for population growth in the absence of fishing, as well as substantial variability in realized population growth rates among years.
+
+However, there have been comparatively few empirical studies exploring the demographic variability of harvested populations from a conservation biology or population ecology perspective (FIND A COUPLE THAT DO SOMETHING LIKE WHAT WE ARE DOING).
+Here, our overarching objective was to quantify the variability of the realized demographic parameters of harvested marine teleost populations.
+We relied on a database containing data which enabled the estimation of age specific vital rates for `r n.stocks` populations in the north Atlantic and the northeast Pacific Oceans [@charbonneauAgestructuredmarinefishdatabase2022].
+These data enabled us to reconstruct the life-tables for the populations and utilize metrics commonly used in conservation biology:  (i.e., population growth rates (ref), doubling time (ref), lifetime reproductive success (ref), and generation time (ref).
+Furthermore, we evaluated common perceptions about compensatory dynamics, specifically by comparing the strength and magnitude of variability among species with different life histories as well as among populations of the same species that were separated geographically.
+Our results have implications for sustainable management of exploited marine teleosts and can be used inform the development of rebuilding plans or future status determination for populations that have collapsed.
+
+# Old stuff we can probably shit can, unless we need more material...
 
@@
 
-The underappreciated influence of regional variation in determining recovery potential of exploited teleosts.  - can’t look at a single species and expect it will behave the same way.
+The under appreciated influence of regional variation in determining recovery potential of exploited teleosts.  - can’t look at a single species and expect it will behave the same way.
 

### 2024-05-24 Drafts/Paper_1/03-methods.Rmd
Absract and Intro
Also have corrected a couple species names

--- 2024-04-16 Drafts/Paper_1/03-methods.Rmd
@@
 
-Data from Julie's repo, cite Julie.
-This data repository had sufficient data to run the analysis for 77 stocks from NE Atlantic, NW Atlantic, and the North Pacific, this includes stocks managed by Fisheries and Oceans Canada (DFO), NOAA, and ICES.
-See Appendix X for details on the stocks included.
-These stocks all have age-specific estimates of abundance, biomass, removals, natural mortality, and maturity.
+This analysis used age structured fisheries data obtained from stock assessments for stocks in the Atlantic and Pacific Oceans [@charbonneauAgestructuredmarinefishdatabase2022; @charbonneauEffectsFishingMortality2022].
+This repository had sufficient data to run the analysis for `r n.stocks` stocks from NE Atlantic, NW Atlantic, and the North Pacific, this included stocks managed by International Council for the Exploration of the Sea (ICES; `r n.stock.ices`), NOAA (NOAA;`r n.stock.noaa`), and Fisheries and Oceans Canada (DFO; `r n.stock.dfo` stocks).
+The time series used in this analysis started as early as `r min.year` and the most recent data were from `r max.year`, the average length of the time series for the stocks included in this analysis was `r mn.ts.len` years and the number of years used ranged between `r min.ts.len` and `r max.ts.len` years.
+The stocks used represented `r num.orders` orders, with the most represented orders being the Gadiformes (`r num.gads` stocks), Pleuronectiformes (`r num.pleur` stocks) and Clupeiformes (`r num.clup` stocks).
+The other three orders had relatively few stocks included in the analysis, with `r num.perci` Perciform stocks, `r num.scomb` Scombriform stocks, and just `r num.scorp` Scorpaeniform stock.
+The most common species in this analysis were Atlantic cod (*G.
+morhua*) and the majority of the stocks (`r n.six`) in this analysis were represented by one of six species (*G.
+morhua* (`r num.cod`), *C.
+harengus* (`r num.her`), *M.
+aeglefinus* (`r num.had`),  *P.
+virens* (`r num.pol`), *S.
+solea* (`r num.sol`), and *P.
+platessa* (`r num.plat`)).
 
-## Incidental Catch Model (ICM)
-## Reconstrutive Life-Table Analysis (REC)
-## Life Table Reconstruction (LITAR)
+These data included age-specific estimates of abundance, weight, biomass, maturity, natural mortality, and fishery removals (Table \@ref(tab:tab-meta)), these data were all required to calculate survival-at-age and fecundity-at-age and to estimate the annual productivity of these stocks.
+For the age structured analysis, the last age class was considered the 'terminal' age in the analysis, thus we implicitly assumed there was no contribution to productivity from older aged individuals.
+In addition, for the majority of the stocks the first age class was age 1 (`r n.age.1` stocks) while another `r n.age.2.plus` of the stocks have a first age of 2 or greater.
+The young age classes not included for these stocks (e.g.
+Age 0) consisted of immature individuals that do not contribute to the productivity of the stock; however it has been noted that the exclusion of immature age classes in these types of analyses may lead to a slight overestimate of productivity [@pardoMaximumIntrinsicRate2016].
 
-## Discrete Time Age Structured Life Tables
+## Life Table Reconstruction
 
-The discrete time Euler-Lotka was first proposed by Euler in 1760 (subsequently published by @moserGesetzeLebensdauer1839) and is a special case of the continuous time demographic model first proposed by Lotka in 1907 [@lotkaRelationsBirthRates1907; @sharpeProblemAgedistribution1911; @lotkaRelationBirthRate1918]:
+Information on births and deaths can describe a closed population’s demographics and how they are affected by age and time.
+To do so knowledge of the  population’s age specific fecundity and mortality is required, these values can then be used within the Euler-Lotka equation [@lotkaRelationsBirthRates1907] to estimate the population growth rate ($\lambda$) in a given year.
+These data could be derived from the data available for the `r n.stocks` stocks used in this analysis.
+
+### Fecundity-at-age
+
+The number of spawners in year $y$ and age class $a$ ($NS_{y,a}$) is the proportion of mature individuals in each age class ($Mat_{y,a}$) multiplied by the number of individuals in each age class
 
 $$
-1 = \sum_{x=\alpha}^{\omega} \lambda^{-x} s_x f_x dx
+NS_{y,a} = Mat_{y,a} N_{y,a}
 $$
-Where $x$ is the age, $\alpha$ is the age at first reproduction, $\omega$ is the maximum age, $\lambda$ is the discrete rate of population growth ($\lambda = e^r$), $s_x$ is the survivorship to age $x$, and $f_x$ is the fecundity of individuals of age $x$.
-The discrete time Euler-Lotka equation can be shown to be the characteristic polynomial of the Leslie Matrix, where $f_0$ is the fecundity of the first age class with mature individuals [@leslieUseMatricesCertain1945,@caswellMatrixPopulationModels2001]:
+Fecundity is required to be the number of offspring produced by each female in each age class.
+Given the uncertainty of both fertilization and egg survival, using the number of eggs at a given length or size is inappropriate.
+However, these data do have the number of recruits produced each year, and this can be combined with the spawning stock biomass to obtain an estimate of the number of recruits produced per kilogram of spawning biomass $RPS_{y}$, this is calculated as
 
 $$
-
-  \begin{bmatrix}
-    f_0  & f_1 & f_2  & f_3    & ...          & f_{\omega-1} \\
-    s_0  & 0   & 0    & 0      & ...          & 0 \\
-    0    & s_1 & 0    & 0      & ...          & 0 \\
-    0    & 0   & s_2  & 0      & ...          & 0 \\
-    0    & 0   & 0    & \ddots & ...          & 0 \\
-    0    & 0   & 0    & ...    & s_{\omega-2} & 0 \\
-  \end{bmatrix}
+RPS_{y} = R_{y} SSB_{tot,(y-ra)} 
 $$
 
-## Life-Table Reconstruction (LITAR)
-
-The data necessary to obtain age specific estimates of fecundity and mortality are publicly available from the database  @charbonneauAgestructuredmarinefishdatabase2022.
-
-The Euler-lotka equation requires the fecundity given as the number of offspring produced by each female in each age class.
-This can be estimated from the available recruitment, age at maturity, and biomass information.
-**Note there is no need to divide by 2 for females because we'd divide the recruits by 2 to get the number of females, and the spawning numbers by 2, which would just cancel out**.
-
-The number of spawners in year $t$ and age class $a$ ($SSN_{t,a}$) is the proportion of mature individuals ($Mat_{t,a}$) multiplied by the Number of individuals
+Where $SSB_{yot,y-ra}$ is the total spawning stock biomass in year $y$.
+$R_{y}$ is the number of individuals in the youngest age class available for a specific stock (hereafter referred to as recruits) offset temporally by the age of the recruits.
+For example, if the age of the recruits ($ra$) is 2 years , we assume that the recruits in 2010 were produced by the spawning stock biomass in 2008 ($SSB_{tot,y-ra}$).
+The number of recruits produced by each age class ($RPA_{y,a}$) can then be calculated by multiplying the spawner biomass in each age class $SSB_{y-ra,a}$ by the number of recruits produced per kilogram of SSB
 
 $$
-SSN_{t,a} = Mat_{t,a} N_{t,a}
+RPA_{y,a} =  SSB_{(y-ra),a} RPS_{y}
+$$
+This method does not account for any changes in reproductive success by age, each kilogram of spawning biomass contributes the same to the total total reproductive output, irrespective of their age.
+Finally, the age-specific fecundity ($f_{y,a}$) is calculated as number of offspring produced by each individual in the population.
+This is offset by one year, as the recruits observed in year $y+1$ enter into the Euler-Lotka formulation in year $y$.
+
+$$
+f_{y,a} =  \frac{RPA_{y+1,a}}{NS_{(y-ra+1),a}}
 $$
 
-# NEED TO SORT OUT THE "NOMENCLATURE" AROUND LINING THESE UP RIGHT!
+### Survivorship-to-age
 
-The number of recruits produced per spawner $RPS_{t}$ is calculated as
+The number of animals surviving to each age depends on age-specific mortality rates.
+Commercially-exploited fishes experience fishing mortality ($FM$) once they grow large enough to become vulnerable to the gear (reference).
+Fishing mortality combines with natural mortality ($NM$) to give total mortality ($Z$) affecting each age class in each year.
+Varying assumptions can be made about natural mortality during stock assessments, where it may be an assumed value for each age (EXAMPLE), allowed to vary over time and by age (EXAMPLE), or input as a constant across ages (EXAMPLE).
+Due to challenges with separability in typical stock assessment models, natural mortality is often assumed for each age class, in some assessments it varies by age and over time, in other assessments it does not.
+Irrespective of this, the stock assessment used in this analysis all provide an estimate of natural mortality by age and year, this value is typically an instantaneous rate and is converted to a proportional natural mortality for the Euler-Lotka model.
+
+The data also contained the number of fish harvested by the fishery each year and for each age.
+These can be divided by the assessed numbers at age to get an estimate of fishing mortality in each year for each age.
 
 $$
-RPS_{t+ra} = R_{t+ra} SSB_{t} 
+FM_{y,a} =  \frac{Catch_{y,a}}{N_{y,a}}
+$$
+Together, fishing mortality ($FM_{y,a}$) and natural mortality ($NM_{y,a}$) provide a total mortality estimate ($Z_{y,a}$) for each age in each year
+
+$$
+Z_{y,a} =  FM_{y,a} + NM_{y,a}
+$$
+Survival-at-age is simply
+
+$$
+l_{y,a} = 1= Z_{y,a}
+$$
+The Euler-Lotka equation requires suvivorship-to-age, which is the cumulative survival to age $a$.
+The survival of individuals to the first available age class ($s_{y,1}$) was assumed to be 1 [this may lead to a slight overestimate of $\lambda$; @pardoMaximumIntrinsicRate2016], for the remainder of the age classes it was calculated as
+
+$$
+s_{y,a} =  s_{y,(a-1)} \times l_{y,(a-1)}
+$$
+### Euler-Lotka
+
+The discrete time Euler-Lotka  equation was first proposed by Euler in 1760 (subsequently published by @moserGesetzeLebensdauer1839) and is a special case of the continuous time demographic model first proposed by Lotka in 1907 [@lotkaRelationsBirthRates1907; @sharpeProblemAgedistribution1911; @lotkaRelationBirthRate1918]:
+
+$$
+1 = \sum_{a=\alpha}^{\omega} \lambda_y^{-a} s_{y,a} f_{y,a} dx
 $$
 
-Where $SSB_{t}$ is the total spawning stock biomass in year $t$ and $R_t$ is the number individuals in the youngest age class (hereafter referred to as recruits).
-The spawner abundance ($SSB$) is offset by the age of the recruits ($ra$), for example, if the recruits are two-year olds, we assume that the recruits in 2010 were produced by the spawners in 2008.
-The number of recruits produced by each age class can then be calculated by multiplying the spawner biomass in each age class $S_{t,a}$ by the number of number of recruits produced per kilogram of SSB
+Where $a$ is the age, $\alpha$ is the age at first reproduction, $\omega$ is the maximum age, $\lambda$ is the discrete rate of population growth ($\lambda = e^r$), $s_a$ is the survivorship to age $a$, and $f_a$ is the fecundity of individuals of age $a$.
+This equation is solved for each year ($y$) in which the data are available.
+Note that the discrete time Euler-Lotka equation can be shown to be the characteristic polynomial of the Leslie Matrix, where $f_0$ is the fecundity of the first age class with mature individuals [@leslieUseMatricesCertain1945, @caswellMatrixPopulationModels2001].
+Survivorship-at-age and fecundity-at-age were calcualted using the available stock assessment data, which enabled $\lambda$ to be estimated; note that this assumed that each stock represented a discrete population with individual dynamics.
 
-$$
-RPA_{(t+ra),a} =  SSB_{t,a} RPS_{(t+ra),a}
-$$
-This method assumes that there is no effect of age on reproductive success (i.e., each kilogram of spawning biomass contributes the same to the total total reproductive output, irrespective of their age).
-Finally, the fecundity is calculated as number of offspring produced by each individual in the population
-
-$$
-Fec_{t,a} =  RPA_{t,a} / SSN_{t,a}
-$$
-
-Due to challenges with separability in typical stock assessment models, natural mortality is often assumed for each age class, in some assessments it varies by age and over time, in other assessments it does not.
-Irrespective of this, the stock assessment used in this analysis all provide an estimate of natural mortality by age and year, this value is typically an instantaneous rate and is convert to a proportional natural mortality for the Euler-Lotka model.
-
-The data also contains the number of fish harvested by the fishery each year and for each age.
-This can be combined with the assessed numbers at age to get an estimate of fishing mortality in each year for each age.
-
-$$
-FM_{t,a} =  Catch_{t,a} / N_{t,a}
-$$
-This is combined with the natural mortality to get a total mortality estimate ($Z_{t,a}$) for each age in each year
-
-$$
-Z_{t,a} =  FM_{t,a} + NM_{t,a}
-$$
+### Population Growth Rates $\lambda$
 
@@
 $$
-N_{t+1} = \lambda N_{t}
+N_{y+1} = \lambda_{y} N_{y}
 $$
-The result of this was compared to the abundance estimate from the stock assessment for the upcoming year ($N_{t+1}$).
-Where necessary, the fecundity and natural mortality estimates were adjusted until the $\lambda$ estimate from the Euler-Lotka equation resulted in an abundance time-series estimate ($N_{t+1}$) that was less than 5% different from the abundance estimates from the stock assessment (AVERAGE DIFFERNCE WAS 0.XX%).
-In this way the $\lambda$, fecundity, and natural mortality estimates are obtained for each year in which data are available.
 
-WONDER IF I HAVE THE "AVERAGE" DIFFERENCE of NM and FECUNDITY FROM THE ORIGINAL VALUES FROM THE ABOVE or is that opening up pandora's box.
+The Euler-Lotka model was fit using an iterative minimization process, where predicted abundance in the following year was compared to the abundance estimate from the stock assessment for the corresponding year ($N_{y+1}$).
+Where necessary, the annual age-specific fecundity and natural mortality estimates were adjusted until the $\lambda$ estimate from the Euler-Lotka equation resulted in an abundance time-series estimate ($N_{y+1}$) that was within 5% of the abundance estimates from the stock assessment (median difference was `r med.per.diff`).
+This tolerance ensured that our analyses reflected the same understanding of stock productivity, natural mortality and fecundity as in the current assessments; effectively this methodology treats the abundance estimates from the stock assessments as the 'truth'.
+The minimization procedure resulted in the final estimates of $\lambda$ being approximately `r med.lam.per.diff` smaller than the initial estimates.
+
+The life table reconstruction resulted in stock-specific $\lambda$, fecundity, and natural mortality estimates for each year in which data were available accounting for the age structure and life history characteristics of each stock.
+In other words, we estimated the realized population growth rate using the changes in the population size of the stocks from year to year (realized population growth rates), based on the amount of mortality experienced and annual reproductive success.
+The realized $\lambda$ included fishing mortality  ($\lambda_{FM>0}$), although this method enabled the theoretical population growth rate excluding fishing mortality ($\lambda_{FM=0}$) to be calculated directly from the annual the natural mortality and fecundity estimates.
 
@@
 -->
+
+## Density Dependence
+
+Life table analyses make no assumptions about population regulation and thus do not incorporate a density-dependent relationship between spawners and recruits (Reference?).
+However, the data could be explored for evidence of density-dependence by modelling each stock's estimated annual population growth rate against the relative population size (proportion of maximum abundance) that year.
+This was done twice, once using  ($\lambda_{FM=0}$) and once using ($\lambda_{FM>0}$).
+Negative density dependence is observed when $\lambda$ increases as abundance declines, positive density dependence occurs when $\lambda$ declines with increasing abundance, while density independence is observed when $\lambda$ is not impacted by changes in abundance.
+
+Generalized Additive Mixed Models were used to allow for some non-linearity in the relationships (CITE MCGV and WOOD), the overall effect and the effect for each stock was modelled as
+
+\begin{align}
+\lambda_{i,j} \sim N(0,\sigma^2_{i,j}) \\
+E(\lambda_{i,j}) = \mu_{i,j} \\
+log(\mu_{i,j}) =  Prop_{i} + Stock_{j}  \times Prop_{i} \\
+Stocks_{i,j} \sim N(0,\sigma^2_{Stocks})
+\end{align}
+
+The interaction was modeled using the *fs* basis using the mgcv package in R, this treats the smooth curves as random effects and is used when a factor has a large number of levels (CITE!).
+Various alternative modelling methods were explored (various model formulations, alternative error distributions, etc.) but all models had similar challenges overcoming either the underlying non-normality or the heteroskedasticity of the data.
+As such, the uncertainty surrounding the model output should be treated with caution, while we discuss the general trends this model provides we attempted to avoid discussion of the statistical significance of the trends.
+
+## Recovery Potential
+
+There are numerous demographic parameters that can be derived from the outputs of the life table reconstruction.
+Here we focus on three that are strongly linked to recovery potential: doubling time, lifetime reproductive success, and generation time.
+The doubling time estimates were performing using a simulation technique based on the fecundity and natural mortality estimates used to calcualte $\lambda$.
+Lifetime reproductive success describes the average number of spawners produced by one female spawner throughout her lifetime.
+A value greater than 1 indicates that the average female has produced sufficient offspring over their lifetime to replace themselves.
+Generation time here is calculated for each cohort and is the mean age of spawners that produced recruits.
+
+### Doubling Time
+
+The annual fecundity and natural mortality values varied considerably for each stock.
+To account for this variability when evaluating recovery potential, we used a simulated population projection.
+For `r n.dt.sims` simulations, we took a random sample of the annual values for fecundity and natural mortality, used the life table reconstruction to estimate $\lambda$, and calculated abundance in the following year.
+Abundance of each stock was projected over `n.sim.years` years, and the percentage of the simulations in which the population size had doubled was recorded each year.
+For simplicity, we did not incorporate density-dependent effects (e.g., potential population decline as abundance exceeds carrying capacity) or any correlation (either temporally or between fecundity and natural mortality).
+Once a population had doubled, it was considered to have remained at that abundance or greater for the remainder of the projection.
+
+### Lifetime Reproductive Success
+
+Lifetime reproductive success ($R_0$)  was calculated for each cohort in which fecundity and natural mortality were available for complete cohorts (i.e., cohorts in which all available age classes are represented).
+It was calculated by using only natural mortality component (FM=0) and with the combined effect of natural mortality and fishing mortality ($FM>0$), respectively.
+This provided an understanding of the reproductive potential from observed stock characteristics alone, and how it changed with fishing pressure.
+This was calculated for each cohort as:
+
+$$
+R_0 = \sum_{x=\alpha}^{\omega} s_x f_x
+$$
+This formulation ignores any contribution from a plus group, by assuming that the last observed age in the data represents the longevity of the cohort.
+This simplifying assumption will cause a slight underestimation in the means these values, given that the oldest sampled age class is typically younger than the theoretical longevity of the species based on growth (REFERENCE).
+
+*Here we are treating the plus group as effectively 'terminal', i.e., it assumes that after the last age class the individuals make no contribution, which means these values are probably a bit low, but at this age they really aren't making much of a contribution on average*.
+
+### Generation Time
+
+The generation time was defined as the mean age of the spawners that produced the observed recruits in a cohort ($T_G$).
+A value was calculated for each cohort in which fecundity and natural mortality were available for the complete cohort (i.e., cohorts in which all available age classes are represented).
+As with lifetime reproductive success it was calculated in two ways, using only the natural mortality component ($FM=0$) and using combined effect of natural mortality and fishing mortality ($FM>0$).
+
+$$
+T_G = \frac{\sum_{x=\alpha}^{\omega} x s_x f_x}{\sum_{x=\alpha}^{\omega}  s_x f_x}
+$$

### 2024-05-24 Drafts/Paper_1/04-results.Rmd
Absract and Intro
Also have corrected a couple species names

# Results {#reses-peses}

<!-- Throughout the results we will focus primarily the six most commonly found species in the analysis (*Gadus morhua, Melogrammus aeglefinus, Clupie harengus, Plueronecties platessa, Polluck virens* and *Solea Solea*).  The complete results for all of the populations included in the analysis can be found in the Supplemental material. -->

## Population growth rates ($\lambda$)

The overall median population growth rate when excluding the effects of fishing ($\lambda_{FM=0}$) was `r med.lambda.F0`, indicating that there was a latent potential for population growth for these populations of approximately `r med.r.F0`%. When the effect of fishing was accounted for, the median population growth rate ($\lambda_{FM>0}$) declined to `r med.lambda.F`, which suggested that the populations in this analysis may have been over-fished by approximately `r -med.r.F`% annually. Indeed, $\lambda_{FM>0}$ was below one `r prop.lam.fish.lt.1`% of the time. However, for many of the populations included in this analysis large recruitment events resulted in large estimates of $\lambda_{FM>0}$, in some years, this led to a skewed distribution of the $\lambda$ estimates, with these large events being an integral component of the populations population dynamics (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-bx-other-fig)). The mean $\lambda_{FM>0}$ for the populations in this analysis was `r mn.lambda.F` which would suggest there remains scope for population growth even after fishing for most populations, although the mean $\lambda_{FM>0}$ was less than one for `r num.mn.lambda.fish.lt.1` of the `r n.stocks` populations. Finally, the mean $\lambda_{FM>0}$ was lower than the median for just `r n.stocks-n.mn.higher.med.fish` of the `r n.stocks` in this analysis. The majority of these populations (`r n.nw.ice`) were in the central or NW Atlantic, and this included `r n.cod.low.mn`  of the `r n.cod` Atlantic cod (*G. morhua*) populations in this analysis.

There were regional and species specific trends in both $\lambda_{FM=0}$ and $\lambda_{FM>0}$. Haddock (*M. aeglefinus*) and Atlantic cod populations had some of highest variability in lambda, both at the population level and between populations (Figure \@ref(fig:lambda-sd-fig)). For these two species, the variability of $\lambda$ within a population declined as you moved from the Eastern Atlantic to the Western Atlantic (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig))). The pattern was more pronounced for Atlantic cod, with populations in the eastern Atlantic tending to have relatively low within population variability. The two other species with populations found in the NW and NE Atlantic (*C.harengus* and *P. virens*) the variability of $\lambda$ between the populations was much lower than for Haddock and Atlantic cod and there were no clear differences between regions for these two species (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig))). This was largely due to the within population $\lambda$ variability being lower than the within population variability of Haddock and Atlantic cod populations in the NE Atlantic (Figure \@ref(fig:lambda-bx-6-fig)). Two other populations (*A. tobianus* and *T. esmarkii*) in the North Sea had highly variably $\lambda's$, though notably they were less variable than the Haddock and Atlantic cod $\lambda's$ in this area (Figure \@ref(fig:lambda-bx-other-fig)). For the remainder of other populations in this analysis, years in which the value of $\lambda_{FM=0}$ exceeded 1.5 were more rare. Exceptions to this included *M. merlangus* in the Celtic Sea, *P. dentatus* and *S. Chrysops* in the NW Atlantic, and the Gulf of Alaska *G. chalcogrammus* population in the Pacific Ocean (Figure \@ref(fig:lambda-bx-other-fig)).

## Density Dependence

Overall, the evidence suggested that negative density dependence was common as both $\lambda_{FM=0}$ and $\lambda_{FM>0}$ increased as abundance declined (Figure \@ref(fig:dd-overall-plt)). The strength of density dependence appeared to be more pronounced at low and high abundance levels (i.e., changes in abundance had larger impacts on $\lambda$ when abundance was below $\approx$ 0.4 or above $\approx$ 0.7). $\lambda_{FM=0}$ only declined below 1 when the populations approached their maximum observed abundance ($\approx$ `r pa.lam.nf.at.one`%), indicating that there was a latent capacity for population growth in these populations.  However, when accounting for fishing mortality, $\lambda_{FM>0}$ was below one until the populations were below approximately `r pa.lam.fish.at.one`% of their maximum abundance. At lower abundances, the rate of increase in $\lambda_{FM>0}$ was higher than $\lambda_{FM=0}$, likely due to reductions in fishing mortality at low abundance, but overall $\lambda_{FM>0}$ was lower than $\lambda_{FM=0}$, suggesting that some fishing mortality was common even at very low abundance (Figure \@ref(fig:dd-overall-plt)).

Generally, there was an increase in the variability of the $\lambda$ estimates as abundance declines, largely driven by an increase in the magnitude of the maximum value of $\lambda$ and a small increase in the frequency of low $\lambda$ values (Figure \@ref(fig:dd-overall-plt)). For example, values of $\lambda_{FM>0}$ > `r pa.lam.fish.low.bigs` were not observed at abundances > `100*pa.big.threshold`% of the maximum (similar trends were observed for $\lambda_{FM=0}$, with only one point being above `r pa.lam.nf.low.bigs` when the abundance was > `r 100*pa.big.threshold`% of the maximum). Similarly, the percentage of $\lambda_{FM>0}$ values below `r lam.low.threshold` was `r 100*prop.low.high.abund`% when the proportion of the abundance was >= 0.3, but this increased to `r 100*prop.low.low.abund`% of the data when the proportion of the abundance was below 0.3.

However, these general patterns were highly variable between populations. All of the populations included in this analysis had $\lambda_{FM=0}$ estimates > 1 at their lowest observed abundances (Table \@ref(tab:tab-lambdas) and Figure \@ref(fig:dd-nf-stock-plt)). Populations in the Northwest Atlantic (particularly Atlantic cod) and Alaska had some of the lowest $\lambda_{FM=0}$ estimates at low abundance, while several populations in the North Sea had among the highest $\lambda_{FM=0}$ estimates at low abundance (Table \@ref(tab:tab-lambdas)).  Of the `r n.bl.40` populations that had declined below 40% of the maximum abundance, only `r `n.low.40.nf` of the populations had a $\lambda_{FM=0}$ estimates < 1 at 40% of their maximum abundance; when the effects of fishing were included `r `n.low.40.nf` of the populations had $\lambda_{FM>0}$ estimates below 1 (Table \@ref(tab:tab-lambdas)).

For the vast majority of populations the lowest values of both $\lambda_{FM=0}$ (`r n.low.lam.at.max.nf` of `r n.stocks`) and $\lambda_{FM>0}$ (`r n.low.lam.at.max.fish` of `r n.stocks`) were found near the maximum abundance in the time series (Figures \@ref(fig:dd-nf-stock-plt) and \@ref(fig:dd-fish-stock-plt)). Atlantic cod in the Northwest Atlantic comprised `r n.cod.lam.not.at.max.nf` of the `r n.stocks - n.low.lam.at.max.nf` populations in which the lowest $\lambda$ was observed below the maximum abundance, the low $\lambda$ occurred at population abundances that were remarkably similar for these Atlantic cod populations (ranging between `r pa.low.cod.min` and `r pa.low.cod.max`). For two of the `r n.stocks - n.low.lam.at.max.nf` populations, the lowest $\lambda_{FM=0}$ estimates were less than 0.005 smaller than the estimate at the maximum abundance, for the other four populations the decline in $\lambda_{FM=0}$ from the highest abundance observed was somewhat pronounced, ranging from `r low.4.lam.40.nf` to `r low.lam.40.nf` (Tables \@ref(tab:tab-lambdas) and \@ref(tab:tab-lamda-diffs) and Figures \@ref(fig:dd-nf-stock-plt) and \@ref(fig:dd-fish-stock-plt) ).

## Demographic Parameters

The lifetime reproductive output and generation length were estimated for each cohort in which data were available. When excluding fishing mortality, the overall median lifetime reproductive output, (i.e., the number of females produced by one female that survive to reproduce) was `r r0.med` (mean = `r r0.mn`; Figures \@ref(fig:r0-6-plt) and \@ref(fig:r0-other-plt)). When the realized fishing mortality was accounted for, the median reproductive output dropped to `r r0.med.fish` (mean = `r r0.mn.fish`), this again highlighted the importance of large reproductive events for survival of these populations and the latent capacity for population growth (Figures \@ref(fig:r0-6-plt) and \@ref(fig:r0-other-plt)). For populations which were found across the north Atlantic, the lifetime reproductive output when excluding fishing mortality tended to decline as your move west, this again was most evident for the Atlantic cod populations.  While the reproductive potential of cohorts within a population could be highly variable, there were no clear temporal trends in the $R_0$ (Figures \@ref(fig:r0-nf-ts-plt) and \@ref(fig:r0-fish-ts-plt)).

The generation lengths tended to become more similar between populations both intra- and inter-specifically when accounting fishing mortality (Figures \@ref(fig:gl-6-plt) and \@ref(fig:gl-other-plt)). In addition, the generation length of *C. harengus*, generally considered a short lived species, in the Central and NW Atlantic tended to be higher than the generation length of Atlantic cod and haddock, especially for the populations in the NE Atlantic (Figure \@ref(fig:gl-6-plt)). There were no obvious patterns in the temporal trends in the generation length (Figures \@ref(fig:gl-nf-ts-plt) and \@ref(fig:gl-fish-ts-plt)).

## Recovery Potential

The recovery potential in the absence of fishing was relatively high for the majority of species (Figure \@ref(fig:dub-time-map)). Of the `r n.stocks` populations in this analysis, `r n.dub.10` had a high recovery potential (we define 'high' as at least `r 100*dub.p.high`% of the simulations having experienced a doubling in size) within 10 years, by year 20 this had increased to `r n.dub.20` populations (Figure \@ref(fig:dub-ts)).

The populations in which recovery potential was low (we define low as < `r 100*dub.p.low`% of the simulations experiencing a doubling in size) exhibited clear regional trends. Of the `r n.not.dub.20` populations in this analysis in which the recovery potential was low after 20 years, `r n.alaska.slow` of the populations were in Alaska (`r n.alaska` populations in total), and `r n.nwa.slow` populations in NAFO Regions 2-4 in the NW Atlantic (`r n.nafo.24` populations were in NAFO Regions 2-4). This contrasts to only `r n.nea.slow` of the `r n.nea` populations in the NE Atlantic with a low recovery potential within 20 years in the absence of fishing (Figure \@ref(fig:dub-time-map)).

The recovery potential was influenced both by $\lambda_{FM=0}$ and the variability in $\lambda_{FM=0}$. Populations with a median $\lambda_{FM=0} < 1$  had moderate (defined as populations in which 50-75% of the simulations doubled within 20 years) to high (> 75% doubled in size within 20 years) recovery potential whenever the standard deviation in $\lambda$ was greater than approximately 0.4 (Figure \@ref(fig:dub-vs-sd)). Populations with a median $\lambda_{FM=0}$ near 1 and with low variability were the populations in which the recovery potential tended to be categorized as low (< 50% of the simulations doubled within 20 years).

### 2024-05-24 Drafts/Paper_1/05-discussion.Rmd
Absract and Intro
Also have corrected a couple species names

@@
 Probably something worth citing in here @thorsonPredictingRecruitmentDensity2020
+
+While alternative frameworks have been suggested and are being implemented globally, (e.g., Ecosystem Based management) the uptake of these methods has been relatively slow due to a lack of mechanistic understanding, a lack of data, and the more complicated nature of the science advice alternative methods provide.

### 2024-05-24 Drafts/Paper_1/index.Rmd
Absract and Intro
Also have corrected a couple species names

@@
 abstract: |
-  Here is the abstract text.
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-  Start new paragraphs after a blank line and with 2 spaces indent.
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+  Marine fishes were once believed to be extremely resilient to the effects of fishing, but this view has changed over time, due in part to the collapse of large fisheries and a lack of rebuilding of some populations after these collapses.
+This has lead to questions about the underlying assumptions used in the management of these populations and the impact of environmental factors on the population dynamics.
+Despite a vast amount of research exploring these challenges, there have been few studies exploring the underlying demographic variability of harvested marine fishes using conservation biology and population ecology perspectives.
+Here we take the available data for 77 stocks that are assessed in the north Atlantic and the northeast Pacific Oceans and reconstruct their demographics using life-tables.
+This life-table reconstruction enables us to explore the variability of the demographics of these populations using metrics commonly used in conservation biology (i.e., population growth rates, doubling time, lifetime reproductive success, and generation time).
+In general, these populations have a latent capacity for population growth (median lambda = 1.1) when the effect of fishing was excluded, indeed even when the effect of fishing were accounted for the population mean population growth rate 1.02 overall, although a large minority (37) of the stocks did have a mean population growth rate less than 1 when accounting for fishing mortality.
+Relatively infrequent, large successful reproductive events resulted in years with exceptional population growth rates, these events were critical for the long term sustainability for many of these populations given the population growth rates when accounting for fishing were less than one 57% of the time.
+The population growth rate tended to increase as population abundance declined, this negative density dependence was stronger near the maximum and minimum abundances.
+The trend at low abundance was largely driven by an increase in the frequency of high values of lambda at low abundance.
+These general patterns are highly variable between populations and regionally, the most notable differences are the majority of the Atlantic cod populations in the NW Atlantic, these populations had few large recruitment events and the evidence for positive density dependence (i.e., Allee effects or depensation) is relatively strong.
+The recovery potential of the majority of the populations in this analysis was relatively high, with 60 of the populations able to double in size within 20 years in the absence of fishing, populations with a low recovery potential were constrained to stocks with both a low median population growth rate and low variability in the population growth rate.
+The majority of stocks have a latent population growth capacity in the absence of fishing, however, there are regional and population specific effects and several populations in this analysis have shown little capacity for population growth even in the absence of fishing.
+Knowledge of the observed underlying demographic parameters for a population can be used to help sustainably manage the population and can be used to inform the development of rebuilding plans and the species status for populations that have collapsed.
 
@@
 # If we already have the results don't re-run the models or load data we don't need.
+# Note that running the models takes like 4 days to finish!!
 load.results <- T

### 2024-05-28 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
Full draft!

@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 19,base_height = 15)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"),new.lam.plt.others,base_width = 19,base_height = 15)
 

### 2024-05-28 Drafts/Paper_1/02-intro.Rmd
Full draft!

@@
 The view that marine populations are highly resilient likely originates from the views of some of the first fisheries scientists who suggested that marine fisheries were effectively inexhaustible [e.g., mcintoshFisheriesInterNationalCouncil1919a; @mcintoshFisheriesInternationalCouncil1919].
-These ideas were subsequently married to the theoretical results from some of the earliest population dynamic models [e.g., @verhulstNoticeLoiQue1838] and lead to the development of *modern* fisheries science and MSY theory [@rickerStockRecruitment1954; @schaeferAspectsDynamicsPopulations1954; @bevertonDynamicsExploitedFish1957; ].
+These ideas were subsequently married to the theoretical results from some of the earliest population dynamic models [e.g., @verhulstNoticeLoiQue1838] and led to the development of *modern* fisheries science and MSY theory [@rickerStockRecruitment1954; @schaeferAspectsDynamicsPopulations1954; @bevertonDynamicsExploitedFish1957; ].
 Fundamentally, the belief was that the annual reproductive output and/or juvenile survival rates would increase as abundance declines, otherwise fisheries would collapse (REF), while the old paradigm that fisheries were inexhaustible was no longer supported, the new paradigm indicated that increased harvesting activity would result in the increased *productivity* of a population.
@@
 This means that populations always have the ability to increase in size, and their lifetime reproductive rates in the absence of fishing would be expected to be greater than one (ref, ref).
-At the time many of these fisheries scientists identified the challenges and limitations of their modelling frameworks, including concerns about how applicable these concepts were for species with different life history characteristics, e.g., how different would the fisheries impact be on long lived species with low fecundity and short lived species with high fecundity (CITE SOMETHING).
+At the time, many of these fisheries scientists identified a number of challenges and limitations of their modelling frameworks, these concerns often anticipated many of the criticisms of fisheries science over the last 75 years.
+These early concerns included questions regarding the applicability of these concepts for species with different life history characteristics, e.g., how different would the fisheries impact be on long lived species with low fecundity and short lived species with high fecundity (CITE SOMETHING).
 

### 2024-05-28 Drafts/Paper_1/05-discussion.Rmd
Full draft!

@@
 # DISCUSSION {#disin}
+
+Here we deconstructed the ecological demographics of numerous harvested marine fish populations .
+In general, these populations have latent capacity for growth and, even when accounting for the influence of fishing, these growth rates are very close to 1 in general.
+There is evidence that fisheries stocks are fished in such a way that they will tend to decline until they have declined below 30% of the maximum population size observed, after that most fished populations tend to experience population growth rates above 1.
+Most populations appear to exhibit evidence for negative density dependence, which is in line with general beliefs within fisheries science and population ecology more generally, however there are some populations where the evidence suggests some level of density independence or weak positive density dependence , including most of the *G.
+morhua* populations in NW Atlantic.
+Both variability and median $\lambda_{F=0}$ influence recovery, stocks with a relatively high variability in $\lambda_{F=0}$ had a moderate-high recovery potential even when their median $\lambda_{F=0}$ was below one.
+Effectively recovery of the stocks was likely within 20 years whenever the median $\lambda_{F=0}$ was greater than 1.06 or the standard deviation of lambda was greater than 0.2.
+
+For every population in this analysis the $\lambda_{F=0}$ at the minimum observed abundance was estimated to be greater than one; suggesting all of the populations have the potential for some degree of recovery given enough time when there is no fishing mortality.
+However, there are seven populations in which $\lambda_{F=0}$ at 40% of the maximum abundance is below 1, five of these populations are found in the NW Atlantic, and five of these are in the Gadus genus (*G.
+morhua* (3) and *G.
+chalcogrammus* (2)).
+For both of these Gadus species, there are examples of populations in which the latent capacity for growth is far more robust.
+For example, *G.
+chalcogrammus* is one of the largest fisheries in the world and the vast majority of the landings are from the Eastern Bering Sea population which has a high latent capacity for growth.
+However the $\lambda_{F=0}$ estimates for two neighboring populations in Alaska are much lower, and it is likely that these populations experience much lower fishing pressure because of their low latent capacity for growth.
+In contrast, in the NW Atlantic, several *G.
+morhua* populations supported large distant waters fishery for centuries (citations), however the data used in this analysis indicated the majority of the stocks in the NW Atlantic have minimal recovery potential.
+The maximum abundance used for these populations was likely a small fraction of the historic maximum abundance of these stocks, primarily due to over fishing by the industrial fishery that developed in the latter half of the 20th century (Cite Rose book maybe?, others).
+Here it is likely that the fishery induced changes to the population, which combined with changes in the environment (Cite cold water and seals) has resulted in these populations having little latent capacity for growth or recovery.
+Indeed, it has been suggested that the SGSL cod population will go extinct unless natural mortality declines significantly (Doug’s predator pit stuff); the results of this analysis largely align with these suggestions given the low recovery potential of this stock and it's extremely low latent capacity for growth.
+However, as one moves towards the eastern Atlantic, the low recovery potential of *G.
+morhua* populations was no longer observed, with stocks around mainland Europe all having a high recovery potential.
+As with *G.
+chalcogrammus*, this indicates that regional variability is a factor in the ability of populations to withstand fishing pressure.
+While some Gadus populations have an ability to withstand large fisheries due to their latent capacity for growth, the life-history at a species level is insufficient to predict how a population will respond to fishing.
+Moreover, this analysis is relevant for only the period under study, the recovery potential assumes that the underlying population demographic rates in the future will be similar to those observed in the past.
+However, as is likely the case with the *G.
+morhua* stocks in the NW Atlantic, the response for a population may change over time due to environmental, ecological, and anthropocentric factors (CITE!).
+
+More generally, we observed that populations with high variability in $\lambda_{F=0}$ have a high recovery potential, however, this variability does not necessarily follow on from the expectations of conventional life-history theory (Cite Kingsvader).
+For example, *C.
+harengus* are a small, relatively short lived, low trophic level pelagic species (Cite!), based on life-history theory *C.
+harengus* should exhibit highly variable population growth potential in which they ‘exploit’ opportunities within the environment (CITE).
+However, the variability of $\lambda_{F=0}$ for the *C.
+harengus* populations was much lower than the *G.
+morhua* and *M.
+aeglefinus* populations found throughout the NE Atlantic.
+Other small pelagic populations, such at *A.
+tobianus* and *T.
+esmarkii* do have elevated  $\lambda_{F=0}$ as life-history theory would expect for small low trophic level species.
+However, caution would be advised in suggesting that other populations of these species would have similar population dynamics, especially given these two populations are found in the North Sea, which appears to be an environment in which high variability in $\lambda_{F=0}$ is commonplace.
+In addition, while stocks with a high variability in $\lambda_{F=0}$ do have years with very high population growth, these events happen at irregular intervals, even when populations are at low abundances.
+As such, for populations in which recovery plans and conservation targets are being developed, the developers must account for *both* the magnitude and the frequency of these events.
+Populations do not *always* increase at their maximum intrinsic rate of growth when at low abundance, but they may have the ability to do so occasionally.
+
+The optimization procedure used for the life-table reconstruction herein assumes that both the estimates of abundance and the fishery removals from the stock assessment are correct.
+Given the underlying assessment models estimate biomass and abundance from fishery independent surveys that have undergone multiple years of peer review, we are confident that the underlying trends captured by the assessments provide a reasonable snapshot of the population dynamics of these population.
+However, it is likely that the fisheries removals used in the stock assessments do not capture all the mortality due to fishing, unreported fishing, bycatch and incidental mortality could all result in higher fishery removals than estimated in the assessments (CITE).
+This would result in the estimates of  $\lambda_{F=0}$ being lower than reality; ‘missing’ mortality would have been accounted for by reductions in fecundity and/or an increase in natural mortality.
+The optimization routine resulted in a median decrease in the no-fishing $\lambda_{F=0}$ estimates of approximately 6.8% when compared to the non-optimized estimates; the directionality of this change is consistent with fishing mortality being underestimated.
+Thus, $\lambda_{F=0}$ is likely an underestimate of the latent capacity for growth of these populations, this magnitude of this bias in any year would be dependent on the level of unaccounted for fishing mortality a population experienced.
+
+Here we provide an overview of the population growth and recovery potential of numerous harvested marine fish populations.
+There is a latent capacity for growth for most populations and the majority of the populations appear to have the ability to recover relatively quickly if fishing mortality is reduced to low levels.
+However, there can be significant intra-species variability which may be related to environmental, ecological, and anthropocentric factors.
+This makes it difficult to use species level life-history traits to predict the population dynamics of specific populations.
+The life-table reconstruction enables the underlying demographic rates to be estimated for populations with sufficient age-structured data, this provides an opportunity of understanding the dynamics of these populations using concepts developed in conservation biology and ecology.
+
+## Ignore this, unless something is in here you want to pull into discussion
 

### 2024-07-02 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
Updated Intro with HB edits

@@
 lam.low.threshold <- 0.8
-pa.lam.fish.low.bigs <- max(dd.dat$lam.fish[dd.dat$prop.abund >= pa.big.threshold])
+pa.lam.fish.low.bigs <- round(max(dd.dat$lam.fish[dd.dat$prop.abund >= pa.big.threshold]),digits=2)
 pa.lam.nf.low.bigs <- round(rev(sort(dd.dat$lam.no.fish[dd.dat$prop.abund >= pa.big.threshold]))[2],digits =2)

### 2024-07-02 Drafts/Paper_1/02-intro.Rmd
Updated Intro with HB edits

--- 2024-04-25 Drafts/Paper_1/02-intro.Rmd
@@
 
-Intro – life history paragraph, environmental variation paragraph, management ties paragraph, goals.
+Marine fishes were once believed to be essentially inexhaustible and thus extremely resilient to the effects of fishing [@mcintoshFisheriesInterNationalCouncil1919a].
+However, high profile collapses of large fisheries and a subsequent lack of rebuilding (cite, cite) have fundamentally challenged this perception.
+The assumption of resilience originated from early theoretical population dynamics modeling [e.g., @verhulstNoticeLoiQue1838] that culminated in the development of modern fisheries science, largely built around the concept of maximum sustainable yield [MSY, @rickerStockRecruitment1954; @schaeferAspectsDynamicsPopulations1954; @bevertonDynamicsExploitedFish1957].
+From its inception, MSY was controversial [@finleyAllFishSea2019; @larkinEpitaphConceptMaximum197], yet the theoretical underpinning in equilibrium concepts and the associated idea that annual reproductive output and/or juvenile survival rates increase as abundance declines (implying harvesting activity will increase the per capita productivity of a population) persisted.
+The vast majority of modern assessments incorporate a stock-recruit function (cite, cite) making compensatory dynamics a foundational assumption about the life history of a species.
+Such fisheries assessments implicitly assume that lifetime reproductive rates in the absence of fishing would be expected to be greater than one (Myers cite, cite) and that even heavily-exploited fish populations retain a latent capacity for increase (cite, cite).
+Although MSY and equilibrium concepts are relatively simple and intuitive, and provide a means of developing tractable mechanistic models, questions remain regarding the applicability of these concepts and whether they adequately reflect the reality of the system being modeled [[@wormRebuildingGlobalFisheries2009; cite cite], particularly for species with markedly different life history characteristics (cite, cite).
 
-theoretical expectations related to productivity and life history for various species (e.g. herring vs. Cod) (ties to regional variation in lifetime reproductive rates and doubling time).
+Life history characteristics are now considered indicative of a species’ compensatory capacity (cite, cite) and are increasingly used within data-limited assessment approaches to provide management advice (cite).
+Theory suggests that small fishes, characterized by numerous offspring, rapid growth, early maturity and short lifespans, should have greater compensatory capacity, greater resilience to environmental variability and consequently, be better able to withstand fishing pressure [@kindsvaterTenPrinciplesEvolutionary2016; cite, cite].
+Conversely, life histories characterized by longer lifespans and later maturity, or those with lower per-capita reproductive output are considered less resilient (cite).
+Furthermore, closely related species are anticipated to be more similar than distantly related species owing to a shared evolutionary history (Thorson fishlife), implying less heterogeneity among populations of a single species than among closely-related species.
+There is a general impression that forage fishes or populations at lower trophic levels are better able to take advantage of favorable environmental conditions and grow more quickly, particularly from low abundance (cite, cite).
+This resilience should manifest as a high latent capacity for population growth in the absence of fishing, as well as substantial variability in realized population growth rates among years.
+Dramatic increases in eulecan (FIND OTHER EXAMPLES) following years of particularly low abundance have provided empirical evidence of high compensatory capacity in forage fishes (cites).
+However, it remains unclear if correlated and compounding ecological and environmental processes (e.g.
+climate change effects, predatory prey dynamics) can largely obscure the importance of life history on realized productivity, making evolutionary history and life history characteristics a weak foundation for data-poor assessment in light of our changing oceans.
 
-Evidence for specific species to make use of environmental conditions – boom in recruitment.
-
-How our understanding of productivity is used in a management context – projections, reference points, risk, (ties directly to density dependence figure).  
-Species-environment relationship – is it different from what we expect and how does that influence our capacity for management of exploited fishes.
-
-The underappreciated influence of regional variation in determining recovery potential of exploited teleosts.  - can’t look at a single species and expect it will behave the same way.
-
-Objectives
-  - Quantify the life history variability of exploited marine teleosts
-  - Explore regional and taxonomic correlates of life history variability
-  - Based on the observed life history, quantify the recovery potential of marine teleosts in the absence of fishing
+Stock assessment data from harvested marine telosts provide a unique opportunity to explore demographic variability and realized compensatory responses from a conservation biology or population ecology perspective.
+The long assessment history of these populations means both that their life history characteristics are well-known and that it is possible to quantify realized variability in survival and reproductive output, while accounting for the influence of fisheries.
+We based our analyses on a database containing age specific abundance information for 77 populations in the north Atlantic and the northeast Pacific Oceans [@charbonneauAgestructuredmarinefishdatabase2022].
+By constructing life tables from abundance at age and catch at age data, we calculated common demographic metrics, including  annual population growth rates (cite), doubling time (cite), lifetime reproductive success (cite), and generation time (cite).
+Comparing the strength and magnitude of variability in realized productivity among species with different life histories as well as among populations of the same species yielded unexpected insights.
+Our results have implications for sustainable management of these exploited marine teleosts and could be used inform future management actions for populations that have collapsed.
+More broadly, our results challenged longstanding ideas on the applicability of equilibrium theory, life history theory, and compensatory dynamics to explain expected productivity in fishes.

### 2024-07-02 Drafts/Paper_1/03-methods.Rmd
Updated Intro with HB edits

@@
 $$
+
 ### Euler-Lotka
@@
 Note that the discrete time Euler-Lotka equation can be shown to be the characteristic polynomial of the Leslie Matrix, where $f_0$ is the fecundity of the first age class with mature individuals [@leslieUseMatricesCertain1945, @caswellMatrixPopulationModels2001].
-Survivorship-at-age and fecundity-at-age were calcualted using the available stock assessment data, which enabled $\lambda$ to be estimated; note that this assumed that each stock represented a discrete population with individual dynamics.
+Survivorship-at-age and fecundity-at-age were calculated using the available stock assessment data, which enabled $\lambda$ to be estimated; note that this assumed that each stock represented a discrete population with individual dynamics.
 
@@
 The Euler-Lotka model was fit using an iterative minimization process, where predicted abundance in the following year was compared to the abundance estimate from the stock assessment for the corresponding year ($N_{y+1}$).
-Where necessary, the annual age-specific fecundity and natural mortality estimates were adjusted until the $\lambda$ estimate from the Euler-Lotka equation resulted in an abundance time-series estimate ($N_{y+1}$) that was within 5% of the abundance estimates from the stock assessment (median difference was `r med.per.diff`).
+Where necessary, the annual age-specific fecundity and natural mortality estimates were adjusted until the $\lambda$ estimate from the Euler-Lotka equation resulted in an abundance time-series estimate ($N_{y+1}$) that was within 5% of the abundance estimates from the stock assessment (the median difference was `r med.per.diff`).
 This tolerance ensured that our analyses reflected the same understanding of stock productivity, natural mortality and fecundity as in the current assessments; effectively this methodology treats the abundance estimates from the stock assessments as the 'truth'.
-The minimization procedure resulted in the final estimates of $\lambda$ being approximately `r med.lam.per.diff` smaller than the initial estimates.
+The minimization procedure resulted in the final estimates of $\lambda$ being approximately `r med.lam.per.diff`% smaller than the initial estimates.
 
@@
 
-*Here we are treating the plus group as effectively 'terminal', i.e., it assumes that after the last age class the individuals make no contribution, which means these values are probably a bit low, but at this age they really aren't making much of a contribution on average*.
+**NOTE to Y'all: Here we are treating the plus group as effectively 'terminal', i.e., it assumes that after the last age class the individuals make no contribution, which means these values are probably a bit low, but at this age they really aren't making much of a contribution on average**.
 

### 2024-07-02 Drafts/Paper_1/04-results.Rmd
Updated Intro with HB edits

@@
 # Results {#reses-peses}
-
-<!-- Throughout the results we will focus primarily the six most commonly found species in the analysis (*Gadus morhua, Melogrammus aeglefinus, Clupie harengus, Plueronecties platessa, Polluck virens* and *Solea Solea*).
-The complete results for all of the populations included in the analysis can be found in the Supplemental material.
--->
 
@@
 Indeed, $\lambda_{FM>0}$ was below one `r prop.lam.fish.lt.1`% of the time.
-However, for many of the populations included in this analysis large recruitment events resulted in large estimates of $\lambda_{FM>0}$, in some years, this led to a skewed distribution of the $\lambda$ estimates, with these large events being an integral component of the populations population dynamics (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-bx-other-fig)).
+However, infrequent large recruitment events resulted in large estimates of $\lambda_{FM>0}$ for many populations in a few years.
+This led to a skewed distribution of the $\lambda$ estimates, with these large events being an integral component of the population dynamics for these populations (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-bx-other-fig)).
 The mean $\lambda_{FM>0}$ for the populations in this analysis was `r mn.lambda.F` which would suggest there remains scope for population growth even after fishing for most populations, although the mean $\lambda_{FM>0}$ was less than one for `r num.mn.lambda.fish.lt.1` of the `r n.stocks` populations.
@@
 Haddock (*M.
-aeglefinus*) and Atlantic cod populations had some of highest variability in lambda, both at the population level and between populations (Figure \@ref(fig:lambda-sd-fig)).
-For these two species, the variability of $\lambda$ within a population declined as you moved from the Eastern Atlantic to the Western Atlantic (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig))).
+aeglefinus*) and Atlantic cod populations had some of highest variability in $\lambda$, both at the population level and between populations (Figure \@ref(fig:lambda-sd-fig)).
+For these two species, the variability of $\lambda$ within a population declined as you moved from the Eastern Atlantic to the Western Atlantic (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig)).
 The pattern was more pronounced for Atlantic cod, with populations in the eastern Atlantic tending to have relatively low within population variability.
 The two other species with populations found in the NW and NE Atlantic (*C.harengus* and *P.
-virens*) the variability of $\lambda$ between the populations was much lower than for Haddock and Atlantic cod and there were no clear differences between regions for these two species (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig))).
+virens*) the variability of $\lambda$ between the populations was much lower than for Haddock and Atlantic cod and there were no clear differences between regions for these two species (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig)).
 This was largely due to the within population $\lambda$ variability being lower than the within population variability of Haddock and Atlantic cod populations in the NE Atlantic (Figure \@ref(fig:lambda-bx-6-fig)).
@@
 Generally, there was an increase in the variability of the $\lambda$ estimates as abundance declines, largely driven by an increase in the magnitude of the maximum value of $\lambda$ and a small increase in the frequency of low $\lambda$ values (Figure \@ref(fig:dd-overall-plt)).
-For example, values of $\lambda_{FM>0}$ > `r pa.lam.fish.low.bigs` were not observed at abundances > `100*pa.big.threshold`% of the maximum (similar trends were observed for $\lambda_{FM=0}$, with only one point being above `r pa.lam.nf.low.bigs` when the abundance was > `r 100*pa.big.threshold`% of the maximum).
+For example, values of $\lambda_{FM>0}$ > `r pa.lam.fish.low.bigs` were not observed at abundances > `r 100*pa.big.threshold`% of the maximum (similar trends were observed for $\lambda_{FM=0}$, with only one point being above `r pa.lam.nf.low.bigs` when the abundance was > `r 100*pa.big.threshold`% of the maximum).
 Similarly, the percentage of $\lambda_{FM>0}$ values below `r lam.low.threshold` was `r 100*prop.low.high.abund`% when the proportion of the abundance was >= 0.3, but this increased to `r 100*prop.low.low.abund`% of the data when the proportion of the abundance was below 0.3.
@@
 Populations in the Northwest Atlantic (particularly Atlantic cod) and Alaska had some of the lowest $\lambda_{FM=0}$ estimates at low abundance, while several populations in the North Sea had among the highest $\lambda_{FM=0}$ estimates at low abundance (Table \@ref(tab:tab-lambdas)).
-Of the `r n.bl.40` populations that had declined below 40% of the maximum abundance, only `r `n.low.40.nf` of the populations had a $\lambda_{FM=0}$ estimates < 1 at 40% of their maximum abundance; when the effects of fishing were included `r `n.low.40.nf` of the populations had $\lambda_{FM>0}$ estimates below 1 (Table \@ref(tab:tab-lambdas)).
+Of the `r n.bl.40` populations that had declined below 40% of the maximum abundance, only `r n.low.40.nf` of the populations had $\lambda_{FM=0}$ estimates < 1 at 40% of their maximum abundance; when the effects of fishing were included `r n.low.40.nf` of the populations had $\lambda_{FM>0}$ estimates below 1 (Table \@ref(tab:tab-lambdas)).
 

### 2024-07-02 Drafts/Paper_1/08-figures.Rmd
Updated Intro with HB edits

@@
 \newpage
-```{r lambda-bx-other-fig, echo=F, fig.cap="$\\lambda$ estimates for the remainded of the stocks in this analysis, plotted by the location of the stock.
+```{r lambda-bx-other-fig, echo=F, fig.cap="$\\lambda$ estimates for the remainder of the stocks in this analysis, plotted by the location of the stock.
 The abreviated species name is provided on the x axis."}
@@
 \newpage
-```{r dub-vs-sd, echo=F, fig.cap="The number of stocks which doubled in size by a given year with no fishing mortality  The dashed line represents the 77 stocks in the analysis."}
+```{r dub-vs-sd, echo=F, fig.cap="The recovery potential (low, moderate, or high) of each stock after 20 years compared to the median $\\lambda_{F=0}$ and the standard deviation of $\\lambda_{F=0}$."}
 knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"))

### 2024-07-02 Drafts/Paper_1/index.Rmd
Updated Intro with HB edits

@@
 title: |
-   "Life history variability influence on the recovery potential of globally exploited teleosts "
+   "Variability in the recovery potential of globally exploited teleosts "
 french_title: "Titre ici (*Nom latin de l'espèce*)"

### 2024-12-13 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
Incremental update
Working through Fall updates in hopes I get done before the winter

@@
 six.species <- c('morhua','harengus','aeglefinus','virens','solea','platessa')
+pop.dam <- pop.dam |> collapse::fgroup_by(Stock) |> 
+                           collapse::fmutate(med.gen.len = median(gen.len.opt,na.rm=T),med.r0 = median(R0.opt,na.rm=T)) |>
+                           as.data.frame()
 pop.dam.6 <- pop.dam |> collapse::fsubset(Species %in% six.species)
@@
                                                          "Faroes","Iceland","NAFO 2-4","NAFO 5-6","Gulf of Alaska","Bering Sea & AI","Aleutian Islands"),ordered = T)
-pop.dam <- data.frame(pop.dam)
+
+pop.dam.fish <- pop.dam.fish |> collapse::fgroup_by(Stock) |> 
+                           collapse::fmutate(med.gen.len = median(gen.len.opt,na.rm=T),med.r0 = median(R0.opt,na.rm=T)) |>
+                           as.data.frame()
+
+#pop.dam <- data.frame(pop.dam)
 
@@
 res.lambda.fin.long$group <- gsub("\\."," ",res.lambda.fin.long$group)
-res.lambda.fin.long.others <- res.lambda.fin.long |> collapse::fsubset(!Species %in% six.species)
+res.lambda.fin.long <- res.lambda.fin.long |> collapse::fgroup_by(group,Stock) |> collapse::fmutate(med.lam.stock = median(lambda,na.rm=T))
+
+res.lambda.fin.long.others <- res.lambda.fin.long |> as.data.frame() |> collapse::fsubset(!Species %in% six.species)
 res.lambda.fin.long.others$G.Species <- gsub("\\.","",res.lambda.fin.long.others$G.Species)
 res.lambda.fin.long.others$G.Species.short <- substr(res.lambda.fin.long.others$G.Species,1,5)
-res.lambda.fin.long.6 <- res.lambda.fin.long |> collapse::fsubset(Species %in% six.species)
+
+res.lambda.fin.long.6 <- res.lambda.fin.long |> as.data.frame() |> collapse::fsubset(Species %in% six.species)
 res.lambda.fin.long.6$G.Species <- gsub("\\.","",res.lambda.fin.long.6$G.Species)
@@
 tab.names <- c("Minimum Abundance",
-               "$\\lambda_{FM>0}^{Min}$",
-               "$\\lambda_{FM>0}^{40}$",
-               "$\\lambda_{FM>0}^{Max}$",
-               "$\\lambda_{FM=0}^{Min}$",
-               "$\\lambda_{FM=0}^{40}$",
-               "$\\lambda_{FM=0}^{Max}$",
+               "$\\lambda_{F>0}^{Min}$",
+               "$\\lambda_{F>0}^{40}$",
+               "$\\lambda_{F>0}^{Max}$",
+               "$\\lambda_{F=0}^{Min}$",
+               "$\\lambda_{F=0}^{40}$",
+               "$\\lambda_{F=0}^{Max}$",
                "Stock","Species")
@@
 tab.names <- c("Minimum Abundance",
-               "$\\lambda_{FM>0}^{Min-40}$",
-               "$\\lambda_{FM>0}^{Min-Max}$",
-               "$\\lambda_{FM>0}^{40-Max}$",
-               "$\\lambda_{FM=0}^{Min-40}$",
-               "$\\lambda_{FM=0}^{Min-Max}$",
-               "$\\lambda_{FM=0}^{40-Max}$",
+               "$\\lambda_{F>0}^{Min-40}$",
+               "$\\lambda_{F>0}^{Min-Max}$",
+               "$\\lambda_{F>0}^{40-Max}$",
+               "$\\lambda_{F=0}^{Min-40}$",
+               "$\\lambda_{F=0}^{Min-Max}$",
+               "$\\lambda_{F=0}^{40-Max}$",
                "Stock","Species")
@@
 lam.sd.p.rec$prop.cat <- factor(lam.sd.p.rec$prop.cat,levels=c("Low","Moderate","High"))
-
 ```
@@
 n.age.1 <- meta.sub |> collapse::fsubset(age.min == 1) |> nrow()
+n.age.2 <- meta.sub |> collapse::fsubset(age.min == 2) |> nrow()
 n.age.2.plus <- meta.sub |> collapse::fsubset(age.min >= 2) |> nrow()
+n.age.3.plus <- meta.sub |> collapse::fsubset(age.min > 2) |> nrow()
 min.year <- min(res.lambda.fin$year)
@@
                                                                                               med.lam.nf = median(lam.no.fish,na.rm=T),
-                                                                                              med.lam.fish = median(lam.fish,na.rm=T))
-
+                                                                                              med.lam.fish = median(lam.fish,na.rm=T),
+                                                                                              years.lt.1.nf = length(which(lam.no.fish<1)),
+                                                                                              years.lt.1.fish = length(which(lam.fish<1)),
+                                                                                              n.years = length(lam.fish))
+
+# Figure out what proportion of the time stocks have a lambda < 1 and what stocks usually have a lambda less than one
+prop.lam.lt.1.nf <-   round(100*median(lambda.by.stock$years.lt.1.nf/lambda.by.stock$n.years),digits = 1)    
+prop.lam.lt.1.fish <-   round(100*median(lambda.by.stock$years.lt.1.fish/lambda.by.stock$n.years),digits = 1)
+prop.usually.lt.1.nf <- round(100*length(which(lambda.by.stock$years.lt.1.nf/lambda.by.stock$n.years >= 0.5)) /n.stocks,digits=1)                        
+prop.usually.lt.1.fish <- round(100*length(which(lambda.by.stock$years.lt.1.fish/lambda.by.stock$n.years >= 0.5)) /n.stocks,digits=1)
+
+max.median.stock <- lambda.by.stock[lambda.by.stock$med.lam.nf == max(lambda.by.stock$med.lam.nf,na.rm=T),]
+max.median.lam.nf <- round(max.median.stock$med.lam.nf,digits=2)
+min.median.stock <- lambda.by.stock[lambda.by.stock$med.lam.nf == min(lambda.by.stock$med.lam.nf,na.rm=T),]
+min.median.lam.nf <- round(min.median.stock$med.lam.nf,digits=2)                                          
+mean.nf.of.min.median.lam.nf <- round(min.median.stock$mn.lam.nf,digits=2)
+mean.fish.of.min.median.lam.nf <- round(min.median.stock$mn.lam.fish,digits=2)
 num.mn.lambda.fish.lt.1 <- length(which(lambda.by.stock$mn.lam.fish < 1))
@@
 n.alaska.slow <- length(slow.20$Stock.short[slow.20$Manage.short== "AFSC"])
-n.nwa.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% c("DFO-TRAC","NEFSC")])
+n.nwa.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% c("DFO-TRAC","NEFSC")]) # All in NAFO 2-4
 n.nea.slow <- length(slow.20$Stock.short[slow.20$Manage.short %in% "ICES"])
+
+prop.slow.alaska <- round(100*n.alaska.slow/n.alaska,digits=0)
+prop.slow.n24 <- round(100*n.nwa.slow/n.nafo.24,digits=0)
 
@@
 # This is likely Figure 1
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Stock.no.species),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(G.Species),design=mat,scales='free_x')+
+
+# mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
+#                 3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
+#                 1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
+#                 4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
+#                 4, 10, byrow = TRUE)
+# new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(y=lambda,interaction(group,Stock.no.species),color=group)) +
+#                                            #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
+#                                            scale_x_discrete(NULL, guide = "axis_nested") +
+#                                            xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
+#                                            geom_hline(yintercept = 1,linetype='dashed') +
+#                                            facet_manual(vars(G.Species),design=mat,scales='free_x')+
+#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
+#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+
+## New Figure...
+
+mat <- matrix(c(rep(2,14),
+                rep(3,8), rep(NA,1), rep(5,5),
+                rep(NA,2),rep(4,4),rep(NA,1),rep(6,5),rep(NA,2),
+                rep(NA,2),rep(1,9),rep(NA,3)),
+                nrow=14, ncol=4,byrow=F)
+
+new.lam.plt.6 <- ggplot(res.lambda.fin.long.6) + geom_boxplot(aes(x=lambda,interaction(group,Stock.no.species),fill=group,color=group)) +
+                                           geom_point(aes(x=med.lam.stock,interaction(group,Stock.no.species)),color="firebrick2",fill="firebrick2",shape=8) +
+                                           scale_y_discrete(NULL, guide = "axis_nested") +
+                                           scale_color_manual(values = c("grey","blue")) +
+                                           scale_fill_manual(values = c("grey",'blue')) +
+                                           xlab("") + scale_x_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
+                                           geom_vline(xintercept = 1,linetype='dashed') +
+                                           facet_manual(vars(G.Species),design=mat,scales='free_y')+
                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 19,base_height = 15)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 20,base_height = 10)
 
 # The other stocks, perhaps we put this in a supplement...
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(y=lambda,interaction(group,G.Species.short),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(Area.long),design=mat,scales='free_x')+
+# mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
+#                 7, 7, rep(8,9),
+#                 9, 9, rep(10,7),11,11),
+#                 3, 11, byrow = TRUE)
+# 
+# new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(y=lambda,interaction(group,G.Species.short),color=group,fill=group)) +
+#                                            #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
+#                                            scale_x_discrete(NULL, guide = "axis_nested") +
+#                                            xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
+#                                            geom_hline(yintercept = 1,linetype='dashed') +
+#                                            facet_manual(vars(Area.long),design=mat,scales='free_x')+
+#                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
+#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+
+mat <- matrix(c(rep(NA,1),rep(1,1), rep(2,4), rep(3,1), rep(4,1),rep(5,1),rep(6,1),rep(NA,1),
+                rep(7,2),rep(8,9),
+                rep(9,2),rep(10,7),rep(11,2)),
+                nrow=11, ncol=3,byrow=F)
+
+new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(x=lambda,interaction(group,G.Species.short),color=group,fill=group)) +
+                                           geom_point(aes(x=med.lam.stock,interaction(group,G.Species.short)),color="firebrick2",fill="firebrick2",shape=8) +
+                                           scale_y_discrete(NULL, guide = "axis_nested") +
+                                           scale_color_manual(values = c("grey","blue")) +
+                                           scale_fill_manual(values = c("grey",'blue')) +
+                                           xlab("") + scale_x_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
+                                           geom_vline(xintercept = 1,linetype='dashed') +
+                                           facet_manual(vars(Area.long),design=mat,scales='free_y')+
                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"),new.lam.plt.others,base_width = 19,base_height = 15)
-
-# Standard deviation figure
-colrs.sd <- rep(c(rep('blue',4),rep('orange',4),rep('grey',4),rep('black',4)),20)
-pty.sd <- rep(rep(c(21,4,9,8),4),20)
-
-lam.sd.plt <- ggplot(res.lambda.fin ) + 
-                                       geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
-                                       scale_y_log10("Standard deviation (Lambda)",log_breaks(n=8)) +
-                                       scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
-                                       theme(axis.text.x = element_text(angle =45,hjust=1),
-                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 10)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"),new.lam.plt.others,base_width = 20,base_height = 10)
+
+# # Standard deviation figure
+# colrs.sd <- rep(c(rep('blue',4),rep('orange',4),rep('grey',4),rep('black',4)),20)
+# pty.sd <- rep(rep(c(21,4,9,8),4),20)
+# 
+# lam.sd.plt <- ggplot(res.lambda.fin ) + 
+#                                        geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
+#                                        scale_y_log10("Standard deviation (Lambda)",log_breaks(n=8)) +
+#                                        scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
+#                                        theme(axis.text.x = element_text(angle =45,hjust=1),
+#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
+# 
+# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 10)
+#
+
+# New figure....
+res.chhp <- res.lambda.fin |> collapse::fsubset(Species %in% c("morhua","aeglefinus","harengus","virens"))
+
+res.chhp$locale <- "Eastern Atlantic"
+res.chhp$locale[!res.chhp$Manage.short %in% "ICES"] <- "Western Atlantic"
+res.chhp$locale[res.chhp$Area.broad %in% c("Ice-Faroe","NEA")] <- "Northern Atlantic"
+res.chhp$locale[res.chhp$Manage.short %in% "AFSC"] <- "Pacific"
+
+res.chhp.summary <- res.chhp |> collapse::fgroup_by(locale,G.Species) |> collapse::fsummarise(avg.sd = mean(lam.no.fish.sd,na.rm=T),
+                                                                                 sd.of.sd = sd(lam.no.fish.sd,na.rm=T))
+res.chhp.summary$locale <- factor(res.chhp.summary$local,levels = c("Western Atlantic", "Northern Atlantic","Eastern Atlantic"))
+
+colrs.sd <- c("blue","orange","black","firebrick2")
+
+lam.sd.plt <- ggplot(res.chhp.summary,aes(y = avg.sd,x=locale,group=G.Species,color=G.Species)) + 
+                                              geom_point(position=position_dodge(width=0.3),size=2) + 
+                                              geom_line(position=position_dodge(width=0.3),size=1.25) +
+                                              scale_color_manual(values=colrs.sd) + 
+                                              geom_errorbar(aes(ymin=avg.sd - sd.of.sd, ymax=avg.sd+sd.of.sd,x=locale),width=0 ,position=position_dodge(width=0.3)) +
+                                              xlab("") + ylab("Standard devation (Lambda)") + theme(legend.title = element_blank())
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 6)
 
@@
                                 xlab("") + 
-                                scale_y_log10(name = "Lambda(FM=0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
+                                scale_y_log10(name = "Lambda(F=0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
                                 geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed')+
@@
                                 xlab("") + 
-                                scale_y_log10(name = "Lambda (FM>0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
+                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10),limits=c(0.2,12)) +
                                 geom_hline(yintercept = 1,color='firebrick2',linetype = 'dashed',linewidth=1.5)+
@@
 
-new.lam.plt.others <- ggplot(res.lambda.fin.long.others) + geom_boxplot(aes(y=lambda,interaction(group,G.Species.short),color=group)) +
-                                           #geom_boxplot(aes(y=lam.no.fish,x=G.Species))  + 
-                                           scale_x_discrete(NULL, guide = "axis_nested") +
-                                           xlab("") + scale_y_log10("Lambda",breaks = log_breaks(n=8),limits=c(0.2,12)) + 
-                                           geom_hline(yintercept = 1,linetype='dashed') +
-                                           facet_manual(vars(Area.long),design=mat,scales='free_x')
-
 # Density dependence by stock 
@@
                                 xlab("Proportion of maximum abundance") + 
-                                scale_y_log10(name = "Lambda (FM=0)",breaks = log_breaks(n=10)) +
+                                scale_y_log10(name = "Lambda (F=0)",breaks = log_breaks(n=10)) +
                                 geom_ribbon(aes(ymin=lower,ymax=upper,color=G.Species),alpha=0.10,linewidth=0)+
@@
                                 xlab("Proportion of maximum abundance") + 
-                                scale_y_log10(name = "Lambda (FM>0)",breaks = log_breaks(n=10)) +
+                                scale_y_log10(name = "Lambda (F>0)",breaks = log_breaks(n=10)) +
                                 facet_manual(vars(Area.long),design=mat,scales='free_x')+
@@
 
+pop.dam <- pop.dam |> collapse::fgroup_by(Stock) |> 
+                           collapse::fmutate(med.gen.len = median(gen.len.opt,na.rm=T),med.r0 = median(R0.opt,na.rm=T)) |>
+                           as.data.frame()
 # Lifetime reproductive success 
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-r0.boxplt.6 <- ggplot(pop.dam.all.6) + geom_boxplot(aes(y=R0.opt,interaction(group,Stock.no.species),color=group))  + 
-                                       scale_x_discrete(NULL, guide = "axis_nested") + scale_y_log10(name = "Lifetime Reproductive Output")+
-                                       geom_hline(yintercept = 1,linetype='dashed',color='blue')+
-                                       facet_manual(vars(G.Species),design=mat,scales='free_x')+
+mat <- matrix(c(rep(2,14),
+                rep(3,8), rep(NA,1), rep(5,5),
+                rep(NA,2),rep(4,4),rep(NA,1),rep(6,5),rep(NA,2),
+                rep(NA,2),rep(1,9),rep(NA,3)),
+                nrow=14, ncol=4,byrow=F)
+
+r0.boxplt.6 <- ggplot(pop.dam.all.6) + geom_boxplot(aes(x=R0.opt,interaction(group,Stock.no.species),fill=group,color=group)) +
+                                           geom_point(aes(x=med.r0,interaction(group,Stock.no.species)),color="firebrick2",fill="firebrick2",shape=8) +
+                                           scale_y_discrete(NULL, guide = "axis_nested") +
+                                           scale_color_manual(values = c("grey","blue")) +
+                                           scale_fill_manual(values = c("grey",'blue')) +
+                                       #scale_x_discrete(NULL, guide = "axis_nested") + 
+                                        scale_x_log10(name = "Lifetime Reproductive Output")+
+                                       geom_vline(xintercept = 1,linetype='dashed',color='blue')+
+                                       facet_manual(vars(G.Species),design=mat,scales='free_y')+
                                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"),r0.boxplt.6,base_width = 19,base_height = 15)
-
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-r0.boxplot.others <- ggplot(pop.dam.all.others) +   geom_boxplot(aes(y=R0.opt,interaction(group,G.Species.short),color=group))  + 
-                                                    scale_x_discrete(NULL, guide = "axis_nested") + 
-                                                    scale_y_log10(name = "Lifetime Reproductive Output")+
-                                                    geom_hline(yintercept = 1,linetype='dashed',color='blue')+
-                                                    facet_manual(vars(Area.long),design=mat,scales='free')+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"),r0.boxplt.6,base_width = 20,base_height = 10)
+
+mat <- matrix(c(rep(NA,1),rep(1,1), rep(2,4), rep(3,1), rep(4,1),rep(5,1),rep(6,1),rep(NA,1),
+                rep(7,2),rep(8,9),
+                rep(9,2),rep(10,7),rep(11,2)),
+                nrow=11, ncol=3,byrow=F)
+
+r0.boxplot.others <- ggplot(pop.dam.all.others) +   geom_boxplot(aes(x=R0.opt,interaction(group,G.Species.short),fill=group,color=group)) +
+                                                   geom_point(aes(x=med.r0,interaction(group,G.Species.short)),color="firebrick2",fill="firebrick2",shape=8) +
+                                                   scale_y_discrete(NULL, guide = "axis_nested") +
+                                                   scale_color_manual(values = c("grey","blue")) +
+                                                   scale_fill_manual(values = c("grey",'blue')) +
+                                                    #scale_x_discrete(NULL, guide = "axis_nested") + 
+                                                    scale_x_log10(name = "Lifetime Reproductive Output")+
+                                                    geom_vline(xintercept = 1,linetype='dashed',color='blue')+
+                                                    facet_manual(vars(Area.long),design=mat,scales='free_y')+
                                                     theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"),r0.boxplot.others,base_width = 15,base_height = 10)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"),r0.boxplot.others,base_width = 20,base_height = 10)
 
@@
 # Generation length
-mat <- matrix(c(2, 2, 2, 2, 2, 2, 2, 2,  2,  2,
-                3, 3, 3, 3, 3, 3, 5, 5,  5,  5, 
-                1, 1, 1, 1, 1, 1, 1, 1, NA, NA,
-                4, 4, 4, 6, 6, 6, 6, NA, NA, NA), 
-                4, 10, byrow = TRUE)
-gen.boxplt.6 <- ggplot(pop.dam.all.6) +
-                            geom_boxplot(aes(y=gen.len.opt,interaction(group,Stock.no.species),color=group))  + 
-                            scale_x_discrete(NULL, guide = "axis_nested") +
-                            scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
-                             facet_manual(vars(G.Species),design=mat,scales='free_x')+
+mat <- matrix(c(rep(2,14),
+                rep(3,8), rep(NA,1), rep(5,5),
+                rep(NA,2),rep(4,4),rep(NA,1),rep(6,5),rep(NA,2),
+                rep(NA,2),rep(1,9),rep(NA,3)),
+                nrow=14, ncol=4,byrow=F)
+
+r0.boxplt.6 <- ggplot(pop.dam.all.6) + geom_boxplot(aes(x=R0.opt,interaction(group,Stock.no.species),fill=group,color=group)) +
+                                           geom_point(aes(x=med.r0,interaction(group,Stock.no.species)),color="firebrick2",fill="firebrick2",shape=8) +
+                                           scale_y_discrete(NULL, guide = "axis_nested") +
+                                           scale_color_manual(values = c("grey","blue")) +
+                                           scale_fill_manual(values = c("grey",'blue')) +
+                                       #scale_x_discrete(NULL, guide = "axis_nested") + 
+                                        scale_x_log10(name = "Lifetime Reproductive Output")+
+                                       geom_vline(xintercept = 1,linetype='dashed',color='blue')+
+
+gen.boxplt.6 <- ggplot(pop.dam.all.6) + geom_boxplot(aes(x=gen.len.opt,interaction(group,Stock.no.species),fill=group,color=group)) +
+                                        geom_point(aes(x=med.gen.len,interaction(group,Stock.no.species)),color="firebrick2",fill="firebrick2",shape=8) +
+                                        scale_y_discrete(NULL, guide = "axis_nested") +
+                                        scale_color_manual(values = c("grey","blue")) +
+                                        scale_fill_manual(values = c("grey",'blue')) +
+                                        scale_x_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
+                                        facet_manual(vars(G.Species),design=mat,scales='free_y')+
                                          theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"),gen.boxplt.6,base_width = 19,base_height = 15)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"),gen.boxplt.6,base_width = 20,base_height = 10)
 
 # Then the generation length for others.
-mat <- matrix(c(1, 2, 2, 2, 2, 3, 4, 5,6,NA,NA,
-                7, 7, rep(8,9),
-                9, 9, rep(10,7),11,11),
-                3, 11, byrow = TRUE)
-
-gen.boxplt.others <- ggplot(pop.dam.all.others) +
-                            geom_boxplot(aes(y=gen.len.opt,interaction(group,G.Species.short),color=group))  + 
-                            scale_x_discrete(NULL, guide = "axis_nested") +
-                            scale_y_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
-                            facet_manual(vars(Area.long),design=mat,scales='free')+
+mat <- matrix(c(rep(NA,1),rep(1,1), rep(2,4), rep(3,1), rep(4,1),rep(5,1),rep(6,1),rep(NA,1),
+                rep(7,2),rep(8,9),
+                rep(9,2),rep(10,7),rep(11,2)),
+                nrow=11, ncol=3,byrow=F)
+
+gen.boxplt.others <- ggplot(pop.dam.all.others) + geom_boxplot(aes(x=gen.len.opt,interaction(group,G.Species.short),fill=group,color=group)) +
+                                                  geom_point(aes(x=med.gen.len,interaction(group,G.Species.short)),color="firebrick2",fill="firebrick2",shape=8) +
+                                                  scale_y_discrete(NULL, guide = "axis_nested") +
+                                                  scale_color_manual(values = c("grey","blue")) +
+                                                  scale_fill_manual(values = c("grey",'blue')) +
+                                                  scale_x_continuous("Generation Length (years)",limits=c(0,13),breaks= seq(0,20,by=2)) +
+                                                  facet_manual(vars(Area.long),design=mat,scales='free_y')+
                                                   theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"),gen.boxplt.others,base_width = 15,base_height = 10)
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"),gen.boxplt.others,base_width = 20,base_height = 10)
 
@@
 
+colrs.cat <- c("firebrick2","white","blue")
+# Can I show this thing better?
+lam.sd.p.rec.ordered <- lam.sd.p.rec[order(lam.sd.p.rec$prop.cat,lam.sd.p.rec$lam.no.fish.sd,lam.sd.p.rec$lam.no.fish.med,lam.sd.p.rec$Stock),]
+lam.sd.p.rec.ordered$Stock <- factor(lam.sd.p.rec.ordered$Stock,levels =rev(lam.sd.p.rec.ordered$Stock))
+
+lam.sd.p.rec.ordered$lme.short <- "NWA"
+lam.sd.p.rec.ordered$lme.short[lam.sd.p.rec.ordered$LME == "NE Atlantic"] <- "NEA"
+lam.sd.p.rec.ordered$lme.short[lam.sd.p.rec.ordered$LME == "Pacific (Alaska)"] <- "Pac"
+lam.sd.p.rec.ordered$spec.lme <- paste0(lam.sd.p.rec.ordered$G.Species," (",lam.sd.p.rec.ordered$lme.short,")")
+
+p1 <- ggplot(lam.sd.p.rec.ordered) + geom_bar(aes(x=lam.no.fish.med,y=Stock,group = prop.cat,fill=prop.cat,color=prop.cat),stat='identity') + 
+                                     scale_y_discrete("",position='right',breaks = NULL) +
+                                     scale_fill_manual(values=colrs.cat) +
+                                     scale_color_manual(values=rep('black',3)) +
+                                     geom_vline(xintercept =1,linetype = 'dashed') + scale_x_reverse("Median lambda") +
+                                     theme(legend.position = 'none',
+                                           plot.margin = margin(t=53,b=8,l=5),)
+
+p2 <- ggplot(lam.sd.p.rec.ordered) + geom_bar(aes(x=lam.no.fish.sd,y=Stock,group = prop.cat,fill=prop.cat,color=prop.cat),stat='identity')  + 
+                                     theme(legend.position = 'top',legend.title = element_blank()) + scale_x_continuous("Standard deviation (lambda)") +
+                                     scale_y_discrete("",position='left',labels = rev(lam.sd.p.rec.ordered$spec.lme)) + 
+                                     scale_fill_manual(values=colrs.cat) +
+                                     scale_color_manual(values=rep('black',3)) +
+                                     theme(axis.text.y = element_text(hjust=0.5),
+                                           plot.margin = margin(t=53,l=-30,b=8),
+                                           axis.ticks.y = element_blank(),
+                                           legend.position = c(-0.3,1.02),legend.direction = 'horizontal',)
+
+p3 <- cowplot::plot_grid(p1,p2)
+p3
+
+save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"),p3,base_width = 11,base_height = 15)
+
 # Is there a relationship between median and sd?
-colrs.cat <- c("blue","black","orange")
-pts.cat <- 21:23
-sd.rec.plt <- ggplot(lam.sd.p.rec, aes(y=lam.no.fish.med,x=lam.no.fish.sd,color=prop.cat,group=prop.cat)) + 
-                       geom_point(size =3,aes(shape=prop.cat,fill=prop.cat)) + 
-                       geom_hline(yintercept=1,linetype="dashed") + 
-                       scale_y_continuous(name="median Lambda") + scale_x_continuous(name="standard deviation Lambda") +
-                       scale_color_manual(values=colrs.cat) + scale_fill_manual(values=colrs.cat) +  
-                       scale_shape_manual(values=pts.cat) + theme(legend.title = element_blank())
-
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"),sd.rec.plt,base_width = 10,base_height = 10)
+# pts.cat <- 21:23
+# sd.rec.plt <- ggplot(lam.sd.p.rec, aes(y=lam.no.fish.med,x=lam.no.fish.sd,color=prop.cat,group=prop.cat)) +
+#                        geom_point(size =3,aes(shape=prop.cat,fill=prop.cat)) +
+#                        geom_hline(yintercept=1,linetype="dashed") +
+#                        scale_y_continuous(name="median Lambda") + scale_x_continuous(name="standard deviation Lambda") +
+#                        scale_color_manual(values=colrs.cat) + scale_fill_manual(values=colrs.cat) +
+#                        scale_shape_manual(values=pts.cat) + theme(legend.title = element_blank())
 

### 2024-12-13 Drafts/Paper_1/03-methods.Rmd
Incremental update
Working through Fall updates in hopes I get done before the winter

@@
 
-This analysis used age structured fisheries data obtained from stock assessments for stocks in the Atlantic and Pacific Oceans [@charbonneauAgestructuredmarinefishdatabase2022; @charbonneauEffectsFishingMortality2022].
-This repository had sufficient data to run the analysis for `r n.stocks` stocks from NE Atlantic, NW Atlantic, and the North Pacific, this included stocks managed by International Council for the Exploration of the Sea (ICES; `r n.stock.ices`), NOAA (NOAA;`r n.stock.noaa`), and Fisheries and Oceans Canada (DFO; `r n.stock.dfo` stocks).
-The time series used in this analysis started as early as `r min.year` and the most recent data were from `r max.year`, the average length of the time series for the stocks included in this analysis was `r mn.ts.len` years and the number of years used ranged between `r min.ts.len` and `r max.ts.len` years.
-The stocks used represented `r num.orders` orders, with the most represented orders being the Gadiformes (`r num.gads` stocks), Pleuronectiformes (`r num.pleur` stocks) and Clupeiformes (`r num.clup` stocks).
+These analyses used an existing data repository for 77 stocks from the Northeast Atlantic, Northwest Atlantic, and the North Pacific; including stocks managed by International Council for the Exploration of the Sea; including stocks managed by International Council for the Exploration of the Sea (ICES; `r n.stock.ices`), NOAA (NOAA;`r n.stock.noaa`), and Fisheries and Oceans Canada [DFO, `r n.stock.dfo` stocks, @charbonneauAgestructuredmarinefishdatabase2022; @charbonneauEffectsFishingMortality2022].
+Time series started as early as `r min.year` and spanned until `r max.year`, with an average length of `r mn.ts.len` years (range `r min.ts.len` and `r max.ts.len` years).
+The assessed stocks represented `r num.orders` orders, with the majority of stocks representing Gadiformes (`r num.gads` stocks), Pleuronectiformes (`r num.pleur` stocks) and Clupeiformes (`r num.clup` stocks).
 The other three orders had relatively few stocks included in the analysis, with `r num.perci` Perciform stocks, `r num.scomb` Scombriform stocks, and just `r num.scorp` Scorpaeniform stock.
-The most common species in this analysis were Atlantic cod (*G.
-morhua*) and the majority of the stocks (`r n.six`) in this analysis were represented by one of six species (*G.
-morhua* (`r num.cod`), *C.
-harengus* (`r num.her`), *M.
-aeglefinus* (`r num.had`),  *P.
-virens* (`r num.pol`), *S.
-solea* (`r num.sol`), and *P.
-platessa* (`r num.plat`)).
+The majority of the data came from one of six species: Atlantic cod (*Gadus morhua*;`r num.cod`), (*Clupea harengus*;`r num.her`), haddock (*Melanogrammus aeglefinus*; `r num.had`), pollock (*Pollachius virens*; `r num.pol`), Common sole (*Solea solea*; `r num.sol`), and plaice (*Pleuronectes platessa*; `r num.plat`).
 
-These data included age-specific estimates of abundance, weight, biomass, maturity, natural mortality, and fishery removals (Table \@ref(tab:tab-meta)), these data were all required to calculate survival-at-age and fecundity-at-age and to estimate the annual productivity of these stocks.
-For the age structured analysis, the last age class was considered the 'terminal' age in the analysis, thus we implicitly assumed there was no contribution to productivity from older aged individuals.
-In addition, for the majority of the stocks the first age class was age 1 (`r n.age.1` stocks) while another `r n.age.2.plus` of the stocks have a first age of 2 or greater.
-The young age classes not included for these stocks (e.g.
-Age 0) consisted of immature individuals that do not contribute to the productivity of the stock; however it has been noted that the exclusion of immature age classes in these types of analyses may lead to a slight overestimate of productivity [@pardoMaximumIntrinsicRate2016].
+The repository included age-specific estimates of abundance, weight, biomass, maturity, natural mortality, and fishery removals for each stock (Table \@ref(tab:tab-meta)).
+Despite uncertainty inherent in assessment processes, each assessment was accepted as a basis for management advice, and thus the time series in the data repository represented the best available understanding of the population dynamics of each stock.
 
-## Life Table Reconstruction
+## Population Growth Rates
 
-Information on births and deaths can describe a closed population’s demographics and how they are affected by age and time.
-To do so knowledge of the  population’s age specific fecundity and mortality is required, these values can then be used within the Euler-Lotka equation [@lotkaRelationsBirthRates1907] to estimate the population growth rate ($\lambda$) in a given year.
-These data could be derived from the data available for the `r n.stocks` stocks used in this analysis.
-
-### Fecundity-at-age
-
-The number of spawners in year $y$ and age class $a$ ($NS_{y,a}$) is the proportion of mature individuals in each age class ($Mat_{y,a}$) multiplied by the number of individuals in each age class
-
-$$
-NS_{y,a} = Mat_{y,a} N_{y,a}
-$$
-Fecundity is required to be the number of offspring produced by each female in each age class.
-Given the uncertainty of both fertilization and egg survival, using the number of eggs at a given length or size is inappropriate.
-However, these data do have the number of recruits produced each year, and this can be combined with the spawning stock biomass to obtain an estimate of the number of recruits produced per kilogram of spawning biomass $RPS_{y}$, this is calculated as
-
-$$
-RPS_{y} = R_{y} SSB_{tot,(y-ra)} 
-$$
-
-Where $SSB_{yot,y-ra}$ is the total spawning stock biomass in year $y$.
-$R_{y}$ is the number of individuals in the youngest age class available for a specific stock (hereafter referred to as recruits) offset temporally by the age of the recruits.
-For example, if the age of the recruits ($ra$) is 2 years , we assume that the recruits in 2010 were produced by the spawning stock biomass in 2008 ($SSB_{tot,y-ra}$).
-The number of recruits produced by each age class ($RPA_{y,a}$) can then be calculated by multiplying the spawner biomass in each age class $SSB_{y-ra,a}$ by the number of recruits produced per kilogram of SSB
-
-$$
-RPA_{y,a} =  SSB_{(y-ra),a} RPS_{y}
-$$
-This method does not account for any changes in reproductive success by age, each kilogram of spawning biomass contributes the same to the total total reproductive output, irrespective of their age.
-Finally, the age-specific fecundity ($f_{y,a}$) is calculated as number of offspring produced by each individual in the population.
-This is offset by one year, as the recruits observed in year $y+1$ enter into the Euler-Lotka formulation in year $y$.
-
-$$
-f_{y,a} =  \frac{RPA_{y+1,a}}{NS_{(y-ra+1),a}}
-$$
-
-### Survivorship-to-age
-
-The number of animals surviving to each age depends on age-specific mortality rates.
-Commercially-exploited fishes experience fishing mortality ($FM$) once they grow large enough to become vulnerable to the gear (reference).
-Fishing mortality combines with natural mortality ($NM$) to give total mortality ($Z$) affecting each age class in each year.
-Varying assumptions can be made about natural mortality during stock assessments, where it may be an assumed value for each age (EXAMPLE), allowed to vary over time and by age (EXAMPLE), or input as a constant across ages (EXAMPLE).
-Due to challenges with separability in typical stock assessment models, natural mortality is often assumed for each age class, in some assessments it varies by age and over time, in other assessments it does not.
-Irrespective of this, the stock assessment used in this analysis all provide an estimate of natural mortality by age and year, this value is typically an instantaneous rate and is converted to a proportional natural mortality for the Euler-Lotka model.
-
-The data also contained the number of fish harvested by the fishery each year and for each age.
-These can be divided by the assessed numbers at age to get an estimate of fishing mortality in each year for each age.
-
-$$
-FM_{y,a} =  \frac{Catch_{y,a}}{N_{y,a}}
-$$
-Together, fishing mortality ($FM_{y,a}$) and natural mortality ($NM_{y,a}$) provide a total mortality estimate ($Z_{y,a}$) for each age in each year
-
-$$
-Z_{y,a} =  FM_{y,a} + NM_{y,a}
-$$
-Survival-at-age is simply
-
-$$
-l_{y,a} = 1= Z_{y,a}
-$$
-The Euler-Lotka equation requires suvivorship-to-age, which is the cumulative survival to age $a$.
-The survival of individuals to the first available age class ($s_{y,1}$) was assumed to be 1 [this may lead to a slight overestimate of $\lambda$; @pardoMaximumIntrinsicRate2016], for the remainder of the age classes it was calculated as
-
-$$
-s_{y,a} =  s_{y,(a-1)} \times l_{y,(a-1)}
-$$
-
-### Euler-Lotka
-
+We used life table reconstructions to calculate survival-at-age and fecundity-at-age over time from the available data series, and applied the Euler-Lotka equation [@lotkaRelationsBirthRates1907] to estimate the corresponding population growth rate ($\lambda$)  in a given year.
+This allowed us to use information on births, deaths and maturity to describe each stock’s demographics and how they changed over age and over time using a tractable and consistent model, despite variability among stock assessments.
 The discrete time Euler-Lotka equation was first proposed by Euler in 1760 (subsequently published by @moserGesetzeLebensdauer1839) and is a special case of the continuous time demographic model first proposed by Lotka in 1907 [@lotkaRelationsBirthRates1907; @sharpeProblemAgedistribution1911; @lotkaRelationBirthRate1918]:
@@
 
-### Population Growth Rates $\lambda$
+When calculating survival and fecundity inputs, we considered the last observed age class to be the terminal age, beyond which there was no contribution to productivity.
+The first age class was age 1 for the majority of stocks (N = `r n.age.1`), where only `r n.age.2.plus` of the stocks had a first age of 2 (N = `r n.age.2`) or greater (N = `r `n.age.3.plus`).
+For simplicity, we assumed survivorship to the first age class represented by the data to be 1, which results in a slight overestimate of productivity from the Euler-Lotka equation [@pardoMaximumIntrinsicRate2016].
+However, we tested back-calculating abundance for the earliest ages using the available time series of age-specific natural mortality rates for several stocks, but this resulted in negligible differences to the annual productivity estimates.
 
-The fecundity, natural mortality, and fishing mortality estimates were then used to obtain an estimate of $\lambda$ for a given year from the Euler-Lotka equation and used to predict the abundance in the following year.
+### Fecundity-at-age
+
+We parameterized fecundity as the number of offspring (recruits) produced by each female in each age class rather than as a number of eggs, given that egg production by size, fertilization rates, and egg to age-0 survival rates are unknown.
+We first calculated an overall rate of recruitment, as the number of recruits produced per kilogram of spawning biomass $RPS_y$:
+
+$$
+RPS_{y} = \frac{R_{y}} {SSB_{y-ra}} 
+$$
+
+Where $R_y$ is the number of individuals in the youngest age class available for a specific stock (hereafter referred to as recruits) and $SSB_{y-ra}$ is the total spawning stock biomass in year $y$, offset by the age of recruits ($ra$).
+For example, if the first age class in the abundance time series is 2 years, we assumed that the recruits in 2010 were produced by the spawning stock biomass in 2008 ($SSB_{y-ra}$).
+
+Then we calculated the total number of recruits produced by each age class ($RPA_{y,a}$) by multiplying the spawner biomass in each age class $SSB_{(y-ra),a}$ by the number of recruits produced per kilogram of SSB
+
+$$
+RPA_{y,a} =  SSB_{(y-ra),a} RPS_{y}
+$$
+Fish are expected to have variability in reproductive success by age (ref, ref).
+However, we had to make the simplifying assumption that each kilogram of spawning biomass contributed the same to the total total reproductive output, irrespective of age.
+We calculated the age-specific fecundity ($f_{y,a}$) as the number of offspring produced by each spawner in the population.
+The number of spawners in year $y$ and age class $a$ ($NS_{y,a]$) is the proportion of mature individuals in each age class ($Mat_{y,a}$) multiplied by the number of individuals in each age class:
+
+$$
+NS_{y,a} = Mat_{y,a} N_{y,a}
+$$
+
+and annual fecundity becomes:
+
+$$
+f_{y,a} =  \frac{RPA_{y+1,a}}{NS_{(y-ra+1),a}}
+$$
+
+Fecundity is offset by one year, as the recruits observed in year $y+1$ enter into the Euler-Lotka formulation in year $y$.
+
+<!-- Fecundity is required to be the number of offspring produced by each female in each age class.
+Given the uncertainty of both fertilization and egg survival, using the number of eggs at a given length or size is inappropriate.
+However, these data do have the number of recruits produced each year, and this can be combined with the spawning stock biomass to obtain an estimate of the number of recruits produced per kilogram of spawning biomass $RPS_{y}$, this is calculated as -->
+
+<!-- Where $SSB_{yot,y-ra}$ is the total spawning stock biomass in year $y$.
+$R_{y}$ is the number of individuals in the youngest age class available for a specific stock (hereafter referred to as recruits) offset temporally by the age of the recruits.
+For example, if the age of the recruits ($ra$) is 2 years , we assume that the recruits in 2010 were produced by the spawning stock biomass in 2008 ($SSB_{tot,y-ra}$).
+The number of recruits produced by each age class ($RPA_{y,a}$) can then be calculated by multiplying the spawner biomass in each age class $SSB_{y-ra,a}$ by the number of recruits produced per kilogram of SSB -->
+
+<!-- This method does not account for any changes in reproductive success by age, each kilogram of spawning biomass contributes the same to the total total reproductive output, irrespective of their age.
+Finally, the age-specific fecundity ($f_{y,a}$) is calculated as number of offspring produced by each individual in the population.
+-->
+
+### Survivorship-to-age
+
+The number of animals surviving to each age (survivorship-to-age) depends on age-specific mortality rates (or conversely survival-at-age).
+Commercially-exploited fishes experience fishing mortality ($F$) once they grow large enough to become vulnerable to the gear (reference).
+Fishing mortality combines with natural mortality ($M$) to give total mortality ($Z$) affecting each age class in each year.
+Due to challenges with separability in typical stock assessment models, varying assumptions can be made about natural mortality during stock assessments, where it may be an assumed value for each age (EXAMPLE), allowed to vary over time and by age (EXAMPLE), or input as a constant across ages (EXAMPLE).
+We did not explore these differences and used the estimates of natural mortality by age and year found in the data repository (representing outputs from each assessment), which we converted into an annual rate and for input into the Euler-Lotka equation
+
+The data also contained the number of fish harvested by the fishery each year and for each age.
+These can be divided by the assessed numbers at age to get an estimate of fishing mortality in each year for each age.
+
+$$
+F_{y,a} =  \frac{Catch_{y,a}}{N_{y,a}}
+$$
+Together, fishing mortality ($F_{y,a}$) and natural mortality ($M_{y,a}$) provide a total mortality estimate ($Z_{y,a}$) for each age in each year.
+
+$$
+Z_{y,a} =  F_{y,a} + M_{y,a}
+$$
+Survival-at-age is simply:
+
+$$
+l_{y,a} = 1= Z_{y,a}
+$$
+Survival-at-age was used to calculate cumulative suvivorship-to-age for input into the Euler-Lotka equation:
+
+$$
+s_{y,a} =  s_{y,(a-1)} \times l_{y,(a-1)}
+$$
+The availability of catch-at-age time series in the data repository meant that fishing mortality and natural mortality rates were separable.
+Given this method provides separate estimates of $F$ and $M$ it was possible to calculate survival as well as theoretical population growth rates using the $M$ and fecundity ($\lambda_{F=0}$) estimates from the reconstruction.
+We recognize that the age structure in the underlying time series are still influenced by fishing pressure and that populations are at varying size.
+This means that ($\lambda_{F=0}$) does not represent the maximum intrinsic rate of abundance increase [e.g., r_max; CITE].
+However, our theoretical annual growth rates in the absence of fishing represent the productivity that the population could have achieved in each specific year, if there had not been a fishery in that year.
+
+### Estimation
+
+One limitation of calculating survivorship-to-age and fecundity-at-age using the archived data in the repository is that it is not straightforward to propagate observation error in each time series of data.
+To ensure that variability did not accumulate into unreasonable predictions for annual population productivity, we fit the Euler-Lotka model using an iterative minimization process, where predicted abundance in the following year:
 
@@
 $$
+was compared to the abundance estimate from the stock assessment for the corresponding year ($N_{y+1}$).
 
-The Euler-Lotka model was fit using an iterative minimization process, where predicted abundance in the following year was compared to the abundance estimate from the stock assessment for the corresponding year ($N_{y+1}$).
-Where necessary, the annual age-specific fecundity and natural mortality estimates were adjusted until the $\lambda$ estimate from the Euler-Lotka equation resulted in an abundance time-series estimate ($N_{y+1}$) that was within 5% of the abundance estimates from the stock assessment (the median difference was `r med.per.diff`).
-This tolerance ensured that our analyses reflected the same understanding of stock productivity, natural mortality and fecundity as in the current assessments; effectively this methodology treats the abundance estimates from the stock assessments as the 'truth'.
+Where necessary, we adjusted the annual age-specific fecundity and natural mortality estimates were adjusted until the $\lambda$ estimate from the Euler-Lotka equation resulted in an abundance time-series estimate ($N_{y+1}$) that was within 5% of the abundance estimates time series output from the stock assessment (median difference was `r med.per.diff`%).
+The adjustment was performed iteratively, with a step change (for most stocks each step was a change of 0.5%, for some stocks the step size was 0.05%) first made to the natural mortality estimates (applied to each age), if the estimated abundance was not within 5% of the observed abundance estimate this was followed by a step change in the fecundity(applied to each age).
+This procedure was repeated until the estimated abundance was within 5% of the observed abundance.
+
+This approach ensured that our analyses reflected the same understanding of stock productivity, natural mortality and fecundity as in the current assessments, by effectively treating the abundance estimates in the data repository as the ‘truth’.
+Although there are inherent limitations to treating stock assessment outputs as observed data [@brooksWhenDataAre2015], these assessments represent the best available knowledge on the population dynamics of each stock.
+Thus, we consider the abundance time series to be an appropriate benchmark to compare against.
 The minimization procedure resulted in the final estimates of $\lambda$ being approximately `r med.lam.per.diff`% smaller than the initial estimates.
-
-The life table reconstruction resulted in stock-specific $\lambda$, fecundity, and natural mortality estimates for each year in which data were available accounting for the age structure and life history characteristics of each stock.
-In other words, we estimated the realized population growth rate using the changes in the population size of the stocks from year to year (realized population growth rates), based on the amount of mortality experienced and annual reproductive success.
-The realized $\lambda$ included fishing mortality  ($\lambda_{FM>0}$), although this method enabled the theoretical population growth rate excluding fishing mortality ($\lambda_{FM=0}$) to be calculated directly from the annual the natural mortality and fecundity estimates.
-
-<!-- For consistency in the Euler-lotka estimates across all the stocks, the first age used in the analysis was 'age 0' (which is simply an estimate of abundance of fish in the year they were born).
-For some stocks this information is not available (see Table X, **possibly in an Appendix where we have meta-data**).
-For the stocks in which age 0 information is unavailable, an estimate of the abundance of the younger age classes were back calculated using average natural mortality provided for the youngest age class available.
--->
+Population growth rates from life table analyses typically decline when variability in the input parameters is accounted for [e.g., CITE Bowlby & Gibson 2020].
+However, it is also possible that the removals series used in the stock assessments do not capture all sources of fishing mortality [e.g., unreported catch, bycatch and incidental mortality; CITE].
+This would result in the estimates of $\lambda_{F=0}$ being lower than reality, necessitating the slight reductions in fecundity and/or increases in natural mortality during the iterative minimization process.
 
@@
 
+Life table analyses make no assumptions about population regulation and thus do not incorporate a density-dependent relationship between spawners and recruits [@mcallisterUsingDemographicMethods2001].
+However, our estimated productivity parameters could be explored for evidence of density-dependence by modelling each stock’s annual population growth rate against relative population size (expressed as a proportion of maximum abundance) in the same year.
+Negative density dependence is observed when $\lambda$ increases as abundance declines [CITE] which is the type of compensatory response described by typical spawner-recruit relationships (ref, ref).
+Positive density dependence occurs when λ declines with increasing abundance, which is also called an Allee effect when it occurs at low abundance (ref, ref).
+Density independence occurs when λ shows no relationship with changes in abundance.
+We evaluated both the realized productivity estimates ($\lambda_{F>0}$) and the theoretical productivity values excluding the impact of fishing mortality ($\lambda_{F=0}$).
+
 Life table analyses make no assumptions about population regulation and thus do not incorporate a density-dependent relationship between spawners and recruits (Reference?).
 However, the data could be explored for evidence of density-dependence by modelling each stock's estimated annual population growth rate against the relative population size (proportion of maximum abundance) that year.
-This was done twice, once using  ($\lambda_{FM=0}$) and once using ($\lambda_{FM>0}$).
+This was done twice, once using  ($\lambda_{F=0}$) and once using ($\lambda_{F>0}$).
 Negative density dependence is observed when $\lambda$ increases as abundance declines, positive density dependence occurs when $\lambda$ declines with increasing abundance, while density independence is observed when $\lambda$ is not impacted by changes in abundance.
 
-Generalized Additive Mixed Models were used to allow for some non-linearity in the relationships (CITE MCGV and WOOD), the overall effect and the effect for each stock was modelled as
+We used Generalized Additive Mixed Models (CITE MCGV and WOOD) to describe potential relationships, where the overall effect and the effect for each stock was modelled as
 
@@
 
-The interaction was modeled using the *fs* basis using the mgcv package in R, this treats the smooth curves as random effects and is used when a factor has a large number of levels (CITE!).
+The interaction was modeled using the *fs* basis in the mgcv package in R, which treats the smooth curves as random effects and is used when a factor has a large number of levels (CITE!).
+Although we explored various model formulations and alternative error distributions,  all models had similar challenges overcoming either the underlying non-normality or the heteroskedasticity of the data.
+Given these challenges we do not use the model to determine the statistical significance of the trends.
+This approach was preferred to fitting simple loess smooths to individual data series, because we were able to better capture the global relationship in addition to providing a relative metric of variability among the stocks.
+
+For a reconstruction of time series as undertaken here, the maximum value of $\lambda$ is constrained at higher abundances because the maximum abundance is a known value (e.g., the maximum possible $\lambda$ at 50% of the maximum abundance is 2, at 25% is it 4, and at 100% it is 1).
+Conversely, the minimum value of $\lambda$ will be constrained at lower abundances (e.g., $\lambda$ must be $\ge$ 1 when the stock is at it's minimum observed abundance).
+As a result, at the maximum abundance $\lambda$ will be $\le$ 1, at the minimum $\lambda$ will be $\ge$ 1, and, on the natural scale, higher variability in $\lambda$ values at low abundances should be relatively common.
+
+<!-- The interaction was modeled using the *fs* basis using the mgcv package in R, this treats the smooth curves as random effects and is used when a factor has a large number of levels (CITE!).
 Various alternative modelling methods were explored (various model formulations, alternative error distributions, etc.) but all models had similar challenges overcoming either the underlying non-normality or the heteroskedasticity of the data.
 As such, the uncertainty surrounding the model output should be treated with caution, while we discuss the general trends this model provides we attempted to avoid discussion of the statistical significance of the trends.
+-->
 
@@
 
-There are numerous demographic parameters that can be derived from the outputs of the life table reconstruction.
+There are numerous demographic parameters that can be derived from the outputs of the life table reconstruction [CITE].
+Here we focus on three that are strongly linked to recovery potential:  doubling time, lifetime reproductive success, and generation time.
+Comparing the median time frame over which abundance can double gives a good indication of relative productivity among species and stocks.
+Monte Carlo draws from the observed distribution of fecundity and natural mortality were used in a projection simulation to estimate the doubling time for each stock.
+Lifetime reproductive success, also called the net reproductive rate, describes the average number of female spawners produced by one female spawner throughout her lifetime.
+Values greater than 1 suggest a stock would tend to increase, values less than 1 suggest a stock would tend to decline, and a value of exactly 1 indicates that the average female has produced sufficient offspring over their lifetime to only replace themselves.
+
+Generation time is an alternate indicator for the relative reproductive rate of a stock, where shorter generation times are associated with faster population growth.
+Here, we calculated generation time as  is calculated for each cohort and is the mean age of spawners that produced recruits [CITE].
+Values of both the lifetime reproductive rate and generation time were derived for each complete cohort, which meant we could also evaluate changes in reproductive capacity over time for each stock.
+Additionally, we compared theoretical reproductive potential and generation times from life history characteristics alone ($F=0$) with those expected under current fishing mortality ($F>0$), as detailed in section 3.2.2.
+
+<!-- There are numerous demographic parameters that can be derived from the outputs of the life table reconstruction.
 Here we focus on three that are strongly linked to recovery potential: doubling time, lifetime reproductive success, and generation time.
@@
 Generation time here is calculated for each cohort and is the mean age of spawners that produced recruits.
+-->
 
@@
 For `r n.dt.sims` simulations, we took a random sample of the annual values for fecundity and natural mortality, used the life table reconstruction to estimate $\lambda$, and calculated abundance in the following year.
-Abundance of each stock was projected over `n.sim.years` years, and the percentage of the simulations in which the population size had doubled was recorded each year.
+Abundance of each stock was projected over `r `n.sim.years` years, and the proportion of the simulations in which the population size had doubled was recorded each year.
+We considered stocks to have high recovery potential if 75% of simulated trajectories doubled, medium potential if 50-74% of simulations doubled, and low recovery potential if < 50% of simulated trajectories doubled, calculated at 10 and 20 years into the projection.
 For simplicity, we did not incorporate density-dependent effects (e.g., potential population decline as abundance exceeds carrying capacity) or any correlation (either temporally or between fecundity and natural mortality).
 Once a population had doubled, it was considered to have remained at that abundance or greater for the remainder of the projection.
+This means that the metric gave the earliest possible doubling time for each simulation, assuming no future fishing mortality.
 
@@
 Lifetime reproductive success ($R_0$) was calculated for each cohort in which fecundity and natural mortality were available for complete cohorts (i.e., cohorts in which all available age classes are represented).
-It was calculated by using only natural mortality component (FM=0) and with the combined effect of natural mortality and fishing mortality ($FM>0$), respectively.
+For species with a long lifespan, this meant that lifetime reproductive success was more indicative of expectations from earlier in the exploitation history, rather than more recent years.
+
+It was calculated both by using only natural mortality component ($F=0$) and with the combined effect of natural mortality and fishing mortality ($F>0$), respectively.
 This provided an understanding of the reproductive potential from observed stock characteristics alone, and how it changed with fishing pressure.
-This was calculated for each cohort as:
+$R_0$ was calculated for each cohort as:
 
@@
 This formulation ignores any contribution from a plus group, by assuming that the last observed age in the data represents the longevity of the cohort.
-This simplifying assumption will cause a slight underestimation in the means these values, given that the oldest sampled age class is typically younger than the theoretical longevity of the species based on growth (REFERENCE).
+This simplifying assumption will cause a slight values negative bias in the values, given that the oldest sampled age class is typically younger than the theoretical longevity of a given species based on growth (CITE).
 
@@
 
-The generation time was defined as the mean age of the spawners that produced the observed recruits in a cohort ($T_G$).
-A value was calculated for each cohort in which fecundity and natural mortality were available for the complete cohort (i.e., cohorts in which all available age classes are represented).
-As with lifetime reproductive success it was calculated in two ways, using only the natural mortality component ($FM=0$) and using combined effect of natural mortality and fishing mortality ($FM>0$).
+We defined generation time as the mean age of the spawners that produced the observed recruits in a cohort [$T_G$,@caswellMatrixPopulationModels2001].
 

### 2024-12-13 Drafts/Paper_1/04-results.Rmd
Incremental update
Working through Fall updates in hopes I get done before the winter

@@
 
-The overall median population growth rate when excluding the effects of fishing ($\lambda_{FM=0}$) was `r med.lambda.F0`, indicating that there was a latent potential for population growth for these populations of approximately `r med.r.F0`%.
-When the effect of fishing was accounted for, the median population growth rate ($\lambda_{FM>0}$) declined to `r med.lambda.F`, which suggested that the populations in this analysis may have been over-fished by approximately `r -med.r.F`% annually.
-Indeed, $\lambda_{FM>0}$ was below one `r prop.lam.fish.lt.1`% of the time.
-However, infrequent large recruitment events resulted in large estimates of $\lambda_{FM>0}$ for many populations in a few years.
-This led to a skewed distribution of the $\lambda$ estimates, with these large events being an integral component of the population dynamics for these populations (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-bx-other-fig)).
-The mean $\lambda_{FM>0}$ for the populations in this analysis was `r mn.lambda.F` which would suggest there remains scope for population growth even after fishing for most populations, although the mean $\lambda_{FM>0}$ was less than one for `r num.mn.lambda.fish.lt.1` of the `r n.stocks` populations.
-Finally, the mean $\lambda_{FM>0}$ was lower than the median for just `r n.stocks-n.mn.higher.med.fish` of the `r n.stocks` in this analysis.
-The majority of these populations (`r n.nw.ice`) were in the central or NW Atlantic, and this included `r n.cod.low.mn`  of the `r n.cod` Atlantic cod (*G.
+The overall median population growth rate when excluding the effects of fishing ($\lambda_{F=0}$) was `r med.lambda.F0`, which represents a latent capacity for population growth of only `r med.r.F0`% annually.
+Aggregating over years, the population with highest median theoretical population growth rate was Atlantic cod in the Irish Sea (median $\lambda_{F=0}$ = `r max.median.lam.nf`) and the lowest was pollock in the Gulf of Alaska (median $\lambda_{F=0}$ = `r min.median.lam.nf`).
+When the effects of fishing was were accounted for, the overall median population growth rate ($\lambda_{F>0}$) declined to `r med.lambda.F`, which would correspond to overfishing by  `r -med.r.F`% annually.
+The realized range of population growth rates was much narrower, as would be expected from managed stocks, where a typical goal is to maintain stock size at or above a specific biomass reference point [CITE].
+Indeed, median $\lambda_{F>0}$ was below one the majority of the time for `r prop.usually.lt.1.fish`% of the stocks, suggesting that stocks were being managed in a way that essentially eliminated their capacity for abundance increase in more than half of the years in the data.
+However, many of the populations included in our analysis experienced infrequent large recruitment events that resulted in high $\lambda_{F>0}$ estimates (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-bx-other-fig)).
+For example, while Gulf of Alaskan pollock has the lowest median $\lambda_{F=0}$, it's mean $\lambda_{F=0}$ was `r mean.nf.of.min.median.lam.nf`, and when the effects of fishing are included this population had the $8^{th}$ highest mean $\lambda_{F>0}$ (`r mean.fish.of.min.median.lam.nf`) in this analysis.
+Consequently, the overall mean realized growth rate $\lambda_{F>0}$ for the populations in this analysis remained slightly greater than one.
+On average, population growth tended to compensate for declines in other years, maintaining a net positive overall productivity for most of these stocks.
+
+Mean $\lambda_{F>0}$ was lower than the median for just `r n.stocks-n.mn.higher.med.fish` of the `r n.stocks` populations in this analysis, and the mean $\lambda_{F>0}$ was less than one for only `r num.mn.lambda.fish.lt.1` of the `r n.stocks` populations.
+The majority of the populations experiencing these consistent declines (N = `r n.nw.ice`) were in the central or NW Atlantic, and included `r n.cod.low.mn`  of the `r n.cod` Atlantic cod (*G.
 morhua*) populations in this analysis.
 
-There were regional and species specific trends in both $\lambda_{FM=0}$ and $\lambda_{FM>0}$.
+There were regional and species specific trends in both $\lambda_{F=0}$ and $\lambda_{F>0}$.
 Haddock (*M.
-aeglefinus*) and Atlantic cod populations had some of highest variability in $\lambda$, both at the population level and between populations (Figure \@ref(fig:lambda-sd-fig)).
-For these two species, the variability of $\lambda$ within a population declined as you moved from the Eastern Atlantic to the Western Atlantic (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig)).
-The pattern was more pronounced for Atlantic cod, with populations in the eastern Atlantic tending to have relatively low within population variability.
-The two other species with populations found in the NW and NE Atlantic (*C.harengus* and *P.
-virens*) the variability of $\lambda$ between the populations was much lower than for Haddock and Atlantic cod and there were no clear differences between regions for these two species (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig)).
-This was largely due to the within population $\lambda$ variability being lower than the within population variability of Haddock and Atlantic cod populations in the NE Atlantic (Figure \@ref(fig:lambda-bx-6-fig)).
-Two other populations (*A.
-tobianus* and *T.
-esmarkii*) in the North Sea had highly variably $\lambda's$, though notably they were less variable than the Haddock and Atlantic cod $\lambda's$ in this area (Figure \@ref(fig:lambda-bx-other-fig)).
-For the remainder of other populations in this analysis, years in which the value of $\lambda_{FM=0}$ exceeded 1.5 were more rare.
-Exceptions to this included *M.
-merlangus* in the Celtic Sea, *P.
-dentatus* and *S.
-Chrysops* in the NW Atlantic, and the Gulf of Alaska *G.
-chalcogrammus* population in the Pacific Ocean (Figure \@ref(fig:lambda-bx-other-fig)).
+aeglefinus*) and Atlantic cod populations exhibited some of the highest variability in population growth rates, both over time and among stocks, with $\lambda_{F=0}$ values exceeding 2 for multiple years and for multiple populations for both species (Figure \@ref(fig:lambda-bx-6-fig)).
+For these two species, the variability of population growth rate declined as you moved from the eastern Atlantic to the western Atlantic demonstrating that growth rates tended to be more consistent in the eastern as opposed to western Atlantic (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig)).
+The pattern was most pronounced for Atlantic cod, with populations in the eastern Atlantic tending to have relatively low within population variability.
+A comparison between populations found in the western and eastern Atlantic was possible for two other species, Atlantic herring (*C.
+harengus*) and pollock (*P.
+virens*).
+Surprisingly, the variability of $\lambda$ between the Atlantic herring and pollock populations was much lower (Figure \@ref(fig:lambda-bx-6-fig)) than for either haddock or Atlantic cod and there were no clear differences between regions for these two species (Figure \@ref(fig:lambda-sd-fig)).
+Two other populations, sand eel (*A.
+tobianus*) and Norway pout (*T.
+esmarkii*), in the North Sea had highly variably $\lambda's$, though notably less variable than the Haddock and Atlantic cod $\lambda's$ in this area (Figure \@ref(fig:lambda-bx-other-fig)).
+For the remainder of other populations in this analysis, years in which the value of $\lambda_{F=0}$ were elevated (e.g., above $\approx$ 1.5) were more rare.
+Exceptions included whiting (*M.
+merlangus*) in the Celtic Sea, summer flounder (*P.
+dentatus*) and scup (*S.
+Chrysops*) in the western Atlantic, and the Gulf of Alaska pollock (*G.
+chalcogrammus*) population in the Pacific Ocean (Figure \@ref(fig:lambda-bx-other-fig)).
 
@@
 
-Overall, the evidence suggested that negative density dependence was common as both $\lambda_{FM=0}$ and $\lambda_{FM>0}$ increased as abundance declined (Figure \@ref(fig:dd-overall-plt)).
-The strength of density dependence appeared to be more pronounced at low and high abundance levels (i.e., changes in abundance had larger impacts on $\lambda$ when abundance was below $\approx$ 0.4 or above $\approx$ 0.7).
-$\lambda_{FM=0}$ only declined below 1 when the populations approached their maximum observed abundance ($\approx$ `r pa.lam.nf.at.one`%), indicating that there was a latent capacity for population growth in these populations.
-However, when accounting for fishing mortality, $\lambda_{FM>0}$ was below one until the populations were below approximately `r pa.lam.fish.at.one`% of their maximum abundance.
-At lower abundances, the rate of increase in $\lambda_{FM>0}$ was higher than $\lambda_{FM=0}$, likely due to reductions in fishing mortality at low abundance, but overall $\lambda_{FM>0}$ was lower than $\lambda_{FM=0}$, suggesting that some fishing mortality was common even at very low abundance (Figure \@ref(fig:dd-overall-plt)).
+Overall, the data suggested that negative density dependence was common as both $\lambda_{F=0}$ and $\lambda_{F>0}$ increased as abundance declined (Figure \@ref(fig:dd-overall-plt)).
+Changes in the rate of population growth were more pronounced at low and high abundance levels; the relationship from the fitted GAMM was essentially flat when relative abundance ranged between 40-70% of maximum.
+This suggests that there was a surprisingly large range of population abundances that would not be expected to exhibit strong compensatory dynamics.
+The predicted population growth rate excluding the impacts of fishing ($\lambda_{F=0}$) only declined below one when the populations approached their maximum observed abundance ($\gtrsim$ `r pa.lam.nf.at.one`%).
+However, when accounting for fishing mortality ($\lambda_{F>0}$), the modelled relationship dropped below one when the population abundance exceeded approximately `r pa.lam.fish.at.one`% of their maximum abundance.
+At lower abundances, the model estimated population growth rate excluding fishing ($\lambda_{F=0}$) increased more slowly than realized population growth rates ($\lambda_{F>0}$) likely due to reductions in fishing mortality at low abundance.
+However, the fitted values never converged, suggesting that some fishing mortality remained even at very low abundance (Figure \@ref(fig:dd-overall-plt)).
 
-Generally, there was an increase in the variability of the $\lambda$ estimates as abundance declines, largely driven by an increase in the magnitude of the maximum value of $\lambda$ and a small increase in the frequency of low $\lambda$ values (Figure \@ref(fig:dd-overall-plt)).
-For example, values of $\lambda_{FM>0}$ > `r pa.lam.fish.low.bigs` were not observed at abundances > `r 100*pa.big.threshold`% of the maximum (similar trends were observed for $\lambda_{FM=0}$, with only one point being above `r pa.lam.nf.low.bigs` when the abundance was > `r 100*pa.big.threshold`% of the maximum).
-Similarly, the percentage of $\lambda_{FM>0}$ values below `r lam.low.threshold` was `r 100*prop.low.high.abund`% when the proportion of the abundance was >= 0.3, but this increased to `r 100*prop.low.low.abund`% of the data when the proportion of the abundance was below 0.3.
+As expected, there was generally an increase in the variability of the $\lambda$ estimates as abundance declines, largely driven by an increase in the magnitude of the maximum value of $\lambda$ and a small increase in the frequency of low $\lambda$ values (Figure \@ref(fig:dd-overall-plt)).
+While there was a consistent overall pattern, the estimated random effects demonstrated substantial variability among stocks in the strength of negative density dependence.
+For examples, populations in the western Atlantic (particularly Atlantic cod) and Alaska had some of the lowest $\lambda_{F=0}$ estimates at low abundance, while several populations in the North Sea (including Atlatnic cod) had among the highest $\lambda_{F=0}$ estimates at low abundance (Table \@ref(tab:tab-lambdas)).
+Of the `r n.bl.40` populations that had declined below 40% of the maximum abundance, only `r n.low.40.nf` of the populations had $\lambda_{F=0}$ estimates < 1 at 40% of their maximum abundance; when the effects of fishing were included `r n.low.40.nf` of the populations had $\lambda_{F>0}$ estimates below 1 (Table \@ref(tab:tab-lambdas)).
 
-However, these general patterns were highly variable between populations.
-All of the populations included in this analysis had $\lambda_{FM=0}$ estimates > 1 at their lowest observed abundances (Table \@ref(tab:tab-lambdas) and Figure \@ref(fig:dd-nf-stock-plt)).
-Populations in the Northwest Atlantic (particularly Atlantic cod) and Alaska had some of the lowest $\lambda_{FM=0}$ estimates at low abundance, while several populations in the North Sea had among the highest $\lambda_{FM=0}$ estimates at low abundance (Table \@ref(tab:tab-lambdas)).
-Of the `r n.bl.40` populations that had declined below 40% of the maximum abundance, only `r n.low.40.nf` of the populations had $\lambda_{FM=0}$ estimates < 1 at 40% of their maximum abundance; when the effects of fishing were included `r n.low.40.nf` of the populations had $\lambda_{FM>0}$ estimates below 1 (Table \@ref(tab:tab-lambdas)).
-
-For the vast majority of populations the lowest values of both $\lambda_{FM=0}$ (`r n.low.lam.at.max.nf` of `r n.stocks`) and $\lambda_{FM>0}$ (`r n.low.lam.at.max.fish` of `r n.stocks`) were found near the maximum abundance in the time series (Figures \@ref(fig:dd-nf-stock-plt) and \@ref(fig:dd-fish-stock-plt)).
-Atlantic cod in the Northwest Atlantic comprised `r n.cod.lam.not.at.max.nf` of the `r n.stocks - n.low.lam.at.max.nf` populations in which the lowest $\lambda$ was observed below the maximum abundance, the low $\lambda$ occurred at population abundances that were remarkably similar for these Atlantic cod populations (ranging between `r pa.low.cod.min` and `r pa.low.cod.max`).
-For two of the `r n.stocks - n.low.lam.at.max.nf` populations, the lowest $\lambda_{FM=0}$ estimates were less than 0.005 smaller than the estimate at the maximum abundance, for the other four populations the decline in $\lambda_{FM=0}$ from the highest abundance observed was somewhat pronounced, ranging from `r low.4.lam.40.nf` to `r low.lam.40.nf` (Tables \@ref(tab:tab-lambdas) and \@ref(tab:tab-lamda-diffs) and Figures \@ref(fig:dd-nf-stock-plt) and \@ref(fig:dd-fish-stock-plt) ).
-
-## Demographic Parameters
-
-The lifetime reproductive output and generation length were estimated for each cohort in which data were available.
-When excluding fishing mortality, the overall median lifetime reproductive output, (i.e., the number of females produced by one female that survive to reproduce) was `r r0.med` (mean = `r r0.mn`; Figures \@ref(fig:r0-6-plt) and \@ref(fig:r0-other-plt)).
-When the realized fishing mortality was accounted for, the median reproductive output dropped to `r r0.med.fish` (mean = `r r0.mn.fish`), this again highlighted the importance of large reproductive events for survival of these populations and the latent capacity for population growth (Figures \@ref(fig:r0-6-plt) and \@ref(fig:r0-other-plt)).
-For populations which were found across the north Atlantic, the lifetime reproductive output when excluding fishing mortality tended to decline as your move west, this again was most evident for the Atlantic cod populations.
-While the reproductive potential of cohorts within a population could be highly variable, there were no clear temporal trends in the $R_0$ (Figures \@ref(fig:r0-nf-ts-plt) and \@ref(fig:r0-fish-ts-plt)).
-
-The generation lengths tended to become more similar between populations both intra- and inter-specifically when accounting fishing mortality (Figures \@ref(fig:gl-6-plt) and \@ref(fig:gl-other-plt)).
-In addition, the generation length of *C.
-harengus*, generally considered a short lived species, in the Central and NW Atlantic tended to be higher than the generation length of Atlantic cod and haddock, especially for the populations in the NE Atlantic (Figure \@ref(fig:gl-6-plt)).
-There were no obvious patterns in the temporal trends in the generation length (Figures \@ref(fig:gl-nf-ts-plt) and \@ref(fig:gl-fish-ts-plt)).
+The vast majority of populations the lowest values of both $\lambda_{F=0}$ (`r n.low.lam.at.max.nf` of `r n.stocks`) and $\lambda_{F>0}$ (`r n.low.lam.at.max.fish` of `r n.stocks`) were found near the maximum abundance in the time series, this conforms to the expectations of this type of historical reconstruction and population dynamics theory (i.e., negative density dependence; see Supplemental Figures \@ref(fig:dd-nf-stock-plt) and \@ref(fig:dd-fish-stock-plt)).
+However, Atlantic cod in the Northwest Atlantic comprised `r n.cod.lam.not.at.max.nf` of the `r n.stocks - n.low.lam.at.max.nf` populations in which the lowest population growth rates were observed at abundances markedly below the maximum.
+These Atlantic cod populations seemed to have the least compensatory capacity at relative abundances between `r pa.low.cod.min` and `r pa.low.cod.max` even when excluding the impacts of fishing mortality.
+For two of the `r n.stocks - n.low.lam.at.max.nf` populations, the lowest $\lambda_{F=0}$ estimates were less than 0.005 smaller than the estimate at the maximum abundance, indicating extremely similar compensatory capacity over the majority of observed stock sizes.
+The declines in $\lambda_{F=0}$ for the other four populations were more pronounced (Supplemental Figure \@ref(fig:dd-nf-stock-plt)), ranging from `r low.4.lam.40.nf` to `r low.lam.40.nf` (Tables \@ref(tab:tab-lambdas) and \@ref(tab:tab-lamda-diffs)).
 
@@
 
-The recovery potential in the absence of fishing was relatively high for the majority of species (Figure \@ref(fig:dub-time-map)).
-Of the `r n.stocks` populations in this analysis, `r n.dub.10` had a high recovery potential (we define 'high' as at least `r 100*dub.p.high`% of the simulations having experienced a doubling in size) within 10 years, by year 20 this had increased to `r n.dub.20` populations (Figure \@ref(fig:dub-ts)).
+Lifetime reproductive output and generation length were estimated for each cohort in which data were available, population decline would be assured from lifetime reproductive rates consistently below 1.
+When excluding fishing mortality, the overall median lifetime reproductive output, (i.e., the number of females spawners per female spawner) was `r r0.med` (mean = `r r0.mn`; Figure \@ref(fig:r0-6-plt)).
+When realized fishing mortality was accounted for, the median reproductive output dropped to `r r0.med.fish` (mean = `r r0.mn.fish`).
+This difference between the mean and median for stocks experiencing exploitation, again highlighted the importance of large reproductive events to persistence by maintaining the latent capacity for population growth (Figure \@ref(fig:r0-6-plt)).
+For species which were found across the North Atlantic, the lifetime reproductive output when excluding fishing mortality tended to decline from east to west, which again was most evident for the Atlantic cod populations.
+While the reproductive potential of cohorts within a population could be highly variable, there were no clear temporal trends in $R_0$ (Figures \@ref(fig:r0-nf-ts-plt) and \@ref(fig:r0-fish-ts-plt)).
 
-The populations in which recovery potential was low (we define low as < `r 100*dub.p.low`% of the simulations experiencing a doubling in size) exhibited clear regional trends.
-Of the `r n.not.dub.20` populations in this analysis in which the recovery potential was low after 20 years, `r n.alaska.slow` of the populations were in Alaska (`r n.alaska` populations in total), and `r n.nwa.slow` populations in NAFO Regions 2-4 in the NW Atlantic (`r n.nafo.24` populations were in NAFO Regions 2-4).
-This contrasts to only `r n.nea.slow` of the `r n.nea` populations in the NE Atlantic with a low recovery potential within 20 years in the absence of fishing (Figure \@ref(fig:dub-time-map)).
+Generation length (calculated as the mean age of spawners contributing to a recruit cohort) tended to become more similar with fishing pressure included both among stocks and among species (Figures \@ref(fig:gl-6-plt) and \@ref(fig:gl-other-plt)).
+This is an expected outcome of reduced survivorship-to-age.
+However, there were regional and interspecific patterns that were unexpected.
+For example, Atlantic herring is typically considered to be a short-lived species yet its generation length in the Central and western Atlantic tended to be higher than the generation length of Atlantic cod and haddock (especially for the populations in the eastern Atlantic; (Figure \@ref(fig:gl-6-plt)).
+Similar to lifetime reproductive output there were no obvious temporal trends in the generation length among cohorts for the populations in this analysis  (Figures \@ref(fig:gl-nf-ts-plt) and \@ref(fig:gl-fish-ts-plt)).
 
-The recovery potential was influenced both by $\lambda_{FM=0}$ and the variability in $\lambda_{FM=0}$.
-Populations with a median $\lambda_{FM=0} < 1$  had moderate (defined as populations in which 50-75% of the simulations doubled within 20 years) to high (> 75% doubled in size within 20 years) recovery potential whenever the standard deviation in $\lambda$ was greater than approximately 0.4 (Figure \@ref(fig:dub-vs-sd)).
-Populations with a median $\lambda_{FM=0}$ near 1 and with low variability were the populations in which the recovery potential tended to be categorized as low (< 50% of the simulations doubled within 20 years).
+Based on simulated stock trajectories, the recovery potential in the absence of fishing was relatively high for the majority of species (Figure \@ref(fig:dub-time-map)).
+Of the `r n.stocks` populations in this analysis, `r n.dub.10` had at least 75% of the simulations double in size withing 10 years, which increased to `r n.dub.20` populations by 20 years (Figure \@ref(fig:dub-ts)).
+Conversely, there were clear regional trends in stocks with low recovery potential.
+Of the `r n.not.dub.20` populations in this analysis in which < 50% of simulations doubled in size after 20 years, `r n.alaska.slow` were in Alaska and `r n.nwa.slow` in NAFO Regions 2-4 in the western Atlantic.
+This meant that `r prop.slow.alaska`% and `r prop.slow.n24`% of assessed stocks in Alaska and NAFO Regions 2-4, respectively, had low recovery potential.
+This contrasts to only `r n.nea.slow` of the `r n.nea` populations in the eastern Atlantic with a low recovery potential within 20 years in the absence of fishing (Figure \@ref(fig:dub-time-map)).
+
+Recovery potential was intrinsically linked to both the magnitude and variability in annual population growth rates.
+The recovery potential was influenced both b$\lambda_{F=0}$ and the variability in $\lambda_{F=0}$.
+Populations with a median $\lambda_{F=0} < 1$  had moderate (defined as populations in which 50-75% of the simulations doubled within 20 years) to high (> 75% doubled in size within 20 years) recovery potential whenever the standard deviation in $\lambda$ was $\gtrsim$ 0.4 (Figure \@ref(fig:dub-vs-sd)).
+Populations with a median $\lambda_{F=0}$ near 1 and with low variability tended to be stocks with low recovery potential.

### 2024-12-13 Drafts/Paper_1/05-discussion.Rmd
Incremental update
Working through Fall updates in hopes I get done before the winter

@@
 # DISCUSSION {#disin}
+
+@hobdayEcologicalRiskAssessment2011 is a paper using life history for closely related species.
+
+Exploring demographic variability and realized compensatory responses in marine fish populations highlight several instances where stock dynamics do not conform to expected theoretical relationships, which has potentially serious implications for future management.
+Although most stocks exhibited a latent capacity for annual growth, and exhibited evidence for negative density dependence, overall theoretical growth rates in the absence of fishing were surprisingly close to 1, with several stocks having no apparent capacity for abundance increase in the majority of years.
+Quota-based fisheries management strategies often aim for neutral (50%) risk in the probability of population decline when setting harvest advice (ref, ref), so it was not unexpected that realized population growth rates centered around 1.
+
+What was unsettling was how little capacity for increase these stocks seemed to retain when excluding the effects of fishing (i.e., $\lambda_{F=0}$).
+If fishing ceased, future recovery was likely within 20 years whenever the median  $\lambda_{F=0}$ was greater than 1.06 or the standard deviation of lambda was greater than 0.2.
+This applied to only ADD SOMETHING and none of the highest trophic level species.
+Widespread distributions, high egg production per female, and broadcast spawning strategies have all contributed to the impression that marine fishes should have very high potential for annual population growth [(CITE)].
+When environmental variation results in favorable conditions, stocks are anticipated to exhibit high survival, resulting in large recruitment events or higher overall survival [(CITE)].
+While we found indirect evidence of this, in that populations with high variability in  $\lambda_{F=0}$ also had high recovery potential, the magnitude of intra-species variability did not conform to expectations from conventional life-history theory [@kindsvaterTenPrinciplesEvolutionary2016].
+For example, Atlantic herring are a small, relatively short lived, low trophic level pelagic species [CITE].
+Their life history characteristics are considered to result in highly variable population growth potential which should allow them to exploit favorable environmental conditions and increase quickly in abundance [CITE].
+However, the variability of  $\lambda_{F=0}$ for Atlantic herring was much lower than for the higher trophic level and longer lived Atlantic cod and haddock stocks in the same region.
+Furthermore, these three species co-occur in the NE Atlantic [CITE] and the timespan of data collection was similar, suggesting they likely experienced similar variability in oceanographic conditions.
+Other small pelagic populations, such as $A.
+tobianus$ and $T.
+esmarkii$ were characterized by higher  $\lambda_{F=0}$ values, which conforms to theoretical expectations for small, low trophic level species.
+However, these two stocks were found in the North Sea, which appears to be an environment in which high variability in  $\lambda_{F=0}$ is commonplace for harvested stocks.
+In addition, while stocks with a high variability in $\lambda_{F=0}$ do have years with very high population growth, these events happen at irregular intervals, even when populations are at low abundances.
+Contrary to assumptions from typical stock-recruit relationships [CITE], stocks do not necessarily exhibit increased compensatory capacity when at low abundance.
+These data suggest that while most stocks have the capacity for rapid abundance increase, they only do so occasionally even when at low abundance.
+Thus, accounting for both the magnitude and frequency of years with high population growth become key components during the development of fisheries advice, as well as for the development of recovery plans and conservation targets [CITE ref new Fisheries act stuff?
+Precautionary approach stuff?].
+
+NOTE THAT THE BECAUSE WE ASSUMED FISHERY REMOVALS WERE CORRECT COMBINED WITH THE PRODUCITIVTY PARAMETERS HAVING RESULTED IN LAMBDA VALUES THAT ARE 5% LOWER, IF THAT DECLINE IN LAMBDA WAS DUE TO FISHING, OUR PROJECTIONS, GENERATION TIME, AND R0 VALUES WOULD ALL BE SOMEWHAT CONSERVATIVE AS TO GET THAT LOWER LAMBDA VALUE WE ATTRIBUTED THIS TO THE PRODUCTIVITY OF THE SYSTEM BEING LOWER, WHEREAS ATTRIBUTING THAT DIFFERENCE SOLELY TO FISHING WOULD HAVE HAD NO IMPACT ON THE NATURAL MORTALITY OR FECUNDITY
+
+Our best understanding of productivity in these assessed fish stocks suggests that equilibrium theory and general life history characteristics (e.g.
+longevity, trophic level) are poor predictors of population growth rates and recovery potential.
+For stocks that have collapsed or are considered to be at very low abundance, it would be prudent to evaluate lifetime reproductive rates prior to developing harvest advice.
+Numerous stocks in our analysis had no apparent capacity to increase in abundance even in the absence of fishing, which would assure further declines if harvesting continued.
+For example, there were seven populations in which $\lambda_{F=0}$ at 40% of maximum abundance is below 1, five of these populations are found in the NW Atlantic, and five of these are in the Gadus genus (*G.
+morhua* [3] and *G.
+chalcogrammus* [2]).
+These stocks exhibited characteristics much more similar to endangered populations [e.g., several Atlantic salmon Designatable Units in Canada, CITE COSEWIC REPORT], which can also have lifetime reproductive rates < 1 [Gibson refs, CITE], in addition, there was little evidence of negative density dependence for these stocks.
+In our analysis, the most marked example was Atlantic cod in the NW Atlantic.
+We have little understanding of how large these Atlantic cod stocks would have been originally.
+The maximum abundance and thus the magnitude of decline used for our analyses represents the outcome of > 100 years of industrial fishing [Cite Rose book maybe?, others].
+Similar to salmon, extreme abundance decline combined with changes in the environment [Cite cold water and seals] may have resulted in these stocks having little latent capacity for growth or recovery.
+Indeed, it has been suggested that the SGSL cod population will go extinct unless natural mortality declines significantly [CITE Doug’s predator pit stuff], a conclusion supported by our analysis.
+However, the low recovery potential of Atlantic cod was no longer observed as one moves towards the eastern Atlantic, with stocks around mainland Europe all exhibiting high recovery potential.
+As with $G.
+chalcogrammus$, this indicates that regional variability must factor strongly into a species’ ability to withstand fishing pressure.
+Given that variability in population growth potential among stocks could be substantially greater than among species (e.g., compare the variability of $\lambda$ between Atlantic cod and Atlantic herring), life history characteristics and/or trophic level appear to be poor predictors of how marine teleosts will respond to fishing.
+This problem would compound for less data-rich stocks, in that typical assumptions made for data-poor assessments (give examples of assessment methods) would be more likely to lead to inappropriate harvest advice.
+That life history characteristics did not link strongly to expected productivity is extremely concerning, given the need for sustainable fisheries management of data-poor stocks [CITE] to mitigate risks of overfishing across the globe [CITE].
+
+Our life-table reconstruction enables the underlying demographic rates to be estimated for populations with sufficient age-structured data, this provides an opportunity of understanding the dynamics of these populations using concepts developed in conservation biology and ecology.
+In doing so, our optimization procedure assumed that both the estimates of abundance and the fishery removals from the stock assessment are correct.
+Although these assumptions are unlikely to be fully met [CITE], it is important to remember that harvest advice is being derived for these stocks under the same general assumptions.
+Thus, our analyses reveal that current assessments can be based on vastly different understandings of productivity and the potential for population growth for the same species, even when incorporating similar elements to describe population dynamics (e.g., equilibrium theory).
+Our analysis suggests that management advice might be fairly accurate for stocks that aren’t overly variable or those that retain high latent capacity for population increase.
+Low variability would suggest that the stock is not overly influenced by variation in environmental conditions [or that there was little environmental variability in the ecosystem, CITE], while high latent capacity for population increase could indicate the opposite [CITE].
+However, it is not immediately apparent what conditions (environmental, ecological and/or anthropogenic) might be the primary determinants of population growth rates for a given cohort or system.
+Our findings underscore the need for alternative frameworks in which to derive advice, particularly those that incorporate consideration of interspecies relationships and/or environmental conditions under the umbrella of ecosystem-based fishery management [CITE].
+They also underscore the need to collect stock-specific data on marine teleosts, rather than using species-level information from global repositories [e.g., Fishbase, Fishlife, CITE] or assuming values from closely related species to derive harvest advice [CITE].
+
+SOMETHING ABOUT EXPLOITATION HISTORY IF THERE ISN'T ALREADY.
+MISSING CAVIATS (e.g. exploitation history, assumptions related to assuming model fit and fishing is right, )
+
+Looking to the future, …..
+
+---- End Heathers edits that need tidied up---
 
@@
 In general, these populations have latent capacity for growth and, even when accounting for the influence of fishing, these growth rates are very close to 1 in general.
-There is evidence that fisheries stocks are fished in such a way that they will tend to decline until they have declined below 30% of the maximum population size observed, after that most fished populations tend to experience population growth rates above 1.
-Most populations appear to exhibit evidence for negative density dependence, which is in line with general beliefs within fisheries science and population ecology more generally, however there are some populations where the evidence suggests some level of density independence or weak positive density dependence , including most of the *G.
-morhua* populations in NW Atlantic.
-Both variability and median $\lambda_{F=0}$ influence recovery, stocks with a relatively high variability in $\lambda_{F=0}$ had a moderate-high recovery potential even when their median $\lambda_{F=0}$ was below one.
-Effectively recovery of the stocks was likely within 20 years whenever the median $\lambda_{F=0}$ was greater than 1.06 or the standard deviation of lambda was greater than 0.2.
 
@@
 However the $\lambda_{F=0}$ estimates for two neighboring populations in Alaska are much lower, and it is likely that these populations experience much lower fishing pressure because of their low latent capacity for growth.
+
 In contrast, in the NW Atlantic, several *G.
@@
 
-More generally, we observed that populations with high variability in $\lambda_{F=0}$ have a high recovery potential, however, this variability does not necessarily follow on from the expectations of conventional life-history theory (Cite Kingsvader).
+More generally, we observed that populations with high variability in $\lambda_{F=0}$ have a high recovery potential, however, this variability does not necessarily follow on from the expectations of conventional life-history theory [@kindsvaterTenPrinciplesEvolutionary2016].
 For example, *C.

### 2024-12-13 Drafts/Paper_1/08-figures.Rmd
Incremental update
Working through Fall updates in hopes I get done before the winter

@@
 \newpage
-```{r lambda-sd-fig, echo=F, fig.cap="Standard deviation of the $\\lambda$ estimates for each stock, ordered by species, in this analysis. "}
+```{r lambda-sd-fig, echo=F, fig.cap="The average standard deviation of $\\lambda_{F = 0}$  for Atlantic herring (*C.
+harenugs*), Atlantic cod (*G.
+morhua*), haddock (*M.
+aeglefinus*), and pollock (*P.
+virens) stocks in the western Atlantic (NAFO regions 2-5), Northern Altantic (Iceland, Faroe's, and the northeast Arctic), and Eastern Atlantic (Irish, Celtic, North, and Baltic Seas).
+The errorbars represent one standard deviation.
+"}
 knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"))
@@
 \newpage
+```{r r0-6-plt, echo=F, fig.cap="$R_0$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"))
+```
+
+\newpage
+```{r gl-6-plt, echo=F, fig.cap="Generation length estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"))
+```
+
+<!-- Now for the Doubling time -->
+
+\newpage
+```{r dub-time-map, echo=F, fig.cap="Doubling time estimate for each stock with no fishing mortality."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"))
+```
+
+\newpage
+```{r dub-vs-sd, echo=F, fig.cap="The recovery potential (low, moderate, or high) of each stock after 20 years compared to the median $\\lambda_{F=0}$ and the standard deviation of $\\lambda_{F=0}$."}
+knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"))
+```
+
+# Supplemental Figures {-}
+
+\newpage
 ```{r dd-nf-stock-plt, echo=F, fig.cap="Density dependence of $\\lambda_{F=0}$ for each stock in the analysis plotted regionally."}
@@
 knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_fish_stocks_",what.2.tune,".png"))
-```
-
-\newpage
-```{r r0-6-plt, echo=F, fig.cap="$R_0$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"))
 ```
@@
 \newpage
-```{r gl-6-plt, echo=F, fig.cap="Generation length estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"))
-```
-
-\newpage
 ```{r gl-other-plt, echo=F, fig.cap="Generation length estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
@@
 
-<!-- Now for the Doubling time -->
-
-\newpage
-```{r dub-time-map, echo=F, fig.cap="Doubling time estimate for each stock with no fishing mortality."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"))
-```
-
 \newpage
@@
 ```
-
-\newpage
-```{r dub-vs-sd, echo=F, fig.cap="The recovery potential (low, moderate, or high) of each stock after 20 years compared to the median $\\lambda_{F=0}$ and the standard deviation of $\\lambda_{F=0}$."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"))
-```
-
-# Supplemental Figures {-}

### 2024-12-17 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
Working on Discussion update
All comments from the summer are now integrated

@@
 prop.slow.n24 <- round(100*n.nwa.slow/n.nafo.24,digits=0)
+# standard deviation in which rebuilding time was also above the low category
+sd.rebuild.safe <- ceiling(max(lam.sd.p.rec$lam.no.fish.sd[lam.sd.p.rec$prop.cat == "Low"])*100)/100
+lam.rebuild.safe <- ceiling(max(lam.sd.p.rec$lam.no.fish.med[lam.sd.p.rec$prop.cat == "Low"])*100)/100
 
@@
                                         scale_x_log10(name = "Lifetime Reproductive Output")+
-                                       geom_vline(xintercept = 1,linetype='dashed',color='blue')+
+                                       geom_vline(xintercept = 1,linetype='dashed',color='blue')
 

### 2024-12-17 Drafts/Paper_1/03-methods.Rmd
Working on Discussion update
All comments from the summer are now integrated

@@
 $$
-
 Where $a$ is the age, $\alpha$ is the age at first reproduction, $\omega$ is the maximum age, $\lambda$ is the discrete rate of population growth ($\lambda = e^r$), $s_a$ is the survivorship to age $a$, and $f_a$ is the fecundity of individuals of age $a$.
@@
 However, we had to make the simplifying assumption that each kilogram of spawning biomass contributed the same to the total total reproductive output, irrespective of age.
-We calculated the age-specific fecundity ($f_{y,a}$) as the number of offspring produced by each spawner in the population.
+We calculated the age-specific fecundity ($f_{y,a}$) as the number of offspring produced by each spawner in the stock.
 The number of spawners in year $y$ and age class $a$ ($NS_{y,a]$) is the proportion of mature individuals in each age class ($Mat_{y,a}$) multiplied by the number of individuals in each age class:
@@
 <!-- This method does not account for any changes in reproductive success by age, each kilogram of spawning biomass contributes the same to the total total reproductive output, irrespective of their age.
-Finally, the age-specific fecundity ($f_{y,a}$) is calculated as number of offspring produced by each individual in the population.
+Finally, the age-specific fecundity ($f_{y,a}$) is calculated as number of offspring produced by each individual in the stock.
 -->
@@
 Given this method provides separate estimates of $F$ and $M$ it was possible to calculate survival as well as theoretical population growth rates using the $M$ and fecundity ($\lambda_{F=0}$) estimates from the reconstruction.
-We recognize that the age structure in the underlying time series are still influenced by fishing pressure and that populations are at varying size.
+We recognize that the age structure in the underlying time series are still influenced by fishing pressure and that stocks are at varying size.
 This means that ($\lambda_{F=0}$) does not represent the maximum intrinsic rate of abundance increase [e.g., r_max; CITE].
-However, our theoretical annual growth rates in the absence of fishing represent the productivity that the population could have achieved in each specific year, if there had not been a fishery in that year.
+However, our theoretical annual growth rates in the absence of fishing represent the productivity that the stock could have achieved in each specific year, if there had not been a fishery in that year.
 
@@
 One limitation of calculating survivorship-to-age and fecundity-at-age using the archived data in the repository is that it is not straightforward to propagate observation error in each time series of data.
-To ensure that variability did not accumulate into unreasonable predictions for annual population productivity, we fit the Euler-Lotka model using an iterative minimization process, where predicted abundance in the following year:
+To ensure that variability did not accumulate into unreasonable predictions for annual stock productivity, we fit the Euler-Lotka model using an iterative minimization process, where predicted abundance in the following year:
 
@@
 Life table analyses make no assumptions about population regulation and thus do not incorporate a density-dependent relationship between spawners and recruits [@mcallisterUsingDemographicMethods2001].
-However, our estimated productivity parameters could be explored for evidence of density-dependence by modelling each stock’s annual population growth rate against relative population size (expressed as a proportion of maximum abundance) in the same year.
+However, our estimated productivity parameters could be explored for evidence of density-dependence by modelling each stock’s annual population growth rate against relative stock size (expressed as a proportion of maximum abundance) in the same year.
 Negative density dependence is observed when $\lambda$ increases as abundance declines [CITE] which is the type of compensatory response described by typical spawner-recruit relationships (ref, ref).
@@
 Life table analyses make no assumptions about population regulation and thus do not incorporate a density-dependent relationship between spawners and recruits (Reference?).
-However, the data could be explored for evidence of density-dependence by modelling each stock's estimated annual population growth rate against the relative population size (proportion of maximum abundance) that year.
+However, the data could be explored for evidence of density-dependence by modelling each stock's estimated annual population growth rate against the relative stock size (proportion of maximum abundance) that year.
 This was done twice, once using  ($\lambda_{F=0}$) and once using ($\lambda_{F>0}$).
@@
 The annual fecundity and natural mortality values varied considerably for each stock.
-To account for this variability when evaluating recovery potential, we used a simulated population projection.
+To account for this variability when evaluating recovery potential, we used a simulated stock projection.
 For `r n.dt.sims` simulations, we took a random sample of the annual values for fecundity and natural mortality, used the life table reconstruction to estimate $\lambda$, and calculated abundance in the following year.
-Abundance of each stock was projected over `r `n.sim.years` years, and the proportion of the simulations in which the population size had doubled was recorded each year.
+Abundance of each stock was projected over `r `n.sim.years` years, and the proportion of the simulations in which the stock size had doubled was recorded each year.
 We considered stocks to have high recovery potential if 75% of simulated trajectories doubled, medium potential if 50-74% of simulations doubled, and low recovery potential if < 50% of simulated trajectories doubled, calculated at 10 and 20 years into the projection.

### 2024-12-17 Drafts/Paper_1/05-discussion.Rmd
Working on Discussion update
All comments from the summer are now integrated

@@
 Although most stocks exhibited a latent capacity for annual growth, and exhibited evidence for negative density dependence, overall theoretical growth rates in the absence of fishing were surprisingly close to 1, with several stocks having no apparent capacity for abundance increase in the majority of years.
-Quota-based fisheries management strategies often aim for neutral (50%) risk in the probability of population decline when setting harvest advice (ref, ref), so it was not unexpected that realized population growth rates centered around 1.
+Quota-based fisheries management strategies often implicitly or explicitly aim for neutral (50%) risk in the probability of population decline when setting harvest advice [e.g., @marentetteCrossJurisdictionalReviewInternational2020; @dfoScienceAdvicePrecautionary2021], so it was not unexpected that realized population growth rates centered around 1 when the impact of fishing activity was included.
 
 What was unsettling was how little capacity for increase these stocks seemed to retain when excluding the effects of fishing (i.e., $\lambda_{F=0}$).
-If fishing ceased, future recovery was likely within 20 years whenever the median  $\lambda_{F=0}$ was greater than 1.06 or the standard deviation of lambda was greater than 0.2.
-This applied to only ADD SOMETHING and none of the highest trophic level species.
-Widespread distributions, high egg production per female, and broadcast spawning strategies have all contributed to the impression that marine fishes should have very high potential for annual population growth [(CITE)].
-When environmental variation results in favorable conditions, stocks are anticipated to exhibit high survival, resulting in large recruitment events or higher overall survival [(CITE)].
+If fishing ceased, future recovery was likely within 20 years whenever the median  $\lambda_{F=0}$ was $\gtrsim$ lam.rebuild.safe or the standard deviation of lambda was $\gtrsim$ `r sd.rebuild.safe`.
+Widespread distributions, high egg production per female, and broadcast spawning strategies have all contributed to the impression that marine fishes should have very high potential for annual population growth [CITE].
+When environmental variation results in favorable conditions, stocks are anticipated to exhibit high survival, resulting in large recruitment events or higher overall survival [CITE SOME BET HEDGING IN FISH STUFF?].
 While we found indirect evidence of this, in that populations with high variability in  $\lambda_{F=0}$ also had high recovery potential, the magnitude of intra-species variability did not conform to expectations from conventional life-history theory [@kindsvaterTenPrinciplesEvolutionary2016].
@@
 These data suggest that while most stocks have the capacity for rapid abundance increase, they only do so occasionally even when at low abundance.
-Thus, accounting for both the magnitude and frequency of years with high population growth become key components during the development of fisheries advice, as well as for the development of recovery plans and conservation targets [CITE ref new Fisheries act stuff?
-Precautionary approach stuff?].
-
-NOTE THAT THE BECAUSE WE ASSUMED FISHERY REMOVALS WERE CORRECT COMBINED WITH THE PRODUCITIVTY PARAMETERS HAVING RESULTED IN LAMBDA VALUES THAT ARE 5% LOWER, IF THAT DECLINE IN LAMBDA WAS DUE TO FISHING, OUR PROJECTIONS, GENERATION TIME, AND R0 VALUES WOULD ALL BE SOMEWHAT CONSERVATIVE AS TO GET THAT LOWER LAMBDA VALUE WE ATTRIBUTED THIS TO THE PRODUCTIVITY OF THE SYSTEM BEING LOWER, WHEREAS ATTRIBUTING THAT DIFFERENCE SOLELY TO FISHING WOULD HAVE HAD NO IMPACT ON THE NATURAL MORTALITY OR FECUNDITY
+Thus, accounting for both the magnitude and frequency of years with high population growth become key components during the development of fisheries advice, as well as for the development of recovery plans and conservation targets [@marentetteCrossJurisdictionalReviewInternational2020; @dfoScienceAdvicePrecautionary2021].
 
@@
 Numerous stocks in our analysis had no apparent capacity to increase in abundance even in the absence of fishing, which would assure further declines if harvesting continued.
-For example, there were seven populations in which $\lambda_{F=0}$ at 40% of maximum abundance is below 1, five of these populations are found in the NW Atlantic, and five of these are in the Gadus genus (*G.
+For example, there were seven stocks in which $\lambda_{F=0}$ at 40% of maximum abundance is below 1, five of these stocks are found in the NW Atlantic, and five of these are in the Gadus genus (*G.
 morhua* [3] and *G.
 chalcogrammus* [2]).
-These stocks exhibited characteristics much more similar to endangered populations [e.g., several Atlantic salmon Designatable Units in Canada, CITE COSEWIC REPORT], which can also have lifetime reproductive rates < 1 [Gibson refs, CITE], in addition, there was little evidence of negative density dependence for these stocks.
+These stocks exhibited characteristics much more similar to endangered stocks [e.g., several Atlantic salmon Designatable Units in Canada, CITE COSEWIC REPORT], which can also have lifetime reproductive rates < 1 [@ gibsonEquilibriumAnalysesPopulation2009; @bowlbyReductionFitnessLimits2011, CITE], in addition, there was little evidence of negative density dependence for these stocks.
 In our analysis, the most marked example was Atlantic cod in the NW Atlantic.
@@
 Similar to salmon, extreme abundance decline combined with changes in the environment [Cite cold water and seals] may have resulted in these stocks having little latent capacity for growth or recovery.
-Indeed, it has been suggested that the SGSL cod population will go extinct unless natural mortality declines significantly [CITE Doug’s predator pit stuff], a conclusion supported by our analysis.
+Indeed, it has been suggested that the SGSL cod stock will go extinct unless natural mortality declines significantly [CITE Doug’s predator pit stuff], a conclusion supported by our analysis.
 However, the low recovery potential of Atlantic cod was no longer observed as one moves towards the eastern Atlantic, with stocks around mainland Europe all exhibiting high recovery potential.
@@
 chalcogrammus$, this indicates that regional variability must factor strongly into a species’ ability to withstand fishing pressure.
-Given that variability in population growth potential among stocks could be substantially greater than among species (e.g., compare the variability of $\lambda$ between Atlantic cod and Atlantic herring), life history characteristics and/or trophic level appear to be poor predictors of how marine teleosts will respond to fishing.
+Given that variability in stock growth potential among stocks could be substantially greater than among species (e.g., compare the variability of $\lambda$ between Atlantic cod and Atlantic herring), life history characteristics and/or trophic level appear to be poor predictors of how marine teleosts will respond to fishing.
 This problem would compound for less data-rich stocks, in that typical assumptions made for data-poor assessments (give examples of assessment methods) would be more likely to lead to inappropriate harvest advice.
@@
 
-Our life-table reconstruction enables the underlying demographic rates to be estimated for populations with sufficient age-structured data, this provides an opportunity of understanding the dynamics of these populations using concepts developed in conservation biology and ecology.
+Our life-table reconstruction enables the underlying demographic rates to be estimated for stocks with sufficient age-structured data, this provides an opportunity of understanding the dynamics of these stocks using concepts developed in conservation biology and ecology.
 In doing so, our optimization procedure assumed that both the estimates of abundance and the fishery removals from the stock assessment are correct.
@@
 
+There are some limitations to this kind of life table reconstruction.
+Given we use historic data sets, the nature of the population growth are somewhat constrained, for example, when the stock is at the highest abundance in the observed time series, $\lambda$, by definition, has to be $\le$ 1, conversely at the lowest abundance observed $\lambda$ must be $\ge$ 1.
+There are more subtle constraints on the lambda estimates, for example, $\lambda$ must be $\le$ 2 when a stock is at 50% of the maximum abundance, and the minimum value of $\lambda$ similarly constrained by the minimun observed abundance observed in the time series.
+These constraints contributed to an increase in the variability of $lambda$ observed in the analysis.
+In addition we assumed that the fishery removals from the stock assessments were correct and modified the productivity parameters to match the time series from the stock assessment; this resulted in $\lambda$ values that were 5% lower than expected using the initial productivity parameters from the stock assessment.
+If this decline in $\lambda$ was instead attributed to fishing mortality, then the underlying productivity of these systems would have resulted in less conservative projections (DOUBLING TIME...
+KEEP PULLING ON THIS THEAD
+)
+NOTE THAT THE BECAUSE WE ASSUMED FISHERY REMOVALS WERE CORRECT COMBINED WITH THE PRODUCITIVTY PARAMETERS HAVING RESULTED IN LAMBDA VALUES THAT ARE 5% LOWER, IF THAT DECLINE IN LAMBDA WAS DUE TO FISHING, OUR PROJECTIONS, GENERATION TIME, AND R0 VALUES WOULD ALL BE SOMEWHAT CONSERVATIVE AS TO GET THAT LOWER LAMBDA VALUE WE ATTRIBUTED THIS TO THE PRODUCTIVITY OF THE SYSTEM BEING LOWER, WHEREAS ATTRIBUTING THAT DIFFERENCE SOLELY TO FISHING WOULD HAVE HAD NO IMPACT ON THE NATURAL MORTALITY OR FECUNDITY
+
 SOMETHING ABOUT EXPLOITATION HISTORY IF THERE ISN'T ALREADY.
@@
 
-Here we deconstructed the ecological demographics of numerous harvested marine fish populations .
-In general, these populations have latent capacity for growth and, even when accounting for the influence of fishing, these growth rates are very close to 1 in general.
+Here we deconstructed the ecological demographics of numerous harvested marine fishs .
+In general, theses have latent capacity for growth and, even when accounting for the influence of fishing, these growth rates are very close to 1 in general.
 
-For every population in this analysis the $\lambda_{F=0}$ at the minimum observed abundance was estimated to be greater than one; suggesting all of the populations have the potential for some degree of recovery given enough time when there is no fishing mortality.
+For every in this analysis the $\lambda_{F=0}$ at the minimum observed abundance was estimated to be greater than one; suggesting all of thes have the potential for some degree of recovery given enough time when there is no fishing mortality.
 However, there are seven populations in which $\lambda_{F=0}$ at 40% of the maximum abundance is below 1, five of these populations are found in the NW Atlantic, and five of these are in the Gadus genus (*G.

### 2024-12-17 Drafts/Paper_1/index.Rmd
Working on Discussion update
All comments from the summer are now integrated

--- 2024-05-09 Drafts/Paper_1/index.Rmd
@@
 title: |
-   "Life history variability influence on the recovery potential of globally exploited teleosts "
+   "Variability in the recovery potential of globally exploited marine teleosts "
 french_title: "Titre ici (*Nom latin de l'espèce*)"
@@
 abstract: |
-  Here is the abstract text.
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-  Start new paragraphs after a blank line and with 2 spaces indent.
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+  Marine fishes were once believed to be extremely resilient to the effects of fishing.
+However, this view has changed over time, partly due to the collapse and subsequent lack of recovery of several histically important stocks across the globe.
+This has raised questions about the underlying assumptions used in the management of these stocks and the impact of environmental factors on the population dynamics.
+Despite extensive research exploring these challenges, few studies have explored the underlying demographic variability of harvested marine fishes using conservation biology and population ecology perspectives.
+Here we reconstruted the demographics of 77 stocks that are assessed in the north Atlantic and the northeast Pacific Oceans using life-tables.
+This method allowed for the exploration of the demographic variability of these stocks using metrics commonly used in conservation biology (i.e., population growth rates, doubling time, lifetime reproductive success, and generation time).In general, these stocks had a latent capacity for population growth (median $\lambda$ = 1.1) when the effect of fishing was excluded.
+When the impacts of fishing were accounted for the stock mean $\lambda$ was 1.02 overall.
+However, $\lambda$ when accounting for fishing were less than one 57% of the time.
+As a result, for many of the stocks in this analysis, population growth is driven by years with exceptionally high population growth rates.
+For most stocks, as abundance declined, $lambda$ tended to increase and become more variable.
+These general patterns are highly variable among stocks and regionally, with notable differences within Atlantic cod stocks in the northwest (NW) Atlantic.
+These stocks had few large recruitment events and evidence of positive density dependence (i.e., Allee effects or depensation) was relatively strong.
+The recovery potential was relatively high, with simulations indicating that 60 of the stocks would be highly likely to double in size within 20 years in the absence of fishing.
+Stocks with a low recovery potential were constrained to stocks with both a low median $\lambda$ and low variability in the $\lambda$.
+While most stocks exhibited a latent population growth capacity in the absence of fishing, regional and stock specific factors revealed that several stocks lacked this capacity, even in the absence of fishing.
+Knowledge of the underlying demographic parameters for a stock can be used to help sustainably manage the stock and can inform the development of rebuilding plans for stocks that have collapsed.
+Finally, we note that life history characteristics alone were a poor predictor of annual population growth or future recovery potential, with greater variability observed among stocks rather than among species with distinct regions associated with generally higher or generally lower vital rates.
 

### 2024-12-19 Drafts/Paper_1/05-discussion.Rmd
Some discussion text

@@
 Given we use historic data sets, the nature of the population growth are somewhat constrained, for example, when the stock is at the highest abundance in the observed time series, $\lambda$, by definition, has to be $\le$ 1, conversely at the lowest abundance observed $\lambda$ must be $\ge$ 1.
-There are more subtle constraints on the lambda estimates, for example, $\lambda$ must be $\le$ 2 when a stock is at 50% of the maximum abundance, and the minimum value of $\lambda$ similarly constrained by the minimun observed abundance observed in the time series.
-These constraints contributed to an increase in the variability of $lambda$ observed in the analysis.
-In addition we assumed that the fishery removals from the stock assessments were correct and modified the productivity parameters to match the time series from the stock assessment; this resulted in $\lambda$ values that were 5% lower than expected using the initial productivity parameters from the stock assessment.
-If this decline in $\lambda$ was instead attributed to fishing mortality, then the underlying productivity of these systems would have resulted in less conservative projections (DOUBLING TIME...
+There are also more subtle constraints on the lambda estimates, for example, $\lambda$ must be $\le$ 2 when a stock is at 50% of the maximum abundance, and the minimum value of $\lambda$ is similarly constrained by the minimum observed abundance observed in the time series.
+These constraints contributed to an increase in the variability of $lambda$ as abundance declines as observed in the analysis.
+In addition, we assumed that the fishery removals from the stock assessments were correct and modified the productivity parameters to match the time series from the stock assessment; this resulted in $\lambda_{F=0}$ values that were 5% lower than would have been calculated using the initial productivity parameters found in the stock assessments.
+If this decline in $\lambda$ was instead attributed to fishing mortality, then the underlying productivity of these systems would have resulted less conservative projections in the absence of fishing (e.g., the doubling time would have increased)...
 KEEP PULLING ON THIS THEAD
-)
-NOTE THAT THE BECAUSE WE ASSUMED FISHERY REMOVALS WERE CORRECT COMBINED WITH THE PRODUCITIVTY PARAMETERS HAVING RESULTED IN LAMBDA VALUES THAT ARE 5% LOWER, IF THAT DECLINE IN LAMBDA WAS DUE TO FISHING, OUR PROJECTIONS, GENERATION TIME, AND R0 VALUES WOULD ALL BE SOMEWHAT CONSERVATIVE AS TO GET THAT LOWER LAMBDA VALUE WE ATTRIBUTED THIS TO THE PRODUCTIVITY OF THE SYSTEM BEING LOWER, WHEREAS ATTRIBUTING THAT DIFFERENCE SOLELY TO FISHING WOULD HAVE HAD NO IMPACT ON THE NATURAL MORTALITY OR FECUNDITY
 
 SOMETHING ABOUT EXPLOITATION HISTORY IF THERE ISN'T ALREADY.
-MISSING CAVIATS (e.g. exploitation history, assumptions related to assuming model fit and fishing is right, )
+
+WRAP UP PARA...
+While most stocks exhibited a latent population growth capacity in the absence of fishing, regional and stock specific factors revealed that several stocks lacked this capacity, even in the absence of fishing.
+Knowledge of the underlying demographic parameters for a stock can be used to help sustainably manage the stock and can inform the development of rebuilding plans for stocks that have collapsed.
+Finally, we note that life history characteristics alone were a poor predictor of annual population growth or future recovery potential, with greater variability observed among stocks rather than among species with distinct regions associated with generally higher or generally lower vital rates.
 

### 2024-12-20 Drafts/Paper_1/08-figures.Rmd
Christmas Gift
Edits from the summer finally all done. Biggest hang up is the discussion at the moment.

@@
 ```
-
-# Supplemental Figures {-}
-
-\newpage
-```{r dd-nf-stock-plt, echo=F, fig.cap="Density dependence of $\\lambda_{F=0}$ for each stock in the analysis plotted regionally."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"))
-```
-
-\newpage
-```{r dd-fish-stock-plt, echo=F, fig.cap="Density dependence of $\\lambda_{F>0}$ for each stock in the analysis plotted regionally."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_fish_stocks_",what.2.tune,".png"))
-```
-
-\newpage
-```{r r0-other-plt, echo=F, fig.cap="$R_0$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"))
-```
-
-\newpage
-```{r r0-nf-ts-plt, echo=F, fig.cap="$R_0$ estimates for every cohort for each species excluding the effects of fishing."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_nf_",what.2.tune,".png"))
-```
-
-\newpage
-```{r r0-fish-ts-plt, echo=F, fig.cap="$R_0$ estimates for every cohort for each species including the effects of fishing."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_fish_",what.2.tune,".png"))
-```
-
-\newpage
-```{r gl-other-plt, echo=F, fig.cap="Generation length estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"))
-```
-
-\newpage
-```{r gl-nf-ts-plt, echo=F, fig.cap="Generation length estimates for every cohort for each species excluding the effects of fishing."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_nf_",what.2.tune,".png"))
-```
-
-\newpage
-```{r gl-fish-ts-plt, echo=F, fig.cap="Generation length estimates for every cohort for each species including the effects of fishing."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_fish_",what.2.tune,".png"))
-```
-
-\newpage
-```{r dub-ts, echo=F, fig.cap="The number of stocks which doubled in size by a given year with no fishing mortality  The dashed line represents the 77 stocks in the analysis."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_time_series_",what.2.tune,".png"))
-```

### 2024-12-20 Drafts/Paper_1/appendix.Rmd
Christmas Gift
Edits from the summer finally all done. Biggest hang up is the discussion at the moment.

--- 2024-05-21 Drafts/Paper_1/tmp-08-figures.Rmd
@@
----
-output:
-  pdf_document:
-    fig_caption: yes
-    extra_dependencies: float
-linkcolor: blue
-header-includes: \usepackage{float}
-editor_options:
-  chunk_output_type: console
----
+# APPENDIX A {#app:A}
 
-```{r, include=F, echo=F}
-knitr::opts_knit$set(eval.after = "fig.cap")
-knitr::opts_chunk$set(fig.pos = 'H')
-options(knitr.kable.NA = '')
-require(tidyverse)
-options(tinytex.verbose = TRUE)
-
-```
-
-# Figures {-}
-
-```{r lambda-bx-6-fig, echo=F, fig.cap="$\\lambda$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"))
-
-```
-
-\newpage
-```{r lambda-bx-other-fig, echo=F, fig.cap="$\\lambda$ estimates for the remainded of the stocks in this analysis, plotted by the location of the stock.
-The abreviated species name is provided on the x axis."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"))
-
-```
-
-\newpage
-```{r lambda-sd-fig, echo=F, fig.cap="Standard deviation of the $\\lambda$ estimates for each stock, ordered by species, in this analysis. "}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"))
-```
-
-\newpage
-```{r dd-overall-plt, echo=F, fig.cap="Density dependence of $\\lambda$ The top panel shows $\\lambda_{F=0}$ against the proportion of maximum abundance, with a GAM smooth and the GAM estimated 95\\% confidence interval.
-The middle panel shows $\\lambda_{F>0}$ against the proportion of maximum abundance, with a GAM smooth and the GAM estimated 95% confidence interval.
-The bottom panel compares the GAM smooths for $\\lambda_{F=0}$ and $\\lambda_{F>0}$."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_overall_",what.2.tune,".png"))
-```
-
+<!-- f -->
 \newpage
@@
 \newpage
-```{r r0-6-plt, echo=F, fig.cap="$R_0$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"))
-```
-
-\newpage
-```{r r0-other-plt, echo=F, fig.cap="$R_0$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+```{r r0-other-plt, echo=F, fig.cap="$R_0$ estimates for the remainder of the stocks in this analysis, plotted by the location of the stock. The abbreviated species name is provided on the x axis."}
 knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"))
@@
 \newpage
-```{r gl-6-plt, echo=F, fig.cap="Generation length estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
-knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"))
-```
-
-\newpage
-```{r gl-other-plt, echo=F, fig.cap="Generation length estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
+```{r gl-other-plt, echo=F, fig.cap="Generation length estimates for the remainder of the stocks in this analysis, plotted by the location of the stock.
+The abbreviated species name is provided on the x axis."}
 knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"))

### 2024-12-20 Drafts/Paper_1/index.Rmd
Christmas Gift
Edits from the summer finally all done. Biggest hang up is the discussion at the moment.

@@
    highlight: tango
+   number_sections: false
 # ------------

### 2025-01-20 Scripts/Test_for_danielle.Rmd
Code so Danielle can run the tuning sims

--- 2024-12-17 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
@@
 ---
-output: word_document
-editor_options: 
-  chunk_output_type: console
+title: "Untitled"
+author: "David Keith"
+date: "2025-01-20"
+output: html_document
 ---
 
-```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4,include=F,message=F}
-
-if(load.results==F)
+```{r load-libraries-n-data, echo = FALSE, cache = FALSE, message = FALSE, results = 'hide', warning = FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+
+# add other packages here:
+library(dplyr)
+library(readr)
+library(tibble)
+library(csasdown)
+# OK, so using the ICES assessments here's what we get for North Sea cod.
+library(readxl)
+library(tidyverse)
+library(rio)
+library(ggthemes)
+library(cowplot)
+library(gtable)
+library(viridis)
+library(arm)
+library(mgcv)
+library(lme4)
+library(scales)
+library(ggh4x)
+library(gratia)
+theme_set(theme_few(base_size = 14))
+
+# The location of your data
+loc <- 'D:/GitHub/ICM'
+# The parameters for the doubling time simulation
+n.dt.sims <- 1000 # Increase to 1000 for final run, which takes like a full day or something 
+n.sim.years <- 100
+# If we already have the results don't re-run the models or load data we don't need.
+# Note that running the models takes like 4 days to finish!!
+load.results <- T
+# What tunning model are you running or did you run!
+what.2.tune <- 'fec_nm'
+
+#source(paste0(loc,"/Scripts/functions/tuning_sim_fast.R"))
+
+# Download the functions we'll need from github
+funs <- c("https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/simple_Lotka_r.r",
+          #"https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/backwards_project.r",
+          #"https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/forward_project.r",
+          "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/tuning_sim_fast.r"
+)
+  # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
+for(fun in funs) 
 {
-  Stocks <- ASR.long |> 
-                      collapse::fsubset(!is.na(value)) |>
-                      collapse::fgroup_by(Stock, type) |>
-                      collapse::fsummarize(count=length(unique(value))) |>
-                      collapse::fgroup_by(Stock) |>
-                      collapse::fsummarize(types=length(unique(type))) |>
-                      collapse::fsubset(types==5) |>
-                      collapse::fselect(Stock)
-
-  ASR.tmp <- ASR.long 
-  ASR.tmp$age <- as.numeric(ASR.tmp$age)
-  ASR.stocks <- ASR.tmp |> 
-                          collapse::fsubset(Stock %in% Stocks$Stock) |>
-                          collapse::fsubset(!is.na(value)) |>
-                          collapse::roworder(Stock, Year, type, age)
-
-  # print(Stocks)
-  Stocks <- Stocks$Stock
-
-  # Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
-  #Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
-  # Esmarki doesn't work great as it is assessed using a quarterly model.
-  #Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
-  #i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
-  years.tmp <- NULL
-  pnm.tmp <- NULL
-  waa.tmp <- NULL
-  ages.tmp <- NULL
-  rem.tmp <- NULL
-  mx.tmp <- NULL
-  NE.tmp <- NULL
-  vpa.tmp <- NULL
-  am.tmp <- NULL
-  #mr.tmp <- NULL
-  abund.tmp <- NULL
-  full.abund.tmp <- NULL
-  full.rem.tmp <- NULL
-  fs.tmp <- NULL
-  for(i in Stocks)
-  {
-  print(i)
-  ASR.sub <- ASR.long |>
-    collapse::fselect(Year, Stock, type, age, value) |>
-    collapse::fsubset(Stock==i)
-
-    # Dropping the first 7 years as the 8 year olds are all missing
-  if(i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR.sub <- ASR.sub |> collapse::fsubset(Year >= 1972)
-  # maxage <- max(as.numeric(ASR.sub$age[!is.na(ASR.sub$value)]))
-  # maxYear <- max(ASR.sub$Year[!is.na(ASR.sub$value)])
-  # minYear <- min(ASR.sub$Year[!is.na(ASR.sub$value)])
-  # forplot <- ASR.sub[as.numeric(ASR.sub$age) < (maxage+1) & ASR.sub$Year %in% minYear:maxYear,]
-  # 
-  # # summary plots
-  # print(ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
-  #         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
-  #         theme_bw() + 
-  #         ggtitle(i)
-  # )
-
-  age.mat <- ASR.sub |> collapse::fsubset(type=="AM") |> dplyr::rename(AM=value) |> collapse::fselect(-type)
-  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
-  # in case that changes later...
-  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
-  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
-  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
-  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
-  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
-  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0
-
-  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
-  nat.mort <-  ASR.sub |> collapse::fsubset(type=="NM") |> dplyr::rename(NM=value) |> collapse::fselect(-type)
-  abund <- ASR.sub |> collapse::fsubset(type=="Num") |> dplyr::rename(Num=value) |> collapse::fselect(-type)
-  weight.age <- ASR.sub |> collapse::fsubset(type=="WA") |> dplyr::rename(WA=value) |> collapse::fselect(-type)
-  if(i == Stocks[30]) weight.age$WA <- weight.age$WA/1000
-  removals <- ASR.sub |> collapse::fsubset(type=="Catch") |> dplyr::rename(Catch=value) |> collapse::fselect(-type)
-
-  data <- age.mat |>
-    full_join(nat.mort) |>
-    full_join(abund) |>
-    full_join(weight.age) |>
-    full_join(removals)
-
-  # Aahh??  Is this NA dropping useful data, needed to quick fix the age at maturity data...
-  data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
-  data <- data[data$available==T,]
-
-  # Tidy up the data for input...
-  data$prop.nat.mort <- 1-exp(-data$NM)
-  #prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))] <- 1-exp(-prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))])
-
-  rem <- data |> collapse::fgroup_by(Year) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
-  #rem <- data |> dplyr::group_by(Year,.drop=F) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
-
-  # Never run, so not doing anything.
-  # missing_rem<- NULL
-  # if(any(is.na(rem$rem))) 
-  # {
-  #   missing_rem <- unique(data$Year)[which(is.na(rem$rem))]
-  #   rem$rem[is.na(rem$rem)] <- median(rem$rem, na.rm=T)
-  # }
-
-  #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
-  years <- data |> dplyr::pull(Year) |> unique() |> sort()
-
-  N.end <- sum(data[data$Year==max(years),]$Num)
-  vpa.abund <- data |> dplyr::group_by(Year) |> dplyr::summarize(vpa=sum(Num,na.rm=T)) |> pull(vpa)
-
-  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
-  #minage
-  minage <- min(as.numeric(data$age))
-  #maxage
-  maxage <- max(as.numeric(data$age))
-  #recruits
-  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
-  #ssn
-  data$ssn <- data$Num * data$AM
-  #ssb
-  data$ssb <- data$ssn * data$WA #I need to figure out how to line this up with the number of recruits for the right years in the data object.... got it right for the overall r.p.ssb below.
-  #tot.ssb
-  annual <- data |> group_by(Year) |> summarize(tot.ssb = sum(ssb)) |> left_join(annual)
-
-  #tst <- data |> group_by(Year) |> summarize(tot.ssn = sum(ssn)) |> left_join(annual)
-
-  #r.p.ssb This needs to be offset by the age of recruits. So here's my lining this up logic.  For age 0, we get
-  # the recruit and SSB estimates from the same survey, thus these age 0 recruits will have been produced by the SSB in the previous year...
-  # So the R in 1970 were produced by SSB in 1969 when min age =0
-  # If min.age = 1 then R in 1970 is produced by SSB in 1968... and so on.
-  # FIX 1 "Recruit year" = SSB year + min.age + 1 (or min.age +2 as SSB.year is the first column)
-  # Now for RPS there's another wrinkle because of this, because our model is N(1970) = lambda * N(1969) and lambda is made up of lx and mx
-  # so if the recruits show up in 1970, the fecundity term that gets us there (irrespective of the age offset) has to be for 1969, becuase
-  # that gets us to the babies that show up in 1970
-  # FIX 2 So "RPS year, recs.per.age year, and mx year" = SSB year + min.age
-  # I believe this to be correct, but we all need to discuss this to make sure the logic holds.
-  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+2):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage-1)],NA)
-  # recs.per.age
-  data <- left_join(data, annual)
-  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
-  tmp <- NULL
-  for(j in 1:length(years))
-  {
-    tst <- data|> collapse::fsubset(Year == years[j]) |> collapse::fselect(ssb,ssn,Year,age)
-    tst$Year <- tst$Year + minage # We want this to line up the the RPS year, so just adding minage here.
-    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
-    tmp[[j]] <- tst
+  download.file(fun,destfile = basename(fun))
+  source(paste0(getwd(),"/",basename(fun)))
+  file.remove(paste0(getwd(),"/",basename(fun)))
 }
-  # Unpack the list
-  ssb.off <- do.call('rbind',tmp)
-  # And merge it with the data object
-  data <- left_join(data,ssb.off,by=c("Year","age"))
-  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
-  # mx
-  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
-  # No longer dividing by 2 because we should really divide recruits and ssn by 2 to be female only, but that's pointless so we roll along with this.
-  data$mx <- data$recs.per.age/data$ssn.offset # if(grepl("males",i)) 
-  #if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
-  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
-  # Easier to remove the years where we don't have recs.per.age...
-  #data <- data |> collapse::fsubset(Year %in% years[(minage+1):length(years)])
-
-  age.mat <- data |> collapse::fselect("Year", "age", "AM") |> 
-                     pivot_wider(names_from=age, values_from = AM) |> collapse::fselect(-Year)
-  prop.nat.mort <- data |> collapse::fselect("Year", "age", "prop.nat.mort") |> 
-                            pivot_wider(names_from=age, values_from = prop.nat.mort) |> 
-                            collapse::fselect(-Year) |> as.data.frame()
-
-  weight.age <- data |> collapse::fselect("Year", "age", "WA") |> pivot_wider(names_from=age, values_from = WA) |> collapse::fselect(-Year)
-  mx <- data |> collapse::fselect("Year", "age", "mx") |> 
-                 pivot_wider(names_from=age, values_from = mx) |> 
-                 collapse::fselect(-Year) |> as.data.frame()
-  # Get the abundance matrix
-  abund.age <- data |> collapse::fselect("Year", "age", "Num") |> 
-                        pivot_wider(names_from=age, values_from = Num) |> 
-                        collapse::fselect(-Year) |> as.data.frame()
-
-  # Now we can save out the catch and get an instantaneous F
-    data$Catch[is.na(data$Catch)] <- 0
-    data$Exp <- data$Catch/data$Num 
-    # If it is exactly 1 that leads to an Inf, which is annoying, so make it 1.1 and fix it with the rest below
-    data$Exp[data$Exp == 1] <- 1.1
-    # And make this an F
-    data$Fs <- -log(1-data$Exp)
-    if(any(is.na(data$Fs)))
-    {
-      fixers <- which(is.na(data$Fs))
-      print(paste0("Had to replace ",length(fixers), ' exploitation rates for stock ',i))
-      for(f in fixers)
-      {
-        yr <- data$Year[f]
-        fs <- max(data$Fs[data$Year == yr],na.rm=T)
-        data$Fs[f] <- fs
-        data$Exp[f] <- 1-exp(-fs)
-      }
-    }
-
-  full.rems <- data |> collapse::fselect("Year", "age", "Catch") |> pivot_wider(names_from=age, values_from = Catch) |> collapse::fselect(-Year)
-  full.Fs <-  data |> collapse::fselect("Year", "age", "Fs") |> pivot_wider(names_from=age, values_from = Fs) |> collapse::fselect(-Year)
-
-    if(i == "DFO_2J3KL_Gadus_morhua")
-    {
-      age.mat[,8:10] <- 1
-      prop.nat.mort[,8:10] <- prop.nat.mort[,7]
-      weight.age[12:14,9:10] <- weight.age[12:14,8]
-      weight.age[15,10] <- weight.age[15,9]
-      mx[12:16,9:10] <- mx[12:16,8]
-      mx[17,10] <- mx[17,9]
-      full.Fs[12:14,9:10] <- full.Fs[12:14,8]
-      full.Fs[15,10] <- full.Fs[15,9]
-      abund.age[12:14,9:10] <- abund.age[12:14,8]
-      abund.age[15,10] <- abund.age[15,9]
-      # I could calculate, but this will get us to the same place...
-      full.rems[12:14,9:10] <- full.rems[12:14,8]
-      full.rems[15,10] <- full.rems[15,9]
-    }
-
-    if(i == "DFO_4T-Spring_Clupea_harengus")
-    {
-      age.mat[6:7,10] <- 1
-      prop.nat.mort[6:7,10] <- prop.nat.mort[6:7,9]
-      weight.age[6:7,10] <- weight.age[6:7,9]
-      mx[6:9,10] <- mx[6:9,9]
-      full.Fs[6:7,10] <- full.Fs[6:7,9]
-      abund.age[6:7,10] <- abund.age[6:7,9]
-      full.rems[6:7,10] <- full.rems[6:7,9]
-    }
-
-    if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
-    {
-      age.mat[30,8] <- 1
-      prop.nat.mort[30,8] <- prop.nat.mort[30,7]
-      weight.age[30,8] <- weight.age[29,8]
-      mx[30:31,8] <- mx[30:31,9]
-      full.Fs[30,8] <- full.Fs[30,7]
-      abund.age[30,8] <- abund.age[30,7]
-      full.rems[30,8] <- full.rems[30,7]
-    }
-
-    if(i == "ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax")
-    {
-      age.mat[c(14,27,40),5] <- age.mat[1,5]
-      prop.nat.mort[c(14,27,40),5] <- prop.nat.mort[1,5]
-      weight.age[c(14,27,40),5] <- weight.age[c(13,26,39),5]
-      mx[c(14,16,27,29,40,42),5] <- mx[c(14,16,27,29,40,42),6]
-      full.Fs[c(14,27,40),5] <- full.Fs[c(14,27,40),4]
-      abund.age[c(14,27,40),5] <- abund.age[c(14,27,40),4]
-      full.rems[c(14,27,40),5] <- full.rems[c(14,27,40),4]
-    }
-    # Clear out some 0's...
-    if( i == "AFSC_EEBSAI_Limanda_aspera")
-    {
-      mx[5,18] <- mean(unlist(mx[5,c(17,19)]))
-      mx[c(6,8),19] <- mx[c(6,8),18]
-      mx[2:7,20] <- mx[2:7,19] 
-    }
-
-  # I had filled the years with no SSB data to inform them.  instead I'm going to remove those years...
-
-   if(minage >0) 
-  {
-    rm <- -(1:minage)
-    years <- years[rm]
-    prop.nat.mort <- prop.nat.mort[rm,]
-    weight.age <- weight.age[rm,]
-    rem <- rem[rm,]
-    mx <- mx[rm,]
-    vpa.abund <- vpa.abund[rm]
-    age.mat <- age.mat[rm,]
-    abund.age <- abund.age[rm,]
-    full.Fs <- full.Fs[rm,]
-    full.rems <- full.rems[rm,]
-   }
-  #   mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
-  #   names(mx) <- names(mx.fill)
-  #  # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
-  #   mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
-  # }
-
-    years.tmp[[i]] <- years
-    pnm.tmp[[i]] <- prop.nat.mort
-    waa.tmp[[i]] <- weight.age
-    ages.tmp[[i]] <- minage:maxage
-    rem.tmp[[i]] <- rem
-    mx.tmp[[i]] <- mx
-    NE.tmp[[i]] <- N.end
-    vpa.tmp[[i]] <- vpa.abund
-    am.tmp[[i]] <- age.mat
-    #mr.tmp[[i]] <- missing_rem
-    abund.tmp[[i]] <- abund.age
-    fs.tmp[[i]] <- full.Fs
-    full.rem.tmp[[i]] <- full.rems
-  } #end input data loop
-
-  save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,#mr.tmp,
-       am.tmp,Stocks,ASR.stocks,ASR.long,abund.tmp,fs.tmp,full.rem.tmp,
-       file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
-
-  } # end load results
+
 ```
@@
 
-  if(load.results==F)
-  {
   load(file = paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
@@
   for.tune.summary <- NULL
-  for(i in Stocks)
-  {
+  # Danielle this should run the code for Stock #2
+  i <- Stocks[2] 
+  #for(i in Stocks)
+  #{
     years <- years.tmp[[i]]
@@
      for.tune.summary[[i]] <- for.tune.tmp
-  }
-
-  saveRDS(for.tune.summary,paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-  saveRDS(for.tune.all.res,paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
-  # 
+  #}
+
 }# end if load results
@@
 ```
+
+STOP HERE DANIELLE, THE REST OF THIS STUFF IS JUST TAKING MODEL OUTPUT AND PLOTING OR MAKING SECONDARY PRODUCTS FROM THE RESULTS.
 

### 2025-01-20 Scripts/Test_for_danielle.Rmd
tweakers

@@
 
-  for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
-  for.tune.all <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
-
-  load(file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
+  #for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
+  #for.tune.all <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
+
+  #load(file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
   # Get the stocks...
@@
   # saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",what.2.tune,".Rds"))
-  save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
-       file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
-
-  write.csv(meta.sub, paste0(loc,"/Data/metadata_no_age_corection.csv"))
+  #save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
+  #     file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
+
+  #write.csv(meta.sub, paste0(loc,"/Data/metadata_no_age_corection.csv"))
 } # end if load results
@@
 ```{r clean-up-and-stats,include=F,echo=F,message=F,warning=F}
-load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
-for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
+#load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
+#for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 20,base_height = 10)
+##save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 20,base_height = 10)
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"),new.lam.plt.others,base_width = 20,base_height = 10)
+##save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"),new.lam.plt.others,base_width = 20,base_height = 10)
 
@@
 # 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 10)
+# #save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 10)
 #
@@
                                               xlab("") + ylab("Standard devation (Lambda)") + theme(legend.title = element_blank())
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 6)
+##save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 6)
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_overall_",what.2.tune,".png"),dd.overall.combo,base_width = 10,base_height = 10)
+##save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_overall_",what.2.tune,".png"),dd.overall.combo,base_width = 10,base_height = 10)
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"),dd.stocks.nf.plt,base_width = 10,base_height = 10)
+##save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"),dd.stocks.nf.plt,base_width = 10,base_height = 10)
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_fish_stocks_",what.2.tune,".png"),dd.stocks.fish.plt,base_width = 10,base_height = 10)
+#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_fish_stocks_",what.2.tune,".png"),dd.stocks.fish.plt,base_width = 10,base_height = 10)
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"),r0.boxplt.6,base_width = 20,base_height = 10)
+#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"),r0.boxplt.6,base_width = 20,base_height = 10)
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"),r0.boxplot.others,base_width = 20,base_height = 10)
+#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"),r0.boxplot.others,base_width = 20,base_height = 10)
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_nf_",what.2.tune,".png"),r0.heatmap,base_width = 20,base_height = 17)
+#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_nf_",what.2.tune,".png"),r0.heatmap,base_width = 20,base_height = 17)
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_fish_",what.2.tune,".png"),r0.heatmap.fish,base_width = 20,base_height = 17)
+#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_fish_",what.2.tune,".png"),r0.heatmap.fish,base_width = 20,base_height = 17)
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"),gen.boxplt.6,base_width = 20,base_height = 10)
+#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"),gen.boxplt.6,base_width = 20,base_height = 10)
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"),gen.boxplt.others,base_width = 20,base_height = 10)
+#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"),gen.boxplt.others,base_width = 20,base_height = 10)
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_nf_",what.2.tune,".png"),gen.heatmap,base_width = 15,base_height = 10)
+#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_nf_",what.2.tune,".png"),gen.heatmap,base_width = 15,base_height = 10)
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_fish_",what.2.tune,".png"),gen.heatmap.fish,base_width = 15,base_height = 10)
+#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_fish_",what.2.tune,".png"),gen.heatmap.fish,base_width = 15,base_height = 10)
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"),dub.heatmap,base_width = 20,base_height = 20)
+#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"),dub.heatmap,base_width = 20,base_height = 20)
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_time_series_",what.2.tune,".png"),dub.ts.plt,base_width = 10,base_height = 10)
+#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_time_series_",what.2.tune,".png"),dub.ts.plt,base_width = 10,base_height = 10)
 
@@
 
-save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"),p3,base_width = 11,base_height = 15)
+#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"),p3,base_width = 11,base_height = 15)
 
@@
 # 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_sp6_",what.2.tune,".png"),dub.heatmap.sp6,base_width = 20,base_height = 17)
+# #save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_sp6_",what.2.tune,".png"),dub.heatmap.sp6,base_width = 20,base_height = 17)
 # 
@@
 # #lambda.ts.plt
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_timeseries_6_",what.2.tune,".png"),lambda.ts.plt,base_width = 12,base_height = 10)
+# #save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_timeseries_6_",what.2.tune,".png"),lambda.ts.plt,base_width = 12,base_height = 10)
 # 
@@
 #                             facet_wrap(~G.Species,scales='free_y') 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_by_decade_6_",what.2.tune,".png"),lambda.dec.plt,base_width = 12,base_height = 12)
+# #save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_by_decade_6_",what.2.tune,".png"),lambda.dec.plt,base_width = 12,base_height = 12)
 # 
@@
 # 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_no_fishing_6_",what.2.tune,".png"),lambda.plt,base_width = 12,base_height = 10)
+# #save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_no_fishing_6_",what.2.tune,".png"),lambda.plt,base_width = 12,base_height = 10)
 # 
@@
 # 
-# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_with_fishing_6_",what.2.tune,".png"),lambda.plt.fish,base_width = 12,base_height = 10)
+# #save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_with_fishing_6_",what.2.tune,".png"),lambda.plt.fish,base_width = 12,base_height = 10)
 # 
@@
 # 
-# save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_6.png",r0.ts.plt,base_width = 30,base_height = 12)
+# #save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_6.png",r0.ts.plt,base_width = 30,base_height = 12)
 # 
@@
 # gen.ts.plt
-# save_plot("D:/Github/ICM/Figures/tuned/Gen_time_series_6.png",gen.ts.plt,base_width = 20,base_height = 12)
+# #save_plot("D:/Github/ICM/Figures/tuned/Gen_time_series_6.png",gen.ts.plt,base_width = 20,base_height = 12)
 
@@
 #                             theme(axis.text.x = element_text(angle =45,hjust=1))
-# save_plot("D:/Github/ICM/Figures/tuned/R0_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
+# #save_plot("D:/Github/ICM/Figures/tuned/R0_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
 # 
@@
 # cod.r0.ts.plt
-# #save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
+# ##save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)
 # 
@@
 #                                    
-# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_species.png",bycatch.plt,base_width = 8,base_height = 8)
+# #save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_species.png",bycatch.plt,base_width = 8,base_height = 8)
 #                                    
@@
 #                                                                               
-# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_cod_stock.png",bycatch.plt.cod,base_width = 8,base_height = 8)
+# #save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_cod_stock.png",bycatch.plt.cod,base_width = 8,base_height = 8)
 # 

### 2025-02-03 Scripts/ICM_map.R
Create ICM_map.R

@@ -1,0 +1,163 @@
+# Map for ICM
+
+require(sf)
+require(tidyverse)
+require(ggplot2)
+require(rnaturalearth)
+require(ggplot2)
+
+stocks <- read.csv("C:/users/keyserf/Documents/Github/ICM-Dave/Data/metadata.csv")
+world <- ne_countries(scale = "large", returnclass = "sf")
+ggplot() + geom_sf(data=world) + coord_sf(expand=F)
+
+unique(stocks$Area.long)
+
+bering <- c(60.60575, -169.41152)
+alaska <- c(58.58383, -146.74756)
+GB <- c(41.58437, -67.25976)
+NL <- c(45.87445, -58.24261)
+north <- c(56.33245, 3.46180)
+celtic <- c(49.11854, -8.31070)
+baltic <- c(58.49575, 20.07792)
+faroe <- c(61.84574, -7.63399)
+ice <- c(63.35810, -11.95852)
+irish <- c(53.83017, -5.28181)
+biscay <- c(45.49964, -3.48611)
+maine <- c(43.30045, -68.46818)
+us <- c(37.88852, -70.45552)
+arctic <- c(72.13541, -2.38604)
+source("C:/Users/keyserf/Documents/Github/Assessment_fns/Maps/github_spatial_import.R")
+nafo <- github_spatial_import("NAFO", "Divisions.zip")
+ggplot() + geom_sf(data=nafo, aes(fill=Division))
+
+nafo_sub <- nafo[nafo$Division %in% c("4T", "5Y", "5Z"),]
+nafo_sub <- nafo_sub %>% group_by(Division) %>%
+  summarize() %>%
+  st_centroid()
+nafo_sub$lon <- st_coordinates(nafo_sub)[,1]
+nafo_sub$lat <- st_coordinates(nafo_sub)[,2]
+
+coords <- data.frame(Area.long = unique(stocks$Area.long),
+           lat = c(bering[1],
+                   bering[1],
+                   bering[1],
+                   alaska[1],
+                   GB[1],
+                   NL[1],
+                   NL[1],
+                   arctic[1],
+                   north[1],
+                   celtic[1],
+                   baltic[1],
+                   ice[1],
+                   ice[1],
+                   irish[1],
+                   celtic[1],
+                   biscay[1],
+                   GB[1],
+                   GB[1],
+                   GB[1],
+                   GB[1]),
+           lon = c(bering[1],
+                   bering[1],
+                   bering[1],
[…]

### 2025-02-03 Scripts/ICM_map.R
Update ICM_map.R

@@ -113,6 +113,16 @@ locs <- stocks %>% group_by(ID,lat, lon) %>%
 # locs %>% group_by(ID) %>%
 #   summarize(sum(nstocks))
 
+stocks$lambda_cod_var <- NA
+stocks$lambda_cod_var[stocks$ID %in% c(6,7,8,10)] <- "C"
+stocks$lambda_had_var <- NA
+stocks$lambda_had_var[stocks$ID %in% c(6,7,10)] <- "H"
+stocks$low_doubling_time <- NA
+stocks$low_doubling_time[stocks$Area.long %in% c("Gulf of Alaska", "NFLD", "NAFO 4T")] <- "slow"
+st_geometry(stocks) <- NULL
+
+locs <-  left_join(locs, unique(dplyr::select(stocks, ID, lambda_cod_var, lambda_had_var, low_doubling_time)))
+
 cols <- c('#d73027','#fc8d59','#fee090','#e0f3f8','#91bfdb','#4575b4')
 names(cols) <- sort(unique(locs$Order))
 require(magick)
@@ -121,6 +131,9 @@ for (i in 1:11){
   barfig[[i]] <- magick::image_graph(width = 50, height = 50, res = 72, bg="transparent")
   print(ggplot() + geom_bar(data=locs[locs$ID==i,], aes(x=1, y=nstocks),
                       position="stack", stat="identity") +
+          geom_text(data=locs[locs$ID==i,], aes(x=1, y=Inf, label=low_doubling_time), vjust=1)+
+          geom_text(data=locs[locs$ID==i,], aes(x=-Inf, y=Inf, label=lambda_cod_var), vjust=1, hjust=-1.5)+
+          geom_text(data=locs[locs$ID==i,], aes(x=Inf, y=Inf, label=lambda_had_var), vjust=1, hjust=2)+
     #scale_fill_manual(values=cols, guide=F) +
     ylim(0,15)+ # take this lim from the locs summary above
     xlab("") + ylab("") +

### 2025-02-03 Drafts/Paper_1/01-analysis.Rmd

--- 2024-04-09 Scripts/Paper_1.Rmd
@@
 
+  } # end load results
 ```
@@
 
+  if(load.results==F)
+  {
   load(file = paste0(loc,"/Results/model_inputs_all_ages.Rdata"))
@@
      fast.for.tune <- fast.tunes(years,
-                           tuner='fec_nm',
+                             tuner=what.2.tune,
                              step.size = ss.size, 
                              abund.ts = all.abund,
-                           ages=ages,
+                             ages=0:max(ages),
                              nm = -(log(1-prop.nat.mort)),
@@
   #saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_fm.Rds")
-saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_fec_nm.Rds")
-saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_fec_nm.Rds")
-#
+  saveRDS(for.tune.summary,paste0(loc,"/Results/forwards_fully_tuned_summary_",what.2.tune,".Rds"))
+  saveRDS(for.tune.all.res,paste0(loc,"/Results/forwards_fully_tuned_all_res_",what.2.tune,".Rds"))
+  # 
+}# end if load results
 
@@
 
-```{r paper-other-metrics-and-metadata}
-
+```{r paper-other-metrics-and-metadata,echo=F,include=F,warning=F,message=F}
+
+if(load.results==F)
+{
   # We are now looking at everything, lifetime reproductive success
-model <- "fec_nm"
-for.tune.summary <- readRDS(paste0("D:/Github/ICM/Results/forwards_fully_tuned_summary_",model,".Rds"))
-for.tune.all <- readRDS(paste0("D:/Github/ICM/Results/forwards_fully_tuned_all_res_",model,".Rds"))
+
+  for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_",what.2.tune,".Rds"))
+  for.tune.all <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_all_res_",what.2.tune,".Rds"))
 
@@
   pop.dam <- data.frame(pop.dam)
-# saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",model,".Rds"))
-# saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",model,".Rds"))
-# saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",model,".Rds"))
+  # saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",what.2.tune,".Rds"))
+  # saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",what.2.tune,".Rds"))
+  # saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",what.2.tune,".Rds"))
   save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
-     file=paste0("D:/Github/ICM/Results/all_cleaned_forward_tune_summaries_",model,".Rdata"))
-
-write.csv(meta.sub, "D:/Github/ICM/Data/metadata.csv")
-
+       file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_",what.2.tune,".Rdata"))
+
+  write.csv(meta.sub, paste0(loc,"/Data/metadata.csv"))
+} # end if load results
 ```
 
-```{r simp-figs}
-theme_set(theme_few(base_size = 14))
-model <- 'fec_nm'
-load(file=paste0("D:/Github/ICM/Results/all_cleaned_forward_tune_summaries_",model,".Rdata"))
+```{r simp-figs,include=F,echo=F,message=F,warning=F}
+load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_",what.2.tune,".Rdata"))
 pop.dam <- data.frame(pop.dam)
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/lambda_no_fishing_6.png",lambda.plt,base_width = 12,base_height = 10)
+save_plot(paste0(loc,"/Figures/tuned/lambda_no_fishing_6_",what.2.tune,".png"),lambda.plt,base_width = 12,base_height = 10)
 
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/lambda_with_fishing_6.png",lambda.plt.fish,base_width = 12,base_height = 10)
+save_plot(paste0(loc,"/Figures/tuned/lambda_with_fishing_6_",what.2.tune,".png"),lambda.plt.fish,base_width = 12,base_height = 10)
 
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap_by_sp6.png",dub.heatmap.sp6,base_width = 20,base_height = 17)
+save_plot(paste0(loc,"/Figures/tuned/Doubling_time_heatmap_by_sp6_",what.2.tune,".png"),dub.heatmap.sp6,base_width = 20,base_height = 17)
 
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/GL_boxplot_no_fish_6_species.png",gen.boxplt,base_width = 12,base_height = 10)
+save_plot(paste0(loc,"/Figures/tuned/GL_boxplot_no_fish_6_species_",what.2.tune,".png"),gen.boxplt,base_width = 12,base_height = 10)
 
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/R0_boxplot_no_fish_6_species.png",r0.boxplt,base_width = 12,base_height = 10)
+save_plot(paste0(loc,"/Figures/tuned/R0_boxplot_no_fish_6_species_",what.2.tune,".png"),r0.boxplt,base_width = 12,base_height = 10)
 
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap_by_order.png",dub.heatmap,base_width = 20,base_height = 20)
+save_plot(paste0(loc,"/Figures/tuned/Doubling_time_heatmap_by_order_",what.2.tune,".png"),dub.heatmap,base_width = 20,base_height = 20)
 
@@
 #lambda.ts.plt
-save_plot("D:/Github/ICM/Figures/tuned/lambda_timeseries_6.png",lambda.ts.plt,base_width = 12,base_height = 10)
+save_plot(paste0(loc,"/Figures/tuned/lambda_timeseries_6_",what.2.tune,".png"),lambda.ts.plt,base_width = 12,base_height = 10)
 
@@
                             facet_wrap(~G.Species,scales='free_y') 
-save_plot("D:/Github/ICM/Figures/tuned/lambda_by_decade_6.png",lambda.dec.plt,base_width = 12,base_height = 12)
+save_plot(paste0(loc,"/Figures/tuned/lambda_by_decade_6_",what.2.tune,".png"),lambda.dec.plt,base_width = 12,base_height = 12)
 
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/gen_heatmap.png",gen.heatmap,base_width = 20,base_height = 17)
+save_plot(paste0(loc,"/Figures/tuned/gen_heatmap_",what.2.tune,".png"),gen.heatmap,base_width = 20,base_height = 17)
 
@@
 
-save_plot("D:/Github/ICM/Figures/tuned/r0_heatmap.png",r0.heatmap,base_width = 20,base_height = 17)
+save_plot(paste0(loc,"/Figures/tuned/r0_heatmap_",what.2.tune,".png"),r0.heatmap,base_width = 20,base_height = 17)
 

### 2025-02-03 Drafts/Paper_1/02-intro.Rmd

@@
 
-Marine fishes were once believed to be essentially inexhaustible and thus extremely resilient to the effects of fishing [@mcintoshFisheriesInterNationalCouncil1919a].
-However, high profile collapses of large fisheries and a subsequent lack of rebuilding (cite, cite) have fundamentally challenged this perception.
+Marine fishes were once believed to be essentially inexhaustible and thus extremely resilient to the effects of fishing [@mcintoshFisheriesInterNationalCouncil1919a; @nielsenEvolutionFisheriesManagement1976].
+However, high profile collapses of large fisheries and a subsequent lack of rebuilding [@hutchingsCollapseRecoveryMarine2000; @frankAlleeEffectsCompensatory2000; @myersMaximumPopulationGrowth1997] have fundamentally challenged this perception.
 The assumption of resilience originated from early theoretical population dynamics modeling [e.g., @verhulstNoticeLoiQue1838] that culminated in the development of modern fisheries science, largely built around the concept of maximum sustainable yield [MSY, @rickerStockRecruitment1954; @schaeferAspectsDynamicsPopulations1954; @bevertonDynamicsExploitedFish1957].
-From its inception, MSY was controversial [@finleyAllFishSea2019; @larkinEpitaphConceptMaximum197], yet the theoretical underpinning in equilibrium concepts and the associated idea that annual reproductive output and/or juvenile survival rates increase as abundance declines (implying harvesting activity will increase the per capita productivity of a population) persisted.
-The vast majority of modern assessments incorporate a stock-recruit function (cite, cite) making compensatory dynamics a foundational assumption about the life history of a species.
-Such fisheries assessments implicitly assume that lifetime reproductive rates in the absence of fishing would be expected to be greater than one (Myers cite, cite) and that even heavily-exploited fish populations retain a latent capacity for increase (cite, cite).
-Although MSY and equilibrium concepts are relatively simple and intuitive, and provide a means of developing tractable mechanistic models, questions remain regarding the applicability of these concepts and whether they adequately reflect the reality of the system being modeled [[@wormRebuildingGlobalFisheries2009; cite cite], particularly for species with markedly different life history characteristics (cite, cite).
+Despite long standing concerns regarding the applicability of MSY [@finleyAllFishSea2019; @larkinEpitaphConceptMaximum1977], its theoretical underpinning in equilibrium concepts and the associated idea that annual reproductive output and/or juvenile survival rates increase as abundance declines persisted along with the implication that harvesting activity will increase the per capita productivity of a stock [@schaeferAspectsDynamicsPopulations1954].
+Most modern assessments incorporate a stock-recruit function [@rickerStockRecruitment1954; @bevertonDynamicsExploitedFish1957; @hilbornQuantitativeFisheriesStock1992; @subbeyModellingForecastingStock2014] making compensatory dynamics a foundational assumption about the life history of a species.
+Such fisheries assessments implicitly assume that lifetime reproductive rates in the absence of fishing would be expected to be greater than one [@hilbornQuantitativeFisheriesStock1992; @myersPopulationDynamicsExploited1995] and that even heavily-exploited fish stocks retain a latent capacity for increase [maceRelationshipsCommonBiological1994].
+Although MSY and equilibrium concepts are relatively straightforward, intuitive, and provide a means of developing tractable mechanistic models, questions remain regarding their applicability [@finleyAllFishSea2019; @larkinEpitaphConceptMaximum1977].
+There are concerns about whether they accurately reflect the the system being modeled [@hilbornQuantitativeFisheriesStock1992; paulyPrimaryProductionRequired1995; @wormRebuildingGlobalFisheries2009], particularly for species with markedly different life history characteristics [hilbornFisheriesInducedChangesGrowth2008].
 
-Life history characteristics are now considered indicative of a species’ compensatory capacity (cite, cite) and are increasingly used within data-limited assessment approaches to provide management advice (cite).
-Theory suggests that small fishes, characterized by numerous offspring, rapid growth, early maturity and short lifespans, should have greater compensatory capacity, greater resilience to environmental variability and consequently, be better able to withstand fishing pressure [@kindsvaterTenPrinciplesEvolutionary2016; cite, cite].
-Conversely, life histories characterized by longer lifespans and later maturity, or those with lower per-capita reproductive output are considered less resilient (cite).
-Furthermore, closely related species are anticipated to be more similar than distantly related species owing to a shared evolutionary history (Thorson fishlife), implying less heterogeneity among populations of a single species than among closely-related species.
-There is a general impression that forage fishes or populations at lower trophic levels are better able to take advantage of favorable environmental conditions and grow more quickly, particularly from low abundance (cite, cite).
+Life history characteristics are now considered indicative of a species’ compensatory capacity [@myersStockRecruitmentGeneralizations2001; @roseCompensatoryDensityDependence2001; @winemillerLifeHistoryStrategies2005] and are increasingly used within data-limited assessment approaches to provide management advice [@martellSimpleMethodEstimating2013; @pedersenStochasticSurplusProduction2017] .
+Theory suggests that small fishes, characterized by numerous offspring, rapid growth, early maturity and short lifespans, should have greater compensatory capacity, greater resilience to environmental variability and consequently, be better able to withstand fishing pressure [@kindsvaterTenPrinciplesEvolutionary2016; @lawFishingSelectionPhenotypic2000].
+Conversely, life histories characterized by longer lifespans and later maturity, or those with lower per-capita reproductive output are considered less resilient [@winemillerLifeHistoryStrategies2005].
+Furthermore, the life history traits of closely related species are anticipated to be more similar than those distantly related species owing to a shared evolutionary history [@thorsonPredictingRecruitmentDensity2020].
+This implies there should be less heterogeneity in the productivity among stocks of a single species than among closely-related species.
+There is a general impression that forage fishes or stocks at lower trophic levels are better able to take advantage of favorable environmental conditions and grow more quickly, particularly from low abundance [@essingtonFishingMarineFood2006].
 This resilience should manifest as a high latent capacity for population growth in the absence of fishing, as well as substantial variability in realized population growth rates among years.
-Dramatic increases in eulecan (FIND OTHER EXAMPLES) following years of particularly low abundance have provided empirical evidence of high compensatory capacity in forage fishes (cites).
 However, it remains unclear if correlated and compounding ecological and environmental processes (e.g.
-climate change effects, predatory prey dynamics) can largely obscure the importance of life history on realized productivity, making evolutionary history and life history characteristics a weak foundation for data-poor assessment in light of our changing oceans.
+climate change effects, predator-prey dynamics) can largely obscure the importance of life history on realized productivity, making evolutionary history and life history characteristics a weak foundation for data-poor assessment in light of our changing oceans.
 
-Stock assessment data from harvested marine telosts provide a unique opportunity to explore demographic variability and realized compensatory responses from a conservation biology or population ecology perspective.
-The long assessment history of these populations means both that their life history characteristics are well-known and that it is possible to quantify realized variability in survival and reproductive output, while accounting for the influence of fisheries.
-We based our analyses on a database containing age specific abundance information for 77 populations in the north Atlantic and the northeast Pacific Oceans [@charbonneauAgestructuredmarinefishdatabase2022].
-By constructing life tables from abundance at age and catch at age data, we calculated common demographic metrics, including  annual population growth rates (cite), doubling time (cite), lifetime reproductive success (cite), and generation time (cite).
-Comparing the strength and magnitude of variability in realized productivity among species with different life histories as well as among populations of the same species yielded unexpected insights.
-Our results have implications for sustainable management of these exploited marine teleosts and could be used inform future management actions for populations that have collapsed.
+Stock assessment data from harvested marine telosts provide a unique opportunity to explore demographic variability and realized compensatory responses.
+The long assessment history of these stocks means that their life history characteristics are well-known and that it is possible to quantify realized variability in survival and reproductive output, while accounting the impact of fishery removals.
+We based our analyses on 77 marine fish stocks from a database of age-specific data [@charbonneauAgestructuredmarinefishdatabase2022].
+By constructing life tables from abundance-at-age and catch-at-age data, we calculated common demographic metrics, including  annual population growth rates, doubling time, lifetime reproductive success, and generation time [@caswellMatrixPopulationModels2001].
+Comparing the strength and magnitude of variability in realized productivity among species with different life histories as well as among stocks of the same species yielded unexpected insights.
+Our results have implications for sustainable management of these exploited marine teleosts and could be used to inform future management actions for stocks that have collapsed.
 More broadly, our results challenged longstanding ideas on the applicability of equilibrium theory, life history theory, and compensatory dynamics to explain expected productivity in fishes.

### 2025-02-03 Drafts/Paper_1/03-methods.Rmd

@@
 We calculated the age-specific fecundity ($f_{y,a}$) as the number of offspring produced by each spawner in the stock.
-The number of spawners in year $y$ and age class $a$ ($NS_{y,a]$) is the proportion of mature individuals in each age class ($Mat_{y,a}$) multiplied by the number of individuals in each age class:
+The number of spawners in year $y$ and age class $a$ ($NS_{y,a}$) is the proportion of mature individuals in each age class ($Mat_{y,a}$) multiplied by the number of individuals in each age class:
 

### 2025-02-03 Drafts/Paper_1/04-results.Rmd

@@
 When the effects of fishing was were accounted for, the overall median population growth rate ($\lambda_{F>0}$) declined to `r med.lambda.F`, which would correspond to overfishing by  `r -med.r.F`% annually.
-The realized range of population growth rates was much narrower, as would be expected from managed stocks, where a typical goal is to maintain stock size at or above a specific biomass reference point [CITE].
+The realized range of population growth rates was much narrower, as would be expected from managed stocks, where a typical goal is to maintain stock size at or above a specific biomass reference point [@marentetteCrossJurisdictionalReviewInternational2020].
 Indeed, median $\lambda_{F>0}$ was below one the majority of the time for `r prop.usually.lt.1.fish`% of the stocks, suggesting that stocks were being managed in a way that essentially eliminated their capacity for abundance increase in more than half of the years in the data.
@@
 Changes in the rate of population growth were more pronounced at low and high abundance levels; the relationship from the fitted GAMM was essentially flat when relative abundance ranged between 40-70% of maximum.
-This suggests that there was a surprisingly large range of population abundances that would not be expected to exhibit strong compensatory dynamics.
-The predicted population growth rate excluding the impacts of fishing ($\lambda_{F=0}$) only declined below one when the populations approached their maximum observed abundance ($\gtrsim$ `r pa.lam.nf.at.one`%).
-However, when accounting for fishing mortality ($\lambda_{F>0}$), the modelled relationship dropped below one when the population abundance exceeded approximately `r pa.lam.fish.at.one`% of their maximum abundance.
+This suggests that there was a surprisingly large range of stock abundances that would not be expected to exhibit strong compensatory dynamics.
+The predicted population growth rate excluding the impacts of fishing ($\lambda_{F=0}$) only declined below one when the stocks approached their maximum observed abundance ($\gtrsim$ `r pa.lam.nf.at.one`%).
+However, when accounting for fishing mortality ($\lambda_{F>0}$), the modelled relationship dropped below one when the stock abundance exceeded approximately `r pa.lam.fish.at.one`% of their maximum abundance.
 At lower abundances, the model estimated population growth rate excluding fishing ($\lambda_{F=0}$) increased more slowly than realized population growth rates ($\lambda_{F>0}$) likely due to reductions in fishing mortality at low abundance.
@@
 While there was a consistent overall pattern, the estimated random effects demonstrated substantial variability among stocks in the strength of negative density dependence.
-For examples, populations in the western Atlantic (particularly Atlantic cod) and Alaska had some of the lowest $\lambda_{F=0}$ estimates at low abundance, while several populations in the North Sea (including Atlatnic cod) had among the highest $\lambda_{F=0}$ estimates at low abundance (Table \@ref(tab:tab-lambdas)).
-Of the `r n.bl.40` populations that had declined below 40% of the maximum abundance, only `r n.low.40.nf` of the populations had $\lambda_{F=0}$ estimates < 1 at 40% of their maximum abundance; when the effects of fishing were included `r n.low.40.nf` of the populations had $\lambda_{F>0}$ estimates below 1 (Table \@ref(tab:tab-lambdas)).
+For examples, stocks in the western Atlantic (particularly Atlantic cod) and Alaska had some of the lowest $\lambda_{F=0}$ estimates at low abundance, while several stocks in the North Sea (including Atlatnic cod) had among the highest $\lambda_{F=0}$ estimates at low abundance (Table \@ref(tab:tab-lambdas)).
+Of the `r n.bl.40` stocks that had declined below 40% of the maximum abundance, only `r n.low.40.nf` of the stocks had $\lambda_{F=0}$ estimates < 1 at 40% of their maximum abundance; when the effects of fishing were included `r n.low.40.nf` of the stocks had $\lambda_{F>0}$ estimates below 1 (Table \@ref(tab:tab-lambdas)).
 
-The vast majority of populations the lowest values of both $\lambda_{F=0}$ (`r n.low.lam.at.max.nf` of `r n.stocks`) and $\lambda_{F>0}$ (`r n.low.lam.at.max.fish` of `r n.stocks`) were found near the maximum abundance in the time series, this conforms to the expectations of this type of historical reconstruction and population dynamics theory (i.e., negative density dependence; see Supplemental Figures \@ref(fig:dd-nf-stock-plt) and \@ref(fig:dd-fish-stock-plt)).
-However, Atlantic cod in the Northwest Atlantic comprised `r n.cod.lam.not.at.max.nf` of the `r n.stocks - n.low.lam.at.max.nf` populations in which the lowest population growth rates were observed at abundances markedly below the maximum.
-These Atlantic cod populations seemed to have the least compensatory capacity at relative abundances between `r pa.low.cod.min` and `r pa.low.cod.max` even when excluding the impacts of fishing mortality.
-For two of the `r n.stocks - n.low.lam.at.max.nf` populations, the lowest $\lambda_{F=0}$ estimates were less than 0.005 smaller than the estimate at the maximum abundance, indicating extremely similar compensatory capacity over the majority of observed stock sizes.
-The declines in $\lambda_{F=0}$ for the other four populations were more pronounced (Supplemental Figure \@ref(fig:dd-nf-stock-plt)), ranging from `r low.4.lam.40.nf` to `r low.lam.40.nf` (Tables \@ref(tab:tab-lambdas) and \@ref(tab:tab-lamda-diffs)).
+The vast majority of stocks the lowest values of both $\lambda_{F=0}$ (`r n.low.lam.at.max.nf` of `r n.stocks`) and $\lambda_{F>0}$ (`r n.low.lam.at.max.fish` of `r n.stocks`) were found near the maximum abundance in the time series, this conforms to the expectations of this type of historical reconstruction and population dynamics theory (i.e., negative density dependence; see Supplemental Figures \@ref(fig:dd-nf-stock-plt) and \@ref(fig:dd-fish-stock-plt)).
+However, Atlantic cod in the Northwest Atlantic comprised `r n.cod.lam.not.at.max.nf` of the `r n.stocks - n.low.lam.at.max.nf` stocks in which the lowest population growth rates were observed at abundances markedly below the maximum.
+These Atlantic cod stocks seemed to have the least compensatory capacity at relative abundances between `r pa.low.cod.min` and `r pa.low.cod.max` even when excluding the impacts of fishing mortality.
+For two of the `r n.stocks - n.low.lam.at.max.nf` stocks, the lowest $\lambda_{F=0}$ estimates were less than 0.005 smaller than the estimate at the maximum abundance, indicating extremely similar compensatory capacity over the majority of observed stock sizes.
+The declines in $\lambda_{F=0}$ for the other four stocks were more pronounced (Supplemental Figure \@ref(fig:dd-nf-stock-plt)), ranging from `r low.4.lam.40.nf` to `r low.lam.40.nf` (Tables \@ref(tab:tab-lambdas) and \@ref(tab:tab-lamda-diffs)).
 
@@
 This difference between the mean and median for stocks experiencing exploitation, again highlighted the importance of large reproductive events to persistence by maintaining the latent capacity for population growth (Figure \@ref(fig:r0-6-plt)).
-For species which were found across the North Atlantic, the lifetime reproductive output when excluding fishing mortality tended to decline from east to west, which again was most evident for the Atlantic cod populations.
-While the reproductive potential of cohorts within a population could be highly variable, there were no clear temporal trends in $R_0$ (Figures \@ref(fig:r0-nf-ts-plt) and \@ref(fig:r0-fish-ts-plt)).
+For species which were found across the North Atlantic, the lifetime reproductive output when excluding fishing mortality tended to decline from east to west, which again was most evident for the Atlantic cod stocks.
+While the reproductive potential of cohorts within a stock could be highly variable, there were no clear temporal trends in $R_0$ (Figures \@ref(fig:r0-nf-ts-plt) and \@ref(fig:r0-fish-ts-plt)).
 
@@
 However, there were regional and interspecific patterns that were unexpected.
-For example, Atlantic herring is typically considered to be a short-lived species yet its generation length in the Central and western Atlantic tended to be higher than the generation length of Atlantic cod and haddock (especially for the populations in the eastern Atlantic; (Figure \@ref(fig:gl-6-plt)).
-Similar to lifetime reproductive output there were no obvious temporal trends in the generation length among cohorts for the populations in this analysis  (Figures \@ref(fig:gl-nf-ts-plt) and \@ref(fig:gl-fish-ts-plt)).
+For example, Atlantic herring is typically considered to be a short-lived species yet its generation length in the Central and western Atlantic tended to be higher than the generation length of Atlantic cod and haddock (especially for the stocks in the eastern Atlantic; (Figure \@ref(fig:gl-6-plt)).
+Similar to lifetime reproductive output there were no obvious temporal trends in the generation length among cohorts for the stocks in this analysis  (Figures \@ref(fig:gl-nf-ts-plt) and \@ref(fig:gl-fish-ts-plt)).
 
 Based on simulated stock trajectories, the recovery potential in the absence of fishing was relatively high for the majority of species (Figure \@ref(fig:dub-time-map)).
-Of the `r n.stocks` populations in this analysis, `r n.dub.10` had at least 75% of the simulations double in size withing 10 years, which increased to `r n.dub.20` populations by 20 years (Figure \@ref(fig:dub-ts)).
+Of the `r n.stocks` stocks in this analysis, `r n.dub.10` had at least 75% of the simulations double in size withing 10 years, which increased to `r n.dub.20` stocks by 20 years (Figure \@ref(fig:dub-ts)).
 Conversely, there were clear regional trends in stocks with low recovery potential.
-Of the `r n.not.dub.20` populations in this analysis in which < 50% of simulations doubled in size after 20 years, `r n.alaska.slow` were in Alaska and `r n.nwa.slow` in NAFO Regions 2-4 in the western Atlantic.
+Of the `r n.not.dub.20` stocks in this analysis in which < 50% of simulations doubled in size after 20 years, `r n.alaska.slow` were in Alaska and `r n.nwa.slow` in NAFO Regions 2-4 in the western Atlantic.
 This meant that `r prop.slow.alaska`% and `r prop.slow.n24`% of assessed stocks in Alaska and NAFO Regions 2-4, respectively, had low recovery potential.
-This contrasts to only `r n.nea.slow` of the `r n.nea` populations in the eastern Atlantic with a low recovery potential within 20 years in the absence of fishing (Figure \@ref(fig:dub-time-map)).
+This contrasts to only `r n.nea.slow` of the `r n.nea` stocks in the eastern Atlantic with a low recovery potential within 20 years in the absence of fishing (Figure \@ref(fig:dub-time-map)).
 
@@
 The recovery potential was influenced both b$\lambda_{F=0}$ and the variability in $\lambda_{F=0}$.
-Populations with a median $\lambda_{F=0} < 1$  had moderate (defined as populations in which 50-75% of the simulations doubled within 20 years) to high (> 75% doubled in size within 20 years) recovery potential whenever the standard deviation in $\lambda$ was $\gtrsim$ 0.4 (Figure \@ref(fig:dub-vs-sd)).
-Populations with a median $\lambda_{F=0}$ near 1 and with low variability tended to be stocks with low recovery potential.
+Stocks with a median $\lambda_{F=0} < 1$  had moderate (defined as stocks in which 50-75% of the simulations doubled within 20 years) to high (> 75% doubled in size within 20 years) recovery potential whenever the median $\lambda_{F=0}$ was $\gtrsim$ `r ` lam.rebuild.safe or the standard deviation in $\lambda$ was $\gtrsim$ `r sd.rebuild.safe` (Figure \@ref(fig:dub-vs-sd)).
+Stocks with a median $\lambda_{F=0}$ near 1 and with low variability tended to be stocks with low recovery potential.

### 2025-02-03 Drafts/Paper_1/07-tables.Rmd

@@
 # Tables {-}
+
+```{r, process}
+# This will be the meta data really...
+# remove columns we don't need.
+
+rm.meta <- which(names(meta.sub) %in% c("Meeting_or_reference","G.short","G.Species","Manage.short","LME","Area.broad","Area.long","Area.narrow","Stock.short","Stock","Model","Case","Notes","Area"))
+meta.4.tab <- meta.sub[,-rm.meta]
+re.ord <- c(8,2:7,1)
+meta.4.tab <- meta.4.tab[,re.ord]
+names(meta.4.tab) <- c("Stock", "Order", "Family", "Genus", "Species", "Minimum Age", "Maximum Age", "Management Body")
+
+```
+
+```{r,tab-lambdas}
+# The table with the lambda values
+csas_table(comp.lam.res.tab,caption ="A comparison of the $\\lambda_{F=0}$ and $\\lambda_{F>0}$ estimates for stock at the minimum and maximum abundance, along with the estimate at 40\\% of the maximum abundance.
+values greater than 1 indicate that the population would be expected to increase in size, while values less than 1 indicate the population is likely to decline in size")
+```
+
+\newpage
+
+```{r,tab-lamda-diffs}
+# Now make the table for the differences
+csas_table(comp.lam.diff.res.tab,caption ="A comparison of the difference in $\\lambda_{F=0}$ and $\\lambda_{F>0}$ for each stock at the minimum and maximum abundance, along with the change at 40\\% of the maximum abundance.
+Positive values indicate that the $\\lambda$ estimae has increased as abundance declines (consistent with negative density dependence), while negative values indicate the $\\lambda$ estimate has declined (considtent with positive density dependence)")
+```
+
+```{r,tab-meta}
+# Now make the table for the differences
+csas_table(meta.4.tab,caption ="Summary of the stocks included in this analysis.  The minimun and maximum ages are what was used in the stock assessment.")
+```

### 2025-02-03 Drafts/Paper_1/08-figures.Rmd

@@
 ```{r lambda-bx-other-fig, echo=F, fig.cap="$\\lambda$ estimates for the remainder of the stocks in this analysis, plotted by the location of the stock.
-The abreviated species name is provided on the x axis."}
+The abbreviated species name is provided on the x axis."}
 knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"))

### 2025-02-03 Scripts/Test_for_danielle.Rmd
more more more

@@
 }
-
-```
-
-  So now I can try to do some tuning, both forwards and backwards, lets see what we get from that...
-
-```{r tunes,include=F,echo=F,warning=F,message=F}
 
@@
   #}
-
-}# end if load results
-
 ```

### 2025-02-03 Scripts/archive/ASR_stocks.Rmd

--- 2023-10-24 Scripts/ASR_stocks.Rmd
@@
 loc <- 'D:/GitHub/ICM'
+loc <- "C:/Users/Owner/Documents/GitHub/ICM/"
 
@@
   weight.age <- ASR_sub %>% dplyr::filter(type=="WA") %>% dplyr::rename(WA=value) %>% dplyr::select(-type)
+  if(i == Stocks[30]) weight.age$WA <- weight.age$WA/1000
   removals <- ASR_sub %>% dplyr::filter(type=="Catch") %>% dplyr::rename(Catch=value) %>% dplyr::select(-type)
@@
 # Now we can run the figures separately.
-# tuned.res <- readRDS(file = "D:/Github/ICM/Results/tuned_fits.Rds")
-back.ts <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
-back.ts.quants <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
-back.res <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
-load(file = "D:/Github/ICM/Results/model_inputs.Rdata")
+#tuned.res <- readRDS(file = paste0(loc,"/Results/tuned_fits.Rds"))
+back.ts <- readRDS(file = paste0(loc,"/Results/backwards_sim_ts_summaries.Rds"))
+back.ts.quants <- readRDS(file = paste0(loc,"/Results/backwards_sim_ts_quantiles_summaries.Rds"))
+back.res <- readRDS(file = paste0(loc,"/Results/backwards_sim_results.Rds"))
+for.res <- readRDS(file = paste0(loc,"/Results/forwards_sim_results.Rds"))
+for.ts <- readRDS(file = paste0(loc,"/Results/forwards_sim_ts_summaries.Rds"))
+for.ts.quants <- readRDS(file = paste0(loc,"/Results/forwards_sim_ts_quantiles_summaries.Rds"))
+
+loc <- "C:/Users/Owner/Documents/Github/ICM"
+load(file =  paste0(loc,"/Results/model_inputs.Rdata"))
+load(file = paste0(loc,"/Results/all_cleaned_forward_tune_summaries_fec_nm.Rdata"))
+
+Stocks <- unique(for.tunes$Stock)
 
@@
   # Unpack the lists
-  tunes <- tuned.res[[i]] 
-  did.it.work <- back.ts[[i]] 
-  quants <- back.ts.quants[[i]] 
-  missing_rem <- mr.tmp[[i]] 
-  tst <- back.res[[i]]
+ #tunes <- tuned.res[[i]] 
+  did.it.work <- for.tunes |> collapse::fsubset(Stock == i) 
+  #quants <- back.ts.quants[[i]] 
+  #missing_rem <- mr.tmp[[i]] 
+ # tst <- back.res[[i]]
 
-  did.it.work$missing[did.it.work$years %in% missing_rem] <- "missing"
+  #did.it.work$missing[did.it.work$years %in% missing_rem] <- "missing"
 
@@
   p2 <- ggplot() +
-          geom_line(data=did.it.work, aes(x=years,y=abund,color=sim)) +
+          geom_line(data=did.it.work, aes(x=year,y=est.abund),color='blue') +
+          geom_line(data=did.it.work, aes(x=year,y=vpa.abund), color='black') +
           xlab("") +
           ylab("Abundance (1000s)") +
-          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
+          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
           #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
           theme_few() + theme(legend.position = 'none') + scale_color_viridis_d(end = 0.75) +
-          ggtitle(i) +
-          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p2, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/runs_vs_vpa_", i, ".png"), base_width = 6,base_height = 4)
+          ggtitle(i) #+
+          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
+  save_plot(plot = p2, filename = paste0(loc,"/Figures/tuned/", i, "/tuned_vs_vpa_", i, ".png"), base_width = 10,base_height = 8)
   # Same thing but functional boxplots
-  p3 <- ggplot() +
-          geom_line(data=quants, aes(x=years,y= med)) +
-          geom_ribbon(data=quants, aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue') +
-          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
-          xlab("") + ylab("Abundance (1000s)") +
-          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') + #geom_vline()
-          ggtitle(i)+
-          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p3, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/runs_vs_vpa_ribbon_", i, ".png"), base_width = 6,base_height = 4)
+  # p3 <- ggplot() +
+  #         geom_line(data=quants, aes(x=years,y= med)) +
+  #         geom_ribbon(data=quants, aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue') +
+  #         geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
+  #         xlab("") + ylab("Abundance (1000s)") +
+  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
+  #         theme_few() + theme(legend.position = 'none') + #geom_vline()
+  #         ggtitle(i)+
+  #         geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
+  # save_plot(plot = p3, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/runs_vs_vpa_ribbon_", i, ".png"), base_width = 6,base_height = 4)
 
   # Plotting how the estimate of r changes over time (which you can do when we have time varying inputs (e.g. Wgt, M, or maturity at age)
-  p4 <- ggplot(tst$r) +
-          geom_line(aes(x=years,y=r,group=n.sims,color=n.sims)) +
+  p4 <- ggplot(did.it.work) +
+          geom_line(aes(x=year,y=lambda)) +
           xlab("") +
-          ylab("Lotka r") +
+          ylab("Lambda") +
           #scale_y_continuous(breaks = seq(0,1.5,by=0.1)) +
@@
           ggtitle(i)
-  save_plot(plot = p4, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/lokta_r_", i, ".png"), base_width = 6,base_height = 4)
+  save_plot(plot = p4, filename = paste0(loc,"/Figures/tuned/", i, "/lambda_", i, ".png"), base_width = 10,base_height = 8)
 
   # Comparing our new time series with the old
-  p2 <- ggplot() +
-          geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
-          geom_line(data=tunes$res, aes(x=year,y=vpa.n),color='black') +
-          xlab("") +
-          ylab("Abundance (1000s)") +
-          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
-          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') +
-          ggtitle(i) #+
-          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p2, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/tunded_vs_vpa_", i, ".png"), base_width = 6,base_height = 4)
+  # p2 <- ggplot() +
+  #         geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
+  #         geom_line(data=tunes$res, aes(x=year,y=vpa.n),color='black') +
+  #         xlab("") +
+  #         ylab("Abundance (1000s)") +
+  #         #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
+  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
+  #         theme_few() + theme(legend.position = 'none') +
+  #         ggtitle(i) #+
+  #         #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
+  # save_plot(plot = p2, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/tunded_vs_vpa_", i, ".png"), base_width = 6,base_height = 4)
 
   # Comparing the absolute miss from the tuned time series
-   p3 <- ggplot() +
-          #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
-          geom_line(data=tunes$res[-1,], aes(x=year,y=diff.n),color='red') +
-          xlab("") +
-          ylab("Difference in abundance (1000s)") +
-          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
-          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') + 
-          ggtitle(i) 
-          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p3, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/diff_N_", i, ".png"), base_width = 6,base_height = 4)
+  #  p3 <- ggplot(did.it.work) +
+  #         #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
+  #         geom_line( aes(x=year,y=diff.n),color='red') +
+  #         xlab("") +
+  #         ylab("Difference in abundance (1000s)") +
+  #         #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
+  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
+  #         theme_few() + theme(legend.position = 'none') + 
+  #         ggtitle(i) 
+  #         #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
+  # save_plot(plot = p3, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/diff_N_", i, ".png"), base_width = 6,base_height = 4)
 
   # What percentage (mean) difference
-   p4 <- ggplot() +
-          #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
-          geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.n),color='red') +
+  #  p4 <- ggplot() +
+  #         #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
+  #         geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.n),color='red') +
+  #         xlab("") +
+  #         ylab("Difference in abundance (%)") +
+  #         #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
+  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
+  #         theme_few() + theme(legend.position = 'none') + 
+  #         ggtitle(i) #+ ylim(c(-100,100))
+  #         #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
+  # save_plot(plot = p4, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/per_diff_N_", i, ".png"), base_width = 6,base_height = 4)
+
+     # Difference in m's
+   p5 <- ggplot(did.it.work) +
+          geom_line( aes(x=year,y=mean.nm),color='blue') +
+          geom_line( aes(x=year,y=mean.vpa.nm),color='black') +
           xlab("") +
-          ylab("Difference in abundance (%)") +
+          ylab("Natural mortality (Instantaneous)") +
           #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
@@
           #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p4, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/per_diff_N_", i, ".png"), base_width = 6,base_height = 4)
+  save_plot(plot = p5, filename = paste0(loc,"/Figures/tuned/", i, "/Nat_mort_", i, ".png"), base_width = 10,base_height = 8)
+     # % Difference in m's
+  #  p6 <- ggplot() +
+  #         geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.m),color='red') +
+  #         xlab("") +
+  #         ylab("Difference in natural mortality (%)") +
+  #         #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
+  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
+  #         theme_few() + theme(legend.position = 'none') + 
+  #         ggtitle(i) #+ ylim(c(-100,100))
+  #         #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
+  # save_plot(plot = p6, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/per_diff_m_", i, ".png"), base_width = 6,base_height = 4)
 
-     # Difference in m's
-   p5 <- ggplot() +
-          geom_line(data=tunes$res[-1,], aes(x=year,y=diff.m),color='red') +
+    p6 <- ggplot(did.it.work) +
+          geom_line( aes(x=year,y=mean.fec),color='blue') +
+          geom_line( aes(x=year-1,y= mean.vpa.fec),color='black') +
           xlab("") +
-          ylab("Difference in natural mortality (Instantaneous)") +
+          ylab("Recruits (Number) per spawner (kg female)") +
           #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
@@
           #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p5, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/diff_m_", i, ".png"), base_width = 6,base_height = 4)
-     # % Difference in m's
-   p6 <- ggplot() +
-          geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.m),color='red') +
-          xlab("") +
-          ylab("Difference in natural mortality (%)") +
-          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
-          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') + 
-          ggtitle(i) #+ ylim(c(-100,100))
-          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p6, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/per_diff_m_", i, ".png"), base_width = 6,base_height = 4)
-
-   p7 <- ggplot() +
-          geom_line(data=tunes$res[-1,], aes(x=year,y=mn.m),color='blue') +
-          geom_line(data=tunes$res[-1,], aes(x=year,y=vpa.m),color='black') +
-          xlab("") +
-          ylab("Natural mortality (Instantaneous)") +
-          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
-          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') +
-          ggtitle(i) #+
-          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p7, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/Nat_M_", i, ".png"), base_width = 6,base_height = 4)
-
-     p8 <- ggplot() +
-          geom_line(data=tunes$res[-1,], aes(x=year,y=r),color='blue') +
-          xlab("") +
-          ylab("Lotka r") +
-          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
-          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
-          theme_few() + theme(legend.position = 'none') +
-          ggtitle(i) #+
-          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
-  save_plot(plot = p8, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/Lotka_r_", i, ".png"), base_width = 6,base_height = 4)
+  save_plot(plot = p6, filename = paste0(loc,"/Figures/tuned/", i, "/Fecundity_", i, ".png"), base_width = 10,base_height = 8)
 

### 2025-02-03 Scripts/archive/Paper_1.Rmd

--- 2024-04-09 Scripts/Paper_1.Rmd
@@
 source(paste0(loc,"/Scripts/functions/tuning_sim_fast.R"))
+
+# Download the functions we'll need from github
+  funs <- c("https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/simple_Lotka_r.r",
+            "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/backwards_project.r",
+            "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/forward_project.r",
+            "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/tuning_sim_fast.R",
+
+  )
+  # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
+  for(fun in funs) 
+  {
+    download.file(fun,destfile = basename(fun))
+    source(paste0(getwd(),"/",basename(fun)))
+    file.remove(paste0(getwd(),"/",basename(fun)))
+  }
 
